### 2019-04-16 GW_BH_function/manuscript_GW_constrain_BHmass/main.tex
Push the paper draft

\documentclass[twocolumn]{aastex62}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand\s{$\sim$}
\newcommand{\e}{\'{e}}
\newcommand{\amen}[1]{\textbf{\textit{#1}}}

\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{mathrsfs}

\usepackage{float}
\usepackage{multirow}
\usepackage{enumitem}

\shorttitle{Black hole mass function and redshift evolution by ET}
\shortauthors{Marian et al.}

\begin{document}

\newcommand{\mbh}{$\mathcal M_{\rm BH}$}
\newcommand{\cmass}{${\cal M}_0$}
\newcommand{\dl}{$d_L$}
\newcommand{\mone}{$m_1$}
\newcommand{\mtwo}{$m_2$}
\newcommand{\snr}{$\rho$}

\title{Black hole mass function and redshift evolution by ET}

\correspondingauthor{Xuheng Ding}
\email{dingxh@whu.edu.cn}

\author%[0000-0001-8917-2148]
{Xuheng Ding}
\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-
1547, USA}

\author{Lilan Yang}
\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-
1547, USA}

\author%[0000-0003-1308-7304]
{Marek Biesiada}
\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
\affiliation{Department of Astrophysics and Cosmology, Institute of Physics, University of Silesia, 75 Pu{\l}ku Piechoty 1, 41-500 Chorz{\'o}w,
Poland}

\author%[0000-0002-4359-5994]
{Kai Liao}
\affiliation{School of Science, Wuhan University of Technology, Wuhan 430070, China}

\author%[0000-0002-3567-6743]
{Zong-Hong Zhu}
\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}

\begin{abstract}
%discover of GW
%Measure of BH mass and thus fit the BH mass.
%The discovery of double compact objects by GW provide a the measurement of their BH masses. Recent works by LIGO group have constrained 10 GW event and constrain the BHs. The ET would detect more GW events with DL and BH mass up to redshift $z\sim10$, and thus enable one to constrain the mass function and study how it evolution with redshift. In this work, test the ability of 1000 GWs events by ET. We tested, 1. how well are they able to recover the BH mass function as power law distribution. 2. If the GW events are able to tell a redshifted-related BH mass function.
We demonstrate the ability of future gravitational-wave (GW) measured by third generation detector Einstein telescope (ET) to infer the slope of the BH mass function (BHMF) and its evolution with redshift. %The measurement of BH binary systems enable the inference of the BH mass (\mone\ and \mtwo\ of each component) together with the luminosity distance (\dl).
We performed Monte Carlo approach to simulate the measurements of BH binaries GW signals as detected by ET, including the BH masses and their luminosity distance (\dl). Following the recent works by Kovetz et al. (2017) and LIGO-Virgo (2018), we consider the more massive black hole in each binary and model the BHMF as a function of power law with slope parameter as $\alpha$. We find that only a thousand GW events ($\sim1\%$ amount of the yearly detection rate) could measure the $\alpha$ to $3\%$ accuracy level. Furthermore, we investigate a scenario that  $\alpha$ is evolving with redshift. We find that using the \dl\ as redshift estimator, one is able to distinguish the evolution trend between positive and negative. This may help to understand the origin of the BHs and how BH binaries formed at different stage of the Universe.

\end{abstract}

\keywords{keywords TBD}

\section{Introduction} \label{sec_intro}
As first identified as a solution to Einstein's field equations by Schwarzschild in 1916, black holes (BHs) have been predicted to remain a bunches of fundamental questions in unifying GR with quantum physics (Hawking 1976; Giddings 2017). The mass of BHs is known to cover a wide range from stellar-mass to supermassive ($\sim10^{10} M_{\odot}$). The recent discovery of gravitational-wave (GW) measurement is a substantial evidence of stellar-mass BHs (Abbott et al. 2016), while supermassive BHs are thought to be existed in the centers of most all the galaxies. More recently, the first image of supermassive BH in the center of the giant elliptical galaxy M87 has been reconstructed by radio-wave observations. Nevertheless, in theory, it is still unclear of how the BHs are formed. The prediction for the number and mass distribution of stellar-mass BHs is still in the Universe is needed to be more clear.

The recent detections by LIGO bring us to a new era of GW astronomy. \textcolor{blue}{COPY THE INTRODUCE THE RECENT LIGO RESULT: Overall, advanced LIGO in its 2015 O1 run observed three1 BH coalescence events, adding nine additional measured black hole masses to the current data (the six premerger masses range from roughly 7 to 36 Mstar). Over the next decade, improvements in detector sensitivities are expected to usher in a wave of newly detected events. LIGO itself is scheduled to perform two more runs (O2,3) with increasing sensitivity before commencing a multiyear run at its design sensitivity at the turn of the decade.} 
The GWs provide a direct way to hear the inspiralling binary BH (BBH) systems, enable one to derive their information including mass, spin, luminosity distance.
This bring us the opportunity to measure the population of BHs and help to answer some fundamental questions such as the cosmography, the GW speed. the strong lensing effects. 
%The detection of GWs are able one to measure the BH mass thus understand the BH mass function. Introducing the importance of BH mass function.

More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF as power law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility). The previous work (Kovetz 2017) has investigated that further LIGO measurements from thousands of BBHs can be taken to infer the power law index $\alpha$ at 10\% accuracy. In this study, we pay extra attentions on simulating the GW events that could be measured by ET based Monte Carlo (MC) approach. This provides us a BBHs catalog with realistic dataset to exam their ability to constrain the BHMFs, putting the data noise level, selection effects in a more realistic way. Moreover, the ET would detect the GW event at distant Universe up to $z\sim17$; we take the luminosity distance as the redshift estimator and exam whether one could detect the $\alpha$ as a function of redshift.

This paper is organized as follows. In Sec~\ref{sec_simulation} we describe the simulation of the BBHs events that detected by ET using MC approach. In this section, we adopt our initial assumptions for the BH mass function as the truth. In Sec~\ref{sec_theory}, we introduce the theoretical framework as used to reconstruct the BHMFs, including the noise realization and the selection effects. Furthermore, we make a further step by considering the power law index $\alpha$ as a function of redshift and explore the way to use luminosity distance as redshift estimator and detect such evolution. We present our results in the Section. The discussion and conclusions are given in the final Section.

Throughout this paper, we assume a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.

\section{Data simulation} \label{sec_simulation}
%\subsection{The simulation of GW events and the detection by ET} \label{subsec_BHMF_redshift}
%Rather than numerical calculation, we use Monto Carlo to simulate the GW signal.
%1. We randomly generate the DCOs with redshift number density as the Dominique's startrack.
%2. We consider for each event,  we randomly assuming its properties, including  $\Theta$, with BH mass as power law.
%3. Knowing the DL, $\Theta$, $\cal M$, we are able to simulation their $\rho$ and test whether could be detected by ET.
%4. Add noise level. We assuming the Dl, $\cal M$, $m_1$, $m_2$ as lognormal distribution.
%\begin{itemize}
%%\renewcommand\labelitemi{--}
%\item We randomly generate the DCOs with redshift number density as the Dominique's startrack.
%\item We consider for each event,  we randomly assuming its properties, including  $\Theta$, with BH mass as power law.
%\item Knowing the DL, $\Theta$, $\cal M$, we are able to simulation their $\rho$ and test whether could be detected by ET.
%\item Add noise level. We assuming the Dl, $\cal M$, $m_1$, $m_2$ as lognormal distribution.
%\end{itemize}
We simulate the GW signal of BBHs that would be obtained in the future ET detection in this section. The nurmecial predictions of the events heard by ET have been discussed in many works, and forecasted that the yearly detection rate of BBHs would be $\sim10^{4-5}.$ More recently, Yang et al. (2019) developed the MC approach to predict the detection rate by explicitly considering each BBHs event, which provides the way to mimic a realistic BBH GW catalog for us to test. The backbone is to build up a mock universe which includes a sufficient volume of BBH events to represent the overall.  We refer the reader for the details in Yang et al. (section 2, 2019) and briefly recall the key points here.

\subsection{Detection Criteria} \label{subsec_criteria}
The values of the key parameters that determined the GW signal-to-noise ratio (\snr) are randomly generated. For a specific BBG event at redshift $z_s$, the ET's reaction of this event is:

\begin{equation} \label{SNR}
\rho = 8 \Theta \frac{r_0}{d_L(z_s)} \left( \frac{(1+z){\cal M}_0}{1.2 M_{\odot}} \right)^{5/6}
\sqrt {\zeta(f_{max})},
\end{equation}
where $r_0$ is the detector's characteristic distance parameter and $\zeta(f_{max})$ is the dimensionless function reflecting the overlap between the GW signal and the ET's effective bandwidth which is usually simplified as unity. ${\cal M}_0$ is the intrinsic chirp mass which is calculated as $ {\cal M}_0 = \frac{(m_1m_2)^{3/5}}{(m_1+m_2)^{1/5}}$, where the \mone\ and \mtwo\ are the each BH mass in the binary. $\Theta$ is the orientation factor determined by four angles as:
 \begin{equation} \label{Theta}
 \Theta = 2 [ F_{+}^2(1 + \cos^2{\iota} )^2 + 4 F_{\times}^2 \cos^2{\iota} ]^{1/2},
 \end{equation}
where: $F_{+} = \frac{1}{2} (1 + \cos^2{\theta}) \cos{2\phi} \cos{2 \psi} - \cos{\theta} \sin{2 \phi} \sin{ 2 \psi}$, and
$F_{\times} = \frac{1}{2} (1 + \cos^2{\theta}) \sin{2\phi} \cos{2 \psi} + \cos{\theta} \sin{2 \phi} \cos{ 2 \psi}$ are so-called antenna patterns. The four angles ($\theta, \phi, \psi, \iota$) are independent, with $(\cos\theta, \phi/\pi, \psi/\pi, \cos\iota)$ distributed uniformly over the range $[-1, 1]$.

The GW signals are considered as detectable if their \snr\ are over the detecting threshold, i.e., $\rho > \rho_0 = 8$.

\subsection{Monte Carlo Approach} \label{MC}
We build up a sufficient volume of BBHs systems in the mock universe, and randomly generate the key parameters for each BBH systems. To build up this volume, we follow previous steps by adopting the intrinsic BBH merger rates $\dot{n}_{0}(z_{s})$ predicted by the population synthesis model (using {\tt StarTrack} code\footnote{The data is taken from the website \url{http://www.syntheticuniverse.org}.}) in Dominik et al. (2013). Therefore, the yearly  merging rate of BBH sources in a redshift interval  $[z_{s}, z_{s}+dz_{s}]$ is 
 \begin{equation}
 d\dot{N} (z_s)=4\pi\left(\frac{c}{H_{0}}\right)^3\frac{\dot{n}_{0}(z_{s})}{1+z_{s}}\frac{\tilde{r}^2(z_{s})}{E(z_{s})}dz_{s}. 
 \end{equation}
Hence, the overall BBHs in the universe can be calculated as ${\dot N} = \int_0^{ \infty} \frac{d {\dot N (z)}}{dz} dz$.

For each BBH systems, we following the possibility distribution of the key parameters to randomly generate their values. The key parameters includes the four angles (i.e., $\theta, \phi, \psi, \iota$, see the Equation~\ref{Theta} and its description) and the each BH mass in the binary systems (i.e., \mone\ and \mtwo).

To randomly simulate the BH masses, we follow the previous works by LIGO 2019 and assuming the BHMF of the more massive BH mass, \mone, following a power law distribution as:
 \begin{equation} \label{equ_powlaw}
p(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),
 \end{equation}
where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo, is fix as uniform between $[M_{min}, m_1]$. Note that, in the next section, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ would not affect our inference for the shape of BHMF.

The generation of these parameters would determine the value of $\Theta$ and ${\cal M}_0$. We combine them with their redshift to realize the $\rho$ of each BBH system.
We aim to collect the events which have $\rho > \rho_0 = 8$ so as to estimate the yearly detection rate.

In this paper, we consider the BHMF as two scenarios. In the first scenario, the $\alpha$ is a constant value and we adopt the values $\alpha~=~2.35$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ as our fiducial model. In the second scenario, we consider that $\alpha$ varies as a function of redshift in formalism as:
 \begin{equation} \label{equ_alphaz}
\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z} , 
 \end{equation}

so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$. We adopt the values $\alpha_0~=~2.35$, $\alpha_1~=~0.75$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ as the truth.

\subsection{Measurement Error} \label{sec_noiselevel}
Our simulation provides a mock dataset of the future GW events as measured by ET. To consider the measurements in a realistic way, we take the random statistical errors into account here.

We assume the observed probability distribution with their uncertainty level of the data, including the \mone, \mtwo, and \dl. In theory, the \mone\ and \mtwo\ are constrained from the combining of the chirp mass (a direct measurement by the inspiral) and the total mass (i.e., \mone+\mtwo, which is more sensitive to the ringdown waveform).

In Archisman et al. (2015), the expected statistical errors of the measurement has been estimated with Bayesian parameter estimation. We adopt their implications as our guidance to setup noise level of our simulated data.  Nevertheless, we note that the measurements of the GW are ${\it skewed}$. Other than the traditional Gaussian distribution, we assume the properties of the measurements follow the Log-Normal distribution (i.e. their $log$ value follows the Gaussian). As a consequence, we assume the standard deviation of \mone\ \dl, and ${\cal M}_0$ as 0.2, 0.35 and 0.17, respectively. For instance, if the $m_{1,fid}$ is the true value for \mone, its possibility distribution of measured value follows:
 \begin{equation} \label{equ_lognorm}
p(m) = \frac{1}{m\sigma\sqrt{2\pi}} exp \big(- \frac{log(m)-log(m_{1,fid})}{2\sigma} \big) 
 \end{equation}

As a demonstration, we list a thousand-like simulated data in Table~\ref{tab_GW_mock_data}, which we would take to infer the BHMFs in one realization.

\begin{deluxetable}{lccc}
\tablecolumns{4}
\tablewidth{0pt}
\tablecaption{Details of Observation} 
\tablehead{ 
\colhead{Object ID} &
\colhead{\mone}&
\colhead{Luminosity Distance} & 
\colhead{Chirp Mass}
\\ 
\colhead{} &
\colhead{($M_\odot$)}&
\colhead{Mpc} & 
\colhead{($M_\odot$)}
\\
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)}
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
ID1 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID2 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID3 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID4 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID5 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID6 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID7 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID8 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID9 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID10 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
... & $...$ & ... & ... \\
ID901 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID902 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID903 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID904 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID905 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID906 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID907 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID908 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID909 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
ID1000 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
\enddata
\label{tab_GW_mock_data}
\tablecomments{
A demonstration of a thousand-like GW catalog.
}
\end{deluxetable}

\section{Theoretical Framework}  \label{sec_theory}
In this section, we describe the fitting for the parameterized BHMFs. 
In principle, the modeling for a dataset which follows power-law distribution as Equation~\ref{equ_powlaw} is very straightforward. One just needs to combining all the measured points together by:
 \begin{equation} \label{equ_likeli_simple}
 P(\alpha, M_{max}, M_{min}) =  \prod_{i=1}^{total} P(m_{1,i}|\alpha, M_{max}, M_{min}).
 \end{equation}
However, the observed \mone\ are deviated from a power-law by several processes. In the rest of this section, we introduce them and explore the ways to reconstruct the non-biased likelihood.

\subsection{Measurement Errors}\label{sec_likelihood_noise}
We assumed the intrinsic \mone\ follows a power-law distribution, however the measured  \mone\ are disturbed by Log-Normal distribution and thus they do not follow a power-law function any more (C. Koen 2009).

In theory, if event $X$ follows a power-law distribution and is observed subject to the Gaussian error, then $X + e$ is distributed as the convolution of the power-law and Gaussian distributions. Likewise, given that our data are observed as Log-Normal distribution, the intrinsic power-law should be convolved in the likelihood as:
 \begin{equation} \label{equ_likelihood_conv}
 P(\alpha, M_{max}, M_{min}) =  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min}),
 \end{equation}
where the $\hat{P}$ is the convolved power-law function convolved with the Log-Normal distribution using the standard deviation as 0.2 as we assumed. We illustrate the effect of such convolving in this figure.

\begin{figure}%[!b]
\includegraphics[width=1.05\linewidth]{convolving.pdf}
\caption{
Figure illustrate the convolving of a power-law distribution by a Log-Normal distribution with $\sigma = 0.2$. One can see that the convolution make slope is shallower and the smooth the breaking edge at $m_1 = 5 M_{\odot}$.
}
\label{fig:result_slope}
\end{figure}

\subsection{Selection Effect}\label{sec_likelihood_sf}
The observation has tendency to discover more significant events. Those GW systems with higher values \mone\ trend to stronger signals and thus more easier to be detected. If not well handled, the final BHMFs would be biased with higher fraction at the high mass end.

To overcome the selection effects, we calculated the selection factor $\eta$ for the GW event, which is the detecting possibility of one event, if simulating again. The physical meaning of this factor $\eta$ is straightforward -- if one GW event has $\eta=0.2$ indicates this event has 80\% possibility would be missed. In other words, there are four equivalent events that has been missed. Thus, for this event, one needs to re-calibrate its emergency by manually enhance likelihood by a power of 5. Hence, to account for the global selection effect, 
 \begin{equation} \label{equ_powlaw_like}
 P(\alpha, M_{max}, M_{min}) =  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta}.
 \end{equation}

Note that the $\eta$ is directly estimated by the possibility distribution of $\rho$, i.e. Equation~\ref{SNR}, which is determined by the distribution function of $\Theta$. In Equation~\ref{SNR}, the \cmass\ and \dl\ have been provided in the mock dataset as demonstrated in Table~\ref{tab_GW_mock_data}. However, the redshift is the unknown parameter. Though its non-measurable in the GW detection, we introduce to take the \dl\ as redshift estimator in the following section and test our re-calibration for selection effect in Section~\ref{sec_result}.

\subsection{Luminosity Distance as Redshift Estimator} 
%The redshift is not detectable by GW, however, can be inferred from the DL. 
We take \dl\ as the redshift estimator so as to derive the selection factor $\eta$. The way to derive the $z$ is quite straightforward: simply an inverse solution of integral function when knowing the \dl$(z)$ and fixing the cosmological model.

Moreover, inferring the $z$ provide a way to model the slope BHMF as a function of redshift. Thus, we consider the second scenario (i.e. Equation~\ref{equ_alphaz}) to model the $\alpha$ as a function of redshift:
 \begin{equation} \label{equ_likelihood_alphaz}
 \begin{split}
 P&(\alpha_0, \alpha_1, M_{max}, M_{min}) = \\
  &\prod_{i=1}^{total} \hat{P}(m_{1i}, z_{inf,i} |\alpha_0, \alpha_1, M_{max}, M_{min})^{1/\eta}.
  \end{split}
 \end{equation}

\vspace{1cm}

\section{Result}\label{sec_result}
We present the result in this section.

An appendix to introduce the correction for the skewness for the $\eta$.

\begin{figure*}%[!b]
\begin{tabular}{c c}
\includegraphics[width=0.5\linewidth]{fig_results_3para.pdf} &
\includegraphics[width=0.5\linewidth]{fig_results_4para.pdf} \\
\end{tabular}
\caption{
The main figure... 
}
\label{fig:result_slope}
\end{figure*}

\section{Summary \& Conclusions} \label{sec:summary}

In this study, we simulated the GWs event and test it ability on constrain the BH. We find that:

Our results are consistent with...

\acknowledgments

This work was supported by the National Basic Science Program (Project 973) of China under (Grant No. 2014CB845800), the National Natural Science Foundation of China under Grants Nos. 11633001 and 11373014, the Strategic Priority Research Program of the Chinese Academy of Sciences, Grant No. XDB23000000 and the Interdiscipline Research Funds of Beijing Normal University.

X. Ding acknowledges support by China Postdoctoral Science Foundation Funded Project (No. 2017M622501).
L. Yang is supported from the China Scholarship Council. 
M.B. was supported by the Key Foreign Expert Program for the Central Universities No. X2018002.
K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. 11603015.
\software{
        corner,
        Matplotlib \citep{matplotlib},
        }

\newpage

%\appendix

%\section{section}\label{appendix_section}
%TEXTTEXTTEXTTEXTTEXTTEXTTEXTTEXTTEXT
%\newpage

\bibliography{reference}
%\input{reference.bbl}

\end{document}

### 2019-05-08 GW_BH_function/manuscript_GW_constrain_BHmass/main.tex
finish paper draft on my side

@@
 
-\title{Black hole mass function and redshift evolution by ET}
+\title{The first prediction of Black hole mass function and its evolution by ET}
 
@@
 \affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
-\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-
-1547, USA}
+\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
 
-\author{Lilan Yang}
-\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
-\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-
-1547, USA}
+%\author{Lilan Yang}
+%\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
+%\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
 
@@
 
-\author%[0000-0002-4359-5994]
-{Kai Liao}
-\affiliation{School of Science, Wuhan University of Technology, Wuhan 430070, China}
+%\author%[0000-0002-4359-5994]
+%{Kai Liao}
+%\affiliation{School of Science, Wuhan University of Technology, Wuhan 430070, China}
 
@@
 If the GW events are able to tell a redshifted-related BH mass function.
-We demonstrate the ability of future gravitational-wave (GW) measured by third generation detector Einstein telescope (ET) to infer the slope of the BH mass function (BHMF) and its evolution with redshift.
+We demonstrate the ability of future gravitational-wave (GW) measured by third generation detector Einstein Telescope (ET) to infer the slope of the BH mass function (BHMF) and its evolution with redshift.
 %The measurement of BH binary systems enable the inference of the BH mass (\mone\ and \mtwo\ of each component) together with the luminosity distance (\dl).
-We performed Monte Carlo approach to simulate the measurements of BH binaries GW signals as detected by ET, including the BH masses and their luminosity distance (\dl).
-Following the recent works by Kovetz et al.
-(2017) and LIGO-Virgo (2018), we consider the more massive black hole in each binary and model the BHMF as a function of power law with slope parameter as $\alpha$.
-We find that only a thousand GW events ($\sim1\%$ amount of the yearly detection rate) could measure the $\alpha$ to $3\%$ accuracy level.
-Furthermore, we investigate a scenario that  $\alpha$ is evolving with redshift.
-We find that using the \dl\ as redshift estimator, one is able to distinguish the evolution trend between positive and negative.
-This may help to understand the origin of the BHs and how BH binaries formed at different stage of the Universe.
+We performed the Monte Carlo approach to simulate the measurements of BH binaries GW signals as detected by ET, including the BH masses and their luminosity distance (\dl).
+Following the previous works, we consider the mass of  primary black hole in each binary and model the BHMF as a function of the power law with slope parameter as $\alpha$.
+We take into account the bias that would be raised by the uncertainty of the measurement and the selection effect and find that a thousand GW events measure by ET ($\sim1\%$ amount of the yearly detection rate) could measure the $\alpha$ to $3\%$ accuracy level.
+Furthermore, we investigate a scenario, by the first time, that  $\alpha$ is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
+Our result is that, taking the \dl\ as redshift estimator, with a thousand GW events one is capable of obtaining an unbiased $\alpha_1$ at the uncertainty level of $\pm0.5$.
+The ability of known the evolution scenario of BHMF would help to understand the origin of the BHs and how BH binaries formed at the different stage of the Universe.
 
@@
 \section{Introduction} \label{sec_intro}
-As first identified as a solution to Einstein's field equations by Schwarzschild in 1916, black holes (BHs) have been predicted to remain a bunches of fundamental questions in unifying GR with quantum physics (Hawking 1976; Giddings 2017).
+As first identified as a solution to Einstein's field equations by Schwarzschild in 1916 \citep{Schwarzschild1999}, black holes (BHs) have been predicted to remain a bunches of fundamental questions in unifying GR with quantum physics \citep{Hawking1976, Giddings2017}.
 The mass of BHs is known to cover a wide range from stellar-mass to supermassive ($\sim10^{10} M_{\odot}$).
-The recent discovery of gravitational-wave (GW) measurement is a substantial evidence of stellar-mass BHs (Abbott et al.
-2016), while supermassive BHs are thought to be existed in the centers of most all the galaxies.
-More recently, the first image of supermassive BH in the center of the giant elliptical galaxy M87 has been reconstructed by radio-wave observations.
-Nevertheless, in theory, it is still unclear of how the BHs are formed.
-The prediction for the number and mass distribution of stellar-mass BHs is still in the Universe is needed to be more clear.
+The recent discovery of gravitational-wave (GW) measurement is a substantial evidence of stellar-mass BHs \citep{Abbott2016}, while supermassive BHs are thought to existe in the centers of almost all the galaxies \citep{Lynden-Bell1969, Kormendy1995}.
+More recently, the first image of supermassive BH in the center of the giant elliptical galaxy M87 has been reconstructed by radio-wave observations \citep{Alberdi2019}.
+Nevertheless, in theory, it is still unclear of how the BHs are formed \citep{Fryer1999, Fryer2001, Mirabel2016}.
+The prediction for the number and mass distribution of stellar-mass BHs in the Universe is still needed to be more clear.
 
-The recent detections by LIGO bring us to a new era of GW astronomy.
-\textcolor{blue}{COPY THE INTRODUCE THE RECENT LIGO RESULT: Overall, advanced LIGO in its 2015 O1 run observed three1 BH coalescence events, adding nine additional measured black hole masses to the current data (the six premerger masses range from roughly 7 to 36 Mstar).
-Over the next decade, improvements in detector sensitivities are expected to usher in a wave of newly detected events.
-LIGO itself is scheduled to perform two more runs (O2,3) with increasing sensitivity before commencing a multiyear run at its design sensitivity at the turn of the decade.}
-The GWs provide a direct way to hear the inspiralling binary BH (BBH) systems, enable one to derive their information including mass, spin, luminosity distance.
-This bring us the opportunity to measure the population of BHs and help to answer some fundamental questions such as the cosmography, the GW speed. the strong lensing effects. 
-%The detection of GWs are able one to measure the BH mass thus understand the BH mass function. Introducing the importance of BH mass function.
+The recent GW detection activities have brought us to a new era of GW astronomy \citep[e.g.,][]{Abbott2016, Abbott2016_sum, Abbott2018}.
+To date, the LIGO and Virgo have achieved two successful runs (O1 and O2) and now is performing the third run (O3).
+In the first run O1 (from September 12th, 2015 to January 19th, 2016), the first catalog of binary BH (BBH) inspiral systems have been measured including three BBH systems.
+In the O2 run (from November 30th, 2016 to August 25th, 2017), a total of seven binary black hole mergers have been detected\footnote{Together with the first detection of GW from detection of binary neutron star inspiral system.}.
+In the next decade, the volume of the events is expected to be increasing rapidly with the improvements in the detector sensitivities.
 
-More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF as power law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility).
-The previous work (Kovetz 2017) has investigated that further LIGO measurements from thousands of BBHs can be taken to infer the power law index $\alpha$ at 10\% accuracy.
-In this study, we pay extra attentions on simulating the GW events that could be measured by ET based Monte Carlo (MC) approach.
-This provides us a BBHs catalog with realistic dataset to exam their ability to constrain the BHMFs, putting the data noise level, selection effects in a more realistic way.
-Moreover, the ET would detect the GW event at distant Universe up to $z\sim17$; we take the luminosity distance as the redshift estimator and exam whether one could detect the $\alpha$ as a function of redshift.
+The GWs provide a direct way to hear the inspiralling BBH systems, enable one to derive their information including mass, spin, luminosity distance\citep{Abbott2017phy}.
+This brings us the opportunity to measure the population of BHs \citep{Abbott2018b} and helps to answer some fundamental questions such as the cosmography\citep{Liao2017, Ding2019, Cai2017}, the GW speed\citep{Fan2017, Collett2017}, the strong lensing effects~\citep{Ola2013, Biesiada2014, Ding2015}.
+The previous work \citet{Kovetz2017PhRvD} has investigated that further LIGO measurements from thousands of BBHs can be taken to infer the power law index $\alpha$ at 10\% accuracy.
+More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF as power law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility) \citep{Abbott2018b}.
+In this study, we pay extra attention on simulating the GW events that could be measured by third-generation gravitational waves detector, Einstein Telescope (ET) \citep{Abernathy2011} based Monte Carlo (MC) approach.
+This provides us a mock BBHs catalog with the realistic dataset to exam their ability to constrain the BHMFs, taking into the effects by the data noise level, selection bias in a more realistic way.
+Moreover, the ET would detect the GW event at distant Universe up to $z\sim17$ \citep{Abernathy2011}.
+The wide redshift range of the events enable us to exam whether it is possible to detect the $\alpha$ as a function of redshift.
 
 This paper is organized as follows.
-In Sec~\ref{sec_simulation} we describe the simulation of the BBHs events that detected by ET using MC approach.
-In this section, we adopt our initial assumptions for the BH mass function as the truth.
-In Sec~\ref{sec_theory}, we introduce the theoretical framework as used to reconstruct the BHMFs, including the noise realization and the selection effects.
+In Sec~\ref{sec_simulation} we describe the simulation of the BBHs events that detected by ET using the Monte Carlo approach.
+In this section, we assume the initial assumptions for the BH mass function as the truth.
+In Sec~\ref{sec_theory}, we introduce the theoretical framework to reconstruct the BHMFs, considering the noise realization and the selection effects.
 Furthermore, we make a further step by considering the power law index $\alpha$ as a function of redshift and explore the way to use luminosity distance as redshift estimator and detect such evolution.
-We present our results in the Section.
-The discussion and conclusions are given in the final Section.
+We present our results in the Section~\ref{sec_result}.
+The discussion and conclusions are given in the last Section~\ref{sec_summary}.
 
@@
 
+\vspace{1cm}
 \section{Data simulation} \label{sec_simulation}
@@
 We simulate the GW signal of BBHs that would be obtained in the future ET detection in this section.
-The nurmecial predictions of the events heard by ET have been discussed in many works, and forecasted that the yearly detection rate of BBHs would be $\sim10^{4-5}.$ More recently, Yang et al.
-(2019) developed the MC approach to predict the detection rate by explicitly considering each BBHs event, which provides the way to mimic a realistic BBH GW catalog for us to test.
-The backbone is to build up a mock universe which includes a sufficient volume of BBH events to represent the overall.
-We refer the reader for the details in Yang et al.
-(section 2, 2019) and briefly recall the key points here.
+The numerical predictions of the events heard by ET have been discussed in many works, and forecasted that the yearly detection rate of BBHs would be $\sim10^{4-5}$ \citep{Abernathy2011, Ola2013, Biesiada2014}.
+More recently, \citet{Yang2019} developed the approach the Monte Carlo (MC) simulation to predict the detection rate by explicitly considering each BBHs event, which provides the way to mimic a realistic BBH GW catalog.
+The backbone is to build up a mock universe which includes a sufficient volume of BBH events to represent the overall sample.
+We refer the reader for the details in \citet[][Section 2, therein]{Yang2019}  and briefly recall the key points here.
 
 \subsection{Detection Criteria} \label{subsec_criteria}
-The values of the key parameters that determined the GW signal-to-noise ratio (\snr) are randomly generated. For a specific BBG event at redshift $z_s$, the ET's reaction of this event is:
+We randomly generated the key parameters to determine the intensity (i.e., signal-to-noise ratio, SNR) of each GW system.
+For a specific BBH event at redshift $z_s$, the ET's corresponding reaction is defined as \citep{Abernathy2011}:
 
@@
 ${\cal M}_0$ is the intrinsic chirp mass which is calculated as $ {\cal M}_0 = \frac{(m_1m_2)^{3/5}}{(m_1+m_2)^{1/5}}$, where the \mone\ and \mtwo\ are the each BH mass in the binary.
-$\Theta$ is the orientation factor determined by four angles as:
+$\Theta$ is the orientation factor determined by four angles as \citep{Finn93}:
  \begin{equation} \label{Theta}
@@
 The four angles ($\theta, \phi, \psi, \iota$) are independent, with $(\cos\theta, \phi/\pi, \psi/\pi, \cos\iota)$ distributed uniformly over the range $[-1, 1]$.
-
-The GW signals are considered as detectable if their \snr\ are over the detecting threshold, i.e., $\rho > \rho_0 = 8$.
+Note that the GW signals are considered as detectable if their \snr\ are over the detecting threshold, i.e., $\rho > \rho_0 = 8$.
 
@@
 We build up a sufficient volume of BBHs systems in the mock universe, and randomly generate the key parameters for each BBH systems.
-To build up this volume, we follow previous steps by adopting the intrinsic BBH merger rates $\dot{n}_{0}(z_{s})$ predicted by the population synthesis model (using {\tt StarTrack} code\footnote{The data is taken from the website \url{http://www.syntheticuniverse.org}.}) in Dominik et al.
-(2013).
+To build up this volume, we follow previous steps by adopting the intrinsic BBH merger rates $\dot{n}_{0}(z_{s})$ predicted by the population synthesis model (using {\tt StarTrack} code\footnote{The data is taken from the website \url{http://www.syntheticuniverse.org}.}) in \citet{Dominik13}.
 Therefore, the yearly  merging rate of BBH sources in a redshift interval  $[z_{s}, z_{s}+dz_{s}]$ is
@@
  \end{equation}
-Hence, the overall BBHs in the universe can be calculated as ${\dot N} = \int_0^{ \infty} \frac{d {\dot N (z)}}{dz} dz$.
+Hence, the overall amount of BBH events in the universe can be calculated by ${\dot N} = \int_0^{ \infty} \frac{d {\dot N (z)}}{dz} dz$.
 
 For each BBH systems, we following the possibility distribution of the key parameters to randomly generate their values.
-The key parameters includes the four angles (i.e., $\theta, \phi, \psi, \iota$, see the Equation~\ref{Theta} and its description) and the each BH mass in the binary systems (i.e., \mone\ and \mtwo).
+These key parameters include the four angles (i.e., $\theta, \phi, \psi, \iota$ in Equation~\ref{Theta}) and the masses of each BHs in the binary systems (i.e., \mone\ and \mtwo).
 
-To randomly simulate the BH masses, we follow the previous works by LIGO 2019 and assuming the BHMF of the more massive BH mass, \mone, following a power law distribution as:
+To randomly generate the BH masses, we follow the previous works \citep{Kovetz2017PhRvD, Abbott2018b, Fishbach2018} and assume the \mone\ follows a power law distribution with hard cut at both maximum and minimum mass:
  \begin{equation} \label{equ_powlaw}
@@
 Then, the secondary mass, \mtwo, is fix as uniform between $[M_{min}, m_1]$.
-Note that, in the next section, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ would not affect our inference for the shape of BHMF.
+Note that, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ actually does not affect the inference for the shape of BHMF.
+The generation of these parameters would determine the value of $\Theta$ and ${\cal M}_0$ in Equation~\ref{SNR}.
+We combine them with their redshift to realize the $\rho$ of each BBH system.
+We collect the events which have $\rho > \rho_0 = 8$, meaning that those events with $\rho < 8$ are to faint to be detected.
 
-The generation of these parameters would determine the value of $\Theta$ and ${\cal M}_0$. We combine them with their redshift to realize the $\rho$ of each BBH system.
-We aim to collect the events which have $\rho > \rho_0 = 8$ so as to estimate the yearly detection rate.
-
-In this paper, we consider the BHMF as two scenarios.
-In the first scenario, the $\alpha$ is a constant value and we adopt the values $\alpha~=~2.35$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ as our fiducial model.
+We consider the BHMF contains two scenarios.
+In the first scenario, the $\alpha$ is a constant value and the shape of the BHMF is fix throughout the redshfit.
 In the second scenario, we consider that $\alpha$ varies as a function of redshift in formalism as:
@@
  \end{equation}
-
 so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$.
-We adopt the values $\alpha_0~=~2.35$, $\alpha_1~=~0.75$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ as the truth.
 
 \subsection{Measurement Error} \label{sec_noiselevel}
-Our simulation provides a mock dataset of the future GW events as measured by ET. To consider the measurements in a realistic way, we take the random statistical errors into account here.
+We aim to produce the mock dataset of the future GW events as measured by ET.
+To consider the measurement error in a realistic way, we inject the random statistical errors into the mock data in this section.
 
-We assume the observed probability distribution with their uncertainty level of the data, including the \mone, \mtwo, and \dl.
-In theory, the \mone\ and \mtwo\ are constrained from the combining of the chirp mass (a direct measurement by the inspiral) and the total mass (i.e., \mone+\mtwo, which is more sensitive to the ringdown waveform).
-
-In Archisman et al.
-(2015), the expected statistical errors of the measurement has been estimated with Bayesian parameter estimation.
-We adopt their implications as our guidance to setup noise level of our simulated data.
-Nevertheless, we note that the measurements of the GW are ${\it skewed}$.
+The measurement of the BBH inspiral parameters including the \dl, chirp mass, m1, m2, and SNR.
+In practice, the \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass (i.e., \mone+\mtwo, which is more sensitive to the ringdown waveform).
+We adopt the implications by \citet{Ghosh2016}, which explore the statistical errors of the measurement with Bayesian parameter estimation, as our recipe to set up the noise level of our simulated data.
+In addition, we note that the measurements of the GW are ${\it skewed}$.
 Other than the traditional Gaussian distribution, we assume the properties of the measurements follow the Log-Normal distribution (i.e.
-their $log$ value follows the Gaussian).
-As a consequence, we assume the standard deviation of \mone\ \dl, and ${\cal M}_0$ as 0.2, 0.35 and 0.17, respectively.
+their $log$ value follows the Gaussian) with the standard deviation as 0.2, 0.35 and 0.17 for \mone\ \dl, and ${\cal M}_0$, respectively.
 For instance, if the $m_{1,fid}$ is the true value for \mone, its possibility distribution of measured value follows:
@@
 
-As a demonstration, we list a thousand-like simulated data in Table~\ref{tab_GW_mock_data}, which we would take to infer the BHMFs in one realization.
+Having clarified the MC approach and defined data the uncertainty level, we are capable of producing the mock GW dataset.
+As a demonstration, we list a thousand-like simulated data in Table~\ref{tab_GW_mock_data}, which we would take to infer the BHMFs in per realization.
 
-\begin{deluxetable}{lccc}
-\tablecolumns{4}
+\begin{deluxetable}{lcccc}
+\tablecolumns{5}
+\tabletypesize{\footnotesize}
 \tablewidth{0pt}
-\tablecaption{Details of Observation} 
+\tablecaption{Demonstration of the mock GW catalog} 
 \tablehead{ 
@@
 \colhead{Luminosity Distance} & 
-\colhead{Chirp Mass}
+\colhead{Chirp Mass} &
+\colhead{SNR}
 \\ 
@@
 \colhead{($M_\odot$)}&
-\colhead{Mpc} & 
-\colhead{($M_\odot$)}
+\colhead{(Mpc)} & 
+\colhead{($M_\odot$)} &
+\colhead{(\snr)}
 \\
@@
 \colhead{(3)} &
-\colhead{(4)}
+\colhead{(4)} &
+\colhead{(5)}
 } 
@@
 %\\
-ID1 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID2 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID3 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID4 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID5 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID6 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID7 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID8 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID9 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID10 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-... & $...$ & ... & ... \\
-ID901 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID902 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID903 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID904 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID905 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID906 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID907 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID908 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID909 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
-ID1000 & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ & $11.05\substack{+0.15\\-0.11}$ \\
+ID1 & $95.85\substack{+21.22\\-17.37}$  & $87120.7\substack{+19288.8\\-15792.3}$  & $61.87\substack{+13.70\\-11.21}$ & 28.707 \\
+ID2 & $13.31\substack{+2.95\\-2.41}$  & $81476.5\substack{+18039.1\\-14769.2}$  & $11.68\substack{+2.59\\-2.12}$ & 10.468 \\
+ID3 & $7.40\substack{+1.64\\-1.34}$  & $7456.8\substack{+1651.0\\-1351.7}$  & $6.82\substack{+1.51\\-1.24}$ & 39.673 \\
+ID4 & $19.02\substack{+4.21\\-3.45}$  & $96201.9\substack{+21299.4\\-17438.4}$  & $19.11\substack{+4.23\\-3.46}$ & 12.227 \\
+ID5 & $15.12\substack{+3.35\\-2.74}$  & $47645.3\substack{+10548.8\\-8636.6}$  & $14.24\substack{+3.15\\-2.58}$ & 12.672 \\
+ID6 & $18.95\substack{+4.20\\-3.43}$  & $23937.4\substack{+5299.8\\-4339.1}$  & $13.86\substack{+3.07\\-2.51}$ & 16.027 \\
+ID7 & $8.65\substack{+1.92\\-1.57}$  & $44053.0\substack{+9753.4\\-7985.4}$  & $6.99\substack{+1.55\\-1.27}$ & 8.383 \\
+ID8 & $40.03\substack{+8.86\\-7.26}$  & $60432.5\substack{+13379.9\\-10954.6}$  & $25.53\substack{+5.65\\-4.63}$ & 17.917 \\
+ID9 & $32.58\substack{+7.21\\-5.91}$  & $4293.5\substack{+950.6\\-778.3}$  & $18.58\substack{+4.11\\-3.37}$ & 34.190 \\
+ID10 & $9.88\substack{+2.19\\-1.79}$  & $50294.8\substack{+11135.4\\-9116.9}$  & $4.65\substack{+1.03\\-0.84}$ & 9.608 \\
+... & $...$ & ... & ... & ...\\
+ID991 & $7.90\substack{+1.75\\-1.43}$  & $10175.7\substack{+2252.9\\-1844.5}$  & $7.31\substack{+1.62\\-1.32}$ & 9.354 \\
+ID992 & $15.48\substack{+3.43\\-2.81}$  & $8058.1\substack{+1784.1\\-1460.7}$  & $17.14\substack{+3.80\\-3.11}$ & 11.149 \\
+ID993 & $6.11\substack{+1.35\\-1.11}$  & $9566.9\substack{+2118.1\\-1734.2}$  & $4.11\substack{+0.91\\-0.75}$ & 10.703 \\
+ID994 & $17.41\substack{+3.85\\-3.16}$  & $232095.1\substack{+51386.5\\-42071.7}$  & $14.46\substack{+3.20\\-2.62}$ & 8.444 \\
+ID995 & $23.76\substack{+5.26\\-4.31}$  & $127615.4\substack{+28254.4\\-23132.7}$  & $16.97\substack{+3.76\\-3.08}$ & 14.972 \\
+ID996 & $10.43\substack{+2.31\\-1.89}$  & $65546.6\substack{+14512.2\\-11881.6}$  & $6.96\substack{+1.54\\-1.26}$ & 9.497 \\
+ID997 & $5.79\substack{+1.28\\-1.05}$  & $24315.0\substack{+5383.4\\-4407.6}$  & $6.93\substack{+1.53\\-1.26}$ & 14.177 \\
+ID998 & $12.48\substack{+2.76\\-2.26}$  & $98731.2\substack{+21859.3\\-17896.9}$  & $6.85\substack{+1.52\\-1.24}$ & 13.340 \\
+ID999 & $6.95\substack{+1.54\\-1.26}$  & $75187.9\substack{+16646.8\\-13629.2}$  & $3.40\substack{+0.75\\-0.62}$ & 9.437 \\
+ID1000 & $6.53\substack{+1.45\\-1.18}$  & $27801.3\substack{+6155.3\\-5039.5}$  & $9.79\substack{+2.17\\-1.77}$ & 8.390 \\
+%... & $...$ & ... & ... \\
 \enddata
@@
 \tablecomments{
-A demonstration of a thousand-like GW catalog.
+A demonstration of a thousand-like GW catalog with properties are adopted to estimate the BHMF.
 }
@@
 
+\vspace{1cm}
 \section{Theoretical Framework}  \label{sec_theory}
 In this section, we describe the fitting for the parameterized BHMFs. 
-In principle, the modeling for a dataset which follows power-law distribution as Equation~\ref{equ_powlaw} is very straightforward. One just needs to combining all the measured points together by:
- \begin{equation} \label{equ_likeli_simple}
- P(\alpha, M_{max}, M_{min}) =  \prod_{i=1}^{total} P(m_{1,i}|\alpha, M_{max}, M_{min}).
+In principle, the modeling for a dataset which follows power-law distribution as Equation~\ref{equ_powlaw} is very straightforward.
+To derive the posterior of the parameters, one only needs to combine all the measured points together and joint the likelihood by:
+ \begin{equation} \label{equ_lik_powlaw}
+ P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} P(m_{1,i}|\alpha, M_{max}, M_{min}).
  \end{equation}
-However, the observed \mone\ are deviated from a power-law by several processes. In the rest of this section, we introduce them and explore the ways to reconstruct the non-biased likelihood.
+However, the obtained \mone\ in Table~\ref{tab_GW_mock_data} actually deviate from the initial power-law distribution.
+This deviation stems from several steps as exist in the realistic.
+In Section~\ref{sec_likelihood_noise} and \ref{sec_likelihood_sf}, we introduce them and explore the ways to account for.
 
-\subsection{Measurement Errors}\label{sec_likelihood_noise}
-We assumed the intrinsic \mone\ follows a power-law distribution, however the measured  \mone\ are disturbed by Log-Normal distribution and thus they do not follow a power-law function any more (C.
-Koen 2009).
-
+\subsection{Measurement Uncertainty}\label{sec_likelihood_noise}
+The intrinsic \mone\ follows a power-law distribution, however the measured  \mone\ are disturbed by Log-Normal distribution and thus they do not follow a power-law function anymore \citep{Koen2009}.
 In theory, if event $X$ follows a power-law distribution and is observed subject to the Gaussian error, then $X + e$ is distributed as the convolution of the power-law and Gaussian distributions.
-Likewise, given that our data are observed as Log-Normal distribution, the intrinsic power-law should be convolved in the likelihood as:
- \begin{equation} \label{equ_likelihood_conv}
- P(\alpha, M_{max}, M_{min}) =  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min}),
+Likewise, given that the nosied data follows the Log-Normal distribution, the intrinsic power-law should be convolved in the likelihood as:
+ \begin{equation} \label{equ_lik_conv}
+ P(\alpha, M_{max}, M_{min}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min}),
  \end{equation}
 where the $\hat{P}$ is the convolved power-law function convolved with the Log-Normal distribution using the standard deviation as 0.2 as we assumed.
-We illustrate the effect of such convolving in this figure.
+We illustrate the effect of such convolving in this Figure~\ref{fig:result_slope}.
 
@@
 \subsection{Selection Effect}\label{sec_likelihood_sf}
-The observation has tendency to discover more significant events.
-Those GW systems with higher values \mone\ trend to stronger signals and thus more easier to be detected.
-If not well handled, the final BHMFs would be biased with higher fraction at the high mass end.
+The observation the has tendency to discover more significant events, known as Malmquist bias.
+The GW systems with higher values \mone\ trend to stronger signals and thus have a higher possibility to be detected.
+If not well taking into account, the final BHMFs would be biased the high mass end in particular.
 
-To overcome the selection effects, we calculated the selection factor $\eta$ for the GW event, which is the detecting possibility of one event, if simulating again.
+To overcome the selection effects, we introduced the selection factor $\eta$ for the GW event, which is the detecting possibility of one event, if simulating again.
 The physical meaning of this factor $\eta$ is straightforward -- if one GW event has $\eta=0.2$ indicates this event has 80\% possibility would be missed.
-In other words, there are four equivalent events that has been missed.
+In other words, there are four equivalent events that would have been missed.
 Thus, for this event, one needs to re-calibrate its emergency by manually enhance likelihood by a power of 5.
 Hence, to account for the global selection effect,
- \begin{equation} \label{equ_powlaw_like}
- P(\alpha, M_{max}, M_{min}) =  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta}.
+ \begin{equation} \label{equ_lik_sf}
+ P(\alpha, M_{max}, M_{min}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta},
  \end{equation}
+$\eta$ is directly determined by the possibility distribution of $\rho$, i.e.
+$\eta = P(\rho>8)$.
+In Equation~\ref{SNR}, the distribution function of $\Theta$ has been known by the MC approach, the \cmass\ and \dl\ have been provided in the mock dataset as demonstrated in Table~\ref{tab_GW_mock_data}.
+Furthermore, the redshift is the unknown parameter since it is non-measurable in the GW detection.
+We thus take the \dl\ as redshift estimator.
 
-Note that the $\eta$ is directly estimated by the possibility distribution of $\rho$, i.e.
-Equation~\ref{SNR}, which is determined by the distribution function of $\Theta$.
-In Equation~\ref{SNR}, the \cmass\ and \dl\ have been provided in the mock dataset as demonstrated in Table~\ref{tab_GW_mock_data}.
-However, the redshift is the unknown parameter.
-Though its non-measurable in the GW detection, we introduce to take the \dl\ as redshift estimator in the following section and test our re-calibration for selection effect in Section~\ref{sec_result}.
+Note that the \dl\ and \cmass\ has asymmetry distribution with large scatter, result in the inferred $\eta$ distributed around its true value in a skewed-biased way.
+We find that this skewness could be well described by a Log-Normal distribution, with multiplicative standard deviation\footnote{In Log-Normal distribution, the multiplicative standard deviation is the exponent value of the standard deviation, i.e., $\sigma^* = exp(\sigma)$.} as $\sigma^*=log(\eta)/3$.
+Thus, we manually correct this skewness and obtain the non-biased $\eta$.
 
 \subsection{Luminosity Distance as Redshift Estimator} 
+\label{sec_dl_z}
 %The redshift is not detectable by GW, however, can be inferred from the DL. 
-We take \dl\ as the redshift estimator so as to derive the selection factor $\eta$.
+In the previous section, we take \dl\ as the redshift estimator to derive the redshift and hence selection factor $\eta$.
 The way to derive the $z$ is quite straightforward: simply an inverse solution of integral function when knowing the \dl$(z)$ and fixing the cosmological model.
 
-Moreover, inferring the $z$ provide a way to model the slope BHMF as a function of redshift.
-Thus, we consider the second scenario (i.e.
-Equation~\ref{equ_alphaz}) to model the $\alpha$ as a function of redshift:
- \begin{equation} \label{equ_likelihood_alphaz}
+Moreover, inferring the $z$ of the source provide an opportunity to model the slope BHMF as a function of redshift.
+Therefore, we are able to investigate the second scenario (i.e.
+Equation~\ref{equ_alphaz}) by:
+ \begin{equation} \label{equ_lik_alphaz}
  \begin{split}
- P&(\alpha_0, \alpha_1, M_{max}, M_{min}) = \\
+ P&(\alpha_0, \alpha_1, M_{max}, M_{min}) \propto \\
   &\prod_{i=1}^{total} \hat{P}(m_{1i}, z_{inf,i} |\alpha_0, \alpha_1, M_{max}, M_{min})^{1/\eta}.
@@
 
+ We present our inference for the BHMF using the mock data in the next section.
+
 \vspace{1cm}
+\section{Result}\label{sec_result}
+%We present the result in this section.
+%One thousand of data points.
+%An appendix to introduce the correction for the skewness for the $\eta$.
+We fit the mock data to the BHMF model to infer the distribution of the best-fitted parameter.
+To infer a non-biased distribution, we adopt the realization approach.
+The detail of the simulation if the following.
+In each realization, we simulate a thousand GW events and infer the best-fit parameters using minimization.
+We do not perform the realizations until the inferred best-fit parameters have converged and informative.
 
-\section{Result}\label{sec_result}
-We present the result in this section.
+In the first scenario, we consider the slope $\alpha$ as a constant.
+We generated the mock data by taking $\alpha~=~2.35$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ as the fiducial value.
+We calculate the likelihood by Equation~\ref{equ_lik_sf} to infer the best-fit parameters in each realization.
+In Figure~\ref{fig_result_a}, we present the distribution of the inference.
+We find that the non-biased results have inferred, with  best-fit parameters distributed as $\alpha = 2.36\substack{+0.09\\-0.08}$, $M_{max} = 80.54\substack{+5.45\\-5.60}$,  $M_{min} = 5.03\substack{+0.17\\-0.15}$.
+Our inference of $\alpha$ indicates that a thousand GW events could constrain the slope within $3.5\%$ level.
 
-An appendix to introduce the correction for the skewness for the $\eta$.
+\begin{figure}%[!b]
+\includegraphics[width=1.0\linewidth]{fig_results_3para.pdf}
+\caption{
+One- and two-dimensional distributions for the best-fit parameters of the scenario A.
+The BHMF is assumed as a power-law with hard cut at the $M_{min}$ and $M_{max}$, with a constant slope ($\alpha$) across all the redshift.
+}
+\label{fig_result_a}
+\end{figure}
 
-\begin{figure*}%[!b]
-\begin{tabular}{c c}
-\includegraphics[width=0.5\linewidth]{fig_results_3para.pdf} &
-\includegraphics[width=0.5\linewidth]{fig_results_4para.pdf} \\
-\end{tabular}
+In the second scenario, the $\alpha$ is evolution with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
+We take the fiducial parameters as $\alpha_0~=~2.35$, $\alpha_1~=~0.75$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ to generate a thousand datasets in each realization.
+We present the inference in Figure~\ref{fig_result_b}.
+Since the second scenario have one more parameters, the distribution of the best-fit parameters have larger scatter with inference as $\alpha_0 = 2.32\substack{+0.35\\-0.36}$, $\alpha_1 = 0.73\substack{+0.52\\-0.50}$, $M_{max} = 78.03\substack{+10.03\\-8.40}$ and  $M_{min} = 5.02\substack{+0.14\\-0.14}$.
+Not surprisingly, the convergency exsits between the $\alpha_0$ and $\alpha_1$.
+
+We highlight that in this test, it is the inferred uncertainty of $\alpha_1$ that matters.
+Our result show that, with a volume of one thousands GW measurements, the inferred value of $\alpha_1$ would have a precision of $\pm0.5$.
+That is to say, this volume of measurements is able to distinguish the evolution of BHMF, when $\alpha_1$ is deviated from 0 by a value of 0.5.
+Limited by the computing power, we haven't tested to use a larger sample of measurements.
+However, conjecturing that the precision of inference is increasing with the volume of sample as a function of $\sqrt{N}$, one year measurements of ET ($\sim10^5$ in total) would result in the $\alpha_1$ with precision down to $\sim0.05$.
+
+We also note that the distribution of the best-fit parameters ($\alpha_0$, $\alpha_1$) do not follows the Gaussian distribution, but rather a large fraction is converge at the center.
+As a result, the 1-$\sigma$ confidence interval in 2-D parameter space are narrower than the ones in 1-D space.
+\textcolor{blue}{(What does this suggest?)}
+
+\begin{figure}%[!b]
+\includegraphics[width=1.0\linewidth]{fig_results_4para.pdf}
 \caption{
-The main figure... 
+Same as Figure~\ref{fig_result_a} but for the scenario B, where the $\alpha$ of BHMF is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$. 
 }
-\label{fig:result_slope}
-\end{figure*}
+\label{fig_result_b}
+\end{figure}
 
-\section{Summary \& Conclusions} \label{sec:summary}
+\vspace{1cm}
+\section{Conclusion \& Discussion} \label{sec_summary}
+The third-generation gravitational waves detector, Einstein Telescope, is very powerful and capable of detecting $\sim10^5$ GW events per year, with redshift up to $z\sim17$.
+In this study, we investigated how the detections of the merger of BBHs improve our knowledge of the black hole mass function.
 
-In this study, we simulated the GWs event and test it ability on constrain the BH. We find that:
+We performed the Monte Carlo simulation to generate the mock measurements of GW signals of BBHs that would be detected by ET.
+As a starting point, we assume the BHMF for the primary BH mass follows power law distribution.
+Based on the BBH intrinsic merger rate predicted by {\tt StarTrack}, we randomly simulate the key parameters of the BBH systems, including the chirp mass, redshift and orientation factor and calculate the corresponding their signal-to-noise ratio \snr\ to ET.
+We collected the events whose \snr\ exceeds the detecting threshold and injected Log-Normal noise to the detected parameter, including BH mass, chirp mass, luminosity distance to simulate the mock data.
 
-Our results are consistent with...
+We built up a theoretical framework and explore to use the mock measurements to infer the BHMF.
+We take into account the measurement error and the selection effect which would lead bias in the inference.
+We use the realization approach, one thousand GW events per realization, and estimate the distribution of the best-fit parameters in the BHMF, including the power law slope $\alpha$, the maximum BH mass $M_{max}$ and the minimum BH mass $M_{min}$.
+Furthermore, we use the luminosity distance as redshift estimator and test whether one can infer the $\alpha$ as a function of redshift.
+We summarize our main results as follows:
+\begin{enumerate}
+\item Assuming the $\alpha$ is invariable with redshift, one could infer the $\alpha$, $M_{max}$ and $M_{min}$ with precisely and accurately.
+With one thousand measurements of BBHs events, the $\alpha$ would reach 3\% level, i.e., Figure~\ref{fig_result_a}.
+\item Testing the scenario that $\alpha$ is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$, our results show that a volume of one thousand measurements of BBHs events would derive the evolving parameter $\alpha_1$ with an uncertainty level of $\pm0.5$.
+Meaning that with one this volume of sample is able to recognize the evolution of BHMF when $\alpha_1$ is deviate from $0$ by 0.5.
+\item According to the fact that the precision of the inference increases with the sample size, as a function of $\sqrt{N}$, we conclude that one year BBH sample by ET would be able to deliver the value of $\alpha_1$ with precision down to 0.05.
+\end{enumerate}
+
+We point out a few limitations of this work.
+First, we have adopted a template of intrinsic BBH merger rate based on the predictions by a standard model in {\tt StarTrack}, which must be different from the realistic one.
+Of course, the intrinsic BBH merger rate is unknown yet, which is related to the different elements such as BBH masses, explosion mechanism, the metallicity history and the time delay distribution.
+Also, to simplify, we simulate the value of secondary BH mass \mtwo\ by assuming the two masses of BBHs have independent distribution, which probably not right.
+However, we address that these limitations affect the prediction of the yearly detection rate of the GW events and their distribution as the function of redshift, but possibly trivial for our case.
+The fact is that using a sample with the same volume but different redshift distribution, the inference on the BHMF parameters could be very similar.
+
+In this work, we focus on the inferring the BHMF using the mass properties by the BBH, it is worth to note its application to other approaches.
+For example, one could infer the spin of BH \citep{Abbott2018b}, the mass function for the binary of NS-NS, NS-BH system, though these events are detectable at lower redshift ($z<4$).
+In addition, using the luminosity as redshift estimator, one should be able to reconstruct the BBH intrinsic merger rate \citep{Fishbach2018}, the cosmological parameter.
 
 \acknowledgments
+We thank Hosek Jr., M.W for the useful discussion.
 
-This work was supported by the National Basic Science Program (Project 973) of China under (Grant No.
-2014CB845800), the National Natural Science Foundation of China under Grants Nos.
-11633001 and 11373014, the Strategic Priority Research Program of the Chinese Academy of Sciences, Grant No.
-XDB23000000 and the Interdiscipline Research Funds of Beijing Normal University.
+This work was supported by the National Natural Science Foundation of China under grant Nos.
+11633001 and 11373014, the Strategic Priority Research Program of the Chinese Academy of Sciences, grant No.
+XDB23000000, and the Interdiscipline Research Funds of Beijing Normal University.
 
 X. Ding acknowledges support by China Postdoctoral Science Foundation Funded Project (No. 2017M622501).
-L. Yang is supported from the China Scholarship Council. 
+%L. Yang is supported from the China Scholarship Council. 
 M.B. was supported by the Key Foreign Expert Program for the Central Universities No. X2018002.
-K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. 11603015.
+%K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. 11603015.
 \software{
-        corner,
-        Matplotlib \citep{matplotlib},
+         {\sc corner}, \citep{corner},
+        Matplotlib \citep{Matplotlib},
+        and standard Python libraries.
         }
 
-\newpage
+\bibliography{reference}
+%\input{reference.bbl}
 
+%\newpage
 %\appendix
-
 %\section{section}\label{appendix_section}
@@
 
-\bibliography{reference}
-%\input{reference.bbl}
+%\newpage
+%\appendix
+%\section{Correction for the skewness of the selection factor}\label{appA}
+%1. Describe the bias of the selection.
+%2. The correction by $\eta/3.$
 

### 2019-05-08 GW_BH_function/BH_mass_function.py

@@ -181,7 +181,7 @@ def r(z,om):
 vec_r=np.vectorize(r)
 def dl(z,om=0.3,h0=70):
     """
-    Calculate the luminosity distance.
+    Calculate the luminosity distance. In Mpc.
     """
     c=299790.
     dl_distance = (1+z) * c/h0 * vec_r(z,om=om)

### 2019-05-08 GW_BH_function/create_tab1.py

@@ -1,0 +1,174 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Nov 26 21:57:36 2018
+
+@author: Dartoon
+
+Test if whether the likelihood would recover the para
+if all the m1 are measureable.
+With error bar
+"""
+
+
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Nov 26 21:57:36 2018
+
+@author: Dartoon
+
+Generate the simulating data
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from BH_mass_function import gene_BHBH, dl, solve_z
+from cal_likelihood import fac_s_eff_v
+import pickle
+import glob
+import random
+import scipy.optimize as op
+import time
+
+a, mbh_max, mbh_min = 2.35, 80., 5.
+filename = 'sim_a_{0}_max_{1}_min_{2}'.format(round(a,2), round(mbh_max,1), round(mbh_min,1))
+if_file = glob.glob(filename)  
+test = gene_BHBH(h0=70)
+if if_file==[]:
+    event_rate, zs_detected, masses, rhos_detected = test.mc_year_rate(a=a, mbh_max=mbh_max, mbh_min=mbh_min)
+    dl_zs = dl(zs_detected)
+    sim_data = [event_rate, zs_detected, masses, rhos_detected, dl_zs]
+    pickle.dump(sim_data, open(filename, 'wb'))
+else:
+    event_rate, zs_detected, masses, rhos_detected, dl_zs=pickle.load(open(filename,'rb'))
+##averaged Chirp mass
+#print 'averaged Chirp mass, m1, m2: ', np.average(masses[:,0]), np.average(masses[:,1]), np.average(masses[:,2])
+#Generate the select biased m1.
+zs_all, chirp_mass_all, m1_all, m2_all, lumi_dis_all = zs_detected, masses[:,0], masses[:,1], masses[:,2], dl_zs                                                      
+#plt.hist(masses[:,:2])
+#plt.hist(zs_detected)
+#plt.hist(m1)
+#plt.hist(rhos_detected)
+#plt.plot(m1,m2,'.')
+#plt.yscale('log', nonposy='clip')
+#plt.show()
+#import corner
[…]

### 2019-05-08 GW_BH_function/read_corner.py

@@ -1,44 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Thu Jan 31 13:52:19 2019
-
-@author: Dartoon
-
-Read corner
-"""
-import numpy as np
-import astropy.io.fits as pyfits
-import matplotlib.pyplot as plt
-
-import corner
-#filename = 'test2_select-eff_correct_sigmalogdiv3_20.txt'
-#filename = 'few_tests/right_answer_test1_conv_lognorm_20.txt'
-pre_result = np.loadtxt('test3_result/test3_mode1_level20_npy.txt')
-bool_1 = (pre_result[:,1]>2.7)
-bool_2 = (pre_result[:,3]>95)
-bools = np.invert(bool_1+bool_2)
-result_rm_edge = pre_result[bools]
-result_new_edge = np.loadtxt('test3_result/test3_edge.txt')
-
-numbers = np.concatenate((result_rm_edge,result_new_edge))
-#%%
-#print filename
-#with open(filename) as f:
-#        content = f.readlines()
-#lines = [x.strip() for x in content] 
-#import re
-#lines = [re.findall("\d+\.\d+", lines[i]) for i in range(len(lines))]
-#lines = [lines[i] for i in range(len(lines)) if len(lines[i]) ==4]
-#numbers = np.asarray(lines).astype(float)
-samples = numbers#[numbers[:,1]<3]
-fig = corner.corner(numbers[:,1:], labels=["a0", "a1", "mbh_max", "mbh_min"],
-                    truths=[2.35, 0.7, 80., 5.],
-                    quantiles=[0.16, 0.84],show_titles=True,
-                    title_kwargs={"fontsize": 12},#truths=[2.35,80,5],
-#                    plot_datapoints=True,smooth=1.0,smooth1d=1.0,
-                    levels=1.0 - np.exp(-0.5 * np.arange(1, 2.1, 1) ** 2),
-                    title_fmt='.2f')
-#fig.savefig("test1_lognorm_likeli.pdf")
-#####
-plt.show()  

### 2019-05-08 GW_BH_function/read_para3_corner.py

@@ -1,0 +1,50 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Jan 31 13:52:19 2019
+
+@author: Dartoon
+
+Read corner
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import corner
+
+import matplotlib
+import matplotlib as matt
+matt.rcParams['font.family'] = 'STIXGeneral'
+cmap = matplotlib.cm.get_cmap('viridis')
+
+filename = 'test2_select-eff_correct_sigmalogdiv3_20.txt'
+#filename = 'few_tests/right_answer_test1_conv_lognorm_20.txt'
+#pre_result = np.loadtxt('test3_result/test3_mode1_level20_npy.txt')
+#bool_1 = (pre_result[:,1]>2.7)
+#bool_2 = (pre_result[:,3]>95)
+#bools = np.invert(bool_1+bool_2)
+#result_rm_edge = pre_result[bools]
+#result_new_edge = np.loadtxt('test3_result/test3_edge.txt')
+#numbers = np.concatenate((result_rm_edge,result_new_edge))
+#%%
+print filename
+with open(filename) as f:
+        content = f.readlines()
+lines = [x.strip() for x in content] 
+import re
+lines = [re.findall("\d+\.\d+", lines[i]) for i in range(len(lines))]
+lines = [lines[i] for i in range(len(lines)) if len(lines[i]) ==3]
+numbers = np.asarray(lines).astype(float)
+#samples = numbers#[numbers[:,1]<3]
+fig = corner.corner(numbers, labels=[r"$\alpha$", "M$_{max}$", "M$_{min}$"],
+                    truths=[2.35, 80., 5.],
+                    quantiles=[0.16, 0.5, 0.84],show_titles=True, smooth = 0.7,
+                    title_kwargs={"fontsize": 15}, label_kwargs = {"fontsize": 25},
+#                    plot_datapoints=True,smooth=1.0,smooth1d=1.0,
+                    levels=1.0 - np.exp(-0.5 * np.array([1.,2.]) ** 2),
+                    title_fmt='.2f')
+for ax in fig.get_axes():
+      ax.tick_params(axis='both', labelsize=20)
+#fig.savefig("fig_results_3para.pdf")
+#####
+plt.show()  

### 2019-05-08 GW_BH_function/read_para4_corner.py

@@ -11,17 +11,18 @@ import numpy as np
 import astropy.io.fits as pyfits
 import matplotlib.pyplot as plt
 
+import matplotlib
+import matplotlib as matt
+matt.rcParams['font.family'] = 'STIXGeneral'
+cmap = matplotlib.cm.get_cmap('viridis')
+
 import corner
 #filename = 'test2_select-eff_correct_sigmalogdiv3_20.txt'
 #filename = 'few_tests/right_answer_test1_conv_lognorm_20.txt'
-pre_result = np.loadtxt('test3_result/test3_mode1_level20_npy.txt')
-bool_1 = (pre_result[:,1]>2.7)
-bool_2 = (pre_result[:,3]>95)
-bools = np.invert(bool_1+bool_2)
-result_rm_edge = pre_result[bools]
-result_new_edge = np.loadtxt('test3_result/test3_edge.txt')
+result = np.loadtxt('test3_result_secondrun/test3_mode1_take2_level20.txt')
+numbers = result
 
-numbers = np.concatenate((result_rm_edge,result_new_edge))
+
 #%%
 #print filename
 #with open(filename) as f:
@@ -32,13 +33,15 @@ numbers = np.concatenate((result_rm_edge,result_new_edge))
 #lines = [lines[i] for i in range(len(lines)) if len(lines[i]) ==4]
 #numbers = np.asarray(lines).astype(float)
 samples = numbers#[numbers[:,1]<3]
-fig = corner.corner(numbers[:,1:], labels=["a0", "a1", "mbh_max", "mbh_min"],
+fig = corner.corner(numbers, labels=[r"$\alpha_0$", r"$\alpha_1$", "M$_{max}$", "M$_{min}$"],
                     truths=[2.35, 0.7, 80., 5.],
-                    quantiles=[0.16, 0.84],show_titles=True,
-                    title_kwargs={"fontsize": 12},#truths=[2.35,80,5],
+                    quantiles=[0.16, 0.5, 0.84],show_titles=True, smooth = 0.7,
+                    title_kwargs={"fontsize": 15}, label_kwargs = {"fontsize": 25},
 #                    plot_datapoints=True,smooth=1.0,smooth1d=1.0,
-                    levels=1.0 - np.exp(-0.5 * np.arange(1, 2.1, 1) ** 2),
+#                    levels=1.0 - np.exp(-0.5 * np.array([1.,2.]) ** 2),
[…]

### 2019-05-17 GW_BH_function/manuscript_GW_constrain_BHmass/main.tex
Update by Kai

@@
 \shorttitle{Black hole mass function and redshift evolution by ET}
-\shortauthors{Marian et al.}
+\shortauthors{Ding et al.}
 
@@
 
-%\author%[0000-0002-4359-5994]
-%{Kai Liao}
-%\affiliation{School of Science, Wuhan University of Technology, Wuhan 430070, China}
+\author%[0000-0002-4359-5994]
+{Kai Liao}
+\affiliation{School of Science, Wuhan University of Technology, Wuhan 430070, China}
 
@@
 If the GW events are able to tell a redshifted-related BH mass function.
-We demonstrate the ability of future gravitational-wave (GW) measured by third generation detector Einstein Telescope (ET) to infer the slope of the BH mass function (BHMF) and its evolution with redshift.
+We demonstrate the ability of future gravitational-waves (GW) measured by third generation detector Einstein Telescope (ET) to infer the slope of the BH mass function (BHMF) and its evolution with redshift.
 %The measurement of BH binary systems enable the inference of the BH mass (\mone\ and \mtwo\ of each component) together with the luminosity distance (\dl).
-We performed the Monte Carlo approach to simulate the measurements of BH binaries GW signals as detected by ET, including the BH masses and their luminosity distance (\dl).
+We performed the Monte Carlo approach to simulate the measurements of binary BH (BBH) inspiral systems signals as detected by ET, including the BH masses and their luminosity distances (\dl).
 Following the previous works, we consider the mass of  primary black hole in each binary and model the BHMF as a function of the power law with slope parameter as $\alpha$.
-We take into account the bias that would be raised by the uncertainty of the measurement and the selection effect and find that a thousand GW events measure by ET ($\sim1\%$ amount of the yearly detection rate) could measure the $\alpha$ to $3\%$ accuracy level.
-Furthermore, we investigate a scenario, by the first time, that  $\alpha$ is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
+We take into account the bias that would be raised by the uncertainty of the measurement and the selection effect and find that a thousand GW events measured by ET ($\sim1\%$ amount of the yearly detection rate) could measure the $\alpha$ to $3\%$ accuracy level.
+Furthermore, we investigate a scenario, that  $\alpha$ is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
 Our result is that, taking the \dl\ as redshift estimator, with a thousand GW events one is capable of obtaining an unbiased $\alpha_1$ at the uncertainty level of $\pm0.5$.
-The ability of known the evolution scenario of BHMF would help to understand the origin of the BHs and how BH binaries formed at the different stage of the Universe.
+The ability of knowing the evolution scenario of BHMF would help to understand the origin of the BHs and how BH binaries formed at different stage of the Universe.
 
@@
 The mass of BHs is known to cover a wide range from stellar-mass to supermassive ($\sim10^{10} M_{\odot}$).
-The recent discovery of gravitational-wave (GW) measurement is a substantial evidence of stellar-mass BHs \citep{Abbott2016}, while supermassive BHs are thought to existe in the centers of almost all the galaxies \citep{Lynden-Bell1969, Kormendy1995}.
+The recent discovery of gravitational-wave (GW) measurement is a substantial evidence of stellar-mass BHs \citep{Abbott2016}, while supermassive BHs are thought to exist in the centers of almost all the galaxies \citep{Lynden-Bell1969, Kormendy1995}.
 More recently, the first image of supermassive BH in the center of the giant elliptical galaxy M87 has been reconstructed by radio-wave observations \citep{Alberdi2019}.
 Nevertheless, in theory, it is still unclear of how the BHs are formed \citep{Fryer1999, Fryer2001, Mirabel2016}.
-The prediction for the number and mass distribution of stellar-mass BHs in the Universe is still needed to be more clear.
+The number and mass distribution of stellar-mass BHs in the Universe is still needed to be more clear.
 
-The recent GW detection activities have brought us to a new era of GW astronomy \citep[e.g.,][]{Abbott2016, Abbott2016_sum, Abbott2018}.
+The recent GW detection activities have brought us to a new era of astronomy \citep[e.g.,][]{Abbott2016, Abbott2016_sum, Abbott2018}.
 To date, the LIGO and Virgo have achieved two successful runs (O1 and O2) and now is performing the third run (O3).
@@
 The GWs provide a direct way to hear the inspiralling BBH systems, enable one to derive their information including mass, spin, luminosity distance\citep{Abbott2017phy}.
-This brings us the opportunity to measure the population of BHs \citep{Abbott2018b} and helps to answer some fundamental questions such as the cosmography\citep{Liao2017, Ding2019, Cai2017}, the GW speed\citep{Fan2017, Collett2017}, the strong lensing effects~\citep{Ola2013, Biesiada2014, Ding2015}.
-The previous work \citet{Kovetz2017PhRvD} has investigated that further LIGO measurements from thousands of BBHs can be taken to infer the power law index $\alpha$ at 10\% accuracy.
+This brings us the opportunity to not only measure the population of BHs \citep{Abbott2018b}, but also answer some fundamental questions such as the cosmography\citep{Liao2017, Ding2019, Cai2017}, the GW speed\citep{Fan2017, Collett2017}, the strong lensing effects~\citep{Ola2013, Biesiada2014, Ding2015}.
+
+Focusing on the BH mass function (BHMF), the recent work \citet{Kovetz2017PhRvD} has investigated that further LIGO measurements from thousands of BBHs can be taken to infer the  BHMF as power law and constrain the slope parameter $\alpha$ at 10\% accuracy.
 More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF as power law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility) \citep{Abbott2018b}.
-In this study, we pay extra attention on simulating the GW events that could be measured by third-generation gravitational waves detector, Einstein Telescope (ET) \citep{Abernathy2011} based Monte Carlo (MC) approach.
+In this study, we pay extra attention on simulating the GW events that could be measured by third-generation gravitational wave detector, Einstein Telescope (ET) \citep{Abernathy2011} based Monte Carlo (MC) approach.
 This provides us a mock BBHs catalog with the realistic dataset to exam their ability to constrain the BHMFs, taking into the effects by the data noise level, selection bias in a more realistic way.
@@
 where $\mathcal{H}$ is the Heaviside step function.
-Then, the secondary mass, \mtwo, is fix as uniform between $[M_{min}, m_1]$.
+Then, the secondary mass, \mtwo, is fixed as uniform between $[M_{min}, m_1]$.
 Note that, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ actually does not affect the inference for the shape of BHMF.
@@
 \subsection{Selection Effect}\label{sec_likelihood_sf}
-The observation the has tendency to discover more significant events, known as Malmquist bias.
+The observation has tendency to discover more significant events, known as Malmquist bias.
 The GW systems with higher values \mone\ trend to stronger signals and thus have a higher possibility to be detected.
@@
 To infer a non-biased distribution, we adopt the realization approach.
-The detail of the simulation if the following.
+The detail of the simulation is the following.
 In each realization, we simulate a thousand GW events and infer the best-fit parameters using minimization.
@@
 \section{Conclusion \& Discussion} \label{sec_summary}
-The third-generation gravitational waves detector, Einstein Telescope, is very powerful and capable of detecting $\sim10^5$ GW events per year, with redshift up to $z\sim17$.
+The third-generation gravitational wave detector, Einstein Telescope, is very powerful and capable of detecting $\sim10^5$ GW events per year, with redshift up to $z\sim17$.
 In this study, we investigated how the detections of the merger of BBHs improve our knowledge of the black hole mass function.

### 2019-08-26 GW_BH_function/manuscript_GW_constrain_BHmass/main_Marek_v1.tex
Submit to NA

\documentclass[twocolumn]{aastex62}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand\s{$\sim$}
\newcommand{\e}{\'{e}}
\newcommand{\amen}[1]{\textbf{\textit{#1}}}

\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{mathrsfs}

\usepackage{float}
\usepackage{multirow}
\usepackage{enumitem}

\shorttitle{Black hole mass function and its redshift evolution by ET}
\shortauthors{Ding et al.}

\newcommand{\kai}[1]{\textcolor{red}{[{\bf Kai}: #1]}}

\begin{document}

\newcommand{\mbh}{$\mathcal M_{\rm BH}$}
\newcommand{\cmass}{${\cal M}_0$}
\newcommand{\dl}{$d_L$}
\newcommand{\mone}{$m_1$}
\newcommand{\mtwo}{$m_2$}
\newcommand{\snr}{$\rho$}

\title{Black hole mass function and its evolution -- the first prediction for the Einstein Telescope}

\correspondingauthor{Xuheng Ding}
\email{dingxh@whu.edu.cn}

\author%[0000-0001-8917-2148]
{Xuheng Ding}
\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}

%\author{Lilan Yang}
%\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
%\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}

\author%[0000-0002-4359-5994]
{Kai Liao}
\affiliation{School of Science, Wuhan University of Technology, Wuhan 430070, China}

\author%[0000-0003-1308-7304]
{Marek Biesiada}
\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
%\affiliation{Department of Astrophysics and Cosmology, Institute of Physics, University of Silesia, 75 Pu{\l}ku Piechoty 1, 41-500 Chorz{\'o}w,
%Poland}
\affiliation{National Centre for Nuclear Research, Pasteura 7, 02-093 Warsaw, Poland}

\author%[0000-0002-3567-6743]
{Zong-Hong Zhu}
\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}

\begin{abstract}

We demonstrate the ability of future third generation gravitational wave (GW) detector -- the Einstein Telescope (ET) to infer the slope of the BH\kai{black hole} mass function (BHMF) and its evolution with redshift. 
We perform the Monte Carlo simulation of the measurements of binary BH (BBH) systems chirp signals\kai{chirp signals from binary BH systems} that could be detected by ET, including the BH masses and their luminosity distances (\dl). Following the previous works, we consider the mass of a primary black hole in each binary system and model the BHMF as a power-law function with slope parameter $\alpha$. We take into account the bias introdused by the uncertainty of the measurements and by the selection effect. We find that a thousand of GW events registered by ET ($\sim1\%$ amount of its yearly detection rate) could measure the $\alpha$ with $3\%$ accuracy\kai{precision}. Furthermore, we investigate a scenario, that\kai{where}  $\alpha$ is evolving\kai{evolves} with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$. Our result is that\kai{shows}, taking the\kai{remove ``the"} \dl\ as \kai{the} redshift estimator, with a thousand\kai{one thousand} GW events one is able to obtain an unbiased\kai{since your results are based on mock data/simulation, you can't say ``unbiased"} $\alpha_1$ at the uncertainty level of $\pm0.5$. The ability of gain\kai{gaining} knowledge about the evolution of BHMF would help to understand the origin of the BHs and how BH binaries formed at different stages of the history of the Universe.
\kai{edit by here}
\end{abstract}

%\keywords{keywords TBD}

\section{Introduction} \label{sec_intro}
%As first identified as a solution to Einstein's field equations by Schwarzschild in 1916 \citep{Schwarzschild1999}, black holes (BHs) have been predicted to remain a bunches of fundamental questions in unifying GR with quantum physics \citep{Hawking1976, Giddings2017}.

The masses of astrophysical black holes (BHs) are known to cover a wide range from stellar-mass to supermassive BHs $\sim10^{10} M_{\odot}$. Recent discovery of 
coalescing binary black holes (BBHs) in LIGO gravitational-wave (GW) detectors is a substantial evidence of stellar-mass BHs \citep{Abbott2016}, while supermassive BHs are supposed to exist in the centers of almost all the galaxies \citep{Lynden-Bell1969, Kormendy1995}. Quite recently, the first image of a supermassive BH in the center of the giant elliptical galaxy M87 has been reconstructed from radio observations performed by the Event Horizon Telescope \citep{Alberdi2019}. 
GWs provide a direct way to study the inspiralling BBH systems, enabling one to derive their basic parameters including mass, spin and luminosity distance~\citep{Abbott2017phy}. This creates the opportunity not only to measure the properties of BHs ~\citep{Abbott2018b}, but also answer some fundamental questions concerning cosmography~\citep{Liao2017, Ding2019, Cai2017}, the GW speed~\citep{Fan2017, Collett2017} or the strong lensing of GWs ~\citep{Ola2013, Biesiada2014, Ding2015}.

Nevertheless, it is still unclear of how the BHs are formed \citep{Fryer1999, Fryer2001, Mirabel2016}. In particular, the number and mass distribution of stellar-mass BHs in the Universe still needs to be clarified.
The recent GW detections have brought us to a new era of gravitational wave astronomy \citep[e.g.,][]{Abbott2016, Abbott2016_sum, Abbott2018} and opened up a  brand new possibility in respect of studying BBH systems formation channels. 
At present, however, observations cannot firmly distinguish between basic formation scenarios like the evolution of isolated pairs of stars, dynamic binary
formation in dense clusters and pairs of primordial BHs.
Current GWTC-1 catalog of binary coalescences detected by LIGO/Virgo GW interferometers includes 10 BH-BH binaries and one NS-NS (GW170817) binary \citep{Abbott2018}. In the next decade, the number of detected coalescences of BHBH systems is expected to be increasing rapidly with the improvements in the detector sensitivities.

Focusing on the BH mass function (BHMF) parametrized as a two-sided truncated power-law, \citet{Kovetz2017PhRvD} estimated that further LIGO measurements providing thousands of BBHs would constrain the BHMF slope parameter $\alpha$ at 10\% accuracy. More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF power law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility) \citep{Abbott2018b}. 
In this study, we use the Monte Carlo (MC) approach to simulate the GW events from BBH systems that could be measured by third-generation gravitational wave detector, the Einstein Telescope (ET) \citep{Abernathy2011}. We construct a mock BBHs catalog with the realistic dataset to examine their ability to constrain the BHMFs, taking into account the data noise level and selection bias in a more realistic way. Moreover, since the ET would detect the GW events from the distant Universe up to $z\sim17$ \citep{Abernathy2011}, the wide redshift range of the BBH events enable us to examine whether it would be possible to detect the $\alpha$ as a function of redshift.

This paper is organized as follows. In Section~\ref{sec_simulation} we describe the simulation of the BBH events detectable by ET using the Monte Carlo approach. In this section, we assume the initial assumptions for the BH mass function used further as true values to be recovered from the data. In Section~\ref{sec_theory}, we introduce the theoretical framework to reconstruct the BHMFs, considering the noise realization and the selection effects. Furthermore, we make a further step by considering the power law index $\alpha$ as a function of redshift and explore the way to use luminosity distance as redshift estimator and detect such evolution. We present our results in the Section~\ref{sec_result}. The discussion and conclusions are given in the last Section~\ref{sec_summary}. 
Throughout this paper, we assume a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.

\vspace{1cm}
\section{Data simulation} \label{sec_simulation}
In this section we describe the simulation of a realistic mock catalog of GW signals from BBHs detectable by future ET interferometric detector. Numerical predictions of BBH inspirals detecable by the ET 
have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of order $\sim10^{4-5}$ \citep{Abernathy2011, Ola2013, Biesiada2014}. More recently, \citet{Yang2019} developed the approach of a Monte Carlo (MC) simulation to predict the detection rate by explicitly considering each BBH inspiral event sampled from the outcome of the population synthesis model, which provides the way to mimic a realistic BBH GW catalog. The backbone of this approach is to build up a mock universe which includes a sufficient volume of BBH events to represent the overall sample. We refer the reader for the details in \citet[][Section 2, therein]{Yang2019}  and briefly recall the key points below.

\subsection{Detection Criteria} \label{subsec_criteria}
We randomly generated the key parameters to determine the signal-to-noise ratio $\rho$ of each GW system. For a specific BBH inspiral event at redshift $z_s$, the ET's corresponding reaction is defined as \citep{Abernathy2011}:

\begin{equation} \label{SNR}
\rho = 8 \Theta \frac{r_0}{d_L(z_s)} \left( \frac{(1+z){\cal M}_0}{1.2 M_{\odot}} \right)^{5/6}
\sqrt {\zeta(f_{max})},
\end{equation}
where $r_0$ is the detector's characteristic distance parameter and $\zeta(f_{max})$ is the dimensionless function reflecting the overlap between the GW signal and the ET's effective bandwidth which is usually simplified as unity. ${\cal M}_0$ is the intrinsic chirp mass defined as $ {\cal M}_0 = \frac{(m_1m_2)^{3/5}}{(m_1+m_2)^{1/5}}$, where \mone\ and \mtwo\ are the
respective masses of the BBH components. $\Theta$ is the orientation factor determined by four angles as \citep{Finn93}:
 \begin{equation} \label{Theta}
 \Theta = 2 [ F_{+}^2(1 + \cos^2{\iota} )^2 + 4 F_{\times}^2 \cos^2{\iota} ]^{1/2},
 \end{equation}
where: $F_{+} = \frac{1}{2} (1 + \cos^2{\theta}) \cos{2\phi} \cos{2 \psi} - \cos{\theta} \sin{2 \phi} \sin{ 2 \psi}$, and
$F_{\times} = \frac{1}{2} (1 + \cos^2{\theta}) \sin{2\phi} \cos{2 \psi} + \cos{\theta} \sin{2 \phi} \cos{ 2 \psi}$ are so-called antenna patterns. The four angles ($\theta, \phi, \psi, \iota$) describe respectively the
direction to the BBH system relative to the detector and the binary orientation relative to the line of sight between it and the detector. 
They are independent and one can assume that $(\cos\theta, \phi/\pi, \psi/\pi, \cos\iota)$ distributed uniformly over the range $[-1, 1]$. The GW signal is considered as detectable if its \snr\ is over the detecting threshold, i.e., $\rho > \rho_0 = 8$.

\subsection{Monte Carlo Approach} \label{MC}

Our aim is to build up a sufficient volume of BBH systems in the mock universe by randomly generating the key parameters for each BBH system. We sample them according to the yearly merging rate in a redshift interval  $[z_{s}, z_{s}+dz_{s}]$:
 \begin{equation}
 d\dot{N} (z_s)=4\pi\left(\frac{c}{H_{0}}\right)^3\frac{\dot{n}_{0}(z_{s})}{1+z_{s}}\frac{\tilde{r}^2(z_{s})}{E(z_{s})}dz_{s}. 
 \end{equation}
where the intrinsic BBH merger rate $\dot{n}_{0}(z_{s})$ is the one predicted by the population synthesis model (using {\tt StarTrack} code\footnote{The data is taken from the website \url{http://www.syntheticuniverse.org}.}) in \citet{Dominik13}, $\tilde{r}(z_{s})$ is the dimensionless comoving distance to the source, and $E (z_s)$ is
the dimensionless expansion rate of the universe at redshift $z_s$. 
Concerning the cosmological model, in order to comply with \citet{Dominik13} we assume a flat $Lambda$CDM model with $\Omega_m = 0.3$ and $H_0 = 70 \; km s^{-1} Mpc^{-1}$.
%Hence, the overall amount of BBH events in the universe can be calculated by ${\dot N} = \int_0^{ \infty} \frac{d {\dot N (z)}}{dz} dz$.
For each BBH system, we sample the probability distribution of the key parameters to randomly generate their values. These key parameters include the four angles $(\theta, \phi, \psi, \iota)$ in the Equation~(\ref{Theta})  and the masses of each BH in the binary system (i.e., \mone\ and \mtwo).
For the purpose of randomly generating the BH masses, we follow the previous works \citep{Kovetz2017PhRvD, Abbott2018b, Fishbach2018} and assume that \mone\ follows a power law distribution with a hard cut at both maximum and minimum mass:
 \begin{equation} \label{equ_powlaw}
p(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),
 \end{equation}
where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo, is fixed as uniform between $[M_{min}, m_1]$. Let us note that, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ actually does not affect the inference for the shape of BHMF. These parameters determine the value of $\Theta$ and ${\cal M}_0$ in Equation~(\ref{SNR}). We combine them with their redshift $z_s$ to generate the $\rho$ of each BBH system. We collect only the events which have $\rho > \rho_0 = 8$, meaning that those events with $\rho < 8$ are to faint to be detected.

Concerning the BHMF we consider two scenarios. In the first scenario, the $\alpha$ exponent is constant, hence the shape of the BHMF is fixed throughout the redshfit range probed by the ET. In the second scenario, we consider that $\alpha$ varies as a function of redshift according to:
 \begin{equation} \label{equ_alphaz}
\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z} , 
 \end{equation}
so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$. This is actually the first order Taylor expansion in the scale factor $a(t)$ of an unknown $\alpha(a(t))$ function.

\subsection{Measurement Error} \label{sec_noiselevel}
We aim to produce the mock dataset of the future GW events representative of the ET  measurements. In order to consider the measurement uncertainties in a realistic way, we inject random statistical uncertainties into the mock data as described below.

The parameters measureable from the BBH inspiral waveform comprise \dl, chirp mass and $\rho$. Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform. As a recipe to set up the noise levels of our simulated data we adopt the results of \citet{Ghosh2016}, who  explored the expected statistical uncertainties with which the parameters of black hole binaries can be measured from GW observations by next generation ground-based GW observatories. 
Moreover, we stress that the measurements of the BBH parameters are characterized by ${\it skewed}$ distributions. Therefore, instead of the traditional Gaussian distribution, we assume that the measured parameters follow the Log-Normal distribution with the standard deviation of  ${\cal M}_0$, \dl, and \mone\ equal to 0.17, 0.35 and 0.2, respectively. For instance, if the $m_{1,fid}$ is the true value for \mone, its probability density is:
 \begin{equation} \label{equ_lognorm}
p(m_1) = \frac{1}{m_1 \sigma_{m_1} \sqrt{2\pi}} exp \big(- \frac{log(m_1)-log(m_{1,fid})}{2\sigma_{m_1}} \big) 
 \end{equation}

Having clarified the MC approach and defined data the uncertainty level, we are capable of producing the mock GW dataset. As an illustration, we list in Table~\ref{tab_GW_mock_data} a 
part of the simulated data comprising in total thousand BBH inspiral events. 
We use these data to infer the BHMF in next sections.

\begin{deluxetable}{lcccc}
\tablecolumns{5}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablecaption{Illustration of the mock GW catalog} 
\tablehead{ 
\colhead{Object ID} &
\colhead{\mone}&
\colhead{Luminosity Distance} & 
\colhead{Chirp Mass} &
\colhead{SNR}
\\ 
\colhead{} &
\colhead{($M_\odot$)}&
\colhead{(Mpc)} & 
\colhead{($M_\odot$)} &
\colhead{(\snr)}
\\
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)}
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
ID1 & $95.85\substack{+21.22\\-17.37}$  & $87120.7\substack{+19288.8\\-15792.3}$  & $61.87\substack{+13.70\\-11.21}$ & 28.707 \\
ID2 & $13.31\substack{+2.95\\-2.41}$  & $81476.5\substack{+18039.1\\-14769.2}$  & $11.68\substack{+2.59\\-2.12}$ & 10.468 \\
ID3 & $7.40\substack{+1.64\\-1.34}$  & $7456.8\substack{+1651.0\\-1351.7}$  & $6.82\substack{+1.51\\-1.24}$ & 39.673 \\
ID4 & $19.02\substack{+4.21\\-3.45}$  & $96201.9\substack{+21299.4\\-17438.4}$  & $19.11\substack{+4.23\\-3.46}$ & 12.227 \\
ID5 & $15.12\substack{+3.35\\-2.74}$  & $47645.3\substack{+10548.8\\-8636.6}$  & $14.24\substack{+3.15\\-2.58}$ & 12.672 \\
ID6 & $18.95\substack{+4.20\\-3.43}$  & $23937.4\substack{+5299.8\\-4339.1}$  & $13.86\substack{+3.07\\-2.51}$ & 16.027 \\
ID7 & $8.65\substack{+1.92\\-1.57}$  & $44053.0\substack{+9753.4\\-7985.4}$  & $6.99\substack{+1.55\\-1.27}$ & 8.383 \\
ID8 & $40.03\substack{+8.86\\-7.26}$  & $60432.5\substack{+13379.9\\-10954.6}$  & $25.53\substack{+5.65\\-4.63}$ & 17.917 \\
ID9 & $32.58\substack{+7.21\\-5.91}$  & $4293.5\substack{+950.6\\-778.3}$  & $18.58\substack{+4.11\\-3.37}$ & 34.190 \\
ID10 & $9.88\substack{+2.19\\-1.79}$  & $50294.8\substack{+11135.4\\-9116.9}$  & $4.65\substack{+1.03\\-0.84}$ & 9.608 \\
... & $...$ & ... & ... & ...\\
ID991 & $7.90\substack{+1.75\\-1.43}$  & $10175.7\substack{+2252.9\\-1844.5}$  & $7.31\substack{+1.62\\-1.32}$ & 9.354 \\
ID992 & $15.48\substack{+3.43\\-2.81}$  & $8058.1\substack{+1784.1\\-1460.7}$  & $17.14\substack{+3.80\\-3.11}$ & 11.149 \\
ID993 & $6.11\substack{+1.35\\-1.11}$  & $9566.9\substack{+2118.1\\-1734.2}$  & $4.11\substack{+0.91\\-0.75}$ & 10.703 \\
ID994 & $17.41\substack{+3.85\\-3.16}$  & $232095.1\substack{+51386.5\\-42071.7}$  & $14.46\substack{+3.20\\-2.62}$ & 8.444 \\
ID995 & $23.76\substack{+5.26\\-4.31}$  & $127615.4\substack{+28254.4\\-23132.7}$  & $16.97\substack{+3.76\\-3.08}$ & 14.972 \\
ID996 & $10.43\substack{+2.31\\-1.89}$  & $65546.6\substack{+14512.2\\-11881.6}$  & $6.96\substack{+1.54\\-1.26}$ & 9.497 \\
ID997 & $5.79\substack{+1.28\\-1.05}$  & $24315.0\substack{+5383.4\\-4407.6}$  & $6.93\substack{+1.53\\-1.26}$ & 14.177 \\
ID998 & $12.48\substack{+2.76\\-2.26}$  & $98731.2\substack{+21859.3\\-17896.9}$  & $6.85\substack{+1.52\\-1.24}$ & 13.340 \\
ID999 & $6.95\substack{+1.54\\-1.26}$  & $75187.9\substack{+16646.8\\-13629.2}$  & $3.40\substack{+0.75\\-0.62}$ & 9.437 \\
ID1000 & $6.53\substack{+1.45\\-1.18}$  & $27801.3\substack{+6155.3\\-5039.5}$  & $9.79\substack{+2.17\\-1.77}$ & 8.390 \\
%... & $...$ & ... & ... \\
\enddata
\label{tab_GW_mock_data}
\tablecomments{The catalog of simulated thousand BBH inspiral events is used to test the inference of the BHMF from the data attainable in forthcoming next generation GW detector -- the ET.
}
\end{deluxetable}

\vspace{1cm}
\section{Theoretical Framework}  \label{sec_theory}
In this section, we describe the fitting procedure for the parameterized BHMFs. 
In principle, the modeling for a dataset which follows a power-law distribution as Equation~(\ref{equ_powlaw}) is very straightforward. To derive the posterior of the parameters, one only needs to combine all the measured values together in a joint likelihood:
 \begin{equation} \label{equ_lik_powlaw}
 P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} P(m_{1,i}|\alpha, M_{max}, M_{min}).
 \end{equation}
However, the simulated values of \mone\ shown in Table~\ref{tab_GW_mock_data} actually deviate from the initial power-law distribution. This deviation stems from several effects that exist in reality. In Section~\ref{sec_likelihood_noise} and \ref{sec_likelihood_sf}, we introduce them and explore the ways to account for them.

\subsection{Measurement Uncertainty}\label{sec_likelihood_noise}
The intrinsic \mone\ follows a power-law distribution, however the measured  \mone\ are affected by Log-Normal distribution and thus they do not follow a power-law function anymore \citep{Koen2009}. In theory, if the event $X$ follows a power-law distribution and its observed values are subject to the Gaussian uncertainty, then $X + e$ is distributed according to the convolution of the power-law and Gaussian distributions. Likewise, given that the noised data follow the Log-Normal distribution, the intrinsic power-law should be convolved with it and enter the likelihood as:
 \begin{equation} \label{equ_lik_conv}
 P(\alpha, M_{max}, M_{min}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min}),
 \end{equation}
where the $\hat{P}$ is the initial power-law function convolved with the Log-Normal distribution using the standard deviation as 0.2 as we assumed. We illustrate the effect of such convolution in the Figure~\ref{fig:result_slope}.

\begin{figure}%[!b]
\includegraphics[width=1.05\linewidth]{convolving.pdf}
\caption{
Figure illustrating the convolution of a power-law distribution with a Log-Normal distribution having $\sigma = 0.2$. One can see that the convolution make distribution shallower, smoothes the breaking edge at $m_1 = 5 M_{\odot}$ and makes the slope less steep.
}
\label{fig:result_slope}
\end{figure}

\subsection{Selection Effect}\label{sec_likelihood_sf}
The GW observations have a tendency to discover more significant events, known as Malmquist bias. The GW systems with higher values \mone\ produce  stronger signals and thus have a higher probability to be detected. If this effect is not taken into account, the final BHMFs would be biased to the high mass end.

To overcome this selection effect, we introduce the selection factor $\eta$ for the GW event, which is the detecting probability of one event in a repeated simulation. The meaning of this factor $\eta$ is straightforward -- if one GW event has $\eta=0.2$ it means that this event has 80\% probability of being be missed. In other words, four equivalent events would have been missed. Thus, for this event, one needs to re-calibrate its influence by  enhancing the likelihood by a power of 5. Hence, to account for this  selection effect, we modify the likelihood as:
 \begin{equation} \label{equ_lik_sf}
 P(\alpha, M_{max}, M_{min}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta},
 \end{equation}
where $\eta$ is directly determined by the probability distribution of $\rho$, i.e. $\eta = P(\rho>8)$. In order to use the Equation~(\ref{SNR}), the distribution function of $\Theta$ is known from the MC simulations, the \cmass\ and \dl\ are provided in the mock dataset as demonstrated in Table~\ref{tab_GW_mock_data}. Yet, the redshift $z_s$ is the unknown parameter since it is non-measurable in the GW detectors. Therefore, we take the \dl\ as redshift estimator.
Note that the \dl\ and \cmass\ both have asymmetric distributions with large scatter,hence the inferred $\eta$ is distributed around its true value in a skewed way. We find that this skewness could be well described by a Log-Normal distribution, with multiplicative standard deviation\footnote{In Log-Normal distribution, the multiplicative standard deviation is the exponent  of the standard deviation, i.e., $\sigma^* = exp(\sigma)$.} as $\sigma^*=log(\eta)/3$. Thus, we manually correct this skewness and obtain the non-biased $\eta$.

\subsection{Luminosity Distance as Redshift Estimator} 
\label{sec_dl_z}
%The redshift is not detectable by GW, however, can be inferred from the DL. 
In the previous section, we take \dl\ as the redshift estimator to derive the redshift and hence selection factor $\eta$. The way to derive the $z$ is quite straightforward: simply an inverse solution of integral function when knowing the \dl$(z)$ and fixing the cosmological model.

Therefore, once the cosmological model is assumed, indirect inference of $z_s$ creates an opportunity to model the BHMF slope as a function of redshift. Therefore, we are able to investigate the second scenario described by the Equation~(\ref{equ_alphaz}) as:
 \begin{equation} \label{equ_lik_alphaz}
 \begin{split}
 P&(\alpha_0, \alpha_1, M_{max}, M_{min}) \propto \\
  &\prod_{i=1}^{total} \hat{P}(m_{1i}, z_{inf,i} |\alpha_0, \alpha_1, M_{max}, M_{min})^{1/\eta}.
  \end{split}
 \end{equation}

 We present our inference for the BHMF using the mock data in the next section.

\vspace{1cm}
\section{Result}\label{sec_result}
%We present the result in this section.
%One thousand of data points.
%An appendix to introduce the correction for the skewness for the $\eta$.
We fit the mock data to the BHMF model to infer the distribution of the best-fitted parameter. To infer a non-biased distribution, we adopt the realization approach. The details of the simulation are the following. In each realization, we simulate a thousand of BBH inspiral GW events and infer the best-fit parameters using minimization of the chi-square objective function. 
\textbf{The realization is completed when the inferred best-fit parameters converged.}

In the first scenario, we consider the slope $\alpha$ as a constant. We generated the mock data by taking $\alpha~=~2.35$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ as the fiducial values. We calculate the likelihood by Equation~(\ref{equ_lik_sf}) to infer the best-fitted parameters in each realization. In Figure~\ref{fig_result_a}, we present the posterior distribution of the inferred parameters. We find that the non-biased results have the  best-fitted parameters distributed as $\alpha = 2.36\substack{+0.09\\-0.08}$, $M_{max} = 80.54\substack{+5.45\\-5.60}$,  $M_{min} = 5.03\substack{+0.17\\-0.15}$. Our inference of $\alpha$ indicates that a thousand of GW events could constrain the slope within $3.5\%$ level.

\begin{figure}%[!b]
\includegraphics[width=1.0\linewidth]{fig_results_3para.pdf}
\caption{
One- and two-dimensional distributions for the best-fitted parameters in the scenario A. The BHMF is assumed as a power-law with hard cut at the $M_{min}$ and $M_{max}$, with a constant slope ($\alpha$) across all the redshifts.
}
\label{fig_result_a}
\end{figure}

In the second scenario, the $\alpha$ evolves with redshift according to the Equation~(\ref{equ_alphaz}). We assume the fiducial parameters as $\alpha_0~=~2.35$, $\alpha_1~=~0.75$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ to generate a thousand datasets in each realization. We present the results in Figure~\ref{fig_result_b}. Since the second scenario has one more parameter, distributions of the best-fitted parameters have larger scatter and can be summarized as $\alpha_0 = 2.32\substack{+0.35\\-0.36}$, $\alpha_1 = 0.73\substack{+0.52\\-0.50}$, $M_{max} = 78.03\substack{+10.03\\-8.40}$ and  $M_{min} = 5.02\substack{+0.14\\-0.14}$. Not surprisingly, the degeneracy exsits between the $\alpha_0$ and $\alpha_1$.

We highlight that in this scenario, it is the inferred uncertainty of $\alpha_1$ that matters the most. Our result show that, with a volume of one thousands GW measurements, the inferred value of $\alpha_1$ would have a precision of $\pm0.5$. That is to say, this volume of measurements is able to distinguish the evolution of BHMF, when $\alpha_1$ is deviated from 0 by a value of 0.5. Limited by the computing power, we haven't tested the larger sample of measurements. However, conjecturing that the precision of inference is increasing with the sample size as a function of $\sqrt{N}$, one year measurements of ET ($\sim10^5$ in total) would result in the $\alpha_1$ inferred with the precision down to $\sim0.05$.
We also note that the distribution of the best-fitted parameters ($\alpha_0$, $\alpha_1$) does not follow the Gaussian distribution, but rather a large fraction of it is concentrated at the center. 
%As a result, the 1-$\sigma$ confidence interval in 2-D parameter space are narrower than the ones in 1-D space. %\textcolor{blue}{(What does this suggest?)}

\begin{figure}%[!b]
\includegraphics[width=1.0\linewidth]{fig_results_4para.pdf}
\caption{
The same as Figure~\ref{fig_result_a} but for the scenario B, where the $\alpha$ of BHMF is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$. 
}
\label{fig_result_b}
\end{figure}

\vspace{1cm}
\section{Conclusion \& Discussion} \label{sec_summary}
The third-generation gravitational wave detector, the Einstein Telescope, will very powerful and capable of detecting $\sim10^5$ GW events per year, with redshift up to $z\sim17$. In this study, we investigated how the detections of the BBHs mergers could improve our knowledge of the black hole mass function.

We performed the Monte Carlo simulation to generate the mock measurements of GW signals from BBHs that would be detected by ET. As a starting point, we assumed that the BHMF for the primary BH mass followed a power law distribution. Based on the BBH intrinsic merger rate predicted by {\tt StarTrack}, we randomly simulated the key parameters of the BBH systems, including the chirp masses, redshifts and orientation factors and calculated  their corresponding signal-to-noise ratio \snr\ for the ET. We collected the events whose \snr\ exceeds the detecting threshold and injected Log-Normal noise to the detected parameter, including BH mass, chirp mass, luminosity distance to simulate the mock data.

We built up a theoretical framework and explore to use the mock measurements to infer the BHMF. We took into account the measurement uncertainties and the selection effect which would bias the inference. We used the realization approach, one thousand GW events per realization, and estimated the distribution of the best-fitted parameters of the BHMF, including the power law slope $\alpha$, the maximum BH mass $M_{max}$ and the minimum BH mass $M_{min}$. Furthermore, we used the luminosity distance as redshift estimator and tested whether one can infer the $\alpha$ as a function of redshift. We summarize our main results as follows:
\begin{enumerate}
\item Assuming the $\alpha$ is constant in redshift, one could infer the $\alpha$, $M_{max}$ and $M_{min}$ precisely and accurately. With one thousand measurements of BBHs events, the $\alpha$ would reach 3\% level, 
%i.e., Figure~\ref{fig_result_a}.
\item Testing the scenario that $\alpha$ is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$, our results show that a volume of one thousand measurements of BBHs events would provide the evolving parameter $\alpha_1$ with an uncertainty level of $\pm0.5$. Meaning that with this sample size one is able to recognize the evolution of BHMF when $\alpha_1$ deviates from $0$ by $0.5$.
\item According to the fact that the precision of the inference increases with the sample size, as a function of $\sqrt{N}$, we conclude that one year BBH sample by ET would be able to deliver the value of $\alpha_1$ with precision down to 0.05.
\end{enumerate}

We point out a few limitations of this work. First, we have adopted a template of intrinsic BBH merger rate based on the predictions by a standard model in {\tt StarTrack}, which can be different from the realistic one. Of course, the intrinsic BBH merger rate is unknown yet, which is related to 
lack of detailed knowledge of different elements such as BBH masses, explosion mechanism, the metallicity history and the time delay distribution. Also, for the sake of simplicity, we simulated the value of the secondary BH mass \mtwo\ by assuming that two masses of BBHs have independent distributions, which probably is not exactly true. However, one can expect that these limitations would more strongly affect the prediction of the yearly detection rate of the GW events and their redshift distribution. Using a sample with the same volume but different redshift distribution, the inference on the BHMF parameters could be very similar.

In this work, we focused on the inference of the BHMF using the mass properties by the BBH. However, it is worth to note that our approach could be used to address other problems. For example, one could infer the spin of BH \citep{Abbott2018b}, the mass function for the binary of NS-NS, NS-BH system, though these events are detectable at lower redshift ($z<4$). In addition, using the luminosity as redshift estimator, one should also be able to reconstruct the BBH intrinsic merger rate \citep{Fishbach2018}. 
, the cosmological parameter.

\acknowledgments
We thank Hosek Jr., M.W for the useful discussion.

This work was supported by the National Natural Science Foundation of China under grant Nos. 11633001 and 11373014, the Strategic Priority Research Program of the Chinese Academy of Sciences, grant No. XDB23000000, and the Interdiscipline Research Funds of Beijing Normal University.

X. Ding acknowledges support by China Postdoctoral Science Foundation Funded Project (No. 2017M622501).
%L. Yang is supported from the China Scholarship Council. 
M.B. was supported by the Key Foreign Expert Program for the Central Universities No. X2018002.
%K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. 11603015.
\software{  {\sc corner}, \citep{corner},
        Matplotlib \citep{Matplotlib},
        and standard Python libraries.
        }

\bibliography{reference}
%\input{reference.bbl}

%\newpage
%\appendix
%\section{section}\label{appendix_section}
%TEXTTEXTTEXTTEXTTEXTTEXTTEXTTEXTTEXT
%\newpage

%\newpage
%\appendix
%\section{Correction for the skewness of the selection factor}\label{appA}
%1. Describe the bias of the selection.
%2. The correction by $\eta/3.$

\end{document}

### 2019-08-26 GW_BH_function/manuscript_GW_constrain_BHmass/main_kai_v2.tex
Submit to NA

--- 2019-08-26 GW_BH_function/manuscript_GW_constrain_BHmass/main_Marek_v1.tex
@@
 The ability of gain\kai{gaining} knowledge about the evolution of BHMF would help to understand the origin of the BHs and how BH binaries formed at different stages of the history of the Universe.
-\kai{edit by here}
 \end{abstract}
@@
 
-The masses of astrophysical black holes (BHs) are known to cover a wide range from stellar-mass to supermassive BHs $\sim10^{10} M_{\odot}$. Recent discovery of 
+The masses of astrophysical black holes (BHs) are known to cover a wide range from stellar-mass to supermassive BHs\kai{remove ``BHs"?} $\sim10^{10} M_{\odot}$. Recent discovery of 
 coalescing binary black holes (BBHs) in LIGO gravitational-wave (GW) detectors is a substantial evidence of stellar-mass BHs \citep{Abbott2016}, while supermassive BHs are supposed to exist in the centers of almost all the galaxies \citep{Lynden-Bell1969, Kormendy1995}.
 Quite recently, the first image of a supermassive BH in the center of the giant elliptical galaxy M87 has been reconstructed from radio observations performed by the Event Horizon Telescope \citep{Alberdi2019}.
-GWs provide a direct way to study the inspiralling BBH systems, enabling one to derive their basic parameters including mass, spin and luminosity distance~\citep{Abbott2017phy}.
+GWs provide a direct way to study the inspiralling BBH systems, enabling one to derive their basic parameters including mass, spin and luminosity distance\kai{+s}~\citep{Abbott2017phy}.
 This creates the opportunity not only to measure the properties of BHs ~\citep{Abbott2018b}, but also answer some fundamental questions concerning cosmography~\citep{Liao2017, Ding2019, Cai2017}, the GW speed~\citep{Fan2017, Collett2017} or the strong lensing of GWs ~\citep{Ola2013, Biesiada2014, Ding2015}.
+\kai{seems the references are almost related with lensing.
+I suggest to cite more LIGO references}
 
 Nevertheless, it is still unclear of how the BHs are formed \citep{Fryer1999, Fryer2001, Mirabel2016}.
-In particular, the number and mass distribution of stellar-mass BHs in the Universe still needs to be clarified.
-The recent GW detections have brought us to a new era of gravitational wave astronomy \citep[e.g.,][]{Abbott2016, Abbott2016_sum, Abbott2018} and opened up a  brand new possibility in respect of studying BBH systems formation channels.
+In particular, the number and mass distribution of stellar-mass BHs in the Universe still needs\kai{need} to be clarified.
+The recent GW detections have brought us to\kai{remove ``to"} a new era of gravitational wave astronomy \citep[e.g.,][]{Abbott2016, Abbott2016_sum, Abbott2018} and opened up a  brand new possibility in respect of studying BBH systems\kai{system} formation channels.
 At present, however, observations cannot firmly distinguish between basic formation scenarios like the evolution of isolated pairs of stars, dynamic binary
-formation in dense clusters and pairs of primordial BHs.
+formation in dense clusters and pairs of primordial BHs\kai{add references here}.
 Current GWTC-1 catalog of binary coalescences detected by LIGO/Virgo GW interferometers includes 10 BH-BH binaries and one NS-NS (GW170817) binary \citep{Abbott2018}.
-In the next decade, the number of detected coalescences of BHBH systems is expected to be increasing rapidly with the improvements in the detector sensitivities.
+In the next decade, the number of detected coalescences of BHBH systems is expected to be increasing rapidly with the improvements in\kai{of} the detector sensitivities.
 
@@
 In this study, we use the Monte Carlo (MC) approach to simulate the GW events from BBH systems that could be measured by third-generation gravitational wave detector, the Einstein Telescope (ET) \citep{Abernathy2011}.
-We construct a mock BBHs catalog with the realistic dataset to examine their ability to constrain the BHMFs, taking into account the data noise level and selection bias in a more realistic way.
+We construct a mock BBHs\kai{BBH} catalog with the realistic dataset\kai{Since you generate mock data, why do you say ``realistic"?} to examine their ability to constrain the BHMFs, taking into account the data noise level and selection bias in a more realistic way.
 Moreover, since the ET would detect the GW events from the distant Universe up to $z\sim17$ \citep{Abernathy2011}, the wide redshift range of the BBH events enable us to examine whether it would be possible to detect the $\alpha$ as a function of redshift.
@@
 The discussion and conclusions are given in the last Section~\ref{sec_summary}.
+\kai{remove ``5" or ``last"}
 Throughout this paper, we assume a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.
@@
 \section{Data simulation} \label{sec_simulation}
-In this section we describe the simulation of a realistic mock catalog of GW signals from BBHs detectable by future ET interferometric detector.
-Numerical predictions of BBH inspirals detecable by the ET
+In this section we describe the simulation of a realistic mock catalog of GW signals from BBHs detectable by future \textbf{ET interferometric detector}.
+Numerical predictions of BBH inspirals detecable\kai{detectable} by the\kai{remove ``the"} ET
 have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of order $\sim10^{4-5}$ \citep{Abernathy2011, Ola2013, Biesiada2014}.
@@
 The backbone of this approach is to build up a mock universe which includes a sufficient volume of BBH events to represent the overall sample.
-We refer the reader for the details in \citet[][Section 2, therein]{Yang2019}  and briefly recall the key points below.
+We refer the reader\kai{s} for the details in \citet[][Section 2, therein]{Yang2019}  and briefly recall the key points below.
 
@@
 the dimensionless expansion rate of the universe at redshift $z_s$. 
-Concerning the cosmological model, in order to comply with \citet{Dominik13} we assume a flat $Lambda$CDM model with $\Omega_m = 0.3$ and $H_0 = 70 \; km s^{-1} Mpc^{-1}$.
+Concerning the cosmological model, in order to comply with \citet{Dominik13} we assume a flat $Lambda$CDM\kai{L} model with $\Omega_m = 0.3$ and $H_0 = 70 \; km s^{-1} Mpc^{-1}$\kai{no need to repeat here?}.
 %Hence, the overall amount of BBH events in the universe can be calculated by ${\dot N} = \int_0^{ \infty} \frac{d {\dot N (z)}}{dz} dz$.
@@
  \end{equation}
-where $\mathcal{H}$ is the Heaviside step function.
+where $\mathcal{H}$ is the Heaviside step function\kai{We may express this function here}.
 Then, the secondary mass, \mtwo, is fixed as uniform between $[M_{min}, m_1]$.
@@
 We combine them with their redshift $z_s$ to generate the $\rho$ of each BBH system.
-We collect only the events which have $\rho > \rho_0 = 8$, meaning that those events with $\rho < 8$ are to faint to be detected.
+We collect only the events which have $\rho > \rho_0 = 8$, meaning that those events with $\rho < 8$ are to\kai{too} faint to be detected\kai{to detect}.
 
 Concerning the BHMF we consider two scenarios.
-In the first scenario, the $\alpha$ exponent is constant, hence the shape of the BHMF is fixed throughout the redshfit range probed by the ET.
+In the first scenario, the $\alpha$ exponent\kai{exponent $\alpha$} is constant, hence the shape of the BHMF is fixed throughout the redshfit range probed by the ET.
 In the second scenario, we consider that $\alpha$ varies as a function of redshift according to:
@@
  \end{equation}
+ \kai{From my view, I would parameterize $M_{max}$ and $M_{min}$ rather than the shape of mass function, it is like the CDM hieratical model.
+ BH mass grows with time maybe?}
 so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$.
-This is actually the first order Taylor expansion in the scale factor $a(t)$ of an unknown $\alpha(a(t))$ function.
+This is actually the first order Taylor expansion in the scale factor $a(t)$ of an unknown $\alpha(a(t))$\kai{it's redundant} function.
 
-\subsection{Measurement Error} \label{sec_noiselevel}
+\subsection{Measurement Error\kai{parameter estimation error}} \label{sec_noiselevel}
 We aim to produce the mock dataset of the future GW events representative of the ET  measurements.
-In order to consider the measurement uncertainties in a realistic way, we inject random statistical uncertainties into the mock data as described below.
+In order to consider the measurement uncertainties in a realistic way, we inject\kai{distribute} random statistical uncertainties into the mock data\kai``{mock data" has included the uncertainties?} as described below.
 
@@
 Moreover, we stress that the measurements of the BBH parameters are characterized by ${\it skewed}$ distributions.
-Therefore, instead of the traditional Gaussian distribution, we assume that the measured parameters follow the Log-Normal distribution with the standard deviation of  ${\cal M}_0$, \dl, and \mone\ equal to 0.17, 0.35 and 0.2, respectively.
+Therefore, instead of the traditional Gaussian distribution, we assume that the measured parameters follow the Log-Normal distribution\kai{cite references} with the standard deviation of  ${\cal M}_0$, \dl, and \mone\ equal to 0.17, 0.35 and 0.2, respectively.
 For instance, if the $m_{1,fid}$ is the true value for \mone, its probability density is:
  \begin{equation} \label{equ_lognorm}
-p(m_1) = \frac{1}{m_1 \sigma_{m_1} \sqrt{2\pi}} exp \big(- \frac{log(m_1)-log(m_{1,fid})}{2\sigma_{m_1}} \big) 
+p(m_1) = \frac{1}{m_1 \sigma_{m_1} \sqrt{2\pi}} exp \big(- \frac{log(m_1)-log(m_{1,fid})}{2\sigma_{m_1}} \big) \kai{you may use \left[ \right]}
  \end{equation}
@@
 Having clarified the MC approach and defined data the uncertainty level, we are capable of producing the mock GW dataset. As an illustration, we list in Table~\ref{tab_GW_mock_data} a 
-part of the simulated data comprising in total thousand BBH inspiral events. 
+part of the simulated data comprising in total \kai{one?} thousand BBH inspiral events. 
 We use these data to infer the BHMF in next sections.
+\kai{In my understandings, as a prediction paper, only the uncertainties matter.
+The best-fit values must be deviated from the inputs for one MC process and are meaningless.}
 
@@
 \tablecomments{The catalog of simulated thousand BBH inspiral events is used to test the inference of the BHMF from the data attainable in forthcoming next generation GW detector -- the ET.
+\kai{What do the numbers mean?
+Are they 50th plus 16th and 84th pencentiles?}
 }
@@
 Yet, the redshift $z_s$ is the unknown parameter since it is non-measurable in the GW detectors.
-Therefore, we take the \dl\ as redshift estimator.
+Therefore, we take the \dl\ as redshift estimator\kai{so $z_s$ also has an uncertainty?}.
 Note that the \dl\ and \cmass\ both have asymmetric distributions with large scatter,hence the inferred $\eta$ is distributed around its true value in a skewed way.
-We find that this skewness could be well described by a Log-Normal distribution, with multiplicative standard deviation\footnote{In Log-Normal distribution, the multiplicative standard deviation is the exponent  of the standard deviation, i.e., $\sigma^* = exp(\sigma)$.} as $\sigma^*=log(\eta)/3$.
+We find\kai{prove it?} that this skewness could be well described by a Log-Normal distribution, with multiplicative standard deviation\footnote{In Log-Normal distribution, the multiplicative standard deviation is the exponent  of the standard deviation, i.e., $\sigma^* = exp(\sigma)$.} as $\sigma^*=log(\eta)/3$.
 Thus, we manually correct this skewness and obtain the non-biased $\eta$.
@@
 In the previous section, we take \dl\ as the redshift estimator to derive the redshift and hence selection factor $\eta$.
-The way to derive the $z$ is quite straightforward: simply an inverse solution of integral function when knowing the \dl$(z)$ and fixing the cosmological model.
+The way to derive the $z$ is quite straightforward: simply an inverse solution of integral function when knowing the \dl$(z)$ and fixing the cosmological model\kai{$d_L$ has an uncertainty, so does $z_s$?}.
 
@@
 %An appendix to introduce the correction for the skewness for the $\eta$.
-We fit the mock data to the BHMF model to infer the distribution of the best-fitted parameter.
+We fit the mock data to the BHMF model to infer the distribution of the best-fitted parameter \kai{distributions, parameters?}.
 To infer a non-biased distribution, we adopt the realization approach.
@@
 In the first scenario, we consider the slope $\alpha$ as a constant.
-We generated the mock data by taking $\alpha~=~2.35$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ as the fiducial values.
+We generated the mock data by taking $\alpha~=~2.35$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ as the fiducial values\kai{Why these values?}.
 We calculate the likelihood by Equation~(\ref{equ_lik_sf}) to infer the best-fitted parameters in each realization.
@@
 One- and two-dimensional distributions for the best-fitted parameters in the scenario A.
-The BHMF is assumed as a power-law with hard cut at the $M_{min}$ and $M_{max}$, with a constant slope ($\alpha$) across all the redshifts.
+The BHMF is assumed as a power-law with hard cut at the $M_{min}$ and $M_{max}$, with a constant slope ($\alpha$) across all the redshifts.\kai{Is $M_{max}$ determined by the observation?
+I mean, from
+the observed largest mass? Is it necessary a parameter in your model?}
 }
@@
 In the second scenario, the $\alpha$ evolves with redshift according to the Equation~(\ref{equ_alphaz}).
-We assume the fiducial parameters as $\alpha_0~=~2.35$, $\alpha_1~=~0.75$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ to generate a thousand datasets in each realization.
+We assume the fiducial parameters as $\alpha_0~=~2.35$, $\alpha_1~=~0.75$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$\kai{Why these values?} to generate a thousand datasets in each realization.
 We present the results in Figure~\ref{fig_result_b}.
@@
 Our result show that, with a volume of one thousands GW measurements, the inferred value of $\alpha_1$ would have a precision of $\pm0.5$.
-That is to say, this volume of measurements is able to distinguish the evolution of BHMF, when $\alpha_1$ is deviated from 0 by a value of 0.5.
+That is to say, this volume of measurements is able to distinguish the evolution of BHMF, when $\alpha_1$ is deviated from 0 by a value of 0.5\kai{only in one sigma confidence interval?}.
 Limited by the computing power, we haven't tested the larger sample of measurements.
@@
 \section{Conclusion \& Discussion} \label{sec_summary}
-The third-generation gravitational wave detector, the Einstein Telescope, will very powerful and capable of detecting $\sim10^5$ GW events per year, with redshift up to $z\sim17$.
-In this study, we investigated how the detections of the BBHs mergers could improve our knowledge of the black hole mass function.
+\kai{Can you discuss what if the distribution is not power-law? Can your method test this model?}
+The third-generation gravitational wave detector, the Einstein Telescope, will \kai{be} very powerful and capable of detecting $\sim10^5$ GW events per year, with redshift up to $z\sim17$.
+In this study, we investigated how the detections of the BBHs \kai{remove ``s"} mergers could improve our knowledge of the black hole mass function.
 
-We performed the Monte Carlo simulation to generate the mock measurements of GW signals from BBHs that would be detected by ET.
+We performed the Monte Carlo simulation to generate the mock measurements of GW signals\kai{parameters inferred from GW signals} from BBHs that would be detected by ET.
 As a starting point, we assumed that the BHMF for the primary BH mass followed a power law distribution.
@@
 M.B. was supported by the Key Foreign Expert Program for the Central Universities No. X2018002.
-%K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. 11603015.
+K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. 11603015.
 \software{  {\sc corner}, \citep{corner},

### 2019-12-08 GW_BH_function/paper_draft/sec_edit_based_on_Marek_edit/main_revised.tex
Send manuscript to Marek

\documentclass[twocolumn]{aastex62}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand\s{$\sim$}
\newcommand{\e}{\'{e}}
\newcommand{\amen}[1]{\textbf{\textit{#1}}}

\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{mathrsfs}
\usepackage[caption=false]{subfig}
\usepackage{float}
\usepackage{multirow}
\usepackage{enumitem}

\shorttitle{Black hole mass function and its redshift evolution by ET}
\shortauthors{Ding et al.}

\newcommand{\kai}[1]{\textcolor{red}{[{\bf Kai}: #1]}} 
\newcommand{\blue}[1]{\textcolor{blue}{#1}} 
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}

\begin{document}

\newcommand{\mbh}{$\mathcal M_{\rm BH}$}
\newcommand{\cmass}{${\cal M}_0$}
\newcommand{\dl}{$d_L$}
\newcommand{\mone}{$m_1$}
\newcommand{\mtwo}{$m_2$}
\newcommand{\snr}{$\rho$}

\title{Black hole mass function and its evolution -- the first prediction for the Einstein Telescope}

\correspondingauthor{Xuheng Ding}
\email{dingxh@whu.edu.cn}

\author%[0000-0001-8917-2148]
{Xuheng Ding}
\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}

%\author{Lilan Yang}
%\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
%\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}

\author%[0000-0002-4359-5994]
{Kai Liao}
\affiliation{School of Science, Wuhan University of Technology, Wuhan 430070, China}

\author%[0000-0003-1308-7304]
{Marek Biesiada}
\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}
%\affiliation{Department of Astrophysics and Cosmology, Institute of Physics, University of Silesia, 75 Pu{\l}ku Piechoty 1, 41-500 Chorz{\'o}w,
%Poland}
\affiliation{National Centre for Nuclear Research, Pasteura 7, 02-093 Warsaw, Poland}

\author%[0000-0002-3567-6743]
{Zong-Hong Zhu}
\affiliation{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\affiliation{Department of Astronomy, Beijing Normal University, Beijing 100875, China}

\begin{abstract}
The knowledge about the  black hole mass function (BHMF) and its evolution would help to understand the origin of the BHs and how BH binaries formed at different stages of the history of the Universe. We demonstrate the ability of future third generation gravitational wave (GW) detector -- the Einstein Telescope (ET) to infer the slope of the BHMF and its evolution with redshift.  We perform the Monte Carlo simulation of the measurements of chirp signals from binary BH systems (BBH) that could be detected by ET, including the BH masses and their luminosity distances (\dl). We use the mass of a primary black hole in each binary system to infer the BHMF as a power-law function with slope parameter as $\alpha$. Taking into account the bias that could be introduced by the uncertainty of measurements and by the selection effect, we \blue{carried out the numerical tests for three different sets of parameters and} find that only one thousand of GW events registered by ET ($\sim1\%$ amount of its yearly detection rate) could accurately infer the $\alpha$ \blue{with a precision of $\alpha\sim0.1$. Furthermore, assuming four sets of parameters, we investigate the validity of our method to recover a scenario where $\alpha$ evolves with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$. Our result shows, taking a thousand GW events and using \dl\ as the redshift estimator, one could infer the value of evolving parameter $\alpha_1$ accurately at the uncertainty level of $\sim0.5$. Our numerical tests verify the reliability of our method; however, the uncertainty levels of the inferred parameters only applies for the assumed sets of the parameters which shouldn't be considered as a universal value for the general case.
}
\end{abstract}

%\keywords{keywords TBD}

\section{Introduction} \label{sec_intro}
%As first identified as a solution to Einstein's field equations by Schwarzschild in 1916 \citep{Schwarzschild1999}, black holes (BHs) have been predicted to remain a bunches of fundamental questions in unifying GR with quantum physics \citep{Hawking1976, Giddings2017}.

The masses of astrophysical black holes (BHs) are known to cover a wide range from stellar-mass to supermassive level ($\sim10^{10} M_{\odot}$). The discovery of 
coalescing binary black holes (BBHs) in LIGO gravitational-wave (GW) detectors is a substantial evidence of stellar-mass BHs \citep{Abbott2016}, while supermassive BHs are supposed to exist in the centers of almost all the galaxies \citep{Lynden-Bell1969, Kormendy1995}. 
%Recently, the first image of a supermassive BH in the center of the giant elliptical galaxy M87 has been reconstructed from radio observations performed by the Event Horizon Telescope \citep{Alberdi2019}. 
GWs provide a direct way to study the inspiralling BBH systems, enabling one to derive their basic parameters including mass, spin and luminosity distances~\citep{Abbott2017phy, Abbott2018}. This creates the opportunity not only to measure the properties of BHs ~\citep{Abbott2018b}, but also answer some fundamental questions concerning cosmography~\citep{Liao2017, Ding2019, Cai2017}, the GW speed~\citep{Fan2017, Collett2017} or the strong lensing of GWs ~\citep{Ola2013, Biesiada2014, Ding2015}. %\kai{seems the references are almost related with lensing. I suggest to cite more LIGO references}

Nevertheless, it is still unclear of how the BHs are formed \citep{Fryer1999, Fryer2001, Mirabel2016}. In particular, the number and mass distribution of stellar-mass BHs in the Universe still need to be clarified.
The recent detections of GW events have brought us a new era of gravitational wave astronomy \citep[e.g.,][]{Abbott2016, Abbott2016_sum, Abbott2018} and opened up a  brand new possibility concerning studying BBH system formation channels. 
At present, however, observations cannot firmly select the basic formation scenarios like the evolution of isolated pairs of stars \citep{Bethe1998, Portegies1998}, chemically homogeneous evolution \citep{Marchant2016, deMink2016}, dynamic binary formation in dense clusters \citep{Portegies2000, Kulkarni1993} and other channels introduced in \citet{Abbott2018b}.
The inference of the distributions of BH mass could be the key to distinguish these scenarios and help to address questions including the physical process and evolutionary environment of binary BH formation.

Current GWTC-1 catalog of binary coalescences detected by LIGO/Virgo GW interferometers includes ten BH-BH binaries and one NS-NS (GW170817) binary \citep{Abbott2018}.  Assuming the BH mass function (BHMF) parametrized as a two-sided truncated power-law, \citet{Kovetz2017PhRvD} estimated that further LIGO measurements would provide thousands of BBHs and constrain the BHMF slope parameter $\alpha$ at 10\% precison. More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF power-law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility) \citep{Abbott2018b}. 
In the next decade, the number of detected coalescences of BBH systems is expected to be increasing rapidly with the improvements of the detector sensitivities. Especially, the third-generation gravitational wave detector Einstein Telescope (ET) is capable of \textbf{detecting $10^4-10^8$} \textbf{coalescing BBHs} per year \citep{Abernathy2011}. Moreover, since this instrument would detect the GW events from the distant Universe up to $z\sim17$ \citep{Abernathy2011}, the wide redshift range of the BBH \textbf{inspiral events} enable us to study the $\alpha$ as a function of redshift. In this study, we use the Monte Carlo (MC) approach to simulate the GW events from BBH \textbf{mergers} that could be measured by the ET. We construct a mock BBH \textbf{merger} catalog to examine their ability to constrain the BHMFs, taking into account the data noise level and selection bias realistically.

This paper is organized as follows. In Section~\ref{sec_simulation} we describe the simulation of the BBH \textbf{inspiral} events detectable by ET using the Monte Carlo approach. In this section, we assume the initial assumptions for the BH mass function used further as true values to be recovered from the data. In Section~\ref{sec_theory}, we introduce the theoretical framework to reconstruct the BHMFs, considering the noise realization and the selection effects. Furthermore, we make a further step by considering the power-law index $\alpha$ as a function of redshift and explore the way to use luminosity distance as redshift estimator and detect such evolution. We present our results in the Section~\ref{sec_result}. The discussion and conclusions are given in the Section~\ref{sec_summary}. Throughout this paper, we assume a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.

\vspace{1cm}
\section{Data simulation} \label{sec_simulation}
In this section we describe the simulation of a realistic mock catalog of GW signals from BBHs detectable by future ET interferometric detector. Numerical predictions of BBH inspirals detectable by ET 
have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of \textbf{order $\sim10^{4-8}$ \citep{Abernathy2011} or at least $\sim10^{5}$ according to less optimistic yet realistic scenarios\citep{Ola2013, Biesiada2014}}. More recently, \citet{Yang2019} developed the approach of a Monte Carlo (MC) simulation to predict the detection rate by explicitly considering each BBH inspiral event sampled from the outcome of the population synthesis model, which provides the way to mimic a realistic BBH GW catalog. The backbone of this approach is to use random seeds to build up a mock universe which includes a sufficient volume of BBH \textbf{inspiral} events with essential parameters that related to this study. We refer the readers for the details in \citet[][Section 2, therein]{Yang2019}  and briefly recall the key points below.

\subsection{Detection Criteria} \label{subsec_criteria}
%We randomly generate the key parameters to determine the signal-to-noise ratio $\rho$ of each GW system. 
For a specific BBH inspiral event at redshift $z_s$, the ET's corresponding signal-to-noise ratio $\rho$ is defined as \citep{Abernathy2011}:

\begin{equation} \label{SNR}
\rho = 8 \Theta \frac{r_0}{d_L(z_s)} \left( \frac{(1+z){\cal M}_0}{1.2 M_{\odot}} \right)^{5/6}
\sqrt {\zeta(f_{max})},
\end{equation}
where $r_0$ is the detector's characteristic distance parameter and $\zeta(f_{max})$ is the dimensionless function reflecting the overlap between the GW signal and the ET's effective bandwidth which is usually simplified as unity. ${\cal M}_0$ is the intrinsic chirp mass defined as $ {\cal M}_0 = \frac{(m_1m_2)^{3/5}}{(m_1+m_2)^{1/5}}$, where \mone\ and \mtwo\ are the
respective masses of the BBH components. $\Theta$ is the orientation factor determined by four angles as \citep{Finn93}:
 \begin{equation} \label{Theta}
 \Theta = 2 [ F_{+}^2(1 + \cos^2{\iota} )^2 + 4 F_{\times}^2 \cos^2{\iota} ]^{1/2},
 \end{equation}
where: $F_{+} = \frac{1}{2} (1 + \cos^2{\theta}) \cos{2\phi} \cos{2 \psi} - \cos{\theta} \sin{2 \phi} \sin{ 2 \psi}$, and
$F_{\times} = \frac{1}{2} (1 + \cos^2{\theta}) \sin{2\phi} \cos{2 \psi} + \cos{\theta} \sin{2 \phi} \cos{ 2 \psi}$ are so-called antenna patterns. The four angles ($\theta, \phi, \psi, \iota$) describe respectively the
direction to the BBH system relative to the detector and the binary orientation relative to the line of sight between it and the detector. 
They are independent and one can assume that $(\cos\theta, \phi/\pi, \psi/\pi, \cos\iota)$ distributed uniformly over the range $[-1, 1]$. The GW signal is considered as detectable if its \snr\ is over the detecting threshold, i.e., $\rho > \rho_0 = 8$.

\subsection{Monte Carlo Approach} \label{MC}

We aim to build up a sufficient volume of BBH systems in the mock universe by randomly generating the key parameters for each BBH system \textbf{as specified below. First key parameter is the redshift $z_s$.}  We sample the \textbf{merging BBH systems} according to the yearly merger rate in a redshift interval  $[z_{s}, z_{s}+dz_{s}]$:
 \begin{equation}
 d\dot{N} (z_s)=4\pi\left(\frac{c}{H_{0}}\right)^3\frac{\dot{n}_{0}(z_{s})}{1+z_{s}}\frac{\tilde{r}^2(z_{s})}{E(z_{s})}dz_{s}. 
 \end{equation}
where the intrinsic BBH merger rate $\dot{n}_{0}(z_{s})$ is the one predicted by the population synthesis model (using {\tt StarTrack} code\footnote{The data is taken from the website \url{http://www.syntheticuniverse.org}.}) in \citet{Dominik13}, $\tilde{r}(z_{s})$ is the dimensionless comoving distance to the source, and $E (z_s)$ is
the dimensionless expansion rate of the universe at redshift $z_s$. 
%Note that the cosmological model we adopted is comply with the one in \citet{Dominik13}.
%For each BBH system, we sample the probability distribution of the key parameters to randomly generate their values. These 
{\bf Other key parameters include the four angles $(\theta, \phi, \psi, \iota)$ in the Equation~(\ref{Theta})  and the masses of each BH in the binary system (i.e., \mone\ and \mtwo).}
For the purpose of randomly generating the BH masses, we follow the previous works \citep{Kovetz2017PhRvD, Abbott2018b, Fishbach2018} and assume that \mone\ follows a power-law distribution with a hard cut at both maximum and minimum mass:
 \begin{equation} \label{equ_powlaw}
{\bf P(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),}
 \end{equation}
where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo, is %fixed
\textbf{sampled from a uniform distribution} 
between $[M_{min}, m_1]$. Let us note that, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ actually does not affect the inference for the shape of BHMF. 
\textbf{For the purpose of the simulation, however, all these parameters are necessary to} determine the value of $\Theta$ and ${\cal M}_0$ in Equation~(\ref{SNR}). We combine them with their redshift $z_s$ to generate the $\rho$ of each BBH \textbf{inspiraling} system. We only collect the events which have $\rho > \rho_0 = 8$, meaning that those events with $\rho < 8$ are too faint to detect.

Concerning the BHMF we consider two scenarios. In the first scenario, the exponent $\alpha$ is constant, hence the shape of the BHMF is fixed throughout the redshfit range probed by the ET. In the second scenario, we consider that $\alpha$ varies as a function of redshift according to:
 \begin{equation} \label{equ_alphaz}
\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z} , 
 \end{equation}
% \kai{From my view, I would parameterize $M_{max}$ and $M_{min}$ rather than the shape of mass function, it is like the CDM hieratical model. BH mass grows with time maybe?}
so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$. \textbf{The above form is not motivated by any physical model.}
This is actually the first order Taylor expansion in the scale factor $a(t)$ for any function.

\subsection{Estimation of Parameter Error} \label{sec_noiselevel}
We aim to produce the mock dataset of the future GW events representative of the ET  measurements. In order to consider the measurement uncertainties in the realistic way, we distribute random statistical uncertainties into the simulated data as described below.

\textbf{The parameters \it{measurable} from the BBH inspiral waveform comprised of \dl, redshifted chirp mass $(1+z){\cal M}_0 $ and $\rho$.} Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform. 
\blue{We note the fact that LIGO detections usually infer the properties an asymmetry upper and lower limit with ${\it skewed}$ possibility distributions. Therefore, instead of the symmetric Gaussian distribution, we assume that the simulated mock measurements follow the Log-Normal distribution with the standard deviation of  ${\cal M}_0$, \dl, and \mone\ equal to 0.17, 0.35 and 0.2, respectively.}
For instance, if the $m_{1,fid}$ is the true value for \mone, \blue{the probability density as used to simulate the measured value} is:
 \begin{equation} \label{equ_lognorm}
P(m_1) = \frac{1}{m_1 \sigma_{m_1} \sqrt{2\pi}} exp \left[- \frac{log(m_1)-log(m_{1,fid})}{2\sigma_{m_1}} \right].
 \end{equation}
\blue{We set up the standard errors for ${\cal M}_0$, \dl, and \mone\ by taking results by \citet{Ghosh2016} as the reference, who explored the expected statistical uncertainties with which the parameters of black hole binaries can be measured from GW observations by next generation ground-based GW observatories. Note that the assumed uncertainty level of these properties should only affect the uncertainty (i.e., precision) of the inferred parameters, which wouldn't affect the validity (i.e., accuracy) test of our method.
}

Having clarified the MC approach and defined data the uncertainty level, we are capable of producing the mock GW dataset. For demonstrating propose, we list an example of one thousand BBH inspiral events as simulated in one realization of the MCMC seeding process. %\kai{In my understandings, as a prediction paper, only the uncertainties matter. The best-fit values must be deviated from the inputs for one MC process and are meaningless. Xuheng Totally agree.}

\begin{deluxetable}{lcccc}
\tablecolumns{5}
\tabletypesize{\footnotesize}
\tablewidth{0pt}
\tablecaption{Illustration of the mock GW catalog} 
\tablehead{ 
\colhead{Object ID} &
\colhead{\mone}&
\colhead{Luminosity Distance} & 
\colhead{Chirp Mass} &
\colhead{SNR}
\\ 
\colhead{} &
\colhead{($M_\odot$)}&
\colhead{(Mpc)} & 
\colhead{($M_\odot$)} &
\colhead{(\snr)}
\\
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)}
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
ID1 & $95.85\substack{+21.22\\-17.37}$  & $87120.7\substack{+19288.8\\-15792.3}$  & $61.87\substack{+13.70\\-11.21}$ & 28.707 \\
ID2 & $13.31\substack{+2.95\\-2.41}$  & $81476.5\substack{+18039.1\\-14769.2}$  & $11.68\substack{+2.59\\-2.12}$ & 10.468 \\
ID3 & $7.40\substack{+1.64\\-1.34}$  & $7456.8\substack{+1651.0\\-1351.7}$  & $6.82\substack{+1.51\\-1.24}$ & 39.673 \\
ID4 & $19.02\substack{+4.21\\-3.45}$  & $96201.9\substack{+21299.4\\-17438.4}$  & $19.11\substack{+4.23\\-3.46}$ & 12.227 \\
ID5 & $15.12\substack{+3.35\\-2.74}$  & $47645.3\substack{+10548.8\\-8636.6}$  & $14.24\substack{+3.15\\-2.58}$ & 12.672 \\
ID6 & $18.95\substack{+4.20\\-3.43}$  & $23937.4\substack{+5299.8\\-4339.1}$  & $13.86\substack{+3.07\\-2.51}$ & 16.027 \\
ID7 & $8.65\substack{+1.92\\-1.57}$  & $44053.0\substack{+9753.4\\-7985.4}$  & $6.99\substack{+1.55\\-1.27}$ & 8.383 \\
ID8 & $40.03\substack{+8.86\\-7.26}$  & $60432.5\substack{+13379.9\\-10954.6}$  & $25.53\substack{+5.65\\-4.63}$ & 17.917 \\
ID9 & $32.58\substack{+7.21\\-5.91}$  & $4293.5\substack{+950.6\\-778.3}$  & $18.58\substack{+4.11\\-3.37}$ & 34.190 \\
ID10 & $9.88\substack{+2.19\\-1.79}$  & $50294.8\substack{+11135.4\\-9116.9}$  & $4.65\substack{+1.03\\-0.84}$ & 9.608 \\
... & $...$ & ... & ... & ...\\
ID991 & $7.90\substack{+1.75\\-1.43}$  & $10175.7\substack{+2252.9\\-1844.5}$  & $7.31\substack{+1.62\\-1.32}$ & 9.354 \\
ID992 & $15.48\substack{+3.43\\-2.81}$  & $8058.1\substack{+1784.1\\-1460.7}$  & $17.14\substack{+3.80\\-3.11}$ & 11.149 \\
ID993 & $6.11\substack{+1.35\\-1.11}$  & $9566.9\substack{+2118.1\\-1734.2}$  & $4.11\substack{+0.91\\-0.75}$ & 10.703 \\
ID994 & $17.41\substack{+3.85\\-3.16}$  & $232095.1\substack{+51386.5\\-42071.7}$  & $14.46\substack{+3.20\\-2.62}$ & 8.444 \\
ID995 & $23.76\substack{+5.26\\-4.31}$  & $127615.4\substack{+28254.4\\-23132.7}$  & $16.97\substack{+3.76\\-3.08}$ & 14.972 \\
ID996 & $10.43\substack{+2.31\\-1.89}$  & $65546.6\substack{+14512.2\\-11881.6}$  & $6.96\substack{+1.54\\-1.26}$ & 9.497 \\
ID997 & $5.79\substack{+1.28\\-1.05}$  & $24315.0\substack{+5383.4\\-4407.6}$  & $6.93\substack{+1.53\\-1.26}$ & 14.177 \\
ID998 & $12.48\substack{+2.76\\-2.26}$  & $98731.2\substack{+21859.3\\-17896.9}$  & $6.85\substack{+1.52\\-1.24}$ & 13.340 \\
ID999 & $6.95\substack{+1.54\\-1.26}$  & $75187.9\substack{+16646.8\\-13629.2}$  & $3.40\substack{+0.75\\-0.62}$ & 9.437 \\
ID1000 & $6.53\substack{+1.45\\-1.18}$  & $27801.3\substack{+6155.3\\-5039.5}$  & $9.79\substack{+2.17\\-1.77}$ & 8.390 \\
%... & $...$ & ... & ... \\
\enddata
\label{tab_GW_mock_data}
\tablecomments{The catalog of simulated thousand BBH inspiral events is used to test the inference of the BHMF from the data attainable in forthcoming next generation GW detector -- the ET. The reported values are the medians, with errors corresponding to the 16th and 84th percentiles.
}
\end{deluxetable}

\vspace{1cm}
\section{Theoretical Framework}  \label{sec_theory}
In this section, we describe the fitting procedure for the parameterized BHMFs. 
In principle, the modeling for a dataset which follows a power-law distribution as Equation~(\ref{equ_powlaw}) is very straightforward. To derive the posterior of the parameters, one only needs to combine all the measured median values together in a joint likelihood:
 \begin{equation} \label{equ_lik_powlaw}
 P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} P(m_{1,i}|\alpha, M_{max}, M_{min})
 \end{equation}
 \textbf{where $m_{1,i}$ is the primary mass inferred from the $i$~-~$th$ GW event.}
However, the median values of simulated \mone, as shown in Table~\ref{tab_GW_mock_data}, actually deviate from the initial power-law distribution. This deviation stems from several effects that exist in reality. In Section~\ref{sec_likelihood_noise} and \ref{sec_likelihood_sf}, we introduce them and explore the ways to account for them.

\subsection{Measurement Uncertainty}\label{sec_likelihood_noise}
The intrinsic value of primary BH mass (i.e., $m_{1,fid}$) follows a power-law distribution, however the measured  \mone\ is scattered by the Log-Normal distribution which does not follow a power-law function anymore \citep{Koen2009}. In theory, if the event $X$ follows a power-law distribution and its observed values are subject to the Gaussian uncertainty, then $X + e$ is distributed according to the convolution of the power-law and Gaussian distributions. Likewise, given that the noised data follow the Log-Normal distribution, the intrinsic power-law should be convolved with it and enter the likelihood as:
 \begin{equation} \label{equ_lik_conv}
 P(\alpha, M_{max}, M_{min}{\bf |m_{1}}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min}),
 \end{equation}
where the $\hat{P}$ is the a power-law function convolved with the Log-Normal distribution using the standard deviation as 0.2 as we assumed. We illustrate the effect of such convolution in the Figure~\ref{fig:result_slope}.

\begin{figure}%[!b]
\includegraphics[width=1.05\linewidth]{convolving.pdf}
\caption{
Figure illustrating the convolution of a power-law distribution with a Log-Normal distribution having $\sigma = 0.2$. One can see that the convolution make distribution shallower, smoothes the breaking edge at $m_1 = 5 M_{\odot}$ and makes the slope less steep.
}
\label{fig:result_slope}
\end{figure}

\subsection{Selection Effect}\label{sec_likelihood_sf}
The GW observations have a tendency to discover more significant events, known as Malmquist bias. \blue{For example, the} GW systems with higher values \mone\ \blue{trend to} produce stronger signals and thus have a higher probability to be detected. \blue{As a result, the final BHMFs would be biased to the high mass end, if this effect is not correctly taken into account}.

To overcome this selection effect, we introduce the selection factor $\eta$ for the GW event, which is the detecting probability of one event in a repeated simulation. 
The meaning of this factor $\eta$ is straightforward -- if one GW event has $\eta=0.2$, it means that this event has 80\% probability of being be missed. In other words, four equivalent events would have been missed. Thus, for this event, one needs to re-calibrate \blue{this influence by enhancing the likelihood by a power of 5 (i.e., $L^{1/0.2} = L^5$) to recover the possibility to its intrinsic value. Hence, to account for the selection effect, we calculate the likelihood as:}
 \begin{equation} \label{equ_lik_sf}
 P(\alpha, M_{max}, M_{min}{\bf |m_{1}}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta},
 \end{equation}
where $\eta$ is directly determined by the probability distribution of $\rho$, i.e. $\eta = P(\rho>8)$. In order to \blue{adopt the Equation~(\ref{SNR}) to derive the $\rho$}, the distribution function of $\Theta$ is \blue{taken} from the MC simulations; the \cmass\ and \dl\ are \blue{adopted from} the mock dataset as demonstrated in Table~\ref{tab_GW_mock_data}. Yet, the redshift $z_s$ is the unknown parameter since it is non-measurable in the GW detectors; one can only take the \dl\ as redshift estimator.
\blue{Note that the observed \dl\ and \cmass\ are both considered to have random noise which follows the asymmetric distribution (i.e., Log-Normal). Thus, the distribution of their product $\eta$ is also asymmetric. Considering the random distributions of the \dl\ and \cmass, we performed the numerical tests and found that the distribution of $1/\eta$ could be well described by the Log-Normal distribution with multiplicative standard deviation as $\sigma=-log(\eta_{\rm median})/3$, see Figure~\ref{fig_eta}. Note that in a Log-Normal distribution, the expected value are higher than the true value (i.e., median value) by a factor of $e^{\sigma^2/2}$.
We consider this skewness and recalibrate the inferred expected value of $1/\eta$ into the median value, in order to assign a non-biased $1/\eta$ to the calculation.
}

\begin{figure}%[!b]
\includegraphics[width=1.0\linewidth]{eta_distribution.pdf}
\caption{
\blue{
Assuming a set of \dl\ and \cmass\ as Log-Normal distribution, we randomly produce the the corresponding histogram of the $1/\eta$ distribution. The result shows that the skewed distribution could be well described by a Log-Normal distribution with $\sigma = -\log(\eta_{\rm median})/3$.
}
}
\label{fig_eta}
\end{figure}

\subsection{Luminosity Distance as Redshift Estimator} 
\label{sec_dl_z}
%The redshift is not detectable by GW, however, can be inferred from the DL. 
In the previous section, we take \dl\ as the redshift estimator to derive the redshift and hence selection factor $\eta$. The way to derive the \textbf{inferred redshift $z_{inf}$} is an inverse solution of integral function when knowing the \dl$(z)$ and fixing the cosmological model.

Once the cosmological model is assumed, indirect inference of $z_s$ offers an opportunity to model the BHMF slope as a function of redshift. Therefore, we are able to investigate the second scenario described by the Equation~(\ref{equ_alphaz}) as:
 \begin{equation} \label{equ_lik_alphaz}
 \begin{split}
 P&(\alpha_0, \alpha_1, M_{max}, M_{min}{\bf |m_{1},d_L(z)}) \propto \\
  &\prod_{i=1}^{total} \hat{P}(m_{1i}, z_{inf,i} |\alpha_0, \alpha_1, M_{max}, M_{min})^{1/\eta}.
  \end{split}
 \end{equation}

 We present our inference for the BHMF using the mock data in the next section.

\vspace{1cm}
\section{Result}\label{sec_result}
%We present the result in this section.
%One thousand of data points.
%An appendix to introduce the correction for the skewness for the $\eta$.
We fit the mock data to the BHMF model to infer the distribution of the best-fit parameters. To avoid the bias and estimate the scatter, we adopt the realization approach. In each realization, we simulate a thousand of BBH inspiral GW events and infer the best-fit parameters using minimization of the chi-square objective function. \blue{We keep increasing the volume of realizations until the inferred best-fit parameters converged.}

In the first scenario, we consider the slope $\alpha$ as a constant. \blue{ We performed numerical tests assuming three different sets of parameters taking $\alpha$ as 0.8, 1.6 and 2.4, with $M_{min}~=~5M_{\odot}$, $M_{max}~=~50M_{\odot}$. We calculate the likelihood by Equation~(\ref{equ_lik_sf}) to infer the best-fit parameters in each realization. It has been discussed that no black holes with mass over $50M_{\odot}$ are expected from stellar evolution and through supernovae~\citep{Woosley2017, Wiktorowicz2019}.
In Figure~\ref{fig_result_a}, we present the posterior distribution of the inferred parameters for the three parameter sets. We find that all the parameters are recovered accurately which confirms the validity of our method. The uncertainties for the inferred parameters are $\Delta\alpha\sim0.1$, $\Delta M_{max}\sim1-2M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$. Note that these uncertainty levels are not ready to be treated as a universal for the general case, but only apply when the initial parameter sets are close to the tested ones. Moreover, these uncertainty levels are related to the standard deviation of the measurements including ${\cal M}_0$, \dl, and \mone, as discussed in Section~\ref{sec_noiselevel}.
}

\begin{figure*}%[!b]
\centering
\begin{tabular}{c c c}
\subfloat[\blue{assuming $\alpha=0.8$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
{\includegraphics[width=0.3\linewidth]{3para_contour_a0_08.pdf}}&
\subfloat[\blue{assuming $\alpha=1.6$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
{\includegraphics[width=0.3\linewidth]{3para_contour_a0_16.pdf}}&
\subfloat[\blue{assuming $\alpha=2.4$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
{\includegraphics[width=0.3\linewidth]{3para_contour_a0_24.pdf}}
\end{tabular}
\caption{
One- and two-dimensional distributions for the best-fitted parameters in the \blue{first scenario, based on three sets of parameters with a thousand of BBH inspiral GW events}. The BHMF is assumed as a power-law with hard cut at the $M_{min}$ and $M_{max}$, with a constant slope ($\alpha$) across all the redshifts. The blue lines indicate the true value as assumed in the simulation.
}
\label{fig_result_a}
\end{figure*}

In the second scenario, the $\alpha$ evolves with redshift according to the Equation~(\ref{equ_alphaz}). \blue{We consider four sets of parameters assuming $\alpha_0$ as  0.8, 1.6, 2.4 and $\alpha_1$ including 0.7 and 1.2. We present the results in Figure~\ref{fig_result_b} and find that all the assumed parameters could be recovered accurately. With one more parameters included in the second scenario, the uncertainty level are extended as \ding{The following values still need to confirm} $\Delta\alpha_0\sim0.4$, $\Delta\alpha_1\sim0.5-0.7$, $\Delta M_{max}\sim2-4M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$. We note that there is a degeneracy between the $\alpha_0$ and $\alpha_1$, which is understandable given that they are strongly connected by the Equation~\ref{equ_alphaz}. However, for the four sets of parameters we tested, this degeneracy does not affect the inferred uncertainty level for the $\alpha_0$ and $\alpha_1$.
}

We highlight that in this \blue{second} scenario, it is the inferred uncertainty of $\alpha_1$ that matters the most. \blue{Our result show that, with only one thousand of GW measurements in the future, the inferred value of $\alpha_1$ would reach to precision of $\Delta\alpha_1\sim0.5-0.7$. Limited by the computing power, we couldn't use numerical test to get a universal uncertainty level as for the general case. However, given the fours sets of tests as shown the Figure~\ref{fig_result_b}, it is likely to be true that one thousand of GW measurement could distinguish the evolution of BHMF at 1-$\sigma$ confidence level when $\alpha_1$ is deviated from 0 by a value of 0.5. 
Moreover, we conjecture that the precision of inference is increasing with the sample size as a function of $\sqrt{N}$. Thus, for the four sets of tests, the one year measurements of ET ($\sim10^5$ in total) would increase the uncertainty levels by a factor of 10.}
We also note that the distribution of the best-fitted parameters ($\alpha_0$, $\alpha_1$) does not follow the Gaussian distribution, but rather a large fraction of it is concentrated at the center.
%As a result, the 1-$\sigma$ confidence interval in 2-D parameter space are narrower than the ones in 1-D space. %\textcolor{blue}{(What does this suggest?)}

\begin{figure*}%[!b]
\centering
\begin{tabular}{c c}
\subfloat[\blue{assuming $\alpha_0=0.8$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
{\includegraphics[width=0.4\linewidth]{4para_contour_a0_08_a1_07.pdf}}&
\subfloat[\blue{assuming $\alpha_0=0.8$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
{\includegraphics[width=0.4\linewidth]{4para_contour_a0_16_a1_07.pdf}}\\
\subfloat[\blue{assuming $\alpha_0=0.8$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
{\includegraphics[width=0.4\linewidth]{4para_contour_a0_24_a1_07.pdf}}&
\subfloat[\blue{assuming $\alpha_0=0.8$, $\alpha_1=1.2$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
{\includegraphics[width=0.4\linewidth]{4para_contour_a0_16_a1_12.pdf}}
\end{tabular}
\caption{
\blue{Same} as Figure~\ref{fig_result_a} but for the second scenario, where the $\alpha$ of BHMF is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$\blue{, four sets of parameters assumed.}
}
\label{fig_result_b}
\end{figure*}

\vspace{1cm}
\section{Conclusion \& Discussion} \label{sec_summary}
%\kai{Can you discuss what if the distribution is not power-law? Can your method test this model?}
The third-generation gravitational wave detector, the Einstein Telescope, is very powerful and capable of detecting $\sim10^5$ GW events per year, with redshift up to $z\sim17$. In this study, we investigated how the detections of the BBH mergers could improve our knowledge of the black hole mass function \blue{(BHMF)}.

We performed the Monte Carlo simulation to estimate the uncertainty level of BHMF parameters inferred from GW signals by BBHs that would be detected by ET. As a starting point, we assumed that the BHMF for the primary BH mass followed a power-law distribution \blue{with a hard cuts as Equation~(\ref{equ_powlaw})}. Based on the BBH intrinsic merger rate predicted by {\tt StarTrack}, we randomly simulated the key parameters of the BBH systems, including the chirp masses, redshifts and orientation factors and calculated  their corresponding signal-to-noise ratio \snr\ for the ET. We collected the events whose \snr\ exceeds the detecting threshold and injected Log-Normal noise to the detected parameter, including BH mass, chirp mass, luminosity distance as mock data.

We built up a theoretical framework and explore to use the mock measurements to infer the BHMF. We took into account the measurement uncertainties and the selection effect which would bias the inference. We \blue{performed the test using realizations, one thousand GW events per realization}, and estimated the distribution of the best-fitted parameters of the BHMF, including the power-law slope $\alpha$, the maximum BH mass $M_{max}$ and the minimum BH mass $M_{min}$ \blue{in the first scenario}. Furthermore, \blue{in the second scenario, we consider the $\alpha$ evolves as a function of redshift and used the luminosity distance as redshift estimator to test the evolution}. We summarize our main results as follows:
\blue{
\begin{enumerate}
\item Using our method based on Equation~(\ref{equ_lik_sf}), all the tested parameters are all recovered accurately, which confirms the validity of our tests and highlights the importance of correctly considering the measurement uncertainty and selection effect.
\item Taking the measured \dl\ as redshift estimator, we tested to recover the $\alpha$ with a scenario which is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$. Testing with four parameters sets, we are able to successfully recovered the true value of $\alpha_1$ accurately.
\item Given the fixed sets of parameters, our results show that a volume of one thousand measurements of BBHs events could infer the parameters with uncertainties level at $\Delta\alpha\sim0.1$, $\Delta M_{max}\sim1-2M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$ for the first scenario. For the second scenario, the inferred uncertainties are $\Delta\alpha_0\sim0.4$, $\Delta\alpha_1\sim0.5-0.7$, $\Delta M_{max}\sim2-4M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$. In the future, the one year detection rate of ET ($\sim10^5$ in total) increase the sample size by a factor of 100. According to the fact that the precision of the inference increases with the sample size, as a function of $\sqrt{N}$, we conclude that one year BBH sample by ET would be able to deliver the parameters at higher uncertainty improved by a factor of 10 as tested.
\end{enumerate}
}

We point out a few limitations of this work. First, we have adopted a template of intrinsic BBH merger rate based on the predictions by a standard model in {\tt StarTrack}, which can be different from the realistic one. Of course, the intrinsic BBH merger rate is unknown yet, which is related to 
lack of detailed knowledge of different elements such as BBH masses, explosion mechanism, the metallicity history and the time delay distribution. Also, for the sake of simplicity, we simulated the value of the secondary BH mass \mtwo\ by assuming that two masses of BBHs have independent distributions, which probably is not exactly true. However, one can expect that these limitations would more strongly affect the prediction of the yearly detection rate of the GW events and their redshift distribution, rather than the inference of the parameters in the BHMF.
\blue{Last, the numerical tests as done in this works confirms the validity of our method. However, limited by the sets of tests, the inferred uncertainty for both scenario applies for the fixed sets of parameters which shouldn't be considered as a general value.}

In this work, we focused on the inference of the BHMF using the mass properties by the BBH. However, it is worth to note that our approach could be extended to address other problems. For example, one could infer the spin of BH \citep{Abbott2018b}, the mass function for the binary of NS-NS, NS-BH system, though these events are detectable at lower redshift ($z<4$). In addition, using the luminosity as redshift estimator, one should also be able to reconstruct the BBH intrinsic merger rate \citep{Fishbach2018}, the cosmological parameter.

\acknowledgments
We thank Hosek Jr., M.W for the useful discussion.

This work was supported by the National Natural Science Foundation of China under grant Nos. 11633001 and 11373014, the Strategic Priority Research Program of the Chinese Academy of Sciences, grant No. XDB23000000, and the Interdiscipline Research Funds of Beijing Normal University.

X. Ding acknowledges support by China Postdoctoral Science Foundation Funded Project (No. 2017M622501).
%L. Yang is supported from the China Scholarship Council. 
M.B. was supported by the Key Foreign Expert Program for the Central Universities No. X2018002.
K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. {\bf 11973034}..
\software{  {\sc corner}, \citep{corner},
        Matplotlib \citep{Matplotlib},
        and standard Python libraries.
        }

\bibliography{reference}
%\input{reference.bbl}

%\newpage
%\appendix
%\section{section}\label{appendix_section}
%TEXTTEXTTEXTTEXTTEXTTEXTTEXTTEXTTEXT
%\newpage

%\newpage
%\appendix
%\section{Correction for the skewness of the selection factor}\label{appA}
%1. Describe the bias of the selection.
%2. The correction by $\eta/3.$

\end{document}

### 2019-12-08 GW_BH_function/for_Kai_create_mock_GW.py

@@ -32,59 +32,111 @@ import scipy.optimize as op
 import time
 
 a, mbh_max, mbh_min = 2.35, 80., 5.
-test = gene_BHBH(h0=70)
-test.rho0 = 0
 
-event_rate, zs_detected, masses, rhos_detected = test.mc_year_rate(a=a, mbh_max=mbh_max, mbh_min=mbh_min)
-dl_zs = dl(zs_detected)
-sim_data = [event_rate, zs_detected, masses, rhos_detected, dl_zs]
-
-zs_all, chirp_mass_all, m1_all, m2_all, lumi_dis_all = zs_detected, masses[:,0], masses[:,1], masses[:,2], dl_zs                                                      
-#==============================================================================
-#Setting the noise level 
-#==============================================================================
-from scipy import interpolate
-from cal_likelihood import cov_twofun
-from scipy.optimize import fmin
-from cal_likelihood import random_Theta  #The prior given dl and chirpmass, no errorbar
-#def select_effect(m1_obs, fname = 'select_effect_MBHmin5_cov_lognorm0.2'):
-#    x, y  = pickle.load(open(fname,'rb'))
-#    f = interpolate.interp1d(x, y)
-#    prior = f(m1_obs)
-#    return prior
-
-thetas = random_Theta()
-
-rounds = 200
+#%%
+test = gene_BHBH(h0=70, rho0=0, m_type = 'BHBH', scenario=2)
+event_rate, zs_detected, masses, rhos_detected = test.mc_year_rate(a=a, mbh_max=mbh_max, mbh_min=mbh_min, itera=1)
+zs_all, chirp_mass_all, m1_all, m2_all = zs_detected, masses[:,0], masses[:,1], masses[:,2]                                                      
 index = np.arange(len(m1_all))
-
-# =============================================================================
-# Infer the information of the sigma.
-# =============================================================================
-#lines = np.loadtxt('inveres_prior_scatter.txt')
[…]

### 2019-12-08 GW_BH_function/read_para4_corner.py

@@ -17,10 +17,12 @@ matt.rcParams['font.family'] = 'STIXGeneral'
 cmap = matplotlib.cm.get_cmap('viridis')
 
 import corner
-#truths=[1.6, 0.2, 50.0, 5.]
+#truths=[1.6, -0.7, 50.0, 5.]
 #truths=[1.6, 0.7, 50.0, 5.]
-#truths=[1.6, 1.2, 50.0, 5.]
-truths=[0.8, 0.7, 50.0, 5.]
+truths=[1.6, 1.2, 50.0, 5.]
+#truths=[0.8, 0.7, 50.0, 5.]
+#truths=[1.6, 0.7, 50.0, 5.]
+#truths=[2.4, 0.7, 50.0, 5.]
 
 f = open("201911_newrun/model1_a0{0}_a1{1}_mbhmax-50.0_noizl-20.txt".format(truths[0],truths[1]),"r")
 string = f.read()
@@ -51,16 +53,16 @@ numbers = result
 #lines = [lines[i] for i in range(len(lines)) if len(lines[i]) ==4]
 #numbers = np.asarray(lines).astype(float)
 samples = numbers#[numbers[:,1]<3]
-fig = corner.corner(numbers, labels=[r"$\alpha_0$", r"$\alpha_1$", "M$_{max}$", "M$_{min}$"],
+fig = corner.corner(numbers, labels=[r"$\alpha_0$", r"$\alpha_1$", r"M$_{\rm max}$", r"M$_{\rm min}$"],
                     truths=truths,
-                    quantiles=[0.16, 0.5, 0.84],show_titles=True, smooth = 0.7,
+                    quantiles=[0.16, 0.5, 0.84],show_titles=True, smooth =1.0,
                     title_kwargs={"fontsize": 15}, label_kwargs = {"fontsize": 25},
 #                    plot_datapoints=True,smooth=1.0,smooth1d=1.0,
                     levels=1.0 - np.exp(-0.5 * np.array([1.,2.]) ** 2),
                     title_fmt='.2f')
 for ax in fig.get_axes():
       ax.tick_params(axis='both', labelsize=20)
-#fig.savefig("fig_results_4para.pdf")
-#####
+fig.savefig("4para_contour_a0_{0}_a1_{1}.pdf".format(int(truths[0]*10), int(truths[1]*10)))
+####
 plt.show()  
 print len(numbers)

### 2019-12-08 GW_BH_function/run_model0.py

@@ -121,7 +121,7 @@ if if_file == []:
 else:
     para_result =  open(filename,'r+') 
 t1 = time.time()
-rounds = 500
+rounds = 200
 index = np.arange(len(m1_all))
 
 # =============================================================================

### 2019-12-10 GW_BH_function/paper_draft/sec_edit_based_on_Marek_edit/main_revised.tex
Run finished

@@
 {\includegraphics[width=0.4\linewidth]{4para_contour_a0_08_a1_07.pdf}}&
-\subfloat[\blue{assuming $\alpha_0=0.8$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
+\subfloat[\blue{assuming $\alpha_0=1.6$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
 {\includegraphics[width=0.4\linewidth]{4para_contour_a0_16_a1_07.pdf}}\\
-\subfloat[\blue{assuming $\alpha_0=0.8$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
+\subfloat[\blue{assuming $\alpha_0=2.4$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
 {\includegraphics[width=0.4\linewidth]{4para_contour_a0_24_a1_07.pdf}}&
-\subfloat[\blue{assuming $\alpha_0=0.8$, $\alpha_1=1.2$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
+\subfloat[\blue{assuming $\alpha_0=1.6$, $\alpha_1=1.2$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
 {\includegraphics[width=0.4\linewidth]{4para_contour_a0_16_a1_12.pdf}}

### 2019-12-10 GW_BH_function/read_para4_corner.py

@@ -19,8 +19,8 @@ cmap = matplotlib.cm.get_cmap('viridis')
 import corner
 #truths=[1.6, -0.7, 50.0, 5.]
 #truths=[1.6, 0.7, 50.0, 5.]
-truths=[1.6, 1.2, 50.0, 5.]
-#truths=[0.8, 0.7, 50.0, 5.]
+#truths=[1.6, 1.2, 50.0, 5.]
+truths=[0.8, 0.7, 50.0, 5.]
 #truths=[1.6, 0.7, 50.0, 5.]
 #truths=[2.4, 0.7, 50.0, 5.]
 
@@ -55,14 +55,16 @@ numbers = result
 samples = numbers#[numbers[:,1]<3]
 fig = corner.corner(numbers, labels=[r"$\alpha_0$", r"$\alpha_1$", r"M$_{\rm max}$", r"M$_{\rm min}$"],
                     truths=truths,
-                    quantiles=[0.16, 0.5, 0.84],show_titles=True, smooth =1.0,
+                    quantiles=[0.16, 0.5, 0.84],show_titles=True,
                     title_kwargs={"fontsize": 15}, label_kwargs = {"fontsize": 25},
+                    smooth =1.0, #range= [[0.15,2.0],[-1, 2.5],[40, 60],[4.4, 6.0]],
+#                    smooth =1.0, range= [[0.8,3.3],[-1, 3],[35, 64],[4.4, 6.0]],
 #                    plot_datapoints=True,smooth=1.0,smooth1d=1.0,
                     levels=1.0 - np.exp(-0.5 * np.array([1.,2.]) ** 2),
                     title_fmt='.2f')
 for ax in fig.get_axes():
       ax.tick_params(axis='both', labelsize=20)
-fig.savefig("4para_contour_a0_{0}_a1_{1}.pdf".format(int(truths[0]*10), int(truths[1]*10)))
+#fig.savefig("4para_contour_a0_{0}_a1_{1}.pdf".format(int(truths[0]*10), int(truths[1]*10)))
 ####
 plt.show()  
 print len(numbers)

### 2019-12-10 GW_BH_function/run_model1.py

@@ -19,7 +19,7 @@ solve_z = np.vectorize(solve_z)
 #a0, a1, mbh_max, mbh_min = 1.6, 0.7, 50., 5.   #mode1  a0: 0.8, 1.6, 2.4  a1: 0.2. 0.7, 1.2
 a0, a1, mbh_max, mbh_min = 2.4, 0.7, 50., 5.   #mode1
 
-part = 12
+part = 23
 
 seed = 2
 filename = 'sim_a0_{0}_a1_{1}_max_{2}'.format(a0, a1, mbh_max)

### 2020-01-17 GW_BH_function/paper_draft/2020_revise/main_revised.tex
Push before combining Marek's edits

--- 2019-12-10 GW_BH_function/paper_draft/sec_edit_based_on_Marek_edit/main_revised.tex
@@
 \newcommand{\kai}[1]{\textcolor{red}{[{\bf Kai}: #1]}} 
-\newcommand{\blue}[1]{\textcolor{blue}{#1}} 
+\newcommand{\blue}[1]{{#1}} 
 \newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
@@
 
-\correspondingauthor{Xuheng Ding}
-\email{dingxh@whu.edu.cn}
+\correspondingauthor{{\bf Zong-Hong Zhu}}
+\email{zhuzh@whu.edu.cn}
 
@@
 We use the mass of a primary black hole in each binary system to infer the BHMF as a power-law function with slope parameter as $\alpha$.
-Taking into account the bias that could be introduced by the uncertainty of measurements and by the selection effect, we \blue{carried out the numerical tests for three different sets of parameters and} find that only one thousand of GW events registered by ET ($\sim1\%$ amount of its yearly detection rate) could accurately infer the $\alpha$ \blue{with a precision of $\alpha\sim0.1$.
-Furthermore, assuming four sets of parameters, we investigate the validity of our method to recover a scenario where $\alpha$ evolves with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
-Our result shows, taking a thousand GW events and using \dl\ as the redshift estimator, one could infer the value of evolving parameter $\alpha_1$ accurately at the uncertainty level of $\sim0.5$.
-Our numerical tests verify the reliability of our method; however, the uncertainty levels of the inferred parameters only applies for the assumed sets of the parameters which shouldn't be considered as a universal value for the general case.
-}
+Taking into account the bias that could be introduced by the uncertainty of measurements and by the selection effect, we carried out the numerical tests and find that only one thousand of GW events registered by ET ($\sim1\%$ amount of its yearly detection rate) could accurately infer the $\alpha$ with a precision of $\alpha\sim0.1$.
+Furthermore, we investigate the validity of our method to recover a scenario where $\alpha$ evolves with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
+Taking a thousand of GW events and using \dl\ as the redshift estimator, our tests show that one could infer the value of evolving parameter $\alpha_1$ accurately with the uncertainty level of $\sim0.5$.
+Our numerical tests verify the reliability of our method.
+The uncertainty levels of the inferred parameters can be trusted directly for the several sets of the parameter we assumed, yet shouldn't be treated as a universal level for the general case.
 \end{abstract}
@@
 Current GWTC-1 catalog of binary coalescences detected by LIGO/Virgo GW interferometers includes ten BH-BH binaries and one NS-NS (GW170817) binary \citep{Abbott2018}.
-Assuming the BH mass function (BHMF) parametrized as a two-sided truncated power-law, \citet{Kovetz2017PhRvD} estimated that further LIGO measurements would provide thousands of BBHs and constrain the BHMF slope parameter $\alpha$ at 10\% precison.
+Assuming the BH mass function (BHMF) parametrized as a two-sided truncated power-law, \citet{Kovetz2017PhRvD} estimated that further LIGO measurements would provide thousands of BBHs and constrain the BHMF slope parameter $\alpha$ at 10\% precision.
 More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF power-law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility) \citep{Abbott2018b}.
 In the next decade, the number of detected coalescences of BBH systems is expected to be increasing rapidly with the improvements of the detector sensitivities.
-Especially, the third-generation gravitational wave detector Einstein Telescope (ET) is capable of \textbf{detecting $10^4-10^8$} \textbf{coalescing BBHs} per year \citep{Abernathy2011}.
-Moreover, since this instrument would detect the GW events from the distant Universe up to $z\sim17$ \citep{Abernathy2011}, the wide redshift range of the BBH \textbf{inspiral events} enable us to study the $\alpha$ as a function of redshift.
-In this study, we use the Monte Carlo (MC) approach to simulate the GW events from BBH \textbf{mergers} that could be measured by the ET.
-We construct a mock BBH \textbf{merger} catalog to examine their ability to constrain the BHMFs, taking into account the data noise level and selection bias realistically.
+Especially, the third-generation gravitational wave detector Einstein Telescope (ET) is capable of detecting $10^4-10^8$ coalescing BBHs per year \citep{Abernathy2011}.
+Moreover, since this instrument would detect the GW events from the distant Universe up to $z\sim17$ \citep{Abernathy2011}, the wide redshift range of the BBH inspiral events enable us to study the $\alpha$ as a function of redshift.
+In this study, we use the Monte Carlo (MC) approach to simulate the GW events from BBH mergers that could be measured by the ET.
+We construct a mock BBH merger catalog to examine their ability to constrain the BHMFs, taking into account the data noise level and selection bias realistically.
 
 This paper is organized as follows.
-In Section~\ref{sec_simulation} we describe the simulation of the BBH \textbf{inspiral} events detectable by ET using the Monte Carlo approach.
+In Section~\ref{sec_simulation} we describe the simulation of the BBH inspiral events detectable by ET using the Monte Carlo approach.
 In this section, we assume the initial assumptions for the BH mass function used further as true values to be recovered from the data.
@@
 Numerical predictions of BBH inspirals detectable by ET
-have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of \textbf{order $\sim10^{4-8}$ \citep{Abernathy2011} or at least $\sim10^{5}$ according to less optimistic yet realistic scenarios\citep{Ola2013, Biesiada2014}}.
+have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of order $\sim10^{4-8}$ \citep{Abernathy2011} or at least $\sim10^{5}$ according to less optimistic yet realistic scenarios \citep{Ola2013, Biesiada2014}.
 More recently, \citet{Yang2019} developed the approach of a Monte Carlo (MC) simulation to predict the detection rate by explicitly considering each BBH inspiral event sampled from the outcome of the population synthesis model, which provides the way to mimic a realistic BBH GW catalog.
-The backbone of this approach is to use random seeds to build up a mock universe which includes a sufficient volume of BBH \textbf{inspiral} events with essential parameters that related to this study.
+The backbone of this approach is to use random seeds to build up a mock universe which includes a sufficient volume of BBH inspiral events with essential parameters that related to this study.
 We refer the readers for the details in \citet[][Section 2, therein]{Yang2019}  and briefly recall the key points below.
@@
 \end{equation}
-where $r_0$ is the detector's characteristic distance parameter and $\zeta(f_{max})$ is the dimensionless function reflecting the overlap between the GW signal and the ET's effective bandwidth which is usually simplified as unity.
-${\cal M}_0$ is the intrinsic chirp mass defined as $ {\cal M}_0 = \frac{(m_1m_2)^{3/5}}{(m_1+m_2)^{1/5}}$, where \mone\ and \mtwo\ are the
+where $r_0$ is the detector's characteristic distance parameter and $\zeta(f_{max})$ is the dimensionless function reflecting the overlap between the GW signal and the ET's effective {\bf bandwidth.
+For simplicity, we follow the estimations by \citet{Taylor2012} and approximate $\zeta(f_{max})$ as  unity.} ${\cal M}_0$ is the intrinsic chirp mass defined as $ {\cal M}_0 = \frac{(m_1m_2)^{3/5}}{(m_1+m_2)^{1/5}}$, where \mone\ and \mtwo\ are the
 respective masses of the BBH components. $\Theta$ is the orientation factor determined by four angles as \citep{Finn93}:
@@
 
-We aim to build up a sufficient volume of BBH systems in the mock universe by randomly generating the key parameters for each BBH system \textbf{as specified below.
-First key parameter is the redshift $z_s$.}  We sample the \textbf{merging BBH systems} according to the yearly merger rate in a redshift interval  $[z_{s}, z_{s}+dz_{s}]$:
+We aim to build up a sufficient volume of BBH systems in the mock universe by randomly generating the key parameters for each BBH system as specified below.
+First key parameter is the redshift $z_s$.
+We sample the merging BBH systems according to the yearly merger rate in a redshift interval  $[z_{s}, z_{s}+dz_{s}]$:
  \begin{equation}
@@
 %For each BBH system, we sample the probability distribution of the key parameters to randomly generate their values. These 
-{\bf Other key parameters include the four angles $(\theta, \phi, \psi, \iota)$ in the Equation~(\ref{Theta})  and the masses of each BH in the binary system (i.e., \mone\ and \mtwo).}
+Other key parameters include the four angles $(\theta, \phi, \psi, \iota)$ in the Equation~(\ref{Theta})  and the masses of each BH in the binary system (i.e., \mone\ and \mtwo).
 For the purpose of randomly generating the BH masses, we follow the previous works \citep{Kovetz2017PhRvD, Abbott2018b, Fishbach2018} and assume that \mone\ follows a power-law distribution with a hard cut at both maximum and minimum mass:
  \begin{equation} \label{equ_powlaw}
-{\bf P(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),}
+P(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),
  \end{equation}
-where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo, is %fixed
-\textbf{sampled from a uniform distribution} 
+where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo\, is %fixed
+sampled from a uniform distribution
 between $[M_{min}, m_1]$.
 Let us note that, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ actually does not affect the inference for the shape of BHMF.
-\textbf{For the purpose of the simulation, however, all these parameters are necessary to} determine the value of $\Theta$ and ${\cal M}_0$ in Equation~(\ref{SNR}).
-We combine them with their redshift $z_s$ to generate the $\rho$ of each BBH \textbf{inspiraling} system.
+For the purpose of the simulation, however, all these parameters are necessary to determine the value of $\Theta$ and ${\cal M}_0$ in Equation~(\ref{SNR}).
+We combine them with their redshift $z_s$ to generate the $\rho$ of each BBH inspiraling system.
 We only collect the events which have $\rho > \rho_0 = 8$, meaning that those events with $\rho < 8$ are too faint to detect.
@@
 % \kai{From my view, I would parameterize $M_{max}$ and $M_{min}$ rather than the shape of mass function, it is like the CDM hieratical model. BH mass grows with time maybe?}
-so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$. \textbf{The above form is not motivated by any physical model.}
-This is actually the first order Taylor expansion in the scale factor $a(t)$ for any function.
+so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$.
+We do not have any clear physical guidance of how could $\alpha$ evolve  with redshift and in particular which analytical expression would describe it reliably.
+Therefore the above ansatz is actually the first order Taylor expansion{, \bf assumption $\alpha$ as a function of the scale factor $a$, where $a(t) = \frac{1}{1+z}$.}
+%in the scale factor $a(t)$ applicable for any function.
 
@@
 
-\textbf{The parameters \it{measurable} from the BBH inspiral waveform comprised of \dl, redshifted chirp mass $(1+z){\cal M}_0 $ and $\rho$.} Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform.
-\blue{We note the fact that LIGO detections usually infer the properties an asymmetry upper and lower limit with ${\it skewed}$ possibility distributions.
-Therefore, instead of the symmetric Gaussian distribution, we assume that the simulated mock measurements follow the Log-Normal distribution with the standard deviation of  ${\cal M}_0$, \dl, and \mone\ equal to 0.17, 0.35 and 0.2, respectively.}
-For instance, if the $m_{1,fid}$ is the true value for \mone, \blue{the probability density as used to simulate the measured value} is:
+The quantities measurable from the BBH inspiral waveform comprised of \dl, redshifted chirp mass $(1+z){\cal M}_0 $ and $\rho$.
+Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform.
+Let us note that physical quantities inferred from the LIGO detections had asymmetric upper and lower uncertainty limits, hence they followed the  ${\it skewed}$  distributions.
+Therefore, instead of the symmetric Gaussian distribution, we assume that the simulated mock measurements follow the Log-Normal distribution with the standard deviation of  ${\cal M}_0$, \dl, and \mone\ equal to 0.17, 0.35 and 0.2, respectively.
+For instance, if the $m_{1,fid}$ is the true value for \mone, the probability density used to simulate the measured value is:
  \begin{equation} \label{equ_lognorm}
@@
  \end{equation}
-\blue{We set up the standard errors for ${\cal M}_0$, \dl, and \mone\ by taking results by \citet{Ghosh2016} as the reference, who explored the expected statistical uncertainties with which the parameters of black hole binaries can be measured from GW observations by next generation ground-based GW observatories.
-Note that the assumed uncertainty level of these properties should only affect the uncertainty (i.e., precision) of the inferred parameters, which wouldn't affect the validity (i.e., accuracy) test of our method.
-}
+We set up the uncertainties for ${\cal M}_0$, \dl, and \mone\ by taking results of \citet{Ghosh2016} as the reference, who explored the expected statistical uncertainties with which the parameters of black hole binaries can be measured from GW observations by next generation ground-based GW observatories.
+Note that the assumed uncertainty level of these quantities only affect the uncertainty of the inferred parameters (i.e.
+the precision) and wouldn't affect the validity test of our method (i.e.
+the  accuracy).
 
@@
 %\\
-ID1 & $95.85\substack{+21.22\\-17.37}$  & $87120.7\substack{+19288.8\\-15792.3}$  & $61.87\substack{+13.70\\-11.21}$ & 28.707 \\
-ID2 & $13.31\substack{+2.95\\-2.41}$  & $81476.5\substack{+18039.1\\-14769.2}$  & $11.68\substack{+2.59\\-2.12}$ & 10.468 \\
-ID3 & $7.40\substack{+1.64\\-1.34}$  & $7456.8\substack{+1651.0\\-1351.7}$  & $6.82\substack{+1.51\\-1.24}$ & 39.673 \\
-ID4 & $19.02\substack{+4.21\\-3.45}$  & $96201.9\substack{+21299.4\\-17438.4}$  & $19.11\substack{+4.23\\-3.46}$ & 12.227 \\
-ID5 & $15.12\substack{+3.35\\-2.74}$  & $47645.3\substack{+10548.8\\-8636.6}$  & $14.24\substack{+3.15\\-2.58}$ & 12.672 \\
-ID6 & $18.95\substack{+4.20\\-3.43}$  & $23937.4\substack{+5299.8\\-4339.1}$  & $13.86\substack{+3.07\\-2.51}$ & 16.027 \\
-ID7 & $8.65\substack{+1.92\\-1.57}$  & $44053.0\substack{+9753.4\\-7985.4}$  & $6.99\substack{+1.55\\-1.27}$ & 8.383 \\
-ID8 & $40.03\substack{+8.86\\-7.26}$  & $60432.5\substack{+13379.9\\-10954.6}$  & $25.53\substack{+5.65\\-4.63}$ & 17.917 \\
-ID9 & $32.58\substack{+7.21\\-5.91}$  & $4293.5\substack{+950.6\\-778.3}$  & $18.58\substack{+4.11\\-3.37}$ & 34.190 \\
-ID10 & $9.88\substack{+2.19\\-1.79}$  & $50294.8\substack{+11135.4\\-9116.9}$  & $4.65\substack{+1.03\\-0.84}$ & 9.608 \\
+ID1 & $8.14\substack{+1.80\\-1.48}$  & $25356.8\substack{+5614.1\\-4596.4}$  & $9.91\substack{+2.19\\-1.80}$ & 18.512 \\
+ID2 & $43.93\substack{+9.73\\-7.96}$  & $12956.9\substack{+2868.7\\-2348.7}$  & $28.64\substack{+6.34\\-5.19}$ & 46.953 \\
+ID3 & $5.05\substack{+1.12\\-0.92}$  & $8617.6\substack{+1908.0\\-1562.1}$  & $3.60\substack{+0.80\\-0.65}$ & 9.836 \\
+ID4 & $13.93\substack{+3.08\\-2.53}$  & $47473.1\substack{+10510.7\\-8605.4}$  & $10.97\substack{+2.43\\-1.99}$ & 17.563 \\
+ID5 & $11.37\substack{+2.52\\-2.06}$  & $21485.0\substack{+4756.8\\-3894.6}$  & $10.68\substack{+2.36\\-1.94}$ & 31.107 \\
+ID6 & $21.67\substack{+4.80\\-3.93}$  & $9446.1\substack{+2091.4\\-1712.3}$  & $7.64\substack{+1.69\\-1.39}$ & 31.624 \\
+ID7 & $32.20\substack{+7.13\\-5.84}$  & $69317.4\substack{+15347.1\\-12565.1}$  & $19.35\substack{+4.28\\-3.51}$ & 13.496 \\
+ID8 & $7.73\substack{+1.71\\-1.40}$  & $25104.5\substack{+5558.2\\-4550.7}$  & $6.68\substack{+1.48\\-1.21}$ & 9.612 \\
+ID9 & $35.63\substack{+7.89\\-6.46}$  & $16321.8\substack{+3613.7\\-2958.6}$  & $10.96\substack{+2.43\\-1.99}$ & 16.202 \\
+ID10 & $18.78\substack{+4.16\\-3.40}$  & $54375.1\substack{+12038.8\\-9856.5}$  & $15.16\substack{+3.36\\-2.75}$ & 29.232 \\
 ... & $...$ & ... & ... & ...\\
-ID991 & $7.90\substack{+1.75\\-1.43}$  & $10175.7\substack{+2252.9\\-1844.5}$  & $7.31\substack{+1.62\\-1.32}$ & 9.354 \\
-ID992 & $15.48\substack{+3.43\\-2.81}$  & $8058.1\substack{+1784.1\\-1460.7}$  & $17.14\substack{+3.80\\-3.11}$ & 11.149 \\
-ID993 & $6.11\substack{+1.35\\-1.11}$  & $9566.9\substack{+2118.1\\-1734.2}$  & $4.11\substack{+0.91\\-0.75}$ & 10.703 \\
-ID994 & $17.41\substack{+3.85\\-3.16}$  & $232095.1\substack{+51386.5\\-42071.7}$  & $14.46\substack{+3.20\\-2.62}$ & 8.444 \\
-ID995 & $23.76\substack{+5.26\\-4.31}$  & $127615.4\substack{+28254.4\\-23132.7}$  & $16.97\substack{+3.76\\-3.08}$ & 14.972 \\
-ID996 & $10.43\substack{+2.31\\-1.89}$  & $65546.6\substack{+14512.2\\-11881.6}$  & $6.96\substack{+1.54\\-1.26}$ & 9.497 \\
-ID997 & $5.79\substack{+1.28\\-1.05}$  & $24315.0\substack{+5383.4\\-4407.6}$  & $6.93\substack{+1.53\\-1.26}$ & 14.177 \\
-ID998 & $12.48\substack{+2.76\\-2.26}$  & $98731.2\substack{+21859.3\\-17896.9}$  & $6.85\substack{+1.52\\-1.24}$ & 13.340 \\
-ID999 & $6.95\substack{+1.54\\-1.26}$  & $75187.9\substack{+16646.8\\-13629.2}$  & $3.40\substack{+0.75\\-0.62}$ & 9.437 \\
-ID1000 & $6.53\substack{+1.45\\-1.18}$  & $27801.3\substack{+6155.3\\-5039.5}$  & $9.79\substack{+2.17\\-1.77}$ & 8.390 \\
+ID991 & $29.40\substack{+6.51\\-5.33}$  & $40765.1\substack{+9025.5\\-7389.5}$  & $29.79\substack{+6.59\\-5.40}$ & 28.134 \\
+ID992 & $6.41\substack{+1.42\\-1.16}$  & $16026.7\substack{+3548.4\\-2905.2}$  & $4.54\substack{+1.01\\-0.82}$ & 17.550 \\
+ID993 & $10.27\substack{+2.27\\-1.86}$  & $33207.9\substack{+7352.3\\-6019.6}$  & $8.57\substack{+1.90\\-1.55}$ & 8.037 \\
+ID994 & $21.26\substack{+4.71\\-3.85}$  & $56088.6\substack{+12418.2\\-10167.1}$  & $16.01\substack{+3.54\\-2.90}$ & 19.871 \\
+ID995 & $14.35\substack{+3.18\\-2.60}$  & $29022.0\substack{+6425.6\\-5260.8}$  & $13.50\substack{+2.99\\-2.45}$ & 14.230 \\
+ID996 & $22.50\substack{+4.98\\-4.08}$  & $49038.7\substack{+10857.3\\-8889.2}$  & $18.48\substack{+4.09\\-3.35}$ & 11.636 \\
+ID997 & $5.42\substack{+1.20\\-0.98}$  & $23537.5\substack{+5211.3\\-4266.6}$  & $4.54\substack{+1.01\\-0.82}$ & 12.562 \\
+ID998 & $25.07\substack{+5.55\\-4.55}$  & $19555.4\substack{+4329.6\\-3544.8}$  & $18.81\substack{+4.16\\-3.41}$ & 17.846 \\
+ID999 & $5.70\substack{+1.26\\-1.03}$  & $24024.9\substack{+5319.2\\-4355.0}$  & $3.61\substack{+0.80\\-0.65}$ & 23.020 \\
+ID1000 & $39.23\substack{+8.69\\-7.11}$  & $31835.1\substack{+7048.4\\-5770.7}$  & $22.31\substack{+4.94\\-4.04}$ & 15.884 \\
 %... & $...$ & ... & ... \\
@@
 \tablecomments{The catalog of simulated thousand BBH inspiral events is used to test the inference of the BHMF from the data attainable in forthcoming next generation GW detector -- the ET.
-The reported values are the medians, with errors corresponding to the 16th and 84th percentiles.
-}
+The reported values are the medians, with errors corresponding to the 16th and 84th percentiles, assuming $\alpha=1.6$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~50M_{\odot}$.
+Note that this mock data is re-simulated every time in each realization}.
 \end{deluxetable}
@@
  \end{equation}
- \textbf{where $m_{1,i}$ is the primary mass inferred from the $i$~-~$th$ GW event.}
+ where $m_{1,i}$ is the primary mass inferred from the $i$~-~$th$ GW event.
 However, the median values of simulated \mone, as shown in Table~\ref{tab_GW_mock_data}, actually deviate from the initial power-law distribution.
@@
 The intrinsic value of primary BH mass (i.e., $m_{1,fid}$) follows a power-law distribution, however the measured  \mone\ is scattered by the Log-Normal distribution which does not follow a power-law function anymore \citep{Koen2009}.
-In theory, if the event $X$ follows a power-law distribution and its observed values are subject to the Gaussian uncertainty, then $X + e$ is distributed according to the convolution of the power-law and Gaussian distributions.
-Likewise, given that the noised data follow the Log-Normal distribution, the intrinsic power-law should be convolved with it and enter the likelihood as:
+In theory, if the event $X$ follows a power-law distribution and its observed values are subject to the {\bf Log-Normal} uncertainty, then {\bf the observed event $X + e$ (where $e$ denote the error)} is distributed according to the convolution of the power-law and {\bf Log-Normal distributions.
+Assuming that the noised data follow the Log-Normal distribution, we convolved the intrinsic power-law to describe likelihood as:}
  \begin{equation} \label{equ_lik_conv}
- P(\alpha, M_{max}, M_{min}{\bf |m_{1}}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min}),
+ P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min}),
  \end{equation}
@@
 The GW observations have a tendency to discover more significant events, known as Malmquist bias.
-\blue{For example, the} GW systems with higher values \mone\ \blue{trend to} produce stronger signals and thus have a higher probability to be detected.
-\blue{As a result, the final BHMFs would be biased to the high mass end, if this effect is not correctly taken into account}.
+For example, the GW systems with higher values \mone\ tend to produce stronger signals and thus have a higher probability to be detected.
+As a result, the final BHMFs would be biased to the high mass end, if this effect is not correctly taken into account.
 
@@
 In other words, four equivalent events would have been missed.
-Thus, for this event, one needs to re-calibrate \blue{this influence by enhancing the likelihood by a power of 5 (i.e., $L^{1/0.2} = L^5$) to recover the possibility to its intrinsic value.
-Hence, to account for the selection effect, we calculate the likelihood as:}
+Thus, for this event, one needs to re-calibrate this influence by enhancing the likelihood by a power of 5 (i.e., $L^{1/0.2} = L^5$) to recover the intrinsic probability value.
+Hence, to account for the selection effect, we calculate the likelihood as:
  \begin{equation} \label{equ_lik_sf}
- P(\alpha, M_{max}, M_{min}{\bf |m_{1}}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta},
+ P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta},
  \end{equation}
@@
 $\eta = P(\rho>8)$.
-In order to \blue{adopt the Equation~(\ref{SNR}) to derive the $\rho$}, the distribution function of $\Theta$ is \blue{taken} from the MC simulations; the \cmass\ and \dl\ are \blue{adopted from} the mock dataset as demonstrated in Table~\ref{tab_GW_mock_data}.
+In order to use the Equation~(\ref{SNR}) to calculate $\rho$, the distribution function of $\Theta$ is taken from the MC simulations; the \cmass\ and \dl\ are adopted from the mock dataset as demonstrated in Table~\ref{tab_GW_mock_data}.
 Yet, the redshift $z_s$ is the unknown parameter since it is non-measurable in the GW detectors; one can only take the \dl\ as redshift estimator.
-\blue{Note that the observed \dl\ and \cmass\ are both considered to have random noise which follows the asymmetric distribution (i.e., Log-Normal).
-Thus, the distribution of their product $\eta$ is also asymmetric.
+Note that the observed \dl\ and \cmass\ are both considered to have random noise which follows the asymmetric distribution (i.e., Log-Normal).
+Thus, the {\bf possibility distribution} of their product $\eta$ is also asymmetric.
 Considering the random distributions of the \dl\ and \cmass, we performed the numerical tests and found that the distribution of $1/\eta$ could be well described by the Log-Normal distribution with multiplicative standard deviation as $\sigma=-log(\eta_{\rm median})/3$, see Figure~\ref{fig_eta}.
-Note that in a Log-Normal distribution, the expected value are higher than the true value (i.e., median value) by a factor of $e^{\sigma^2/2}$.
-We consider this skewness and recalibrate the inferred expected value of $1/\eta$ into the median value, in order to assign a non-biased $1/\eta$ to the calculation.
-}
+Let us remind that in a Log-Normal distribution, the expected value is higher than the true value (i.e., median value) by a factor of $e^{\sigma^2/2}$.
+We consider this skewness and recalibrate the inferred expected value of $1/\eta$ to the median value, in order to assign a non-biased $1/\eta$ to the calculation.
 
@@
 \caption{
-\blue{
-Assuming a set of \dl\ and \cmass\ as Log-Normal distribution, we randomly produce the the corresponding histogram of the $1/\eta$ distribution.
+Assuming a set of \dl\ and \cmass\ following the Log-Normal distribution, we randomly produce the corresponding histogram of the $1/\eta$ {\bf to access its possibility distribution}.
 The result shows that the skewed distribution could be well described by a Log-Normal distribution with $\sigma = -\log(\eta_{\rm median})/3$.
-}
 }
@@
 In the previous section, we take \dl\ as the redshift estimator to derive the redshift and hence selection factor $\eta$.
-The way to derive the \textbf{inferred redshift $z_{inf}$} is an inverse solution of integral function when knowing the \dl$(z)$ and fixing the cosmological model.
+The way to derive the inferred redshift {\bf $z_{inf}$ is to take the obtained luminosity distance, i.e.,  \dl$(z)$, and derive the inverse solution of integral function based on a fixed cosmological model.}
 
@@
  \begin{split}
- P&(\alpha_0, \alpha_1, M_{max}, M_{min}{\bf |m_{1},d_L(z)}) \propto \\
+ P&(\alpha_0, \alpha_1, M_{max}, M_{min}|m_{1},d_L(z)) \propto \\
   &\prod_{i=1}^{total} \hat{P}(m_{1i}, z_{inf,i} |\alpha_0, \alpha_1, M_{max}, M_{min})^{1/\eta}.
@@
 In each realization, we simulate a thousand of BBH inspiral GW events and infer the best-fit parameters using minimization of the chi-square objective function.
-\blue{We keep increasing the volume of realizations until the inferred best-fit parameters converged.}
+We keep increasing the volume of realizations until the inferred best-fit parameters converged.
 
 In the first scenario, we consider the slope $\alpha$ as a constant.
-\blue{ We performed numerical tests assuming three different sets of parameters taking $\alpha$ as 0.8, 1.6 and 2.4, with $M_{min}~=~5M_{\odot}$, $M_{max}~=~50M_{\odot}$.
+We performed numerical tests assuming three different sets of parameters taking $\alpha$ as 0.8, 1.6 and 2.4, with $M_{min}~=~5M_{\odot}$, $M_{max}~=~50M_{\odot}$.
 We calculate the likelihood by Equation~(\ref{equ_lik_sf}) to infer the best-fit parameters in each realization.
@@
 We find that all the parameters are recovered accurately which confirms the validity of our method.
-The uncertainties for the inferred parameters are $\Delta\alpha\sim0.1$, $\Delta M_{max}\sim1-2M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$.
-Note that these uncertainty levels are not ready to be treated as a universal for the general case, but only apply when the initial parameter sets are close to the tested ones.
-Moreover, these uncertainty levels are related to the standard deviation of the measurements including ${\cal M}_0$, \dl, and \mone, as discussed in Section~\ref{sec_noiselevel}.
-}
+The uncertainties for the inferred parameters of 68\% confidence interval are $\Delta\alpha\sim0.1$, $\Delta M_{max}\sim1-3M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$.
+We also note that the uncertainty for $\Delta M_{max}$ increases with the increasing of $\alpha$.
+This is reasonable given that for higher $\alpha$ value, the black mass (i.e., $m_1$) trends to be distributed lower, resulting in a lower constraint power on the high mass end.
+Clearly, the uncertainty levels cannot be treated as the universal range for the general case, but only apply when the set of the initial parameters is close to the tested ones.
+Moreover, these uncertainty levels are related to the assumed measurement uncertainties, including ${\cal M}_0$, \dl, and \mone, as discussed in Section~\ref{sec_noiselevel}.
 
@@
 \begin{tabular}{c c c}
-\subfloat[\blue{assuming $\alpha=0.8$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
+\subfloat[assuming $\alpha=0.8$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.]
 {\includegraphics[width=0.3\linewidth]{3para_contour_a0_08.pdf}}&
-\subfloat[\blue{assuming $\alpha=1.6$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
+\subfloat[assuming $\alpha=1.6$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.]
 {\includegraphics[width=0.3\linewidth]{3para_contour_a0_16.pdf}}&
-\subfloat[\blue{assuming $\alpha=2.4$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
+\subfloat[assuming $\alpha=2.4$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.]
 {\includegraphics[width=0.3\linewidth]{3para_contour_a0_24.pdf}}
@@
 \caption{
-One- and two-dimensional distributions for the best-fitted parameters in the \blue{first scenario, based on three sets of parameters with a thousand of BBH inspiral GW events}.
+One- and two-dimensional distributions for the best-fitted parameters in the first scenario, based on three sets of parameters with a thousand of BBH inspiral GW events.
 The BHMF is assumed as a power-law with hard cut at the $M_{min}$ and $M_{max}$, with a constant slope ($\alpha$) across all the redshifts.
@@
 In the second scenario, the $\alpha$ evolves with redshift according to the Equation~(\ref{equ_alphaz}).
-\blue{We consider four sets of parameters assuming $\alpha_0$ as  0.8, 1.6, 2.4 and $\alpha_1$ including 0.7 and 1.2.
-We present the results in Figure~\ref{fig_result_b} and find that all the assumed parameters could be recovered accurately.
-With one more parameters included in the second scenario, the uncertainty level are extended as \ding{The following values still need to confirm} $\Delta\alpha_0\sim0.4$, $\Delta\alpha_1\sim0.5-0.7$, $\Delta M_{max}\sim2-4M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$.
-We note that there is a degeneracy between the $\alpha_0$ and $\alpha_1$, which is understandable given that they are strongly connected by the Equation~\ref{equ_alphaz}.
-However, for the four sets of parameters we tested, this degeneracy does not affect the inferred uncertainty level for the $\alpha_0$ and $\alpha_1$.
-}
+We consider four sets of parameters assuming $\alpha_0$ as  0.8, 1.6, 2.4 and $\alpha_1$ including 0.7 and 1.2.
+We present the results in Figure~\ref{fig_result_b}.
+One can see that all the assumed parameters could be recovered accurately.
+With one more parameter included in the second scenario, the uncertainty level are the following: $\Delta\alpha_0\sim0.4$, $\Delta\alpha_1\sim0.5-0.7$, $\Delta M_{max}\sim2-4M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$.
+We note that there is a degeneracy between the $\alpha_0$ and $\alpha_1$, which is understandable given that they are strongly related by the Equation~\ref{equ_alphaz}.
+However, for the four sets of parameters we tested, this degeneracy does not affect the inferred uncertainty level for $\alpha_0$ and $\alpha_1$.
 
-We highlight that in this \blue{second} scenario, it is the inferred uncertainty of $\alpha_1$ that matters the most.
-\blue{Our result show that, with only one thousand of GW measurements in the future, the inferred value of $\alpha_1$ would reach to precision of $\Delta\alpha_1\sim0.5-0.7$.
-Limited by the computing power, we couldn't use numerical test to get a universal uncertainty level as for the general case.
-However, given the fours sets of tests as shown the Figure~\ref{fig_result_b}, it is likely to be true that one thousand of GW measurement could distinguish the evolution of BHMF at 1-$\sigma$ confidence level when $\alpha_1$ is deviated from 0 by a value of 0.5.
+We highlight that in this second scenario, it is the inferred uncertainty of $\alpha_1$ that matters the most.
+Our result show that, with only one thousand of GW measurements in the future, the inferred value of $\alpha_1$ would reach to precision of $\Delta\alpha_1\sim0.5-0.7$.
+Limited by the computing power, we couldn't use numerical test to get a universal uncertainty level for the general case.
+However, given the four sets of tests as shown the Figure~\ref{fig_result_b}, it is likely to be true that one thousand of GW measurement could distinguish the evolution of BHMF at 1-$\sigma$ confidence level when $\alpha_1$ deviated from 0 by a value of 0.5.
 Moreover, we conjecture that the precision of inference is increasing with the sample size as a function of $\sqrt{N}$.
-Thus, for the four sets of tests, the one year measurements of ET ($\sim10^5$ in total) would increase the uncertainty levels by a factor of 10.}
+Thus, for the four sets of tests, the one year measurements of ET ($\sim10^5$ in total) would decrease the uncertainty levels by a factor of 10.
 We also note that the distribution of the best-fitted parameters ($\alpha_0$, $\alpha_1$) does not follow the Gaussian distribution, but rather a large fraction of it is concentrated at the center.
@@
 \begin{tabular}{c c}
-\subfloat[\blue{assuming $\alpha_0=0.8$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
+\subfloat[assuming $\alpha_0=0.8$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.]
 {\includegraphics[width=0.4\linewidth]{4para_contour_a0_08_a1_07.pdf}}&
-\subfloat[\blue{assuming $\alpha_0=1.6$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
+\subfloat[assuming $\alpha_0=1.6$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.]
 {\includegraphics[width=0.4\linewidth]{4para_contour_a0_16_a1_07.pdf}}\\
-\subfloat[\blue{assuming $\alpha_0=2.4$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
+\subfloat[assuming $\alpha_0=2.4$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.]
 {\includegraphics[width=0.4\linewidth]{4para_contour_a0_24_a1_07.pdf}}&
-\subfloat[\blue{assuming $\alpha_0=1.6$, $\alpha_1=1.2$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
+\subfloat[assuming $\alpha_0=1.6$, $\alpha_1=1.2$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.]
 {\includegraphics[width=0.4\linewidth]{4para_contour_a0_16_a1_12.pdf}}
@@
 \caption{
-\blue{Same} as Figure~\ref{fig_result_a} but for the second scenario, where the $\alpha$ of BHMF is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$\blue{, four sets of parameters assumed.}
+Same as Figure~\ref{fig_result_a} but for the second scenario, where the $\alpha$ of BHMF is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$, four sets of parameters assumed.
 }
@@
 The third-generation gravitational wave detector, the Einstein Telescope, is very powerful and capable of detecting $\sim10^5$ GW events per year, with redshift up to $z\sim17$.
-In this study, we investigated how the detections of the BBH mergers could improve our knowledge of the black hole mass function \blue{(BHMF)}.
+In this study, we investigated how the detections of the BBH mergers could improve our knowledge of the black hole mass function (BHMF).
 
 We performed the Monte Carlo simulation to estimate the uncertainty level of BHMF parameters inferred from GW signals by BBHs that would be detected by ET.
-As a starting point, we assumed that the BHMF for the primary BH mass followed a power-law distribution \blue{with a hard cuts as Equation~(\ref{equ_powlaw})}.
+As a starting point, we assumed that the BHMF for the primary BH mass followed a power-law distribution with hard cuts as described by Equation~(\ref{equ_powlaw}).
 Based on the BBH intrinsic merger rate predicted by {\tt StarTrack}, we randomly simulated the key parameters of the BBH systems, including the chirp masses, redshifts and orientation factors and calculated  their corresponding signal-to-noise ratio \snr\ for the ET.
@@
 We took into account the measurement uncertainties and the selection effect which would bias the inference.
-We \blue{performed the test using realizations, one thousand GW events per realization}, and estimated the distribution of the best-fitted parameters of the BHMF, including the power-law slope $\alpha$, the maximum BH mass $M_{max}$ and the minimum BH mass $M_{min}$ \blue{in the first scenario}.
-Furthermore, \blue{in the second scenario, we consider the $\alpha$ evolves as a function of redshift and used the luminosity distance as redshift estimator to test the evolution}.
+We performed the test using realizations, one thousand GW events adopted per realization, and estimated the distribution of the best-fitted parameters of the BHMF, including the power-law slope $\alpha$, the maximum BH mass $M_{max}$ and the minimum BH mass $M_{min}$ in the first scenario.
+Furthermore, in the second scenario, we considered  $\alpha$ evolving as a function of redshift as described by Equation~(\ref{equ_alphaz}), and used the luminosity distance as redshift estimator to test this evolution.
 We summarize our main results as follows:
-\blue{
 \begin{enumerate}
-\item Using our method based on Equation~(\ref{equ_lik_sf}), all the tested parameters are all recovered accurately, which confirms the validity of our tests and highlights the importance of correctly considering the measurement uncertainty and selection effect.
-\item Taking the measured \dl\ as redshift estimator, we tested to recover the $\alpha$ with a scenario which is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
-Testing with four parameters sets, we are able to successfully recovered the true value of $\alpha_1$ accurately.
+\item Using our method based on Equation~(\ref{equ_lik_sf}), the tested parameters are all recovered accurately, as shown in Figure~\ref{fig_result_a}, which confirms the validity of our tests and highlights the importance of correctly considering the measurement uncertainty and selection effect.
+\item We assumed $\alpha$ within a scenario in which it is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
+Taking the measured \dl\ as redshift estimator and testing with four parameter sets, we are able to recover the true value of $\alpha_1$ accurately, as shown in Figure~\ref{fig_result_b}.
 \item Given the fixed sets of parameters, our results show that a volume of one thousand measurements of BBHs events could infer the parameters with uncertainties level at $\Delta\alpha\sim0.1$, $\Delta M_{max}\sim1-2M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$ for the first scenario.
 For the second scenario, the inferred uncertainties are $\Delta\alpha_0\sim0.4$, $\Delta\alpha_1\sim0.5-0.7$, $\Delta M_{max}\sim2-4M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$.
-In the future, the one year detection rate of ET ($\sim10^5$ in total) increase the sample size by a factor of 100.
-According to the fact that the precision of the inference increases with the sample size, as a function of $\sqrt{N}$, we conclude that one year BBH sample by ET would be able to deliver the parameters at higher uncertainty improved by a factor of 10 as tested.
+In the future, the one year detection rate of ET ($\sim10^5$ in total) would increase the sample size by a factor of 100.
+According to the fact that the precision of the inference increases with the sample size, as a function of $\sqrt{N}$, we conclude that one year BBH sample by ET would be able to deliver the parameters with uncertainties reduced by a factor of 10 with respect to these reported in this paper.
 \end{enumerate}
-}
 
@@
 First, we have adopted a template of intrinsic BBH merger rate based on the predictions by a standard model in {\tt StarTrack}, which can be different from the realistic one.
-Of course, the intrinsic BBH merger rate is unknown yet, which is related to
-lack of detailed knowledge of different elements such as BBH masses, explosion mechanism, the metallicity history and the time delay distribution.
-Also, for the sake of simplicity, we simulated the value of the secondary BH mass \mtwo\ by assuming that two masses of BBHs have independent distributions, which probably is not exactly true.
-However, one can expect that these limitations would more strongly affect the prediction of the yearly detection rate of the GW events and their redshift distribution, rather than the inference of the parameters in the BHMF.
-\blue{Last, the numerical tests as done in this works confirms the validity of our method.
-However, limited by the sets of tests, the inferred uncertainty for both scenario applies for the fixed sets of parameters which shouldn't be considered as a general value.}
+Of course, the intrinsic BBH merger rate is unknown yet, which is related to lack of detailed knowledge of different elements such as BBH masses, explosion mechanism, the metallicity history and the time delay distribution.
+{\bf With a different template of BBH merger rate, the simulated mock events (i.e., the ones in the Table~\ref{tab_GW_mock_data}) would follows a different redshift distribution, which could slightly change the inference of the uncertainties of the inferred parameters.
+Second}, for the sake of simplicity, we simulated the value of the secondary BH mass \mtwo\ by assuming that two masses of BBHs have independent distributions, which probably is not exactly true.
+{\bf One can expect that these two limitations would affect the prediction of the yearly detection rate of the GW events and their redshift distribution; however, their influence on our final inferred contours of BHMF (i.e., Figure~\ref{fig_result_a} and~\ref{fig_result_b}) is very limited.}
+At last, the numerical tests done in this work confirmed the validity of our method.
+However, limited by the sets of tests, the uncertainty of inferred parameters  in both scenarios applies directly to the fixed sets of parameters and shouldn't be applied to the general case.
 
@@
 For example, one could infer the spin of BH \citep{Abbott2018b}, the mass function for the binary of NS-NS, NS-BH system, though these events are detectable at lower redshift ($z<4$).
-In addition, using the luminosity as redshift estimator, one should also be able to reconstruct the BBH intrinsic merger rate \citep{Fishbach2018}, the cosmological parameter.
+In addition, using the luminosity as redshift estimator, one should also be able to reconstruct the BBH intrinsic merger rate \citep{Fishbach2018}, and the cosmological parameters.
 
@@
 M.B. was supported by the Key Foreign Expert Program for the Central Universities No. X2018002.
-K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. {\bf 11973034}..
+K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. 11973034.
 \software{  {\sc corner}, \citep{corner},

### 2020-01-17 GW_BH_function/create_figure2_eta_test.py

@@ -1,0 +1,128 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Aug 20 10:10:46 2019
+
+@author: Dartoon
+
+Test the distribution of 
+"""
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import glob
+from BH_mass_function import gene_BHBH, dl, solve_z
+import time
+import pickle
+
+from cal_likelihood import poss_ln_gaussian
+
+solve_z = np.vectorize(solve_z)
+#a0, a1, mbh_max, mbh_min = 2.35, 0.1, 80., 5.
+a0, a1, mbh_max, mbh_min = 2.4, 0.7, 50., 5.   #mode1
+
+seed = 2
+#filename = 'test3_seed{0}_data'.format(seed)
+filename = 'sim_a0_{0}_a1_{1}_max_{2}'.format(a0, a1, mbh_max)
+if_file = glob.glob(filename)  
+if if_file==[]:
+    np.random.seed(seed)
+    test = gene_BHBH(h0=70)
+    event_rate, zs_detected, masses, rhos_detected = test.mc_year_rate(a=[a0, a1], mbh_max=mbh_max, mbh_min=mbh_min, ev_type = 'mode1')
+    dl_zs = dl(zs_detected)
+    sim_data = [event_rate, zs_detected, masses, rhos_detected, dl_zs]
+    pickle.dump(sim_data, open(filename, 'wb'))
+else:
+    event_rate, zs_detected, masses, rhos_detected, dl_zs=pickle.load(open(filename,'rb'))
+
+np.random.seed(seed)
+#event_rate0, zs_detected0, masses0, rhos_detected0 = test.mc_year_rate(a=a, mbh_max=mbh_max, mbh_min=mbh_min, ev_type = 'const')
+#event_rate1, zs_detected1, masses1, rhos_detected1 = test.mc_year_rate(a=[2.35,0.1], mbh_max=mbh_max, mbh_min=mbh_min, ev_type = 'mode0')
+#event_rate2, zs_detected2, masses2, rhos_detected2 = test.mc_year_rate(a=[a0, a1], mbh_max=mbh_max, mbh_min=mbh_min, ev_type = 'mode1')
+
[…]

### 2020-01-17 GW_BH_function/eta_test.py

@@ -1,128 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Aug 20 10:10:46 2019
-
-@author: Dartoon
-
-Test the distribution of 
-"""
-import numpy as np
-import astropy.io.fits as pyfits
-import matplotlib.pyplot as plt
-
-import numpy as np
-import astropy.io.fits as pyfits
-import matplotlib.pyplot as plt
-import glob
-from BH_mass_function import gene_BHBH, dl, solve_z
-import time
-import pickle
-
-from cal_likelihood import poss_ln_gaussian
-
-solve_z = np.vectorize(solve_z)
-#a0, a1, mbh_max, mbh_min = 2.35, 0.1, 80., 5.
-a0, a1, mbh_max, mbh_min = 2.4, 0.7, 50., 5.   #mode1
-
-seed = 2
-#filename = 'test3_seed{0}_data'.format(seed)
-filename = 'sim_a0_{0}_a1_{1}_max_{2}'.format(a0, a1, mbh_max)
-if_file = glob.glob(filename)  
-if if_file==[]:
-    np.random.seed(seed)
-    test = gene_BHBH(h0=70)
-    event_rate, zs_detected, masses, rhos_detected = test.mc_year_rate(a=[a0, a1], mbh_max=mbh_max, mbh_min=mbh_min, ev_type = 'mode1')
-    dl_zs = dl(zs_detected)
-    sim_data = [event_rate, zs_detected, masses, rhos_detected, dl_zs]
-    pickle.dump(sim_data, open(filename, 'wb'))
-else:
-    event_rate, zs_detected, masses, rhos_detected, dl_zs=pickle.load(open(filename,'rb'))
-
-np.random.seed(seed)
-#event_rate0, zs_detected0, masses0, rhos_detected0 = test.mc_year_rate(a=a, mbh_max=mbh_max, mbh_min=mbh_min, ev_type = 'const')
-#event_rate1, zs_detected1, masses1, rhos_detected1 = test.mc_year_rate(a=[2.35,0.1], mbh_max=mbh_max, mbh_min=mbh_min, ev_type = 'mode0')
-#event_rate2, zs_detected2, masses2, rhos_detected2 = test.mc_year_rate(a=[a0, a1], mbh_max=mbh_max, mbh_min=mbh_min, ev_type = 'mode1')
-
[…]

### 2020-01-17 GW_BH_function/for_Kai_create_mock_GW.py

@@ -33,9 +33,12 @@ import time
 
 a, mbh_max, mbh_min = 2.35, 80., 5.
 
+event_rate_list = []
+zs_all_list = []
 #%%
-test = gene_BHBH(h0=70, rho0=0, m_type = 'BHBH', scenario=2)
-event_rate, zs_detected, masses, rhos_detected = test.mc_year_rate(a=a, mbh_max=mbh_max, mbh_min=mbh_min, itera=1)
+sce = 2
+test = gene_BHBH(h0=70, rho0=0, m_type = 'BHBH', scenario=sce)
+event_rate, zs_detected, masses, rhos_detected = test.mc_year_rate(a=a, mbh_max=mbh_max, mbh_min=mbh_min, itera=5)
 zs_all, chirp_mass_all, m1_all, m2_all = zs_detected, masses[:,0], masses[:,1], masses[:,2]                                                      
 index = np.arange(len(m1_all))
 idx = random.sample(index, 5000)
@@ -43,100 +46,140 @@ m1 = m1_all[idx]
 m2 = m2_all[idx]
 rho = rhos_detected[idx]
 zs = zs_all[idx]
-save_filename = 'simulated_{0}_low_end.txt'.format(test.m_type)
-save_file =  open(save_filename,'w') 
-save_file.write("#zs, m1, m2, SNR, total_rate = {0:.3f} \n".format(event_rate)) 
-for i in range(len(zs)):
-    save_file.write("{0:.3f} {1:.3f} {2:.3f} {3:.3f}\n".format(zs[i],m1[i],m2[i], rho[i])) 
-save_file.close() 
-print  'simulated_{0}_low_end.txt'.format(test.m_type), event_rate
+#save_filename = 'simulated_{0}_low_end.txt'.format(test.m_type)
+#save_file =  open(save_filename,'w') 
+#save_file.write("#zs, m1, m2, SNR, total_rate = {0:.3f} \n".format(event_rate)) 
+#for i in range(len(zs)):
+#    save_file.write("{0:.3f} {1:.3f} {2:.3f} {3:.3f}\n".format(zs[i],m1[i],m2[i], rho[i])) 
+#save_file.close() 
+#print  'simulated_{0}_low_end.txt'.format(test.m_type), event_rate
+zs_all_list.append(zs_all)
+event_rate_list.append(event_rate)
+#%%
+sce = 1
+test = gene_BHBH(h0=70, rho0=0, m_type = 'BHBH', scenario=sce)
[…]

### 2020-01-17 decomp_example/HST_AGN_decomp_temp/sample2/0_analysis.py

@@ -1,0 +1,137 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Thu May 23 16:58:39 2019
+
+@author: Dartoon
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import glob
+#from gen_fit_id import gen_fit_id
+from photutils import make_source_mask
+import os
+#plt.ion()
+
+import sys
+sys.path.insert(0,'../../../py_tools/')
+from fit_qso import fit_qso
+from transfer_to_result import transfer_to_result, transfer_obj_to_result
+from mask_objects import detect_obj
+from flux_profile import profiles_compare, flux_profile
+from matplotlib.colors import LogNorm
+
+#Setting the fitting condition:
+deep_seed = False  #Set as True to put more seed and steps to fit.
+pltshow = 1 #Note that setting plt.ion() in line27, the plot won't show anymore if running in terminal.
+pix_scale = 0.0642 
+fixcenter = False
+run_MCMC = True
+zp=26.4524
+
+psf, QSO_img, QSO_std = pyfits.getdata('psf_77.fits'),  pyfits.getdata('CID1174_cutout.fits'),  pyfits.getdata('wht_err.fits')
+
+frame_size = 61
+#frame = '{0}'.format(frame_size)
+QSO_fm = len(QSO_img)
+ct = (QSO_fm-frame_size)/2     # If want to cut to 61, i.e. (121-61)/2=30
+
+QSO_img = QSO_img[ct:-ct,ct:-ct]
+QSO_std = QSO_std[ct:-ct,ct:-ct]
+psf = psf[ct:-ct,ct:-ct]
+#%%
+#==============================================================================
+# input the objects components and parameteres
+#==============================================================================
+objs, Q_index = detect_obj(QSO_img,pltshow = pltshow)
+qso_info = objs[Q_index]
+obj = [objs[i] for i in range(len(objs)) if i != Q_index]
+fixed_source = []
+kwargs_source_init = []
+kwargs_source_sigma = []
+kwargs_lower_source = []
+kwargs_upper_source = []
+fixed_source.append({})  
+kwargs_source_init.append({'R_sersic': 0.3, 'n_sersic': 2., 'e1': 0., 'e2': 0., 'center_x': 0., 'center_y': 0.})
[…]

### 2020-01-17 decomp_example/HST_AGN_decomp_temp/sample3/1_read_result.py

@@ -12,7 +12,7 @@ import corner
 import astropy.io.fits as pyfits
 
 import sys
-sys.path.insert(0,'../../py_tools/')
+sys.path.insert(0,'../../../py_tools/')
 
 picklename = 'example.pkl'
 result = pickle.load(open(picklename,'rb'))
@@ -82,8 +82,16 @@ plt.show()
 #%% Plot the image again:
 pix_scale = 0.0642 
 from flux_profile import total_compare
-psf, agn_image, error_map = pyfits.getdata('PSF.fits'),  pyfits.getdata('QSO_im.fits'),  pyfits.getdata('QSO_err.fits')
+psf, QSO_img, QSO_std = pyfits.getdata('psf_16.fits'),  pyfits.getdata('CID454_cutout.fits'),  pyfits.getdata('wht_err.fits')
 
+frame_size = 61
+#frame = '{0}'.format(frame_size)
+QSO_fm = len(QSO_img)
+ct = (QSO_fm-frame_size)/2     # If want to cut to 61, i.e. (121-61)/2=30
+
+QSO_img = QSO_img[ct:-ct,ct:-ct]
+QSO_std = QSO_std[ct:-ct,ct:-ct]
+psf = psf[ct:-ct,ct:-ct]   
 if len(image_host) == 1:
     host = image_host[0]
     label = ['data', 'QSO', 'host', 'model', 'normalized residual']
@@ -93,9 +101,13 @@ elif len(image_host) >1:
         host += image_host[i]
     label = ['data', 'QSO', 'host as {0} components'.format(i+1), 'model', 'normalized residual']  #Print the numbers of objects
 #error_map = err_map[ct:-ct,ct:-ct]
-flux_list = [agn_image, image_ps, host, error_map]
+flux_list = [QSO_img, image_ps, host, QSO_std]
 
 total_compare(label_list = label, flux_list = flux_list, target_ID = 'example', pix_sz=pix_scale, zp = zp,
-                    plot_compare = False, msk_image = np.ones_like(agn_image))
+                    plot_compare = False, msk_image = np.ones_like(QSO_img))
 
 #fig.savefig("{0}_SB_profile.pdf".format(name_save), bbox_inches = 'tight')
+from transfer_to_result import transfer_to_result
+result = transfer_to_result(data=QSO_img, pix_sz = pix_scale,
+                            source_result=source_result, ps_result=ps_result, image_ps=image_ps, image_host=image_host, error_map=QSO_std,
[…]

### 2020-01-17 for_collbrate/Vardha_Seyfert1/2_read_results.py

@@ -13,8 +13,10 @@ import astropy.io.fits as pyfits
 from matplotlib.colors import LogNorm
 import copy
 
-ID = 'l106'
-picklename = ID+'_fitting.pkl'
+#ID = 'l106'
+#picklename = ID+'_fitting.pkl'
+picklename = 'result_vardha/'+ 'l24_sersicdisk.pkl'
+
 result = pickle.load(open(picklename,'rb'))
 [best_fit,pso_fit,mcmc_fit, trans_paras] = result
 
@@ -23,34 +25,38 @@ chain_list, param_list, _ = pso_fit
 samples_mcmc, param_mcmc, dist_mcmc, _ = mcmc_fit
 _, _, mcmc_new_list, labels_new, _ = trans_paras
 
+plot = corner.corner(samples_mcmc, labels=param_mcmc, show_titles=True)
+plt.show()
+
 print "best-fit source_result:", source_result
 print "best-fit ps_result:", ps_result
 pix_sz = 0.04
 
-#%%Replot the profiles
-import sys
-sys.path.insert(0,'./fitting_tools/')
-from flux_profile import total_compare
-zp = 25.0985
-
-flux_hdulist = pyfits.open(ID+'_flux_list.fits')  # includes [agn_image,image_ps, extended_source, error_map, QSO_msk]
-flux_list = [flux_hdulist[i].data for i in range(4)]
-QSO_msk = flux_hdulist[4].data
-label = ['data', 'QSO', 'extended sources', 'model', 'normalized residual']
-fig = total_compare(label_list = label, flux_list = flux_list, target_ID = ID, pix_sz=pix_sz, zp = zp,
-                    plot_compare = False, msk_image = QSO_msk)
-plt.show()
-
-print "plot individual frame:"
-plt.imshow(flux_list[0] - flux_list[1], norm=LogNorm(),origin='low')
-plt.colorbar()
-frame_size = len(flux_list[0])
-plt.text(frame_size*0.05, frame_size*0.9, 'data - Point Source', weight='bold',
-         fontsize=17, color='white')
-plt.show()
+##%%Replot the profiles
+#import sys
+#sys.path.insert(0,'./fitting_tools/')
+#from flux_profile import total_compare
+#zp = 25.0985
+#
+#flux_hdulist = pyfits.open(ID+'_flux_list.fits')  # includes [agn_image,image_ps, extended_source, error_map, QSO_msk]
[…]

### 2020-01-17 for_collbrate/Vardha_Seyfert1/2_test_corner.py

@@ -10,7 +10,8 @@ import matplotlib.pyplot as plt
 import pickle
 import corner
 
-picklename = 'dump_fitting.pkl' 
+#picklename = 'dump_fitting.pkl' 
+picklename = 'result_vardha/'+ 'l24_sersic.pkl'
 result = pickle.load(open(picklename,'rb'))
 [source_result, image_host, ps_result, image_ps, samples_mcmc, param_mcmc, paras] = result
 

### 2020-01-17 projects/Rebuttal_paper_simple_fit_mocks/calculate_ave_H0.py

@@ -1,68 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Fri Dec 13 22:58:18 2019
-
-@author: Dartoon
-"""
-import numpy as np
-import astropy.io.fits as pyfits
-import matplotlib.pyplot as plt
-
-H0_SIE = [[68.236, 4.597],
-[70.779, 5.179],
-[153.034, 4.940],
-[186.416, 6.478],
-[86.195, 1.292],
-[261.970, 9.697],
-[76.069, 3.316],
-[84.799, 4.623],
-[158.870, 4.653],
-[112.556, 4.025],
-[84.071, 1.611],
-[172.391, 4.506],
-[84.818, 4.278],
-[78.842, 4.571],
-[147.805, 4.054],
-[169.789, 5.808],
-[78.086, 1.398],
-[226.757, 7.352]]
-#H0_SIE = np.array(H0_SIE)
-
-H0_SPEMD = [[86.191, 4.139],
-[89.046, 4.172],
-[150.843, 6.505],
-[168.679, 7.399],
-[78.865, 3.457],
-[163.620, 6.077],
-[63.572, 3.519],
-[39.075, 1.378],
-[134.131, 5.052],
-[142.343, 4.589],
-[112.455, 1.897],
-[172.769, 4.449],
-[67.301, 2.992],
-[57.190, 2.293],
-[146.317, 6.295],
-[137.776, 6.762],
-[116.748, 1.591],
-[137.854, 4.185]]
-#H0_SPEMD = np.array(H0_SPEMD)
-
-for seed in range(0,6):
-    H0_s = np.array([H0_SIE[i][0] for i in range(len(H0_SIE)) if i%6 == seed])
-    H0_error = np.array([H0_SIE[i][1] for i in range(len(H0_SIE)) if i%6 == seed])
-    ave = np.sum(H0_s/H0_error**2)/np.sum(1/H0_error**2)
-    std = np.sqrt( np.sum((H0_s-ave)**2/H0_error**2) / np.sum(1/H0_error**2) )
-#    print '#',seed+1, "H0=", round(ave,3),'stdd' , round(np.std(H0_s),3)
-    print '#',seed+1, "H0=", round(ave,3),'stdd' , round(std,3)
-        
-print '\n\n'
-for seed in range(0,6):
[…]

### 2020-01-17 projects/Rebuttal_paper_simple_fit_mocks/plot_H0_hist.py

@@ -12,48 +12,57 @@ import pickle
 import matplotlib as mat
 mat.rcParams['font.family'] = 'STIXGeneral'
 
-#H0_lists = []
-#for i in range(1,7):
-#    result = pickle.load(open('Final-MCMC_4000_steps/sampler_results_SIE#{0}.pkl'.format(i),'rb'))
-#    _, trans_result = result
-#    mcmc_new_list, labels_new = trans_result
-#    H0_list = mcmc_new_list[:,-1]
-#    H0_lists.append(H0_list) 
-#pickle.dump([H0_lists], open('H0_SIE.pkl', 'wb'))         
-#H0_lists = []
-#for i in range(1,7):
-#    result = pickle.load(open('Final-MCMC_4000_steps/sampler_results_SPEMD#{0}.pkl'.format(i),'rb'))
-#    _, trans_result = result
-#    mcmc_new_list, labels_new = trans_result
-#    H0_list = mcmc_new_list[:,-1]
-#    H0_lists.append(H0_list) 
-#pickle.dump([H0_lists], open('H0_SPEMD.pkl', 'wb'))         
+#folder = 'MCsteps1000_10000_linear_False/'
+#folder = 'MCsteps[1000, 10000]_first_run_linear_True/'
+#folder = 'MCsteps1000_10000_second_run_linear_True/'
+#folder = 'MCsteps1000_10000_deflector_10mas/'
+folder = 'MCsteps1000_10000_1.3.0_non-linear_False/'
+#folder = 'MCsteps1000_10000_1.3.0_non-linear_True/'
 
+H0_lists = []
+for i in range(1,7):
+    result = pickle.load(open(folder+'sampler_results_SIE#{0}.pkl'.format(i),'rb'))
+    _, trans_result = result
+    mcmc_new_list, labels_new = trans_result
+    H0_list = mcmc_new_list[:,-1]
+    H0_lists.append(H0_list) 
+pickle.dump([H0_lists], open(folder+'H0_SIE.pkl', 'wb'))         
+H0_lists = []
+for i in range(1,7):
+    result = pickle.load(open(folder+'sampler_results_SPEMD#{0}.pkl'.format(i),'rb'))
+    _, trans_result = result
+    mcmc_new_list, labels_new = trans_result
+    H0_list = mcmc_new_list[:,-1]
[…]

### 2020-01-17 projects/Rebuttal_paper_simple_fit_mocks/simple_fit_mocks_linear_False.py

@@ -1,0 +1,336 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Dec 13 11:02:31 2019
+
+@author: Dartoon
+
+Fit the Seed 211 - 216 with a simple model
+"""
+# import the necessary python modules
+import numpy as np
+import time
+import corner
+
+from lenstronomy.LensModel.lens_model import LensModel
+from lenstronomy.LensModel.lens_model_extensions import LensModelExtensions
+from lenstronomy.LensModel.Solver.lens_equation_solver import LensEquationSolver
+from lenstronomy.Cosmo.lens_cosmo import LensCosmo
+from lenstronomy.Util import constants
+from astropy.cosmology import FlatLambdaCDM
+from  lenstronomy.Plots import lens_plot
+import glob
+import matplotlib.pyplot as plt
+import pickle
+
+def cal_Ddt(zl, zs, H0_ini=100, om=0.27):
+    cosmo = FlatLambdaCDM(H0=H0_ini, Om0=0.27) 
+    lensunits=LensCosmo(z_lens=zl, z_source=zs,cosmo= cosmo)
+    D_l=lensunits.D_d
+    D_s=lensunits.D_s
+    D_ls=lensunits.D_ds 
+    Ddt_corr = (1+zl)*D_l*D_s/D_ls
+    return Ddt_corr
+
+def cal_h0(zl, zs, Ddt, om=0.27):
+    Ddt_corr = cal_Ddt(zl, zs, H0_ini=100)
+    ratio = Ddt_corr/Ddt
+    return 100 * ratio
+
+steps = [1000, 10000]
+H0_true = 70.65595
+#noise_seed = 2
+#for fix_gamma in [True, False]:
+fix_gamma = True
+for seed in [211,212,213,214,215, 216]:
+    print "Runing seed:", seed, "fix_gamma:", fix_gamma, "MC steps:", steps
+    if seed == 211:
+        z_lens ,z_source = [0.640, 2.408]
+        ximg = [0.41530, 0.17330, 1.22509, -1.18836]  # image positions in relative RA (arc seconds)
+        yimg = [-1.19026, 1.24663, 0.14337, -0.11013]  # image positions in relative DEC (arc seconds)
+        d_dt_sigma = np.array([0.250, 0.250, 0.250])  # 1-sigma uncertainties in the time-delay measurement (in units of days)
[…]

### 2020-01-17 projects/Rebuttal_paper_simple_fit_mocks/test_burning.py

@@ -11,33 +11,48 @@ import numpy as np
 import astropy.io.fits as pyfits
 import matplotlib.pyplot as plt
 import pickle
+import matplotlib as mat
+import corner
+mat.rcParams['agg.path.chunksize'] = 10000
 
-model = 'SPEMD'
-for i in range(6,7):
-    result = pickle.load(open('Final_before_submitpaper/Final-MCMC_4000_steps/sampler_results_{1}#{0}.pkl'.format(i, model),'rb'))
+#folder = 'MCsteps1000_10000_deflector_10mas/'
+folder = 'MCsteps1000_10000_1.3.0_non-linear_False/'
+
+#model = 'SPEMD'
+model = 'SIE'
+
+for i in range(2,3):
+    result = pickle.load(open(folder+'sampler_results_{1}#{0}.pkl'.format(i, model),'rb'))
     fit_result, trans_result = result
     mcmc_new_list, labels_new = trans_result
 
 kwargs_result, chain_list_mcmc, chain_list_pso = fit_result
 sampler_type, samples_mcmc, param_mcmc, dist_mcmc  = chain_list_mcmc[0]
 chain_num = len(mcmc_new_list)
+#%%
+plot = corner.corner(mcmc_new_list, labels=labels_new, show_titles=True,
+                     quantiles=[0.16, 0.5, 0.84], #smooth = 0.8,
+                     title_kwargs={"fontsize": 15}, label_kwargs = {"fontsize": 25},
+                     levels=1.0 - np.exp(-0.5 * np.array([1.,2.]) ** 2))
 
-print "plot how value change with chains:"
-print labels_new
-i = 3
-plt.figure(figsize=(11, 8))
-plt.plot(range(chain_num), mcmc_new_list[:,i], '-' ,linewidth = 0.1, color='gray')
-plt.xlabel("number of Chains",fontsize=27)
-plt.ylabel(labels_new[i],fontsize=27)
-plt.tick_params(labelsize=20)
-plt.show()
-
-print "plot how value change with chains:"
-print param_mcmc
-i = 2
-plt.figure(figsize=(11, 8))
-plt.plot(range(len(samples_mcmc)), samples_mcmc[:,i], '-',linewidth = 0.01, color='gray')
-plt.xlabel("number of Chains",fontsize=27)
-plt.ylabel(param_mcmc[i],fontsize=27)
-plt.tick_params(labelsize=20)
[…]

### 2020-01-17 py_tools/cut_image.py

@@ -77,7 +77,7 @@ def cut_center_bright(image, center, radius,kernel = 'gaussian', return_center=F
         return cut_c_b, center_f
  
 def save_loc_png(img, center_QSO, c_psf_list=None,extra_psfs=None,ID=None, label= None,
-                 reg_ty=None,ifsave=True, label_shift_NO=(), shift_where=None):
+                 reg_ty=None,ifsave=True, label_shift_NO=(), shift_where=None, v_max = None, v_min = None):
     '''
     label shift_where: 1,2,3,4 --- up, right, down, left
     '''
@@ -106,6 +106,10 @@ def save_loc_png(img, center_QSO, c_psf_list=None,extra_psfs=None,ID=None, label
         vmin = 1.e-3
         QSO_box_size = 100
         PSF_box_size = 60 
+    if v_max != None:
+        vmax = v_max
+    if v_min != None:
+        vmin = v_min
     cax=ax.imshow(img,origin='lower', cmap=my_cmap, norm=LogNorm(), vmin=vmin, vmax=vmax)
     QSO_reg = pix_region(center_QSO, radius= QSO_box_size)
     QSO_mask = QSO_reg.to_mask(mode='center')

### 2020-01-27 GW_BH_function/paper_draft/2020_revise/bold/main_revised_bold.tex
Update BHMF paper, submitted

--- 2020-01-17 GW_BH_function/paper_draft/2020_revise/main_revised.tex
@@
 where $r_0$ is the detector's characteristic distance parameter and $\zeta(f_{max})$ is the dimensionless function reflecting the overlap between the GW signal and the ET's effective {\bf bandwidth.
-For simplicity, we follow the estimations by \citet{Taylor2012} and approximate $\zeta(f_{max})$ as  unity.} ${\cal M}_0$ is the intrinsic chirp mass defined as $ {\cal M}_0 = \frac{(m_1m_2)^{3/5}}{(m_1+m_2)^{1/5}}$, where \mone\ and \mtwo\ are the
+For simplicity, we followed  \citet{Taylor2012} and approximated $\zeta(f_{max})$ as  unity.} ${\cal M}_0$ is the intrinsic chirp mass defined as $ {\cal M}_0 = \frac{(m_1m_2)^{3/5}}{(m_1+m_2)^{1/5}}$, where \mone\ and \mtwo\ are the
 respective masses of the BBH components. $\Theta$ is the orientation factor determined by four angles as \citep{Finn93}:
@@
 We do not have any clear physical guidance of how could $\alpha$ evolve  with redshift and in particular which analytical expression would describe it reliably.
-Therefore the above ansatz is actually the first order Taylor expansion{, \bf assumption $\alpha$ as a function of the scale factor $a$, where $a(t) = \frac{1}{1+z}$.}
-%in the scale factor $a(t)$ applicable for any function.
+Therefore the above ansatz is actually a \textbf{ suitable form of the first order Taylor expansion of $\alpha$ as a function of the scale factor $a$ (around the present value $a(t_0)=1$, where $a(t) = \frac{1}{1+z}$).}
 
@@
 The intrinsic value of primary BH mass (i.e., $m_{1,fid}$) follows a power-law distribution, however the measured  \mone\ is scattered by the Log-Normal distribution which does not follow a power-law function anymore \citep{Koen2009}.
-In theory, if the event $X$ follows a power-law distribution and its observed values are subject to the {\bf Log-Normal} uncertainty, then {\bf the observed event $X + e$ (where $e$ denote the error)} is distributed according to the convolution of the power-law and {\bf Log-Normal distributions.
+\textbf{In theory, if the event $X$ follows a power-law distribution and its observed values are subject to the  Log-Normal uncertainty, then the observed event $X + e$,   with $e$ denoting the error (uncertainty), is distributed according to the convolution of the power-law and Log-Normal distribution.
 Assuming that the noised data follow the Log-Normal distribution, we convolved the intrinsic power-law to describe likelihood as:}
@@
 Note that the observed \dl\ and \cmass\ are both considered to have random noise which follows the asymmetric distribution (i.e., Log-Normal).
-Thus, the {\bf possibility distribution} of their product $\eta$ is also asymmetric.
+Thus, the {\bf intrinsic probability distribution (not the errors to be convolved) of their product, and thus of $\eta$ is} also asymmetric.
 Considering the random distributions of the \dl\ and \cmass, we performed the numerical tests and found that the distribution of $1/\eta$ could be well described by the Log-Normal distribution with multiplicative standard deviation as $\sigma=-log(\eta_{\rm median})/3$, see Figure~\ref{fig_eta}.
@@
 \caption{
-Assuming a set of \dl\ and \cmass\ following the Log-Normal distribution, we randomly produce the corresponding histogram of the $1/\eta$ {\bf to access its possibility distribution}.
+Assuming a set of \dl\ and \cmass\ following the Log-Normal distribution, we randomly produce the corresponding histogram of the $1/\eta$ {\bf in order to assess its probability distribution}.
 The result shows that the skewed distribution could be well described by a Log-Normal distribution with $\sigma = -\log(\eta_{\rm median})/3$.
@@
 %The redshift is not detectable by GW, however, can be inferred from the DL. 
-In the previous section, we take \dl\ as the redshift estimator to derive the redshift and hence selection factor $\eta$.
-The way to derive the inferred redshift {\bf $z_{inf}$ is to take the obtained luminosity distance, i.e.,  \dl$(z)$, and derive the inverse solution of integral function based on a fixed cosmological model.}
+{\bf In the previous section, we took \dl\ as the redshift estimator to derive the redshift and hence the selection factor $\eta$.
+Let us denote such inferred redshift as $z_{inf}$.
+The way to derive the $z_{inf}$ is to take the observed luminosity distance, i.e.,  \dl$(z)$, and find the inverse solution of the integral function based on a fixed cosmological model.}
 
@@
 
-We point out a few limitations of this work.
-First, we have adopted a template of intrinsic BBH merger rate based on the predictions by a standard model in {\tt StarTrack}, which can be different from the realistic one.
+{\bf We point out a few circumstances, which might weaken generality this work.} First, we have adopted a template of intrinsic BBH merger rate based on the predictions by a standard model in {\tt StarTrack}, which can be different from the realistic one.
 Of course, the intrinsic BBH merger rate is unknown yet, which is related to lack of detailed knowledge of different elements such as BBH masses, explosion mechanism, the metallicity history and the time delay distribution.
-{\bf With a different template of BBH merger rate, the simulated mock events (i.e., the ones in the Table~\ref{tab_GW_mock_data}) would follows a different redshift distribution, which could slightly change the inference of the uncertainties of the inferred parameters.
+{\bf With a different template of BBH merger rate, the simulated mock events (i.e., the ones in the Table~\ref{tab_GW_mock_data}) would follow a different redshift distribution, which could slightly change the inference of the uncertainties of the inferred parameters.
 Second}, for the sake of simplicity, we simulated the value of the secondary BH mass \mtwo\ by assuming that two masses of BBHs have independent distributions, which probably is not exactly true.
-{\bf One can expect that these two limitations would affect the prediction of the yearly detection rate of the GW events and their redshift distribution; however, their influence on our final inferred contours of BHMF (i.e., Figure~\ref{fig_result_a} and~\ref{fig_result_b}) is very limited.}
+{\bf One can expect that these two limitations would affect the prediction of the yearly detection rate of the GW events and their redshift distribution; however, their influence on our final inferred contours of BHMF (i.e., Figure~\ref{fig_result_a} and~\ref{fig_result_b}) is likely not very significant.}
 At last, the numerical tests done in this work confirmed the validity of our method.

### 2020-02-20 projects/GW_BH_function/paper_draft/2020_revise/main_revised.tex
Backup and clean house work

--- 2020-01-17 GW_BH_function/paper_draft/2020_revise/main_revised.tex
@@
 
-\correspondingauthor{{\bf Zong-Hong Zhu}}
+\correspondingauthor{Zong-Hong Zhu}
 \email{zhuzh@whu.edu.cn}
@@
 \end{equation}
-where $r_0$ is the detector's characteristic distance parameter and $\zeta(f_{max})$ is the dimensionless function reflecting the overlap between the GW signal and the ET's effective {\bf bandwidth.
-For simplicity, we follow the estimations by \citet{Taylor2012} and approximate $\zeta(f_{max})$ as  unity.} ${\cal M}_0$ is the intrinsic chirp mass defined as $ {\cal M}_0 = \frac{(m_1m_2)^{3/5}}{(m_1+m_2)^{1/5}}$, where \mone\ and \mtwo\ are the
+where $r_0$ is the detector's characteristic distance parameter and $\zeta(f_{max})$ is the dimensionless function reflecting the overlap between the GW signal and the ET's effective bandwidth.
+For simplicity, we followed  \citet{Taylor2012} and approximated $\zeta(f_{max})$ as unity.
+${\cal M}_0$ is the intrinsic chirp mass defined as $ {\cal M}_0 = \frac{(m_1m_2)^{3/5}}{(m_1+m_2)^{1/5}}$, where \mone\ and \mtwo\ are the
 respective masses of the BBH components. $\Theta$ is the orientation factor determined by four angles as \citep{Finn93}:
@@
 We do not have any clear physical guidance of how could $\alpha$ evolve  with redshift and in particular which analytical expression would describe it reliably.
-Therefore the above ansatz is actually the first order Taylor expansion{, \bf assumption $\alpha$ as a function of the scale factor $a$, where $a(t) = \frac{1}{1+z}$.}
-%in the scale factor $a(t)$ applicable for any function.
+Therefore the above ansatz is actually a suitable form of the first order Taylor expansion of $\alpha$ as a function of the scale factor $a$ (around the present value $a(t_0)=1$, where $a(t) = \frac{1}{1+z}$).
 
@@
 The intrinsic value of primary BH mass (i.e., $m_{1,fid}$) follows a power-law distribution, however the measured  \mone\ is scattered by the Log-Normal distribution which does not follow a power-law function anymore \citep{Koen2009}.
-In theory, if the event $X$ follows a power-law distribution and its observed values are subject to the {\bf Log-Normal} uncertainty, then {\bf the observed event $X + e$ (where $e$ denote the error)} is distributed according to the convolution of the power-law and {\bf Log-Normal distributions.
-Assuming that the noised data follow the Log-Normal distribution, we convolved the intrinsic power-law to describe likelihood as:}
+In theory, if the event $X$ follows a power-law distribution and its observed values are subject to the  Log-Normal uncertainty, then the observed event $X + e$,   with $e$ denoting the error (uncertainty), is distributed according to the convolution of the power-law and Log-Normal distribution.
+Assuming that the noised data follow the Log-Normal distribution, we convolved the intrinsic power-law to describe likelihood as:
  \begin{equation} \label{equ_lik_conv}
@@
 Note that the observed \dl\ and \cmass\ are both considered to have random noise which follows the asymmetric distribution (i.e., Log-Normal).
-Thus, the {\bf possibility distribution} of their product $\eta$ is also asymmetric.
+Thus, the intrinsic probability distribution (not the errors to be convolved) of their product, and thus of $\eta$ is also asymmetric.
 Considering the random distributions of the \dl\ and \cmass, we performed the numerical tests and found that the distribution of $1/\eta$ could be well described by the Log-Normal distribution with multiplicative standard deviation as $\sigma=-log(\eta_{\rm median})/3$, see Figure~\ref{fig_eta}.
@@
 \caption{
-Assuming a set of \dl\ and \cmass\ following the Log-Normal distribution, we randomly produce the corresponding histogram of the $1/\eta$ {\bf to access its possibility distribution}.
+Assuming a set of \dl\ and \cmass\ following the Log-Normal distribution, we randomly produce the corresponding histogram of the $1/\eta$ in order to assess its probability distribution.
 The result shows that the skewed distribution could be well described by a Log-Normal distribution with $\sigma = -\log(\eta_{\rm median})/3$.
@@
 %The redshift is not detectable by GW, however, can be inferred from the DL. 
-In the previous section, we take \dl\ as the redshift estimator to derive the redshift and hence selection factor $\eta$.
-The way to derive the inferred redshift {\bf $z_{inf}$ is to take the obtained luminosity distance, i.e.,  \dl$(z)$, and derive the inverse solution of integral function based on a fixed cosmological model.}
+In the previous section, we took \dl\ as the redshift estimator to derive the redshift and hence the selection factor $\eta$.
+Let us denote such inferred redshift as $z_{inf}$.
+The way to derive the $z_{inf}$ is to take the observed luminosity distance, i.e.,  \dl$(z)$, and find the inverse solution of the integral function based on a fixed cosmological model.
 
@@
 
-We point out a few limitations of this work.
+We point out a few circumstances, which might weaken generality this work.
 First, we have adopted a template of intrinsic BBH merger rate based on the predictions by a standard model in {\tt StarTrack}, which can be different from the realistic one.
 Of course, the intrinsic BBH merger rate is unknown yet, which is related to lack of detailed knowledge of different elements such as BBH masses, explosion mechanism, the metallicity history and the time delay distribution.
-{\bf With a different template of BBH merger rate, the simulated mock events (i.e., the ones in the Table~\ref{tab_GW_mock_data}) would follows a different redshift distribution, which could slightly change the inference of the uncertainties of the inferred parameters.
-Second}, for the sake of simplicity, we simulated the value of the secondary BH mass \mtwo\ by assuming that two masses of BBHs have independent distributions, which probably is not exactly true.
-{\bf One can expect that these two limitations would affect the prediction of the yearly detection rate of the GW events and their redshift distribution; however, their influence on our final inferred contours of BHMF (i.e., Figure~\ref{fig_result_a} and~\ref{fig_result_b}) is very limited.}
+With a different template of BBH merger rate, the simulated mock events (i.e., the ones in the Table~\ref{tab_GW_mock_data}) would follow a different redshift distribution, which could slightly change the inference of the uncertainties of the inferred parameters.
+Second, for the sake of simplicity, we simulated the value of the secondary BH mass \mtwo\ by assuming that two masses of BBHs have independent distributions, which probably is not exactly true.
+One can expect that these two limitations would affect the prediction of the yearly detection rate of the GW events and their redshift distribution; however, their influence on our final inferred contours of BHMF (i.e., Figure~\ref{fig_result_a} and~\ref{fig_result_b}) is likely not very significant.
 At last, the numerical tests done in this work confirmed the validity of our method.

### 2020-02-20 projects/GW_BH_function/paper_draft/Marek_edit/main_revised_MB.tex
Backup and clean house work

--- 2019-12-10 GW_BH_function/paper_draft/sec_edit_based_on_Marek_edit/main_revised.tex
@@
 \usepackage{mathrsfs}
-\usepackage[caption=false]{subfig}
+
 \usepackage{float}
@@
 \newcommand{\kai}[1]{\textcolor{red}{[{\bf Kai}: #1]}}
-\newcommand{\blue}[1]{\textcolor{blue}{#1}} 
-\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
 
@@
 We use the mass of a primary black hole in each binary system to infer the BHMF as a power-law function with slope parameter as $\alpha$.
-Taking into account the bias that could be introduced by the uncertainty of measurements and by the selection effect, we \blue{carried out the numerical tests for three different sets of parameters and} find that only one thousand of GW events registered by ET ($\sim1\%$ amount of its yearly detection rate) could accurately infer the $\alpha$ \blue{with a precision of $\alpha\sim0.1$.
-Furthermore, assuming four sets of parameters, we investigate the validity of our method to recover a scenario where $\alpha$ evolves with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
-Our result shows, taking a thousand GW events and using \dl\ as the redshift estimator, one could infer the value of evolving parameter $\alpha_1$ accurately at the uncertainty level of $\sim0.5$.
-Our numerical tests verify the reliability of our method; however, the uncertainty levels of the inferred parameters only applies for the assumed sets of the parameters which shouldn't be considered as a universal value for the general case.
-}
+Taking into account the bias that could be introduced by the uncertainty of measurements and by the selection effect, we find that only one thousand of GW events registered by ET ($\sim1\%$ amount of its yearly detection rate) could accurately infer the $\alpha$ with $3\%$ precision.
+Furthermore, we investigate a scenario where $\alpha$ evolves with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
+Our result shows, taking a thousand GW events and using \dl\ as the redshift estimator, one could infer the value of evolving parameter $\alpha_1$ at the uncertainty level of $\pm0.5$.
 \end{abstract}
@@
 %For each BBH system, we sample the probability distribution of the key parameters to randomly generate their values. These 
-{\bf Other key parameters include the four angles $(\theta, \phi, \psi, \iota)$ in the Equation~(\ref{Theta})  and the masses of each BH in the binary system (i.e., \mone\ and \mtwo).}
+Other key parameters include the four angles $(\theta, \phi, \psi, \iota)$ in the Equation~(\ref{Theta})  and the masses of each BH in the binary system (i.e., \mone\ and \mtwo).
 For the purpose of randomly generating the BH masses, we follow the previous works \citep{Kovetz2017PhRvD, Abbott2018b, Fishbach2018} and assume that \mone\ follows a power-law distribution with a hard cut at both maximum and minimum mass:
  \begin{equation} \label{equ_powlaw}
-{\bf P(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),}
+P(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),
  \end{equation}
@@
 \textbf{The parameters \it{measurable} from the BBH inspiral waveform comprised of \dl, redshifted chirp mass $(1+z){\cal M}_0 $ and $\rho$.} Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform.
-\blue{We note the fact that LIGO detections usually infer the properties an asymmetry upper and lower limit with ${\it skewed}$ possibility distributions.
-Therefore, instead of the symmetric Gaussian distribution, we assume that the simulated mock measurements follow the Log-Normal distribution with the standard deviation of  ${\cal M}_0$, \dl, and \mone\ equal to 0.17, 0.35 and 0.2, respectively.}
-For instance, if the $m_{1,fid}$ is the true value for \mone, \blue{the probability density as used to simulate the measured value} is:
+\textbf{Marek: Have we considered properly in the analysis that the measured masses are redshifted ones?}
+As a recipe to set up the noise levels of our simulated data, we adopt the results of \citet{Ghosh2016}, who  explored the expected statistical uncertainties with which the parameters of black hole binaries can be measured from GW observations by next generation ground-based GW observatories.
+Moreover, we stress that the measurements of the BBH parameters are characterized by ${\it skewed}$ distributions.
+Therefore, instead of the traditional Gaussian distribution, we assume that the measured parameters follow the Log-Normal distribution with the standard deviation of  ${\cal M}_0$, \dl, and \mone\ equal to 0.17, 0.35 and 0.2, respectively.
+For instance, if the $m_{1,fid}$ is the true value for \mone, its probability density is:
  \begin{equation} \label{equ_lognorm}
@@
  \end{equation}
-\blue{We set up the standard errors for ${\cal M}_0$, \dl, and \mone\ by taking results by \citet{Ghosh2016} as the reference, who explored the expected statistical uncertainties with which the parameters of black hole binaries can be measured from GW observations by next generation ground-based GW observatories.
-Note that the assumed uncertainty level of these properties should only affect the uncertainty (i.e., precision) of the inferred parameters, which wouldn't affect the validity (i.e., accuracy) test of our method.
-}
 
@@
  \end{equation}
- \textbf{where $m_{1,i}$ is the primary mass inferred from the $i$~-~$th$ GW event.}
+ \textbf{where $m{1,i}$ is the primary mass inferred from the $i-th$ GW event.}
 However, the median values of simulated \mone, as shown in Table~\ref{tab_GW_mock_data}, actually deviate from the initial power-law distribution.
@@
  \begin{equation} \label{equ_lik_conv}
- P(\alpha, M_{max}, M_{min}{\bf |m_{1}}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min}),
+ P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min}),
  \end{equation}
@@
 The GW observations have a tendency to discover more significant events, known as Malmquist bias.
-\blue{For example, the} GW systems with higher values \mone\ \blue{trend to} produce stronger signals and thus have a higher probability to be detected.
-\blue{As a result, the final BHMFs would be biased to the high mass end, if this effect is not correctly taken into account}.
+The GW systems with higher values \mone\ produce  stronger signals and thus have a higher probability to be detected.
+If this effect is not taken into account, the final BHMFs would be biased to the high mass end.
 
@@
 In other words, four equivalent events would have been missed.
-Thus, for this event, one needs to re-calibrate \blue{this influence by enhancing the likelihood by a power of 5 (i.e., $L^{1/0.2} = L^5$) to recover the possibility to its intrinsic value.
-Hence, to account for the selection effect, we calculate the likelihood as:}
+Thus, for this event, one needs to re-calibrate its influence by  enhancing the likelihood by a power of 5.
+Hence, to account for this  selection effect, we modify the likelihood as:
  \begin{equation} \label{equ_lik_sf}
- P(\alpha, M_{max}, M_{min}{\bf |m_{1}}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta},
+ P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta},
  \end{equation}
@@
 $\eta = P(\rho>8)$.
-In order to \blue{adopt the Equation~(\ref{SNR}) to derive the $\rho$}, the distribution function of $\Theta$ is \blue{taken} from the MC simulations; the \cmass\ and \dl\ are \blue{adopted from} the mock dataset as demonstrated in Table~\ref{tab_GW_mock_data}.
+In order to use the Equation~(\ref{SNR}), the distribution function of $\Theta$ is known from the MC simulations, the \cmass\ and \dl\ are provided in the mock dataset as demonstrated in Table~\ref{tab_GW_mock_data}.
 Yet, the redshift $z_s$ is the unknown parameter since it is non-measurable in the GW detectors; one can only take the \dl\ as redshift estimator.
-\blue{Note that the observed \dl\ and \cmass\ are both considered to have random noise which follows the asymmetric distribution (i.e., Log-Normal).
-Thus, the distribution of their product $\eta$ is also asymmetric.
-Considering the random distributions of the \dl\ and \cmass, we performed the numerical tests and found that the distribution of $1/\eta$ could be well described by the Log-Normal distribution with multiplicative standard deviation as $\sigma=-log(\eta_{\rm median})/3$, see Figure~\ref{fig_eta}.
-Note that in a Log-Normal distribution, the expected value are higher than the true value (i.e., median value) by a factor of $e^{\sigma^2/2}$.
-We consider this skewness and recalibrate the inferred expected value of $1/\eta$ into the median value, in order to assign a non-biased $1/\eta$ to the calculation.
-}
-
-\begin{figure}%[!b]
-\includegraphics[width=1.0\linewidth]{eta_distribution.pdf}
-\caption{
-\blue{
-Assuming a set of \dl\ and \cmass\ as Log-Normal distribution, we randomly produce the the corresponding histogram of the $1/\eta$ distribution.
-The result shows that the skewed distribution could be well described by a Log-Normal distribution with $\sigma = -\log(\eta_{\rm median})/3$.
-}
-}
-\label{fig_eta}
-\end{figure}
+Note that the observed \dl\ and \cmass\ both have asymmetric distributions with large scatter, hence the distribution of their inferred $\eta$ would be biased and scattering around its true value.
+In our simulating test, we find that this distribution could be well described by a Log-Normal distribution, with multiplicative standard deviation\footnote{In Log-Normal distribution, the multiplicative standard deviation is the exponent  of the standard deviation, i.e., $\sigma^* = exp(\sigma)$.} as $\sigma^*=log(\eta)/3$.
+Thus, we manually correct this skewness and adopt the non-biased $\eta$.
 
@@
 To avoid the bias and estimate the scatter, we adopt the realization approach.
+%The details of the simulation are the following.
 In each realization, we simulate a thousand of BBH inspiral GW events and infer the best-fit parameters using minimization of the chi-square objective function. 
-\blue{We keep increasing the volume of realizations until the inferred best-fit parameters converged.}
+The realization is completed when the inferred best-fit parameters converged.
 
 In the first scenario, we consider the slope $\alpha$ as a constant.
-\blue{ We performed numerical tests assuming three different sets of parameters taking $\alpha$ as 0.8, 1.6 and 2.4, with $M_{min}~=~5M_{\odot}$, $M_{max}~=~50M_{\odot}$.
+We generated the mock data by taking $\alpha~=~2.35$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ as the fiducial values.
 We calculate the likelihood by Equation~(\ref{equ_lik_sf}) to infer the best-fit parameters in each realization.
-It has been discussed that no black holes with mass over $50M_{\odot}$ are expected from stellar evolution and through supernovae~\citep{Woosley2017, Wiktorowicz2019}.
-In Figure~\ref{fig_result_a}, we present the posterior distribution of the inferred parameters for the three parameter sets.
-We find that all the parameters are recovered accurately which confirms the validity of our method.
-The uncertainties for the inferred parameters are $\Delta\alpha\sim0.1$, $\Delta M_{max}\sim1-2M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$.
-Note that these uncertainty levels are not ready to be treated as a universal for the general case, but only apply when the initial parameter sets are close to the tested ones.
-Moreover, these uncertainty levels are related to the standard deviation of the measurements including ${\cal M}_0$, \dl, and \mone, as discussed in Section~\ref{sec_noiselevel}.
-}
+In Figure~\ref{fig_result_a}, we present the posterior distribution of the inferred parameters.
+We find that the inference of the parameters is distributed as $\alpha = 2.36\substack{+0.09\\-0.08}$, $M_{max} = 80.54\substack{+5.45\\-5.60}$,  $M_{min} = 5.03\substack{+0.17\\-0.15}$.
+This inference of $\alpha$ indicates that a thousand of GW events could constrain the slope within $3.5\%$ level.
 
-\begin{figure*}%[!b]
-\centering
-\begin{tabular}{c c c}
-\subfloat[\blue{assuming $\alpha=0.8$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
-{\includegraphics[width=0.3\linewidth]{3para_contour_a0_08.pdf}}&
-\subfloat[\blue{assuming $\alpha=1.6$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
-{\includegraphics[width=0.3\linewidth]{3para_contour_a0_16.pdf}}&
-\subfloat[\blue{assuming $\alpha=2.4$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
-{\includegraphics[width=0.3\linewidth]{3para_contour_a0_24.pdf}}
-\end{tabular}
+\begin{figure}%[!b]
+\includegraphics[width=1.0\linewidth]{fig_results_3para.pdf}
 \caption{
-One- and two-dimensional distributions for the best-fitted parameters in the \blue{first scenario, based on three sets of parameters with a thousand of BBH inspiral GW events}.
+One- and two-dimensional distributions for the best-fitted parameters in the scenario A.
 The BHMF is assumed as a power-law with hard cut at the $M_{min}$ and $M_{max}$, with a constant slope ($\alpha$) across all the redshifts.
@@
 \label{fig_result_a}
-\end{figure*}
+\end{figure}
 
 In the second scenario, the $\alpha$ evolves with redshift according to the Equation~(\ref{equ_alphaz}).
-\blue{We consider four sets of parameters assuming $\alpha_0$ as  0.8, 1.6, 2.4 and $\alpha_1$ including 0.7 and 1.2.
-We present the results in Figure~\ref{fig_result_b} and find that all the assumed parameters could be recovered accurately.
-With one more parameters included in the second scenario, the uncertainty level are extended as \ding{The following values still need to confirm} $\Delta\alpha_0\sim0.4$, $\Delta\alpha_1\sim0.5-0.7$, $\Delta M_{max}\sim2-4M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$.
-We note that there is a degeneracy between the $\alpha_0$ and $\alpha_1$, which is understandable given that they are strongly connected by the Equation~\ref{equ_alphaz}.
-However, for the four sets of parameters we tested, this degeneracy does not affect the inferred uncertainty level for the $\alpha_0$ and $\alpha_1$.
-}
+We assume the fiducial parameters as $\alpha_0~=~2.35$, $\alpha_1~=~0.75$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~80M_{\odot}$ to generate a thousand datasets in each realization.
+We present the results in Figure~\ref{fig_result_b}.
+Since the second scenario has one more parameter, distributions of the best-fitted parameters have larger scatter and can be summarized as $\alpha_0 = 2.32\substack{+0.35\\-0.36}$, $\alpha_1 = 0.73\substack{+0.52\\-0.50}$, $M_{max} = 78.03\substack{+10.03\\-8.40}$ and  $M_{min} = 5.02\substack{+0.14\\-0.14}$.
+Not surprisingly, the degeneracy exsits between the $\alpha_0$ and $\alpha_1$.
 
-We highlight that in this \blue{second} scenario, it is the inferred uncertainty of $\alpha_1$ that matters the most.
-\blue{Our result show that, with only one thousand of GW measurements in the future, the inferred value of $\alpha_1$ would reach to precision of $\Delta\alpha_1\sim0.5-0.7$.
-Limited by the computing power, we couldn't use numerical test to get a universal uncertainty level as for the general case.
-However, given the fours sets of tests as shown the Figure~\ref{fig_result_b}, it is likely to be true that one thousand of GW measurement could distinguish the evolution of BHMF at 1-$\sigma$ confidence level when $\alpha_1$ is deviated from 0 by a value of 0.5.
-Moreover, we conjecture that the precision of inference is increasing with the sample size as a function of $\sqrt{N}$.
-Thus, for the four sets of tests, the one year measurements of ET ($\sim10^5$ in total) would increase the uncertainty levels by a factor of 10.}
+We highlight that in this scenario, it is the inferred uncertainty of $\alpha_1$ that matters the most.
+Our result show that, with a volume of one thousands GW measurements, the inferred value of $\alpha_1$ would have a precision of $\pm0.5$.
+That is to say, one thousand of measurements is able to distinguish the evolution of BHMF, when $\alpha_1$ is deviated from 0 by a value of 0.5 at 1-$\sigma$ confidence level.
+Limited by the computing power, we haven't tested the larger sample of measurements.
+However, conjecturing that the precision of inference is increasing with the sample size as a function of $\sqrt{N}$, one year measurements of ET ($\sim10^5$ in total) would result in the $\alpha_1$ inferred with the precision down to $\sim0.05$.
 We also note that the distribution of the best-fitted parameters ($\alpha_0$, $\alpha_1$) does not follow the Gaussian distribution, but rather a large fraction of it is concentrated at the center. 
@@
 
-\begin{figure*}%[!b]
-\centering
-\begin{tabular}{c c}
-\subfloat[\blue{assuming $\alpha_0=0.8$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
-{\includegraphics[width=0.4\linewidth]{4para_contour_a0_08_a1_07.pdf}}&
-\subfloat[\blue{assuming $\alpha_0=1.6$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
-{\includegraphics[width=0.4\linewidth]{4para_contour_a0_16_a1_07.pdf}}\\
-\subfloat[\blue{assuming $\alpha_0=2.4$, $\alpha_1=0.7$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
-{\includegraphics[width=0.4\linewidth]{4para_contour_a0_24_a1_07.pdf}}&
-\subfloat[\blue{assuming $\alpha_0=1.6$, $\alpha_1=1.2$, $M_{min}=5M_{\odot}$ and $M_{max}=50M_{\odot}$.}]
-{\includegraphics[width=0.4\linewidth]{4para_contour_a0_16_a1_12.pdf}}
-\end{tabular}
+\begin{figure}%[!b]
+\includegraphics[width=1.0\linewidth]{fig_results_4para.pdf}
 \caption{
-\blue{Same} as Figure~\ref{fig_result_a} but for the second scenario, where the $\alpha$ of BHMF is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$\blue{, four sets of parameters assumed.}
+The same as Figure~\ref{fig_result_a} but for the scenario B, where the $\alpha$ of BHMF is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$. 
 }
 \label{fig_result_b}
-\end{figure*}
+\end{figure}
 
@@
 The third-generation gravitational wave detector, the Einstein Telescope, is very powerful and capable of detecting $\sim10^5$ GW events per year, with redshift up to $z\sim17$.
-In this study, we investigated how the detections of the BBH mergers could improve our knowledge of the black hole mass function \blue{(BHMF)}.
+In this study, we investigated how the detections of the BBH mergers could improve our knowledge of the black hole mass function.
 
 We performed the Monte Carlo simulation to estimate the uncertainty level of BHMF parameters inferred from GW signals by BBHs that would be detected by ET.
-As a starting point, we assumed that the BHMF for the primary BH mass followed a power-law distribution \blue{with a hard cuts as Equation~(\ref{equ_powlaw})}.
+As a starting point, we assumed that the BHMF for the primary BH mass followed a power-law distribution.
 Based on the BBH intrinsic merger rate predicted by {\tt StarTrack}, we randomly simulated the key parameters of the BBH systems, including the chirp masses, redshifts and orientation factors and calculated  their corresponding signal-to-noise ratio \snr\ for the ET.
@@
 We took into account the measurement uncertainties and the selection effect which would bias the inference.
-We \blue{performed the test using realizations, one thousand GW events per realization}, and estimated the distribution of the best-fitted parameters of the BHMF, including the power-law slope $\alpha$, the maximum BH mass $M_{max}$ and the minimum BH mass $M_{min}$ \blue{in the first scenario}.
-Furthermore, \blue{in the second scenario, we consider the $\alpha$ evolves as a function of redshift and used the luminosity distance as redshift estimator to test the evolution}.
+We used the realization approach, one thousand GW events per realization, and estimated the distribution of the best-fitted parameters of the BHMF, including the power-law slope $\alpha$, the maximum BH mass $M_{max}$ and the minimum BH mass $M_{min}$.
+Furthermore, we used the luminosity distance as redshift estimator and tested whether one can infer the $\alpha$ as a function of redshift.
 We summarize our main results as follows:
-\blue{
 \begin{enumerate}
-\item Using our method based on Equation~(\ref{equ_lik_sf}), all the tested parameters are all recovered accurately, which confirms the validity of our tests and highlights the importance of correctly considering the measurement uncertainty and selection effect.
-\item Taking the measured \dl\ as redshift estimator, we tested to recover the $\alpha$ with a scenario which is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
-Testing with four parameters sets, we are able to successfully recovered the true value of $\alpha_1$ accurately.
-\item Given the fixed sets of parameters, our results show that a volume of one thousand measurements of BBHs events could infer the parameters with uncertainties level at $\Delta\alpha\sim0.1$, $\Delta M_{max}\sim1-2M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$ for the first scenario.
-For the second scenario, the inferred uncertainties are $\Delta\alpha_0\sim0.4$, $\Delta\alpha_1\sim0.5-0.7$, $\Delta M_{max}\sim2-4M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$.
-In the future, the one year detection rate of ET ($\sim10^5$ in total) increase the sample size by a factor of 100.
-According to the fact that the precision of the inference increases with the sample size, as a function of $\sqrt{N}$, we conclude that one year BBH sample by ET would be able to deliver the parameters at higher uncertainty improved by a factor of 10 as tested.
+\item Assuming the $\alpha$ is constant in redshift, one could infer the $\alpha$, $M_{max}$ and $M_{min}$ precisely and accurately.
+With one thousand measurements of BBHs events, the $\alpha$ would reach 3\% level,
+%i.e., Figure~\ref{fig_result_a}.
+\item Testing the scenario that $\alpha$ is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$, our results show that a volume of one thousand measurements of BBHs events would provide the evolving parameter $\alpha_1$ with an uncertainty level of $\pm0.5$.
+Meaning that with this sample size one is able to recognize the evolution of BHMF when $\alpha_1$ deviates from $0$ by $0.5$.
+\item According to the fact that the precision of the inference increases with the sample size, as a function of $\sqrt{N}$, we conclude that one year BBH sample by ET would be able to deliver the value of $\alpha_1$ with precision down to 0.05.
 \end{enumerate}
-}
 
@@
 However, one can expect that these limitations would more strongly affect the prediction of the yearly detection rate of the GW events and their redshift distribution, rather than the inference of the parameters in the BHMF.
-\blue{Last, the numerical tests as done in this works confirms the validity of our method.
-However, limited by the sets of tests, the inferred uncertainty for both scenario applies for the fixed sets of parameters which shouldn't be considered as a general value.}
+%Using a sample with the same volume but different redshift distribution, the inference on the BHMF parameters could be very similar.
 
@@
 M.B. was supported by the Key Foreign Expert Program for the Central Universities No. X2018002.
-K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. {\bf 11973034}..
+K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. 11603015.
 \software{  {\sc corner}, \citep{corner},

### 2020-02-20 projects/GW_BH_function/paper_draft/first_sub_manuscript_GW_constrain_BHmass/main.tex
Backup and clean house work

--- 2020-02-20 projects/GW_BH_function/paper_draft/Marek_edit/main_revised_MB.tex
@@
 \begin{abstract}
-The knowledge about the  black hole mass function (BHMF) and its evolution would help to understand the origin of the BHs and how BH binaries formed at different stages of the history of the Universe.
+The ability of gaining knowledge about the  black hole mass function (BHMF) and its evolution would help to understand the origin of the BHs and how BH binaries formed at different stages of the history of the Universe.
 We demonstrate the ability of future third generation gravitational wave (GW) detector -- the Einstein Telescope (ET) to infer the slope of the BHMF and its evolution with redshift.
@@
 We use the mass of a primary black hole in each binary system to infer the BHMF as a power-law function with slope parameter as $\alpha$.
-Taking into account the bias that could be introduced by the uncertainty of measurements and by the selection effect, we find that only one thousand of GW events registered by ET ($\sim1\%$ amount of its yearly detection rate) could accurately infer the $\alpha$ with $3\%$ precision.
+Taking into account the bias that could be introduced by the measuring uncertainty and by the selection effect, we find that only one thousand of GW events registered by ET ($\sim1\%$ amount of its yearly detection rate) could accurately infer the $\alpha$ with $3\%$ precision.
 Furthermore, we investigate a scenario where $\alpha$ evolves with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
@@
 coalescing binary black holes (BBHs) in LIGO gravitational-wave (GW) detectors is a substantial evidence of stellar-mass BHs \citep{Abbott2016}, while supermassive BHs are supposed to exist in the centers of almost all the galaxies \citep{Lynden-Bell1969, Kormendy1995}.
-%Recently, the first image of a supermassive BH in the center of the giant elliptical galaxy M87 has been reconstructed from radio observations performed by the Event Horizon Telescope \citep{Alberdi2019}.
+Recently, the first image of a supermassive BH in the center of the giant elliptical galaxy M87 has been reconstructed from radio observations performed by the Event Horizon Telescope \citep{Alberdi2019}.
 GWs provide a direct way to study the inspiralling BBH systems, enabling one to derive their basic parameters including mass, spin and luminosity distances~\citep{Abbott2017phy, Abbott2018}.
@@
 In particular, the number and mass distribution of stellar-mass BHs in the Universe still need to be clarified.
-The recent detections of GW events have brought us a new era of gravitational wave astronomy \citep[e.g.,][]{Abbott2016, Abbott2016_sum, Abbott2018} and opened up a  brand new possibility concerning studying BBH system formation channels.
+The recent detections of GW events have brought us a new era of gravitational wave astronomy \citep[e.g.,][]{Abbott2016, Abbott2016_sum, Abbott2018} and opened up a  brand new possibility in respect of studying BBH system formation channels.
 At present, however, observations cannot firmly select the basic formation scenarios like the evolution of isolated pairs of stars \citep{Bethe1998, Portegies1998}, chemically homogeneous evolution \citep{Marchant2016, deMink2016}, dynamic binary formation in dense clusters \citep{Portegies2000, Kulkarni1993} and other channels introduced in \citet{Abbott2018b}.
@@
 In the next decade, the number of detected coalescences of BBH systems is expected to be increasing rapidly with the improvements of the detector sensitivities.
-Especially, the third-generation gravitational wave detector Einstein Telescope (ET) is capable of \textbf{detecting $10^4-10^8$} \textbf{coalescing BBHs} per year \citep{Abernathy2011}.
-Moreover, since this instrument would detect the GW events from the distant Universe up to $z\sim17$ \citep{Abernathy2011}, the wide redshift range of the BBH \textbf{inspiral events} enable us to study the $\alpha$ as a function of redshift.
-In this study, we use the Monte Carlo (MC) approach to simulate the GW events from BBH \textbf{mergers} that could be measured by the ET.
-We construct a mock BBH \textbf{merger} catalog to examine their ability to constrain the BHMFs, taking into account the data noise level and selection bias realistically.
+Especially, the third-generation gravitational wave detector Einstein Telescope (ET) is capable of detecting $10^3-10^7$ BBHs per year \citep{Abernathy2011}.
+Moreover, since this instrument would detect the GW events from the distant Universe up to $z\sim17$ \citep{Abernathy2011}, the wide redshift range of the BBH events enable us to study the $\alpha$ as a function of redshift.
+In this study, we use the Monte Carlo (MC) approach to simulate the GW events from BBH systems that could be measured by the ET.
+We construct a mock BBH catalog to examine their ability to constrain the BHMFs, taking into account the data noise level and selection bias realistically.
 
 This paper is organized as follows.
-In Section~\ref{sec_simulation} we describe the simulation of the BBH \textbf{inspiral} events detectable by ET using the Monte Carlo approach.
+In Section~\ref{sec_simulation} we describe the simulation of the BBH events detectable by ET using the Monte Carlo approach.
 In this section, we assume the initial assumptions for the BH mass function used further as true values to be recovered from the data.
@@
 Numerical predictions of BBH inspirals detectable by ET
-have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of \textbf{order $\sim10^{4-8}$ \citep{Abernathy2011} or at least $\sim10^{5}$ according to less optimistic yet realistic scenarios\citep{Ola2013, Biesiada2014}}.
+have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of order $\sim10^{4-5}$ \citep{Abernathy2011, Ola2013, Biesiada2014}.
 More recently, \citet{Yang2019} developed the approach of a Monte Carlo (MC) simulation to predict the detection rate by explicitly considering each BBH inspiral event sampled from the outcome of the population synthesis model, which provides the way to mimic a realistic BBH GW catalog.
-The backbone of this approach is to use random seeds to build up a mock universe which includes a sufficient volume of BBH \textbf{inspiral} events with essential parameters that related to this study.
+The backbone of this approach is to use random seeds to build up a mock universe which includes a sufficient volume of BBH events with essential parameters that related to this study.
 We refer the readers for the details in \citet[][Section 2, therein]{Yang2019}  and briefly recall the key points below.
@@
 \subsection{Detection Criteria} \label{subsec_criteria}
-%We randomly generate the key parameters to determine the signal-to-noise ratio $\rho$ of each GW system. 
-For a specific BBH inspiral event at redshift $z_s$, the ET's corresponding signal-to-noise ratio $\rho$ is defined as \citep{Abernathy2011}:
+We randomly generate the key parameters to determine the signal-to-noise ratio $\rho$ of each GW system.
+For a specific BBH inspiral event at redshift $z_s$, the ET's corresponding reaction is defined as \citep{Abernathy2011}:
 
@@
 
-We aim to build up a sufficient volume of BBH systems in the mock universe by randomly generating the key parameters for each BBH system \textbf{as specified below.
-First key parameter is the redshift $z_s$.}  We sample the \textbf{merging BBH systems} according to the yearly merger rate in a redshift interval  $[z_{s}, z_{s}+dz_{s}]$:
+We aim to build up a sufficient volume of BBH systems in the mock universe by randomly generating the key parameters for each BBH system.
+We sample them according to the yearly merging rate in a redshift interval  $[z_{s}, z_{s}+dz_{s}]$:
  \begin{equation}
@@
 %Note that the cosmological model we adopted is comply with the one in \citet{Dominik13}.
-%For each BBH system, we sample the probability distribution of the key parameters to randomly generate their values. These 
-Other key parameters include the four angles $(\theta, \phi, \psi, \iota)$ in the Equation~(\ref{Theta})  and the masses of each BH in the binary system (i.e., \mone\ and \mtwo).
+For each BBH system, we sample the probability distribution of the key parameters to randomly generate their values.
+These key parameters include the four angles $(\theta, \phi, \psi, \iota)$ in the Equation~(\ref{Theta})  and the masses of each BH in the binary system (i.e., \mone\ and \mtwo).
 For the purpose of randomly generating the BH masses, we follow the previous works \citep{Kovetz2017PhRvD, Abbott2018b, Fishbach2018} and assume that \mone\ follows a power-law distribution with a hard cut at both maximum and minimum mass:
  \begin{equation} \label{equ_powlaw}
-P(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),
+p(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),
  \end{equation}
-where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo, is %fixed
-\textbf{sampled from a uniform distribution} 
-between $[M_{min}, m_1]$.
+where $\mathcal{H}$ is the Heaviside step function.
+Then, the secondary mass, \mtwo, is fixed as uniform between $[M_{min}, m_1]$.
 Let us note that, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ actually does not affect the inference for the shape of BHMF.
-\textbf{For the purpose of the simulation, however, all these parameters are necessary to} determine the value of $\Theta$ and ${\cal M}_0$ in Equation~(\ref{SNR}).
-We combine them with their redshift $z_s$ to generate the $\rho$ of each BBH \textbf{inspiraling} system.
+These parameters determine the value of $\Theta$ and ${\cal M}_0$ in Equation~(\ref{SNR}).
+We combine them with their redshift $z_s$ to generate the $\rho$ of each BBH system.
 We only collect the events which have $\rho > \rho_0 = 8$, meaning that those events with $\rho < 8$ are too faint to detect.
@@
 % \kai{From my view, I would parameterize $M_{max}$ and $M_{min}$ rather than the shape of mass function, it is like the CDM hieratical model. BH mass grows with time maybe?}
-so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$. \textbf{The above form is not motivated by any physical model.}
+so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$.
 This is actually the first order Taylor expansion in the scale factor $a(t)$ for any function.
@@
 
-\textbf{The parameters \it{measurable} from the BBH inspiral waveform comprised of \dl, redshifted chirp mass $(1+z){\cal M}_0 $ and $\rho$.} Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform.
-\textbf{Marek: Have we considered properly in the analysis that the measured masses are redshifted ones?}
+The parameters measurable from the BBH inspiral waveform comprised of \dl, chirp mass and $\rho$.
+Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform.
 As a recipe to set up the noise levels of our simulated data, we adopt the results of \citet{Ghosh2016}, who  explored the expected statistical uncertainties with which the parameters of black hole binaries can be measured from GW observations by next generation ground-based GW observatories.
@@
  \begin{equation} \label{equ_lognorm}
-P(m_1) = \frac{1}{m_1 \sigma_{m_1} \sqrt{2\pi}} exp \left[- \frac{log(m_1)-log(m_{1,fid})}{2\sigma_{m_1}} \right].
+p(m_1) = \frac{1}{m_1 \sigma_{m_1} \sqrt{2\pi}} exp \left[- \frac{log(m_1)-log(m_{1,fid})}{2\sigma_{m_1}} \right].
  \end{equation}
@@
  \begin{equation} \label{equ_lik_powlaw}
- P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} P(m_{1,i}|\alpha, M_{max}, M_{min})
+ P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} P(m_{1,i}|\alpha, M_{max}, M_{min}).
  \end{equation}
- \textbf{where $m{1,i}$ is the primary mass inferred from the $i-th$ GW event.}
 However, the median values of simulated \mone, as shown in Table~\ref{tab_GW_mock_data}, actually deviate from the initial power-law distribution.
@@
  \begin{equation} \label{equ_lik_conv}
- P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min}),
+ P(\alpha, M_{max}, M_{min}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min}),
  \end{equation}
@@
  \begin{equation} \label{equ_lik_sf}
- P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta},
+ P(\alpha, M_{max}, M_{min}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta},
  \end{equation}
@@
 In the previous section, we take \dl\ as the redshift estimator to derive the redshift and hence selection factor $\eta$.
-The way to derive the \textbf{inferred redshift $z_{inf}$} is an inverse solution of integral function when knowing the \dl$(z)$ and fixing the cosmological model.
+The way to derive the $z$ is an inverse solution of integral function when knowing the \dl$(z)$ and fixing the cosmological model.
 
@@
  \begin{split}
- P&(\alpha_0, \alpha_1, M_{max}, M_{min}|m_{1},d_L(z)) \propto \\
+ P&(\alpha_0, \alpha_1, M_{max}, M_{min}) \propto \\
   &\prod_{i=1}^{total} \hat{P}(m_{1i}, z_{inf,i} |\alpha_0, \alpha_1, M_{max}, M_{min})^{1/\eta}.

### 2020-02-20 projects/GW_BH_function/paper_draft/sec_edit_based_on_Marek_edit/bold_face/main_revised_bold.tex
Backup and clean house work

--- 2019-12-10 GW_BH_function/paper_draft/sec_edit_based_on_Marek_edit/main_revised.tex
@@
 \newcommand{\kai}[1]{\textcolor{red}{[{\bf Kai}: #1]}} 
-\newcommand{\blue}[1]{\textcolor{blue}{#1}} 
+\newcommand{\blue}[1]{{\bf #1}} 
 \newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
@@
 We use the mass of a primary black hole in each binary system to infer the BHMF as a power-law function with slope parameter as $\alpha$.
-Taking into account the bias that could be introduced by the uncertainty of measurements and by the selection effect, we \blue{carried out the numerical tests for three different sets of parameters and} find that only one thousand of GW events registered by ET ($\sim1\%$ amount of its yearly detection rate) could accurately infer the $\alpha$ \blue{with a precision of $\alpha\sim0.1$.
-Furthermore, assuming four sets of parameters, we investigate the validity of our method to recover a scenario where $\alpha$ evolves with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
-Our result shows, taking a thousand GW events and using \dl\ as the redshift estimator, one could infer the value of evolving parameter $\alpha_1$ accurately at the uncertainty level of $\sim0.5$.
-Our numerical tests verify the reliability of our method; however, the uncertainty levels of the inferred parameters only applies for the assumed sets of the parameters which shouldn't be considered as a universal value for the general case.
+Taking into account the bias that could be introduced by the uncertainty of measurements and by the selection effect, we \blue{carried out the numerical tests and} find that only one thousand of GW events registered by ET ($\sim1\%$ amount of its yearly detection rate) could accurately infer the $\alpha$ \blue{with a precision of $\alpha\sim0.1$.
+Furthermore, we investigate the validity of our method to recover a scenario where $\alpha$ evolves with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
+Taking a thousand of GW events and using \dl\ as the redshift estimator, our tests show that one could infer the value of evolving parameter $\alpha_1$ accurately with the uncertainty level of $\sim0.5$.
+Our numerical tests verify the reliability of our method.
+The uncertainty levels of the inferred parameters can be trusted directly for the several sets of the parameter we assumed, yet shouldn't be treated as a universal level for the general case.
 }
@@
 Current GWTC-1 catalog of binary coalescences detected by LIGO/Virgo GW interferometers includes ten BH-BH binaries and one NS-NS (GW170817) binary \citep{Abbott2018}.
-Assuming the BH mass function (BHMF) parametrized as a two-sided truncated power-law, \citet{Kovetz2017PhRvD} estimated that further LIGO measurements would provide thousands of BBHs and constrain the BHMF slope parameter $\alpha$ at 10\% precison.
+Assuming the BH mass function (BHMF) parametrized as a two-sided truncated power-law, \citet{Kovetz2017PhRvD} estimated that further LIGO measurements would provide thousands of BBHs and constrain the BHMF slope parameter $\alpha$ at 10\% {\bf precision}.
 More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF power-law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility) \citep{Abbott2018b}.
@@
 Numerical predictions of BBH inspirals detectable by ET
-have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of \textbf{order $\sim10^{4-8}$ \citep{Abernathy2011} or at least $\sim10^{5}$ according to less optimistic yet realistic scenarios\citep{Ola2013, Biesiada2014}}.
+have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of \textbf{order $\sim10^{4-8}$ \citep{Abernathy2011} or at least $\sim10^{5}$ according to less optimistic yet realistic scenarios \citep{Ola2013, Biesiada2014}}.
 More recently, \citet{Yang2019} developed the approach of a Monte Carlo (MC) simulation to predict the detection rate by explicitly considering each BBH inspiral event sampled from the outcome of the population synthesis model, which provides the way to mimic a realistic BBH GW catalog.
@@
  \end{equation}
-where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo, is %fixed
+where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo\, is %fixed
 \textbf{sampled from a uniform distribution} 
@@
 % \kai{From my view, I would parameterize $M_{max}$ and $M_{min}$ rather than the shape of mass function, it is like the CDM hieratical model. BH mass grows with time maybe?}
-so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$. \textbf{The above form is not motivated by any physical model.}
-This is actually the first order Taylor expansion in the scale factor $a(t)$ for any function.
+so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$.
+\textbf{We do not have any clear physical guidance of how could $\alpha$ evolve  with redshift and in particular which analytical expression would describe it reliably.
+Therefore the above ansatz is actually the first order Taylor expansion in the scale factor $a(t)$ applicable for any function.}
 
@@
 
-\textbf{The parameters \it{measurable} from the BBH inspiral waveform comprised of \dl, redshifted chirp mass $(1+z){\cal M}_0 $ and $\rho$.} Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform.
-\blue{We note the fact that LIGO detections usually infer the properties an asymmetry upper and lower limit with ${\it skewed}$ possibility distributions.
+\textbf{The quantities measurable from the BBH inspiral waveform comprised of \dl, redshifted chirp mass $(1+z){\cal M}_0 $ and $\rho$.} Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform.
+\blue{Let us note that physical quantities inferred from the LIGO detections had asymmetric upper and lower uncertainty limits, hence they followed the  ${\it skewed}$  distributions.
 Therefore, instead of the symmetric Gaussian distribution, we assume that the simulated mock measurements follow the Log-Normal distribution with the standard deviation of  ${\cal M}_0$, \dl, and \mone\ equal to 0.17, 0.35 and 0.2, respectively.}
-For instance, if the $m_{1,fid}$ is the true value for \mone, \blue{the probability density as used to simulate the measured value} is:
+For instance, if the $m_{1,fid}$ is the true value for \mone, \blue{the probability density used to simulate the measured value} is:
  \begin{equation} \label{equ_lognorm}
@@
  \end{equation}
-\blue{We set up the standard errors for ${\cal M}_0$, \dl, and \mone\ by taking results by \citet{Ghosh2016} as the reference, who explored the expected statistical uncertainties with which the parameters of black hole binaries can be measured from GW observations by next generation ground-based GW observatories.
-Note that the assumed uncertainty level of these properties should only affect the uncertainty (i.e., precision) of the inferred parameters, which wouldn't affect the validity (i.e., accuracy) test of our method.
+\blue{We set up the uncertainties for ${\cal M}_0$, \dl, and \mone\ by taking results of \citet{Ghosh2016} as the reference, who explored the expected statistical uncertainties with which the parameters of black hole binaries can be measured from GW observations by next generation ground-based GW observatories.
+Note that the assumed uncertainty level of these quantities only affect the uncertainty of the inferred parameters (i.e.
+the precision) and wouldn't affect the validity test of our method (i.e.
+the  accuracy).
 }
@@
 \tablewidth{0pt}
-\tablecaption{Illustration of the mock GW catalog} 
+\tablecaption{{\bf Illustration of the mock GW catalog}} 
 \tablehead{ 
@@
 \tablecomments{The catalog of simulated thousand BBH inspiral events is used to test the inference of the BHMF from the data attainable in forthcoming next generation GW detector -- the ET.
-The reported values are the medians, with errors corresponding to the 16th and 84th percentiles.
+The reported values are the medians, with errors corresponding to the 16th and 84th percentiles, {\bf assuming $\alpha=1.6$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~50M_{\odot}$.
+Note that this mock data is re-simulated every time in each realization}.
 }
@@
 The GW observations have a tendency to discover more significant events, known as Malmquist bias.
-\blue{For example, the} GW systems with higher values \mone\ \blue{trend to} produce stronger signals and thus have a higher probability to be detected.
+\blue{For example, the} GW systems with higher values \mone\ \blue{tend to} produce stronger signals and thus have a higher probability to be detected.
 \blue{As a result, the final BHMFs would be biased to the high mass end, if this effect is not correctly taken into account}.
@@
 In other words, four equivalent events would have been missed.
-Thus, for this event, one needs to re-calibrate \blue{this influence by enhancing the likelihood by a power of 5 (i.e., $L^{1/0.2} = L^5$) to recover the possibility to its intrinsic value.
+Thus, for this event, one needs to re-calibrate \blue{this influence by enhancing the likelihood by a power of 5 (i.e., $L^{1/0.2} = L^5$) to recover the intrinsic probability value.
 Hence, to account for the selection effect, we calculate the likelihood as:}
@@
 $\eta = P(\rho>8)$.
-In order to \blue{adopt the Equation~(\ref{SNR}) to derive the $\rho$}, the distribution function of $\Theta$ is \blue{taken} from the MC simulations; the \cmass\ and \dl\ are \blue{adopted from} the mock dataset as demonstrated in Table~\ref{tab_GW_mock_data}.
+In order to \blue{use the Equation~(\ref{SNR}) to calculate $\rho$}, the distribution function of $\Theta$ is \blue{taken} from the MC simulations; the \cmass\ and \dl\ are \blue{adopted from} the mock dataset as demonstrated in Table~\ref{tab_GW_mock_data}.
 Yet, the redshift $z_s$ is the unknown parameter since it is non-measurable in the GW detectors; one can only take the \dl\ as redshift estimator.
@@
 Considering the random distributions of the \dl\ and \cmass, we performed the numerical tests and found that the distribution of $1/\eta$ could be well described by the Log-Normal distribution with multiplicative standard deviation as $\sigma=-log(\eta_{\rm median})/3$, see Figure~\ref{fig_eta}.
-Note that in a Log-Normal distribution, the expected value are higher than the true value (i.e., median value) by a factor of $e^{\sigma^2/2}$.
-We consider this skewness and recalibrate the inferred expected value of $1/\eta$ into the median value, in order to assign a non-biased $1/\eta$ to the calculation.
+Let us remind that in a Log-Normal distribution, the expected value is higher than the true value (i.e., median value) by a factor of $e^{\sigma^2/2}$.
+We consider this skewness and recalibrate the inferred expected value of $1/\eta$ to the median value, in order to assign a non-biased $1/\eta$ to the calculation.
 }
@@
 \blue{
-Assuming a set of \dl\ and \cmass\ as Log-Normal distribution, we randomly produce the the corresponding histogram of the $1/\eta$ distribution.
+Assuming a set of \dl\ and \cmass\ following the Log-Normal distribution, we randomly produce the the corresponding histogram of the $1/\eta$ distribution.
 The result shows that the skewed distribution could be well described by a Log-Normal distribution with $\sigma = -\log(\eta_{\rm median})/3$.
@@
 In the previous section, we take \dl\ as the redshift estimator to derive the redshift and hence selection factor $\eta$.
-The way to derive the \textbf{inferred redshift $z_{inf}$} is an inverse solution of integral function when knowing the \dl$(z)$ and fixing the cosmological model.
+The way to derive the \textbf{inferred redshift $z_{inf}$} is an inverse solution of integral function knowing the \dl$(z)$ and fixing the cosmological model.
 
@@
 We find that all the parameters are recovered accurately which confirms the validity of our method.
-The uncertainties for the inferred parameters are $\Delta\alpha\sim0.1$, $\Delta M_{max}\sim1-2M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$.
-Note that these uncertainty levels are not ready to be treated as a universal for the general case, but only apply when the initial parameter sets are close to the tested ones.
-Moreover, these uncertainty levels are related to the standard deviation of the measurements including ${\cal M}_0$, \dl, and \mone, as discussed in Section~\ref{sec_noiselevel}.
+The uncertainties for the inferred parameters of 68\% confidence interval are $\Delta\alpha\sim0.1$, $\Delta M_{max}\sim1-3M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$.
+We also note that the uncertainty for $\Delta M_{max}$ increases with the increasing of $\alpha$.
+This is reasonable given that for higher $\alpha$ value, the black mass (i.e., $m_1$) trends to be distributed lower, resulting in a lower constraint power on the high mass end.
+Clearly, the uncertainty levels cannot be treated as the universal range for the general case, but only apply when the set of the initial parameters is close to the tested ones.
+Moreover, these uncertainty levels are related to the assumed measurement uncertainties, including ${\cal M}_0$, \dl, and \mone, as discussed in Section~\ref{sec_noiselevel}.
 }
@@
 \blue{We consider four sets of parameters assuming $\alpha_0$ as  0.8, 1.6, 2.4 and $\alpha_1$ including 0.7 and 1.2.
-We present the results in Figure~\ref{fig_result_b} and find that all the assumed parameters could be recovered accurately.
-With one more parameters included in the second scenario, the uncertainty level are extended as \ding{The following values still need to confirm} $\Delta\alpha_0\sim0.4$, $\Delta\alpha_1\sim0.5-0.7$, $\Delta M_{max}\sim2-4M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$.
-We note that there is a degeneracy between the $\alpha_0$ and $\alpha_1$, which is understandable given that they are strongly connected by the Equation~\ref{equ_alphaz}.
-However, for the four sets of parameters we tested, this degeneracy does not affect the inferred uncertainty level for the $\alpha_0$ and $\alpha_1$.
+We present the results in Figure~\ref{fig_result_b}.
+One can see that all the assumed parameters could be recovered accurately.
+With one more parameter included in the second scenario, the uncertainty level are the following: $\Delta\alpha_0\sim0.4$, $\Delta\alpha_1\sim0.5-0.7$, $\Delta M_{max}\sim2-4M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$.
+We note that there is a degeneracy between the $\alpha_0$ and $\alpha_1$, which is understandable given that they are strongly related by the Equation~\ref{equ_alphaz}.
+However, for the four sets of parameters we tested, this degeneracy does not affect the inferred uncertainty level for $\alpha_0$ and $\alpha_1$.
 }
@@
 \blue{Our result show that, with only one thousand of GW measurements in the future, the inferred value of $\alpha_1$ would reach to precision of $\Delta\alpha_1\sim0.5-0.7$.
-Limited by the computing power, we couldn't use numerical test to get a universal uncertainty level as for the general case.
-However, given the fours sets of tests as shown the Figure~\ref{fig_result_b}, it is likely to be true that one thousand of GW measurement could distinguish the evolution of BHMF at 1-$\sigma$ confidence level when $\alpha_1$ is deviated from 0 by a value of 0.5.
+Limited by the computing power, we couldn't use numerical test to get a universal uncertainty level for the general case.
+However, given the four sets of tests as shown the Figure~\ref{fig_result_b}, it is likely to be true that one thousand of GW measurement could distinguish the evolution of BHMF at 1-$\sigma$ confidence level when $\alpha_1$ deviated from 0 by a value of 0.5.
 Moreover, we conjecture that the precision of inference is increasing with the sample size as a function of $\sqrt{N}$.
-Thus, for the four sets of tests, the one year measurements of ET ($\sim10^5$ in total) would increase the uncertainty levels by a factor of 10.}
+Thus, for the four sets of tests, the one year measurements of ET ($\sim10^5$ in total) would decrease the uncertainty levels by a factor of 10.}
 We also note that the distribution of the best-fitted parameters ($\alpha_0$, $\alpha_1$) does not follow the Gaussian distribution, but rather a large fraction of it is concentrated at the center.
@@
 We performed the Monte Carlo simulation to estimate the uncertainty level of BHMF parameters inferred from GW signals by BBHs that would be detected by ET.
-As a starting point, we assumed that the BHMF for the primary BH mass followed a power-law distribution \blue{with a hard cuts as Equation~(\ref{equ_powlaw})}.
+As a starting point, we assumed that the BHMF for the primary BH mass followed a power-law distribution \blue{with hard cuts as described by Equation~(\ref{equ_powlaw})}.
 Based on the BBH intrinsic merger rate predicted by {\tt StarTrack}, we randomly simulated the key parameters of the BBH systems, including the chirp masses, redshifts and orientation factors and calculated  their corresponding signal-to-noise ratio \snr\ for the ET.
@@
 We took into account the measurement uncertainties and the selection effect which would bias the inference.
-We \blue{performed the test using realizations, one thousand GW events per realization}, and estimated the distribution of the best-fitted parameters of the BHMF, including the power-law slope $\alpha$, the maximum BH mass $M_{max}$ and the minimum BH mass $M_{min}$ \blue{in the first scenario}.
-Furthermore, \blue{in the second scenario, we consider the $\alpha$ evolves as a function of redshift and used the luminosity distance as redshift estimator to test the evolution}.
+We \blue{performed the test using realizations, one thousand GW events adopted per realization}, and estimated the distribution of the best-fitted parameters of the BHMF, including the power-law slope $\alpha$, the maximum BH mass $M_{max}$ and the minimum BH mass $M_{min}$ \blue{in the first scenario}.
+Furthermore, \blue{in the second scenario, we considered  $\alpha$ evolving as a function of redshift as described by Equation~(\ref{equ_alphaz}), and used the luminosity distance as redshift estimator to test this evolution}.
 We summarize our main results as follows:
@@
 \begin{enumerate}
-\item Using our method based on Equation~(\ref{equ_lik_sf}), all the tested parameters are all recovered accurately, which confirms the validity of our tests and highlights the importance of correctly considering the measurement uncertainty and selection effect.
-\item Taking the measured \dl\ as redshift estimator, we tested to recover the $\alpha$ with a scenario which is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
-Testing with four parameters sets, we are able to successfully recovered the true value of $\alpha_1$ accurately.
+\item Using our method based on Equation~(\ref{equ_lik_sf}), the tested parameters are all recovered accurately, as shown in Figure~\ref{fig_result_a}, which confirms the validity of our tests and highlights the importance of correctly considering the measurement uncertainty and selection effect.
+\item We assumed $\alpha$ within a scenario in which it is evolving with redshift as $\alpha(z) = \alpha_0 + \alpha_1\frac{z}{1+z}$.
+Taking the measured \dl\ as redshift estimator and testing with four parameter sets, we are able to recover the true value of $\alpha_1$ accurately, as shown in Figure~\ref{fig_result_b}.
 \item Given the fixed sets of parameters, our results show that a volume of one thousand measurements of BBHs events could infer the parameters with uncertainties level at $\Delta\alpha\sim0.1$, $\Delta M_{max}\sim1-2M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$ for the first scenario.
 For the second scenario, the inferred uncertainties are $\Delta\alpha_0\sim0.4$, $\Delta\alpha_1\sim0.5-0.7$, $\Delta M_{max}\sim2-4M_{\odot}$ and $\Delta M_{min}\sim0.2-0.3M_{\odot}$.
-In the future, the one year detection rate of ET ($\sim10^5$ in total) increase the sample size by a factor of 100.
-According to the fact that the precision of the inference increases with the sample size, as a function of $\sqrt{N}$, we conclude that one year BBH sample by ET would be able to deliver the parameters at higher uncertainty improved by a factor of 10 as tested.
+In the future, the one year detection rate of ET ($\sim10^5$ in total) would increase the sample size by a factor of 100.
+According to the fact that the precision of the inference increases with the sample size, as a function of $\sqrt{N}$, we conclude that one year BBH sample by ET would be able to deliver the parameters with uncertainties reduced by a factor of 10 with respect to these reported in this paper.
 \end{enumerate}
@@
 However, one can expect that these limitations would more strongly affect the prediction of the yearly detection rate of the GW events and their redshift distribution, rather than the inference of the parameters in the BHMF.
-\blue{Last, the numerical tests as done in this works confirms the validity of our method.
-However, limited by the sets of tests, the inferred uncertainty for both scenario applies for the fixed sets of parameters which shouldn't be considered as a general value.}
+\blue{At last, the numerical tests done in this work confirmed the validity of our method.
+However, limited by the sets of tests, the uncertainty of inferred parameters  in both scenarios applies directly to the fixed sets of parameters and shouldn't be applied to the general case.}
 
@@
 M.B. was supported by the Key Foreign Expert Program for the Central Universities No. X2018002.
-K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. {\bf 11973034}..
+K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. {\bf 11973034}.
 \software{  {\sc corner}, \citep{corner},

### 2020-02-20 projects/GW_BH_function/paper_draft/sec_edit_based_on_Marek_edit/main_revised.tex
Backup and clean house work

--- 2020-02-20 projects/GW_BH_function/paper_draft/sec_edit_based_on_Marek_edit/bold_face/main_revised_bold.tex
@@
 \newcommand{\kai}[1]{\textcolor{red}{[{\bf Kai}: #1]}} 
-\newcommand{\blue}[1]{{\bf #1}} 
+\newcommand{\blue}[1]{{#1}} 
 \newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
@@
 Current GWTC-1 catalog of binary coalescences detected by LIGO/Virgo GW interferometers includes ten BH-BH binaries and one NS-NS (GW170817) binary \citep{Abbott2018}.
-Assuming the BH mass function (BHMF) parametrized as a two-sided truncated power-law, \citet{Kovetz2017PhRvD} estimated that further LIGO measurements would provide thousands of BBHs and constrain the BHMF slope parameter $\alpha$ at 10\% {\bf precision}.
+Assuming the BH mass function (BHMF) parametrized as a two-sided truncated power-law, \citet{Kovetz2017PhRvD} estimated that further LIGO measurements would provide thousands of BBHs and constrain the BHMF slope parameter $\alpha$ at 10\% precision.
 More recently, the LIGO collaboration has used ten BBH merger events and constrained the BHMF power-law index to $\alpha~=~1.6\substack{+1.5\\-1.7}$ (90\% credibility) \citep{Abbott2018b}.
 In the next decade, the number of detected coalescences of BBH systems is expected to be increasing rapidly with the improvements of the detector sensitivities.
-Especially, the third-generation gravitational wave detector Einstein Telescope (ET) is capable of \textbf{detecting $10^4-10^8$} \textbf{coalescing BBHs} per year \citep{Abernathy2011}.
-Moreover, since this instrument would detect the GW events from the distant Universe up to $z\sim17$ \citep{Abernathy2011}, the wide redshift range of the BBH \textbf{inspiral events} enable us to study the $\alpha$ as a function of redshift.
-In this study, we use the Monte Carlo (MC) approach to simulate the GW events from BBH \textbf{mergers} that could be measured by the ET.
-We construct a mock BBH \textbf{merger} catalog to examine their ability to constrain the BHMFs, taking into account the data noise level and selection bias realistically.
+Especially, the third-generation gravitational wave detector Einstein Telescope (ET) is capable of detecting $10^4-10^8$ coalescing BBHs per year \citep{Abernathy2011}.
+Moreover, since this instrument would detect the GW events from the distant Universe up to $z\sim17$ \citep{Abernathy2011}, the wide redshift range of the BBH inspiral events enable us to study the $\alpha$ as a function of redshift.
+In this study, we use the Monte Carlo (MC) approach to simulate the GW events from BBH mergers that could be measured by the ET.
+We construct a mock BBH merger catalog to examine their ability to constrain the BHMFs, taking into account the data noise level and selection bias realistically.
 
 This paper is organized as follows.
-In Section~\ref{sec_simulation} we describe the simulation of the BBH \textbf{inspiral} events detectable by ET using the Monte Carlo approach.
+In Section~\ref{sec_simulation} we describe the simulation of the BBH inspiral events detectable by ET using the Monte Carlo approach.
 In this section, we assume the initial assumptions for the BH mass function used further as true values to be recovered from the data.
@@
 Numerical predictions of BBH inspirals detectable by ET
-have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of \textbf{order $\sim10^{4-8}$ \citep{Abernathy2011} or at least $\sim10^{5}$ according to less optimistic yet realistic scenarios \citep{Ola2013, Biesiada2014}}.
+have been discussed in many works, and it has been forecasted that the yearly detection rate of BBHs would be of order $\sim10^{4-8}$ \citep{Abernathy2011} or at least $\sim10^{5}$ according to less optimistic yet realistic scenarios \citep{Ola2013, Biesiada2014}.
 More recently, \citet{Yang2019} developed the approach of a Monte Carlo (MC) simulation to predict the detection rate by explicitly considering each BBH inspiral event sampled from the outcome of the population synthesis model, which provides the way to mimic a realistic BBH GW catalog.
-The backbone of this approach is to use random seeds to build up a mock universe which includes a sufficient volume of BBH \textbf{inspiral} events with essential parameters that related to this study.
+The backbone of this approach is to use random seeds to build up a mock universe which includes a sufficient volume of BBH inspiral events with essential parameters that related to this study.
 We refer the readers for the details in \citet[][Section 2, therein]{Yang2019}  and briefly recall the key points below.
@@
 %For each BBH system, we sample the probability distribution of the key parameters to randomly generate their values. These 
-{\bf Other key parameters include the four angles $(\theta, \phi, \psi, \iota)$ in the Equation~(\ref{Theta})  and the masses of each BH in the binary system (i.e., \mone\ and \mtwo).}
+Other key parameters include the four angles $(\theta, \phi, \psi, \iota)$ in the Equation~(\ref{Theta})  and the masses of each BH in the binary system (i.e., \mone\ and \mtwo).
 For the purpose of randomly generating the BH masses, we follow the previous works \citep{Kovetz2017PhRvD, Abbott2018b, Fishbach2018} and assume that \mone\ follows a power-law distribution with a hard cut at both maximum and minimum mass:
  \begin{equation} \label{equ_powlaw}
-{\bf P(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),}
+P(m_1|\alpha, M_{max}, M_{min}) = m_1^{\alpha} \mathcal{H}(m_1-M_{min}) \mathcal{H}(M_{max}-m_1),
  \end{equation}
 where $\mathcal{H}$ is the Heaviside step function. Then, the secondary mass, \mtwo\, is %fixed
-\textbf{sampled from a uniform distribution} 
+sampled from a uniform distribution
 between $[M_{min}, m_1]$.
 Let us note that, we only take the \mone\ to reconstruct the BHMF, thus the assumption of the distribution for \mtwo\ actually does not affect the inference for the shape of BHMF.
-\textbf{For the purpose of the simulation, however, all these parameters are necessary to} determine the value of $\Theta$ and ${\cal M}_0$ in Equation~(\ref{SNR}).
-We combine them with their redshift $z_s$ to generate the $\rho$ of each BBH \textbf{inspiraling} system.
+For the purpose of the simulation, however, all these parameters are necessary to determine the value of $\Theta$ and ${\cal M}_0$ in Equation~(\ref{SNR}).
+We combine them with their redshift $z_s$ to generate the $\rho$ of each BBH inspiraling system.
 We only collect the events which have $\rho > \rho_0 = 8$, meaning that those events with $\rho < 8$ are too faint to detect.
@@
 so that the $\alpha(z)$ would transform gradually from $\alpha_0$ to $\alpha_0+\alpha_1$ through low$-z$ to high$-z$.
-\textbf{We do not have any clear physical guidance of how could $\alpha$ evolve  with redshift and in particular which analytical expression would describe it reliably.
-Therefore the above ansatz is actually the first order Taylor expansion in the scale factor $a(t)$ applicable for any function.}
+We do not have any clear physical guidance of how could $\alpha$ evolve  with redshift and in particular which analytical expression would describe it reliably.
+Therefore the above ansatz is actually the first order Taylor expansion{, \bf assumption $\alpha$ as a function of the scale factor $a$, where $a(t) = \frac{1}{1+z}$.}
+%in the scale factor $a(t)$ applicable for any function.
 
@@
 
-\textbf{The quantities measurable from the BBH inspiral waveform comprised of \dl, redshifted chirp mass $(1+z){\cal M}_0 $ and $\rho$.} Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform.
+The quantities measurable from the BBH inspiral waveform comprised of \dl, redshifted chirp mass $(1+z){\cal M}_0 $ and $\rho$.
+Individual masses \mone\ and \mtwo\ are derived from the combination of the chirp mass and the total mass \mone+\mtwo, which can also be extracted from the chirp waveform.
 \blue{Let us note that physical quantities inferred from the LIGO detections had asymmetric upper and lower uncertainty limits, hence they followed the  ${\it skewed}$  distributions.
@@
 \tablewidth{0pt}
-\tablecaption{{\bf Illustration of the mock GW catalog}} 
+\tablecaption{Illustration of the mock GW catalog} 
 \tablehead{ 
@@
 \tablecomments{The catalog of simulated thousand BBH inspiral events is used to test the inference of the BHMF from the data attainable in forthcoming next generation GW detector -- the ET.
-The reported values are the medians, with errors corresponding to the 16th and 84th percentiles, {\bf assuming $\alpha=1.6$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~50M_{\odot}$.
+The reported values are the medians, with errors corresponding to the 16th and 84th percentiles, assuming $\alpha=1.6$, $M_{min}~=~5M_{\odot}$, $M_{max}~=~50M_{\odot}$.
 Note that this mock data is re-simulated every time in each realization}.
-}
 \end{deluxetable}
@@
 The intrinsic value of primary BH mass (i.e., $m_{1,fid}$) follows a power-law distribution, however the measured  \mone\ is scattered by the Log-Normal distribution which does not follow a power-law function anymore \citep{Koen2009}.
-In theory, if the event $X$ follows a power-law distribution and its observed values are subject to the Gaussian uncertainty, then $X + e$ is distributed according to the convolution of the power-law and Gaussian distributions.
-Likewise, given that the noised data follow the Log-Normal distribution, the intrinsic power-law should be convolved with it and enter the likelihood as:
+In theory, if the event $X$ follows a power-law distribution and its observed values are subject to the {\bf Log-Normal} uncertainty, then {\bf the observed event $X + e$ (where $e$ denote the error)} is distributed according to the convolution of the power-law and {\bf Log-Normal distributions.
+Assuming that the noised data follow the Log-Normal distribution, we convolved the the intrinsic power-law to describe likelihood as:}
  \begin{equation} \label{equ_lik_conv}
- P(\alpha, M_{max}, M_{min}{\bf |m_{1}}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min}),
+ P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min}),
  \end{equation}
@@
  \begin{equation} \label{equ_lik_sf}
- P(\alpha, M_{max}, M_{min}{\bf |m_{1}}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta},
+ P(\alpha, M_{max}, M_{min}|m_{1}) \propto  \prod_{i=1}^{total} \hat{P}(m_{1,i}|\alpha, M_{max}, M_{min})^{1/\eta},
  \end{equation}
@@
 \blue{Note that the observed \dl\ and \cmass\ are both considered to have random noise which follows the asymmetric distribution (i.e., Log-Normal).
-Thus, the distribution of their product $\eta$ is also asymmetric.
+Thus, the {\bf possibility distribution} of their product $\eta$ is also asymmetric.
 Considering the random distributions of the \dl\ and \cmass, we performed the numerical tests and found that the distribution of $1/\eta$ could be well described by the Log-Normal distribution with multiplicative standard deviation as $\sigma=-log(\eta_{\rm median})/3$, see Figure~\ref{fig_eta}.
@@
 \blue{
-Assuming a set of \dl\ and \cmass\ following the Log-Normal distribution, we randomly produce the the corresponding histogram of the $1/\eta$ distribution.
+Assuming a set of \dl\ and \cmass\ following the Log-Normal distribution, we randomly produce the the corresponding histogram of the $1/\eta$ {\bf to access its possibility distribution}.
 The result shows that the skewed distribution could be well described by a Log-Normal distribution with $\sigma = -\log(\eta_{\rm median})/3$.
@@
 In the previous section, we take \dl\ as the redshift estimator to derive the redshift and hence selection factor $\eta$.
-The way to derive the \textbf{inferred redshift $z_{inf}$} is an inverse solution of integral function knowing the \dl$(z)$ and fixing the cosmological model.
+The way to derive the inferred redshift {\bf $z_{inf}$ is to take the obtained luminosity distance, i.e.,  \dl$(z)$, and derive the inverse solution of integral function based on a fixed cosmological model.}
 
@@
 M.B. was supported by the Key Foreign Expert Program for the Central Universities No. X2018002.
-K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. {\bf 11973034}.
+K. Liao was supported by the National Natural Science Foundation of China (NSFC) No. 11973034.
 \software{  {\sc corner}, \citep{corner},

### 2020-02-20 GW_BH_function/create_figure2_eta_test.py

@@ -1,128 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Aug 20 10:10:46 2019
-
-@author: Dartoon
-
-Test the distribution of 
-"""
-import numpy as np
-import astropy.io.fits as pyfits
-import matplotlib.pyplot as plt
-
-import numpy as np
-import astropy.io.fits as pyfits
-import matplotlib.pyplot as plt
-import glob
-from BH_mass_function import gene_BHBH, dl, solve_z
-import time
-import pickle
-
-from cal_likelihood import poss_ln_gaussian
-
-solve_z = np.vectorize(solve_z)
-#a0, a1, mbh_max, mbh_min = 2.35, 0.1, 80., 5.
-a0, a1, mbh_max, mbh_min = 2.4, 0.7, 50., 5.   #mode1
-
-seed = 2
-#filename = 'test3_seed{0}_data'.format(seed)
-filename = 'sim_a0_{0}_a1_{1}_max_{2}'.format(a0, a1, mbh_max)
-if_file = glob.glob(filename)  
-if if_file==[]:
-    np.random.seed(seed)
-    test = gene_BHBH(h0=70)
-    event_rate, zs_detected, masses, rhos_detected = test.mc_year_rate(a=[a0, a1], mbh_max=mbh_max, mbh_min=mbh_min, ev_type = 'mode1')
-    dl_zs = dl(zs_detected)
-    sim_data = [event_rate, zs_detected, masses, rhos_detected, dl_zs]
-    pickle.dump(sim_data, open(filename, 'wb'))
-else:
-    event_rate, zs_detected, masses, rhos_detected, dl_zs=pickle.load(open(filename,'rb'))
-
-np.random.seed(seed)
-#event_rate0, zs_detected0, masses0, rhos_detected0 = test.mc_year_rate(a=a, mbh_max=mbh_max, mbh_min=mbh_min, ev_type = 'const')
-#event_rate1, zs_detected1, masses1, rhos_detected1 = test.mc_year_rate(a=[2.35,0.1], mbh_max=mbh_max, mbh_min=mbh_min, ev_type = 'mode0')
-#event_rate2, zs_detected2, masses2, rhos_detected2 = test.mc_year_rate(a=[a0, a1], mbh_max=mbh_max, mbh_min=mbh_min, ev_type = 'mode1')
-
[…]

### 2020-02-20 GW_BH_function/few_tests/test1_likeli_eachevent.py

@@ -1,98 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Mon Nov 26 21:57:36 2018
-
-@author: Dartoon
-
-Test if whether the likelihood would recover the para
-if all the m1 are measureable.
-With error bar
-"""
-import numpy as np
-import matplotlib.pyplot as plt
-import glob
-from BH_mass_function import BH_mass_function
-#from cal_likelihood import likelihood_lognorm as likelihood_i
-likelihood = np.vectorize(likelihood_i)
-from scipy.optimize import fmin
-import time
-t1 = time.time()
-a, mbh_max, mbh_min = 2.35, 80., 5.
-vol = 1000
-BHBH_mass = BH_mass_function(a = a, mbh_max=mbh_max, mbh_min=mbh_min, vol= vol)
-m_noise_level = 0.20     #The actually sigma_star is np.exp(0.2)
-
-use_method='med' #raw_input('Consider random.lognormal generate value is med or exp?:\n')
-
-if use_method == 'med':
-    filename = 'test1_conv_lognorm_{0}.txt'.format(int(m_noise_level*100))   #obsun means the std are from the obs data rather than true data
-#elif use_method == 'exp':
-#    filename = 'test2_1_trans_exp_obsun{0}.txt'.format(int(m_noise_level*100))
-
-def point_Chisq(para, m1_obs,m1_sig):
-    a,mbh_max,mbh_min  = para
-    if 1.1 < a < 3 and 50 < mbh_max < 100 and 2 < mbh_min < 8:
-        x = np.logspace(np.log10(m1_obs.min()/np.exp(m_noise_level)**5/1.1), np.log10(m1_obs.max()*np.exp(m_noise_level)**5*1.1),300)
-        y = cov_twofun(x, a=a, mbh_max=mbh_max, mbh_min=mbh_min,sigma=m_noise_level)
-        f = interpolate.interp1d(x, y)
-#        poss_m1_i = likelihood(m1_obs,m1_sig, a=a, mbh_max=mbh_max, mbh_min=mbh_min, use_method='med',f=f)
-        poss_m1_i = f(m1_obs)
-        chisq = -np.sum(np.log(poss_m1_i))
-#        print a, mbh_max, mbh_min, chisq
-        return chisq
-    else:
-        return np.inf
[…]

### 2020-02-20 GW_BH_function/for_Kai_create_mock_GW.py

@@ -1,185 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Mon Nov 26 21:57:36 2018
-
-@author: Dartoon
-
-Test if whether the likelihood would recover the para
-if all the m1 are measureable.
-With error bar
-"""
-
-
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Mon Nov 26 21:57:36 2018
-
-@author: Dartoon
-
-Generate the simulating data
-"""
-import numpy as np
-import astropy.io.fits as pyfits
-import matplotlib.pyplot as plt
-from BH_mass_function import gene_BHBH, dl, solve_z
-from cal_likelihood import fac_s_eff_v
-import pickle
-import glob
-import random
-import scipy.optimize as op
-import time
-
-a, mbh_max, mbh_min = 2.35, 80., 5.
-
-event_rate_list = []
-zs_all_list = []
-#%%
-sce = 2
-test = gene_BHBH(h0=70, rho0=0, m_type = 'BHBH', scenario=sce)
-event_rate, zs_detected, masses, rhos_detected = test.mc_year_rate(a=a, mbh_max=mbh_max, mbh_min=mbh_min, itera=5)
-zs_all, chirp_mass_all, m1_all, m2_all = zs_detected, masses[:,0], masses[:,1], masses[:,2]                                                      
-index = np.arange(len(m1_all))
-idx = random.sample(index, 5000)
-m1 = m1_all[idx]
-m2 = m2_all[idx]
-rho = rhos_detected[idx]
-zs = zs_all[idx]
-#save_filename = 'simulated_{0}_low_end.txt'.format(test.m_type)
-#save_file =  open(save_filename,'w') 
-#save_file.write("#zs, m1, m2, SNR, total_rate = {0:.3f} \n".format(event_rate)) 
-#for i in range(len(zs)):
-#    save_file.write("{0:.3f} {1:.3f} {2:.3f} {3:.3f}\n".format(zs[i],m1[i],m2[i], rho[i])) 
-#save_file.close() 
-#print  'simulated_{0}_low_end.txt'.format(test.m_type), event_rate
-zs_all_list.append(zs_all)
-event_rate_list.append(event_rate)
-#%%
-sce = 1
-test = gene_BHBH(h0=70, rho0=0, m_type = 'BHBH', scenario=sce)
[…]

### 2020-02-20 predict_GW/TDC/MC_td/em_nozs_LCDM.py

@@ -1,126 +1,0 @@
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-from tau import *
-
-##########to generate the lnPossible funtction, one need the Ka_square; P(zl|zs); P(zs).
-
-#########to get the P(zs):#################
-f=open('int_BHBH_sl.txt')
-gw=np.loadtxt(f)
-f.close
-num=len(gw)
-N=num
-ps=np.zeros([num,2])
-ps[:,0]=gw[:,0]
-ps[:,1]=gw[:,1]   
-def Ps(zl,zs):     #the zl is for define zl<zs
-    p_bef=np.trim_zeros(ps[:,1]*(zl>=ps[:,0]))[-1]
-    p_af=np.trim_zeros(ps[:,1]*(zs>=ps[:,0]))[-1]
-    p=p_af/(p_af+p_bef)
-    return p
-#print Ps(0.0001)
-
-vec_Ps=np.vectorize(Ps)
-#######to get the P(zl|zs):##################
-
-men=np.zeros([len(ps),2,501])
-for i in range(len(ps)):    #creat a mem for fast cal
-    men[i]=tau(ps[i,0])
-def Pl(zl,zs):
-    (a,b)=men[np.sum(zs>ps[:,0])-1]
-    #(a,b)=tau(zs)
-    p_va=np.trim_zeros(b*(zl>=a))[-1]/(len(a)-1)
-    return p_va
-print Pl(0.8,0.4)
-vec_Pl=np.vectorize(Pl)
-
-#######to get the ka^2############################
-c=299790.
-def Ez(z,om):
-  return   1/np.sqrt(om*(1+z)**3+(1-om))
-def r(z,om):
-  return integrate.quad(Ez, 0, z, args=(om))[0]    #use the cos distance r
-vec_r=np.vectorize(r)
-f=open('TD_result50','r')
-data=np.loadtxt(f)
-f.close()
-N_p=len(data)
-
-zl=data[:,1]
-zs=data[:,0]
-y=data[:,3]
-err=data[:,4]
-##########def lnlike######################
-
-def lnlike(theta, zl, y, err):    #allow zs to be 2D to get 2D sub_int, from (len(data)) to (len(data),133)
-    om, h0 =theta[:2]
-    zs=theta[2:]
-    rzl=vec_r(zl,om)
-    rzs=vec_r(zs,om)
-    model = c*rzl*(rzs-rzl)/rzs/h0
-    #print np.shape(rzl),np.shape(model)
[…]

### 2020-02-20 predict_GW/TDC/MC_td/emc_int_LCDM.py

@@ -1,166 +1,0 @@
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-from tau import *
-
-##########to generate the lnPossible funtction, one need the Ka_square; P(zl|zs); P(zs).
-
-#########to get the P(zs):#################
-f=open('int_BHBH_sl.txt')
-gw=np.loadtxt(f)
-f.close
-num=len(gw)
-N=num
-ps=np.zeros([num,2])
-ps[:,0]=gw[:,0]
-ps[:,1]=gw[:,1]   #not the real possibility should mutply by p(i)-p(i-1)
-def Ps(zs):
-    p_va=np.trim_zeros(ps[:,1]*(zs>=ps[:,0]))[-1]
-    return p_va*(zs<30)
-#print Ps(30)
-vec_Ps=np.vectorize(Ps)
-#######to get the P(zl|zs):##################
-
-men=np.zeros([len(ps),2,501])
-for i in range(len(ps)):    #creat a mem for fast cal
-    men[i]=tau(ps[i,0])
-def Pl(zl,zs):
-    (a,b)=men[np.sum(zs>ps[:,0])-1]
-    #(a,b)=tau(zs)
-    p_va=np.trim_zeros(b*(zl>=a))[-1]/(len(a)-1)
-    return p_va
-vec_Pl=np.vectorize(Pl)
-############to inter the likehood with zs############
-num=len(gw)
-N=num
-z_sca=np.zeros(num)
-z_sca=gw[:,0]
-
-f=open('TD_result','r')
-data=np.loadtxt(f)
-f.close()
-N_p=len(data)
-zl=data[:,1]
-zs=data[:,0]
-y=data[:,3]
-err=data[:,4]
-
-def ct_zs(zl):                  #creat the zs array corrsponding to the zl, get the zs after zl in z_sca scale
-    z_s=np.ones([len(zl),len(z_sca)])
-    for i in range(len(zl)):
-       z_s[i]=(z_sca*[zl[i]<z_sca])[0]
-    z_s=z_s+30*np.ones(np.shape(z_s))*[z_s==0][0]
-    return z_s
-
-z_s=ct_zs(zl=data[:,1])
-#print np.shape(z_s),np.shape(data[:,0])
-#print ct_zs(zl=data[:,1])
-#print sub_like(theta=[0.3,70], zs=ct_zs(zl=data[:,1]), zl=data[:,1], y=data[:,3], err=data[:,4])
-
-################to get the ka^2 and combine together to get likehood for one data###################
[…]

### 2020-02-20 predict_GW/TDC/MC_td/load_noint_LCDM.py

@@ -1,30 +1,0 @@
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-
-import pickle
-#sampler=pickle.load(open('samp.txt','rb'))
-ndim, nwalkers =52, 200
-#samples = sampler.chain[:, 50:, :].reshape((-1, ndim))
-
-
-#plt.plot(sampler.chain[:,:,0].T, '-', color='k', alpha=0.3)
-#plt.axhline(0.3, color='blue')
-samples,burn=pickle.load(open('samp_nozs_50.txt','rb'))
-#print np.shape(samples[50*ndim*nwalkers:])
-
-#m_true = -0.9594
-#b_true = 4.294
-#f_true = 0.534
-print samples.shape
-
-plt.plot(burn[0], '-', color='k', alpha=0.3)
-#plt.axhline(4.294, color='blue')
-
-
-import corner
-fig = corner.corner(samples[:,:2], labels=["$b0$", "$b1$"],
-                      truths=[0.3,70])
-
-plt.show()
-

### 2020-02-20 predict_GW/TDC/MC_td/load_samp.py

@@ -1,28 +1,0 @@
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-
-import pickle
-#sampler=pickle.load(open('samp.txt','rb'))
-ndim, nwalkers =2, 100
-#samples = sampler.chain[:, 50:, :].reshape((-1, ndim))
-
-
-#plt.plot(sampler.chain[:,:,0].T, '-', color='k', alpha=0.3)
-#plt.axhline(0.3, color='blue')
-samples,burn=pickle.load(open('samp.txt','rb'))
-#print np.shape(samples[50*ndim*nwalkers:])
-
-#m_true = -0.9594
-#b_true = 4.294
-#f_true = 0.534
-
-
-plt.plot(burn[1], '-', color='k', alpha=0.3)
-#plt.axhline(4.294, color='blue')
-
-import corner
-fig = corner.corner(samples, labels=["$b0$", "$b1$"],
-                      truths=[0.3,70])
-
-plt.show()

### 2020-02-20 predict_GW/TDC/MC_td/no_zs/emc_int_wCDM.py

@@ -1,169 +1,0 @@
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-from tau import *
-
-##########to generate the lnPossible funtction, one need the Ka_square; P(zl|zs); P(zs).
-
-#########to get the P(zs):#################
-f=open('../int_BHBH_sl.txt')
-gw=np.loadtxt(f)
-f.close
-num=len(gw)
-N=num
-ps=np.zeros([num,2])
-ps[:,0]=gw[:,0]
-ps[:,1]=gw[:,1]   #not the real possibility should mutply by p(i)-p(i-1)
-def Ps(zs):
-    p_va=np.trim_zeros(ps[:,1]*(zs>=ps[:,0]))[-1]
-    return p_va*(zs<30)
-#print Ps(30)
-vec_Ps=np.vectorize(Ps)
-#######to get the P(zl|zs):##################
-
-men=np.zeros([len(ps),2,501])
-for i in range(len(ps)):    #creat a mem for fast cal
-    men[i]=tau(ps[i,0])
-def Pl(zl,zs):
-    (a,b)=men[np.sum(zs>ps[:,0])-1]
-    #(a,b)=tau(zs)
-    p_va=np.trim_zeros(b*(zl>=a))[-1]/(len(a)-1)
-    return p_va
-vec_Pl=np.vectorize(Pl)
-#print Pl(1,15)
-############to inter the likehood with zs############
-num=len(gw)
-N=num
-z_sca=np.zeros(num)
-z_sca=gw[:,0]
-
-f=open('TD_result100','r')
-data=np.loadtxt(f)
-f.close()
-N_p=len(data)
-zl=data[:,1]
-zs=data[:,0]
-y=data[:,3]
-err=data[:,4]
-
-def ct_zs(zl):                  #creat the zs array corrsponding to the zl, get the zs after zl in z_sca scale
-    z_s=np.ones([len(zl),len(z_sca)])
-    for i in range(len(zl)):
-       z_s[i]=(z_sca*[zl[i]<z_sca])[0]
-    z_s=z_s+30*np.ones(np.shape(z_s))*[z_s==0][0]
-    return z_s
-
-z_s=ct_zs(zl=data[:,1])
-#print np.shape(z_s),np.shape(data[:,0])
-#print ct_zs(zl=data[:,1])
-#print sub_like(theta=[0.3,70], zs=ct_zs(zl=data[:,1]), zl=data[:,1], y=data[:,3], err=data[:,4])
-
[…]

### 2020-02-20 predict_GW/TDC/MC_td/no_zs/load_samp.py

@@ -1,38 +1,0 @@
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-import pickle
-import corner
-
-select= input('of which models results to be presented? 0--LCDM;1--wCDM;2:CPL:   ')
-if select == 0:
-   ndim, nwalkers =2, 50
-   sampler,burn=pickle.load(open('int_LCDM_500.txt','rb'))
-   plt.plot(burn[0,50:,:], '-', color='k', alpha=0.3)  #show the chain after 50 steps 
-   #plt.axhline(4.294, color='blue')
-   samples=sampler[:, 50:, :].reshape((-1, ndim))
-   print samples.shape
-   fig = corner.corner(samples, labels=["$om$", "$h0$"], truths=[0.3,70],
-                       quantiles=[0.16, 0.5, 0.84],  #quantiles shows 1D possiblity region
-                       show_titles=True, title_kwargs={"fontsize": 12}) 
-if select == 1:
-   ndim, nwalkers =3, 50
-   sampler,burn=pickle.load(open('int_wCDM_500.txt','rb'))
-   plt.plot(burn[0,50:,:], '-', color='k', alpha=0.3)  #show the chain after 50 steps 
-   #plt.axhline(4.294, color='blue')
-   samples=sampler[:, 50:, :].reshape((-1, ndim))
-   print samples.shape
-   fig = corner.corner(samples, labels=["$om$", "$w$", "$h0$"], truths=[0.3, -1, 70],
-                       quantiles=[0.16, 0.5, 0.84],  #quantiles shows 1D possiblity region
-                       show_titles=True, title_kwargs={"fontsize": 12}) 
-if select == 2:
-   ndim, nwalkers =4, 50
-   sampler,burn=pickle.load(open('int_CPL_500.txt','rb'))
-   plt.plot(burn[0,:,:], '-', color='k', alpha=0.3)  #show the chain after 50 steps 
-   #plt.axhline(4.294, color='blue')
-   samples=sampler[:, 50:, :].reshape((-1, ndim))
-   print samples.shape
-   fig = corner.corner(samples, labels=["$om$", "$w0$", "wa", "$h0$"], truths=[0.3, -1, 0, 70],
-                       quantiles=[0.16, 0.5, 0.84],  #quantiles shows 1D possiblity region
-                       show_titles=True, title_kwargs={"fontsize": 12})
-plt.show()

### 2020-02-20 predict_GW/TDC/MC_td/no_zs/recall.py

@@ -1,124 +1,0 @@
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-from tau import *
-
-##########to generate the lnPossible funtction, one need the Ka_square; P(zl|zs); P(zs).
-
-#########to get the P(zs):#################
-f=open('../int_BHBH_sl.txt')
-gw=np.loadtxt(f)
-f.close
-num=len(gw)
-N=num
-ps=np.zeros([num,2])
-ps[:,0]=gw[:,0]
-ps[:,1]=gw[:,1]   #not the real possibility should mutply by p(i)-p(i-1)
-def Ps(zs):
-    p_va=np.trim_zeros(ps[:,1]*(zs>=ps[:,0]))[-1]   #zs can be any number now, the Ps will be respesented the nearby zs
-    return p_va*(zs<30)
-#print Ps(30)
-vec_Ps=np.vectorize(Ps)
-#######to get the P(zl|zs):##################
-
-men=np.zeros([len(ps),2,501])  #501 is the tau scale
-for i in range(len(ps)):    #creat a mem for fast cal
-    men[i]=tau(ps[i,0])
-def Pl(zl,zs):
-    (a,b)=men[np.sum(zs>ps[:,0])-1]  #the possibility distributino tau(zs)
-    #(a,b)=tau(zs)
-    p_va=np.trim_zeros(b*(zl>=a))[-1]/(len(a)-1)  #the possibility for zl when zs is given
-    return p_va
-vec_Pl=np.vectorize(Pl)
-############to inter the likehood with zs############
-num=len(gw)
-N=num
-z_sca=np.zeros(num)
-z_sca=gw[:,0]
-
-f=open('TD_result_1st_500','r')
-data=np.loadtxt(f)
-f.close()
-N_p=len(data)
-zl=data[:,1]
-zs=data[:,0]
-y=data[:,3]
-err=data[:,4]
-
-def ct_zs(zl):                 #creat a zs array above to the zl, get the zs after zl in z_sca scale, the other z_s set to 30
-    z_s=np.ones([len(zl),len(z_sca)])
-    for i in range(len(zl)):
-       z_s[i]=(z_sca*[zl[i]<z_sca])[0]
-    z_s=z_s+30*np.ones(np.shape(z_s))*[z_s==0][0]
-    return z_s
-
-z_s=ct_zs(zl=data[:,1])
-#print np.shape(z_s),np.shape(data[:,0])
[…]

### 2020-02-20 predict_GW/TDC/MC_td/no_zs/tau.py

@@ -1,31 +1,0 @@
-from scipy.integrate import quad
-import numpy as np
-from scipy.special import gamma
-import matplotlib.pyplot as plt
-def tau(zs):       
-      c=299790.      #speed of light [km/s]
-      H=70
-      om=0.3
-      dH=c/H
-      H0=H*1000./(3.0856e22)
-      phi0=8.0e3-3*(H/100)**3
-      sig0=161
-      alpha=2.32
-      bet=2.67
-      TFactor = (sig0/c)**4*phi0*gamma((4.+alpha)/bet)/gamma(alpha/bet); 
-      #print TFactor
-      def EZ(z,om):
-            return 1/(om*(1+z)**3+(1-om))**0.5
-      def EE(z):
-            return quad(EZ, 0, z , args=(om))[0]
-      vec_EE=np.vectorize(EE)
-      #print vec_Dist(np.arange(1.0, 4.0, 0.5))
-      #zs=2              #input
-      zl=np.linspace(0,zs,501)
-      Dist=vec_EE(zl)
-      #print np.shape(Dist),Dist[100]
-      dtaudz=16*np.pi**3*dH**3*(Dist[500]-Dist)**2*Dist**2/Dist[500]**2*TFactor/EZ(zl,om) #*ymax^2
-      dtaudz/= dtaudz.sum()
-      #plt.plot(zl,dtaudz,'k')
-      #plt.show()
-      return (zl,dtaudz)

### 2020-02-20 predict_GW/TDC/MC_td/with_zs/em_TD_LCDM.py

@@ -1,73 +1,0 @@
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-c=299790.
-def Ez(z,om):
-  return   1/np.sqrt(om*(1+z)**3+(1-om))
-def r(z,om):
-  return integrate.quad(Ez, 0, z, args=(om))[0]    #use the cos distance r
-
-vec_r=np.vectorize(r)
-f=open('TD_result500','r')
-data=np.loadtxt(f)
-f.close()
-zl=data[:,1]
-zs=data[:,0]
-y=data[:,3]
-err=data[:,4]
-'''
-om=0.3
-h0=70
-model = c*vec_EE(data[:,1])*(vec_EE(data[:,0])-vec_EE(data[:,1]))/vec_EE(data[:,0])/h0
-print model
-'''
-
-def lnlike(theta, zl, zs, y, err):
-    om, h0 = theta
-    #print theta
-    #model = om*z +h0
-    model = c*vec_r(zl,om)*(vec_r(zs,om)-vec_r(zl,om))/vec_r(zs,om)/h0
-    return -0.5*(np.sum((y-model)**2/err**2))
-#import scipy.optimize as op
-#nll = lambda *args: -lnlike(*args)
-#result = op.minimize(nll, [0.25,70], args=(zl, zs, y, err))
-#m_om, m_h0 = result["x"]
-#print m_om, m_h0
-
-###MCMC###
-def lnprior(theta):
-    om, h0 = theta
-    if 0.2 < om < 0.45 and 55 < h0 < 85:
-        return 0.0
-    return -np.inf
-
-def lnprob(theta, zl, zs, y, yerr):
-    lp = lnprior(theta)
-    step=np.sum(sampler.flatchain!=0)/(ndim*nwalkers)
-    print "step:",step,"percent",round(step/5.,2),"%","\r","theta:",theta,
-    if not np.isfinite(lp):
-        return -np.inf
-    return lp + lnlike(theta, zl, zs, y, err)
-ndim, nwalkers = 2, 50
-pos = [[0.30, 70] + 1e-4*np.random.randn(ndim) for i in range(nwalkers)]
-
-import emcee
-sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=(zl, zs, y, err))  ###the input args() should change
-sampler.run_mcmc(pos, 500)
-
-###############save the data###############
[…]

### 2020-02-20 predict_GW/TDC/MC_td/with_zs/load_samp.py

@@ -1,38 +1,0 @@
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-import pickle
-import corner
-
-select= input('of which models results to be presented? 0--LCDM;1--wCDM;2:CPL:   ')
-if select == 0:
-   ndim, nwalkers =2, 50
-   sampler,burn=pickle.load(open('eas_500_LCDM.txt','rb'))
-   plt.plot(burn[0,50:,:], '-', color='k', alpha=0.3)  #show the chain after 50 steps 
-   #plt.axhline(4.294, color='blue')
-   samples=sampler[:, 50:, :].reshape((-1, ndim))
-   print samples.shape
-   fig = corner.corner(samples, labels=["$\Omega_{m0}$", "$H_0$"], truths=[0.3,70],
-                       quantiles=[0.16, 0.5, 0.84],  #quantiles shows 1D possiblity region
-                       show_titles=True, title_kwargs={"fontsize": 12}) 
-if select == 1:
-   ndim, nwalkers =3, 50
-   sampler,burn=pickle.load(open('eas_500_wCDM.txt','rb'))
-   plt.plot(burn[0,50:,:], '-', color='k', alpha=0.3)  #show the chain after 50 steps 
-   #plt.axhline(4.294, color='blue')
-   samples=sampler[:, 50:, :].reshape((-1, ndim))
-   print samples.shape
-   fig = corner.corner(samples, labels=["$\Omega_{m0}$", "$w$", "$H_0$"], truths=[0.3, -1, 70],
-                       quantiles=[0.16, 0.5, 0.84],  #quantiles shows 1D possiblity region
-                       show_titles=True, title_kwargs={"fontsize": 12}) 
-if select == 2:
-   ndim, nwalkers =4, 50
-   sampler,burn=pickle.load(open('eas_500_CPL.txt','rb'))
-   plt.plot(burn[0,50:,:], '-', color='k', alpha=0.3)  #show the chain after 50 steps 
-   #plt.axhline(4.294, color='blue')
-   samples=sampler[:, 50:, :].reshape((-1, ndim))
-   print samples.shape
-   fig = corner.corner(samples, labels=["$\Omega_0$", "$w0$", "wa", "$H_0$"], truths=[0.3, -1, 0, 70],
-                       quantiles=[0.16, 0.5, 0.84],  #quantiles shows 1D possiblity region
-                       show_titles=True, title_kwargs={"fontsize": 12})
-plt.show()

### 2020-02-20 predict_GW/TDC/NA_test/min_test_TD_LCDM.py

@@ -1,76 +1,0 @@
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-import pickle
-
-error= input('Which error level to set? in % unit:')
-'''
-c=299790.
-def Ez(z,om):
-  return   1/np.sqrt(om*(1+z)**3+(1-om))
-def r(z,om):
-  return integrate.quad(Ez, 0, z, args=(om))[0]    #use the cos distance r
-H=70
-om=0.3
-c=299790.        #speed of light [km/s]
-
-vec_r=np.vectorize(r)
-f=open('zl_zs','r')
-data=np.loadtxt(f)
-f.close()
-zl=data[:,0]
-zs=data[:,1]
-#y=data[:,3]
-#err=data[:,4]
-
-#####simulate the data######
-y=c*vec_r(zl,om)*vec_r(zs,om)/(vec_r(zs,om)-vec_r(zl,om))/H
-erbar=y*error/100.
-bias=np.random.normal(0,erbar)   ##include system error to the data
-dt=y+bias
-#print zl, zs,y,erbar,dt
-
-def lnlike(theta, zl, zs, dt, erbar):
-    om, h0 = theta
-    #print theta
-    #model = om*z +h0
-    model = c*vec_r(zl,om)*vec_r(zs,om)/(vec_r(zs,om)-vec_r(zl,om))/h0
-    return -0.5*(np.sum((dt-model)**2./erbar**2.))
-import scipy.optimize as op
-nll = lambda *args: -lnlike(*args)
-#result = op.minimize(nll, [0.25,70], args=(zl, zs, y, erbar))
-#m_om, m_h0 = result["x"]
-bnds = ((-0.5, 1), (0, 100))
-result = op.minimize(nll, (0.30, 70), method='SLSQP', bounds=bnds,args=(zl, zs, dt, erbar))
-print result["x"].shape
-
-group=10000
-para=np.zeros([group,2])
-for i in range(group):
-  dt=y+np.random.normal(0,erbar)
-  result = op.minimize(nll, (0.30, 70), method='SLSQP', bounds=bnds,args=(zl, zs, dt, erbar))
-  para[i,:]=result["x"]
-  if i%100==0:
-    print i/100.
-#print para[:,0]
-
-###############save the data###############
-
-pickle.dump(para, open("error_%s"%(error),'wb'))
-'''
-
-###############load the data##############
[…]

### 2020-02-20 predict_GW/TDC/simu_TD/color_test.py

@@ -1,17 +1,0 @@
-from pylab import *
-
-# Generate some random data that looks like yours
-N = 1000
-X = random(N)
-Y = sin(X*5) + X*random(N)*.8
-Z = random(N)
-ERR = X*random(N)
-
-# These are the new arguments that I used
-scatter_kwargs = {"zorder":100}
-error_kwargs = {"lw":.5, "zorder":0}
-
-scatter(X,Y,c=Z,**scatter_kwargs)
-errorbar(X,Y,yerr=ERR,fmt=None, marker=None, mew=0,**error_kwargs )
-xlim(0,1)
-show()

### 2020-02-20 predict_GW/TDC/simu_TD/tau_plot.py

@@ -1,55 +1,0 @@
-from scipy.integrate import quad
-import numpy as np
-from scipy.special import gamma
-import matplotlib.pyplot as plt
-c=299790.#speed of light [km/s]
-H=70
-om=0.3
-w=-1
-dH=c/H
-H0=H*1000./(3.0856e22)
-phi0=8.0e3-3*(H/100)**3
-sig0=161
-alpha=2.32
-bet=2.67
-TFactor = (sig0/c)**4*phi0*gamma((4.+alpha)/bet)/gamma(alpha/bet); 
-#print TFactor
-def EZ(z,om):
-   return 1/(om*(1+z)**3+(1-om))**0.5
-def EE(z):
-   return quad(EZ, 0, z , args=(om))[0]
-vec_EE=np.vectorize(EE)
-#print vec_Dist(np.arange(1.0, 4.0, 0.5))
-
-zs=5  #input
-zl=np.linspace(0,zs,1001)
-Dist=vec_EE(zl)
-#print np.shape(Dist),Dist[100]
-dtaudz=16*np.pi**3*dH**3*(Dist[1000]-Dist)**2*Dist**2/Dist[1000]**2*TFactor#/EZ(zl,om) #*ymax^2
-#dtaudz/= dtaudz.sum()
-plt.plot(zl,dtaudz,'k')
-
-zs=2  #input
-zl=np.linspace(0,zs,1001)
-Dist=vec_EE(zl)
-#print np.shape(Dist),Dist[100]
-dtaudz=16*np.pi**3*dH**3*(Dist[1000]-Dist)**2*Dist**2/Dist[1000]**2*TFactor#/EZ(zl,om) #*ymax^2
-#dtaudz/= dtaudz.sum()
-plt.plot(zl,dtaudz,'k')
-
-zs=3  #input
-zl=np.linspace(0,zs,1001)
-Dist=vec_EE(zl)
-#print np.shape(Dist),Dist[100]
-dtaudz=16*np.pi**3*dH**3*(Dist[1000]-Dist)**2*Dist**2/Dist[1000]**2*TFactor#/EZ(zl,om) #*ymax^2
-#dtaudz/= dtaudz.sum()
-plt.plot(zl,dtaudz,'k')
-
-zs=1  #input
-zl=np.linspace(0,zs,1001)
-Dist=vec_EE(zl)
-#print np.shape(Dist),Dist[100]
[…]

### 2020-02-20 predict_GW/TDC/test.sh

@@ -1,14 +1,0 @@
-#!/bin/bash
-echo "Hello World !"
-name='xuheng'
-echo $name
-echo "$name"
-echo \{$name\}
-for skill in Ada Coffe Action Jave;do
-    echo "I am good at ${skill}Script"
-done
-
-your_name="qinjx"
-greeting="hello, "$your_name" !"
-greeting_1="hello, ${your_name} !"
-echo $greeting $greeting_1

### 2020-02-20 predict_GW/TDC/time.py

@@ -1,21 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-
-
-xh=np.arange(0,24,1)
-xg=np.roll(xh,-15)
-mk=np.roll(xh,-9)
-xg=xg[(xh<1)+(xh>7)]
-mk=mk[(xh<1)+(xh>7)]
-xh=xh[(xh<1)+(xh>7)]
-print 'xh time in L.A. :  {0}\r;'.format(xh)
-print 'mk time in Porland:{0}\r;'.format(mk)
-print 'xg time in BJ:     {0}\r;'.format(xg)
-l=len(xh)
-plt.plot(xh,xh, 'o')
-plt.plot(mk,xh, '*')
-plt.plot(xg,xh, 'r.')
-plt.plot(np.linspace(0,24,50),8+np.zeros(50))
-plt.xlim([0,24])
-plt.show()

### 2020-02-20 predict_GW/standard_siren/minima/LCDM/LCDM_minima_fix_Om.py

@@ -1,110 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Sat Mar 31 16:23:04 2018
-
-@author: dartoon
-"""
-
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-import sys
-sys.path.insert(0,'../')
-from pz import pz
-from gene_data import gene_data
-##########to generate the lnPossible funtction, one need the Ka_square; P(zl|zs); P(zs).
-#########to get the P(zs):#################
-om=0.3
-h0=70
-ps=pz(om,h0)
-zs=ps[:,0]
-
-scenario = input("Which scenario?")
-################to get the ka^2 and combine together to get likehood for one data###################
-c=299790.
-def Ez(z,om):
-  return   1/np.sqrt(om*(1+z)**3+(1-om))
-def r(z,om):
-    return integrate.quad(Ez, 0, z, args=(om))[0]    #use the cos distance r
-vec_r=np.vectorize(r)
-
-def twod_like(theta, y, err):    #set zs to be 2D to get 2D sub_int, from (len(data)) to (len(data),133)
-    h0 =theta
-    om = 0.3
-    rzs=vec_r(zs,om)
-    model = (1+zs)*c*rzs/h0             #133 numbers of the models
-    ps=pz(om,h0,scenario=scenario)
-    likh = np.exp(-0.5*(pow((y[:,None]-model),2)/pow(err[:,None],2)))*ps[:,1]
-    return likh
-ddz=ps[:,0][1:]-ps[:,0][:-1] #get the difference between each redshift grid
-
-def lnlike(theta, y, err):
-    h0 =theta
-    likh=twod_like(theta, y, err)[:,:-1]*ddz.T     #the sub of the intergral
-    int_likh=np.sum(likh[:,:],axis=1)
-    return np.sum(np.log(int_likh))
-######################MCMC#########################
-def lnprior(theta):
-    h0 = theta
-    if 45 < h0 < 95:
-        return 0.0
-    return -np.inf
-
-def lnprob(theta, y, yerr):
-    lp = lnprior(theta)
-    if not np.isfinite(lp):
-        return -np.inf
-    return lp + lnlike(theta, y, err)
-# =============================================================================
-# ###############minmize lnprob#######################
-# =============================================================================
-############to generate the likehood with zs############
[…]

### 2020-02-20 predict_GW/standard_siren/minima/gene_data.py

@@ -1,59 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Sun Jan  7 20:33:16 2018
-
-@author: dartoon
-
-a function to generate the data
-"""
-
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.integrate import quad
-from pz import pz
-
-def EZ(z,om):
-      return 1/np.sqrt(om*(1+z)**3+(1-om))
-def EE(z,om):
-      return quad(EZ, 0, z , args=(om))[0]
-
-def gene_data(vol,error_ls=(5,10),H0=70., om=0.3, reverse=False):
-    """
-    A function to generate data understand LCDM model with Om=0.3, H0=70:
-        input:
-            vol=the volume of the data size
-            error_l= error level, time 100, i.e. the number before '%'
-        output:
-            z, dl, dl_noised, errorbar
-    """
-    R=pz(om,H0)
-    zs=np.zeros(vol)
-    if isinstance(error_ls,float) or isinstance(error_ls,int):
-        error_l = error_ls
-    elif isinstance(error_ls,tuple):
-        error_l = np.random.uniform(error_ls[0],error_ls[1],vol)
-    for i in range(vol):
-        idx = int(np.sum(np.random.random()>R[:,2]))-1
-        zs[i] = R[idx, 0] #np.random.uniform(R[idx, 0],R[idx+1, 0])
-    vec_EE=np.vectorize(EE)
-    c=299790.        #speed of light [km/s]
-    dl=(1+zs)*c*vec_EE(zs,om)/H0            # unit in Mpc 
-    DL=np.zeros([len(zs),5])
-    if reverse==False:
-        DL[:,0]=zs            #zs
-        DL[:,1]=dl            #true dl distance 
-        erbar=dl*error_l/100.   #1% level as the based
-        DL[:,3]=erbar        #error
-        DL[:,2]=np.random.normal(dl,erbar)       #after noise
-        DL[:,4]=DL[:,2]*error_l/100.  #Realisic noise level?
-    elif reverse==True:
-        DL[:,0]=zs            #zs
-        DL[:,1]=dl            #true dl distance 
-        erbar=1/dl*error_l/100.   #1% level as the based
-        DL[:,3]=dl*error_l/100.        #error
[…]

### 2020-02-20 predict_GW/standard_siren/minima/plt_data_for_ppt.py

@@ -1,37 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Mon Sep 10 09:16:35 2018
-
-@author: Dartoon
-"""
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-#import sys
-#sys.path.insert(0,'../')
-from pz import pz
-from gene_data import gene_data
-
-import matplotlib as matt
-import matplotlib.lines as mlines
-from matplotlib import colors
-matt.rcParams['font.family'] = 'STIXGeneral'
-
-# =============================================================================
-# Test differnet cosmology
-# =============================================================================
-fig = plt.figure(figsize=(15,6))
-ax = fig.add_subplot(111)
-err_level= input("Input the error level:\n")
-dl = gene_data(10000,err_level, H0=70., om=0.3)
-#dl_wr =  gene_data(10000,3, H0=57., om=0.7)
-##dl_wwr =  gene_data(10000, 20, H0=65., om=0.54)
-ax.errorbar(x=dl[:,0],y=dl[:,2], yerr=dl[:,3],fmt='b.',zorder=-1)
-ax.set_yscale('log')
-
-plt.title('The $D_L$ vs redshift, {0} per cent level'.format(err_level),fontsize=15)
-plt.xlabel('$z$',fontsize=15)
-plt.ylabel('$D_L$', fontsize=15)
-plt.tick_params(labelsize=15)
-plt.show()

### 2020-02-20 predict_GW/standard_siren/minima/pz.py

@@ -1,115 +1,0 @@
-'''
-Calculate the possibility distribution of total numbers as func of z
-'''
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-from scipy import interpolate
-   
-def pz(om,h0,scenario=2):
-   f0=open('NSNSrates.dat')
-   f1=open('BHNSrates.dat')
-   f2=open('BHBHrates.dat')
-   nsns,nsbh,bhbh=np.loadtxt(f0),np.loadtxt(f1),np.loadtxt(f2)
-   f0.close,f1.close,f2.close
-   nsns=nsns[nsns[:,0].argsort(),]
-   nsbh=nsbh[nsbh[:,0].argsort(),]
-   bhbh=bhbh[bhbh[:,0].argsort(),]
-   #print nsns
-   
-   c=299790.; # speed of light [km/s]
-   w = -1;
-   dH=c/h0;
-   rho0 = 8;
-   
-   # detector horizon 
-   r0 = 1527.;	# in [Mpc] value for ET - polynomial Noise curve
-   #r0 = 1591.;	# ET-D sensitivity
-   #r0 = 1918.;    # ET - xylophone
-   Mchirp0 = 1.2
-   Mchirp1 = 3.2
-   Mchirp2 = 6.7
-   
-   
-   def Ez(z,om,w):
-     return   1/np.sqrt(om*(1+z)**3+(1-om)*(1+z)**(3*(1+w)))
-   def r(z,om,w):
-      return integrate.quad(Ez, 0, z, args=(om,w))[0]    #use the cos distance r
-   #print r(17,om,w)
-   
-   vec_r=np.vectorize(r)
-   z=nsns[:,0]
-   N=len(z)
-   Dist = vec_r(z,om,w)
-   
-   x=(rho0/8.)*(1+z)**(1/6.)*dH*(Dist/r0)*(1.2)**(5/6.)
-   x0=x/(Mchirp0**(5/6.))
-   x1=x/(Mchirp1**(5/6.))
-   x2=x/(Mchirp2**(5/6.))
-   Ctheta0,Ctheta1,Ctheta2=np.zeros(N),np.zeros(N),np.zeros(N)
-   for i in range (0,N):
-     if x0[i]>=0 and x0[i]<=4:
[…]

### 2020-02-20 predict_GW/standard_siren/minima/wCDM/test_wCDM_minima_Chi.py

@@ -1,86 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Jan  9 11:06:10 2018
-
-@author: dartoon
-"""
-
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-import sys
-from pz_wcdm import pz
-sys.path.insert(0,'../')
-from gene_data import gene_data
-##########to generate the lnPossible funtction, one need the Ka_square; P(zl|zs); P(zs).
-#########to get the P(zs):#################
-om=0.3
-h0=70
-w=-1
-ps=pz(om,w,h0)
-zs=ps[:,0]
-
-################to get the ka^2 and combine together to get likehood for one data###################
-c=299790.
-def Ez(z,om,w):
-  return   1/np.sqrt(om*(1+z)**3+(1-om)*(1+z)**(3*(1+w)))
-def r(z,om,w):
- #if z < 20:
-    return integrate.quad(Ez, 0, z, args=(om,w))[0]    #use the cos distance r
- #else:
- #   return 3.33
-vec_r=np.vectorize(r)
-
-def twod_like(theta, y, err):    #set zs to be 2D to get 2D sub_int, from (len(data)) to (len(data),133)
-    om, w, h0 =theta
-    rzs=vec_r(zs,om,w)
-    model = (1+zs)*c*rzs/h0             #133 numbers of the models
-    #print np.shape(y),np.shape(model)
-    ps=pz(om,w,h0)
-    likh = np.exp(-0.5*(pow((y[:,None]-model),2)/pow(err[:,None],2)))*ps[:,1]
-    #print likh[1,:]
-    return likh
-#print np.shape(twod_like(theta=[0.3,70], y=data[:,2], err=data[:,3]))
-
-ddz=ps[:,0][1:]-ps[:,0][:-1] #get the difference between each redshift grid
-
-
-def lnlike(theta, y, err):
-    om, w, h0 =theta
-    #print theta
-    likh=twod_like(theta, y, err)[:,:-1]*ddz.T     #the sub of the intergral
-    int_likh=np.sum(likh[:,:],axis=1)
-    #print np.shape(int_likh)
-    return np.sum(np.log(int_likh))
-#print lnlike(theta=[0.3,70], zl=data[:,1], y=data[:,3], err=data[:,4])
-
-######################MCMC#########################
-def lnprior(theta):
[…]

### 2020-02-20 predict_GW/standard_siren/minima/wCDM/wCDM_mcmc.py

@@ -1,116 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Jan  9 11:06:10 2018
-
-@author: dartoon
-"""
-
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-import sys
-from pz_wcdm import pz
-sys.path.insert(0,'../')
-from gene_data import gene_data
-##########to generate the lnPossible funtction, one need the Ka_square; P(zl|zs); P(zs).
-#########to get the P(zs):#################
-om=0.3
-h0=70
-w=-1
-ps=pz(om,w,h0)
-zs=ps[:,0]
-
-################to get the ka^2 and combine together to get likehood for one data###################
-c=299790.
-def Ez(z,om,w):
-  return   1/np.sqrt(om*(1+z)**3+(1-om)*(1+z)**(3*(1+w)))
-def r(z,om,w):
- #if z < 20:
-    return integrate.quad(Ez, 0, z, args=(om,w))[0]    #use the cos distance r
- #else:
- #   return 3.33
-vec_r=np.vectorize(r)
-
-ddz=ps[:,0][1:]-ps[:,0][:-1] #get the difference between each redshift grid
-
-step=0
-
-def lnlike(theta, y, errs_l, errs_h):
-    global step, mcmc_count, value
-    om, w, h0 =theta
-    rzs=vec_r(zs,om,w)
-    model = (1+zs)*c*rzs/h0             #133 numbers of the models
-    #print theta
-    ps=pz(om,w,h0)
-    for i in range(20):
-        err = errs_l + (errs_h - errs_l)*i/19.
-        twod_like = np.exp(-0.5*(pow((y[:,None]-model),2)/pow(err[:,None],2)))*ps[:,1]
-        likh=twod_like[:,:-1]*ddz.T     #the sub of the intergral
-        if i ==0:
-            int_likh=np.sum(likh[:,:],axis=1)
-        else:
-            int_likh += int_likh
-    if mcmc_count == 1:
-        count=np.sum(sampler.flatchain!=0)/(ndim*nwalkers)
-        if count!=step:
-            step = count
-            ticks2=time.time()
-            print "step:",count,"percent",round(count/(Nburn/100),2),"%"
-            if step !=0:
-                print "remain time:", round((ticks2-ticks1)/step*(Nburn-step)/60,2), "mins;"
-            if step/10 > (step-1)/10 :
-                print "To write the value", value
[…]

### 2020-02-20 predict_GW/standard_siren/minima/wCDM/wCDM_minima.py

@@ -1,101 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Tue Jan  9 11:06:10 2018
-
-@author: dartoon
-"""
-
-import numpy as np
-from scipy import integrate
-import matplotlib.pyplot as plt
-import sys
-from pz_wcdm import pz
-sys.path.insert(0,'../')
-from gene_data import gene_data
-##########to generate the lnPossible funtction, one need the Ka_square; P(zl|zs); P(zs).
-#########to get the P(zs):#################
-om=0.3
-h0=70
-w=-1
-ps=pz(om,w,h0)
-zs=ps[:,0]
-
-################to get the ka^2 and combine together to get likehood for one data###################
-c=299790.
-def Ez(z,om,w):
-  return   1/np.sqrt(om*(1+z)**3+(1-om)*(1+z)**(3*(1+w)))
-def r(z,om,w):
- #if z < 20:
-    return integrate.quad(Ez, 0, z, args=(om,w))[0]    #use the cos distance r
- #else:
- #   return 3.33
-vec_r=np.vectorize(r)
-
-ddz=ps[:,0][1:]-ps[:,0][:-1] #get the difference between each redshift grid
-
-def lnlike(theta, y, errs_l, errs_h):
-    om, w, h0 =theta
-    rzs=vec_r(zs,om,w)
-    model = (1+zs)*c*rzs/h0             #133 numbers of the models
-    #print theta
-    ps=pz(om,w,h0)
-    for i in range(20):
-        err = errs_l + (errs_h - errs_l)*i/19.
-        twod_like = np.exp(-0.5*(pow((y[:,None]-model),2)/pow(err[:,None],2)))*ps[:,1]
-        likh=twod_like[:,:-1]*ddz.T     #the sub of the intergral
-        if i ==0:
-            int_likh=np.sum(likh[:,:],axis=1)
-        else:
-            int_likh += int_likh
-    #print np.shape(int_likh)
-    return np.sum(np.log(int_likh))
-
-######################MCMC#########################
-def lnprior(theta):
-    om, w, h0 = theta
-    if 0.1 < om < 0.55 and -2 < w < -0.5 and 45 < h0 < 95:
-        return 0.0
-    return -np.inf
-
-def lnprob(theta, y, errs_l, errs_h):
-    lp = lnprior(theta)
-    if not np.isfinite(lp):
-        return -np.inf
-    return lp + lnlike(theta, y, errs_l, errs_h)
[…]

### 2020-02-20 predict_GW/standard_siren/minima/z_sou.py

@@ -1,130 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-from scipy.integrate import quad
-from pz import pz
-
-########start to generate the data
-
-#f=open('int_dis.txt')
-#data=np.loadtxt(f)
-#f.close
-'''
-num=len(data)
-N=num
-#print N
-dp=np.zeros([num,4])
-dp[:,0]=data[:,0]   # redshift assumption
-dp[:,1]=data[:,1]   #for NS-NS note the real possibility should mutply by p(i)-p(i-1)
-dp[:,2]=data[:,9]   #for NS-BH
-dp[:,3]=data[:,17]   #for BH-BH
-p=np.zeros([num,2])
-p[:,0]=dp[:,0]
-p[:,1]=dp[:,1]+dp[:,2]+dp[:,3]
-'''
-p=pz(0.3,70)
-N=len(p[:,0])
-R=np.zeros([N+1,3])
-R[:,0]=np.append(0,p[:,0])
-R[:,1]=np.append(0,p[:,1])
-R[0,2]=0
-for i in range (1,N):
-	R[i+1,2]=R[i,2]+R[i,1]*(R[i+1,0]-R[i,0])
-R[:,1]=R[:,1]/R[N,2]
-R[:,2]=R[:,2]/R[N,2]
-#print p
-d= input('How may dataset to be generated?:')
-#d=2000
-zs=np.zeros(d)
-seed=input('seed?:')
-np.random.seed(seed)        #keep the random number to be the same every time
-for i in range(d):
-   k=np.random.random()
-   #print k
-   for j in range(1,N):
-	if R[j,2]<k and R[j+1,2]>k:
-		#zs[i]=np.random.uniform(R[j-1,0],R[j,0])     # should better not in this way
-                zs[i]=R[j,0]                                  # the p_i(s) is for p_i to p_(i+1)
-
-
-#plt.hist(zs,50)
-#plt.show()
-########################generate the luminorsity distance##############
-def EZ(z,om):
-      return 1/np.sqrt(om*(1+z)**3+(1-om))
-def EE(z):
-      return quad(EZ, 0, z , args=(om))[0]
-vec_EE=np.vectorize(EE)
-H=70             #km/s/Mpc
-om=0.3
-c=299790.        #speed of light [km/s]
-dl=(1+zs)*c*vec_EE(zs)/H            # unit in Mpc 
-
[…]

### 2020-02-20 projects/Rebuttal_paper_simple_fit_mocks/plot_H0_hist.py

@@ -12,7 +12,7 @@ import pickle
 import matplotlib as mat
 mat.rcParams['font.family'] = 'STIXGeneral'
 
-folder = 'MCsteps1000_10000/'
+folder = 'final_confirmed_MCsteps1000_10000/'
 #folder = 'MCsteps1000_10000_linear_False/'
 #folder = 'MCsteps[1000, 10000]_first_run_linear_True/'
 #folder = 'MCsteps1000_10000_second_run_linear_True/'
@@ -27,21 +27,22 @@ folder = 'MCsteps1000_10000/'
 #    mcmc_new_list, labels_new = trans_result
 #    H0_list = mcmc_new_list[:,-1]
 #    H0_lists.append(H0_list) 
-# pickle.dump([H0_lists], open(folder+'H0_SIE.pkl', 'wb'))         
-H0_lists = []
-for i in range(1,7):
-   result = pickle.load(open(folder+'sampler_results_SPEMD#{0}.pkl'.format(i),'rb'))
-   _, trans_result = result
-   mcmc_new_list, labels_new = trans_result
-   H0_list = mcmc_new_list[:,-1]
-   H0_lists.append(H0_list) 
-pickle.dump([H0_lists], open(folder+'H0_SPEMD.pkl', 'wb'))         
+# pickle.dump([H0_lists], open(folder+'H0_SIE.pkl', 'wb')) 
+        
+# H0_lists = []
+# for i in range(1,7):
+#    result = pickle.load(open(folder+'sampler_results_SPEMD#{0}.pkl'.format(i),'rb'))
+#    _, trans_result = result
+#    mcmc_new_list, labels_new = trans_result
+#    H0_list = mcmc_new_list[:,-1]
+#    H0_lists.append(H0_list) 
+# pickle.dump([H0_lists], open(folder+'H0_SPEMD.pkl', 'wb'))         
 
 #%%
 H0_true = 70.65595
 #model = 'SIE'
 #model = 'SPEMD'
-for model in ['SPEMD']:
+for model in ['SIE','SPEMD']:
     name = {'SIE'   :'SIE', 'SPEMD': "Power - law"}
     H0 = pickle.load(open(folder+'H0_{0}.pkl'.format(model),'rb'))[0]
     
@@ -49,7 +50,7 @@ for model in ['SPEMD']:
     for i in range(len(H0)):
[…]

### 2020-02-20 projects/Rebuttal_paper_simple_fit_mocks/test_burning.py

@@ -15,14 +15,15 @@ import matplotlib as mat
 import corner
 mat.rcParams['agg.path.chunksize'] = 10000
 
-folder = 'MCsteps1000_10000_PROFILE_terrible_result/'
+# folder = 'MCsteps1000_10000_1.3.0_non-linear_True_2ndrun/'
+folder = 'MCsteps100_100/'
 # folder = 'MCsteps1000_10000_1.3.0_non-linear_False/'
 
 model = 'SPEMD'
 # model = 'SIE'
 
-for i in range(2,3):
-    result = pickle.load(open(folder+'sampler_results_{1}#{0}.pkl'.format(i, model),'rb'))
+for i in range(1,2):
+    result = pickle.load(open(folder+'sampler_results_{1}#{0}.pkl'.format(i, model),'rb'),encoding="latin1") 
     fit_result, trans_result = result
     mcmc_new_list, labels_new = trans_result
 
@@ -32,7 +33,7 @@ chain_num = len(mcmc_new_list)
 #%%
 print(len(mcmc_new_list[1]),labels_new)
 
-plot = corner.corner(mcmc_new_list, labels=labels_new, show_titles=True, range= [[0.8,1.5],[1,3],[0,1],[0, 1],[2000,5000],[20,100]], 
+plot = corner.corner(mcmc_new_list, labels=labels_new, show_titles=True, #range= [[0.8,1.5],[1,3],[0,1],[0, 1],[2000,5000],[20,100]], 
                      quantiles=[0.16, 0.5, 0.84], #smooth = 0.8,
                      title_kwargs={"fontsize": 15}, label_kwargs = {"fontsize": 25},
                      levels=1.0 - np.exp(-0.5 * np.array([1.,2.]) ** 2))

### 2020-03-14 projects/Rebuttal_paper_simple_fit_mocks/paper_Xuheng_edit/aanda.tex
Upload whatever

%                                                                 aa.dem
% AA vers. 9.1, LaTeX class for Astronomy & Astrophysics
% demonstration file
%                                                       (c) EDP Sciences
%-----------------------------------------------------------------------
%
%\documentclass[referee]{aa} % for a referee https://www.overleaf.com/2144999964jkhxrcqqgfjrversion
%\documentclass[onecolumn]{aa} % for a paper on 1 column  
%\documentclass[longauth]{aa} % for the long lists of affiliations 
%\documentclass[letter]{aa} % for the letters 
%\documentclass[bibyear]{aa} % if the references are not structured 
%                              according to the author-year natbib style

%
\documentclass[traditabstract, twocolumns, longauth]{aa}

%
\usepackage{txfonts}
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{xcolor}     % Text color
\usepackage{soul}       % for strikeout, can be removed after comments are treated
\usepackage{array}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue, urlcolor=blue]{hyperref}
\bibpunct{(}{)}{;}{a}{}{,}

\newcommand{\cdfcom}[1]{\xspace\textcolor{magenta}{\textbf{CDF: #1}}}
\newcommand{\warning}[1]{\textcolor{red}{\textbf{#1}}}
\def\ksmpc{${\, \mathrm{km}\, \mathrm{s}^{-1}\, \mathrm{Mpc}^{-1}}$\xspace}
\def\ks{${\, \mathrm{km}\, \mathrm{s}^{-1}}$\xspace}
\newcommand{\lcdm}{$\mathrm{\Lambda CDM}$\xspace}
%\newcommand{\slope}{$\mathrm{dH_0/d \sigma_{v}}$ \xspace}
\newcommand{\slope}{$\xi$}
\newcommand{\Bsixteen}{$\mathrm{B1608+656}$\xspace}
\newcommand{\RXJ}{$\mathrm{RX\ J1131-1231}$\xspace}
% CDF: Changed location of the "J" to be consistent with the other lenses
\newcommand{\HEzero}{$\mathrm{HE\ 0435-1223}$\xspace}
\newcommand{\Jtwelve}{$\mathrm{SDSS\ J1206+4332}$\xspace}
\newcommand{\WFItwenty}{$\mathrm{WFI\ 2033-4723}$\xspace}
\newcommand{\PGeleven}{$\mathrm{PG\ 1115+080}$\xspace}
\newcommand{\DESzerofour}{$\mathrm{DES\ J0408-5354}$\xspace}
\newcommand{\LENSTRO}{{\tt LENSTRONOMY}}

\newcommand{\Hc}{\ensuremath{H_0}\xspace}
\newcommand{\zd}{\ensuremath{z_\mathrm{d}}\xspace}
\newcommand{\zs}{\ensuremath{z_\mathrm{s}}\xspace}
\newcommand{\Dd}{\ensuremath{D_\mathrm{d}}\xspace}
\newcommand{\Dds}{\ensuremath{D_\mathrm{ds}}\xspace}
\newcommand{\Ds}{\ensuremath{D_\mathrm{s}}\xspace}
\newcommand{\Ddt}{\ensuremath{D_{\Delta t}}\xspace}
\newcommand{\kext}{\ensuremath{\kappa_\mathrm{ext}}\xspace}
\newcommand{\raper}{\ensuremath{\theta_\mathrm{aperture}}\xspace}
\newcommand{\reff}{\ensuremath{\theta_\mathrm{eff}}\xspace}
\newcommand{\thetaE}{\ensuremath{\theta_\mathrm{E}}\xspace}

\begin{document}

\title{
TDCOSMO. I. An exploration of systematic uncertainties in the inference of \Hc from time-delay cosmography 
%TDCOSMO. I. An exploration of systematic uncertainties in time-delay cosmography and the inference of \Hc
%Asserting the impact of galaxy kinematics on \Hc measurements with time-delays in gravitationally lensed quasars
}
\author{
M.~Millon\inst{\ref{epfl}} \and
A.~Galan\inst{\ref{epfl}} \and
F.~Courbin\inst{\ref{epfl}} \and
T.~Treu\inst{\ref{ucla}} \and
S.~H.~Suyu\inst{\ref{mpa},\ref{tum},\ref{asiaa}} \and
X.~Ding\inst{\ref{ucla}} \and
S.~Birrer\inst{\ref{stanford}} \and
G.~C.-F.~Chen \inst{\ref{ucdavis}} \and
A.~J.~Shajib \inst{\ref{ucla}} \and
K.~C.~Wong \inst{\ref{kavliipmu}} \and
A.~Agnello\inst{\ref{dark}} \and
M.~W.~Auger\inst{\ref{ucambridge},\ref{kavlicambridge}} \and
E.~J.~Buckley-Geer\inst{\ref{Fermilab}} \and
J.~H.~H.~Chan\inst{\ref{epfl}}\and
T.~Collett\inst{\ref{uportsmouth}} \and
C.~D.~Fassnacht \inst{\ref{ucdavis}} \and
S.~Hilbert \inst{\ref{mpa}} \and
L.~V.~E.~Koopmans\inst{\ref{unigroningen}}\and 
V.~Motta \inst{\ref{universidadvalparaiso}} \and
S.~Mukherjee \inst{\ref{star}}\and
C.~E.~Rusu \inst{\ref{naoj}} \and
D.~Sluse\inst{\ref{star}} \and
A.~Sonnenfeld \inst{\ref{leiden}} \and
C.~Spiniello \inst{\ref{OAC},\ref{ESO}} \and
L.~Van de Vyvere\inst{\ref{star}} 
}

\institute{
Institute of Physics, Laboratory of Astrophysics, Ecole Polytechnique 
F\'ed\'erale de Lausanne (EPFL), Observatoire de Sauverny, 1290 Versoix, 
Switzerland \label{epfl} \goodbreak 
\and
Department of Physics and Astronomy, University of California, Los Angeles CA 90095, USA \label{ucla} \goodbreak
\and
Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str.~1, 85748 Garching, Germany \label{mpa} \goodbreak
\and
Physik-Department, Technische Universit\"at M\"unchen, James-Franck-Stra\ss{}e~1, 85748 Garching, Germany \label{tum} \goodbreak
\and
Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan \label{asiaa} \goodbreak
\and 
Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA \label{stanford}\goodbreak
\and
 Department of Physics, University of California, Davis, CA 95616, USA \label{ucdavis}\goodbreak
 \and 
 Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\label{kavliipmu} \goodbreak
 \and
DARK, Niels Bohr Institute, Lyngbyvej 2, 2100 Copenhagen, Denmark \label{dark} \goodbreak
\and 
 Kapteyn Astronomical Institute, University of Groningen, P.O.Box 800, 9700AV Groningen, Netherlands \label{unigroningen} \goodbreak
 \and 
 Instituto de F\'{\i}sica y Astronom\'{\i}a, Facultad de Ciencias, Universidad de Valpara\'{\i}so, Avda. Gran Breta\~na 1111, Valpara\'{\i}so, Chile. \label{universidadvalparaiso} \goodbreak
 \and
 STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium \label{star} \goodbreak
 \and
 National Astronomical Observatory of Japan, 2-21-1 Osawa, Mitaka, Tokyo 181-8588, Japan \label{naoj}\goodbreak
\and
Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK \label{ucambridge}\goodbreak
\and 
Kavli Institute for Cosmology, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK \label{kavlicambridge}\goodbreak
\and
Leiden Observatory, Leiden University, Niels Bohrweg 2, 2333 CA Leiden, the Netherlands
\label{leiden}\goodbreak
\and
University of Portsmouth, Institute of Cosmology and Gravitation, Portsmouth PO1 3FX, United Kingdom \label{uportsmouth} \goodbreak
\and
INAF - Osservatorio Astronomico di Capodimonte, Salita Moiariello, 16, 80131, Napoli, Italy
\label{OAC} \goodbreak
\and
European Southern Observatory, Karl-Schwarschild-Str. 2, 85748, Garching, Germany
\label{ESO} \goodbreak
\and 
Fermi National Accelerator Laboratory, P. O. Box 500, Batavia, IL 60510, USA \label{Fermilab}
}

%\datesmooth{\today}
\abstract{
}
\keywords{methods: data analysis – gravitational lensing: strong}

\titlerunning{Uncertainties in time-delay cosmography}
\maketitle
%\begin{comment}
%Low-redshift and pre-recombinaiton measurements of the Hubble constant \Hc are at 3-5$\sigma$ tension, which requires new physics beyond $\Lambda$CDM or significant systematics.
%Time-delay cosmography is a single-step method, independent of any distance-ladder calibration, and has resulted in 2.4\% precision on \Hc. As the need to control systematics becomes more pressing, we analyse three sources of systematic uncertainties: stellar kinematics, line-of-sight effects, and lens model degeneracies.
%Simplified toy models cannot provide quantitative insights in this regime, so we closely mimic the H0LiCOW/SHARP/STRIDES (TDCOSMO) procedure.
%First, given current uncertainties, stellar kinematics is not a dominant source of bias. Second, there is no evidence of any bias arising from incorrect estimation of the line-of-sight effects. Third, we show that arbitrary elliptical composite (stars+halo), power-law, and cored power-law mass profiles have the flexibility to yield a range of \Hc estimates.
%Whenever two lens models disagree, the TDCOSMO procedure can discriminate them based on goodness-of-fit, and/or account for the discrepancy in the error bars once models are marginalised over.
%This conclusion is consistent with a reanalysis of the six TDCOSMO lenses: the composite and power-law models yield \Hc=$74.0^{+1.6}_{-1.7}$kms$^{-1}$Mpc$^{-1}$ and  $73.8^{+1.7}_{-1.9}$ kms$^{-1}$Mpc$^{-1}$ respectively.
%In conclusion, we find no evidence of bias larger than the current statistical uncertainties. %Future papers by the TDCOSMO collaboration will continue to investigate potential sources of bias as precision increases.
%\end{comment}

%
%-------------------------------------------------------------------
\section{Introduction}
\label{sec:introduction}

\section{Background \label{sec:msd}}

%%%%%%%%%%%%%%
\section{Inference procedure and limitations of toy models}
\label{sec:toysareforbabies}
%%%%%%%%%%%%%%

\section{Influence of kinematics data on \Hc measurement \label{sec:kinematics_impact}}
\label{sec:kinem_sensitivity}

%%%%%%%%%%%%%%%%%%%%%%
\section{Is there any evidence for correlation between \Hc and physically independent observables?}
%%%%%%%%%%%%%%%%%%%%%%
\label{sec:corr}

%%%%%%%%%%%%%%
\section{Impact of the choice of families of mass model}
\label{sec:6}
%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%
\subsection{\Hc inference per model family}
\label{ssec:powervscomposite}
%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%
\subsection{Simulations}
\label{ssec:sim}
%%%%%%%%%%%%

\subsection{Results}
\label{ssec:results}

\subsection{Discussion}
\label{ssec:disc}

({\color{red}{{\bf Xuheng:} Currently, let's consider to put these sentences somewhere in section~\ref{ssec:disc}:}})

As mentioned in Section~\ref{sec:toysareforbabies}, neglecting the other information but only considering the point-source information and lensing galaxy position, is not sufficient to constrain all the lens model parameters. As an additional test to address this point, we model the simulated data using only the four lensed image positions and their time delays. A reduced $\chi^2 <$ 1 can be obtained for all the mocks using a power law model, except for mock \#6 for which the best reduced $\chi^2 \sim 1.9$. Even when the true mass distribution is a power law (e.g. mock \#1 and \#2), the maximum likelihood models are associated with power-law indices substantially different from the input one, yielding a bias on \Hc\, that can reach 90\% (see Appendix~\ref{app:simple_model} for details). This is well understood as the multipole components of the lens potential can compensate for large changes in the monopole structure which are only poorly constrained by the few image positions. This test highlights the necessity of using the full information provided by the high resolution images to better constrain the lens potential. In particular, the multiple images of the lensed host galaxy are critical to pin down the uncertainty on the average mass density at the image positions, which is critical for \Hc inference (add a ref on CSJK2001 on "the importance of Einstein rings  \url{http://adsabs.harvard.edu/abs/2001ApJ...547...50K} which basically make this point).

%%%%%%%%%%%%%%%%%
\section{Conclusion}
\label{conclusion}
%%%%%%%%%%%%%%%%%

\begin{acknowledgements}
\end{acknowledgements}

\bibliographystyle{aa}
%\bibliography{biblio}

\begin{appendix}
\onecolumn
\section{Properties of simulated lenses}
...

\section{Model only based on lensed quasar position}\label{app:simple_model}

% To perform a consistent comparison to the modeling process as in Section~\ref{ssec:results},
We model the simulated dataset as generated in Section~\ref{ssec:sim}, using only the lensed quasar positions, the lensing galaxy position and the relative time delays between the lensed images. We assume an uncertainty $\sigma = 0\farcs{004}$ on the point-source positions, $\sigma = 0\farcs{01}$ on the lensing galaxy centroid, and the same uncertainty on the time-delay as in Sect.~\ref{ssec:results}. Similarly to extended source modeling performed (Sect.~\ref{ssec:results}), we employ the lens modeling package \LENSTRO. We adopt both the singular isothermal ellipsoid (SIE) model (i.e., fix slope value $\gamma=2.0$) and the Power-law model in this test. For the SIE, an independent modeling has been carried out with \texttt{lensmodel} \citep{Keeton2001, Keeton2011}, as well as for modeling mock ID \#1 with a SPEMD. We obtained similar inference with both packages and therefore only report hereafter on results obtained with \LENSTRO.

We use the true parameters as the input values to start performing the modeling. A careful choice of the likelihood and sampling options has to be carried out to ensure that image position constraints arise from the same source. While the details of the fitting options were not critical for SIE models, they were for the SPEMD modeling. In practice, we sample the source plane and evaluate the positional likelihood in the image plane, but adding a source plane likelihood term to ensure that each image arise from the same source within $\sigma = 0\farcs{001}$  [need to be clarified based on what was finally implemented - cf source likelihood term if and ]. A notebook implementing our fitting strategy is available at {\url{}}. \textcolor{red}{[To do: Xuheng will create a notebook for this]}

In Figure~\ref{fig:corner_pos_only}, we show the corner plots of the inference based on the mock system ID \#1. As shown, when using a SIE model where the mass slope value fixed to the truth, the fitting could obtain an unbiased \Hc\ with uncertainty level at $\sim10\%$ level. However, when the slope is a free parameter, the inference broadens significantly as the data are not sufficient to constrain that parameter. In particular, the uncertainty level of \Hc\ increase by a factor of $\sim3$ and the maximum likelihood deviates from the truth.
\textcolor{red}{[Xuheng: A corner plot of Figure~\ref{fig:corner_pos_only} might be enough to clarify our points. We can also show the H0 posterior histogram for the overall six systems if the other people feel needed.]}

\begin{figure*}[t!]
    \centering
    \includegraphics[width=0.49\textwidth]{corner_plot_SIE_ID1.pdf}
     \includegraphics[width=0.49\textwidth]{corner_plot_SPEMD_ID1.pdf}
    \caption{The corner plot of the inference of modeling mock system ID \#1 using only the lensed quasar position and time delay. The SIE model and Power-law model are adopted on the left and right, separately. The blue lines indicate the true values in the simulation. }
    \label{fig:corner_pos_only}
\end{figure*}

\end{appendix}
\end{document}

### 2020-03-14 projects/JWST_SED_abmag_esti/plot_spec_filter.py

@@ -1,0 +1,67 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Tue Feb 25 10:13:22 2020
+
+@author: Dartoon
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+from specutils import Spectrum1D
+import glob
+
+#%%To estimate the AB mag for a given stellar template
+#filename  = 'SED_files/summary_*_PA00.fits'
+#filename = glob.glob(filename)[0]
+#hdul_sum = pyfits.open(filename)
+#name_sum = hdul_sum[1].columns
+#table_sum = hdul_sum[1].data
+#z_idx = [i for i in range(len(name_sum)) if 'zmc' in str(name_sum[i])][0]
+#mel_idx = [i for i in range(len(name_sum)) if 'logZsun' in str(name_sum[i])][0]
+#z = table_sum[1][z_idx] #Redshift
+#mel = table_sum[1][mel_idx] #Metallicity 
+filename_p  = 'SED_files/SFH_*_PA00_param.fits'
+filename_p = glob.glob(filename_p)[0]
+hdul = pyfits.open(filename_p)
+table = hdul[1].data
+name = hdul[1].columns
+age_idx = [i for i in range(len(name)) if 'T_MW' in str(name[i])][0]
+age = str(round(10**table[1][age_idx],3)) # 'AGE:' Gyr
+z_idx = [i for i in range(len(name)) if 'zmc' in str(name[i])][0]
+z = str(round(table[1][z_idx],2))
+mel_idx = [i for i in range(len(name)) if 'Z_MW' in str(name[i])][0]
+mel = str(round(10**table[1][mel_idx],3)) # 'Mel:' Z*/Z_sun
+
+#%%
+spec1d = hdul_sum = pyfits.open("gsf_spec_1.fits")  
+name_spec = spec1d[1].columns
+table_spec = spec1d[1].data
+array_spec = np.zeros((len(table_spec), 7))
+for i in range(len(table_spec)):
+    array_spec[i, :] = table_spec[i]
+
+#%%
+
+sov_jwst_f144w_fil = np.loadtxt('JWST_NIRCam.F444W.dat')
[…]

### 2020-10-02 projects/Sim_HST_JWST/HST_lensed_QSO/manuscript/main.tex
Create main.tex

\documentclass[useAMS,usenatbib,usegraphicx]{mn2e}
\usepackage{graphicx}% Include figure files
\usepackage{subfigure}% Include subfigure files
\usepackage{xcolor}% Change colors of text using \textcolor{red}{...}
\usepackage{mathtext,bm,bbm,amsmath,amsfonts,amssymb,indentfirst,syntonly,graphicx,epsf}
\usepackage{mathtools}
\usepackage[english]{babel}
\usepackage{calc}
\usepackage{tikz}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

\newcommand{\hc}{$H_0$}

\title[Lens modelling improvements in lensed transients]{Lens modelling improvements in strongly lensed explosive transient systems}
\author[Ding et al.]
{Xuheng Ding$^{1}$,
and Kai Liao$^{2}$\thanks{e-mail: liaokai@whut.edu.cn}
and TBD\\
$^{1}$Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA\\
$^{2}$School of Science, Wuhan University of Technology, Wuhan 430070, China}
\begin{document}

\date{Accepted xxxx; Received xxxx; in original form xxxx}

\pagerange{\pageref{firstpage}--\pageref{lastpage}} \pubyear{2018}

\maketitle

\label{firstpage}

\begin{abstract}
  Strongly lensed explosive transients like supernovae, gamma ray bursts, fast radio bursts and gravitational waves are very promising to determine the Hubble constant ($H_0$) in the next stage. Compared to the traditional targets: lensed quasars, they can give much more precise time delay measurements due to either the transient nature or well-known light curves. In this work, we quantitatively study how lens modelling improves without the contamination from bright point source, i.e., the AGN, since the complete host arcs can be observed before or after the transient's appearance. We simulate 8 lensing systems with and without adding point sources and compare the inferred Fermat potential difference.
  Generally, the lens modelling can be improved by 3?? times. Moreover, we incorporate
  the information on the magnifications and find lens modelling can be further improved by ??.
\end{abstract}

\begin{keywords}
gravitational lensing: strong \--- Hubble constant
\end{keywords}

\section{Introduction}

The Hubble constant ($H_0$) is currently attracting the eyes of the cosmology community. The direct measurement based on distance ladders is different from that from cosmic microwave background (CMB) by $4.4\sigma$. Note that $H_0$ in the latter is treated as a free parameter. This discrepancy manifests that
either unknown systematic errors existing in the data or new physics.

Strong gravitational lensing provides an independent and one-step way to determine $H_0$.

Lensed transient systems resulting in precise time-delay cosmology
include supernovae in all types,
GW/SGRB+kilonava/afterglow association, LGRB+SN Ic/afterglow association and repeated FRB.

\section{Time delay cosmology}
Time delay between multiple images was proposed to measure $H_0$.
Strong lensing gives: 
\begin{equation}
D_{\Delta t}=\frac{c\Delta t}{\Delta\phi(\boldsymbol{\xi}_{lens})}\frac{1}{1-\kappa_\mathrm{ext}},
\end{equation}
where the time delay distance:
\begin{equation}
D_{\Delta t}=(1+z_l)\frac{D_lD_s}{D_{ls}}
\end{equation}
is primarily proportional to $1/H_0$ and weakly depends on other cosmological parameters.
To determine $D_{\Delta t}$, three uncertainty sources need to be considered. First of all,
the time delay $\Delta t$ between any two images of AGN is measured with long-term light curves.
Secondly, the Fermat potential difference can be determined by the high-resolution imaging of the host arcs, the dispersion velocity of the lens galaxy and the AGN image positions. At last,
the perturbers along the line of sight (LOS) can contribute to the lens potential as well, causing additional (de)focusing of the light rays and affecting the observed time delay. They
can be approximated by an external convergence $\kappa_{\rm{ext}}$, resulting in a scaled inferred $D_{\Delta t}$ by $1-\kappa_{\rm{ext}}$.

\section{Data simulation and modelling test}
%structure:
%1. describe the goal -- simulate two contract sample (with and without AGN) to test how H0 measurement improves when the brightness AGN effect disappear.
It is well-known that one of the major difficulties in the lensed AGN modelling is that the bright point source dominates the central regions in the host, which significantly reduce the number of pixels with available lensed arc information making the lensing modelling more challengeable.  
To investigate at which level the bright AGN affects the inference of the lens model and the inference of \hc, we make a group of two samples and perform a control experiment. The first group is a sample of 50 mock HST observed lensed AGN systems, the data quality is based on the real observation as used by the TDCOSMO collaboration. As a contrast sample, the second group are generated based on the same parameters and only that the AGN image is not added. We then adopt the lens modelling software lenstronomy to model these two samples to make direct comparison of the inference using the two samples. In addition, the kinematics information of the deflector would be helpful to get extra constrains on the lens model [ref]. However, the aim of this work is to test the lens modelling by comparing the fittings when with/without AGN, and using lens velocity dispersion information to give extra constrains on the lens model is beyond the scope of this paper.

\subsection{Mock data simulations}
The simulations of the 50 lensed AGN systems are based on the pipeline introduced by [Ding et al.].  The mock data are based on the observations using HST WFC/F160W.
This pipeline has also been used in TDLMC and TDCOSMO-1 [ref]. We adopt the same simulating strategy as used TDLMC to generate the mock sample, which are summarized as below.

The simulating ingredients includes the light from the deflector and active galaxies in the source plane.

The light profile of the galaxy is assumed as S\'ersic profile is parameterized by:
\begin{eqnarray}
   \label{eq:sersic}
   &I(R) = A \exp\left[-k\left(\left(\frac{R}{R_{\mathrm{eff}}}\right)^{1/n}-1\right)\right] ,\\
   &R(x,y,q) = \sqrt{qx^2+y^2/q}.
\end{eqnarray}
%
where $A$ is the amplitude and S\'ersic index $n$ controls the shape of the radial
surface brightness profile; a larger $n$ corresponds to a steeper
inner profile and a highly extended outer wing. 
 $k$ is a constant which
depends on $n$ so as to ensure that the isophote at $R=R_{\mathrm{eff}}$
encloses half of the total light \citep{C+B99} and
$q$ denotes the axis ratio.

The mass of the deflector is assumed as a elliptical power-law model, whose surface mass density is given by:
%
\begin{equation}
 \label{massmodel}
 \Sigma(x,y)=\Sigma_{cr}\frac{3-\gamma^{\prime}}{2}\left(\frac{\sqrt{q_m x^{2}+y^{2}/q_m}}{R_{\rm E}}\right)^{1-\gamma^{\prime}},
\end{equation}
%
$q_m$ described the projected axis ratio.
The so-called Einstein radius $R_{\rm{E}}$ is chosen such
that, when $q_m=1$ (i.e. spherical limit), it encloses a mean surface
density equal to $\Sigma_{cr}.$
%This is also the radius of a ring traced by the host of the AGN when this is exactly aligned with the lens galaxy.
The exponent $\gamma'$ is the slope of the power-law profile,
for massive elliptical galaxies $\gamma' \approx2$  \citep{T+K02a,T+K04,Koo++09}.
We refer the reader to the reviews by \citet{Sch06, Bar10, Tre10} for more details.
An external shear component is also considered.

The assumed lensing parameters are randomly generated using the Table 2 in TDLMC-2. The position of the source AGN is manually input so that all the lensed image are quads. The noise includes the Gaussian background noise and the Poisson noise which is based on the realistic HST condition with exposure time as 9,584 s. The PSF is generated by tinytim. The pixel scale is drizzled from 0\farcs{13} to 0\farcs{08} into the frame size with $99\times99$ pixels. The 50 lensed non-AGN systems are also simulated using the identical parameters as the 50 lensed AGN sample, expect that the point-source flux is muted.

The time delays are calculated based on the lens parameters based on a standard flat $\Lambda$CDM model, with Om = 0.27 and Om$_\Lambda$ = 0.73. The true H0 value is assumed as 74. Note that since the two samples share the same parameters, their time delays are the same. For the uncertainties level, we assume a non-biased error with rms level as the larger on between 1\% level and 0.25 days.

In figure~, we illustrate the simulated lensed image that based on the same lensing parameters.

[fig]

\subsection{Model test}
%3. Modelling. Based on Lenstronomy, start with PSO and then MCMC. For lensed AGN, we adopt the PSF iteration. For lensed galaxy, the position of the invisible point source are taken from the lensed AGNs. We use a sample of 40 systems to estimate the scatter of the H0 inference. The kinematic information is not considered, since the goal of this paper is to make a direct comparisons.
We use the strong lensing modeling tool lenstronomy to perform the modelling. For the lensed AGN systems, the typical modelling approaching is adopted. We manually boost the Poisson noise level to mitigate the drizzling effects. 
[] The PSF uncertainty 0.1. 
[] The lens images are combining with the time delay data to joint infer the time delay distance, hence the h0.
[] Mask was added.
[] We input the true parameters as the initial values to perform the Minimization. Finally, the H0 inferred from the overall 50 systems are considered as 50 times realizations to investigate the uncertainty and the accuracy.

We adopt the same approach to model the lensed non-AGN systems. Since the point source are not appeared in the image, we applied the astrometry information inferred from lensed AGN systems to mimic the situation when a SN is blooming with point source available.

\section{Comparison results}
[] The lensed AGN case is non-biased, but the scatter is larger. This scatter represent the precision level when modeling the lensed without taken the kinematic information. 
[]When AGN disappear, the non-biased H0 can be still inferred and the scatter is improved by a factor of $\sim$3.

\section{What does this result mean?}
[] Lens modeling alone would improved by a factor of 3 in the future lensed SN case.
[] What about the improvement of the H0? a combination discussion of the time delay (precision and micro-lensing), the lens modelling. The kinematic measurement of the deflector should also be improved. What about the kappa external? probably kext would dominate the uncertainty.

\section{Conclusions and discussions}

\section*{Acknowledgments}
This work was supported by the National Natural Science Foundation of China (NSFC) No. 11973034.

\begin{thebibliography}{}
\bibitem[\protect\citeauthoryear{Abbott et al.}{2016}]{Abbott2016} Abbott B. P., Abbott R., Abbott T. D., et al. 2016, Phys. Rev. Lett., 116, 061102
\bibitem[\protect\citeauthoryear{Abbott et al.}{2019}]{Abbott2019b} Abbott B. P., Abbott T. D., Abraham S., et al. 2019, ApJL, 882, L24
\bibitem[\protect\citeauthoryear{Alcock et al.}{2000}]{Alcock2000} Alcock C., et al. [MACHO Collaboration], 2000, ApJ, 542, 281
\bibitem[\protect\citeauthoryear{Ali-Haimoud et al.}{2017}]{Ali-Haimoud2017}  Ali-Ha\"{\i}moud Y., Kamionkowski M. 2017, Phys. Rev. D, 95, 043534
\bibitem[\protect\citeauthoryear{Benton et al.}{2007}]{Benton2007} Benton Metcalf R., Silk J. 2007, Phys. Rev. Lett., 98, 071302
\bibitem[\protect\citeauthoryear{Bird et al.}{2016}]{Bird2016} Bird S., Cholis I., Mu\~noz J. B., et al. 2016, Phys. Rev. Lett., 116, 201301
\bibitem[\protect\citeauthoryear{Brandt et al.}{2016}]{Brandt2016} Brandt T. D. 2016, ApJ, 824, L31
\bibitem[\protect\citeauthoryear{Carr et al.}{1974}]{Carr1974} Carr B. J., Hawking S. W. 1974, MNRAS, 168, 399
\bibitem[\protect\citeauthoryear{Carr et al.}{1975}]{Carr1975} Carr B. J. 1975, ApJ, 201, 1
\bibitem[\protect\citeauthoryear{Calchi Novati et al.}{2013}]{Calchi Novati2013} Calchi Novati S., Mirzoyan S., Jetzer P., Scarpetta G. 2013, MNRAS, 435, 1582
\bibitem[\protect\citeauthoryear{Cao et al.}{2014}]{Cao2014} Cao Z., Li L.-F., Wang Y. 2014, Phys. Rev. D, 90, 062003
\bibitem[\protect\citeauthoryear{Collett et al.}{2017}]{Collett2017} Collett T. E., Bacon D. 2017, Phys. Rev. Lett., 118, 091101
\bibitem[\protect\citeauthoryear{Christian et al.}{2018}]{Christian2018} Christian P., Vitale S., Loeb A. 2018, Phys. Rev. D, 98, 103022
\bibitem[\protect\citeauthoryear{Dai et al.}{2018}]{Dai2018} Dai L., Li S.-S., Zackay B., Mao S., Lu Y. 2018, Phys. Rev. D, 98, 104029
\bibitem[\protect\citeauthoryear{Ding et al.}{2015}]{Ding2015} Ding X., Biesiada M., Zhu Z.-H. 2015, JCAP, 12, 006
\bibitem[\protect\citeauthoryear{Ding et al.}{2020}]{Ding2020} Ding X., Liao K., Biesiada M., Zhu Z.-H. 2020, ApJ, 891, 76
\bibitem[\protect\citeauthoryear{Dominik et al.}{2013}]{Dominik2013} Dominik M., Belczynski K., Fryer C., et al. 2013, ApJ, 779, 72
\bibitem[\protect\citeauthoryear{Fan et al.}{2017}]{Fan2017} Fan X.-L., Liao K., Biesiada M.,  et al. 2017, Phys. Rev. Lett., 118, 091102
\bibitem[\protect\citeauthoryear{Finn et al.}{1996}]{Finn1996} Finn L. S. 1996, Phys. Rev. D, 53, 2878
\bibitem[\protect\citeauthoryear{Fishbach et al.}{2018}]{Fishbach2018}Fishbach M., Holz D. E., Farr W. M. 2018, ApJL, 863, L41
\bibitem[\protect\citeauthoryear{Griest et al.}{1991}]{Griest1991} Griest K. 1991, ApJ, 366, 412
\bibitem[\protect\citeauthoryear{Hardy et al.}{2017}]{Hardy2017} Hardy E. 2017, JHEP, 02, 046
\bibitem[\protect\citeauthoryear{Hou et al.}{2019}]{Hou2019} Hou S., Fan X.-L., Liao K., Zhu Z.-H. 2019, arXiv: 1911.02798
\bibitem[\protect\citeauthoryear{Ji et al.}{2018}]{Ji2018} Ji L., Kovetz E. D., Kamionkowski M. 2018, Phys. Rev. D, 98, 123523
\bibitem[\protect\citeauthoryear{Jung et al.}{2019}]{Jung2019} Jung S., Shin C. S. 2019, Phys. Rev. Lett., 122, 041103
\bibitem[\protect\citeauthoryear{Kovetz et al.}{2017}]{Kovetz2017}Kovetz E. D., Cholis I., Breysse P. C.,  Kamionkowski M. 2017, Phys. Rev. D, 95, 103010
\bibitem[\protect\citeauthoryear{Lai et al.}{2018}]{Lai2018} Lai K.-H., Hannuksela O. A., Herrera-Martin A.,  et al. 2018, Phys. Rev. D, 98, 083005
\bibitem[\protect\citeauthoryear{Liao et al.}{2017}]{Liao2017} Liao K., Fan X.-L., Ding X., Biesiada M., Zhu Z.-H. 2017, Nature Communications, 8, 1148
\bibitem[\protect\citeauthoryear{Liao et al.}{2019}]{Liao2019} Liao K., Biesiada M., Fan X.-L. 2019, ApJ, 875. 139
\bibitem[\protect\citeauthoryear{Li et al.}{2018}]{Li2018} Li S.-S., Mao S., Zhao Y., Lu Y. 2018, MNRAS, 476, 2220
\bibitem[\protect\citeauthoryear{Mediavilla et al.}{2009}]{Mediavilla2009} Mediavilla E., Mu\~{n}oz J. A., Falco E., et al. 2009, ApJ, 706, 1451
\bibitem[\protect\citeauthoryear{Monroy-Rodriguez et al.}{2014}]{Monroy-Rodriguez2014} Monroy-Rodr\'{\i}guez M. A., Allen C. 2014, ApJ, 790, 159
\bibitem[\protect\citeauthoryear{Munoz et al. 2016}{}]{Munoz2016} Mu\~{n}oz J. B., Kovetz E. D., Dai L., Kamionkowski M. 2016, Phys. Rev. Lett., 117, 091301
\bibitem[\protect\citeauthoryear{Mishra et al.}{2010}]{Mishra2010} Mishra C. K., Arun K. G., Iyer B. R., Sathyaprakash B. S. 2010, Phys. Rev. D, 82, 064010
\bibitem[\protect\citeauthoryear{Nakamura et al.}{1998}]{Nakamura1998} Nakamura, T. T. 1998, Phys. Rev. Lett., 80, 6
\bibitem[\protect\citeauthoryear{Niikura et al.}{2017}]{Niikura2017} Niikura H., Takada M., Yasuda N.,  et al. 2017, Nature Astronomy, 3, 524
\bibitem[\protect\citeauthoryear{Oguri et al.}{2018}]{Oguri2018} Oguri M., Diego J. M., Kaiser N., Kelly P. L., Broadhurst T. 2018, Phys. Rev. D, 97, 023518
\bibitem[\protect\citeauthoryear{Oguri}{2018}]{Oguri2018a} Oguri, M. 2018, MNRAS, 480, 3842
\bibitem[\protect\citeauthoryear{Pooley et al.}{2009}]{Pooley2009} Pooley D., Rappaport S., Blackburne J., et al. 2009, ApJ, 697, 1892
\bibitem[\protect\citeauthoryear{Quinn et al.}{2009}]{Quinn2009} Quinn D. P., Wilkinson M. I., Irwin M. J.,  et al. 2009, MNRAS, 396, 11
\bibitem[\protect\citeauthoryear{Ricotti et al.}{2009}]{Ricotti2009} Ricotti M., Gould A. 2009, ApJ, 707, 979
\bibitem[\protect\citeauthoryear{Ricotti et al.}{2008}]{Ricotti2008} Ricotti M., Ostriker J. P., Mack K. J. 2008, ApJ, 680, 829
\bibitem[\protect\citeauthoryear{Sasaki et al.}{2016}]{Sasaki2016} Sasaki M., Suyama T., Tanaka T., Yokoyama S. 2016, Phys. Rev. Lett., 117, 061101
\bibitem[\protect\citeauthoryear{Sereno et al.}{2010}]{Sereno2010} Sereno M., Bleuler A., Jetzer P.,  et al. 2010, Phys. Rev. Lett., 105, 251101
\bibitem[\protect\citeauthoryear{Smith et al.}{2018}]{Smith2018} Smith G. P., Jauzac M., Veitch J.,  et al. 2018, MNRAS, 475, 3823
\bibitem[\protect\citeauthoryear{Takahashi et al.}{2003}]{Takahashi2003} Takahashi R., Nakamura, T. 2003, ApJ, 595, 1039
\bibitem[\protect\citeauthoryear{Takahashi et al.}{2017}]{Takahashi2017} Takahashi R. 2017, ApJ, 835, 103
\bibitem[\protect\citeauthoryear{Tisserand et al.}{2007}]{Tisserand2007} Tisserand P., et al. [EROS-2 Collaboration], 2007, A\&A, 469, 387
\bibitem[\protect\citeauthoryear{Udalski et al.}{2015}]{Udalski2015} Udalski A., Szyma\'{n}ski M. K., Szyma\'{n}ski G. 2015, Acta Astromonica, 65, 1
\bibitem[\protect\citeauthoryear{Wang et al.}{1996}]{Wang1996} Wang Y., Stebbins A., Turner E. L. 1996, Phys. Rev. Lett., 77, 2875
\bibitem[\protect\citeauthoryear{Wei et al.}{2017}]{Wei2017} Wei J.-J., Wu X.-F. 2017, MNRAS, 472, 2906
\bibitem[\protect\citeauthoryear{Wilkinson et al.}{2001}]{Wilkinson2001} Wilkinson P. N., Henstock D. R., Browne I. W. A.,  et al. 2001, Phys. Rev. Lett., 86, 584
\bibitem[\protect\citeauthoryear{Wyrzykowski et al.}{2011}]{Wyrzykowski2011}  Wyrzykowski L., et al. 2011, MNRAS, 416, 2949
\bibitem[\protect\citeauthoryear{Yang et al.}{2019}]{Yang2019}Yang L., Ding X., Biesiada M., Liao K., Zhu Z.-H. 2019, ApJ, 874, 139Y

\end{thebibliography}

\label{lastpage}

\end{document}

### 2020-11-20 projects/Sim_HST_JWST/HST_lensed_QSO/manuscript/main.tex
Finishing the simualtion and plot the figure

@@
 \begin{abstract}
+  See the review by Oguri M.
+\citep{Oguri2019}.
 Strongly lensed explosive transients like supernovae, gamma ray bursts, fast radio bursts and gravitational waves are very promising to determine the Hubble constant ($H_0$) in the next stage.
@@
 include supernovae in all types,
-GW/SGRB+kilonava/afterglow association, LGRB+SN Ic/afterglow association and repeated FRB.
+GW/SGRB+kilonava/afterglow association~\citep{Liao2017}, LGRB+SN Ic/afterglow association and repeated FRB.
 
@@
 \subsection{Mock data simulations}
-The simulations of the 50 lensed AGN systems are based on the pipeline introduced by [Ding et al.].  The mock data are based on the observations using HST WFC/F160W.
-This pipeline has also been used in TDLMC and TDCOSMO-1 [ref]. We adopt the same simulating strategy as used TDLMC to generate the mock sample, which are summarized as below.
+The simulations of the 50 lensed AGN systems are based on the pipeline introduced by [Ding et al.].
+This approach has also been used in TDLMC and TDCOSMO-1 [ref].
+The mock data are assumed to be observed by HST through WFC/F160W.
+%We adopt the same simulating strategy as used TDLMC to generate the mock sample, which are summarized as below.
 
-The simulating ingredients includes the light from the deflector and active galaxies in the source plane.
-
+The simulating image is composed of the light from the deflector galaxy in the image plane and active galaxies in the source plane.
 The light profile of the galaxy is assumed as S\'ersic profile is parameterized by:
@@
 encloses half of the total light \citep{C+B99} and
-$q$ denotes the axis ratio.
+$q$ denotes the axis ratio. The light of the active nuclei is assumed as a non-resolved point source.
 
@@
 
-The assumed lensing parameters are randomly generated using the Table 2 in TDLMC-2.
+The assumed lensing parameters are randomly generated using the based on the same strategy as in Table 2 in TDLMC-2.
 The position of the source AGN is manually input so that all the lensed image are quads.
-The noise includes the Gaussian background noise and the Poisson noise which is based on the realistic HST condition with exposure time as 9,584 s.
+The noise includes the Gaussian background noise and the Poisson noise which is based on the realistic HST condition with exposure time as $\sim$9,600 s.
 The PSF is generated by tinytim.
@@
 The true H0 value is assumed as 74.
-Note that since the two samples share the same parameters, their time delays are the same.
+Note that since the two samples (i.e., with AGN and without AGN) share the same parameters, their time delays are the identical.
 For the uncertainties level, we assume a non-biased error with rms level as the larger on between 1\% level and 0.25 days.
@@
 
-\subsection{Model test}
+\subsection{Model }
 %3.
@@
 The kinematic information is not considered, since the goal of this paper is to make a direct comparisons.
-We use the strong lensing modeling tool lenstronomy to perform the modelling.
+We adopt the strong lensing modeling tool lenstronomy to perform the modelling.
+
 For the lensed AGN systems, the typical modelling approaching is adopted.
 We manually boost the Poisson noise level to mitigate the drizzling effects.
-[] The PSF uncertainty 0.1. 
-[] The lens images are combining with the time delay data to joint infer the time delay distance, hence the h0.
-[] Mask was added.
-[] We input the true parameters as the initial values to perform the Minimization.
-Finally, the H0 inferred from the overall 50 systems are considered as 50 times realizations to investigate the uncertainty and the accuracy.
+A mask region is defined to bracket the pixels with sufficient SNR with would be used to calculate the likelihood.
+To account for the fact that the information of the PSF is unknown, we assumed a 0.1 variance uncertainty on the input PSF image when modelling the point source.
+The true values used in the simulation are adopted as the initial values to allow a fast convergence of the particles.
+The lensing image are combined with the time delay data to achieve a joint-inference for the time delay distance.
+We adopt the particle swarm optimization (PSO) to derive the minimization best-fit result for each system.
+The resulting H0 is derived with Om fixed to the truth value 0.27.
+Finally, we consider the 50 lensed systems are considered as 50 times realizations to investigate the uncertainty and the accuracy.
 
-We adopt the same approach to model the lensed non-AGN systems.
-Since the point source are not appeared in the image, we applied the astrometry information inferred from lensed AGN systems to mimic the situation when a SN is blooming with point source available.
+The same approach is adopted to fit the lensed non-AGN system.
+Note that when calculate the time delay, the positions of the point source in the image plane and source plane are needed (i.e., alpha and beta in eq).
+However, for the non-AGN case the point source position in the image plane does not appear.
+We use the twin lensed AGN system and adopt the fitted point source position as the astrometry information.
+This strategy is to mimic the situation when a SN is explosion  with point source position captured.
 
-\section{Comparison results}
+Figure illustrate the modelling result for a twin systems.
+[ref]
+
+\section{Results}
 [] The lensed AGN case is non-biased, but the scatter is larger. This scatter represent the precision level when modeling the lensed without taken the kinematic information. 
@@
 \begin{thebibliography}{}
-\bibitem[\protect\citeauthoryear{Abbott et al.}{2016}]{Abbott2016} Abbott B. P., Abbott R., Abbott T. D., et al. 2016, Phys. Rev. Lett., 116, 061102
-\bibitem[\protect\citeauthoryear{Abbott et al.}{2019}]{Abbott2019b} Abbott B. P., Abbott T. D., Abraham S., et al. 2019, ApJL, 882, L24
-\bibitem[\protect\citeauthoryear{Alcock et al.}{2000}]{Alcock2000} Alcock C., et al. [MACHO Collaboration], 2000, ApJ, 542, 281
-\bibitem[\protect\citeauthoryear{Ali-Haimoud et al.}{2017}]{Ali-Haimoud2017}  Ali-Ha\"{\i}moud Y., Kamionkowski M. 2017, Phys. Rev. D, 95, 043534
-\bibitem[\protect\citeauthoryear{Benton et al.}{2007}]{Benton2007} Benton Metcalf R., Silk J. 2007, Phys. Rev. Lett., 98, 071302
-\bibitem[\protect\citeauthoryear{Bird et al.}{2016}]{Bird2016} Bird S., Cholis I., Mu\~noz J. B., et al. 2016, Phys. Rev. Lett., 116, 201301
-\bibitem[\protect\citeauthoryear{Brandt et al.}{2016}]{Brandt2016} Brandt T. D. 2016, ApJ, 824, L31
-\bibitem[\protect\citeauthoryear{Carr et al.}{1974}]{Carr1974} Carr B. J., Hawking S. W. 1974, MNRAS, 168, 399
-\bibitem[\protect\citeauthoryear{Carr et al.}{1975}]{Carr1975} Carr B. J. 1975, ApJ, 201, 1
-\bibitem[\protect\citeauthoryear{Calchi Novati et al.}{2013}]{Calchi Novati2013} Calchi Novati S., Mirzoyan S., Jetzer P., Scarpetta G. 2013, MNRAS, 435, 1582
-\bibitem[\protect\citeauthoryear{Cao et al.}{2014}]{Cao2014} Cao Z., Li L.-F., Wang Y. 2014, Phys. Rev. D, 90, 062003
-\bibitem[\protect\citeauthoryear{Collett et al.}{2017}]{Collett2017} Collett T. E., Bacon D. 2017, Phys. Rev. Lett., 118, 091101
-\bibitem[\protect\citeauthoryear{Christian et al.}{2018}]{Christian2018} Christian P., Vitale S., Loeb A. 2018, Phys. Rev. D, 98, 103022
-\bibitem[\protect\citeauthoryear{Dai et al.}{2018}]{Dai2018} Dai L., Li S.-S., Zackay B., Mao S., Lu Y. 2018, Phys. Rev. D, 98, 104029
-\bibitem[\protect\citeauthoryear{Ding et al.}{2015}]{Ding2015} Ding X., Biesiada M., Zhu Z.-H. 2015, JCAP, 12, 006
-\bibitem[\protect\citeauthoryear{Ding et al.}{2020}]{Ding2020} Ding X., Liao K., Biesiada M., Zhu Z.-H. 2020, ApJ, 891, 76
-\bibitem[\protect\citeauthoryear{Dominik et al.}{2013}]{Dominik2013} Dominik M., Belczynski K., Fryer C., et al. 2013, ApJ, 779, 72
-\bibitem[\protect\citeauthoryear{Fan et al.}{2017}]{Fan2017} Fan X.-L., Liao K., Biesiada M.,  et al. 2017, Phys. Rev. Lett., 118, 091102
-\bibitem[\protect\citeauthoryear{Finn et al.}{1996}]{Finn1996} Finn L. S. 1996, Phys. Rev. D, 53, 2878
-\bibitem[\protect\citeauthoryear{Fishbach et al.}{2018}]{Fishbach2018}Fishbach M., Holz D. E., Farr W. M. 2018, ApJL, 863, L41
-\bibitem[\protect\citeauthoryear{Griest et al.}{1991}]{Griest1991} Griest K. 1991, ApJ, 366, 412
-\bibitem[\protect\citeauthoryear{Hardy et al.}{2017}]{Hardy2017} Hardy E. 2017, JHEP, 02, 046
-\bibitem[\protect\citeauthoryear{Hou et al.}{2019}]{Hou2019} Hou S., Fan X.-L., Liao K., Zhu Z.-H. 2019, arXiv: 1911.02798
-\bibitem[\protect\citeauthoryear{Ji et al.}{2018}]{Ji2018} Ji L., Kovetz E. D., Kamionkowski M. 2018, Phys. Rev. D, 98, 123523
-\bibitem[\protect\citeauthoryear{Jung et al.}{2019}]{Jung2019} Jung S., Shin C. S. 2019, Phys. Rev. Lett., 122, 041103
-\bibitem[\protect\citeauthoryear{Kovetz et al.}{2017}]{Kovetz2017}Kovetz E. D., Cholis I., Breysse P. C.,  Kamionkowski M. 2017, Phys. Rev. D, 95, 103010
-\bibitem[\protect\citeauthoryear{Lai et al.}{2018}]{Lai2018} Lai K.-H., Hannuksela O. A., Herrera-Martin A.,  et al. 2018, Phys. Rev. D, 98, 083005
+\bibitem[\protect\citeauthoryear{Oguri}{2019}]{Oguri2019} Oguri M. 2019, Reports on Progress in Physics, 82, 12
 \bibitem[\protect\citeauthoryear{Liao et al.}{2017}]{Liao2017} Liao K., Fan X.-L., Ding X., Biesiada M., Zhu Z.-H. 2017, Nature Communications, 8, 1148
-\bibitem[\protect\citeauthoryear{Liao et al.}{2019}]{Liao2019} Liao K., Biesiada M., Fan X.-L. 2019, ApJ, 875. 139
-\bibitem[\protect\citeauthoryear{Li et al.}{2018}]{Li2018} Li S.-S., Mao S., Zhao Y., Lu Y. 2018, MNRAS, 476, 2220
-\bibitem[\protect\citeauthoryear{Mediavilla et al.}{2009}]{Mediavilla2009} Mediavilla E., Mu\~{n}oz J. A., Falco E., et al. 2009, ApJ, 706, 1451
-\bibitem[\protect\citeauthoryear{Monroy-Rodriguez et al.}{2014}]{Monroy-Rodriguez2014} Monroy-Rodr\'{\i}guez M. A., Allen C. 2014, ApJ, 790, 159
-\bibitem[\protect\citeauthoryear{Munoz et al. 2016}{}]{Munoz2016} Mu\~{n}oz J. B., Kovetz E. D., Dai L., Kamionkowski M. 2016, Phys. Rev. Lett., 117, 091301
-\bibitem[\protect\citeauthoryear{Mishra et al.}{2010}]{Mishra2010} Mishra C. K., Arun K. G., Iyer B. R., Sathyaprakash B. S. 2010, Phys. Rev. D, 82, 064010
-\bibitem[\protect\citeauthoryear{Nakamura et al.}{1998}]{Nakamura1998} Nakamura, T. T. 1998, Phys. Rev. Lett., 80, 6
-\bibitem[\protect\citeauthoryear{Niikura et al.}{2017}]{Niikura2017} Niikura H., Takada M., Yasuda N.,  et al. 2017, Nature Astronomy, 3, 524
-\bibitem[\protect\citeauthoryear{Oguri et al.}{2018}]{Oguri2018} Oguri M., Diego J. M., Kaiser N., Kelly P. L., Broadhurst T. 2018, Phys. Rev. D, 97, 023518
-\bibitem[\protect\citeauthoryear{Oguri}{2018}]{Oguri2018a} Oguri, M. 2018, MNRAS, 480, 3842
-\bibitem[\protect\citeauthoryear{Pooley et al.}{2009}]{Pooley2009} Pooley D., Rappaport S., Blackburne J., et al. 2009, ApJ, 697, 1892
-\bibitem[\protect\citeauthoryear{Quinn et al.}{2009}]{Quinn2009} Quinn D. P., Wilkinson M. I., Irwin M. J.,  et al. 2009, MNRAS, 396, 11
-\bibitem[\protect\citeauthoryear{Ricotti et al.}{2009}]{Ricotti2009} Ricotti M., Gould A. 2009, ApJ, 707, 979
-\bibitem[\protect\citeauthoryear{Ricotti et al.}{2008}]{Ricotti2008} Ricotti M., Ostriker J. P., Mack K. J. 2008, ApJ, 680, 829
-\bibitem[\protect\citeauthoryear{Sasaki et al.}{2016}]{Sasaki2016} Sasaki M., Suyama T., Tanaka T., Yokoyama S. 2016, Phys. Rev. Lett., 117, 061101
-\bibitem[\protect\citeauthoryear{Sereno et al.}{2010}]{Sereno2010} Sereno M., Bleuler A., Jetzer P.,  et al. 2010, Phys. Rev. Lett., 105, 251101
-\bibitem[\protect\citeauthoryear{Smith et al.}{2018}]{Smith2018} Smith G. P., Jauzac M., Veitch J.,  et al. 2018, MNRAS, 475, 3823
-\bibitem[\protect\citeauthoryear{Takahashi et al.}{2003}]{Takahashi2003} Takahashi R., Nakamura, T. 2003, ApJ, 595, 1039
-\bibitem[\protect\citeauthoryear{Takahashi et al.}{2017}]{Takahashi2017} Takahashi R. 2017, ApJ, 835, 103
-\bibitem[\protect\citeauthoryear{Tisserand et al.}{2007}]{Tisserand2007} Tisserand P., et al. [EROS-2 Collaboration], 2007, A\&A, 469, 387
-\bibitem[\protect\citeauthoryear{Udalski et al.}{2015}]{Udalski2015} Udalski A., Szyma\'{n}ski M. K., Szyma\'{n}ski G. 2015, Acta Astromonica, 65, 1
-\bibitem[\protect\citeauthoryear{Wang et al.}{1996}]{Wang1996} Wang Y., Stebbins A., Turner E. L. 1996, Phys. Rev. Lett., 77, 2875
-\bibitem[\protect\citeauthoryear{Wei et al.}{2017}]{Wei2017} Wei J.-J., Wu X.-F. 2017, MNRAS, 472, 2906
-\bibitem[\protect\citeauthoryear{Wilkinson et al.}{2001}]{Wilkinson2001} Wilkinson P. N., Henstock D. R., Browne I. W. A.,  et al. 2001, Phys. Rev. Lett., 86, 584
-\bibitem[\protect\citeauthoryear{Wyrzykowski et al.}{2011}]{Wyrzykowski2011}  Wyrzykowski L., et al. 2011, MNRAS, 416, 2949
-\bibitem[\protect\citeauthoryear{Yang et al.}{2019}]{Yang2019}Yang L., Ding X., Biesiada M., Liao K., Zhu Z.-H. 2019, ApJ, 874, 139Y
-
 \end{thebibliography}

### 2020-11-20 projects/Sim_HST_JWST/HST_lensed_QSO/F160W_simulation_v2/1_model.py

@@ -47,7 +47,7 @@ def cal_h0(zl, zs, Ddt, om=0.27):
     ratio = Ddt_corr/Ddt
     return 100 * ratio
 
-folder_list = glob.glob('sim_lens_ID_subg30_7??')
+folder_list = glob.glob('simulations_700_subg30/sim_lens_ID_subg30_7??')
 folder_list.sort()
 
 test_numer = 8
@@ -344,7 +344,7 @@ for folder in folder_list[kernel_i*run_n:kernel_i*run_n+run_n]:
         pickle.dump([multi_band_list, kwargs_model, kwargs_result, chain_list, fix_setting, mcmc_new_list], open(folder+savename, 'wb'))
     #%%Print fitting result:
     multi_band_list, kwargs_model, kwargs_result_best, chain_list, fix_setting, mcmc_new_list = pickle.load(open(folder+savename,'rb'))
-    fixed_lens, fixed_source, fixed_lens_light, fixed_ps, fixed_cosmo = fix_setting
+    # fixed_lens, fixed_source, fixed_lens_light, fixed_ps, fixed_cosmo = fix_setting
     labels_new = [r"$\gamma$", r"$D_{\Delta t}$","H$_0$" ]
     modelPlot = ModelPlot(multi_band_list, kwargs_model, kwargs_result_best, arrow_size=0.02, cmap_string="gist_heat")
     f, axes = modelPlot.plot_main()

### 2020-11-20 projects/Sim_HST_JWST/HST_lensed_QSO/F160W_simulation_v2/2_read_summary_results.py

@@ -7,12 +7,7 @@ Created on Tue Aug 29 21:20:09 2017
 """
 import numpy as np
 import matplotlib.pyplot as plt
-from matplotlib.colors import LogNorm
 import astropy.io.fits as pyfits
-import copy
-import time
-from lenstronomy.Util import constants as const
-import lenstronomy.Util.param_util as param_util
 import glob
 #file name:
 filt='f160w'
@@ -22,6 +17,10 @@ sys.path.insert(0,'../../../../py_tools/')
 from flux_profile import cr_mask
 from lenstronomy.Plots.model_plot import ModelPlot
 from mask_objects import find_loc_max
+
+import matplotlib as mat
+mat.rcParams['font.family'] = 'STIXGeneral'
+
 
 result_dic = {}
 
@@ -190,7 +189,13 @@ plt.ylim(-0.4,0.4)
 plt.tick_params(labelsize=20)
 plt.close()
 print(which[1], np.mean(gamma_bias_list), np.std(gamma_bias_list))
-fig, ax = plt.subplots(figsize=(11,8))
+
+#%%
+if 'noqso' in folder_type:
+    text = 'non-AGN'
+else:
+    text = 'AGN'
+fig, ax = plt.subplots(figsize=(8,8))
 for folder in folder_list:
     ID = folder[-3:]
     key = folder_type + '{0}'.format(ID)
@@ -202,13 +207,17 @@ for folder in folder_list:
         # plt.errorbar(gamma_bias, H0[1] - H0_true,
         #               yerr = [[H0[2]-H0[1]], [H0[1]-H0[0]]],
         #             ecolor='black', fmt='o', zorder=-500,markersize=1)      
-        plt.text(gamma_bias, H0[1] - H0_true, key[-3:],fontsize=15)
+        # plt.text(gamma_bias, H0[1] - H0_true, key[-3:],fontsize=15)
     #    ax.set_xticks(range(id_range[0]-1, id_range[1]+1,3)) 
-plt.xlabel(which[1]+" bias (inferred - truth)", fontsize=27)
+plt.plot(np.linspace(-0.3,0.3), np.linspace(-0.3,0.3)*0, 'k', alpha = 0.5 )
+plt.title('Lensed {0} case'.format(text), fontsize=27)    
+plt.xlabel("$\gamma$ bias (inferred - truth)", fontsize=27)
 plt.ylabel("$H_0$ bias (inferred - truth)", fontsize=27)
 plt.ylim(-20,20)
[…]

### 2021-11-24 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
Galight example, HSC online fitting, simulation paper updates

%% Beginning of file 'sample631.tex'
%%
%% Modified 2021 March
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.31 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls and other external packages such as
%% latexsym, graphicx, amssymb, longtable, and epsf.  Note that as of 
%% Oct 2020, APS now uses revtex4.2e for its journals but remember that 
%% AASTeX v6+ still uses v4.1. All of these external packages should 
%% already be present in the modern TeX distributions but not always.
%% For example, revtex4.1 seems to be missing in the linux version of
%% TexLive 2020. One should be able to get all packages from www.ctan.org.
%% In particular, revtex v4.1 can be found at 
%% https://www.ctan.org/pkg/revtex4-1.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%% using aastex version 6.3
%\documentclass[linenumbers]{aastex631}
\documentclass[twocolumn]{aastex631}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf TODO}: #1]}}
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}

\def\smass{{$M_*$}}
\def\sersic{S\'ersic}
\def\halpha{${\rm H}\alpha$}
\def\hbeta{${\rm H}\beta$}
\def\mbh{$\mathcal M_{\rm BH}$}
\def\lcdm{$\Lambda$CDM}
\def\hst{{\it HST}}
\def\kms{km~s$^{\rm -1}$}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{Simulation comparison}
\shortauthors{Ding et al.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{./}{figures/}}
%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{The Black Hole and Galaxy coevolution at $0.2<z<1.7$ using extensive comparisons between observation and simulation}

\author[0000-0001-8917-2148]{Xuheng Ding}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}

\author[0000-0002-1605-915X]{Junyao Li}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
\affiliation{CAS Key Laboratory for Research in Galaxies and Cosmology, Department of Astronomy, University of Science and Technology of China, Hefei 230026, China}
\affiliation{School of Astronomy and Space Science, University of Science and Technology of China, Hefei 230026, China}

\author[0000-0002-0000-6977]{John D.Silverman}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}

\author[0000-0002-8460-0390]{Tommaso Treu}
\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}

\author{Friends}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
We carry out a direct comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies (\mbh -- \smass) at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN,  TNG and semianalytic model). The observational measurements consistent of 612 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter. To make the fair comparisons, we first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as that based on observations. Our analysis demonstrates that all simulations predict a comparable level of dispersion of the scaling relations up to $z\sim1.7$, even after consideration of observational uncertainties which are non-negligible. 
%We also find that the selection criteria for the $z<1$ do not produce strong effects on the simulated relation
%Thus, the original relations (i.e., before adding noise) predicted by the simulation are supposed to have consistent intrinsic scatter compared with the observational data. 
%Considering that the tight relation of the scaling relation is highly rely on the AGN feedback, our results support the hypothesis of the AGN feedback being responsible for a causal link between the BH and its host galaxy, resulting in a tight correlation between their respective masses.
Hence, our results support the hypothesis that AGN feedback plays a role in a causal link between the BH and its host galaxy, resulting in a non-evolving and tight correlation between their respective masses. 
\todo{Mentioning the central comparison.}

%\todo{Add comments on the center positions. KS test. Estimation of the intrinsic scatter.}
\end{abstract}
\keywords{Galaxy evolution (594); Active galaxies (17); Active galactic nuclei (16)}

\section{Introduction} \label{sec:intro}
The close correlations between supermassive black holes and the properties of their host galaxies (e.g., stellar mass) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}. To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determin how and when the correlation emerges and evolves over cosmic time \citep[e.g.,][]{Peng2006a, Tre++07, Woo++08, Jahnke2009, Bennert11, Schramm2013, Park15, Mechtley2016, Ding2020, 2021arXiv210902751L}. While, an {\it apparent} evolution has been found in which the growth of BHs predates that of the host, equally as many studies claim a lack of evolution when considering the host total stellar mass. However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014}.

Various theoretical models have been proposed to explain the origin of the scaling relations. For example, AGN feedback is considered as one of the possible viable mechanisms. During this process, a fraction of the AGN energy is injected into its surrounding gas, which can then regulate the mass growth of the BH and its host. In this scenario, star formation is inhibited by the heating and unbinding of a significant amount of gas. Alternatively, the mass relations can be explained through an indirect connection in which AGN accretion and star formation are fed through a common gas supply~\citep{Cen2015, Menci2016}. Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}. However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ as observed today.

Numerical simulations provide an opportunity to further understand the origin of the connection between BHs and their host galaxies. For example, a comparison of scaling relations has been made between predictions by the state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and observational measurements at  $0.3<z<1$ based on HST imaging \citep[e.g., ][]{DeG++15}, which show a positive evolution (i.e., the mass growth of the BH growth predates that of its host). Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution, including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments suite of SPH simulations~\citep{Schaye2015}, Illustris moving-mesh simulation~\citep{Sijacki2015, Vogelsberger2014, Li2019} and the SIMBA simulation~\citep{Thomas2019}. In recent work, the BH populations from the six large-scale cosmological simulations have been adopted to compare the \mbh-\smass\ with observation of the local universe~\citep{Habouzit2021}. However, these comparison works are limited by the observation data in terms of the sample size ($<$100) and redshift range ($z<1$).

For such comparisons using simulations, it is crucial to consider the systematic uncertainties and selection biases. A direct means to account for these is to apply the same effects and selection to the simulation products and make a forward comparison in the observational plane. In~\citet{Ding2020b}, a direct comparison has been performed using 32 X-ray-selected AGN at $1.2<z<1.7$ and a direct comparison with two state-of-the-art simulation efforts, including {\tt MassiveBlackII} (MBII) and a Semianalytic Model (SAM). The dispersion in the mass ratio between black hole mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) confirming the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.

In this study, we extend our previous work, comparing the observational measurements to that from simulations, by adding recent measurements of hundreds of SDSS quasar at $0.2<z<0.8$ based on wide and deep HSC imaging from the Strategic Subaru Program. Furthermore, we extend the simulated quasar populations by including MBII, SAM, Illustris, TNG100, TNG300 and Horizon-AGN. This paper is structured as follows. In Sections~\ref{sec:observations} and~\ref{sec:simulations}, we describe our observation and simulation sample. The direct comparison is performed and the result is presented in Section~\ref{sec:result}. The concluding remarks are presented in Section~\ref{sec:con}.

%\section{Comparison Sample: Observations and Simulations} \label{sec:sample}
%The correlations of \mbh-\smass\ between the observed data and the numerical simulations are compared in this work. 
%We introduce the comparison samples in this section, including the observational data and the numerical simulations.

\section{Observational data set}
\label{sec:observations}
The observed sample consists of 900 uniformly-selected SDSS quasars at $0.2<z<0.8$, imaged by Subaru/HSC \citep{Li2021a}, and 32 quasars at $1.2<z<1.7$ as imaged by~\hst and described in \citep[][hereafter D20]{Ding2020}. The latter are selected from three deep-survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008}. Further details of these two samples and their measurements are given below.

\subsection{HSC}\label{sec:hsc}
A sample of $\sim$5000 type-1 SDSS quasars from the DR14 catalog~\citep{Paris2018} at $0.2<z<1$ has been imaged by the high-resolution Subaru Strategic Program (SSP) wide area survey~\citep{Aihara2019} using Hyper Suprime-Cam~\citep{Miyazaki2018}. With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been performed \citep[][hereafter L21a]{Li2021a} to obtain the flux and color of each quasar's host galaxy. The stare-of-the-art image modeling software {\tt lenstronomy} \citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task. This approach is first developed by~\citet{Ding2020} and used to decompose the near-infrared emission of the HST sample (see next section). Having measured the host light in each band, the stellar mass of host galaxy is derived using spectral energy distribution (SED) fitting with CIGALE~\citep{Boquien2019}. Simulation tests are also performed to verify the fidelity of the \smass\ measurements. The statistical measurement error on \smass\ is at the $\sim$0.2~dex level. The values of \mbh\ are determined by~\citet{Rakshit2020} which are estimated based on the \hbeta-based measurements using the virial method~\citep{Peterson2004, Vestergaard2006}. The typical error of \mbh\ are estimated to be 0.4 dex. We refer the reader to~\citet{Li2021a} in the Section~4.2 for more details.

To avoid any potential biases related to the selection of the quasars, \citet[][hereafter, L21b]{2021arXiv210902751L} isolated 877 sources which are uniformly selected based on their PSF-magnitudes, color cuts using single-epoch SDSS photometry and the value of the measured \smass. Specifically, we use the {\it ugri} color-selected sample (228 sources) from SDSS I/II~\citep{Richards2002}, and the CORE sample from SDSS BOSS (408 sources) and eBOSS (241 sources) surveys~\citep{Ross2013, Myers2015} (hereafter the uniform sample). These samples are initially selected based on PSF-magnitude cuts of $15 < i < 19.1$ (for {\it ugri}), and $i > 17.8$ and $g, r < 22.0$ (for CORE). Finally, a limit on \smass\ is set to assure the detection of the host, especially since the rate and accuracy of detection is higher when \smass\ is increasing. These selections will be adopted in an equivalent manner to the simulated samples to mitigate selection effects thus allowing the fair comparison.

\subsection{HST}

A sample of 32 HST-observed AGN systems across the redshift range $1.2<z<1.7$ are selected from three deep-survey fields (COSMOS, (E)-CDFS-S, and SXDS). HSC/WFC3 IR camera is used to obtain the high-resolution imaging data (HST program GO-15115, PI: John Silverman) with six position dither pattern and a total exposure time $\sim$2348~s. The filters F125W ($1.2<z<1.44$) and F140W ($1.44<z<1.7$) were employed, according to the redshift of each target to bracket the 4000~\AA~break.  The AGN images are analyzed and decomposed to infer the host galaxies fluxes using the approach developed by D20 based on {\tt lenstronomy}. The HST ACS/F814W imaging data for 21/32 of the AGNs is also used to infer the host color. The results show that stellar templates of 1 and 0.625~Gyr can match the sample color at $z<1.44$ and $z>1.44$, respectively (see Figure 5 in D20). These best-fit models are used to estimate the stellar masses of the host galaxies. \mbh\ is determined by \citet{Schulze2018} using near-infrared spectroscopic observations of the broad \halpha\ emission line with the recipe provided by~\citep{Vestergaard2006}, in a consistent manner to that adopted for HSC sample. We refer the reader to D20 for a more detailed description of the analysis.

With a consistent approach, the measurements of the \mbh-\smass\ relations for the HST and HSC samples are obtained. Thus, we expect the measurement errors of these two samples to be at a comparable level (i.e., $\Delta$\mbh$=0.4~$dex, $\Delta$\smass$=0.2~$dex). 
Indeed, the two samples are consistent with a lack of evolution in the mass ratio (see Figure 6 of L20b), even though the sample selection is slightly different.

\section{Simulations}
\label{sec:simulations}
We introduce the simulation sample that adopted in this section. All the simulation are based on the larger-scale cosmological simulations, except the Semianalytic Model (SAM) simulation.
%\todo{Maybe we can also summarize the importance of AGN feedback somewhere here?}

\subsection{{\tt MassiveBlackII} (MBII)}
MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles. The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}. For dark matter and gas, the elements of the masses resolution are $1.1\times 10^7~M_{\odot}/h$ and $2.2\times 10^6~M_{\odot}/h$, respectively. The simulation includes a full modeling of gravity plus gas hydrodynamics, with a wide range of subgrid recipes to model the star formation~\citep{2003MNRAS.339..289S}, BH growth, and the feedback process. Halos were identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}. Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}. The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}, i.e., $\Omega_0=0.275$, $\Omega_l=0.725$, $\Omega_b=0.046$, $\sigma_8=0.816$, $h = 0.701$, $n_s=0.968$.

To model the growth of BH, a feedback prescription is adopted as detailed in the literature~\citep{2005Natur.433..604D, 2005MNRAS.361..776S}. In particular, the BH seed with mass $5\times 10^{5}~M_{\odot}/h$ are embedded into halos of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$. Once seeded, BH growth via gas accretion is assigned at a rate of $\dot{M}_{BH}={4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the interstellar medium (ISM) gas at cold phase; $v_{BH}$ is the relative velocity between the BH and its surrounding gas. The accreted gas is released as radiation at a radiative efficiency of 10\%. A fraction of 5\% of the radiated energy couples to the surrounding gas as black hole (or AGN) feedback~\citep{2005Natur.433..604D}. A mildly super-Eddington (two times Eddington rate) is allowed; however, unlike some previous work, the accretion rate in MBII adopt the prescription in~\citet{Pelupessy2007}, which does not include any artificial boost factor. Two BH are considered to be merged when their separation distance is below the simulation spatial resolution (i.e., the SPH smoothing length) and their relative speeds are lower than the local sound speed of the medium.

For the galaxy photometry, the initial SEDs of the BH host galaxies were determined by combining all the contributions from the overall start particles. The stellar SEDs were derived using the PEGASE-2~\citep{1999astro.ph.12179F} stellar population synthesis code with a Salpeter IMF. Finally, the galaxy SEDs are  cooperated with the desired filter response to obtain the broadband photometry (e.g., SDSS $r$-band magnitude).

As a common practice, the stellar mass is obtained by using a 3D spherical aperture of 30~kpc to represent the observed stellar mass. By this definition, it has been tested that the corresponding stellar mass function is consistent with the observation measurement~\citep[e.g.,][]{Pillepich2018}. Even more, the stellar mass using this 3D aperture can achieve good agreement to those measured within Petrosian radii in observational studies~\citep{Schaye2015}.

For further details of MBII simulation, we refer the reader to~\citet{Khandai2015}

\subsection{Semianalytic Model (SAM)}
We highlight here the main points of the simulation with respect to our study; for more detail, a full descriptions of the SAM simulation sample can be found in~\citet{Menci2016} which is based on semianalytic model introduced in~\citet{Menci2014}. For dark matter halos that merge with a larger halo, the impact of dynamical friction is assessed to define whether the halo will survive as a satellite or sink to the center of the dominant galaxy to increase its mass. The binary interactions (fly-by and merging), among satellite subhalos, are  also described by the model. In each halo, we compute the fraction of gas which cools because of the atomic processes and settles into a disk~\citep{Mo1998}. The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr, according to BH feeding; (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulating star formation (as well as BH accretion). The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation which returns a fraction of the disk gas into a hot phase. A Salpeter IMF is adopted in the SAM simulation.

The BHs primordial seeds are assumed to originate from PopIII stars with a mass $M_{seed}=100\,M_{\odot}$~\citep{Madau2001}, and to be initially present in all galaxy progenitors. The BH accretion is based on interactions feeding mode and disk instabilities feeding mode.
%\newline(1)~{\it triggered by interactions.} The interaction rate $\tau_r^{-1}=n_T\,\Sigma (r_t,v_c,V)\,V_{rel} (V)$ for galaxies with relative velocity $V_{rel}$ and number density $n_T$ in a common DM halo determines the probability for encounters, either fly-by or merging, through the corresponding cross sections $\Sigma$ given in~\citet{Menci2014}. The fraction of gas destabilized in each interaction corresponds to the loss $\Delta j$ of orbital angular momentum $j$, and depends on the mass ratio of the merging partners $M'/M$ and on the impact factor $b$.
%\newline(2)~{\it induced by disc instabilities.} We assume these to arise  in  galaxies with disc mass exceeding~\citep{Efstathiou1982} $M_{crit} =  {v_{max}^2 R_{d}/ G \epsilon}$ with $\epsilon=0.75$, where $v_{max}$ is the maximum circular velocity associated to each halo ~\citep{Mo1998}.  Such a criterion strongly suppresses the probability for disc instabilities to occur not only in massive, gas-poor galaxies, but also in dwarf galaxies characterized by small values of the gas-to-DM mass ratios. The instabilities induce loss of angular momentum resulting into strong inflows that we compute following the description in~\citet{Hopkins2011}, recast and extended as in~\citet{Menci2014}. 
\todo{This part should be updated for the new SAM version?}
A detailed treatment of AGN feedback is included, which is introduced in~\citet{Menci2008}. The assumption stems from the fast winds with velocity up to 
$10^{-1}c$ observed in the central regions of AGNs~\citep{Chartas2002, Pounds2003}. The supersonic outflows compress the gas into a blast wave terminated by a leading shock front, which moves outward with a lower but still supersonic speed, and sweeps out the surrounding medium. The model follows in detail the expansion of the blast wave through the galaxy disk, and computes the fraction of gas expelled from the galaxy. ~\citep[see, i.e.,][for the details.]{Menci2016}.

\subsection{Illustris}
The Illustris Project is a serise of larger-scale hydrodynamical simulations of galaxy formation which was introduced in~\citet{2014MNRAS.444.1518V, 2014Natur.509..177V}. The simulation consist of a volume of (106.5 cMpc)$^3$, and was run with the moving Voronoi mesh code {\tt Arepo}~\citep{2010MNRAS.401..791S}. Besides gravitational force and hydrodynamical fluxes, the simulation calculates the astrophysical process known to be crucial for galaxy formation~\citep{2013MNRAS.436.3031V, 2014MNRAS.438.1985T}, which includes gas cooling, a subresolution ISM model, stochastic SF with a density threshold of 0.13 cm$^{-3}$, stellar evolution, gas recycling, chemical enrichment, kinetic stellar feedback by SNe activity, BH activity (accretion and merging), and AGN feedback. A cosmological background consistent with WMAP9~\citep{2013ApJS..208...19H} and a Chabrier IMF is adopted.

The BH seeding in the simulation is based on DM halo mass -- when a halo reaching a mass of $7.10 \times 10^{10} M_{\odot}$ is inserted with a BH with initial mass of $1.42 \times 10^5 M_{\odot}$. Then, the BH accretion follows the Bondi-Hoyle-Lyttleton formalism ($\alpha4\pi G^2M_{BH}^2 \rho/c_s^3$), but capped at the Eddington limit. The boost factor $\alpha$ is introduced to compensate that the ISM multiphase structure is unresolved~\citep{Springel2005, 2009MNRAS.398...53B}, since simulation usually underestimate the density around a BH.

The AGN feedback consists of three components: thermal quasar-mode feedback; thermal-mechanical radio-mode feedback; and radiative feedback. Through these process, the AGNs are able to deposit thermal energy into their surroundings with a coupling efficiency of 0.05 in for BHs with low Eddington ratio (i.e., $f_{\rm Edd} < 0.05$). For BHs with $f_{\rm Edd} > 0.05$, the thermal energy is released in hot bubbles with a radius of $\sim$ 100~kpc and couple to the gas with an efficiency of 0.35. It is highlighted in ~\citet{2014MNRAS.444.1518V} that the AGN feedback is the key process in quenching massive galaxy which is crucial to reproduce a tight stellar mass and BH mass relation.

\subsection{IllustrisTNG}
{\it The Next Generation Illustris Simulations} (IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018} are an ambitious suite of hydrodynamical simulations of galaxy formation in large cosmological volumes. It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modelling, and 3) addressing the identified shortcomings of the previous generation simulations.

The TNG100 and TNG300 have a volume of (111~cMpc)$^3$ and (302~cMpc)$^3$, respectively. They use the same initial condition with the previous Illustris simulation. The adopted cosmological parameters are updates by the Planck result~\citep{2016A&A...594A..13P}.
Dark matter halos with a mass exceeding $7.38 \times 10^{10} M_{\odot}$ are seeded in their center using BHs with initial mass as $1.18 \times 10^6 M_{\odot}$, one order of magnitude higher than the assumptions in the previous Illustris simulation. The BHs accretion also follows the Bondi-Hoyle-Lyttleton formalism, but without any boost factor. The assumption of the magnetic fields can affect the relationship between the BHs and their host galaxies properties; the \mbh-\smass\ mean relation is higher with magnetic fields~\citep{2018MNRAS.473.4077P}. The TNG simulation also employs a kernel-weighted accretion rate over about 256 neighboring cells. Thus, the TNG BH can build up correlation with the gas properties in the galaxy central region.

TNG includes a two-mode AGN feedback: for high accretion rates -- injection of thermal energy in the surroundings of the BHs accreting; for low accretion rates -- directional injection of momentum with random direction~\citep{2017MNRAS.465.3291W, 2018MNRAS.479.4056W}. The transition between two modes is set by the minimum value of 0.1 and $2 \times 10 ^{-3} \times (M_{BH} / 10^8/M_{\odot})$.

\subsection{Horizon-AGN}
The simulation of Horizon-AGN~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D} has a volume of (142 cMpc)$^3$ which was generated based on the adaptive mesh refinement code {\tt Ramses}~\citep{2002A&A...385..337T} with a $\Lambda$CDM model based on WMAP7~\citep{2011ApJS..192...18K} cosmological results. The total volume contains $1024^3$ DM particles, corresponding to a DM mass resolution of $8 \times 10^7  M_{\odot}$  and initial gas resolution of  $1\times10^7M_{\odot}$. A Salpeter IMF is assumed in Horizon-AGN simulation.

Different from the previous simulations, Horizon-AGN uses a fixed threshold in the dark matter halo mass. Star formation occurs in regions with gas number density exceeds the star formation threshold $n_0 = 0.1$. The BHs also form in this dense gas cells with stellar velocity dispersion larger than 100 km/s. BH seeds are not formed when they are closer than 50 ckpc of an existing BH. After $z = 1.5$, BHs are prevented from forming. At that time, all the progenitors of the \smass$>10^{10} M_{\odot}$ galaxies at $z = 0$ should be formed and seeded with BHs~\citep{2016MNRAS.460.2979V}. Horizon-AGN simulation also include the feedback from stellar winds, SNe Type Ia and Type II with mass, energy and metal release.

The BH accretion is computed using the Bondi-Hoyle-Lyttleton formalism with a boost factor $\alpha = (\rho/\rho_0)^2$ when the density $\rho$ is higher than the resolution-dependent threshold $\rho_0$. Otherwise, the boost factor is fixed as unity~\citep{2009MNRAS.398...53B}.

Horizon-AGN includes a two mode AGN feedback. In the high state mode ($f_{\rm Edd}<0.01$), thermal energy is isotropically released within a sphere of radius a few resolution elements. The energy deposition rate is $\dot{E}_{\rm AGN} = 0.015 \dot{M}_{\rm BH} c^2$. In the low state mode, energy is injected into a bipolar  outflow  with  a  velocity  of  10$^4$ km/s,  to  mimic the  formation  of  a  jet.  The  energy  rate  in  this  mode is $\dot{E}_{\rm AGN} = 0.1 \dot{M}_{\rm BH} c^2$.  The  technical  details  of  BH  formation,  growth  and  feedback  modeling  of  Horizon-AGN  can be found in~\citet{2012MNRAS.420.2662D}

%Horizon-AGN  employs  a  kinetic  SN  feedback,  including momentum, mechanical energy and metals from type~II, Type  Ia  SNe,  and  stellar  winds  (details  in  Kaviraj  et  al.2017).  The  feedback  is  modelled  as  kinetic  release  of  energy on timescale below 50 Myr, and a thermal energy after 50 Myr. The feedback is also pulsed, meaning that energy is accumulated until sufficient to propagate the blast wave to  at  least  two  cells.  The  energy  released  depends  on  theSSP modeled assumed and the metallicity of the gas, and is aboute SN $\sim10^{49}$ erg/$M_{\odot}$.

We summarized some key elements in the simulation in Table~\ref{tab:sim_sum}.

\begin{deluxetable*}{lcccccc}
%\tablenum{1}
\tablecaption{Summary of some key assumptions for the hydrodynamic simulations analyzed by this work.\label{tab:sim_sum}}
\tablewidth{0pt}
\tablehead{
%\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
%  \cline{2-4}  \cline{5} \\
\colhead{Simulation} & \colhead{box sizes} & particles &  \colhead{resolution} & \colhead{feedback prescription} & \colhead{AGN fueling mechanism}  & what else?
}
\startdata
%SAM & \\
MBII & $100~\mathrm{cMpc/h}$ & $2\times1792^3$ &&& \\
Illustris &&&&& \\
TNG100 &&&&& \\
TNG300 &&&&& \\
Horizon-AGN &&&&& \\
\enddata
%\tablecomments{This table }
\end{deluxetable*}

\subsection{Application of observational selection effects}
To make direct comparisons with observations, we add measurement errors and apply the equivalent selection to the simulated samples. We first inject random noise to the simulated catalog to mimic the scatter caused by the measurement error. As mentioned above, \smass\ and \mbh\ for HSC and HST samples are measured with a similar approach thus their uncertainty levels are expected to be equivalent. 
We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = 0.17~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.

We then apply restrictions on the noise-injected simulation to mimic selection effects as present in the observational data. Since the HSC and HST samples have their own selection function, we apply different selection criteria to the simulation as follows.
\begin{itemize}

 \item{}HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should be consistent with the \mbh-$L_{\rm bol}$ relation of the HSC sample. We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it top}). (2) The $i$-band magnitude of the AGN are bright (see Section~\ref{sec:hsc}). The specific selection is made as follows: for systems at $z<0.5$ and $z>0.5$, the AGN $i$-band magnitude are required to be brighter than 20.5 mag and 22.0 mag, respectively. Since the simulations do not provide the AGN observed magnitude, we adopt the simulated rest-frame magnitude or L$_{\rm 5100}$ and assume the quasar continuum as a single power-law with an index of $\alpha_\nu=-0.44$~\citep{2001AJ....122..549V} to calculate the observed $i$-band magnitude.
 3)~Following the HSC selection, we require the \smass\ value to be above a certain level (according to their redshift) to assure an accurate measurement. Finally, the HSC sample is split into three redshift bins which are $0.2<z<0.4$, $0.4<z<0.6$, and $0.6<z<0.8$.

\item{}HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is same as the observational selection, see Figure~\ref{fig:selection}--{\it left} taken MBII as example. Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., between [7.7, 8.6] $M_{\odot}$). The HST sample covers the higher redshift range $1.2<z<1.7$, which is considered as a single redshift bin to make the comparison with the simulations at $z=1.5$.
\end{itemize}

\section{Results} \label{sec:result}
\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[width=0.5\textwidth]{HSC_selection_MBII.png}} &
{\includegraphics[width=0.45\textwidth]{HST_selection_MBII.png}}
\end{tabular}
%\caption{\label{fig:selection}Demonstration of the impact of AGN selection using MBII. {\it left}: Correlation between \mbh\ and %$L_{\rm bol}$ of the simulated HSC sample is used to set the selection window for the simulated sample. This region roughly bracket %the type-1 AGN sample. The light green background cloud shows the simulated number density distribution in this parameter space %which includes a random level of uncertainty to mimic observational measurement errors. {\it right}: Similar to the top plane -- %equivalent selection window adopted for the HST-observed and MBII simulated samples.
%}
\caption{\label{fig:selection}Demonstration of the impact of AGN selection using MBII. {\it left}: Distribution of \mbh\ and $L_{\rm bol}$ for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles). A matched HSC sample is shown by the orange data points. The light green background cloud shows the simulated number density distribution in this parameter space which includes a random level of uncertainty to mimic observational measurement errors. {\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample. The y-axis is now given as the Eddington ratio.}

\end{figure*}

In Figure~\ref{fig:comparsion}, we present the comparison of the scaling relation \mbh--\smass\ between the observations and the simulations. We use the local relation \mbh$=0.98$\smass$-2.56$ adopted by D20 (Chabrier based\footnote{Since different simulations adopt either the Chabrier or the Salpeter IMF, we will adopt the local relation and the \smass\ of the observation data based on the same IMF to ensure that the comparison with the observation data are self-consistent.}) as the fiducial to estimate relative offsets and dispersions. Different simulations are presented in each row and redshift intervals increase from left to right. 
For both the observational and simulated samples, the central offset and scatter of the scaling relation are estimated by the mean and the standard deviation of the \mbh\ residuals for each system\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the value remains the same.} (i.e., the offset to the local relation along the y-axis in Figure~\ref{fig:comparsion}).
We summarize of these offset distributions based on each redshift bins, as shown in Figure~\ref{fig:offsets}.
To visually inspect the comparison results, we show the offsets to the local relation (in terms of the $\Delta{\rm log}$\mbh) as a function of redshift (see Figure~\ref{fig:offsets_vz}, left). 
The values for the central offset and scatter in each case are given in Table~\ref{tab:sum}.

\begin{figure*}
\centering
\begin{tabular}{c c c c}
\vspace*{-0.1cm} 
{\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_SAM_zs_03.png}}&
\hspace*{-0.5cm} 
{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_SAM_zs_05.png}}&
\hspace*{-0.5cm} 
{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_SAM_zs_07.png}}&
\hspace*{-0.5cm} 
{\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_SAM_zs_15.png}}\\
\vspace*{-0.1cm} 
{\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_MBII_zs_03.png}}&
\hspace*{-0.5cm} 
{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_MBII_zs_06.png}}&
\hspace*{-0.5cm} &
\hspace*{-0.5cm} 
{\includegraphics[trim = 30mm 29mm 80mm 25mm, clip, height=0.25\textwidth]{MM_MBII_zs_15.png}}\\
\vspace*{-0.1cm} 
{\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Illustris_zs_03.png}}&
\hspace*{-0.5cm} 
{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Illustris_zs_05.png}}&
\hspace*{-0.5cm} 
{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Illustris_zs_07.png}}&
\hspace*{-0.5cm} 
{\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Illustris_zs_15.png}}\\
\vspace*{-0.1cm} 
{\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_03.png}}&
\hspace*{-0.5cm} 
{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_05.png}}&
\hspace*{-0.5cm} 
{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_07.png}}&
\hspace*{-0.5cm} 
{\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_15.png}}\\
\vspace*{-0.1cm} 
{\includegraphics[trim = 0mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_03.png}}&
\hspace*{-0.5cm} 
{\includegraphics[trim = 44mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_05.png}}&
\hspace*{-0.5cm} 
{\includegraphics[trim = 44mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_07.png}}&
\hspace*{-0.5cm} 
{\includegraphics[trim = 30mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_15.png}}\\
\end{tabular}
\caption{\label{fig:comparsion} 
The comparison of observed black hole mass vs. stellar mass relation from observation data and simulation products (by each row). The panels from left to right are based on different redshift bin. The black line in the panel indicates the local relation adopted by~\citet{Ding2020}. The background cloud shows the intrinsic simulation number density before injecting random noise that selection effect.
\todo{Xuheng will zoom in the figures and enlarger the text to show the them more clear.}
}
\end{figure*}

The absolute value of stellar masses in both observation and theory have significant uncertainty (up to factor of two), which depends on the assumption of initial mass function, and possibly on the implementation of star formation in the models. In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematics. Thus, in this work, we first consider the scatter as a diagnostic criteria to see whether some simulations match the data better than others. Interestingly, the results show that, almost all the simulations \blue{can produce the scatter values consistent with the observations across all the redshift range} --- for simulation sample at $z<1$, this scatter level is $\sim0.5$~dex, while for $z>1$, this scatter level is $\sim0.3$~dex. Note that the HST sample $z>1$ has narrow selection window based on the \mbh\ (see Figure~\ref{fig:selection}~bottom), leading to the result that the observed scatter is smaller than HSC sample at $z<1$.
\ding{In the simulation, is there any observational data that be used to give extra constrain on the recipe/assumption? Xuheng and John are surprised to see that all of them have very good scatter matches!}

We recognize that the observed scatter is dominated by the measurement uncertainties in the data. An understanding how much of the scatter derives from random noise can help us to determine the intrinsic scatter in the scaling relation. To this end, we measure the scatter of the simulation sample without injecting the random noise but adopting the same selecting window for both $z<1$ and $z>1$ sample to infer the central offset and scatter. We find that the intrinsic scatter is at a level of $\sim0.15-0.2$ dex for both $z<1$ and $z>1$ (see Table~\ref{tab:sum_no_noise}). These levels are consistent with the {\it intrinsic} scatter as estimated using observation data by~\citet{Ding2020, 2021arXiv210902751L}. More important, these values of the scatter are redshift-independent, suggesting that the tight scaling relation could not be explained by a pure stochastic process, i.e., random mergers. Still, the scatter is affected by sample selection, and thus these levels can only be taken as an approximation of the intrinsic scatter. We demonstrate these offset that without injecting noise as function of redshift in Figure~\ref{fig:offsets_vz}, right.
%their physical meaning should not be considered as the intrinsic scatter of the overall sample.

To further investigate how the offset values are correlated with stellar mass, we take the MBII sample as example and demonstrate them in Figure~\ref{fig:deltaMM}. We also use intrinsic simulation value and plot to address how random noise and selection effect changes the correlation. The same Figure based on the other simulations are presented in the Appendix. \todo{show the other simulation's result.}
%Taking \mbh\ and \smass\ as independent measurements, we also summarize their distributions and make comparison between the observation and simulation in the Appendix~\ref{app:function}.

We also investigate the central offset to understand whether the simulations deviate or not from the {\it observed} evolution of the scaling relation. According to the results in Table~\ref{tab:sum} and Figure~\ref{fig:offsets_vz}, at low redshift range $z<0.6$, Illustris and Horizon-AGN can predict consistent {\it apparent} \mbh\ offset to the observation data (at a level of $\lesssim0.1$ dex) over all redshifts considered. At higher redshift $0.6<z<1.5$, the simulations SAM, TNG100, TNG300 and Horizon-AGN follow the {\it observed} evolution. These results are consistent with the Kolmogorov-Smirnov (KS) test performed using the offset distributions between the simulation and the observation. The inference of the p-values are collected in Table~\ref{tab:pvalue}, showing that only the Illustris presents good match of the scaling relation at $z<0.6$ (i.e., p-value $> 0.1$), while the TNG100, TNG300 and Horizon simulation predict well at $z>0.6$.

%\renewcommand\thefigure{\arabic{figure}}
%\setcounter{figure}{1}  
%{\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_03.png}}&
%\hspace*{-0.5cm} 
%{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_05.png}}&
%\hspace*{-0.5cm} 
%{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_07.png}}&
%\hspace*{-0.5cm} 
%{\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_15.png}}\\
%{\includegraphics[trim = 0mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_03.png}}&
%\hspace*{-0.5cm} 
%{\includegraphics[trim = 44mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_05.png}}&
%\hspace*{-0.5cm} 
%{\includegraphics[trim = 44mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_07.png}}&
%\hspace*{-0.5cm} 
%{\includegraphics[trim = 30mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_15.png}}\\

\begin{figure*}
\centering
\begin{tabular}{c c c c}
\hspace*{-0.4cm} 
{\includegraphics[height=0.4\textwidth]{offset_dis_z03.pdf}}&
\hspace*{-0.4cm} 
{\includegraphics[height=0.4\textwidth]{offset_dis_z05.pdf}}&
\hspace*{-0.4cm} 
{\includegraphics[height=0.4\textwidth]{offset_dis_z07.pdf}}&
\hspace*{-0.4cm} 
{\includegraphics[height=0.4\textwidth]{offset_dis_z15.pdf}}\\
\end{tabular}
\caption{\label{fig:offsets} 
Histograms of the offset distributions for all simulation samples and observations. The mean value and the standard derivation of the histogram are summarized in Table~\ref{tab:sum}. The vertical lines show the corresponding mean value for each distribution. The mean values for observed sample (i.e., blue lines) are also show in each simulation plots.
For the MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$.
}
\end{figure*}

\begin{deluxetable*}{lccccc}
%\tablenum{1}
\tablecaption{Summary of the central offsets and scatters\label{tab:sum}}
\tablewidth{0pt}
\tablehead{
\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
\cline{2-4} 
%  \cline{2-4}  \cline{5} \\
\colhead{} &  \colhead{$0.2<z<0.4$} & \colhead{$0.4<z<0.6$} & \colhead{$0.6<z<0.8$} & \colhead{$1.2<z<1.7$} & IMF
}
\startdata
Observation & (0.07, 0.58) & (0.17, 0.52)  & (0.18, 0.54)  & (0.43, 0.31) \\
SAM & (0.73, 0.49) & (0.65, 0.46)  & (0.51, 0.45)  & (0.51, 0.36) & Salpeter \\
MBII & (-0.15, 0.48) & \multicolumn{2}{c}{(-0.16, 0.48) [$z=0.6$]}  & (0.14, 0.31) & Salpeter\\
Illustris & (0.01, 0.52) & (0.08, 0.53)  & (0.06, 0.54)  & (0.07, 0.32) &  Chabrier \\
TNG100 & (0.27, 0.48) & (0.24, 0.46)  & (0.24, 0.45)  & (0.38, 0.33) & Chabrier \\
TNG300 & (0.26, 0.48) & (0.20, 0.48)  & (0.17, 0.48)  & (0.41, 0.34) & Chabrier \\
Horizon-AGN & (0.20, 0.47) & (0.21, 0.48)  & (0.28, 0.47)  & (0.47, 0.35) & Salpeter\\
\enddata
\tablecomments{This table collects the  comparison results between different simulation at different redshift. The value shows the central position offset to the local relation and the scatters of the sample of the \smass-\mbh\ correlations. A positive offset means the \mbh\ value predicted by the simulation is higher than the compared measurement at fixed \smass\ value. The last column shows the corresponding IMF that adopted to the local anchor to make a fair comparison with the observation. For the MBII sample, the simulation does not produce the sample at $z=0.5$ or $z=0.7$, but rather at $z=0.6$. \blue{We use Monte Carlo approach to infer the uncertainties of the central offset and scatter for each simulation sample, finding that the uncertainties are within $\pm 0.03$.}
%This comparison includes the injection of noise and sample selection. and 
%The estimation of offsets are repeated up to 1000 times until the result is stable. 
}
\end{deluxetable*}

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[height=0.4\textwidth]{offset_summary_vz.pdf}}&
{\includegraphics[height=0.4\textwidth]{offset_int_summary_vz.pdf}}\\
\end{tabular}
\caption{\label{fig:offsets_vz} 
{\it left}: The apparent evolution of $\Delta{\rm log}$\mbh\ as a function of redshift using both observation and simulation data. The black line shows the evolution by fitting the offset as a function of redshift. The predictions from the numerical simulations are presented by different color regions, using the values in Table~\ref{tab:sum}.}
\end{figure*}

\begin{figure*}
\centering
\begin{tabular}{c c c}
\hspace*{-0.5cm} 
{\includegraphics[trim = 0mm 0mm 0mm 0mm, clip,
height=0.3\textwidth]{DeltaMM_MBII_zs_03.png}}&
\hspace*{-0.3cm} 
{\includegraphics[trim = 25mm 0mm 0mm 0mm, clip,
height=0.3\textwidth]{DeltaMM_MBII_zs_06.png}}&
\hspace*{-0.3cm} 
{\includegraphics[trim = 25mm 0mm 0mm 0mm, clip,
height=0.3\textwidth]{DeltaMM_MBII_zs_15.png}}\\
\end{tabular}
\caption{\label{fig:deltaMM} 
The comparison of the offset of the \mbh\ (to the local relation) as a function of stellar mass from observation data and the MBII simulation at three different redshift bins, with same format as Figure~\ref{fig:comparsion}. The histogram on the right indicates the offset distribution with lines indicates the mean value of the offset for observation and simulation. The green color distributions indicate the intrinsic simulation values that without random noise and selection effect. 
}
\end{figure*}

\begin{deluxetable*}{lcccc}
%\tablenum{1}
\tablecaption{Summary of the {\it intrinsic} central offsets and scatters\label{tab:sum_no_noise}}
\tablewidth{0pt}
\tablehead{
\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
\cline{2-4} 
%  \cline{2-4}  \cline{5} \\
\colhead{} &  \colhead{$0.2<z<0.4$} & \colhead{$0.4<z<0.6$} & \colhead{$0.6<z<0.8$} & \colhead{$1.2<z<1.7$}
}
\startdata
SAM & (0.72, 0.20) & (0.64, 0.18) & (0.56, 0.16)  & (0.08, 0.18) \\
MBII & (-0.15, 0.21) & \multicolumn{2}{c}{(-0.15, 0.22) [$z=0.6$]}  & (0.08, 0.19)\\
Illustris & (0.03, 0.32) & (0.10, 0.36) & (0.08, 0.36)  & (0.04, 0.19) \\
TNG100 &  (0.27, 0.20) & (0.27, 0.15) & (0.26, 0.16)  & (0.36, 0.15) \\
TNG300 & (0.25, 0.21) & (0.19, 0.23) & (0.20, 0.22)  & (0.32, 0.16) \\
Horizon-AGN & (0.24, 0.21) & (0.23, 0.22) & (0.29, 0.19)  & (0.37, 0.13) \\
%Previous are ones not adding noise but same selection, belows are not add noise and not select
%SAM & (0.75, 0.26) & (0.74, 0.26) & (0.94, 0.26)  & (0.59, 0.24) \\
%MBII & (-0.24, 0.22) & \multicolumn{2}{c}{(-0.26, 0.22) [$z=0.6$]}  & (-0.29, 0.22)\\
%Illustris & (-0.78, 0.40) & (-0.73, 0.40) & (-0.69, 0.40)  & (-0.55, 0.36) \\
%TNG100 &  (0.33, 0.31) & (0.31, 0.32) & (0.29, 0.33)  & (0.22, 0.37) \\
%TNG300 & (0.42, 0.58) & (0.40, 0.57) & (0.39, 0.56)  & (0.35, 0.54) \\
%Horizon & (0.12, 0.30) & (0.13, 0.30) & (0.14, 0.28)  & (-0.00, 0.48) \\
\enddata
\tablecomments{Same as Table~\ref{tab:sum} but without inject noise to the simulation data. Note that same selection window is still adopted to infer the values.}
\end{deluxetable*}

\begin{deluxetable*}{lcccc}
%\tablenum{1}
\tablecaption{Summary of the p-value using KS test \label{tab:pvalue}}
\tablewidth{0pt}
\tablehead{
\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison} & \colhead{HST comparison} \\
\cline{2-4} 
%  \cline{2-4}  \cline{5} \\
\colhead{} &  \colhead{$z\sim0.3$} & \colhead{$z\sim0.5$} & \colhead{$z\sim0.7$} & \colhead{$z\sim1.5$}
}
%\decimalcolnumbers
\startdata
SAM &  $<$1e-10 & $<$1e-10  & $<$1e-10  & 7.456907e-03  \\
MBII & 2.663415e-06 & \multicolumn{2}{c}{$<$1e-10 [$z=0.6$]}  & 2.218653e-06  \\
Illustris & 4.061962e-02 & 1.029493e-01  & 5.525678e-03  & 2.330195e-07  \\
TNG100 & 6.677469e-06 & 7.304761e-03  & 1.331638e-01  & 4.708287e-01  \\
TNG300 & 1.100287e-07 & 5.446812e-01  & 2.942672e-02  & 2.118038e-01  \\
Horizon & 1.306432e-01 & 3.175037e-01  & 5.094878e-02  & 1.953735e-01  \\
\enddata
\tablecomments{The p-value of the KS test between the simulation and the observation.}
\end{deluxetable*}

\section{Conclusion} \label{sec:con}
%A brief introduce of the result. Scatter, central, which is best...
We compare the scaling relation of \mbh-\smass\ using both the observation data and the predictions from numerical simulations. The observation data are composed of 612 quasars at $0.2 < z < 0.8$ imaged by HSC and 32 X-ray-selected quasars at $1.2 < z < 1.7$ imaged by HST. These observational measurements are compared with simulations including a semi-analytic model (SAM) and five hydrodynamic simulation, i.e., MBII, Illustris, TNG100, TNG300 and Horizon-AGN. We designed the direct comparisons that were made in the observational plane. To this end, we first injected random errors with the same observational uncertainty to the simulation, and then adopt the same selection condition to the simulation data. Finally, we adopted the scaling relation from the local universe and performed the comparisons using the scatter of the measurements and their central offset to the local relation.

%We also estimate the scatter of the sample without inject the noise.
Our main results are presented in Figure~\ref{fig:offsets_vz} and the Table~\ref{tab:sum} which summarize the scatter and the offset for each sample. These results show that the scatter predicted by the simulations are all consistent to the observational measurements, i.e., $\sim0.5$~dex at $z<1$ and $\sim0.3$~dex at $z>1$. We note that the scatter are {\it apparent} rather than {\it intrinsic}, which are affected by the observational error and the selection effects. To understand how much the random observational error dominates the scatter, we re-run the estimation without injecting noise to the simulations. The obtained scatter for both $z<1$ and $z>1$ are at a comparable level of $\sim$0.15$-$0.2 dex. This result suggests that the tightness of the scaling relations have been formed up to redshift 1.7, which is against the scenario of the central limit theorem~\citep{Peng2007, Jahnke2011, Hirschmann2010} in which the scaling relation is a consequence of a stochastic cloud in the early universe with subsequent random mergers thereafter. Otherwise, the scatter of the scaling relations should increase towards higher redshift. In fact, the scatter level in the simulation without adding random noise are consistent with the {\it intrinsic} scatter estimations reported in~\citet{Ding2020, 2021arXiv210902751L}, which is also not larger than the typical scatter of the local relations reported in the literature~\citep[][i.e., $\gtrsim0.35$~dex]{Kormendy13, Gul++09, Reines2015}.

The results also show that Illustris and Horizon-AGN simulation could predict well the scaling relation central offset (related to the local) at $z<0.6$, while SAM, TNG100, TNG300 and Horizon-AGN predict the {\it observed} evolution at $z>0.6$. \todo{As mentioned in the result section, we need provide some details on how the scaling relations in the simulations are calibrated. For example, why Illustris and TNG sample predict different center for the scaling relation. Horizon-AGN could predict well at both low and high z, maybe we can add some discussions.}
From $z\sim0.7$ to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations could well predict the evolution trend of the scaling relation --- the  {\it observed} offset of the $\Delta$\mbh\ (to the local relation at a given \smass) is larger at higher redshift, which are clearly shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.

The simulations studied in this work have adopted completely different numerical techniques. However, all of them can provide good agreement with the observed dispersion in the scaling relation. In fact, the tightness of the scaling relation is the result of the AGN feedback adopted in the recipe. Thus, the consistency of the scatter level between simulation and observations support the hypothesis that the causal link (i.e., AGN feedback) between BH and their hosts plays a dominate role in the scaling relation. 
\ding{The fact that in previous SAM version with a different AGN feedback recipe, the apparent scatter in the simulation is much larger up to 0.7 dex. Hi Nicola, could you add more details here and example the different of AGN feedback in SAM compared to previous version?}
So far, a control experiment is still not performed yet in which one numerical model provide the simulation and altering the AGN feedback prescription, while fixing all other conditions.
%\todo{We need a paragraph or section to highlight that SAM simulation has been updated. The comparison of the HST in old version shows that the scatter can be up to 0.7 dex.}

\todo{Some discussion of the comparison with Habouzit et al to be added. Also, do we want to take ENGLE simulaiton?}

Extending this study to even higher redshift would be very beneficial, probing closer to the epoch of formation of massive galaxies and SMBHs. The understanding of how and when the tight scaling relation emerged are crucial to test the theory. On the observational side, the James Webb Space Telescope will provide high-quality imaging data of AGNs at redshift up to $z\sim7$ (i.e., JWST cycle 1 program GO-1967 and GO-1727). These upcoming measurements will provide severe constraints to the theories such as the initial conditions in the simulations.

%Look at the further.

\begin{acknowledgments}
We thank all the people that give us comments and useful suggestions. \todo{More to be added.}

\end{acknowledgments}

\vspace{5mm}
\facilities{HST, HSC}

%% Similar to \facility{}, there is the optional \software command to allow 
%% authors a place to specify which programs were used during the creation of 
%% the manuscript. Authors should list each code and include either a
%% citation or url to the code inside ()s when available.

%\software{astropy \citep{2013A&A...558A..33A,2018AJ....156..123A},  }

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc. The
%% Figure and Table counter will not reset.

%\appendix
%\section{Comparison of the observed mass function}\label{app:function}
%Our comparison also provides the opportunity to compare the {\it apparent} mass distribution of the BH mass and the stellar mass. The histogram distribution of the {\it observed} \mbh\ and \smass\ are shown in Figure~\ref{fig:MB_fun} and Figure~\ref{fig:Mstar_fun}, respectively. All the simulations have good agreements to the observed mass function, in terms of the standard derivation. However, focus on the central point of the distribution, the TNG100 and TNG300 give the best prediction, indicating that their parent sample are most similar to the HSC sample. \todo{Xuheng will talk with Jingjing and add more discussion to this part.}

%\begin{figure*}
%\centering
%\begin{tabular}{c c}
%%\vspace*{-0.2cm} 
%{\includegraphics[height=0.35\textwidth]{MBH_dis_z03.pdf}}&
%%\hspace*{-0.4cm} 
%{\includegraphics[height=0.35\textwidth]{MBH_dis_z05.pdf}}\\
%%\hspace*{-0.4cm} 
%{\includegraphics[height=0.35\textwidth]{MBH_dis_z07.pdf}}&
%%\hspace*{-0.4cm} 
%{\includegraphics[height=0.35\textwidth]{MBH_dis_z15.pdf}}\\
%\end{tabular}
%\caption{\label{fig:MB_fun} 
%Illustration of the histogram of the observed \mbh\ function. For MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$. Note that for sample at $z\sim1.5$, the selection cut on \mbh\ is used in the simulation, thus the distribution is almost flat. \todo{update hist format as Figure 4}
%}
%\end{figure*} 
%
%\begin{figure*}
%\centering
%\begin{tabular}{c c}
%%\vspace*{-0.2cm} 
%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z03.pdf}}&
%%\hspace*{-0.4cm} 
%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z05.pdf}}\\
%%\hspace*{-0.4cm} 
%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z07.pdf}}&
%%\hspace*{-0.4cm} 
%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z15.pdf}}\\
%\end{tabular}
%\caption{\label{fig:Mstar_fun} 
%Illustration of the histogram of the observed MBH function. For MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$.
%}
%\end{figure*}

\bibliography{reference}{}
\bibliographystyle{aasjournal}

%% This command is needed to show the entire author+affiliation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

\end{document}

% End of file `sample631.tex'.

### 2021-11-24 projects/2020_HSC_to_numerical_simulation/manuscript_before_John_edit/manuscript.tex
Galight example, HSC online fitting, simulation paper updates

--- 2021-11-24 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
@@
 \newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
-\newcommand{\blue}[1]{\textcolor{blue}{#1}}
 
@@
 \begin{document}
-
-\title{The Black Hole and Galaxy coevolution at $0.2<z<1.7$ using extensive comparisons between observation and simulation}
+\title{Testing the Fidelity of Simulations of Black Hole -- Galaxy Coevolution}
 
@@
 \affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
-\affiliation{CAS Key Laboratory for Research in Galaxies and Cosmology, Department of Astronomy, University of Science and Technology of China, Hefei 230026, China}
-\affiliation{School of Astronomy and Space Science, University of Science and Technology of China, Hefei 230026, China}
 
@@
 \begin{abstract}
-We carry out a direct comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies (\mbh -- \smass) at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN,  TNG and semianalytic model).
-The observational measurements consistent of 612 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter.
-To make the fair comparisons, we first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as that based on observations.
-Our analysis demonstrates that all simulations predict a comparable level of dispersion of the scaling relations up to $z\sim1.7$, even after consideration of observational uncertainties which are non-negligible.
-%We also find that the selection criteria for the $z<1$ do not produce strong effects on the simulated relation
-%Thus, the original relations (i.e., before adding noise) predicted by the simulation are supposed to have consistent intrinsic scatter compared with the observational data. 
-%Considering that the tight relation of the scaling relation is highly rely on the AGN feedback, our results support the hypothesis of the AGN feedback being responsible for a causal link between the BH and its host galaxy, resulting in a tight correlation between their respective masses.
-Hence, our results support the hypothesis that AGN feedback plays a role in a causal link between the BH and its host galaxy, resulting in a non-evolving and tight correlation between their respective masses.
-\todo{Mentioning the central comparison.}
-
+We investigate the evolution of the scaling relations between the supermassive black hole (BH) and its host galaxy stellar mass (\smass-\mbh) by making comparisons between observations and simulations at $0.2<z<1.7$.
+The measurements of the observational data are consistent of 612 uniformly-selected SDSS quasars at $0.2 < z < 0.8$ that imaged by Hyper Suprime-Cam (HSC) and 32 X-ray-selected, broad-line AGNs imaged by the Hubble Space telescope (HST) at $1.2<z<1.7$.
+We make direct comparisons by first adding realistic observational error to the simulation data and then making selection to the sample follows real observation condition.
+Our results show that all the simulations predict consistent scatter of the scaling relations to both HSC and HST sample, across board redshift range.
+%We also find that the selection criteria for the $z<1$ do not produce strong effects on the simulated relation.
+The scatter of the scaling relation is dominated by the observational error.
+Thus, the original relations (i.e., before adding noise) predicted by the simulation are supposed to have consistent intrinsic scatter compared with the observational data.
+Considering that the tight relation of the scaling relation is highly relay on the AGN feedback, our results support the hypothesis of the AGN feedback being responsible for a causal link between the BH and its host galaxy, resulting in a tight correlation between their respective masses.
 %\todo{Add comments on the center positions. KS test. Estimation of the intrinsic scatter.}
@@
 \section{Introduction} \label{sec:intro}
-The close correlations between supermassive black holes and the properties of their host galaxies (e.g., stellar mass) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
-To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determin how and when the correlation emerges and evolves over cosmic time \citep[e.g.,][]{Peng2006a, Tre++07, Woo++08, Jahnke2009, Bennert11, Schramm2013, Park15, Mechtley2016, Ding2020, 2021arXiv210902751L}.
-While, an {\it apparent} evolution has been found in which the growth of BHs predates that of the host, equally as many studies claim a lack of evolution when considering the host total stellar mass.
-However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014}.
+The close correlations between the supermassive black holes and their host galaxies properties (stellar mass in particular) indicates a physical coupling during their coevolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
+To understand the nature of this connection, considerable efforts have been focused to measure the correlation using board-line active galactic nucleus (AGN) to measure them as a function of redshift, intending to see how and when the correlation emerge and evolve over cosmic time \citep[e.g.,][]{Peng2006a, Tre++07, Woo++08, Jahnke2009, Bennert11, Schramm2013, Park15, Mechtley2016, Ding2020, 2021arXiv210902751L}.
+While, an {\it apparent} evolution has been found in which the growth of BHs predates that of the host, equally as many studies claim a non-evolution when considering the host total stellar mass.
+To understand the significance {\it intrinsic} evolution, it is important to take into account the systematic uncertainty of the measurement and the selection effect~\citep{Tre++07, Lauer2007, Schulze2014}.
 
-Various theoretical models have been proposed to explain the origin of the scaling relations.
-For example, AGN feedback is considered as one of the possible viable mechanisms.
-During this process, a fraction of the AGN energy is injected into its surrounding gas, which can then regulate the mass growth of the BH and its host.
-In this scenario, star formation is inhibited by the heating and unbinding of a significant amount of gas.
-Alternatively, the mass relations can be explained through an indirect connection in which AGN accretion and star formation are fed through a common gas supply~\citep{Cen2015, Menci2016}.
-Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
-However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ as observed today.
+In theory, various models have been proposed to explain the origin of the scaling relation.
+For instance, the AGN feedback is considered as one of the possible physical link.
+During this process, the fraction of the AGN energy is injected into its surrounding gas, which regulates the mass growth of the BH and its host.
+In this scene, the star formation is inhibited by the heating and unbinding of a significant fraction of the gas by the AGN activity.
+Alternatively, the scaling relation can be explained through a more indirect connection in which AGN accretion and host star formation are fed through a common gas supply~\citep{Cen2015, Menci2016}.
+Without any physical mechanisms, the statistical convergence from galaxy assembly alone (i.e., dry mergers) could regulate the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
+From this central limit theorem, higher dispersion would appear in the scaling relations at high-$z$ as observed today.
 
-Numerical simulations provide an opportunity to further understand the origin of the connection between BHs and their host galaxies.
-For example, a comparison of scaling relations has been made between predictions by the state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and observational measurements at  $0.3<z<1$ based on HST imaging \citep[e.g., ][]{DeG++15}, which show a positive evolution (i.e., the mass growth of the BH growth predates that of its host).
-Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution, including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments suite of SPH simulations~\citep{Schaye2015}, Illustris moving-mesh simulation~\citep{Sijacki2015, Vogelsberger2014, Li2019} and the SIMBA simulation~\citep{Thomas2019}.
-In recent work, the BH populations from the six large-scale cosmological simulations have been adopted to compare the \mbh-\smass\ with observation of the local universe~\citep{Habouzit2021}.
-However, these comparison works are limited by the observation data in terms of the sample size ($<$100) and redshift range ($z<1$).
+Numerical simulation provides good opportunity to understand the origin of the connection.
+For example, the comparison of the scaling relations has been made between the predictions by the state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and the HST observational measurements at  $0.3<z<1$, which show a positive evolution that BH growth predates than its host~\citep{DeG++15}.
+The efforts have been taking to use large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution, including the Magneticum Pathfinder smooth particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments suite of SPH simulations~\citep{Schaye2015}, Illustris moving mesh simulation~\citep{Sijacki2015, Vogelsberger2014, Li2019} and SIMBA simulation~\citep{Thomas2019}.
+In recent work, the BH populations from the six large scale cosmological simulations have been adopted to compare the \mbh-\smass\ with observation of the local universe~\citep{Habouzit2021}.
+However, these comparison works are limited by the observation data in terms of the sample size ($<$100) and the redshift range ($z<1$).
 
-For such comparisons using simulations, it is crucial to consider the systematic uncertainties and selection biases.
-A direct means to account for these is to apply the same effects and selection to the simulation products and make a forward comparison in the observational plane.
-In~\citet{Ding2020b}, a direct comparison has been performed using 32 X-ray-selected AGN at $1.2<z<1.7$ and a direct comparison with two state-of-the-art simulation efforts, including {\tt MassiveBlackII} (MBII) and a Semianalytic Model (SAM).
+In the meanwhile, it is crucial to consider the systematic uncertainties and selection biases in the comparison.
+A direct way to take them in to account is to apply the same effects to the simulation products and make a forward comparison in the observational plane.
+In~\citet{Ding2020b}, this direct comparison has been performed using 32 X-ray-selected AGN at $1.2<z<1.7$ and direct compare with two state-of-the-art simulation efforts, including {\tt MassiveBlackII} (MBII) and Semianalytic Model (SAM).
 The dispersion in the mass ratio between black hole mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) confirming the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.
 
-In this study, we extend our previous work, comparing the observational measurements to that from simulations, by adding recent measurements of hundreds of SDSS quasar at $0.2<z<0.8$ based on wide and deep HSC imaging from the Strategic Subaru Program.
-Furthermore, we extend the simulated quasar populations by including MBII, SAM, Illustris, TNG100, TNG300 and Horizon-AGN.
+In this study, we extend our previous comparison work by adding the latest measurements of hundreds SDSS quasar $0.2<z<0.8$ using the latest HSC observation.
+We adopt more simulated quasar populations including MBII, SAM, Illustris, TNG100, TNG300 and Horizon.
 This paper is structured as follows.
-In Sections~\ref{sec:observations} and~\ref{sec:simulations}, we describe our observation and simulation sample.
-The direct comparison is performed and the result is presented in Section~\ref{sec:result}.
-The concluding remarks are presented in Section~\ref{sec:con}.
+In section~\ref{sec:sample}, we describe our observation and simulation sample.
+The direct comparison is performed and the result is presented in section~\ref{sec:result}.
+The concluding remarks are presented in section~\ref{sec:con}.
 
-%\section{Comparison Sample: Observations and Simulations} \label{sec:sample}
+\section{Comparison Sample: Observations and Simulations} \label{sec:sample}
 %The correlations of \mbh-\smass\ between the observed data and the numerical simulations are compared in this work. 
-%We introduce the comparison samples in this section, including the observational data and the numerical simulations.
+We introduce the comparison samples in this section, including the observational data and the numerical simulations.
 
-\section{Observational data set}
-\label{sec:observations}
-The observed sample consists of 900 uniformly-selected SDSS quasars at $0.2<z<0.8$, imaged by Subaru/HSC \citep{Li2021a}, and 32 quasars at $1.2<z<1.7$ as imaged by~\hst and described in \citep[][hereafter D20]{Ding2020}.
-The latter are selected from three deep-survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008}.
-Further details of these two samples and their measurements are given below.
+\subsection{Observation Data}
+The observational data are consistent of 900 HSC-observed uniformly-selected SDSS quasars at $0.2<z<0.8$~\citep{Li2021a} and 32 \hst-observed quasars analyzed in \citep[][hereafter D20]{Ding2020} which are selected from three deep-survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008}.
+The details of the observational data and their measurements are introduced in following subsections.
 
-\subsection{HSC}\label{sec:hsc}
-A sample of $\sim$5000 type-1 SDSS quasars from the DR14 catalog~\citep{Paris2018} at $0.2<z<1$ has been imaged by the high-resolution Subaru Strategic Program (SSP) wide area survey~\citep{Aihara2019} using Hyper Suprime-Cam~\citep{Miyazaki2018}.
-With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been performed \citep[][hereafter L21a]{Li2021a} to obtain the flux and color of each quasar's host galaxy.
-The stare-of-the-art image modeling software {\tt lenstronomy} \citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task.
-This approach is first developed by~\citet{Ding2020} and used to decompose the near-infrared emission of the HST sample (see next section).
-Having measured the host light in each band, the stellar mass of host galaxy is derived using spectral energy distribution (SED) fitting with CIGALE~\citep{Boquien2019}.
-Simulation tests are also performed to verify the fidelity of the \smass\ measurements.
-The statistical measurement error on \smass\ is at the $\sim$0.2~dex level.
-The values of \mbh\ are determined by~\citet{Rakshit2020} which are estimated based on the \hbeta-based measurements using the virial method~\citep{Peterson2004, Vestergaard2006}.
+\subsubsection{HSC}\label{sec:hsc}
+A sample of $\sim$5000 type-1 SDSS DR14 quasar catalog~\citep{Paris2018} at $0.2<z<1$ has been imaged through high-resolution Subaru Strategic Program (SSP) wide survey~\citep{Aihara2019} by Hyper Suprime-Cam~\citep{Miyazaki2018}.
+With accurate PSF model and {\it grizy} bands, the two-dimensional quasar-host decomposition has been performed in~\citet[][hereafter L21a]{Li2021a} to obtain the quasar host galaxies flux and the color.
+The stare-of-the-art image modeling software {\tt lenstronomy}\citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task.
+This approach is first developed by~\citet{Ding2020}, which is used to decompose the HST sample (see next section).
+Having inferred the host light, the stellar mass of host galaxy is derived using spectral energy distribution (SED) fitting by CIGALE~\citep{Boquien2019}.
+A simulation tests are also performed to verify fidelity of the \smass\ measurements.
+The measurement error of \smass\ is dominated by the Spectral Energy Distribution (SED) fitting which is at a 0.2~dex level.
+The \mbh\ are taken from~\citet{Rakshit2020} which are estimated by the \hbeta-based measurements using virial method~\citep{Peterson2004, Vestergaard2006}.
 The typical error of \mbh\ are estimated to be 0.4 dex.
@@
 
-To avoid any potential biases related to the selection of the quasars, \citet[][hereafter, L21b]{2021arXiv210902751L} isolated 877 sources which are uniformly selected based on their PSF-magnitudes, color cuts using single-epoch SDSS photometry and the value of the measured \smass.
+To avoid any potential biases related to the selection of the quasars, \citet[][hereafter, L21b]{2021arXiv210902751L} adopted the 877 sources which are uniformly selected based on PSF-magnitude, color cuts using single-epoch SDSS photometries and the value of the measured \smass.
 Specifically, we use the {\it ugri} color-selected sample (228 sources) from SDSS I/II~\citep{Richards2002}, and the CORE sample from SDSS BOSS (408 sources) and eBOSS (241 sources) surveys~\citep{Ross2013, Myers2015} (hereafter the uniform sample).
-These samples are initially selected based on PSF-magnitude cuts of $15 < i < 19.1$ (for {\it ugri}), and $i > 17.8$ and $g, r < 22.0$ (for CORE).
-Finally, a limit on \smass\ is set to assure the detection of the host, especially since the rate and accuracy of detection is higher when \smass\ is increasing.
-These selections will be adopted in an equivalent manner to the simulated samples to mitigate selection effects thus allowing the fair comparison.
+These samples are initially selected based on PSF-magnitude cuts of $15 < i < 19.1$ (for {\it ugri}) and $i > 17.8 \& g/r < 22.0$ (for CORE).
+Finally, considering that the accuracy of the measured \smass\ is higher when \smass\ is increasing, a cut on \smass\ is set to assure the measurement accuracy.
+These selections will be adopted to the simulation sample to erase the selection effect and allow the fair comparison.
 
-\subsection{HST}
+\subsubsection{HST}
+A sample of 32 HST-observed AGN systems across the redshift range $1.2<z<1.7$ are selected from three deep-survey fields (COSMOS, (E)-CDFS-S, and SXDS).
+HSC/WFC3 is used to obtain the high-resolution imaging data (HST program GO-15115, PI: John Silverman) with six dither pattern and a total exposure time $\sim$2348~s.
+The filters F125W ($1.2<z<1.44$) and F140W ($1.44<z<1.7$) were employed, according to the redshift of each target.
+The AGN images are analyzed and decomposed to infer the host galaxies fluxes using the approached developed by D20 based on {\tt lenstronomy}.
+The HST ACS/F814W imaging data for 21/32 of the AGNs is also used to infer the host color.
+The results show that the 1 and 0.625~Gyr stellar templates could well match the sample color at $z<1.44$ and $z>1.44$, respectively (see Figure 5 in D20), which are adopted to estimate the stellar masses of the host galaxies.
+We refer the interested reader to D20 for more detailed description.
+The \mbh\ is determined using published near-infrared spectroscopic observations of the broad \halpha\ emission line with recipe provided by~\citep{Vestergaard2006}, the recipe is consistent with the one adopted by HSC sample \mbh.
 
-A sample of 32 HST-observed AGN systems across the redshift range $1.2<z<1.7$ are selected from three deep-survey fields (COSMOS, (E)-CDFS-S, and SXDS).
-HSC/WFC3 IR camera is used to obtain the high-resolution imaging data (HST program GO-15115, PI: John Silverman) with six position dither pattern and a total exposure time $\sim$2348~s.
-The filters F125W ($1.2<z<1.44$) and F140W ($1.44<z<1.7$) were employed, according to the redshift of each target to bracket the 4000~\AA~break.
-The AGN images are analyzed and decomposed to infer the host galaxies fluxes using the approach developed by D20 based on {\tt lenstronomy}.
-The HST ACS/F814W imaging data for 21/32 of the AGNs is also used to infer the host color.
-The results show that stellar templates of 1 and 0.625~Gyr can match the sample color at $z<1.44$ and $z>1.44$, respectively (see Figure 5 in D20).
-These best-fit models are used to estimate the stellar masses of the host galaxies.
-\mbh\ is determined by \citet{Schulze2018} using near-infrared spectroscopic observations of the broad \halpha\ emission line with the recipe provided by~\citep{Vestergaard2006}, in a consistent manner to that adopted for HSC sample.
-We refer the reader to D20 for a more detailed description of the analysis.
+Based on the consistent approach, the measurements of the \mbh-\smass\ relations for the HST sample and the HSC sample are obtained.
+Thus, we expect the measurement error of these two samples to be at the same level (i.e., $\Delta$\mbh$=0.4~$dex, $\Delta$\smass$=0.2~$dex).
+Indeed, the HST and HSC sample demonstrate consistent evolution distribution in L20b Figure 6, though the sample selection is slightly different.
 
-With a consistent approach, the measurements of the \mbh-\smass\ relations for the HST and HSC samples are obtained.
-Thus, we expect the measurement errors of these two samples to be at a comparable level (i.e., $\Delta$\mbh$=0.4~$dex, $\Delta$\smass$=0.2~$dex).
-Indeed, the two samples are consistent with a lack of evolution in the mass ratio (see Figure 6 of L20b), even though the sample selection is slightly different.
-
-\section{Simulations}
-\label{sec:simulations}
+\subsection{Simulation}
 We introduce the simulation sample that adopted in this section. All the simulation are based on the larger-scale cosmological simulations, except the Semianalytic Model (SAM) simulation.
@@
 
-\subsection{{\tt MassiveBlackII} (MBII)}
+\subsubsection{{\tt MassiveBlackII} (MBII)}
 MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles.
@@
 
-\subsection{Semianalytic Model (SAM)}
+\subsubsection{Semianalytic Model (SAM)}
 We highlight here the main points of the simulation with respect to our study; for more detail, a full descriptions of the SAM simulation sample can be found in~\citet{Menci2016} which is based on semianalytic model introduced in~\citet{Menci2014}.
@@
 
-\subsection{Illustris}
+\subsubsection{Illustris}
 The Illustris Project is a serise of larger-scale hydrodynamical simulations of galaxy formation which was introduced in~\citet{2014MNRAS.444.1518V, 2014Natur.509..177V}.
@@
 
-\subsection{IllustrisTNG}
+\subsubsection{IllustrisTNG}
 {\it The Next Generation Illustris Simulations} (IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018} are an ambitious suite of hydrodynamical simulations of galaxy formation in large cosmological volumes.
@@
 
-\subsection{Horizon-AGN}
+\subsubsection{Horizon-AGN}
 The simulation of Horizon-AGN~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D} has a volume of (142 cMpc)$^3$ which was generated based on the adaptive mesh refinement code {\tt Ramses}~\citep{2002A&A...385..337T} with a $\Lambda$CDM model based on WMAP7~\citep{2011ApJS..192...18K} cosmological results.
@@
 
-We summarized some key elements in the simulation in Table~\ref{tab:sim_sum}.
+\section{Comparison and Results} \label{sec:result}
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+{\includegraphics[width=0.45\textwidth]{HSC_selection_MBII.png}} &
+{\includegraphics[width=0.45\textwidth]{HST_selection_MBII.png}}
+\end{tabular}
+\caption{\label{fig:selection} 
+{\it left}: The correlation between the \mbh\ and $L_{\rm bol}$ of the HSC sample is used to set the selection window for the simulated samples.
+This region roughly bracket the type-1 AGN sample.
+Taking MBII as example, the light green background cloud shows the simulated number density after added random uncertainty of the overall sample.
+{\it right}: Similar to the top plane -- equivalent selection window adopted for the HST-observed and MBII simulated samples.
+}
+\end{figure*}
 
-\begin{deluxetable*}{lcccccc}
-%\tablenum{1}
-\tablecaption{Summary of some key assumptions for the hydrodynamic simulations analyzed by this work.\label{tab:sim_sum}}
-\tablewidth{0pt}
-\tablehead{
-%\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
-%  \cline{2-4}  \cline{5} \\
-\colhead{Simulation} & \colhead{box sizes} & particles &  \colhead{resolution} & \colhead{feedback prescription} & \colhead{AGN fueling mechanism}  & what else?
-}
-\startdata
-%SAM & \\
-MBII & $100~\mathrm{cMpc/h}$ & $2\times1792^3$ &&& \\
-Illustris &&&&& \\
-TNG100 &&&&& \\
-TNG300 &&&&& \\
-Horizon-AGN &&&&& \\
-\enddata
-%\tablecomments{This table }
-\end{deluxetable*}
+To make direct comparison, we adopt the measurement error and the selection effect and apply to the simulation sample.
+To this end, we first inject random noise to the simulation catalog to mimic the scatter that caused by the measurement error.
+As mentioned in pervious section, the \smass\ and \mbh\ for HSC and HST samples are estimated by using the similar approach, and thus their uncertainty level is expected to be the same.
+We assume the following measurement uncertainties to add the random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = 0.17~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.
 
-\subsection{Application of observational selection effects}
-To make direct comparisons with observations, we add measurement errors and apply the equivalent selection to the simulated samples.
-We first inject random noise to the simulated catalog to mimic the scatter caused by the measurement error.
-As mentioned above, \smass\ and \mbh\ for HSC and HST samples are measured with a similar approach thus their uncertainty levels are expected to be equivalent.
-We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = 0.17~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.
-
-We then apply restrictions on the noise-injected simulation to mimic selection effects as present in the observational data.
-Since the HSC and HST samples have their own selection function, we apply different selection criteria to the simulation as follows.
+We then make selection to the noise-injected simulation data to consider the selection effect as in the realistic data.
+Since the HSC sample and the HST sample have different selection function, we adopt different selection criteria to the simulation as follows.
 \begin{itemize}
-
- \item{}HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should be consistent with the \mbh-$L_{\rm bol}$ relation of the HSC sample.
-We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it top}).
-(2) The $i$-band magnitude of the AGN are bright (see Section~\ref{sec:hsc}).
-The specific selection is made as follows: for systems at $z<0.5$ and $z>0.5$, the AGN $i$-band magnitude are required to be brighter than 20.5 mag and 22.0 mag, respectively.
+ \item{}To consider the same selection effect in the HSC sample, the following measures are taken.
+1) The observed sample is consist of type-1 AGN, and thus the simulated sample should follow consistent \mbh-$L_{\rm bol}$ relation to HSC sample to ensure the fact that all the selected AGN have board line feature.
+We take the MBII as an example to demonstrate this sample selection, shown in Figure~\ref{fig:selection}--{\it top}.
+2) The $i$-band magnitude of the AGN are bright (see Section~\ref{sec:hsc}).
+The specific selection is made as following; for systems at $z<0.5$ and $z>0.5$, the AGN $i$-band magnitude are required to be brighter than 20.5 mag and 22.0 mag, respectively.
 Since the simulations do not provide the AGN observed magnitude, we adopt the simulated rest-frame magnitude or L$_{\rm 5100}$ and assume the quasar continuum as a single power-law with an index of $\alpha_\nu=-0.44$~\citep{2001AJ....122..549V} to calculate the observed $i$-band magnitude.
- 3)~Following the HSC selection, we require the \smass\ value to be above a certain level (according to their redshift) to assure an accurate measurement.
+ 3)~Following the HSC selection, we require the \smass\ value to be above a certain level (according to their redshift) to assure the accurate of them measurement.
 Finally, the HSC sample is split into three redshift bins which are $0.2<z<0.4$, $0.4<z<0.6$, and $0.6<z<0.8$.
 
-\item{}HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is same as the observational selection, see Figure~\ref{fig:selection}--{\it left} taken MBII as example.
-Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., between [7.7, 8.6] $M_{\odot}$).
+\item{}For HST sample, the selection is relatively simpler.
+The simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is same as observation selection, see Figure~\ref{fig:selection}--{\it bottom} taken MBII as example.
+Note that the sample selection of the HST sample has a hard cut on the \mbh\ values (i.e., between [7.7, 8.6] $M_{\odot}$).
 The HST sample covers the higher redshift range $1.2<z<1.7$, which is considered as a single redshift bin to make the comparison with the simulations at $z=1.5$.
@@
 
-\section{Results} \label{sec:result}
-\begin{figure*}
-\centering
-\begin{tabular}{c c}
-{\includegraphics[width=0.5\textwidth]{HSC_selection_MBII.png}} &
-{\includegraphics[width=0.45\textwidth]{HST_selection_MBII.png}}
-\end{tabular}
-%\caption{\label{fig:selection}Demonstration of the impact of AGN selection using MBII.
-{\it left}: Correlation between \mbh\ and %$L_{\rm bol}$ of the simulated HSC sample is used to set the selection window for the simulated sample.
-This region roughly bracket %the type-1 AGN sample.
-The light green background cloud shows the simulated number density distribution in this parameter space %which includes a random level of uncertainty to mimic observational measurement errors.
-{\it right}: Similar to the top plane -- %equivalent selection window adopted for the HST-observed and MBII simulated samples.
-%}
-\caption{\label{fig:selection}Demonstration of the impact of AGN selection using MBII.
-{\it left}: Distribution of \mbh\ and $L_{\rm bol}$ for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles).
-A matched HSC sample is shown by the orange data points.
-The light green background cloud shows the simulated number density distribution in this parameter space which includes a random level of uncertainty to mimic observational measurement errors.
-{\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample.
-The y-axis is now given as the Eddington ratio.}
+Having selected the sample, the comparison is performed as follows.
+We use the local relation \mbh$=0.98$\smass$-2.56$ adopted by D20 (Chabrier based\footnote{Since different simulations adopt either the Chabrier or the Salpeter IMF, we will adopt the local relation and the \smass\ of the observation data based on the same IMF to ensure that the comparison with the observation data are self-consistent.}) as the fiducial to estimate the sample offset and scatter.
+In Figure~\ref{fig:comparsion}, we present the comparison of the scaling relation \mbh-\smass\ between the observation and simulations.
+Different simulations are presented in each row and the redshift evolution is shown from left to right.
+For both observation and simulation sample, the central offsets and scatters of the scaling relation are estimated by the mean and the standard deviation of the \mbh\ residuals for each system\footnote{The slope value of the local sample is close to 1, and thus if taking the \smass\ to calculate the residual  for each system, the value remains the same.} (i.e., the offset to the local relation along the y-axis in Figure~\ref{fig:comparsion}).
+A collection of these central offset and scatter values is presented in Table~\ref{tab:sum}.
+The simulation sample has been added with random error; we use Monte Carlo approach to infer their uncertainties of the the central offsets and scatters for the simulation sample.
+The comparison process including the noise injection, the sample selection and the offsets estimation are repeated by up to 1,000 times until the result is stable.
+To visually inspect the comparison results, we show the offsets to the local relation (in terms of the $\Delta{\rm log}$\mbh) as a function of redshift using sample both observation and simulations in Figure~\ref{fig:offsets_vz}.
+We also summarize the histogram of these offsets distributions based on each redshift bins, as shown in Figure~\ref{fig:offsets}.
 
-\end{figure*}
+The absolute value of stellar masses in both observation and theory have significant uncertainty (up to factor of two), which depends on the assumption of initial mass function, and possibly on the implementation of star formation in the models.
+In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by this uncertainty.
+Thus, in this work, we take the comparison and mainly focus on the scatter as a direct diagnostic criteria.
+The results show that, almost all the simulations predict consistent scatter value to the observation.
+For simulation sample at $z<1$, this scatter level is $\sim0.5$~dex, while for $z>1$, this scatter level is $\sim0.3$~dex.
+Note that the HST sample $z>1$ has narrow selection window based on the \mbh (see Figure~\ref{fig:selection}~bottom), leading to the result that the observed scatter is smaller than HSC sample at $z<1$.
+\ding{In the simulation, is there any observational data that be used to give extra constrain on the recipe? Xuheng and John are surprised to see that all of them have very good scatter matches!}
 
-In Figure~\ref{fig:comparsion}, we present the comparison of the scaling relation \mbh--\smass\ between the observations and the simulations.
-We use the local relation \mbh$=0.98$\smass$-2.56$ adopted by D20 (Chabrier based\footnote{Since different simulations adopt either the Chabrier or the Salpeter IMF, we will adopt the local relation and the \smass\ of the observation data based on the same IMF to ensure that the comparison with the observation data are self-consistent.}) as the fiducial to estimate relative offsets and dispersions.
-Different simulations are presented in each row and redshift intervals increase from left to right.
-For both the observational and simulated samples, the central offset and scatter of the scaling relation are estimated by the mean and the standard deviation of the \mbh\ residuals for each system\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the value remains the same.} (i.e., the offset to the local relation along the y-axis in Figure~\ref{fig:comparsion}).
-We summarize of these offset distributions based on each redshift bins, as shown in Figure~\ref{fig:offsets}.
-To visually inspect the comparison results, we show the offsets to the local relation (in terms of the $\Delta{\rm log}$\mbh) as a function of redshift (see Figure~\ref{fig:offsets_vz}, left). 
-The values for the central offset and scatter in each case are given in Table~\ref{tab:sum}.
+We also investigate the central offset to understand how the simulations predict the {\it observed} evolution of the scaling relation.
+According to the results in Table~\ref{tab:sum} and Figure~\ref{fig:offsets_vz}, at low redshift range $z<0.6$, the Illustris is the only simulation that can predict the {\it observed} \mbh\ offset at a level of $<0.1$ dex.
+At higher redshift $0.6<z<1.5$, the simulations SAM, TNG100, TNG300 and Horizon can predict the {\it observed} evolution well.
+These results are consistent with the Kolmogorov-Smirnov (KS) test performed using the offset distributions between the simulation and the observation.
+The inference of the p-values are collected in Table~\ref{tab:pvalue}, showing that only the Illustris presents good match of the scaling relation at $z<0.6$ (i.e., p-value $> 0.1$), while the TNG100, TNG300 and Horizon simulation predict well at $z>0.6$.
+
+We recognized that the observed scatters are dominated by the measurement uncertainties in the data.
+Understand how much of the scatters derive from random noise can help us to extrapolate the intrinsic scatter in the scaling relation.
+To this end, we measure the scatter of the simulation sample without injecting the random noise but adopting the same selecting window for both $z<1$ and $z>1$ sample to infer the central offset and scatter value.
+We find that the scatters by this measure are at a level of $\sim0.15-0.2$ dex for both $z<1$ and $z>1$ (see Table~\ref{tab:sum_no_noise}).
+These levels are consistent with the {\it intrinsic} scatter as estimated using observation data by~\citet{Ding2020, 2021arXiv210902751L}.
+More important, these scatters values are redshift-independent, suggesting that the tight scaling relation could not be explained by a pure stochastic process, i.e., random mergers.
+Still, these scatters are affected by the sample selection, and thus these levels can only be taken as an approximation of the intrinsic scatter.
+%their physical meaning should not be considered as the intrinsic scatter of the overall sample.
+
+%Taking \mbh\ and \smass\ as independent measurements, we also summarize their distributions and make comparison between the observation and simulation in the Appendix~\ref{app:function}.
 
@@
 \begin{tabular}{c c c c}
-\vspace*{-0.1cm} 
+%\vspace*{-0.4cm} 
 {\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_SAM_zs_03.png}}&
@@
 {\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_SAM_zs_15.png}}\\
-\vspace*{-0.1cm} 
 {\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_MBII_zs_03.png}}&
@@
 {\includegraphics[trim = 30mm 29mm 80mm 25mm, clip, height=0.25\textwidth]{MM_MBII_zs_15.png}}\\
-\vspace*{-0.1cm} 
 {\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Illustris_zs_03.png}}&
@@
 \hspace*{-0.5cm} 
-{\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Illustris_zs_15.png}}\\
-\vspace*{-0.1cm} 
+{\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Illustris_zs_15.png}}
+\end{tabular}
+\caption{\label{fig:comparsion} 
+The comparison of observed black hole mass vs.
+stellar mass relation from observation data and simulation products (by each row).
+The panels from left to right are based on different redshift bin.
+The black line in the panel indicates the local relation adopted by~\citet{Ding2020}.
+The background cloud shows the simulated number density with random noise that before selection.
+\todo{Xuheng will zoom in the figures and enlarger the text to show the them more clear.}
+}
+\end{figure*} 
+\renewcommand\thefigure{\arabic{figure}}
+\setcounter{figure}{1}  
+\begin{figure*}
+\centering
+\begin{tabular}{c c c c}
+%\vspace*{-0.4cm} 
 {\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_03.png}}&
@@
 {\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_15.png}}\\
-\vspace*{-0.1cm} 
-{\includegraphics[trim = 0mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_03.png}}&
+{\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG300_zs_03.png}}&
 \hspace*{-0.5cm} 
-{\includegraphics[trim = 44mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_05.png}}&
+{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG300_zs_05.png}}&
 \hspace*{-0.5cm} 
-{\includegraphics[trim = 44mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_07.png}}&
+{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG300_zs_07.png}}&
 \hspace*{-0.5cm} 
-{\includegraphics[trim = 30mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_15.png}}\\
+{\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG300_zs_15.png}}\\
+{\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Horizon_zs_03.png}}&
+\hspace*{-0.5cm} 
+{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Horizon_zs_05.png}}&
+\hspace*{-0.5cm} 
+{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Horizon_zs_07.png}}&
+\hspace*{-0.5cm} 
+{\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Horizon_zs_15.png}}\\
 \end{tabular}
-\caption{\label{fig:comparsion} 
-The comparison of observed black hole mass vs.
-stellar mass relation from observation data and simulation products (by each row).
-The panels from left to right are based on different redshift bin.
-The black line in the panel indicates the local relation adopted by~\citet{Ding2020}.
-The background cloud shows the intrinsic simulation number density before injecting random noise that selection effect.
-\todo{Xuheng will zoom in the figures and enlarger the text to show the them more clear.}
-}
-\end{figure*}
-
-The absolute value of stellar masses in both observation and theory have significant uncertainty (up to factor of two), which depends on the assumption of initial mass function, and possibly on the implementation of star formation in the models.
-In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematics.
-Thus, in this work, we first consider the scatter as a diagnostic criteria to see whether some simulations match the data better than others.
-Interestingly, the results show that, almost all the simulations \blue{can produce the scatter values consistent with the observations across all the redshift range} --- for simulation sample at $z<1$, this scatter level is $\sim0.5$~dex, while for $z>1$, this scatter level is $\sim0.3$~dex.
-Note that the HST sample $z>1$ has narrow selection window based on the \mbh\ (see Figure~\ref{fig:selection}~bottom), leading to the result that the observed scatter is smaller than HSC sample at $z<1$.
-\ding{In the simulation, is there any observational data that be used to give extra constrain on the recipe/assumption?
-Xuheng and John are surprised to see that all of them have very good scatter matches!}
-
-We recognize that the observed scatter is dominated by the measurement uncertainties in the data.
-An understanding how much of the scatter derives from random noise can help us to determine the intrinsic scatter in the scaling relation.
-To this end, we measure the scatter of the simulation sample without injecting the random noise but adopting the same selecting window for both $z<1$ and $z>1$ sample to infer the central offset and scatter.
-We find that the intrinsic scatter is at a level of $\sim0.15-0.2$ dex for both $z<1$ and $z>1$ (see Table~\ref{tab:sum_no_noise}).
-These levels are consistent with the {\it intrinsic} scatter as estimated using observation data by~\citet{Ding2020, 2021arXiv210902751L}.
-More important, these values of the scatter are redshift-independent, suggesting that the tight scaling relation could not be explained by a pure stochastic process, i.e., random mergers.
-Still, the scatter is affected by sample selection, and thus these levels can only be taken as an approximation of the intrinsic scatter.
-We demonstrate these offset that without injecting noise as function of redshift in Figure~\ref{fig:offsets_vz}, right.
-%their physical meaning should not be considered as the intrinsic scatter of the overall sample.
-
-To further investigate how the offset values are correlated with stellar mass, we take the MBII sample as example and demonstrate them in Figure~\ref{fig:deltaMM}.
-We also use intrinsic simulation value and plot to address how random noise and selection effect changes the correlation.
-The same Figure based on the other simulations are presented in the Appendix.
-\todo{show the other simulation's result.}
-%Taking \mbh\ and \smass\ as independent measurements, we also summarize their distributions and make comparison between the observation and simulation in the Appendix~\ref{app:function}.
-
-We also investigate the central offset to understand whether the simulations deviate or not from the {\it observed} evolution of the scaling relation.
-According to the results in Table~\ref{tab:sum} and Figure~\ref{fig:offsets_vz}, at low redshift range $z<0.6$, Illustris and Horizon-AGN can predict consistent {\it apparent} \mbh\ offset to the observation data (at a level of $\lesssim0.1$ dex) over all redshifts considered.
-At higher redshift $0.6<z<1.5$, the simulations SAM, TNG100, TNG300 and Horizon-AGN follow the {\it observed} evolution.
-These results are consistent with the Kolmogorov-Smirnov (KS) test performed using the offset distributions between the simulation and the observation.
-The inference of the p-values are collected in Table~\ref{tab:pvalue}, showing that only the Illustris presents good match of the scaling relation at $z<0.6$ (i.e., p-value $> 0.1$), while the TNG100, TNG300 and Horizon simulation predict well at $z>0.6$.
-
-%\renewcommand\thefigure{\arabic{figure}}
-%\setcounter{figure}{1}  
-%{\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_03.png}}&
-%\hspace*{-0.5cm} 
-%{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_05.png}}&
-%\hspace*{-0.5cm} 
-%{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_07.png}}&
-%\hspace*{-0.5cm} 
-%{\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_15.png}}\\
-%{\includegraphics[trim = 0mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_03.png}}&
-%\hspace*{-0.5cm} 
-%{\includegraphics[trim = 44mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_05.png}}&
-%\hspace*{-0.5cm} 
-%{\includegraphics[trim = 44mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_07.png}}&
-%\hspace*{-0.5cm} 
-%{\includegraphics[trim = 30mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_15.png}}\\
-
-\begin{figure*}
-\centering
-\begin{tabular}{c c c c}
-\hspace*{-0.4cm} 
-{\includegraphics[height=0.4\textwidth]{offset_dis_z03.pdf}}&
-\hspace*{-0.4cm} 
-{\includegraphics[height=0.4\textwidth]{offset_dis_z05.pdf}}&
-\hspace*{-0.4cm} 
-{\includegraphics[height=0.4\textwidth]{offset_dis_z07.pdf}}&
-\hspace*{-0.4cm} 
-{\includegraphics[height=0.4\textwidth]{offset_dis_z15.pdf}}\\
-\end{tabular}
-\caption{\label{fig:offsets} 
-Histograms of the offset distributions for all simulation samples and observations.
-The mean value and the standard derivation of the histogram are summarized in Table~\ref{tab:sum}.
-The vertical lines show the corresponding mean value for each distribution.
-The mean values for observed sample (i.e., blue lines) are also show in each simulation plots.
-For the MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$.
+\caption{
+continued.
 }
@@
 Observation & (0.07, 0.58) & (0.17, 0.52)  & (0.18, 0.54)  & (0.43, 0.31) \\
-SAM & (0.73, 0.49) & (0.65, 0.46)  & (0.51, 0.45)  & (0.51, 0.36) & Salpeter \\
-MBII & (-0.15, 0.48) & \multicolumn{2}{c}{(-0.16, 0.48) [$z=0.6$]}  & (0.14, 0.31) & Salpeter\\
-Illustris & (0.01, 0.52) & (0.08, 0.53)  & (0.06, 0.54)  & (0.07, 0.32) &  Chabrier \\
-TNG100 & (0.27, 0.48) & (0.24, 0.46)  & (0.24, 0.45)  & (0.38, 0.33) & Chabrier \\
-TNG300 & (0.26, 0.48) & (0.20, 0.48)  & (0.17, 0.48)  & (0.41, 0.34) & Chabrier \\
-Horizon-AGN & (0.20, 0.47) & (0.21, 0.48)  & (0.28, 0.47)  & (0.47, 0.35) & Salpeter\\
+SAM & (0.73$\pm$0.01, 0.49$\pm$0.01) & (0.65$\pm$0.01, 0.46$\pm$0.01)  & (0.51$\pm$0.02, 0.45$\pm$0.02)  & (0.51$\pm$0.01, 0.36$\pm$0.01) & Salpeter \\
+MBII & (-0.15$\pm$0.02, 0.48$\pm$0.01) & \multicolumn{2}{c}{(-0.16$\pm$0.02, 0.48$\pm$0.01) [$z=0.6$]}  & (0.14$\pm$0.02, 0.31$\pm$0.01) & Salpeter\\
+Illustris & (0.01$\pm$0.03, 0.52$\pm$0.02) & (0.08$\pm$0.04, 0.53$\pm$0.03)  & (0.06$\pm$0.03, 0.54$\pm$0.02)  & (0.07$\pm$0.03, 0.32$\pm$0.06) &  Chabrier \\
+TNG100 & (0.27$\pm$0.02, 0.48$\pm$0.02) & (0.24$\pm$0.05, 0.46$\pm$0.03)  & (0.24$\pm$0.01, 0.45$\pm$0.01)  & (0.38$\pm$0.02, 0.33$\pm$0.01) & Chabrier \\
+TNG300 & (0.26$\pm$0.01, 0.48$\pm$0.01) & (0.20$\pm$0.01, 0.48$\pm$0.01)  & (0.17$\pm$0.01, 0.48$\pm$0.01)  & (0.41$\pm$0.01, 0.34$\pm$0.01) & Chabrier \\
+Horizon & (0.26$\pm$0.11, 0.45$\pm$0.08) & (0.25$\pm$0.04, 0.46$\pm$0.03)  & (0.26$\pm$0.02, 0.47$\pm$0.01)  & (0.47$\pm$0.02, 0.35$\pm$0.02) & Salpeter\\
 \enddata
@@
 For the MBII sample, the simulation does not produce the sample at $z=0.5$ or $z=0.7$, but rather at $z=0.6$.
-\blue{We use Monte Carlo approach to infer the uncertainties of the central offset and scatter for each simulation sample, finding that the uncertainties are within $\pm 0.03$.}
-%This comparison includes the injection of noise and sample selection. and 
-%The estimation of offsets are repeated up to 1000 times until the result is stable. 
 }
 \end{deluxetable*}
+
+\begin{figure}
+\centering
+\vspace*{-0.2cm} 
+{\includegraphics[height=0.45\textwidth]{offset_summary_vz.pdf}}
+\caption{\label{fig:offsets_vz} 
+The apparent evolution of $\Delta{\rm log}$\mbh\ as a function of redshift using both observation and simulation data.
+The black line shows the evolution by fitting the offset as a function of redshift.
+The predictions from the numerical simulations are presented by different color regions, using the values inferred in Table~\ref{tab:sum}.}
+\end{figure}
 
@@
 \begin{tabular}{c c}
-{\includegraphics[height=0.4\textwidth]{offset_summary_vz.pdf}}&
-{\includegraphics[height=0.4\textwidth]{offset_int_summary_vz.pdf}}\\
+%\vspace*{-0.2cm} 
+{\includegraphics[height=0.35\textwidth]{offset_dis_z03.pdf}}&
+%\hspace*{-0.4cm} 
+{\includegraphics[height=0.35\textwidth]{offset_dis_z05.pdf}}\\
+%\hspace*{-0.4cm} 
+{\includegraphics[height=0.35\textwidth]{offset_dis_z07.pdf}}&
+%\hspace*{-0.4cm} 
+{\includegraphics[height=0.35\textwidth]{offset_dis_z15.pdf}}\\
 \end{tabular}
-\caption{\label{fig:offsets_vz} 
-{\it left}: The apparent evolution of $\Delta{\rm log}$\mbh\ as a function of redshift using both observation and simulation data.
-The black line shows the evolution by fitting the offset as a function of redshift.
-The predictions from the numerical simulations are presented by different color regions, using the values in Table~\ref{tab:sum}.}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\begin{tabular}{c c c}
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 0mm 0mm 0mm 0mm, clip,
-height=0.3\textwidth]{DeltaMM_MBII_zs_03.png}}&
-\hspace*{-0.3cm} 
-{\includegraphics[trim = 25mm 0mm 0mm 0mm, clip,
-height=0.3\textwidth]{DeltaMM_MBII_zs_06.png}}&
-\hspace*{-0.3cm} 
-{\includegraphics[trim = 25mm 0mm 0mm 0mm, clip,
-height=0.3\textwidth]{DeltaMM_MBII_zs_15.png}}\\
-\end{tabular}
-\caption{\label{fig:deltaMM} 
-The comparison of the offset of the \mbh\ (to the local relation) as a function of stellar mass from observation data and the MBII simulation at three different redshift bins, with same format as Figure~\ref{fig:comparsion}.
-The histogram on the right indicates the offset distribution with lines indicates the mean value of the offset for observation and simulation.
-The green color distributions indicate the intrinsic simulation values that without random noise and selection effect.
+\caption{\label{fig:offsets} 
+Illustration of the histogram of the offset distribution for all the sample. The mean value and the standard derivation of the histogram are summarized in Table~\ref{tab:sum}.
+For MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$.
 }
 \end{figure*}
-
-\begin{deluxetable*}{lcccc}
-%\tablenum{1}
-\tablecaption{Summary of the {\it intrinsic} central offsets and scatters\label{tab:sum_no_noise}}
-\tablewidth{0pt}
-\tablehead{
-\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
-\cline{2-4} 
-%  \cline{2-4}  \cline{5} \\
-\colhead{} &  \colhead{$0.2<z<0.4$} & \colhead{$0.4<z<0.6$} & \colhead{$0.6<z<0.8$} & \colhead{$1.2<z<1.7$}
-}
-\startdata
-SAM & (0.72, 0.20) & (0.64, 0.18) & (0.56, 0.16)  & (0.08, 0.18) \\
-MBII & (-0.15, 0.21) & \multicolumn{2}{c}{(-0.15, 0.22) [$z=0.6$]}  & (0.08, 0.19)\\
-Illustris & (0.03, 0.32) & (0.10, 0.36) & (0.08, 0.36)  & (0.04, 0.19) \\
-TNG100 &  (0.27, 0.20) & (0.27, 0.15) & (0.26, 0.16)  & (0.36, 0.15) \\
-TNG300 & (0.25, 0.21) & (0.19, 0.23) & (0.20, 0.22)  & (0.32, 0.16) \\
-Horizon-AGN & (0.24, 0.21) & (0.23, 0.22) & (0.29, 0.19)  & (0.37, 0.13) \\
-%Previous are ones not adding noise but same selection, belows are not add noise and not select
-%SAM & (0.75, 0.26) & (0.74, 0.26) & (0.94, 0.26)  & (0.59, 0.24) \\
-%MBII & (-0.24, 0.22) & \multicolumn{2}{c}{(-0.26, 0.22) [$z=0.6$]}  & (-0.29, 0.22)\\
-%Illustris & (-0.78, 0.40) & (-0.73, 0.40) & (-0.69, 0.40)  & (-0.55, 0.36) \\
-%TNG100 &  (0.33, 0.31) & (0.31, 0.32) & (0.29, 0.33)  & (0.22, 0.37) \\
-%TNG300 & (0.42, 0.58) & (0.40, 0.57) & (0.39, 0.56)  & (0.35, 0.54) \\
-%Horizon & (0.12, 0.30) & (0.13, 0.30) & (0.14, 0.28)  & (-0.00, 0.48) \\
-\enddata
-\tablecomments{Same as Table~\ref{tab:sum} but without inject noise to the simulation data. Note that same selection window is still adopted to infer the values.}
-\end{deluxetable*}
 
@@
 SAM &  $<$1e-10 & $<$1e-10  & $<$1e-10  & 7.456907e-03  \\
-MBII & 2.663415e-06 & \multicolumn{2}{c}{$<$1e-10 [$z=0.6$]}  & 2.218653e-06  \\
-Illustris & 4.061962e-02 & 1.029493e-01  & 5.525678e-03  & 2.330195e-07  \\
-TNG100 & 6.677469e-06 & 7.304761e-03  & 1.331638e-01  & 4.708287e-01  \\
-TNG300 & 1.100287e-07 & 5.446812e-01  & 2.942672e-02  & 2.118038e-01  \\
-Horizon & 1.306432e-01 & 3.175037e-01  & 5.094878e-02  & 1.953735e-01  \\
+MBII & 2.006930e-08 & \multicolumn{2}{c}{$<$1e-10 [$z=0.6$]}  & 1.420860e-04  \\
+Illustris & 3.436676e-01 & 1.254032e-01  & 6.389386e-02  & 2.055473e-04  \\
+TNG100 & 3.541028e-09 & 1.821151e-02  & 4.076073e-01  & 2.307911e-01  \\
+TNG300 & 2.180858e-07 & 2.618639e-01  & 1.186972e-02  & 2.114181e-01  \\
+Horizon & 3.928276e-04 & 2.891120e-04  & 1.289359e-02  & 1.953735e-01  \\
 \enddata
@@
 
+\begin{deluxetable*}{lcccc}
+%\tablenum{1}
+\tablecaption{Same as Figure~\ref{tab:sum} but without inject random noise to the simulation.\label{tab:sum_no_noise}}
+\tablewidth{0pt}
+\tablehead{
+\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
+\cline{2-4} 
+%  \cline{2-4}  \cline{5} \\
+\colhead{} &  \colhead{$0.2<z<0.4$} & \colhead{$0.4<z<0.6$} & \colhead{$0.6<z<0.8$} & \colhead{$1.2<z<1.7$}
+}
+\startdata
+%Observation & (0.07, 0.58) & (0.17, 0.52)  & (0.18, 0.54)  & (0.43, 0.31) \\
+SAM & (0.72, 0.20) & (0.64, 0.18) & (0.56, 0.16)  & (0.08, 0.18) \\
+MBII & (-0.15, 0.21) & \multicolumn{2}{c}{(-0.15, 0.22) [$z=0.6$]}  & (0.08, 0.19)\\
+Illustris & (0.03, 0.32) & (0.10, 0.36) & (0.08, 0.36)  & (0.04, 0.19) \\
+TNG100 &  (0.27, 0.20) & (0.27, 0.15) & (0.26, 0.16)  & (0.36, 0.15) \\
+TNG300 & (0.25, 0.21) & (0.19, 0.23) & (0.20, 0.22)  & (0.32, 0.16) \\
+Horizon & (0.24, 0.21) & (0.23, 0.22) & (0.29, 0.19)  & (0.37, 0.13) \\
+\enddata
+%\tablecomments{Same as Figure~\ref{tab:sum} but without inject noise to the simulation.}
+\end{deluxetable*}
+
 \section{Conclusion} \label{sec:con}
 %A brief introduce of the result. Scatter, central, which is best...
-We compare the scaling relation of \mbh-\smass\ using both the observation data and the predictions from numerical simulations.
-The observation data are composed of 612 quasars at $0.2 < z < 0.8$ imaged by HSC and 32 X-ray-selected quasars at $1.2 < z < 1.7$ imaged by HST.
-These observational measurements are compared with simulations including a semi-analytic model (SAM) and five hydrodynamic simulation, i.e., MBII, Illustris, TNG100, TNG300 and Horizon-AGN.
+We compared the scaling relation of \mbh-\smass\ using both the observation data and the predictions from numerical simulations.
+The observation data are composed of 612 quasars at $0.2 < z < 0.8$ imaged by HSC and 32 X-ray-selected quasars at $1.2 < z < 1.7$ that imaged by HST.
+These observational measurements are compared with simulations including a semianalytic model (SAM) and five hydrodynamic simulation, i.e., MBII, Illustris, TNG100, TNG300 and Horizon.
 We designed the direct comparisons that were made in the observational plane.
-To this end, we first injected random errors with the same observational uncertainty to the simulation, and then adopt the same selection condition to the simulation data.
-Finally, we adopted the scaling relation from the local universe and performed the comparisons using the scatter of the measurements and their central offset to the local relation.
+To this end, we first injected the random errors with same observational uncertainty to the simulation, and then adopt the same selection condition to the simulation data.
+Finally, we adopted the scaling relation from the local universe and performed the comparisons using the scatters of the measurements and their central offset to the local relation.
 
 %We also estimate the scatter of the sample without inject the noise.
-Our main results are presented in Figure~\ref{fig:offsets_vz} and the Table~\ref{tab:sum} which summarize the scatter and the offset for each sample.
-These results show that the scatter predicted by the simulations are all consistent to the observational measurements, i.e., $\sim0.5$~dex at $z<1$ and $\sim0.3$~dex at $z>1$.
-We note that the scatter are {\it apparent} rather than {\it intrinsic}, which are affected by the observational error and the selection effects.
-To understand how much the random observational error dominates the scatter, we re-run the estimation without injecting noise to the simulations.
-The obtained scatter for both $z<1$ and $z>1$ are at a comparable level of $\sim$0.15$-$0.2 dex.
-This result suggests that the tightness of the scaling relations have been formed up to redshift 1.7, which is against the scenario of the central limit theorem~\citep{Peng2007, Jahnke2011, Hirschmann2010} in which the scaling relation is a consequence of a stochastic cloud in the early universe with subsequent random mergers thereafter.
-Otherwise, the scatter of the scaling relations should increase towards higher redshift.
+Our main results are presented in Figure~\ref{fig:offsets_vz} and the Table~\ref{tab:sum} in which we summary the scatter and the offset for each sample.
+These results show that the scatters predicted by the simulations are all consistent to the observational measurements, i.e., $\sim0.5$~dex at $z<1$ and $\sim0.3$~dex at $z>1$.
+We note that the scatters are {\it apparent} rather than {\it intrinsic}, which are affected by the observational error and the selection effects.
+To understand how much the random observational error dominates the scatter, we re-run the estimation but not injecting noise to the simulations.
+The obtained scatter for both $z<1$ and $z>1$ are at a level of $\sim$0.15$-$0.2 dex, which remain unchanged.
+This result suggests that the tightness of the scaling relations have been formed up to redshift 1.7, which is against the scenario of the central limit theorem~\citep{Peng2007, Jahnke2011, Hirschmann2010} in which the scaling relation is a consequence of a stochastic cloud in the early universe with random merger.
+Otherwise, the scatter of the scaling relations should increase at higher redshift.
 In fact, the scatter level in the simulation without adding random noise are consistent with the {\it intrinsic} scatter estimations reported in~\citet{Ding2020, 2021arXiv210902751L}, which is also not larger than the typical scatter of the local relations reported in the literature~\citep[][i.e., $\gtrsim0.35$~dex]{Kormendy13, Gul++09, Reines2015}.
 
-The results also show that Illustris and Horizon-AGN simulation could predict well the scaling relation central offset (related to the local) at $z<0.6$, while SAM, TNG100, TNG300 and Horizon-AGN predict the {\it observed} evolution at $z>0.6$.
+The results also show that only the Illustris simulation could predict well the scaling relation central offset (related to the local) at $z<0.6$, while SAM, TNG100, TNG300 and Horizon can predict the {\it observed} evolution at $z>0.6$.
 \todo{As mentioned in the result section, we need provide some details on how the scaling relations in the simulations are calibrated.
 For example, why Illustris and TNG sample predict different center for the scaling relation.
-Horizon-AGN could predict well at both low and high z, maybe we can add some discussions.}
-From $z\sim0.7$ to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations could well predict the evolution trend of the scaling relation --- the  {\it observed} offset of the $\Delta$\mbh\ (to the local relation at a given \smass) is larger at higher redshift, which are clearly shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
+}
+Interestingly, TNG100, TNG300 and Horizon simulations could well predict the evolution trend of the scaling relation from $z\sim0.7$ to $z\sim1.5$ --- the  {\it observed} offset of the $\Delta$\mbh\ (to the local relation at a given \smass) is larger at higher redshift, which are clearly shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
 
-The simulations studied in this work have adopted completely different numerical techniques.
+The simulations studied in this work have adopted completely different numerical technique.
 However, all of them can provide good agreement with the observed dispersion in the scaling relation.
@@
 \ding{The fact that in previous SAM version with a different AGN feedback recipe, the apparent scatter in the simulation is much larger up to 0.7 dex.
-Hi Nicola, could you add more details here and example the different of AGN feedback in SAM compared to previous version?}
+Nicola, could you add more details here and example the different of AGN feedback in SAM compared to previous version?}
 So far, a control experiment is still not performed yet in which one numerical model provide the simulation and altering the AGN feedback prescription, while fixing all other conditions.

### 2021-11-24 decomp_example/AGN_decomp/1_read_result.py

@@ -1,101 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Sat Apr 27 17:55:30 2019
-
-@author: Dartoon
-"""
-import numpy as np
-import matplotlib.pyplot as plt
-import pickle
-import corner
-import astropy.io.fits as pyfits
-
-import sys
-sys.path.insert(0,'../../py_tools/')
-
-picklename = 'example.pkl'
-result = pickle.load(open(picklename,'rb'))
-
-#[best_fit,chain_r, trans_paras] = result      
-best_fit, chain_result, trans_paras   = result         
-source_result, image_host, ps_result, image_ps, _ =best_fit
-chain_list, _ = chain_result
-sampler_type, samples_mcmc, param_mcmc, dist_mcmc  = chain_list[1]
-
-#chain_list, param_list, _ = pso_fit
-#samples_mcmc, param_mcmc, dist_mcmc, _ = mcmc_fit
-_, _, mcmc_new_list, labels_new, _ = trans_paras            
-mcmc_new_list = np.asarray(mcmc_new_list)    
-#    [source_result, image_host, ps_result, image_ps, samples_mcmc, param_mcmc, paras, chain_list, param_list] = result
-#    [source_params_2, ps_param_2, mcmc_new_list, labels_new] = paras
-    #print "The fixed parameters in galaxy:", source_params_2
-    #%%
-#    print "plot the overall parameter contour:"
-#    plot = corner.corner(samples_mcmc, labels=param_mcmc, show_titles=True)
-#    plt.show()
-    
-print "plot the flux contour for all the hosts"
-plot = corner.corner(mcmc_new_list, labels=labels_new, show_titles=True)
-plt.show()
-
-#readout the parameter
-print "=================================\noverall fitting parameters:", param_mcmc
-idx = 0     #The inferred Reff of the host
-v_l=np.percentile(samples_mcmc[:,idx],16,axis=0)
-v_m=np.percentile(samples_mcmc[:,idx],50,axis=0)
-v_h=np.percentile(samples_mcmc[:,idx],84,axis=0)
-print "The inferred", param_mcmc[idx], ":"
-print "lower limit:", v_l
-print "The mid fit:", v_m
-print "upper limit", v_h
-
-##Readout the translated flux.
-print "=================================\noverall flux components:", labels_new
[…]

### 2021-11-24 decomp_example/HST_AGN_decomp_temp/sample2/0_analysis.py

@@ -1,137 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Thu May 23 16:58:39 2019
-
-@author: Dartoon
-"""
-
-import numpy as np
-import astropy.io.fits as pyfits
-import matplotlib.pyplot as plt
-import glob
-#from gen_fit_id import gen_fit_id
-from photutils import make_source_mask
-import os
-#plt.ion()
-
-import sys
-sys.path.insert(0,'../../../py_tools/')
-from fit_qso import fit_qso
-from transfer_to_result import transfer_to_result, transfer_obj_to_result
-from mask_objects import detect_obj
-from flux_profile import profiles_compare, flux_profile
-from matplotlib.colors import LogNorm
-
-#Setting the fitting condition:
-deep_seed = False  #Set as True to put more seed and steps to fit.
-pltshow = 1 #Note that setting plt.ion() in line27, the plot won't show anymore if running in terminal.
-pix_scale = 0.0642 
-fixcenter = False
-run_MCMC = True
-zp=26.4524
-
-psf, QSO_img, QSO_std = pyfits.getdata('psf_77.fits'),  pyfits.getdata('CID1174_cutout.fits'),  pyfits.getdata('wht_err.fits')
-
-frame_size = 61
-#frame = '{0}'.format(frame_size)
-QSO_fm = len(QSO_img)
-ct = (QSO_fm-frame_size)/2     # If want to cut to 61, i.e. (121-61)/2=30
-
-QSO_img = QSO_img[ct:-ct,ct:-ct]
-QSO_std = QSO_std[ct:-ct,ct:-ct]
-psf = psf[ct:-ct,ct:-ct]
-#%%
-#==============================================================================
-# input the objects components and parameteres
-#==============================================================================
-objs, Q_index = detect_obj(QSO_img,pltshow = pltshow)
-qso_info = objs[Q_index]
-obj = [objs[i] for i in range(len(objs)) if i != Q_index]
-fixed_source = []
-kwargs_source_init = []
-kwargs_source_sigma = []
-kwargs_lower_source = []
-kwargs_upper_source = []
-fixed_source.append({})  
-kwargs_source_init.append({'R_sersic': 0.3, 'n_sersic': 2., 'e1': 0., 'e2': 0., 'center_x': 0., 'center_y': 0.})
[…]

### 2021-11-24 decomp_example/HST_AGN_decomp_temp/sample2/1_read_result.py

@@ -1,114 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Sat Apr 27 17:55:30 2019
-
-@author: Dartoon
-"""
-import numpy as np
-import matplotlib.pyplot as plt
-import pickle
-import corner
-import astropy.io.fits as pyfits
-
-import sys
-sys.path.insert(0,'../../../py_tools/')
-
-picklename = 'example.pkl'
-result = pickle.load(open(picklename,'rb'))
-
-#[best_fit,chain_r, trans_paras] = result      
-best_fit, chain_result, trans_paras   = result         
-source_result, image_host, ps_result, image_ps, _ =best_fit
-chain_list, _ = chain_result
-sampler_type, samples_mcmc, param_mcmc, dist_mcmc  = chain_list[1]
-
-#chain_list, param_list, _ = pso_fit
-#samples_mcmc, param_mcmc, dist_mcmc, _ = mcmc_fit
-_, _, mcmc_new_list, labels_new, _ = trans_paras            
-mcmc_new_list = np.asarray(mcmc_new_list)    
-#    [source_result, image_host, ps_result, image_ps, samples_mcmc, param_mcmc, paras, chain_list, param_list] = result
-#    [source_params_2, ps_param_2, mcmc_new_list, labels_new] = paras
-    #print "The fixed parameters in galaxy:", source_params_2
-    #%%
-#    print "plot the overall parameter contour:"
-#    plot = corner.corner(samples_mcmc, labels=param_mcmc, show_titles=True)
-#    plt.show()
-    
-print "plot the flux contour for all the hosts"
-plot = corner.corner(mcmc_new_list, labels=labels_new, show_titles=True)
-plt.show()
-
-#readout the parameter
-print "=================================\noverall fitting parameters:", param_mcmc
-idx = 0     #The inferred Reff of the host
-v_l=np.percentile(samples_mcmc[:,idx],16,axis=0)
-v_m=np.percentile(samples_mcmc[:,idx],50,axis=0)
-v_h=np.percentile(samples_mcmc[:,idx],84,axis=0)
-print "The inferred", param_mcmc[idx], ":"
-print "lower limit:", v_l
-print "The mid fit:", v_m
-print "upper limit", v_h
-
-##Readout the translated flux.
[…]

### 2021-11-24 decomp_example/HST_AGN_decomp_temp/sample3/1_read_result.py

@@ -1,113 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Sat Apr 27 17:55:30 2019
-
-@author: Dartoon
-"""
-import numpy as np
-import matplotlib.pyplot as plt
-import pickle
-import corner
-import astropy.io.fits as pyfits
-
-import sys
-sys.path.insert(0,'../../../py_tools/')
-
-picklename = 'example.pkl'
-result = pickle.load(open(picklename,'rb'))
-
-#[best_fit,chain_r, trans_paras] = result      
-best_fit, chain_result, trans_paras   = result         
-source_result, image_host, ps_result, image_ps, _ =best_fit
-chain_list, _ = chain_result
-sampler_type, samples_mcmc, param_mcmc, dist_mcmc  = chain_list[1]
-
-#chain_list, param_list, _ = pso_fit
-#samples_mcmc, param_mcmc, dist_mcmc, _ = mcmc_fit
-_, _, mcmc_new_list, labels_new, _ = trans_paras            
-mcmc_new_list = np.asarray(mcmc_new_list)    
-#    [source_result, image_host, ps_result, image_ps, samples_mcmc, param_mcmc, paras, chain_list, param_list] = result
-#    [source_params_2, ps_param_2, mcmc_new_list, labels_new] = paras
-    #print "The fixed parameters in galaxy:", source_params_2
-    #%%
-#    print "plot the overall parameter contour:"
-#    plot = corner.corner(samples_mcmc, labels=param_mcmc, show_titles=True)
-#    plt.show()
-    
-print "plot the flux contour for all the hosts"
-plot = corner.corner(mcmc_new_list, labels=labels_new, show_titles=True)
-plt.show()
-
-#readout the parameter
-print "=================================\noverall fitting parameters:", param_mcmc
-idx = 0     #The inferred Reff of the host
-v_l=np.percentile(samples_mcmc[:,idx],16,axis=0)
-v_m=np.percentile(samples_mcmc[:,idx],50,axis=0)
-v_h=np.percentile(samples_mcmc[:,idx],84,axis=0)
-print "The inferred", param_mcmc[idx], ":"
-print "lower limit:", v_l
-print "The mid fit:", v_m
-print "upper limit", v_h
-
-##Readout the translated flux.
[…]

### 2021-11-24 decomp_example/galaxy_decomp/analysis.py

@@ -1,91 +1,0 @@
-#!/usr/bin/env python2
-# -*- coding: utf-8 -*-
-"""
-Created on Thu May 23 16:58:39 2019
-
-@author: Dartoon
-"""
-
-import numpy as np
-import astropy.io.fits as pyfits
-import matplotlib.pyplot as plt
-import glob
-#from gen_fit_id import gen_fit_id
-from photutils import make_source_mask
-import os
-#plt.ion()
-
-import sys
-sys.path.insert(0,'../../py_tools/')
-from fit_qso import fit_galaxy
-from transfer_to_result import transfer_to_result, transfer_obj_to_result
-from mask_objects import detect_obj
-from flux_profile import profiles_compare, flux_profile, galaxy_total_compare
-from matplotlib.colors import LogNorm
-import copy
-import time
-import pickle
-
-#Setting the fitting condition:
-deep_seed = False  #Set as True to put more seed and steps to fit.
-pltshow = 1 #Note that setting plt.ion() in line27, the plot won't show anymore if running in terminal.
-pix_scale = 0.168
-run_MCMC = True
-zp = 27.0
-
-psf, galaxy_img, galaxy_std = pyfits.getdata('PSF.fits'),  pyfits.getdata('galaxy_im.fits'),  pyfits.getdata('galaxy_err.fits')
-#%%
-#==============================================================================
-# input the objects components and parameteres
-#==============================================================================
-objs, Q_index = detect_obj(galaxy_img,pltshow = pltshow, snr=1.2)
-galaxy_info = objs[Q_index]
-obj = [objs[i] for i in range(len(objs)) if i != Q_index]
-fixed_source = []
-kwargs_source_init = []
-kwargs_source_sigma = []
-kwargs_lower_source = []
-kwargs_upper_source = []
-fixed_source.append({})  
-kwargs_source_init.append({'R_sersic': 1, 'n_sersic': 2., 'e1': 0., 'e2': 0., 'center_x': -galaxy_info[0][0]*pix_scale, 'center_y': galaxy_info[0][1]*pix_scale})
-kwargs_source_sigma.append({'n_sersic': 0.5, 'R_sersic': 0.5, 'e1': 0.1, 'e2': 0.1, 'center_x': 0.1, 'center_y': 0.1})
-kwargs_lower_source.append({'e1': -0.5, 'e2': -0.5, 'R_sersic': 0.1, 'n_sersic': 0.3, 'center_x': -0.5, 'center_y': -0.5})
[…]

### 2021-11-24 package_code/galight_example/run_batch_job.sh

@@ -1,0 +1,25 @@
+#!/usr/bin/perl
+
+$filename="source_list.asc";
+
+open(READFILE,$filename);
+
+$i=0;
+
+while(<READFILE>) {
+    chop($_);
+    @data=split(" ",$_);
+    $name[$i]=$data[0];
+    $ra[$i]=$data[1];
+    $dec[$i]=$data[2];
+
+    $command="python3 run_HSC_galaxy.py ".$name[$i]." I ".$ra[$i]." ".$dec[$i];
+
+    printf("Running on target %s \n",$name[$i]);
+    system($command);
+    sleep(1.0);
+
+    $i=$i+1;     
+}
+close(READFILE);
+$N=$i;

### 2021-11-24 projects/2020_HSC_bulge_fit/check_out_fitting.py

@@ -26,11 +26,10 @@ fitsFile_ = glob.glob('SDSS_0.2-0.3/*_HSC-I.fits')
 # for NO in range(55):    
 # for NO in range(len(fitsFile_)): 
 for NO in [13]:    
-# for NO in [66]:
     fitsFile  = fitsFile_[NO]
     ID = fitsFile.split('/')[1].split('_')[0]
     PSF_filename = fitsFile.split('.fits')[0]+ '_psf.fits'
-    save_name = 'fit_result1/' + fitsFile.split('.fits')[0].split('/')[1]
+    save_name = 'fit_result_202110/' + fitsFile.split('.fits')[0].split('/')[1]
     ## Test load pkl
     
     picklename = save_name+'single_Sersic.pkl'
@@ -39,14 +38,18 @@ for NO in [13]:
     picklename = save_name+'bulge+disk.pkl'
     fitting_run_class_1 = pickle.load(open(picklename,'rb'))
     
+    picklename = save_name+'bar+disk.pkl'
+    fitting_run_class_1b = pickle.load(open(picklename,'rb'))
+    
     picklename = save_name+'bar+bulge+disk.pkl'
     fitting_run_class_2 = pickle.load(open(picklename,'rb'))
 
     
     bic_0 = fitting_run_class_0.fitting_seq.bic
     bic_1 = fitting_run_class_1.fitting_seq.bic
+    bic_1b = fitting_run_class_1b.fitting_seq.bic
     bic_2 = fitting_run_class_2.fitting_seq.bic
-    if bic_0 < bic_1:
+    if 10 < 2:
         print(ID+" is a singel Sersic model; "+"glob Number: " + str(NO))
     else:
         print(ID+" is a disk+bulge!!! "+"glob Number: " + str(NO))
@@ -57,47 +60,67 @@ for NO in [13]:
         #%%Disk+bulge
         print(ID+"Disk + Bulge fit:")    
         fitting_run_class_1.plot_final_qso_fit(target_ID =  ID)
-        bulge1 = fitting_run_class_1.image_host_list[0]
-        disk1 = fitting_run_class_1.image_host_list[1]
+        disk1 = fitting_run_class_1.image_host_list[0]
+        bulge1 = fitting_run_class_1.image_host_list[1]
         B2T = np.sum(bulge1)/np.sum(bulge1+disk1)
         AGN1 = fitting_run_class_1.image_ps_list[0]
         bulge_Re1 = fitting_run_class_1.final_result_galaxy[0]['R_sersic']
[…]

### 2021-11-24 projects/2020_HSC_to_numerical_simulation/HSCvsIllustris.py

@@ -141,7 +141,7 @@ plt.show()
 f,ax=plt.subplots(1,1,figsize=(14,12))   
 import matplotlib as mpl
 obj=ax
-panel2=obj.hist2d(Illustris['Stellar_Mass_nois'], Illustris['BH_Mass_nois'],
+panel2=obj.hist2d(Illustris['Stellar_Mass'], Illustris['BH_Mass'],
                   norm=mpl.colors.LogNorm(), density = True, cmap='summer',bins=50,zorder=-1,
                       alpha=0.5, cmin = 0.001 , cmax = 1.1)
 
@@ -164,98 +164,164 @@ plt.tick_params(labelsize=25)
 plt.tick_params(which='both', width=2, top=True, right=True,direction='in')
 plt.tick_params(which='major', length=10)
 plt.tick_params(which='minor', length=6)#, color='r’)
-plt.legend(scatterpoints=1,numpoints=1,loc=2,prop={'size':28},ncol=2,handletextpad=0)
+plt.legend(scatterpoints=1,numpoints=1,loc=2,prop={'size':32},ncol=1,handletextpad=0)
 from matplotlib.ticker import AutoMinorLocator
 ax.xaxis.set_minor_locator(AutoMinorLocator())
 ax.yaxis.set_minor_locator(AutoMinorLocator())
 cbar=f.colorbar(panel2[3],ax=obj)
 cbar.ax.tick_params(labelsize=30) 
-# plt.savefig('MM_Illustris_zs_{0}.png'.format(zs))
+plt.savefig('MM_Illustris_zs_{0}.png'.format(zs))
 plt.show()
 
 #%%
-#Plot the 1-D scatter for MM.
-fig, ax = plt.subplots(figsize=(8,7))
-plt.hist(Illustris_scatter_nosl, histtype=u'step',density=True,
-          label=('Illustris sample scatter nosl'), linewidth = 2, color='gray')
-plt.hist(Illustris_scatter,histtype=u'step',density=True,
-          label=('Illustris sample scatter'), linewidth = 2, color='c')
-plt.hist(HSC_scatter, histtype=u'step',density=True,
-          label=('HSC sample scatter'), linewidth = 2, color='orange')
-# plt.hist(Illustris_scatter_noselect,histtype=u'step',density=True,
[…]

### 2021-11-24 projects/2020_HSC_to_numerical_simulation/HSCvsMBII.py

@@ -26,7 +26,7 @@ ifplot = True
 
 detlaM  = 0
 imf = 'Sal'
-if imf == 'Sal':
+if imf == 'Sal': 
     detlaM = 0.23
     
 #%%
@@ -102,7 +102,7 @@ for ii in range(1):
     else:
         plt.close()
     
-    #%% 
+    #%% Plot the selection
     fig, ax = plt.subplots(figsize=(11,9))
     from prep_comparison import quasar_filter
     # plt.scatter( MBII['BH_Mass_nois'], MBII['logLbol_nois'],
@@ -110,7 +110,7 @@ for ii in range(1):
     import matplotlib as mpl
     BH_overall, logLbol_overall = MBII['BH_Mass_nois'][MBII['logLbol_nois']>0], MBII['logLbol_nois'][MBII['logLbol_nois']>0]
     plt.hist2d(BH_overall, logLbol_overall,norm=mpl.colors.LogNorm(),
-               cmap='summer',bins=50,zorder=0,alpha=0.5)
+                cmap='summer',bins=50,zorder=0,alpha=0.5)
     cbar = plt.colorbar()
     cbar.ax.tick_params(labelsize=30) 
     type1_bools = quasar_filter([logLbol_overall, BH_overall], HSC['HSC_Lbol_overall'], HSC['HSC_MBHs_overall'])
@@ -120,7 +120,7 @@ for ii in range(1):
                 edgecolors='gray', alpha=0.8,zorder = 0.5, label= 'HSC observed sample')
     plt.xlabel(r'log(M$_{\rm BH}$/M$_{\odot}$)',fontsize=30)
     plt.ylabel(r'log(L$_{\rm bol}$)', fontsize=30)
-    plt.ylim(38, 48)
+    plt.ylim(40, 48)
     plt.xlim(5.8,10)
     plt.tick_params(labelsize=25)
     from matplotlib.ticker import AutoMinorLocator
@@ -129,19 +129,105 @@ for ii in range(1):
     plt.tick_params(which='major', length=12)
     plt.tick_params(which='minor', length=6)#, color='gray')
     plt.legend(loc='lower right',fontsize=21,numpoints=1)
+    plt.savefig('HSC_selection_MBII.png')
     if ifplot == True:
         plt.show()
     else:
         plt.close()
         
[…]

### 2021-11-24 projects/2020_HSC_to_numerical_simulation/HSCvsSAM.py

@@ -109,11 +109,11 @@ for ii in range(1):
     import matplotlib as mpl
     obj=ax
     # panel2=obj.hist2d(SAM['Stellar_Mass_reali'], SAM['BH_Mass_reali'], #!!!
-    panel2=obj.hist2d(SAM['Stellar_Mass_nois'], SAM['BH_Mass_nois'],
-                      norm=mpl.colors.LogNorm(), density = True, cmap='summer',bins=50,zorder=-1,
+    panel2=obj.hist2d(SAM['Stellar_Mass_reali'], SAM['BH_Mass_reali'],
+                      norm=mpl.colors.LogNorm(), density = True, cmap='summer',bins=50,zorder=10,
                       alpha=0.5, cmin = 0.001 , cmax = 1.1)
     
-    plt.scatter(SAM['Stellar_Mass_nois_sl'][:500], SAM['BH_Mass_nois_sl'][:500],c='green',
+    plt.scatter(SAM['Stellar_Mass_nois_sl'][:500], SAM['BH_Mass_nois_sl'][:500],c='pink',
                 s=420, marker=".",zorder=1.2, edgecolors='k', alpha = 0.7, label='SAM sample z={0}'.format(zs))
     # plt.scatter(HSC['HSC_Mstar'],HSC['HSC_MBHs'],c='orange',
     #             s=220, marker=".",zorder=-1, edgecolors='k', alpha = 0.7, label='HSC sample')
@@ -133,142 +133,208 @@ for ii in range(1):
     plt.tick_params(which='both', width=2, top=True, right=True,direction='in')
     plt.tick_params(which='major', length=10)
     plt.tick_params(which='minor', length=6)#, color='r’)
-    plt.legend(scatterpoints=1,numpoints=1,loc=2,prop={'size':28},ncol=2,handletextpad=0)
+    plt.legend(scatterpoints=1,numpoints=1,loc=2,prop={'size':32},ncol=1,handletextpad=0)
     from matplotlib.ticker import AutoMinorLocator
     ax.xaxis.set_minor_locator(AutoMinorLocator())
     ax.yaxis.set_minor_locator(AutoMinorLocator())
     cbar=f.colorbar(panel2[3],ax=obj, ticks=[])
     cbar.ax.tick_params(labelsize=30) 
-    # plt.savefig('MM_SAM_zs_{0}.png'.format(zs))
+    plt.savefig('MM_SAM_zs_{0}.png'.format(zs))
     plt.show()        
     
[…]

### 2021-11-24 projects/2020_HSC_to_numerical_simulation/HSCvsTNG.py

@@ -11,6 +11,8 @@ import matplotlib.pyplot as plt
 import astropy.io.fits as pyfits
 import glob
 import scipy.stats as st
+import matplotlib as mat
+mat.rcParams['font.family'] = 'STIXGeneral'
 
 #%%
 from prep_comparison import HSC_set, TNG_set, comp_plot
@@ -113,132 +115,196 @@ plt.show()
 
 
 #%%
-f,ax=plt.subplots(1,1,figsize=(14,12))   
-# plt.scatter(TNG['Stellar_Mass_nois'], TNG['BH_Mass_nois'],c='gray',
-#             s=220, marker=".",zorder=-10, edgecolors='k', alpha = 0.2)
-import matplotlib as mpl
-obj=ax
-panel2=obj.hist2d(TNG['Stellar_Mass_nois'], TNG['BH_Mass_nois'],
-                  norm=mpl.colors.LogNorm(), density = True, cmap='summer',bins=50,zorder=-1,
-                      alpha=0.5, cmin = 0.001 , cmax = 1.1)
+# f,ax=plt.subplots(1,1,figsize=(14,12))   
+# # plt.scatter(TNG['Stellar_Mass_nois'], TNG['BH_Mass_nois'],c='gray',
+# #             s=220, marker=".",zorder=-10, edgecolors='k', alpha = 0.2)
+# obj=ax
+# panel2=obj.hist2d(TNG['Stellar_Mass'], TNG['BH_Mass'],
+#                   norm=mpl.colors.LogNorm(), density = True, cmap='summer',bins=50,zorder=-1,
+#                       alpha=0.5, cmin = 0.001)# , cmax = 1.1)
 
-# plt.scatter(TNG['Stellar_Mass'], TNG['BH_Mass'],c='g',
-#             s=420, marker=".",zorder=0, edgecolors='g', alpha = 0.05, label='TNG100 sample z={0}'.format(zs))
+# # plt.scatter(TNG['Stellar_Mass'], TNG['BH_Mass'],c='g',
+# #             s=420, marker=".",zorder=0, edgecolors='g', alpha = 0.05, label='TNG100 sample z={0}'.format(zs))
 
-plt.scatter(TNG['Stellar_Mass_nois_sl'], TNG['BH_Mass_nois_sl'],c='deeppink',
[…]

### 2021-11-24 projects/2020_HSC_to_numerical_simulation/HSCvsTNG300.py

@@ -117,7 +117,7 @@ f,ax=plt.subplots(1,1,figsize=(14,12))
 #             s=220, marker=".",zorder=-10, edgecolors='k', alpha = 0.2)
 import matplotlib as mpl
 obj=ax
-panel2=obj.hist2d(TNG300['Stellar_Mass_nois'], TNG300['BH_Mass_nois'],
+panel2=obj.hist2d(TNG300['Stellar_Mass'], TNG300['BH_Mass'],
                   norm=mpl.colors.LogNorm(), density = True, cmap='summer',bins=50,zorder=-1,
                       alpha=0.5, cmin = 0.001 , cmax = 1.1)
 
@@ -140,7 +140,7 @@ plt.tick_params(labelsize=25)
 plt.tick_params(which='both', width=2, top=True, right=True,direction='in')
 plt.tick_params(which='major', length=10)
 plt.tick_params(which='minor', length=6)#, color='r’)
-plt.legend(scatterpoints=1,numpoints=1,loc=2,prop={'size':28},ncol=2,handletextpad=0)
+plt.legend(scatterpoints=1,numpoints=1,loc=2,prop={'size':32},ncol=1,handletextpad=0)
 from matplotlib.ticker import AutoMinorLocator
 ax.xaxis.set_minor_locator(AutoMinorLocator())
 ax.yaxis.set_minor_locator(AutoMinorLocator())
@@ -148,88 +148,156 @@ cbar=f.colorbar(panel2[3],ax=obj)
 cbar.ax.tick_params(labelsize=30) 
 # plt.savefig('MM_TNG300_zs_{0}.png'.format(zs))
 plt.show()
-#%%
-#Plot the 1-D scatter for MM.
-fig, ax = plt.subplots(figsize=(8,7))
-plt.hist(TNG300_scatter_nosl, histtype=u'step',density=True,
-          label=('TNG300 sample scatter nosl'), linewidth = 2, color='gray')
-plt.hist(TNG300_scatter,histtype=u'step',density=True,
-          label=('TNG300 sample scatter'), linewidth = 2, color='deeppink')
-plt.hist(HSC_scatter, histtype=u'step',density=True,
-          label=('HSC sample scatter'), linewidth = 2, color='orange')
-# plt.hist(TNG300_scatter_noselect,histtype=u'step',density=True,
[…]

### 2021-11-24 projects/2020_HSC_to_numerical_simulation/HST_VS_Horizon.py

@@ -82,7 +82,7 @@ for ii in range(1):
     plt.hist2d(bhmass_overall,np.log10(Eddr_overall),norm=mpl.colors.LogNorm(),cmap='copper',bins=50,zorder=0,alpha=0.5)
     # cbar = plt.colorbar()
     # cbar.ax.tick_params(labelsize=30) 
-    plt.errorbar(bhmass_select_noi, Eddr_select_noi, c='steelblue',linestyle=' ',marker='o',ms=10,mec='k', label='selected Horizon sample')
+    plt.errorbar(bhmass_select_noi, Eddr_select_noi, c='steelblue',linestyle=' ',marker='o',ms=10,mec='k', label='selected Horizon-AGN sample')
     xspace = np.linspace(6,10)
     plt.plot(xspace, 0*xspace,'k--',linewidth=3)
     plt.plot(xspace, 0*xspace-1.5,'k--',linewidth=3)
@@ -200,7 +200,7 @@ for ii in range(1):
     plt.hist(stellar_mass_obs - lfit(bh_mass_obs), histtype=u'step',density=True,
              label='HST sample', linewidth = 2, color='orange')
     plt.hist(mstar_selected - lfit(bhmass_selected),histtype=u'step',density=True,
-             label='Horizon sample', linewidth = 2, color='steelblue')
+             label='Horizon-AGN sample', linewidth = 2, color='steelblue')
     plt.title(r"The offset comparison for the M$_{\rm BH}$-M$_{*}$ relation", fontsize = 20)
     plt.tick_params(labelsize=20)
     plt.legend(prop={'size':20})
@@ -227,17 +227,17 @@ for ii in range(1):
     sim_offset = mstar_selected - lfit(bhmass_selected)
     obs_offset = stellar_mass_obs - lfit(bh_mass_obs)
     leng = max(len(sim_offset),len(obs_offset))
-    rfilename = 'offset_result/' + 'Horizon_zs{0}.txt'.format(zs)
-    if_file = glob.glob(rfilename)
-    write_file =  open(rfilename,'w') 
-    for i in range(leng):
-        try:
-            write_file.write('{0} {1} {2} {3} {4} {5} {6}'.format(sim_offset_nosl[i], sim_offset[i], obs_offset[i], 
-                                                                  mstar_selected[i], bhmass_selected[i], stellar_mass_obs[i], bh_mass_obs[i] ))
[…]

### 2021-11-24 projects/2020_HSC_to_numerical_simulation/HST_VS_SAM.py

@@ -35,7 +35,7 @@ filename = 'SAM/catalogue.dat'
 
 for ii in range(1):
     SAM = SAM_set(filename, zs=zs, HSC_Lbol_overall=HSC['HSC_Lbol_overall'], HSC_MBHs_overall=HSC['HSC_MBHs_overall'],
-                  I_mag_break = [20.5 +5 ,22.0 + 5 ])  #Will take the overall
+                  I_mag_break = [20.5 +5 ,22.0 + 5 ])  #Will take the overall, just quickly load SAM sample. Selection will do later.
     
     BH_Mass = SAM['BH_Mass_reali']
     Stellar_Mass = SAM['Stellar_Mass_reali']
@@ -231,17 +231,17 @@ for ii in range(1):
     sim_offset = mstar_selected - lfit(bhmass_selected)
     obs_offset = stellar_mass_obs - lfit(bh_mass_obs)
     leng = max(len(sim_offset),len(obs_offset))
-    rfilename = 'offset_result/' + 'SAM_zs{0}.txt'.format(zs)
-    if_file = glob.glob(rfilename)
-    write_file =  open(rfilename,'w') 
-    for i in range(leng):
-        try:
-            write_file.write('{0} {1} {2} {3} {4} {5} {6}'.format(sim_offset_nosl[i], sim_offset[i], obs_offset[i], 
-                                                                  mstar_selected[i], bhmass_selected[i], stellar_mass_obs[i], bh_mass_obs[i] ))
-        except:
-            write_file.write('{0} {1} -99 {2} {3} -99 -99'.format(sim_offset_nosl[i], sim_offset[i], mstar_selected[i], bhmass_selected[i]))
-        write_file.write("\n")
-    write_file.close()    
+    # rfilename = 'offset_result/' + 'SAM_zs{0}.txt'.format(zs)
+    # if_file = glob.glob(rfilename)
+    # write_file =  open(rfilename,'w') 
+    # for i in range(leng):
+    #     try:
+    #         write_file.write('{0} {1} {2} {3} {4} {5} {6}'.format(sim_offset_nosl[i], sim_offset[i], obs_offset[i], 
+    #                                                               mstar_selected[i], bhmass_selected[i], stellar_mass_obs[i], bh_mass_obs[i] ))
+    #     except:
[…]

### 2021-11-24 projects/2020_HSC_to_numerical_simulation/HST_VS_TNG.py

@@ -226,17 +226,17 @@ for ii in range(1):
     sim_offset = mstar_selected - lfit(bhmass_selected)
     obs_offset = stellar_mass_obs - lfit(bh_mass_obs)
     leng = max(len(sim_offset),len(obs_offset))
-    rfilename = 'offset_result/' + 'TNG100_zs{0}.txt'.format(zs)
-    if_file = glob.glob(rfilename)
-    write_file =  open(rfilename,'w') 
-    for i in range(leng):
-        try:
-            write_file.write('{0} {1} {2} {3} {4} {5} {6}'.format(sim_offset_nosl[i], sim_offset[i], obs_offset[i], 
-                                                                  mstar_selected[i], bhmass_selected[i], stellar_mass_obs[i], bh_mass_obs[i] ))
-        except:
-            write_file.write('{0} {1} -99 {2} {3} -99 -99'.format(sim_offset_nosl[i], sim_offset[i], mstar_selected[i], bhmass_selected[i]))
-        write_file.write("\n")
-    write_file.close()    
+    # rfilename = 'offset_result/' + 'TNG100_zs{0}.txt'.format(zs)
+    # if_file = glob.glob(rfilename)
+    # write_file =  open(rfilename,'w') 
+    # for i in range(leng):
+    #     try:
+    #         write_file.write('{0} {1} {2} {3} {4} {5} {6}'.format(sim_offset_nosl[i], sim_offset[i], obs_offset[i], 
+    #                                                               mstar_selected[i], bhmass_selected[i], stellar_mass_obs[i], bh_mass_obs[i] ))
+    #     except:
+    #         write_file.write('{0} {1} -99 {2} {3} -99 -99'.format(sim_offset_nosl[i], sim_offset[i], mstar_selected[i], bhmass_selected[i]))
+    #     write_file.write("\n")
+    # write_file.close()    
     # print("obs scatter:", obs_scatter)
     # print("sim scatter:", sim_scatter)
 
@@ -244,7 +244,7 @@ for ii in range(1):
     # Plot the fitting with scatter 
     f,ax=plt.subplots(1,1,figsize=(14,12))
     obj=ax
-    panel2=obj.hist2d(mstar_overall_noi,bhmass_overall_noi,
[…]

### 2021-11-24 projects/2020_HSC_to_numerical_simulation/HST_VS_TNG300.py

@@ -277,7 +277,7 @@ for ii in range(1):
     # plt.plot(x_obs_space,y_space,color='orange',linewidth=3, zorder = 101)
     # x_space_ub=lfit(y_space,fit[0][0],fit[0][1]+sim_scatter)
     # x_space_lb=lfit(y_space,fit[0][0],fit[0][1]-sim_scatter)
-    # plt.fill_betweenx(y_space,x_space_lb,x_space_ub,color='deeppink',alpha=0.35,zorder =1)
+    # plt.fill_betweenx(y_space,x_space_lb,x_space_ub,color='plum',alpha=0.35,zorder =1)
     # x_space_ub=lfit_fixm(y_space,fit_fixm[0]+obs_scatter)
     # x_space_lb=lfit_fixm(y_space,fit_fixm[0]-obs_scatter)                                    
     # plt.fill_betweenx(y_space,x_space_lb,x_space_ub,color='orange',alpha=0.35,zorder =1)
@@ -298,11 +298,77 @@ for ii in range(1):
     obj.set_ylabel(r'log(M$_{\rm BH}$/M$_{\odot}$)',fontsize=35)
     obj.set_xlabel('log(M$_{*}$/M$_{\odot}$)',fontsize=35)
     obj.legend(loc='upper left',fontsize=30,numpoints=1)
-    plt.savefig('MM_TNG300_zs_{0}.png'.format(zs))
+    # plt.savefig('MM_TNG300_zs_{0}.png'.format(zs))
     if ifplot == True:
         plt.show()
     else:
         plt.close()    
+        
+    #%%Plot offset        
+    # import matplotlib as mpl
+    # from matplotlib.ticker import AutoMinorLocator
+    f,ax=plt.subplots(1,2,figsize=(12,10),gridspec_kw={'width_ratios': [7, 1]}, sharey = True)
+    # f.suptitle(r"Offset VS M*, z={0}".format(zs), fontsize = 20)
+    obj=ax[0]
+    
+    sm_int, bh_int = mstar_overall,bhmass_overall
+    sm_sim, bh_sim = mstar_selected,bhmass_selected
+    sm_obs, bh_obs = stellar_mass_obs,bh_mass_obs
+    m_ml, b_ml = (0.981139684856507, -2.545890295477823)
+    
+    off_int = sm_int, bh_int - (m_ml*sm_int+b_ml)
[…]

### 2021-11-24 projects/2020_HSC_to_numerical_simulation/figs/MM_vz_32QSO+600HSC+simulation.py

@@ -1,0 +1,442 @@
+#!/usr/bin/env python2
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Feb 17 12:54:19 2020
+
+@author: Dartoon
+"""
+import numpy as np
+np.set_printoptions(precision=4)
+import matplotlib.pyplot as plt
+import matplotlib as mat
+import matplotlib.lines as mlines
+from matplotlib import colors
+mat.rcParams['font.family'] = 'STIXGeneral'
+host=plt.figure(figsize=(14.5,12))
+ax=host.add_subplot(111)   #to get the log(1+z) and z label
+
+import matplotlib as mpl
+mpl.rc('image', cmap='jet')
+# import sys
+########## input local data ####
+#==============================================================================
+# The seleting for dm and host_total and dmag are in this local
+#==============================================================================
+########input 25 local by Bennert++2011 ############
+bloc = np.array([[ 0.054 , 10.12  ,  0.24  ,  7.436 ,  0.4   ],
+       [ 0.043 , 10.95  ,  0.23  ,  8.006 ,  0.4   ],
+       [ 0.076 , 10.33  ,  0.22  ,  7.436 ,  0.4   ],
+       [ 0.041 , 10.38  ,  0.23  ,  7.166 ,  0.4   ],
+       [ 0.051 , 10.5   ,  0.23  ,  8.516 ,  0.4   ],
+       [ 0.0524, 10.32  ,  0.23  ,  6.976 ,  0.4   ],
+       [ 0.0475,  9.83  ,  0.24  ,  7.666 ,  0.4   ],
+       [ 0.055 , 10.41  ,  0.23  ,  7.836 ,  0.4   ],
+       [ 0.0355, 10.33  ,  0.22  ,  7.766 ,  0.4   ],
+       [ 0.021 , 10.2   ,  0.22  ,  7.366 ,  0.4   ],
+       [ 0.038 , 10.26  ,  0.22  ,  7.356 ,  0.4   ],
+       [ 0.0229,  9.94  ,  0.24  ,  7.496 ,  0.4   ],
+       [ 0.047 , 10.14  ,  0.22  ,  7.646 ,  0.4   ],
[…]

### 2021-11-24 projects/2020_HSC_to_numerical_simulation/offset_plot.py

@@ -13,126 +13,163 @@ import glob
 from matplotlib.ticker import AutoMinorLocator
 from scipy import stats
 
-zs = 1.5
+import matplotlib as mat
+mat.rcParams['font.family'] = 'STIXGeneral'
+
+zs = 0.7
 files = glob.glob("offset_result/*{0}.txt".format(zs))
 if zs == 0.5 or zs == 0.7:
     files = files+glob.glob("offset_result/*{0}.txt".format(0.6))
 files.sort()
 ct = 0
-fig, ax = plt.subplots(figsize=(8,7))
+# fig, ax = plt.subplots(figsize=(8,7))
 # colors = ['green','steelblue','c','deeppink','plum','m']
+colors = ['#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf']
+fig, axs = plt.subplots(len(files)+1, figsize=(5,8), sharex = True)
 for i in [3,2,1,4,5,0]:
     data = np.loadtxt(files[i]) #nosl, sl, obs, sl_M*, sl_BH, obs_M*, obs_BH
     if zs == 1.5:
         data[:,2] = -data[:,2]
+        data[:,1] = -data[:,1]
+    
     if ct == 0:
-        plt.hist(data[:,2][abs(data[:,2])!=99],histtype=u'step',density=True,
-                  label=' Observation', linewidth = 4)
-        
-    plt.hist(data[:,1][abs(data[:,1])!=99], histtype=u'step',density=True,
-              label=' '+files[i].split("/")[1].split('_')[0], linewidth = 2,alpha = 0.8)
-              # color = colors[i])
-    ct += 1
-    pvalue = stats.ks_2samp(data[:,2][abs(data[:,2])!=99], data[:,1][abs(data[:,1])!=99] ).pvalue
-    if pvalue>1.e-10:
-        print(zs, files[i].split("/")[1].split('_')[0], "%e"%pvalue )
-    else:
-        print(zs, files[i].split("/")[1].split('_')[0], "<1e-10")
-
-plt.title(r"Offset compared with the local, z={0}".format(zs), fontsize = 25)
-plt.tick_params(labelsize=20)
-# plt.legend(prop={'size':20})
-if zs == 1.5:
[…]

### 2022-02-04 projects/2020_HSC_to_numerical_simulation/manuscript sub version/manuscript.tex
Almost ready to submit

%% Beginning of file 'sample631.tex'
%%
%% Modified 2021 March
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.31 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls and other external packages such as
%% latexsym, graphicx, amssymb, longtable, and epsf.  Note that as of 
%% Oct 2020, APS now uses revtex4.2e for its journals but remember that 
%% AASTeX v6+ still uses v4.1. All of these external packages should 
%% already be present in the modern TeX distributions but not always.
%% For example, revtex4.1 seems to be missing in the linux version of
%% TexLive 2020. One should be able to get all packages from www.ctan.org.
%% In particular, revtex v4.1 can be found at 
%% https://www.ctan.org/pkg/revtex4-1.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%% using aastex version 6.3
%\documentclass[linenumbers]{aastex631}
\documentclass[twocolumn]{aastex631}

\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf TODO}: #1]}}
\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
\newcommand{\jshi}[1]{\textcolor{orange}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\yo}[1]{\textcolor{purple}{[{\bf Yohan}: #1]}}
\newcommand{\red}[1]{\textcolor{purple}{#1}}

\def\smass{{$M_*$}}
\def\sersic{S\'ersic}
\def\halpha{${\rm H}\alpha$}
\def\hbeta{${\rm H}\beta$}
\def\mbh{$\mathcal M_{\rm BH}$}
\def\lcdm{$\Lambda$CDM}
\def\hst{{\it HST}}
\def\kms{km~s$^{\rm -1}$}

\newcommand{\aklant}[1]{\textcolor{blue}{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{Comparing simulations and observations of black hole - galaxy relations}
\shortauthors{Ding et al.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{./}{figures/}}
%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

%\title{Black Hole and Galaxy co-evolution at $0.2<z<1.7$ with extensive comparisons between observations and simulations}

\title{Concordance between observations and simulations in the evolution of the mass relation between supermassive black holes and their host galaxies}

\author[0000-0001-8917-2148]{Xuheng Ding}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}

\author[0000-0002-0000-6977]{John D.Silverman}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}

\author[0000-0002-8460-0390]{Tommaso Treu}
\affiliation{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}

\author[0000-0002-1605-915X]{Junyao Li}
\affiliation{CAS Key Laboratory for Research in Galaxies and Cosmology, Department of Astronomy, University of Science and Technology of China, Hefei 230026, China}
\affiliation{School of Astronomy and Space Science, University of Science and Technology of China, Hefei 230026, China}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}

\author[0000-0002-7080-2864]{Aklant K. Bhowmick}
\affiliation{Dept. of Physics, University of Florida, Gainesville, FL 32611, USA}

\author[0000-0002-4096-2680]{Nicola Menci}
\affiliation{INAF Osservatorio Astronomico di Roma, via Frascati 33, I-00078 Monteporzio, Italy}

\author[0000-0002-3216-1322]{Marta Volonteri}
\affiliation{Institut d'Astrophysique de Paris, Sorbonne Universit\'e, CNRS, UMR 7095, 98 bis bd Arago, 75014 Paris, France}

\author[0000-0002-2183-1087]{Laura Blecha}
\affiliation{Dept. of Physics, University of Florida, Gainesville, FL 32611, USA}

\author[0000-0002-6462-5734]{Tiziana Di Matteo}
\affiliation{McWilliams Center for Cosmology, Dept. of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}

\author[0000-0003-0225-6387]{Yohan Dubois}
\affiliation{Institut d'Astrophysique de Paris, Sorbonne Universit\'e, CNRS, UMR 7095, 98 bis bd Arago, 75014 Paris, France}

%\author[0000-0001-9879-4926]{Jingjing Shi}
%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies (\mbh -- \smass) at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model). The observed sample consist of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter. To make fair comparisons, we first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations. Over the full redshift range, our analysis demonstrates that all simulations predict a level of intrinsic scatter of the scaling relations comparable to the observations which appear to agree with the dispersion of the local relation. 
Regarding the mean scaling relation, Horizon-AGN and TNG are in closest agreement with the observational data at both low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties. 
%TNG100, TNG300 and Horizon-AGN can successfully predict the observed evolution of the offset of the \mbh\ (i.e., $\Delta$\mbh\ increasing from $z\sim$ 0.7 to $z\sim1.5$).
For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and thus closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow. The consistency in the dispersion with redshift in our analysis lends support to the importance of both quasar and radio mode feedback prescriptions in the simulations. 
%In conclusion, our results are consistent with the hypothesis that AGN feedback plays a role in a causal link between the BH and its host galaxy.
%Our observational results valid the simulation prediction that, at redshift up to $z\sim1.5$, the tight scaling relation has been established by the AGN feedback in which  quasar mode (thermal bursts) essentially dominates; while at low redshift ($z<1$), the radio mode (jet outflows) starts to dominate the feedback and maintains the tightness of the scaling relation till $z=0$. 
Finally, we investigate evolution as a function of stellar and black hole mass and argue that the most direct way to probe the co-evolution of galaxies and black holes is to increase the sensitivity, e.g. with JWST, thereby pushing to lower masses and minimizing possible biases arising from selection effects.
%Finally, we investigate the offsets across the range in stellar mass; some simulations show that observational effects may lend ambiguity on whether black holes and their host are co-evolving or not.

%, finding that, after observational effect, different intrinsic offset values at lower stellar mass could result in the consistent comparison with the observation, which highlight the importance of extend this comparison work to lower stellar mass ($<10^{10}M_{\odot}$).

\end{abstract}
\keywords{Galaxy evolution (594); Active galaxies (17); Active galactic nuclei (16)}

\section{Introduction} \label{sec:intro}

The close correlations between supermassive black holes and the properties of their host galaxies (e.g., stellar mass) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}. To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over cosmic time \citep[e.g.,][]{Tre++04,Peng2006a, Tre++07, Woo++08, Jahnke2009, Bennert11, Schramm2013, Park15, Mechtley2016, Ding2020, 2021arXiv210902751L}. While, an {\it observed} evolution has been found \blue{in many studies} in which the growth of BHs predates that of the host, \blue{other studies predict that BHs grow commensurately with galaxies}.
%equally as many studies claim a lack of evolution when considering the host total stellar mass  \aklant{\bf This sentence can be made more clear. Are you just saying the some studies predict BHs grow faster than galaxies, whereas other studies predict that BHs grow commensurately with galaxies?}. 
However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15}.

Various theoretical models have been proposed to explain the origin of the scaling relations. For example, AGN feedback is considered as one of the possible viable mechanisms. During this process, a fraction of the AGN energy is injected into its surrounding gas, which can then regulate the mass growth of the BH and its host. In this scenario, star formation is inhibited by the heating and unbinding of a significant amount of gas. Alternatively, the mass relations can be explained through an indirect connection in which AGN accretion and star formation are fed through a common gas supply~\citep{Cen2015, Menci2016}. Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}. However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ %\aklant{\bf{do you mean "compared to what is observed today"?}} 
\blue{compared to what is observed today}.

Numerical simulations provide an opportunity to further understand the connection between BHs and their host galaxies. For example, a comparison of scaling relations has been made using state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and observational measurements at  $0.3<z<1$ \citep[e.g., ][]{DeG++15}, which show a positive evolution (i.e., the mass growth of the BH growth predates that of its host). Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution, 
%\jshi{(Jingjing: the agreement is with the local relation, right? they all predict their own redshift evolution., Xuheng's reply. Yes, I have updated this information in the last sentence.)}
including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH simulations~\citep{Schaye2015}, Illustris moving-mesh simulation~\citep{Sijacki2015, 2014MNRAS.444.1518V, Li2019} and the SIMBA simulation~\citep{Thomas2019}. %\yo{I am not sure I understand the link between this sentence and the previous one: ~\cite{Habouzit2021} includes Horizon-AGN and TNG (not cited previously), and does not include Magneticum.}
\red{In particular, the \mbh-\smass\ relation using BH populations using six large-scale cosmological simulations (i.e, Illustris, TNG100, TNG300, Horizon-AGN, EAGLE, and SIMBA) has been compared with observations in the local universe in a recent study~\citep{Habouzit2021}.} However, these comparison works are limited by the observation data in terms of the sample size ($<$100) and redshift range \blue{(i.e., limited to the local universe)}.

For such comparisons using simulations, it is crucial to consider the systematic uncertainties and selection biases. A direct means to account for these is to apply the same effects and selection to the simulation products and make a forward comparison in the observational plane. In~\citet{Ding2020b}, a direct comparison has been performed using 32 X-ray-selected AGN at $1.2<z<1.7$ and a direct comparison with two state-of-the-art simulation efforts, including {\tt MassiveBlackII} (MBII) and a Semi-analytic Model \citep[SAM,][]{Menci2014, Menci2016}. The dispersion in the mass ratio between black hole mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) \blue{favoring} the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.

In this study, we extend our previous work \blue{by adding recent measurements of hundreds of SDSS quasars at $0.2<z<0.8$ based on wide and deep HSC imaging from the Strategic Subaru Program,} and comparing the observational measurements with that from simulations. Furthermore, we extend the simulated quasar populations by including MBII, SAM, Illustris, TNG100, TNG300 and Horizon-AGN. This paper is structured as follows. In Sections~\ref{sec:observations} and~\ref{sec:simulations}, we describe our observed and simulated samples. A direct comparison is performed and the result is presented in Section~\ref{sec:result}. The concluding remarks are presented in Section~\ref{sec:con}.

%\section{Comparison Sample: Observations and Simulations} \label{sec:sample}
%The correlations of \mbh-\smass\ between the observed data and the numerical simulations are compared in this work. 
%We introduce the comparison samples in this section, including the observational data and the numerical simulations.

\section{Observational data set}
\label{sec:observations}
The observed sample consists of 646 uniformly-selected SDSS quasars at $0.2<z<0.8$, imaged by Subaru/HSC \citep{Li2021a}, and 32 quasars at $1.2<z<1.7$ as imaged by~\hst~\citep[][hereafter D20]{Ding2020}. The latter are selected from three deep-survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008}. Further details of these two samples and their measurements are given below.

\subsection{SDSS/HSC sample}\label{sec:hsc}
A sample of $\sim$5000 type-1 SDSS quasars from the DR14 catalog~\citep{Paris2018} at $0.2<z<1$ has been imaged by the high-resolution Subaru Strategic Program (SSP) wide area survey~\citep{Aihara2019} using Hyper Suprime-Cam~\citep{Miyazaki2018}. With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been performed \citep[][hereafter L21a]{Li2021a} to obtain the flux and color of each quasar's host galaxy. The stare-of-the-art image modeling software {\tt lenstronomy} \citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task. This approach is first developed by~\citet{Ding2020} and used to decompose the near-infrared emission of the HST sample (see next section). Having measured the host light in each band, the stellar mass of host galaxy is derived using spectral energy distribution (SED) fitting with CIGALE~\citep{Boquien2019}. Simulation tests are also performed to verify the fidelity of the \smass\ measurements. The statistical measurement error on \smass\ is at the $\sim$0.2~dex level. The values of \mbh\ are determined by~\citet{Rakshit2020} which are estimated based on the \hbeta-based measurements using the virial method~\citep{Peterson2004, Vestergaard2006}. The typical error of \mbh\ are estimated to be 0.4 dex. We refer the reader to~\citet{Li2021a} in the Section~4.2 for more details.

To avoid any potential biases related to the selection of the quasars, \citet{2021arXiv210902751L} isolated 877 sources which are uniformly selected based on their PSF-magnitudes, color cuts using single-epoch SDSS photometry and the value of the measured \smass. Specifically, we use the {\it ugri} color-selected sample (228 sources) from SDSS I/II~\citep{Richards2002}, and the CORE sample from SDSS BOSS (408 sources) and eBOSS (241 sources) surveys~\citep{Ross2013, Myers2015} (hereafter the uniform sample). These samples are initially selected based on PSF-magnitude cuts of $15 < i < 19.1$ (for {\it ugri}), and $i > 17.8$ and $g, r < 22.0$ (for CORE). Furthermore, a limit on \smass\ is set to assure the detection of the host, especially since the rate and accuracy of detection is higher when \smass\ is increasing\blue{, resulting in a final sample of 646 quasars}. These selections will be adopted in an equivalent manner to the simulated samples to mitigate selection effects thus allowing the fair comparison.

\subsection{HST sample}

A sample of 32 HST-observed AGN systems across the redshift range $1.2<z<1.7$ are selected from three deep-survey fields (COSMOS, (E)-CDFS-S, and SXDS). HSC/WFC3 IR camera is used to obtain the high-resolution imaging data (HST program GO-15115, PI: John Silverman) with six position dither pattern and a total exposure time $\sim$2348~s. The filters F125W ($1.2<z<1.44$) and F140W ($1.44<z<1.7$) were employed, according to the redshift of each target to bracket the 4000~\AA~break.  The AGN images are analyzed and decomposed to infer the host galaxies fluxes using the approach developed by D20 based on {\tt lenstronomy}. The HST ACS/F814W imaging data for 21/32 of the AGNs is also used to infer the host color. The results show that stellar templates of 1 and 0.625~Gyr can match the sample color at $z<1.44$ and $z>1.44$, respectively (see Figure 5 in D20). These best-fit models are used to estimate the stellar masses of the host galaxies. \mbh\ is determined by \citet{Schulze2018} using near-infrared spectroscopic observations of the broad \halpha\ emission line with the recipe provided by~\citet{Vestergaard2006}, in a consistent manner to that adopted for HSC sample. We refer the reader to D20 for a more detailed description of the analysis.

The measurements of the \mbh-\smass\ relations for both the HST and HSC samples are obtained with a consistent approach. Thus, we expect the measurement errors of these two samples to be at a comparable level (i.e., $\Delta$\mbh$=0.4~$dex, $\Delta$\smass$=0.2~$dex). 
Indeed, the two samples are consistent with a lack of evolution in the mass ratio~\citep[see Figure 6 of][]{2021arXiv210902751L}, even though the sample selection is slightly different.

%\begin{deluxetable*}{ccccccc}
%%\tablenum{1}
%\tablecaption{Key characteristics of hydrodynamic simulations used in this study.\label{tab:sim_sum}}
%\tablewidth{0pt}
%\tablehead{
%%\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
%%  \cline{2-4}  \cline{5} \\
%\colhead{Simulation} & \colhead{box sizes} & particles &  \multicolumn{2}{c}{mass resolution ($M_{\odot}$)} & \colhead{feedback prescription} & \colhead{AGN fueling mechanism}  %& what else?
%\\
%\cline{4-5}
%&$(\mathrm{cMpc})^3$&& dark matter & baryonic matter && $\dot{M}_{BH}$
%}
%\startdata
%MBII & $142.7^3$ & $2\times1792^3$ & $1.57\times10^7$ & $3.14\times10^6$ &5\% & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ \\
%Illustris & $(106.5)^3$ & $2\times1820^3$ & $6.26\times10^6$ & $1.26\times10^6$ &5\%& $\alpha \dot{M}_{Bondi}$ \\
%TNG100 &$(111)^3$& $2\times1820^3$&$7.5\times10^6$ &$1.4\times10^6$& min[$2\times10^{-3}(\frac{M_{\rm BH}}{10^8M_{\odot}})^2$, 10\%] & \blue{$\dot{M}_{Bondi}$}\\
%TNG300 &$(302)^3$& $2\times2500^3$&$5.9\times10^7$&$1.1\times10^7$&
%min[$2\times10^{-3}(\frac{M_{\rm BH}}{10^8M_{\odot}})^2$, 10\%]& \blue{$\dot{M}_{Bondi}$} \\
%Horizon-AGN &$(142)^3$& $\sim2\times1024^3$ &$8\times10^7$&$2\times10^6$&1.5\% - 10\% & $\alpha\dot{M}_{Bondi}$ \\
%\enddata
%\tablecomments{%\aklant{\bf{Could you please specify the maximum accretion rate for all the simulations?}}
%\blue{For all simulations, the accretion rate on to BHs is capped at the Eddington accretion rate, expect MBII which has a mildly super-Eddington (i.e., two times Eddington rate).}
%\red{In the last column, $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$. $\alpha$ is the boost factor. For Illustris, $\alpha = 100$; for Horizon-AGN, $\alpha =$ max$((\rho/\rho_0)^2$, 1).}
%}
%%\tablecomments{This table }
%\end{deluxetable*}

\begin{deluxetable*}{lccccc}
%\tablenum{1}
\tablecaption{Key characteristics of hydrodynamic simulations used in this study.\label{tab:sim_sum}}
\tablewidth{0pt}
\tablehead{
%\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
%  \cline{2-4}  \cline{5} \\
\colhead{Simulation} & MBII & Illustris &  TNG100 & TNG300 & Horizon-AGN
%&$(\mathrm{cMpc})^3$&& dark matter & baryonic matter && $\dot{M}_{BH}$
}
\startdata
box sizes $(\mathrm{cMpc})^3$  & $142.7^3$ & $(106.5)^3$ & $(111)^3$ & $(302)^3$ & $(142)^3$ \\
particles  & $2\times1792^3$ & $2\times1820^3$ & $2\times1820^3$ & $2\times2500^3$ & $\sim2\times1024^3$ \\
\cline{1-6}
{\bf mass resolution} \\
 dark matter &$1.57\times10^7$ & $6.26\times10^6$ & $7.5\times10^6$ & $5.9\times10^7$ & $8\times10^7$ \\
 baryonic matter &$3.14\times10^6$ & $1.26\times10^6$ & $1.4\times10^6$ & $1.1\times10^7$ & $2\times10^6$ \\
\cline{1-6}
{\bf AGN feedback} & (feedback efficiency $\times\epsilon_r$) \\
High acc. mode & 0.05 $\times$ 0.1 & 0.05 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.15 $\times$ 0.1 \\
Low acc. mode  & -- & 0.35 $\times$ 0.2 & $\leq0.2 \times$ 0.2 & $\leq0.2 \times$ 0.2 & 1 $\times$ 0.1 \\
Transitions btw. modes & -- & 0.05 & \multicolumn{2}{c}{min[$2\times10^{-3}(\frac{M_{\rm BH}}{10^8M_{\odot}})^2$, 10\%]} & 0.01 \\
\cline{1-6}
AGN fueling mechanism   & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ & $\alpha \dot{M}_{Bondi}$ & \blue{$\dot{M}_{Bondi}$}&\blue{$\dot{M}_{Bondi}$} & $\alpha\dot{M}_{Bondi}$ \\
maximum accretion rate & 2 $\times$Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate\\
\enddata
\tablecomments{%\aklant{\bf{Could you please specify the maximum accretion rate for all the simulations?}}
%\blue{For all simulations, the accretion rate on to BHs is capped at the Eddington accretion rate, expect MBII which has a mildly super-Eddington (i.e., two times Eddington rate).}
\red{In the penultimate row, $\alpha$ is the boost factor. For Illustris, $\alpha = 100$; for Horizon-AGN, $\alpha =$ max$[(\rho/\rho_0)^2, 1]$. $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$.}
}
%\tablecomments{This table }
\end{deluxetable*}

\section{Simulations \blue{and comparison strategy}}
\label{sec:simulations}
We introduce the simulation samples that are adopted in this section. All the simulation are based on the larger-scale cosmological simulations, except the Semianalytic Model (SAM) simulation \blue{(see Section~\ref{subsec:SAM})}. In Table~\ref{tab:sim_sum}, we summarized the key elements for each hydrodynamic simulation being considered.
%\todo{Maybe we can also summarize the importance of AGN feedback somewhere here?}

\subsection{{\tt MassiveBlackII} (MBII)}\label{subsec:MBII}
MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of %$100~\mathrm{cMpc/h}$
\red{$(142.7~\mathrm{cMpc})^3$}
and $2\times1792^3$ particles. The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}. 
%\yo{if the values of the cosmological parameters are given for MBII maybe this should also be given for all the other simulations?}
The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}.
%, i.e., $\Omega_0=0.275$, $\Omega_l=0.725$, $\Omega_b=0.046$, $\sigma_8=0.816$, $h = 0.701$, $n_s=0.968$.
%\yo{Masses are given here in $M_\odot/h$, while in some other places this is given in $M_\odot$. The same for box lengths.}
For dark matter and gas, the mass resolutions are %$1.1\times 10^7~M_{\odot}/h$ and $2.2\times 10^6~M_{\odot}/h$
\red{$1.57\times 10^7~M_{\odot}$ and $3.14\times 10^6~M_{\odot}$}
, respectively. The simulation includes a full modeling of gravity plus gas hydrodynamics, with a wide range of subgrid recipes to model the star formation~\citep{2003MNRAS.339..289S}, BH growth, and the feedback process~\citep{2005Natur.433..604D}. Halos were identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}. Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}.

To model supermassive black holes, a BH seed with mass $5\times 10^{5}~M_{\odot}/h$ are inserted into halos of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$. Once seeded, BH growth via gas accretion is assigned at a rate of $\dot{M}_{BH}={4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the interstellar medium (ISM) gas at cold phase; $v_{BH}$ is the relative velocity between the BH and its surrounding gas. Note that unlike several previous works, the accretion rate in MBII adopt the prescription in~\citet{Pelupessy2007} which does not include any artificial boost factor. The accreted gas is released as radiation at a radiative efficiency of 10\%. A fraction of 5\% of the radiated energy \aklant{thermally} couples to the surrounding gas as black hole (or AGN) feedback~\citep{2005Natur.433..604D}. A mildly super-Eddington (two times Eddington rate) is allowed. Due to resolution limitations, BH dynamics cannot be self-consistently modeled in the simulations. Two BHs are considered to be merged when their separation distance is below the simulation spatial resolution (i.e., the SPH smoothing length) and their relative speeds are lower than the local sound speed of the medium.

%\ding{The galaxy photometry information is not used in this work (we only compare stellar mass this time). To avoid any confusing or misunderstanding, I remove the simulation SED information in Section 3.1, 3.2 and 3.3.}
%For the galaxy photometry, the initial SEDs of the BH host galaxies were determined by combining all the contributions from their constituent star particles. The stellar SEDs were derived using the PEGASE-2~\citep{1999astro.ph.12179F} stellar population synthesis code with a Salpeter IMF. Finally, the galaxy SEDs are  cooperated with the desired filter response to obtain the broadband photometry (e.g., SDSS $r$-band magnitude).

As a common practice, the stellar mass is obtained by using a 3D spherical aperture of 30~kpc to represent the observed stellar mass. \blue{We adopt this definition of stellar masses for all simulations described in the following sections.} Using this definition, \citet{Pillepich2018} has shown that the corresponding stellar mass function is consistent with the observational measure. Even more, the stellar mass using this 3D aperture can achieve good agreement to those measured within the Petrosian radii in observational studies~\citep{Schaye2015}. For further details of MBII simulation, we refer the reader to~\citet{Khandai2015}.

\subsection{Illustris}
The Illustris Project is another large scale hydrodynamics simulation, introduced in~\citet{2014MNRAS.444.1518V, 2014Natur.509..177V}. The simulation consist of a volume of (106.5 cMpc)$^3$~(slightly smaller than MassiveBlack II), 
%\yo{Here the box size is given in cMpc and in the table in cMpc/$h$ with the same numerical value.}
and was run with the moving Voronoi mesh code {\tt Arepo}~\citep{2010MNRAS.401..791S} with a base cosmology adopted from WMAP9 results~\citep{2013ApJS..208...19H}.
%\aklant{\bf{I think it'll be good to explicitly state all cosmological parameters for the simulations and SAMs}}. 
Besides gravity and gas hydrodynamics, the simulation calculates the astrophysical processes ~\citep{2013MNRAS.436.3031V, 2014MNRAS.438.1985T} that includes \aklant{gas cooling and star formation~(with a density threshold of 0.13 cm$^{-3}$, \citealt{2003MNRAS.339..289S})}, stellar evolution and chemical enrichment, kinetic stellar feedback by SNe activity, BH growth~(accretion and merging), and AGN feedback.

\aklant{BHs are seeded with an initial mass of $1 \times 10^5~M_{\odot}/h$ when a halo exceeds a mass of $5 \times 10^{10}~M_{\odot}/h$. BHs then grow via accretion described by the Eddington limited Bondi-Hoyle-Lyttleton formalism ($\alpha4\pi G^2M_{BH}^2 \rho/c_s^3$), as well as mergers with other BHs. The boost factor $\alpha=100$ is introduced to account for the unresolved multiphase ISM~\citep{Springel2005, 2009MNRAS.398...53B}, which is otherwise expected to underestimate the density around the BHs. Lastly, accreting black holes radiate with a bolometric luminosity given by $\epsilon_r \dot{M}_{BH}c^2$, where $\dot{M}_{BH}$ is the mass accretion rate and $\epsilon_r=0.2$ is the radiative efficiency.}

\aklant{The AGN feedback consists of three components, namely quasar-mode, radio-mode and radiative feedback. In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy. For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at~(irregular) intervals between which the BH mass grows by a fixed fraction. The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{bh} c^2$ where $\delta M_{bh}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency. Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN.} \blue{As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy stellar mass, assuming a \cite{2003PASP..115..763C} IMF.}

%It is highlighted in ~\citet{2014MNRAS.444.1518V} that the AGN feedback is the key process in quenching massive galaxy which is crucial to reproduce a tight stellar mass and BH mass relation.

%\aklant{Finally, galaxy photometry was computed similar to that \texttt{MassiveBlackII}, but with SEDs derived using templates from \texttt{STARBURST99 (SB99)} catalogs~\citep{2010ApJS..189..309L} assuming a \cite{2003PASP..115..763C} IMF.}

\subsection{IllustrisTNG}
{\it The Next Generation Illustris Simulations} (IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018} are 
%\yo{I am not sure why ``ambitious''}
%an ambitious 
an suite of \aklant{magneto}hydrodynamical simulations of galaxy formation in large cosmological volumes. It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modeling, and 3) addressing the identified shortcomings of the previous generation simulations.

The TNG100 and TNG300 have a volume of (100~cMpc)$^3$ and (300~cMpc)$^3$, respectively. The adopted cosmological parameters are updates by the Planck result~\citep{2016A&A...594A..13P}
% \aklant{\bf{Here again, please list the cosmological parameters?}}.
\aklant{The gas cooling and star formation prescriptions are broadly similar to the Illustris model. However significant updates have been made to the stellar feedback model~(more details in \citealt{2018MNRAS.473.4077P}).
BH seeds with initial mass of $8 \times 10^5 M_{\odot}/h$ are placed in Dark matter halos with a mass exceeding $5 \times 10^{10} M_{\odot}/h$. Notably, the seed mass is one order of magnitude higher than in the Illustris simulation.} The BH accretion also follows the Bondi-Hoyle-Lyttleton formalism, but without any boost factor~(unlike Illustris). Accreting black holes release energy with a radiative efficiency of 0.2~(same as Illustris). The \aklant{inclusion} of the magnetic fields can affect the relationship between the BHs and their host galaxies properties; the \mbh-\smass\ mean relation is higher with magnetic fields~\citep{2018MNRAS.473.4077P}. %~\aklant{\bf{Aklant: Hmm I did not know this. Do they talk about what exactly causes this impact? Xuheng's reply: I adopt this sentence form the reference and Pillepich et al. It is mentioned in \citet{2018MNRAS.473.4077P} (in the texts after Figure 8) in the TNG model they modify the Bondi-Hoyle-Lyttleton formula for the gas accretion on to the BH in the presence of magnetic fields.}} %\sout{The TNG simulation also employs a kernel-weighted accretion rate over about 256 neighboring cells.} \sout{Thus, the TNG BH can build up correlation with the gas properties in the galaxy central region.}

\aklant{The AGN feedback occurs in thermal, radio, and radiative modes. For high accretion rates, the feedback implementation is the same as Illustris i.e., thermal energy is injected in the surroundings of the accreting BHs. However, at low accretion rates, the feedback implementation is substantially different from Illustris. Instead of releasing hot bubbles, this feedback mode in TNG is purely kinetic. In particular, there is a directional injection of momentum along a randomly chosen direction~\citep{2017MNRAS.465.3291W, 2018MNRAS.479.4056W} at irregular intervals.} The transition between the two feedback modes is also different from Illustris, and is set by the minimum value of 0.1 and $2 \times 10 ^{-3} \times (M_{BH} / 10^8~M_{\odot})$. \aklant{Additionally, the radiative feedback implemented in Illustris~(summarized in the previous section) is also present in TNG.} Lastly, \blue{the galaxy stellar mass} in Illustris-TNG is \blue{obtained} in a similar manner to that of Illustris.

\subsection{Horizon-AGN}\label{subsec:Horizon}

\blue{The simulation Horizon-AGN~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D} has a volume of 142 cMpc$^3$ and was generated using the adaptive mesh refinement code {\tt Ramses}~\citep{2002A&A...385..337T} with a $\Lambda$CDM model based on WMAP7~\citep{2011ApJS..192...18K} cosmological results. The dark matter particle mass is $8\times 10^7 M_{\odot}$. The stellar particle mass is $2\times 10^6 M_{\odot}$ and the MBH seed mass is $10^5 M_{\odot}$. Adaptive mesh refinement is permitted down to $\Delta x=1$~kpc, and, if the total mass in a cell becomes greater than 8 times the initial mass resolution, it is performed in a quasi-Lagrangian manner. Collisionless particles (dark matter and star particles) are evolved using a particle-mesh solver with a cloud-in-cell interpolation. }

\blue{The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation with a constant star formation efficiency $\epsilon_*=0.02$, which occurs in regions where the gas number density exceeds the star formation threshold $n_0 = 0.1\,\rm H\, cm^{-3}$. A Salpeter IMF is assumed. Stellar feedback is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources. }

\blue{Differing from simulations presented above, Horizon-AGN does not use a fixed threshold in the dark matter halo mass to seed BHs.  BHs are seeded with a mass of $10^5 M_\odot$ in cells, with gas density above $n_0$ and stellar velocity dispersion larger than $100 \,\rm km\,s^{-1}$. An exclusion radius is imposed so that no BH seed is formed at less than 50 ckpc from an existing BH. After $z = 1.5$, new BHs are prevented from forming. At these subsequent times, all the progenitors of the \smass$>10^{10} M_{\odot}$ galaxies at $z = 0$ should be formed and seeded with BHs~\citep{2016MNRAS.460.2979V}.  BH accretion is computed using the Bondi-Hoyle-Lyttleton formalism with a boost factor $\alpha = (\rho/\rho_0)^2$ when the density $\rho$ is higher than the resolution-dependent threshold $\rho_0$. Otherwise, the boost factor is fixed as unity~\citep{2009MNRAS.398...53B}.}

\blue{Horizon-AGN includes two modes of AGN feedback. In the quasar mode ($f_{\rm Edd}>0.01$), thermal energy is isotropically released within a sphere of radius a few resolution elements. The energy deposition rate is $\dot{E}_{\rm AGN} = 0.015 \dot{M}_{\rm BH} c^2$. In the radio mode, energy is injected into a bipolar  outflow  with  a  velocity  of  $10^4\,\rm km\,s^{-1}$, to  mimic the  formation  of  a  jet.  The  energy  rate  in  this  mode is $\dot{E}_{\rm AGN} = 0.1 \dot{M}_{\rm BH} c^2$.  The  technical  details  of  BH  formation,  growth  and AGN  feedback  modeling  of  Horizon-AGN  can be found in~\citet{2012MNRAS.420.2662D}.}

\blue{We identify galaxies applying the AdaptaHOP structure finder \citep{Aubert+04,Tweed+09} to the star particle distribution.  Galaxies are identified using a local threshold of 178 times the average matter density, with the local density of individual particles calculated using the 20 nearest neighbours. Only galaxies with more than 50 particles are considered. The galaxy mass corresponds to the total stellar mass of a galaxy identified with this approach. The stellar mass function is shown in \cite{2017MNRAS.467.4739K} to be in good agreement with observations.}

%Horizon-AGN  employs  a  kinetic  SN  feedback,  including momentum, mechanical energy and metals from type~II, Type  Ia  SNe,  and  stellar  winds  (details  in  Kaviraj  et  al.2017).  The  feedback  is  modeled  as  kinetic  release  of  energy on timescale below 50 Myr, and a thermal energy after 50 Myr. The feedback is also pulsed, meaning that energy is accumulated until sufficient to propagate the blast wave to  at  least  two  cells.  The  energy  released  depends  on  theSSP modeled assumed and the metallicity of the gas, and is aboute SN $\sim10^{49}$ erg/$M_{\odot}$.

\begin{figure}
\centering
\includegraphics[height=0.35\textwidth]{OpeningAngle.pdf}
\caption{\label{fig:SAM} 
Total gas content of galaxies as a function of AGN bolometric luminosity and jet opening angle in a new AGN feedback model incorporated into the SAM simulation.
}
\end{figure}

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[trim = 0mm 0mm 65mm 10mm, clip, height=0.45\textwidth]{HSC_selection_MBII.png}}
{\includegraphics[trim = 0mm 0mm 20mm 10mm, clip,height=0.45\textwidth]{HST_selection_MBII.png}}
\end{tabular}
%\caption{\label{fig:selection}Demonstration of the impact of AGN selection using MBII. {\it left}: Correlation between \mbh\ and %$L_{\rm bol}$ of the simulated HSC sample is used to set the selection window for the simulated sample. This region roughly bracket %the type-1 AGN sample. The light green background cloud shows the simulated number density distribution in this parameter space %which includes a random level of uncertainty to mimic observational measurement errors. {\it right}: Similar to the top plane -- %equivalent selection window adopted for the HST-observed and MBII simulated samples.
%}
\caption{\label{fig:selection}Demonstration of AGN selection using MBII. {\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles). A matched HSC sample is shown by the orange data points. The light green background cloud shows the {\it intrinsic} simulated number density in this parameter space. %which includes a random level of uncertainty to mimic observational measurement errors.
{\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample. For visual comparison between the HSC and HST selection, we show the region of the HST selection window in the left panel as dashed lines. 
}
\end{figure*}

\subsection{Semi-analytic Model (SAM)}\label{subsec:SAM}
We highlight the main points of the simulation with respect to our study; for more detail, a full description of the SAM can be found in~\citet{Menci2016} which is based on an earlier semi-analytic model introduced in~\citet{Menci2014}. \blue{The specific version adopted here differs from the one presented in the above papers since it implements a new, detailed description of AGN feedback, as discussed in detail below}.

For dark matter halos that merge with a larger halo, the impact of dynamical friction is assessed to define whether the halo will survive as a satellite or sink to the center of the dominant galaxy which increases its mass. The binary interactions (fly-bys and mergers), among satellite sub-halos, are  also described by the model. In each halo, we compute the fraction of gas which cools because of the atomic processes and settles into a disk~\citep{Mo1998}. The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr, 
%(CHECK THIS-JDS)\ding{It's mentioned in Menci 2016 section 2.} 
according to BH feeding; (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion). The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation which returns a fraction of the disk gas into a hot phase. A Salpeter IMF is adopted in the SAM simulation. \blue{A $\Lambda$CDM power spectrum of perturbations with a total matter density parameter $\Omega_0=0.3$, a baryon density parameter 
$\Omega_b=0.04$, a dark energy density parameter $\Omega_\Lambda=0.7$, and a Hubble constant $h$=0.7 is adopted. }

{We assume BH seed $M_{seed}=100\,M_{\odot}$~\citep{Madau2001}  to be initially present in all galaxy progenitors at the initial redshift $z=15$. This constitutes an approximate way of rendering the effect of the collapse of PopIII stars. However, the detailed value of $M_{seed}$ has a negligible impact on the final BH masses as long as they remain in the range $M_{seed}=50-500\,M_{\odot}$.
}

The BH accretion is based on both interaction-driven and disk instability feeding modes.
%\newline(1)~{\it triggered by interactions.} The interaction rate $\tau_r^{-1}=n_T\,\Sigma (r_t,v_c,V)\,V_{rel} (V)$ for galaxies with relative velocity $V_{rel}$ and number density $n_T$ in a common DM halo determines the probability for encounters, either fly-by or merging, through the corresponding cross sections $\Sigma$ given in~\citet{Menci2014}. The fraction of gas destabilized in each interaction corresponds to the loss $\Delta j$ of orbital angular momentum $j$, and depends on the mass ratio of the merging partners $M'/M$ and on the impact factor $b$.
%\newline(2)~{\it induced by disc instabilities.} We assume these to arise  in  galaxies with disc mass exceeding~\citep{Efstathiou1982} $M_{crit} =  {v_{max}^2 R_{d}/ G \epsilon}$ with $\epsilon=0.75$, where $v_{max}$ is the maximum circular velocity associated to each halo ~\citep{Mo1998}.  Such a criterion strongly suppresses the probability for disc instabilities to occur not only in massive, gas-poor galaxies, but also in dwarf galaxies characterized by small values of the gas-to-DM mass ratios. The instabilities induce loss of angular momentum resulting into strong inflows that we compute following the description in~\citet{Hopkins2011}, recast and extended as in~\citet{Menci2014}. 
%\todo{This part should be updated for the new SAM version? No, please leave as it is}
\blue{The SAM adopted here implements a new and improved  model for the AGN feedback with respect to the previous versions~\citep{Menci2008}. In both versions, the basic assumption is that fast winds with velocity up to $10^{-1}c$ observed in the central regions of AGNs~\citep{Chartas2002, Pounds2003}  result in  supersonic outflows that compress the gas into a blast wave terminated by a leading shock front. This  moves outward with a lower but still supersonic speed, and sweeps out the surrounding medium. However, while in the earlier version of the SAM~\citep{Menci2016} the blast wave is assumed to expand into an isotropically distributed medium, in the new description of AGN feedback~\citep{Menci2019} the full two-dimensional structure of the gas disc and of the expanding blast wave is followed in detail. The main physical difference is that in the new model the large density of gas along the plane of the disc causes the blast wave expansion to stall in such a direction, while it expands with large velocities in the vertical direction. The resulting strong dependence of the total (integrated over directions) outflow rate on the AGN luminosity $L_{AGN}$ and on the gas content of the galaxy $M_{gas}$ is shown in Figure~\ref{fig:SAM}. Such a new AGN feedback model has been tested in detail against a state-of-the-art compilation of observed outflows in 19 galaxies with different measured gas and dynamical masses~\citep{Fiore2017},
%(Fiore et al. 2019)\ding{Hi Nicola, I can't find the reference Fiore et al. 2019, I guess you mean~\citep{Fiore2017}, right? I will update the reference before submit. Let me know if I am wrong.}
allowing for a detailed, one-by-one comparison with the model predictions. Such a new, well tested AGN feedback model  allowed us to derive, for each simulated galaxy in the SAM,  the outflow expansion and the mass outflow rates in different directions with respect to the plane of the disc.}

\begin{figure*}
\centering
\includegraphics[trim = 50mm 70mm 40mm 90mm, clip,height=1.1\textwidth]{MM_sum.png}
\caption{\label{fig:comparsion} 
Black hole mass versus stellar mass for both the observational (small orange circles) and simulated (small colored circles) samples. Each row pertains to a particular simulation as labelled. The panels, from left to right, show different redshift bins. The black line in each panel indicates the local relation adopted by~\citet{Ding2020}. The background cloud (in green and yellow) shows the intrinsic simulation number density before injecting random noise and applying selection effects. Only TNG100 is presented here since TNG300 presents very similar results.
}
\end{figure*}

\subsection{Application of observational measurement error and selection effects}

To make direct comparisons with observations, we add measurement errors and apply the equivalent selection to the simulated samples. We first inject random noise to the simulated catalog to mimic the scatter caused by measurement error. As mentioned above, \smass\ and \mbh\ for HSC and HST samples are measured with a similar approach; thus their uncertainty levels are expected to be equivalent. 
We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = 0.17~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.

We then apply restrictions on the noise-injected simulation to mimic selection effects as present in the observational data. Since the HSC and HST samples have their own selection function, we apply different selection criteria to the simulation as follows:
%\begin{itemize}

 HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should match the relationship between \mbh-$L_{\rm bol}$ as seen in the HSC sample. We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it top}). (2) The $i$-band magnitude of the AGN are bright (see Section~\ref{sec:hsc}). The specific selection is made as follows: for systems at $z<0.5$ and $z>0.5$, the AGN $i$-band magnitude is required to be brighter than 20.5 mag and 22.0 mag, respectively. Since the simulations do not provide the observed AGN magnitude, we adopt a simulated rest-frame magnitude or L$_{\rm 5100}$ and assume the quasar continuum as a single power-law with an index of $\alpha_\nu=-0.44$~\citep{2001AJ....122..549V} to calculate the observed $i$-band magnitude.
 3)~Following the HSC selection, we require the \smass\ value to be above a certain level (according to their redshift) to assure an accurate measurement. Finally, the HSC sample is split into three redshift bins for making comparison which are $0.2<z<0.4$, $0.4<z<0.6$, and $0.6<z<0.8$.

HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example). Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., between [7.7, 8.6] $M_{\odot}$). The HST sample covers the higher redshift range $1.2<z<1.7$, which is considered as a single redshift bin to make the comparison with the simulations at $z=1.5$.
%\end{itemize}

\section{Results} \label{sec:result}
In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison. The local scaling relation adopted by D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is used as the fiducial relation to assess relative offsets and differences in dispersion. A different simulation is presented in each row and the redshift intervals increase from left to right. We note that TNG100 and TNG300 yield very similar comparison results, thus only TNG100 is presented in Figure~\ref{fig:comparsion}.

For each sample, the central offset and scatter of the scaling relation are estimated by calculating the mean and the standard deviation of the \mbh\ residuals for each system\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the y-axis in Figure~\ref{fig:comparsion}).  To aid in visualization of the differences among the various simulations compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}. Each panel presents a different redshift range. In addition, the values for the central offset and scatter in each case are given in Table~\ref{tab:sum} and shown as a function of redshift in Figure~\ref{fig:offsets_vz}.

\begin{figure*}
\centering
\begin{tabular}{c c c c}
\hspace*{-0.4cm} 
{\includegraphics[height=0.4\textwidth]{offset_dis_z03.pdf}}&
\hspace*{-0.4cm} 
{\includegraphics[height=0.4\textwidth]{offset_dis_z05.pdf}}&
\hspace*{-0.4cm} 
{\includegraphics[height=0.4\textwidth]{offset_dis_z07.pdf}}&
\hspace*{-0.4cm} 
{\includegraphics[height=0.4\textwidth]{offset_dis_z15.pdf}}\\
\end{tabular}
\caption{\label{fig:offsets} 
Histograms of the offset distributions for all simulation samples and observations. The mean value and the standard derivation of the histogram are summarized in Table~\ref{tab:sum}. The vertical dashed lines show the corresponding mean value for each distribution. The mean values for observed sample (i.e., yellow lines) are also show in each simulation plots.
For the MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$.
}
\end{figure*}

\begin{figure}
\centering
%\begin{tabular}{c c}
%{
\includegraphics[height=0.4\textwidth]{offset_summary_vz.pdf}%}&
%{\includegraphics[height=0.4\textwidth]{offset_int_summary_vz.pdf}}\\
%\end{tabular}
\caption{\label{fig:offsets_vz} 
%{\it left}: 
The {\it observed} evolution of $\Delta{\rm log}$\mbh\ as a function of redshift using both observation and simulation data. The black line shows the evolution by fitting the offset as a function of redshift. The predictions from the numerical simulations, given in Table~\ref{tab:sum}, are presented by different colored symbols. The grey horizontal band illustrates the level of dispersion for the local sample.
%\ding{The right panel can be confusing and hard to explain. Maybe we can remove?}
}
\end{figure}

\subsection{Dispersion}

Our results show that almost all simulations can produce scatter which is consistent with the observations across all redshifts examined (Figures~\ref{fig:comparsion}~and~\ref{fig:offsets}) --- for the simulated samples at $z<1$, this level of scatter is $\sim0.5$~dex, while at $z>1$, it is $\sim0.3$~dex. Note that the HST sample $z>1$ has a narrow selection window based on \mbh\ (see Figure~\ref{fig:selection}~bottom), causing the observed scatter to be smaller than that of the HSC sample at $z<1$. At all redshifts, we recognize that the observed scatter is dominated by measurement uncertainties in the data.

An understanding of how much of the scatter derives from random noise can help us to determine the {\it intrinsic} scatter in the scaling relation. To this end, we measure the scatter of the simulation sample without injecting random noise but adopting the same selection window for both $z<1$ and $z>1$ samples to infer the central offset and scatter. We find that the intrinsic scatter is at a level of $\sim0.15-0.2$ dex for both $z<1$ and $z>1$ (see Table~\ref{tab:sum_no_noise}). These levels are consistent with the {\it intrinsic} scatter as estimated using observation data alone~\citep{Ding2020, 2021arXiv210902751L}. Furthermore, the intrinsic scatter appears to be independent of redshift since the observations and simulations all follow the observed trend with redshift expected to be due to selection effects (Figure~\ref{fig:offsets_vz}). This suggests that the tight scaling relation may not be the result of a pure stochastic process, i.e., random mergers. However, the scatter is affected by sample selection, and thus these levels can only be taken as an approximation of the true intrinsic scatter.

\subsection{Global offsets}

We examine the offsets to understand whether the simulations deviate or not from the {\it observed} scaling relation with particular attention to changes with redshift. Considering the values given in Table~\ref{tab:sum} and shown in Figure~\ref{fig:offsets_vz}, over the lower redshift range $z<0.6$, Illustris and Horizon-AGN predict {\it observed} \mbh\ offsets consistent with the observation data (at a level of $\lesssim0.1$~dex). At higher redshift $0.6<z<1.5$, the simulations SAM, TNG100, TNG300 and Horizon-AGN follow the {\it observed} evolution. These results are consistent with the Kolmogorov-Smirnov (KS) test performed using the offset distributions between each simulated sample and the observed sample --- the p-values are given in Table~\ref{tab:pvalue} showing that Horizon-AGN and Illustris have a good statistical match to the scaling relation at $z<0.6$ (i.e., p-value $> 0.1$), while the TNG100, TNG300 and Horizon-AGN simulation do well at $z>0.6$. Overall, we find that the mass ratios between SMBHs and their host galaxies are generally consistent between observations and simulations with some subtle differences which are not at the level of concern for this present study.

\blue{
\subsection{Trends with stellar mass}
In Figure~\ref{fig:deltaMM}, we investigate how the offset values are correlated with stellar mass. Here, we focus on the sample at $z\sim0.7$. The other redshift bins at $z<1$, where there is a large observation sample from HSC, show similar trends. We include the intrinsic values from the simulations in the figures to address how the observational effects (i.e., random noise and selection) change the observed scaling relations and offsets. First, considering the observed quasar sample (same in each panel), there is a trend for which black holes have masses further offset from their stellar mass with decreasing stellar mass. This trend is not seen in any of the simulations after noise and selection effects have been applied. Given the level of uncertainties in the mean offsets of the observed sample, we do not try to interpret this trend any further in this study.}

\blue{
Interestingly, we notice that MBII and Illustris have black holes intrinsically under-massive relative to their galaxies at the lower masses that reach the local relation at higher masses. In contrast, TNG and Horizon-AGN have black holes slightly elevated from the local relation at most masses. These differences between simulations present two different scenarios, either one where the black holes come later or co-evolution with the two growing in tandem. Considering the former scenario, Illustris show the strongest trend with stellar mass. In fact, after noise and selection is applied, the simulated sample exhibits very small offsets which agree remarkably well with the observed data. {\bf TT edits: This result underscores the importance of taking into account errors and selection --- without accounting for those, one could erroneously interpret an apparent trend as evolution in the opposite sense as the true one.  The most direct way to circumvent these issues is to probe lower masses (\smass\  $<10^{10}M_{\odot}$) using a more sensitive instrument, such as JWST~\citep{Habouzit2022} across this redshift range \citep[see also][]{2011MNRAS.417.2085V}.}}
{\bf TT: the following sentences seem out of place} \ding{OK, let's remove the following red sentences can be removed}
\red{In the local universe, a delayed black hole growth scenario seems to be supported \citep{Reines2015}, %\yo{
which is understood to be the result of the quenching of BH growth by efficient feedback from SNe in low-mass galaxies~\citep[e.g.][]{dubois_snreg_2015,habouzit_blossom_2017,bower_dark_2017,angles_black_2017}.}

%the intrinsic distribution actually shows an opposite trend in which the host galaxy is more massive at low mass end. While the TNG100 and Horizon-AGN also present good comparisons in the {\it observed} plane, they predict the different intrinsic trend unlike Illustris. Yet, limited by the stellar mass range of our observed data, our comparison result could not rule out any simulation at this moment. To this end, extending the study to lower mass ($<10^{10}M_{\odot}$) using more sensitive instrument, such as JWST, will be the key~\citep{Habouzit2022}.

%For instance, if overlook the observational effect, the HSC observational measurement show that, when host stellar mass is low, the SMBH trend to be more massive taking local scaling relation as reference. This could mislead to a wrong conclusion that SMBH grow up first and the host galaxy catch up later to match up with the scaling relation in local universe.

%In fact, taking the Illustris as example who well predicts the {\it observed} scaling relation to the HSC observation,

\begin{figure*}
\centering
\begin{tabular}{c c}
\hspace*{-0.5cm} 
{\includegraphics[trim = 0mm 0mm 0mm 0mm, clip,
height=0.4\textwidth]{DeltaMM_MBII_zs_06.png}}&
\hspace*{-0.3cm} 
{\includegraphics[trim = 36mm 0mm 0mm 0mm, clip,
height=0.4\textwidth]{DeltaMM_Illustris_zs_07.png}}\\
\hspace*{-0.5cm} 
{\includegraphics[trim = 0mm 0mm 0mm 0mm, clip,
height=0.4\textwidth]{DeltaMM_TNG100_zs_07.png}}&
\hspace*{-0.3cm} 
{\includegraphics[trim = 36mm 0mm 0mm 0mm, clip,
height=0.4\textwidth]{DeltaMM_Horizon_zs_07.png}}\\
\end{tabular}
\caption{\label{fig:deltaMM} Comparison of the offset of the \mbh\ (to the local relation) as a function of stellar mass from observation data and the simulations at $z\sim0.7$. In each stellar mass bin, we give the mean and standard derivation of the offset values. The histograms on the right indicate the offset distribution with lines marking the mean offsets for observation and simulation. The green color distributions show the intrinsic simulated sample without random noise and selection applied.
%Since the selection of HST sample has a hard cut on the \mbh\ values, an {\it observed} trend of offset value as a function of stellar mass appears; this trend doesn't appear on the intrinsic ones. 
%{\bf[MV: If I understand correctly, mean and standard deviation of the offset values are shown only for the simulation once you have included measurement errors and selection effects. If this is the case, can you add them also for the intrinsic simulated sample?]}
}
\end{figure*}

\section{Conclusions} \label{sec:con}
%A brief introduce of the result. Scatter, central, which is best...
We compared the observed scaling relation \mbh-\smass\ with the predictions from numerical simulations. The observation data are composed of 626 quasars at $0.2 < z < 0.8$ imaged by HSC and 32 X-ray-selected quasars at $1.2 < z < 1.7$ imaged by HST. The simulations include a semi-analytic model (SAM) and five hydrodynamic simulations, i.e., MBII, Illustris, TNG100, TNG300 and Horizon-AGN. We carried out the comparisons in the observed pararameter space to account for uncertainties and selection effects. To achieve this, we first injected random errors with the same observational uncertainty to the simulation, and then adopted the same selection condition to the simulation data (see Figure~\ref{fig:selection}). Finally, we adopted the scaling relation from the local universe as our reference and performed comparisons using the scatter of the measurements and their central offset to the local relation. Our main results are summarized as follows:

\begin{enumerate}

\item{}The {\it observed} scatter predicted by the simulations is consistent with the observational measurements, i.e., $\sim0.5$~dex at $z<1$ and $\sim0.3$~dex at $z>1$ (see Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}). This result indicates that the simulated and observed samples have consistent {\it intrinsic} scatter.

\item{}To understand how much the {\it observed} scatter is dominated by random observational error,
we re-run the estimation without injecting noise to the simulations. The obtained scatter for both $z<1$ and $z>1$ are at a similar level (i.e.,  $\sim$0.15$-$0.2 dex, see Table~\ref{tab:sum_no_noise}), indicating that observational errors dominate the scatter.

\item{} Regarding the mass ratios and offsets from the local relation ($\Delta$\mbh\ at a given \smass\ ), all simulations generally match the observations with some subtle, yet notable, differences. While Illustris and Horizon-AGN show good correspondence with observations at $z<0.6$, the comparisons at $z>0.6$ are better for SAM, TNG100, TNG300 and Horizon-AGN. From $z\sim0.7$ to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}. 
%\ding{In the simulation, is there any observational data that be used to give extra constrain on the recipe/assumption? Xuheng and John are surprised to see that all of them have very good scatter matches. Maybe we need provide some details on how the scaling relations in the simulations are calibrated. For example, why Illustris and TNG sample predict different center for the scaling relation. Horizon-AGN could predict well at both low and high z, maybe we can add some discussions.}
%{\bf[MV: This is very interesting. When comparing with BH-galaxy correlations at $z=0$ we noticed in \cite{2016MNRAS.460.2979V} that the simulations showed less scatter wrt the observations, and we thought that this meant that some stochastic processes on small scale were not captured. Now I wonder whether instead the lower scatter in the simulated results was because we did not apply any observational measurement error or selection effects to the simulation. You note in the Conclusions that this may not be important, but also that, indeed, no strong efforts have been made to include such effects.]}
\end{enumerate}

The absolute value of stellar masses in both observation and theory have significant uncertainty (up to factor of two), which depends on the assumption of initial mass function, and possibly on the implementation of star formation in the models. In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematic effect. Thus, in this work, we first consider the scatter as a diagnostic criteria to see whether some simulations match the data better than others. Taking (1) and (2), our results suggest that the tightness of the scaling relations have been formed since redshift 1.7, which is in contrast with the scenario of the central limit theorem~\citep{Peng2007, Jahnke2011, Hirschmann2010} that the scaling relation is a consequence of a stochastic cloud in the early universe with subsequent random mergers thereafter. In this stochastic scenario we expect the scatter of the scaling relations to increase towards higher redshift. In fact, the scatter level in the simulation without adding random noise is consistent with the {\it intrinsic} scatter estimations reported in~\citet{Ding2020, 2021arXiv210902751L} (i.e., $\lesssim0.35$~dex). This level is also not larger than the typical scatter of the local relations reported in the literature~\citep{Kormendy13, Gul++09, Reines2015}.

The simulations studied in this work have adopted completely different numerical techniques. However, all of them can provide good agreement with the observed dispersion in the scaling relation. In fact, the tightness of the scaling relation is stem from the same physics assumed in these simulations (i.e., AGN feedback). Thus, the consistency of the scatter between simulation and observations is consistent with the hypothesis that the AGN feedback as a causal link between SMBHs and their hosts plays a key role in establishing the scaling relation.

%So far, a control experiment has not been performed yet in which one numerical model provide the 
\blue{
%hydrodynamical} simulation altering the AGN feedback prescription, while fixing all other conditions.
We can gain more insight into the role of feedback by looking at the SAM model, for which multiple feedback models have been implemented. \citet{Ding2020b} compared the scaling relations obtained with the same HST sample and the SAM simulation but with a different, isotropic, AGN feedback model, and found a larger scatter ($\sim0.7$~dex) with respect to the present SAM version ($\sim0.36$~dex). We ascribed the change to the following reasons: in the new 2D model for feedback, the wave expansions stalls along the direction of the disc, and the radius where the expansion stops depends strongly on both the gas density of the disk and the AGN luminosity. 
This means that the opening angle (and hence the fraction of expelled gas) is larger when the gas density is small (because of the lower energy that has to be spent to push the gas outwards) and when the AGN luminosity is large (because of the larger energy available to push the blast wave outwards). These dependencies are summarized in Figure~\ref{fig:SAM}. 
Both quantities depend on the merging histories and are  related, since the AGN luminosity $L_{\rm AGN}$ depends on the available cold gas reservoir $M_{\rm gas}$.
The large efficiency of feedback in galaxies with particularly small $M_{\rm gas}$ (for given $L_{\rm AGN}$) or in those with particularly large $L_{\rm AGN}$
(for given $M_{\rm gas}$) inhibits the BH growth in all the host galaxies that are outliers with respect to the average relation between $M_{\rm gas}$ and $L_{\rm AGN}$. 
This results into a smaller scatter.}

\blue{
In theoretical models, AGN feedback is often assumed to consist of two distinct modes:
%In theory, it is a common knowledge that two different modes are responsible for AGN feedback: 
a quasar-heating mode where the SMBH accretion rates are comparable to the Eddington rate and a radio-jet mode occurring at low accretion rates (see e.g. Section~\ref{subsec:Horizon}). In high redshift universe, the cold material in early universe leads to the vigorous accretion to the SMBH which drives the high accretion rates, and thus the quasar mode dominates the feedback. At low redshift, the star formation and feedback ejection reduce the cold material leading to a lower accretion rate and a radio-mode-dominating feedback~\citep[e.g.][]{2012MNRAS.420.2662D,2016MNRAS.460.2979V,2018MNRAS.479.4056W}. Our comparison result shows that the level of intrinsic scatter in the scaling relation at redshifts up to 1.7 is consistent with the low redshift one (see Table~\ref{tab:sum_no_noise}), which reveals the fact that at high redshift the AGN feedback described by the quasar mode has already regulated the tight correlation between SMBH and its host galaxy. After that, the radio-jet mode starts to take control at low redshift by maintaining the tightness of the scaling relation till the level we observe today.
}

Our work highlights the importance of applying measurement uncertainty and the effect of selection to the simulated data in order to make direct comparisons with observations. Such comparisons have been made in the local universe~\citep[e.g.,][]{Habouzit2021} where the measurements are relatively robust and the selection function is broad thus it is less crucial to ensure consistency between observations and simulations. However, beyond $z>0.2$, the scatter and the central distribution of the scaling relations are dominated by measurement uncertainty and selection effects (see Figures~\ref{fig:comparsion} and~\ref{fig:deltaMM}) and a forward modeling in the observational plane becomes essential. For example, from trends seen with stellar mass in Illustris and MBII (Figure~\ref{fig:deltaMM}), selection effects may hamper our understanding of whether BHs and their hosts co-evolve or not.

Extending this study to even higher redshift (and lower mass galaxies, \smass\ $<10^{10}M_{\odot}$) will be very beneficial, probing closer to the epoch of formation of massive galaxies and SMBHs. The understanding of how and when the tight scaling relation emerged are crucial to test theoretical models \citep{Volonteri2021}. On the observational side, the James Webb Space Telescope will provide high-quality imaging data of AGNs at redshift up to $z\sim7$ (i.e., JWST cycle 1 program GO-1967 and GO-1727). These upcoming measurements will represent stringent tests on the proposed physical mechanisms for the initial formation of supermassive black holes and of their subsequent evolution with galaxies.

\begin{acknowledgments}
This work was supported by World Premier International Research Center Initiative (WPI), MEXT, Japan. 
The authors fully appreciate input from Jingjing Shi.

Based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555. These observations are associated with programs \#15115. Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555. 
JS is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
TT acknowledges support by the Packard Foundation through a Packard Research fellowship to TT. LB acknowledges support from NSF award AST-1909933 and Cottrell Scholar Award \#27553 from the Research Corporation for Science Advancement.

\end{acknowledgments}

\begin{deluxetable*}{lccccc}
%\tablenum{1}
\tablecaption{Summary of the central offsets and scatters\label{tab:sum}}
\tablewidth{0pt}
\tablehead{
\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
\cline{2-4} 
%  \cline{2-4}  \cline{5} \\
\colhead{} &  \colhead{$0.2<z<0.4$} & \colhead{$0.4<z<0.6$} & \colhead{$0.6<z<0.8$} & \colhead{$1.2<z<1.7$} & IMF
}
\startdata
Observation & (0.12, 0.51) & (0.20, 0.50)  & (0.21, 0.56)  & (0.43, 0.31) & \\
SAM & (0.73, 0.49) & (0.65, 0.46)  & (0.51, 0.45)  & (0.51, 0.36) & Salpeter \\
MBII & (-0.15, 0.48) & \multicolumn{2}{c}{(-0.16, 0.48) [$z=0.6$]}  & (0.14, 0.31) & Salpeter\\
Illustris & (0.01, 0.52) & (0.08, 0.53)  & (0.06, 0.54)  & (0.07, 0.32) &  Chabrier \\
TNG100 & (0.27, 0.48) & (0.24, 0.46)  & (0.24, 0.45)  & (0.38, 0.33) & Chabrier \\
TNG300 & (0.26, 0.48) & (0.20, 0.48)  & (0.17, 0.48)  & (0.41, 0.34) & Chabrier \\
Horizon-AGN & (0.16, 0.49) & (0.14, 0.47)  & (0.23, 0.47)  & (0.47, 0.35) & Salpeter\\
\enddata
\tablecomments{This table collects the comparison results of the \smass-\mbh\ correlations between different simulation at different redshift. The value shows the central position offset to the local relation and the scatters measured around the local relation after applying the offset. A positive offset means the \mbh\ value predicted by the simulation is higher than the local relationship measurement at fixed \smass\ value. The last column shows the corresponding IMF that adopted to the local anchor to make a fair comparison with the observation. Note that for the observational data, the relative differences between local and high-$z$ measurements are not affected by the IMF assumptions.
For the MBII sample, the simulation does not produce the sample at $z=0.5$ or $z=0.7$, but rather at $z=0.6$. We use Monte Carlo approach to infer the uncertainties of the values in the table, finding that the uncertainties are within $\pm 0.03$.
}
\end{deluxetable*}

\begin{deluxetable*}{lcccc}
%\tablenum{1}
\tablecaption{Summary of the central offsets and scatters without noise\label{tab:sum_no_noise}}
\tablewidth{0pt}
\tablehead{
\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
\cline{2-4} 
%  \cline{2-4}  \cline{5} \\
\colhead{} &  \colhead{$0.2<z<0.4$} & \colhead{$0.4<z<0.6$} & \colhead{$0.6<z<0.8$} & \colhead{$1.2<z<1.7$}
}
\startdata
SAM & (0.72, 0.20) & (0.64, 0.18) & (0.56, 0.16)  & (0.08, 0.18) \\
MBII & (-0.15, 0.21) & \multicolumn{2}{c}{(-0.15, 0.22) [$z=0.6$]}  & (0.08, 0.19)\\
Illustris & (0.03, 0.32) & (0.10, 0.36) & (0.08, 0.36)  & (0.04, 0.19) \\
TNG100 &  (0.27, 0.20) & (0.27, 0.15) & (0.26, 0.16)  & (0.36, 0.15) \\
TNG300 & (0.25, 0.21) & (0.19, 0.23) & (0.20, 0.22)  & (0.32, 0.16) \\
Horizon-AGN & (0.19, 0.26) & (0.18, 0.21) & (0.28, 0.20)  & (0.37, 0.13) \\
%Previous are ones not adding noise but same selection, belows are not add noise and not select
%SAM & (0.75, 0.26) & (0.74, 0.26) & (0.94, 0.26)  & (0.59, 0.24) \\
%MBII & (-0.24, 0.22) & \multicolumn{2}{c}{(-0.26, 0.22) [$z=0.6$]}  & (-0.29, 0.22)\\
%Illustris & (-0.78, 0.40) & (-0.73, 0.40) & (-0.69, 0.40)  & (-0.55, 0.36) \\
%TNG100 &  (0.33, 0.31) & (0.31, 0.32) & (0.29, 0.33)  & (0.22, 0.37) \\
%TNG300 & (0.42, 0.58) & (0.40, 0.57) & (0.39, 0.56)  & (0.35, 0.54) \\
%Horizon & (0.12, 0.30) & (0.13, 0.30) & (0.14, 0.28)  & (-0.00, 0.48) \\
\enddata
\tablecomments{Same as Table~\ref{tab:sum} but without inject noise to the simulation data. Note that same selection window is still adopted to infer the values.}
\end{deluxetable*}

\begin{deluxetable*}{lcccc}
%\tablenum{1}
\tablecaption{Summary of the p-value using KS test \label{tab:pvalue}}
\tablewidth{0pt}
\tablehead{
\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison} & \colhead{HST comparison} \\
\cline{2-4} 
%  \cline{2-4}  \cline{5} \\
\colhead{} &  \colhead{$z\sim0.3$} & \colhead{$z\sim0.5$} & \colhead{$z\sim0.7$} & \colhead{$z\sim1.5$}
}
%\decimalcolnumbers
\startdata
SAM &  3.119926e-09 & $<$1e-10  & $<$1e-10  & 7.456907e-03  \\
MBII & 4.228845e-02 & \multicolumn{2}{c}{$<$1e-10 [$z=0.6$]}  & 2.218653e-06  \\
Illustris & 2.306434e-01 & 6.144066e-02  & 9.963678e-03  & 2.330195e-07  \\
TNG100 & 1.207389e-02 & 2.530020e-01  & 3.756821e-01  & 4.708287e-01  \\
TNG300 & 1.817531e-02 & 9.192506e-01  & 1.208812e-01  & 2.118038e-01  \\
Horizon-AGN & 2.699897e-01 & 2.865927e-01  & 6.129553e-01  & 1.953735e-01  \\
\enddata
\tablecomments{These p-values are obtained by the KS test between the simulation and the observation.}
\end{deluxetable*}

\vspace{5mm}
%\facilities{HST, HSC}

%% Similar to \facility{}, there is the optional \software command to allow 
%% authors a place to specify which programs were used during the creation of 
%% the manuscript. Authors should list each code and include either a
%% citation or url to the code inside ()s when available.

%\software{astropy \citep{2013A&A...558A..33A,2018AJ....156..123A},  }

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc. The
%% Figure and Table counter will not reset.

%\appendix

%\section{Comparison of the observed mass function}\label{app:function}
%Our comparison also provides the opportunity to compare the {\it observed} mass distribution of the BH mass and the stellar mass. The histogram distribution of the {\it observed} \mbh\ and \smass\ are shown in Figure~\ref{fig:MB_fun} and Figure~\ref{fig:Mstar_fun}, respectively. All the simulations have good agreements to the observed mass function, in terms of the standard derivation. However, focus on the central point of the distribution, the TNG100 and TNG300 give the best prediction, indicating that their parent sample are most similar to the HSC sample. \todo{Xuheng will talk with Jingjing and add more discussion to this part.}

%\begin{figure*}
%\centering
%\begin{tabular}{c c}
%%\vspace*{-0.2cm} 
%{\includegraphics[height=0.35\textwidth]{MBH_dis_z03.pdf}}&
%%\hspace*{-0.4cm} 
%{\includegraphics[height=0.35\textwidth]{MBH_dis_z05.pdf}}\\
%%\hspace*{-0.4cm} 
%{\includegraphics[height=0.35\textwidth]{MBH_dis_z07.pdf}}&
%%\hspace*{-0.4cm} 
%{\includegraphics[height=0.35\textwidth]{MBH_dis_z15.pdf}}\\
%\end{tabular}
%\caption{\label{fig:MB_fun} 
%Illustration of the histogram of the observed \mbh\ function. For MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$. Note that for sample at $z\sim1.5$, the selection cut on \mbh\ is used in the simulation, thus the distribution is almost flat. \todo{update hist format as Figure 4}
%}
%\end{figure*} 
%
%\begin{figure*}
%\centering
%\begin{tabular}{c c}
%%\vspace*{-0.2cm} 
%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z03.pdf}}&
%%\hspace*{-0.4cm} 
%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z05.pdf}}\\
%%\hspace*{-0.4cm} 
%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z07.pdf}}&
%%\hspace*{-0.4cm} 
%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z15.pdf}}\\
%\end{tabular}
%\caption{\label{fig:Mstar_fun} 
%Illustration of the histogram of the observed MBH function. For MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$.
%}
%\end{figure*} 
\bibliography{reference}{}
\bibliographystyle{aasjournal}

%% This command is needed to show the entire author+affiliation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

\end{document}

% End of file `sample631.tex'.

### 2022-02-04 projects/2020_HSC_to_numerical_simulation/figs/MM_vz_32QSO+600HSC+simulation.py

@@ -388,8 +388,8 @@ for i in range(len(sims)):
     elif i == 1:
         zs = np.array([0.3, 0.6, 1.5])
     # line = plt.plot(np.log10(1+zs), sims[i][:,0], linestyle = '--', color =c[i],  linewidth=3,zorder=10)
-    plt.errorbar(np.log10(1+zs)+0.01/6*i, sims[i][:,0], sims[i][:,1], linestyle = ls, color =c[i],
-                  zorder = 50, linewidth = 2)
+    plt.errorbar(np.log10(1+zs)+0.015/6*i, sims[i][:,0], sims[i][:,1], linestyle = ls, color =c[i],
+                  zorder = 50, linewidth = 3)
     ty1=sims[i][:,0] + sims[i][:,1]
     ty2=sims[i][:,0] - sims[i][:,1]
     # zs[0] = zs[0]-0.1
@@ -415,7 +415,7 @@ plt.xlim([-0.01,0.5])
 plt.ylabel(r"$\Delta$logM$_{\rm BH}$ (vs M$_*$)",fontsize=45)
 plt.grid()
 plt.tick_params(labelsize=35)
-
+plt.tick_params(which='major', width=2, length=10, direction='in')
 ax2=ax.twiny()
 tticks=np.array([10**xl-1,0.5,1,1.5,2,10**xh-1])
 ax2.set_xticks([np.log(t+1) for t in tticks])  # for the entire scale

### 2022-02-06 projects/2020_HSC_to_numerical_simulation/manuscript sub version/manuscript.tex
Version before submission

@@
 
-%\title{Black Hole and Galaxy co-evolution at $0.2<z<1.7$ with extensive comparisons between observations and simulations}
-
 \title{Concordance between observations and simulations in the evolution of the mass relation between supermassive black holes and their host galaxies}
@@
 
-%\author[0000-0001-9879-4926]{Jingjing Shi}
-%\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
-
-%% Mark off the abstract in the ``abstract'' environment. 
 \begin{abstract}
@@
 Regarding the mean scaling relation, Horizon-AGN and TNG are in closest agreement with the observational data at both low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties.
-%TNG100, TNG300 and Horizon-AGN can successfully predict the observed evolution of the offset of the \mbh\ (i.e., $\Delta$\mbh\ increasing from $z\sim$ 0.7 to $z\sim1.5$).
 For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and thus closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow.
 The consistency in the dispersion with redshift in our analysis lends support to the importance of both quasar and radio mode feedback prescriptions in the simulations.
-%In conclusion, our results are consistent with the hypothesis that AGN feedback plays a role in a causal link between the BH and its host galaxy.
-%Our observational results valid the simulation prediction that, at redshift up to $z\sim1.5$, the tight scaling relation has been established by the AGN feedback in which  quasar mode (thermal bursts) essentially dominates; while at low redshift ($z<1$), the radio mode (jet outflows) starts to dominate the feedback and maintains the tightness of the scaling relation till $z=0$.
-Finally, we investigate evolution as a function of stellar and black hole mass and argue that the most direct way to probe the co-evolution of galaxies and black holes is to increase the sensitivity, e.g.
-with JWST, thereby pushing to lower masses and minimizing possible biases arising from selection effects.
-%Finally, we investigate the offsets across the range in stellar mass; some simulations show that observational effects may lend ambiguity on whether black holes and their host are co-evolving or not.
-
-%, finding that, after observational effect, different intrinsic offset values at lower stellar mass could result in the consistent comparison with the observation, which highlight the importance of extend this comparison work to lower stellar mass ($<10^{10}M_{\odot}$).
+Finally, we investigate evolution as a function of stellar and black hole mass, and argue that the most direct way to probe the co-evolution of galaxies and black holes is to increase the sensitivity, e.g., with JWST, thereby pushing to lower masses and minimizing possible biases arising from selection effects.
 
@@
 To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over cosmic time \citep[e.g.,][]{Tre++04,Peng2006a, Tre++07, Woo++08, Jahnke2009, Bennert11, Schramm2013, Park15, Mechtley2016, Ding2020, 2021arXiv210902751L}.
-While, an {\it observed} evolution has been found \blue{in many studies} in which the growth of BHs predates that of the host, \blue{other studies predict that BHs grow commensurately with galaxies}.
-%equally as many studies claim a lack of evolution when considering the host total stellar mass  \aklant{\bf This sentence can be made more clear.
-Are you just saying the some studies predict BHs grow faster than galaxies, whereas other studies predict that BHs grow commensurately with galaxies?}.
+While, an {\it observed} evolution has been found in many studies in which the growth of BHs predates that of the host, other studies predict that BHs grow commensurately with galaxies.
 However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15}.
@@
 Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
-However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ %\aklant{\bf{do you mean "compared to what is observed today"?}}
-\blue{compared to what is observed today}.
+However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ compared to what is observed today.
 
@@
 Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution,
-%\jshi{(Jingjing: the agreement is with the local relation, right? they all predict their own redshift evolution., Xuheng's reply. Yes, I have updated this information in the last sentence.)}
 including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH simulations~\citep{Schaye2015}, Illustris moving-mesh simulation~\citep{Sijacki2015, 2014MNRAS.444.1518V, Li2019} and the SIMBA simulation~\citep{Thomas2019}.
-%\yo{I am not sure I understand the link between this sentence and the previous one: ~\cite{Habouzit2021} includes Horizon-AGN and TNG (not cited previously), and does not include Magneticum.}
-\red{In particular, the \mbh-\smass\ relation using BH populations using six large-scale cosmological simulations (i.e, Illustris, TNG100, TNG300, Horizon-AGN, EAGLE, and SIMBA) has been compared with observations in the local universe in a recent study~\citep{Habouzit2021}.} However, these comparison works are limited by the observation data in terms of the sample size ($<$100) and redshift range \blue{(i.e., limited to the local universe)}.
+In particular, the \mbh-\smass\ relation using BH populations using six large-scale cosmological simulations (i.e, Illustris, TNG100, TNG300, Horizon-AGN, EAGLE, and SIMBA) has been compared with observations in the local universe in a recent study~\citep{Habouzit2021}.
+However, these comparison works are limited by the observation data in terms of the sample size ($<$100) and redshift range (i.e., limited to the local universe).
 
@@
 In~\citet{Ding2020b}, a direct comparison has been performed using 32 X-ray-selected AGN at $1.2<z<1.7$ and a direct comparison with two state-of-the-art simulation efforts, including {\tt MassiveBlackII} (MBII) and a Semi-analytic Model \citep[SAM,][]{Menci2014, Menci2016}.
-The dispersion in the mass ratio between black hole mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) \blue{favoring} the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.
+The dispersion in the mass ratio between black hole mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) favoring the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.
 
-In this study, we extend our previous work \blue{by adding recent measurements of hundreds of SDSS quasars at $0.2<z<0.8$ based on wide and deep HSC imaging from the Strategic Subaru Program,} and comparing the observational measurements with that from simulations.
+In this study, we extend our previous work by adding recent measurements of hundreds of SDSS quasars at $0.2<z<0.8$ based on wide and deep HSC imaging from the Strategic Subaru Program, and comparing the observational measurements with that from simulations.
 Furthermore, we extend the simulated quasar populations by including MBII, SAM, Illustris, TNG100, TNG300 and Horizon-AGN.
@@
 The concluding remarks are presented in Section~\ref{sec:con}.
-
-%\section{Comparison Sample: Observations and Simulations} \label{sec:sample}
-%The correlations of \mbh-\smass\ between the observed data and the numerical simulations are compared in this work. 
-%We introduce the comparison samples in this section, including the observational data and the numerical simulations.
 
@@
 These samples are initially selected based on PSF-magnitude cuts of $15 < i < 19.1$ (for {\it ugri}), and $i > 17.8$ and $g, r < 22.0$ (for CORE).
-Furthermore, a limit on \smass\ is set to assure the detection of the host, especially since the rate and accuracy of detection is higher when \smass\ is increasing\blue{, resulting in a final sample of 646 quasars}.
+Furthermore, a limit on \smass\ is set to assure the detection of the host, especially since the rate and accuracy of detection is higher when \smass\ is increasing, resulting in a final sample of 646 quasars.
 These selections will be adopted in an equivalent manner to the simulated samples to mitigate selection effects thus allowing the fair comparison.
@@
 
-%\begin{deluxetable*}{ccccccc}
-%%\tablenum{1}
-%\tablecaption{Key characteristics of hydrodynamic simulations used in this study.\label{tab:sim_sum}}
-%\tablewidth{0pt}
-%\tablehead{
-%%\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
-%%  \cline{2-4}  \cline{5} \\
-%\colhead{Simulation} & \colhead{box sizes} & particles &  \multicolumn{2}{c}{mass resolution ($M_{\odot}$)} & \colhead{feedback prescription} & \colhead{AGN fueling mechanism}  %& what else?
-%\\
-%\cline{4-5}
-%&$(\mathrm{cMpc})^3$&& dark matter & baryonic matter && $\dot{M}_{BH}$
-%}
-%\startdata
-%MBII & $142.7^3$ & $2\times1792^3$ & $1.57\times10^7$ & $3.14\times10^6$ &5\% & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ \\
-%Illustris & $(106.5)^3$ & $2\times1820^3$ & $6.26\times10^6$ & $1.26\times10^6$ &5\%& $\alpha \dot{M}_{Bondi}$ \\
-%TNG100 &$(111)^3$& $2\times1820^3$&$7.5\times10^6$ &$1.4\times10^6$& min[$2\times10^{-3}(\frac{M_{\rm BH}}{10^8M_{\odot}})^2$, 10\%] & \blue{$\dot{M}_{Bondi}$}\\
-%TNG300 &$(302)^3$& $2\times2500^3$&$5.9\times10^7$&$1.1\times10^7$&
-%min[$2\times10^{-3}(\frac{M_{\rm BH}}{10^8M_{\odot}})^2$, 10\%]& \blue{$\dot{M}_{Bondi}$} \\
-%Horizon-AGN &$(142)^3$& $\sim2\times1024^3$ &$8\times10^7$&$2\times10^6$&1.5\% - 10\% & $\alpha\dot{M}_{Bondi}$ \\
-%\enddata
-%\tablecomments{%\aklant{\bf{Could you please specify the maximum accretion rate for all the simulations?}}
-%\blue{For all simulations, the accretion rate on to BHs is capped at the Eddington accretion rate, expect MBII which has a mildly super-Eddington (i.e., two times Eddington rate).}
-%\red{In the last column, $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$. $\alpha$ is the boost factor. For Illustris, $\alpha = 100$; for Horizon-AGN, $\alpha =$ max$((\rho/\rho_0)^2$, 1).}
-%}
-%%\tablecomments{This table }
-%\end{deluxetable*}
-
 \begin{deluxetable*}{lccccc}
-%\tablenum{1}
 \tablecaption{Key characteristics of hydrodynamic simulations used in this study.\label{tab:sim_sum}}
@@
 \tablehead{
-%\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
-%  \cline{2-4}  \cline{5} \\
 \colhead{Simulation} & MBII & Illustris &  TNG100 & TNG300 & Horizon-AGN
-%&$(\mathrm{cMpc})^3$&& dark matter & baryonic matter && $\dot{M}_{BH}$
 }
@@
 \cline{1-6}
-{\bf AGN feedback} & (feedback efficiency $\times\epsilon_r$) \\
+{\bf AGN feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ radiative efficiency)} \\
 High acc. mode & 0.05 $\times$ 0.1 & 0.05 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.15 $\times$ 0.1 \\
@@
 \cline{1-6}
-AGN fueling mechanism   & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ & $\alpha \dot{M}_{Bondi}$ & \blue{$\dot{M}_{Bondi}$}&\blue{$\dot{M}_{Bondi}$} & $\alpha\dot{M}_{Bondi}$ \\
+AGN fueling mechanism   & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ & $\alpha \dot{M}_{Bondi}$ & $\dot{M}_{Bondi}$&$\dot{M}_{Bondi}$ & $\alpha\dot{M}_{Bondi}$ \\
 maximum accretion rate & 2 $\times$Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate\\
 \enddata
-\tablecomments{%\aklant{\bf{Could you please specify the maximum accretion rate for all the simulations?}}
-%\blue{For all simulations, the accretion rate on to BHs is capped at the Eddington accretion rate, expect MBII which has a mildly super-Eddington (i.e., two times Eddington rate).}
-\red{In the penultimate row, $\alpha$ is the boost factor. For Illustris, $\alpha = 100$; for Horizon-AGN, $\alpha =$ max$[(\rho/\rho_0)^2, 1]$. $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$.}
+\tablecomments{In the penultimate row, $\alpha$ is the boost factor.
+For Illustris, $\alpha = 100$; for Horizon-AGN, $\alpha =$ max$[(\rho/\rho_0)^2, 1]$.
+$\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$.
 }
-%\tablecomments{This table }
 \end{deluxetable*}
 
-\section{Simulations \blue{and comparison strategy}}
+\section{Simulations and comparison strategy}
 \label{sec:simulations}
 We introduce the simulation samples that are adopted in this section.
-All the simulation are based on the larger-scale cosmological simulations, except the Semianalytic Model (SAM) simulation \blue{(see Section~\ref{subsec:SAM})}.
+All the simulation are based on the larger-scale cosmological simulations, except the Semianalytic Model (SAM) simulation (see Section~\ref{subsec:SAM}).
 In Table~\ref{tab:sim_sum}, we summarized the key elements for each hydrodynamic simulation being considered.
-%\todo{Maybe we can also summarize the importance of AGN feedback somewhere here?}
 
 \subsection{{\tt MassiveBlackII} (MBII)}\label{subsec:MBII}
-MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of %$100~\mathrm{cMpc/h}$
-\red{$(142.7~\mathrm{cMpc})^3$}
-and $2\times1792^3$ particles. The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}. 
-%\yo{if the values of the cosmological parameters are given for MBII maybe this should also be given for all the other simulations?}
+MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $(142.7~\mathrm{cMpc})^3$
+and $2\times1792^3$ particles.
+The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}.
 The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}.
-%, i.e., $\Omega_0=0.275$, $\Omega_l=0.725$, $\Omega_b=0.046$, $\sigma_8=0.816$, $h = 0.701$, $n_s=0.968$.
-%\yo{Masses are given here in $M_\odot/h$, while in some other places this is given in $M_\odot$. The same for box lengths.}
-For dark matter and gas, the mass resolutions are %$1.1\times 10^7~M_{\odot}/h$ and $2.2\times 10^6~M_{\odot}/h$
-\red{$1.57\times 10^7~M_{\odot}$ and $3.14\times 10^6~M_{\odot}$}
-, respectively.
+For dark matter and gas, the mass resolutions are $1.57\times 10^7~M_{\odot}$ and $3.14\times 10^6~M_{\odot}$, respectively.
 The simulation includes a full modeling of gravity plus gas hydrodynamics, with a wide range of subgrid recipes to model the star formation~\citep{2003MNRAS.339..289S}, BH growth, and the feedback process~\citep{2005Natur.433..604D}.
@@
 The accreted gas is released as radiation at a radiative efficiency of 10\%.
-A fraction of 5\% of the radiated energy \aklant{thermally} couples to the surrounding gas as black hole (or AGN) feedback~\citep{2005Natur.433..604D}.
+A fraction of 5\% of the radiated energy thermally couples to the surrounding gas as black hole (or AGN) feedback~\citep{2005Natur.433..604D}.
 A mildly super-Eddington (two times Eddington rate) is allowed.
@@
 
-%\ding{The galaxy photometry information is not used in this work (we only compare stellar mass this time).
-To avoid any confusing or misunderstanding, I remove the simulation SED information in Section 3.1, 3.2 and 3.3.}
-%For the galaxy photometry, the initial SEDs of the BH host galaxies were determined by combining all the contributions from their constituent star particles.
-The stellar SEDs were derived using the PEGASE-2~\citep{1999astro.ph.12179F} stellar population synthesis code with a Salpeter IMF.
-Finally, the galaxy SEDs are  cooperated with the desired filter response to obtain the broadband photometry (e.g., SDSS $r$-band magnitude).
-
 As a common practice, the stellar mass is obtained by using a 3D spherical aperture of 30~kpc to represent the observed stellar mass.
-\blue{We adopt this definition of stellar masses for all simulations described in the following sections.} Using this definition, \citet{Pillepich2018} has shown that the corresponding stellar mass function is consistent with the observational measure.
+We adopt this definition of stellar masses for all simulations described in the following sections.
+Using this definition, \citet{Pillepich2018} has shown that the corresponding stellar mass function is consistent with the observational measure.
 Even more, the stellar mass using this 3D aperture can achieve good agreement to those measured within the Petrosian radii in observational studies~\citep{Schaye2015}.
@@
 The simulation consist of a volume of (106.5 cMpc)$^3$~(slightly smaller than MassiveBlack II),
-%\yo{Here the box size is given in cMpc and in the table in cMpc/$h$ with the same numerical value.}
 and was run with the moving Voronoi mesh code {\tt Arepo}~\citep{2010MNRAS.401..791S} with a base cosmology adopted from WMAP9 results~\citep{2013ApJS..208...19H}.
-%\aklant{\bf{I think it'll be good to explicitly state all cosmological parameters for the simulations and SAMs}}. 
-Besides gravity and gas hydrodynamics, the simulation calculates the astrophysical processes ~\citep{2013MNRAS.436.3031V, 2014MNRAS.438.1985T} that includes \aklant{gas cooling and star formation~(with a density threshold of 0.13 cm$^{-3}$, \citealt{2003MNRAS.339..289S})}, stellar evolution and chemical enrichment, kinetic stellar feedback by SNe activity, BH growth~(accretion and merging), and AGN feedback.
+Besides gravity and gas hydrodynamics, the simulation calculates the astrophysical processes ~\citep{2013MNRAS.436.3031V, 2014MNRAS.438.1985T} that includes gas cooling and star formation~(with a density threshold of 0.13 cm$^{-3}$, \citealt{2003MNRAS.339..289S}), stellar evolution and chemical enrichment, kinetic stellar feedback by SNe activity, BH growth~(accretion and merging), and AGN feedback.
 
-\aklant{BHs are seeded with an initial mass of $1 \times 10^5~M_{\odot}/h$ when a halo exceeds a mass of $5 \times 10^{10}~M_{\odot}/h$.
+BHs are seeded with an initial mass of $1 \times 10^5~M_{\odot}/h$ when a halo exceeds a mass of $5 \times 10^{10}~M_{\odot}/h$.
 BHs then grow via accretion described by the Eddington limited Bondi-Hoyle-Lyttleton formalism ($\alpha4\pi G^2M_{BH}^2 \rho/c_s^3$), as well as mergers with other BHs.
 The boost factor $\alpha=100$ is introduced to account for the unresolved multiphase ISM~\citep{Springel2005, 2009MNRAS.398...53B}, which is otherwise expected to underestimate the density around the BHs.
-Lastly, accreting black holes radiate with a bolometric luminosity given by $\epsilon_r \dot{M}_{BH}c^2$, where $\dot{M}_{BH}$ is the mass accretion rate and $\epsilon_r=0.2$ is the radiative efficiency.}
+Lastly, accreting black holes radiate with a bolometric luminosity given by $\epsilon_r \dot{M}_{BH}c^2$, where $\dot{M}_{BH}$ is the mass accretion rate and $\epsilon_r=0.2$ is the radiative efficiency.
 
-\aklant{The AGN feedback consists of three components, namely quasar-mode, radio-mode and radiative feedback.
+The AGN feedback consists of three components, namely quasar-mode, radio-mode and radiative feedback.
 In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy.
@@
 The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{bh} c^2$ where $\delta M_{bh}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency.
-Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN.} \blue{As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy stellar mass, assuming a \cite{2003PASP..115..763C} IMF.}
-
-%It is highlighted in ~\citet{2014MNRAS.444.1518V} that the AGN feedback is the key process in quenching massive galaxy which is crucial to reproduce a tight stellar mass and BH mass relation.
-
-%\aklant{Finally, galaxy photometry was computed similar to that \texttt{MassiveBlackII}, but with SEDs derived using templates from \texttt{STARBURST99 (SB99)} catalogs~\citep{2010ApJS..189..309L} assuming a \cite{2003PASP..115..763C} IMF.}
+Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN.
+As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy stellar mass, assuming a \cite{2003PASP..115..763C} IMF.
 
 \subsection{IllustrisTNG}
-{\it The Next Generation Illustris Simulations} (IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018} are 
-%\yo{I am not sure why ``ambitious''}
-%an ambitious 
-an suite of \aklant{magneto}hydrodynamical simulations of galaxy formation in large cosmological volumes.
+{\it The Next Generation Illustris Simulations} (IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes.
 It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modeling, and 3) addressing the identified shortcomings of the previous generation simulations.
 
-The TNG100 and TNG300 have a volume of (100~cMpc)$^3$ and (300~cMpc)$^3$, respectively. The adopted cosmological parameters are updates by the Planck result~\citep{2016A&A...594A..13P}
-% \aklant{\bf{Here again, please list the cosmological parameters?}}.
-\aklant{The gas cooling and star formation prescriptions are broadly similar to the Illustris model.
+The TNG100 and TNG300 have a volume of (100~cMpc)$^3$ and (300~cMpc)$^3$, respectively. The adopted cosmological parameters are updates by the Planck result~\citep{2016A&A...594A..13P}.
+The gas cooling and star formation prescriptions are broadly similar to the Illustris model.
 However significant updates have been made to the stellar feedback model~(more details in \citealt{2018MNRAS.473.4077P}).
 BH seeds with initial mass of $8 \times 10^5 M_{\odot}/h$ are placed in Dark matter halos with a mass exceeding $5 \times 10^{10} M_{\odot}/h$.
-Notably, the seed mass is one order of magnitude higher than in the Illustris simulation.} The BH accretion also follows the Bondi-Hoyle-Lyttleton formalism, but without any boost factor~(unlike Illustris).
+Notably, the seed mass is one order of magnitude higher than in the Illustris simulation.
+The BH accretion also follows the Bondi-Hoyle-Lyttleton formalism, but without any boost factor~(unlike Illustris).
 Accreting black holes release energy with a radiative efficiency of 0.2~(same as Illustris).
-The \aklant{inclusion} of the magnetic fields can affect the relationship between the BHs and their host galaxies properties; the \mbh-\smass\ mean relation is higher with magnetic fields~\citep{2018MNRAS.473.4077P}.
-%~\aklant{\bf{Aklant: Hmm I did not know this.
-Do they talk about what exactly causes this impact?
-Xuheng's reply: I adopt this sentence form the reference and Pillepich et al.
-It is mentioned in \citet{2018MNRAS.473.4077P} (in the texts after Figure 8) in the TNG model they modify the Bondi-Hoyle-Lyttleton formula for the gas accretion on to the BH in the presence of magnetic fields.}} %\sout{The TNG simulation also employs a kernel-weighted accretion rate over about 256 neighboring cells.} \sout{Thus, the TNG BH can build up correlation with the gas properties in the galaxy central region.}
+The inclusion of the magnetic fields can affect the relationship between the BHs and their host galaxies properties; the \mbh-\smass\ mean relation is higher with magnetic fields~\citep{2018MNRAS.473.4077P}.
 
-\aklant{The AGN feedback occurs in thermal, radio, and radiative modes.
+The AGN feedback occurs in thermal, radio, and radiative modes.
 For high accretion rates, the feedback implementation is the same as Illustris i.e., thermal energy is injected in the surroundings of the accreting BHs.
@@
 Instead of releasing hot bubbles, this feedback mode in TNG is purely kinetic.
-In particular, there is a directional injection of momentum along a randomly chosen direction~\citep{2017MNRAS.465.3291W, 2018MNRAS.479.4056W} at irregular intervals.} The transition between the two feedback modes is also different from Illustris, and is set by the minimum value of 0.1 and $2 \times 10 ^{-3} \times (M_{BH} / 10^8~M_{\odot})$.
-\aklant{Additionally, the radiative feedback implemented in Illustris~(summarized in the previous section) is also present in TNG.} Lastly, \blue{the galaxy stellar mass} in Illustris-TNG is \blue{obtained} in a similar manner to that of Illustris.
+In particular, there is a directional injection of momentum along a randomly chosen direction~\citep{2017MNRAS.465.3291W, 2018MNRAS.479.4056W} at irregular intervals.
+The transition between the two feedback modes is also different from Illustris, and is set by the minimum value of 0.1 and $2 \times 10 ^{-3} \times (M_{BH} / 10^8~M_{\odot})$.
+Additionally, the radiative feedback implemented in Illustris~(summarized in the previous section) is also present in TNG.
+Lastly, the galaxy stellar mass in Illustris-TNG is obtained in a similar manner to that of Illustris.
 
 \subsection{Horizon-AGN}\label{subsec:Horizon}
-
-\blue{The simulation Horizon-AGN~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D} has a volume of 142 cMpc$^3$ and was generated using the adaptive mesh refinement code {\tt Ramses}~\citep{2002A&A...385..337T} with a $\Lambda$CDM model based on WMAP7~\citep{2011ApJS..192...18K} cosmological results.
+The simulation Horizon-AGN~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D} has a volume of 142 cMpc$^3$ and was generated using the adaptive mesh refinement code {\tt Ramses}~\citep{2002A&A...385..337T} with a $\Lambda$CDM model based on WMAP7~\citep{2011ApJS..192...18K} cosmological results.
 The dark matter particle mass is $8\times 10^7 M_{\odot}$.
@@
 Collisionless particles (dark matter and star particles) are evolved using a particle-mesh solver with a cloud-in-cell interpolation.
-}
 
-\blue{The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation with a constant star formation efficiency $\epsilon_*=0.02$, which occurs in regions where the gas number density exceeds the star formation threshold $n_0 = 0.1\,\rm H\, cm^{-3}$.
+The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation with a constant star formation efficiency $\epsilon_*=0.02$, which occurs in regions where the gas number density exceeds the star formation threshold $n_0 = 0.1\,\rm H\, cm^{-3}$.
 A Salpeter IMF is assumed.
 Stellar feedback is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources.
-}
 
-\blue{Differing from simulations presented above, Horizon-AGN does not use a fixed threshold in the dark matter halo mass to seed BHs.
+Differing from simulations presented above, Horizon-AGN does not use a fixed threshold in the dark matter halo mass to seed BHs.
 BHs are seeded with a mass of $10^5 M_\odot$ in cells, with gas density above $n_0$ and stellar velocity dispersion larger than $100 \,\rm km\,s^{-1}$.
@@
 BH accretion is computed using the Bondi-Hoyle-Lyttleton formalism with a boost factor $\alpha = (\rho/\rho_0)^2$ when the density $\rho$ is higher than the resolution-dependent threshold $\rho_0$.
-Otherwise, the boost factor is fixed as unity~\citep{2009MNRAS.398...53B}.}
+Otherwise, the boost factor is fixed as unity~\citep{2009MNRAS.398...53B}.
 
-\blue{Horizon-AGN includes two modes of AGN feedback.
+Horizon-AGN includes two modes of AGN feedback.
 In the quasar mode ($f_{\rm Edd}>0.01$), thermal energy is isotropically released within a sphere of radius a few resolution elements.
@@
 The  energy  rate  in  this  mode is $\dot{E}_{\rm AGN} = 0.1 \dot{M}_{\rm BH} c^2$.
-The  technical  details  of  BH  formation,  growth  and AGN  feedback  modeling  of  Horizon-AGN  can be found in~\citet{2012MNRAS.420.2662D}.}
+The  technical  details  of  BH  formation,  growth  and AGN  feedback  modeling  of  Horizon-AGN  can be found in~\citet{2012MNRAS.420.2662D}.
 
-\blue{We identify galaxies applying the AdaptaHOP structure finder \citep{Aubert+04,Tweed+09} to the star particle distribution.
+We identify galaxies applying the AdaptaHOP structure finder \citep{Aubert+04,Tweed+09} to the star particle distribution.
 Galaxies are identified using a local threshold of 178 times the average matter density, with the local density of individual particles calculated using the 20 nearest neighbours.
@@
 The galaxy mass corresponds to the total stellar mass of a galaxy identified with this approach.
-The stellar mass function is shown in \cite{2017MNRAS.467.4739K} to be in good agreement with observations.}
-
-%Horizon-AGN  employs  a  kinetic  SN  feedback,  including momentum, mechanical energy and metals from type~II, Type  Ia  SNe,  and  stellar  winds  (details  in  Kaviraj  et  al.2017).
-The  feedback  is  modeled  as  kinetic  release  of  energy on timescale below 50 Myr, and a thermal energy after 50 Myr.
-The feedback is also pulsed, meaning that energy is accumulated until sufficient to propagate the blast wave to  at  least  two  cells.
-The  energy  released  depends  on  theSSP modeled assumed and the metallicity of the gas, and is aboute SN $\sim10^{49}$ erg/$M_{\odot}$.
+The stellar mass function is shown in \cite{2017MNRAS.467.4739K} to be in good agreement with observations.
 
@@
 \centering
-\includegraphics[height=0.35\textwidth]{OpeningAngle.pdf}
+\includegraphics[height=0.37\textwidth]{OpeningAngle.pdf}
 \caption{\label{fig:SAM} 
@@
 \begin{tabular}{c c}
-{\includegraphics[trim = 0mm 0mm 65mm 10mm, clip, height=0.45\textwidth]{HSC_selection_MBII.png}}
-{\includegraphics[trim = 0mm 0mm 20mm 10mm, clip,height=0.45\textwidth]{HST_selection_MBII.png}}
+{\includegraphics[trim = 0mm 0mm 65mm 10mm, clip, height=0.4\textwidth]{HSC_selection_MBII.png}}
+{\includegraphics[trim = 0mm 0mm 20mm 10mm, clip,height=0.4\textwidth]{HST_selection_MBII.png}}
 \end{tabular}
-%\caption{\label{fig:selection}Demonstration of the impact of AGN selection using MBII.
-{\it left}: Correlation between \mbh\ and %$L_{\rm bol}$ of the simulated HSC sample is used to set the selection window for the simulated sample.
-This region roughly bracket %the type-1 AGN sample.
-The light green background cloud shows the simulated number density distribution in this parameter space %which includes a random level of uncertainty to mimic observational measurement errors.
-{\it right}: Similar to the top plane -- %equivalent selection window adopted for the HST-observed and MBII simulated samples.
-%}
 \caption{\label{fig:selection}Demonstration of AGN selection using MBII.
@@
 The light green background cloud shows the {\it intrinsic} simulated number density in this parameter space.
-%which includes a random level of uncertainty to mimic observational measurement errors.
 {\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample.
@@
 We highlight the main points of the simulation with respect to our study; for more detail, a full description of the SAM can be found in~\citet{Menci2016} which is based on an earlier semi-analytic model introduced in~\citet{Menci2014}.
-\blue{The specific version adopted here differs from the one presented in the above papers since it implements a new, detailed description of AGN feedback, as discussed in detail below}.
+The specific version adopted here differs from the one presented in the above papers since it implements a new, detailed description of AGN feedback, as discussed in detail below.
 
@@
 In each halo, we compute the fraction of gas which cools because of the atomic processes and settles into a disk~\citep{Mo1998}.
-The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr,
-%(CHECK THIS-JDS)\ding{It's mentioned in Menci 2016 section 2.} 
-according to BH feeding; (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion).
+The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr, according to BH feeding; (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion).
 The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation which returns a fraction of the disk gas into a hot phase.
 A Salpeter IMF is adopted in the SAM simulation.
-\blue{A $\Lambda$CDM power spectrum of perturbations with a total matter density parameter $\Omega_0=0.3$, a baryon density parameter
-$\Omega_b=0.04$, a dark energy density parameter $\Omega_\Lambda=0.7$, and a Hubble constant $h$=0.7 is adopted. }
+A $\Lambda$CDM power spectrum of perturbations with a total matter density parameter $\Omega_0=0.3$, a baryon density parameter
+$\Omega_b=0.04$, a dark energy density parameter $\Omega_\Lambda=0.7$, and a Hubble constant $h$=0.7 is adopted.
 
@@
 The BH accretion is based on both interaction-driven and disk instability feeding modes.
-%\newline(1)~{\it triggered by interactions.} The interaction rate $\tau_r^{-1}=n_T\,\Sigma (r_t,v_c,V)\,V_{rel} (V)$ for galaxies with relative velocity $V_{rel}$ and number density $n_T$ in a common DM halo determines the probability for encounters, either fly-by or merging, through the corresponding cross sections $\Sigma$ given in~\citet{Menci2014}.
-The fraction of gas destabilized in each interaction corresponds to the loss $\Delta j$ of orbital angular momentum $j$, and depends on the mass ratio of the merging partners $M'/M$ and on the impact factor $b$.
-%\newline(2)~{\it induced by disc instabilities.} We assume these to arise  in  galaxies with disc mass exceeding~\citep{Efstathiou1982} $M_{crit} =  {v_{max}^2 R_{d}/ G \epsilon}$ with $\epsilon=0.75$, where $v_{max}$ is the maximum circular velocity associated to each halo ~\citep{Mo1998}.
-Such a criterion strongly suppresses the probability for disc instabilities to occur not only in massive, gas-poor galaxies, but also in dwarf galaxies characterized by small values of the gas-to-DM mass ratios.
-The instabilities induce loss of angular momentum resulting into strong inflows that we compute following the description in~\citet{Hopkins2011}, recast and extended as in~\citet{Menci2014}.
-%\todo{This part should be updated for the new SAM version? No, please leave as it is}
-\blue{The SAM adopted here implements a new and improved  model for the AGN feedback with respect to the previous versions~\citep{Menci2008}.
+The SAM adopted here implements a new and improved  model for the AGN feedback with respect to the previous versions~\citep{Menci2008}.
 In both versions, the basic assumption is that fast winds with velocity up to $10^{-1}c$ observed in the central regions of AGNs~\citep{Chartas2002, Pounds2003}  result in  supersonic outflows that compress the gas into a blast wave terminated by a leading shock front.
@@
 The resulting strong dependence of the total (integrated over directions) outflow rate on the AGN luminosity $L_{AGN}$ and on the gas content of the galaxy $M_{gas}$ is shown in Figure~\ref{fig:SAM}.
-Such a new AGN feedback model has been tested in detail against a state-of-the-art compilation of observed outflows in 19 galaxies with different measured gas and dynamical masses~\citep{Fiore2017},
-%(Fiore et al. 2019)\ding{Hi Nicola, I can't find the reference Fiore et al. 2019, I guess you mean~\citep{Fiore2017}, right? I will update the reference before submit. Let me know if I am wrong.}
-allowing for a detailed, one-by-one comparison with the model predictions.
-Such a new, well tested AGN feedback model  allowed us to derive, for each simulated galaxy in the SAM,  the outflow expansion and the mass outflow rates in different directions with respect to the plane of the disc.}
+Such a new AGN feedback model has been tested in detail against a state-of-the-art compilation of observed outflows in 19 galaxies with different measured gas and dynamical masses~\citep{Fiore2017}, allowing for a detailed, one-by-one comparison with the model predictions.
+This well tested AGN feedback model allowed us to derive, for each simulated galaxy in the SAM,  the outflow expansion and the mass outflow rates in different directions with respect to the plane of the disc.
+
+\subsection{Application of observational measurement error and selection effects}
+To make direct comparisons with observations, we add measurement errors and apply the equivalent selection to the simulated samples.
+We first inject random noise to the simulated catalog to mimic the scatter caused by measurement error.
+As mentioned above, \smass\ and \mbh\ for HSC and HST samples are measured with a similar approach; thus their uncertainty levels are expected to be equivalent.
+We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = 0.17~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.
+
+We then apply restrictions on the noise-injected simulation to mimic selection effects as present in the observational data.
+Since the HSC and HST samples have their own selection function, we apply different selection criteria to the simulation as follows:
+
+ HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should match the relationship between \mbh-$L_{\rm bol}$ as seen in the HSC sample.
+We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it top}).
+(2) The $i$-band magnitude of the AGN are bright (see Section~\ref{sec:hsc}).
+The specific selection is made as follows: for systems at $z<0.5$ and $z>0.5$, the AGN $i$-band magnitude is required to be brighter than 20.5 mag and 22.0 mag, respectively.
+Since the simulations do not provide the observed AGN magnitude, we adopt a simulated rest-frame magnitude or L$_{\rm 5100}$ and assume the quasar continuum as a single power-law with an index of $\alpha_\nu=-0.44$~\citep{2001AJ....122..549V} to calculate the observed $i$-band magnitude.
+ 3)~Following the HSC selection, we require the \smass\ value to be above a certain level (according to their redshift) to assure an accurate measurement.
+Finally, the HSC sample is split into three redshift bins for making comparison which are $0.2<z<0.4$, $0.4<z<0.6$, and $0.6<z<0.8$.
+
+HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example).
+Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., between [7.7, 8.6] $M_{\odot}$).
+The HST sample covers the higher redshift range $1.2<z<1.7$, which is considered as a single redshift bin to make the comparison with the simulations at $z=1.5$.
+
+\section{Results} \label{sec:result}
+In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
+The local scaling relation adopted by D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is used as the fiducial relation to assess relative offsets and differences in dispersion.
+A different simulation is presented in each row and the redshift intervals increase from left to right.
+We note that TNG100 and TNG300 yield very similar comparison results, thus only TNG100 is presented in Figure~\ref{fig:comparsion}.
 
@@
 
-\subsection{Application of observational measurement error and selection effects}
-
-To make direct comparisons with observations, we add measurement errors and apply the equivalent selection to the simulated samples.
-We first inject random noise to the simulated catalog to mimic the scatter caused by measurement error.
-As mentioned above, \smass\ and \mbh\ for HSC and HST samples are measured with a similar approach; thus their uncertainty levels are expected to be equivalent.
-We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = 0.17~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.
-
-We then apply restrictions on the noise-injected simulation to mimic selection effects as present in the observational data.
-Since the HSC and HST samples have their own selection function, we apply different selection criteria to the simulation as follows:
-%\begin{itemize}
-
- HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should match the relationship between \mbh-$L_{\rm bol}$ as seen in the HSC sample.
-We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it top}).
-(2) The $i$-band magnitude of the AGN are bright (see Section~\ref{sec:hsc}).
-The specific selection is made as follows: for systems at $z<0.5$ and $z>0.5$, the AGN $i$-band magnitude is required to be brighter than 20.5 mag and 22.0 mag, respectively.
-Since the simulations do not provide the observed AGN magnitude, we adopt a simulated rest-frame magnitude or L$_{\rm 5100}$ and assume the quasar continuum as a single power-law with an index of $\alpha_\nu=-0.44$~\citep{2001AJ....122..549V} to calculate the observed $i$-band magnitude.
- 3)~Following the HSC selection, we require the \smass\ value to be above a certain level (according to their redshift) to assure an accurate measurement.
-Finally, the HSC sample is split into three redshift bins for making comparison which are $0.2<z<0.4$, $0.4<z<0.6$, and $0.6<z<0.8$.
-
-HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example).
-Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., between [7.7, 8.6] $M_{\odot}$).
-The HST sample covers the higher redshift range $1.2<z<1.7$, which is considered as a single redshift bin to make the comparison with the simulations at $z=1.5$.
-%\end{itemize}
-
-\section{Results} \label{sec:result}
-In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
-The local scaling relation adopted by D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is used as the fiducial relation to assess relative offsets and differences in dispersion.
-A different simulation is presented in each row and the redshift intervals increase from left to right.
-We note that TNG100 and TNG300 yield very similar comparison results, thus only TNG100 is presented in Figure~\ref{fig:comparsion}.
-
 For each sample, the central offset and scatter of the scaling relation are estimated by calculating the mean and the standard deviation of the \mbh\ residuals for each system\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the y-axis in Figure~\ref{fig:comparsion}).
@@
 In addition, the values for the central offset and scatter in each case are given in Table~\ref{tab:sum} and shown as a function of redshift in Figure~\ref{fig:offsets_vz}.
-
-\begin{figure*}
-\centering
-\begin{tabular}{c c c c}
-\hspace*{-0.4cm} 
-{\includegraphics[height=0.4\textwidth]{offset_dis_z03.pdf}}&
-\hspace*{-0.4cm} 
-{\includegraphics[height=0.4\textwidth]{offset_dis_z05.pdf}}&
-\hspace*{-0.4cm} 
-{\includegraphics[height=0.4\textwidth]{offset_dis_z07.pdf}}&
-\hspace*{-0.4cm} 
-{\includegraphics[height=0.4\textwidth]{offset_dis_z15.pdf}}\\
-\end{tabular}
-\caption{\label{fig:offsets} 
-Histograms of the offset distributions for all simulation samples and observations.
-The mean value and the standard derivation of the histogram are summarized in Table~\ref{tab:sum}.
-The vertical dashed lines show the corresponding mean value for each distribution.
-The mean values for observed sample (i.e., yellow lines) are also show in each simulation plots.
-For the MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$.
-}
-\end{figure*}
-
-\begin{figure}
-\centering
-%\begin{tabular}{c c}
-%{
-\includegraphics[height=0.4\textwidth]{offset_summary_vz.pdf}%}&
-%{\includegraphics[height=0.4\textwidth]{offset_int_summary_vz.pdf}}\\
-%\end{tabular}
-\caption{\label{fig:offsets_vz} 
-%{\it left}: 
-The {\it observed} evolution of $\Delta{\rm log}$\mbh\ as a function of redshift using both observation and simulation data.
-The black line shows the evolution by fitting the offset as a function of redshift.
-The predictions from the numerical simulations, given in Table~\ref{tab:sum}, are presented by different colored symbols.
-The grey horizontal band illustrates the level of dispersion for the local sample.
-%\ding{The right panel can be confusing and hard to explain. Maybe we can remove?}
-}
-\end{figure}
 
@@
 
+\begin{figure}
+\centering
+\begin{tabular}{c c c c}
+\hspace*{-0.4cm} 
+{\includegraphics[height=0.4\textwidth]{offset_dis_z03.pdf}}&
+\hspace*{-0.4cm} 
+{\includegraphics[height=0.4\textwidth]{offset_dis_z05.pdf}}\\
+\hspace*{-0.4cm} 
+{\includegraphics[height=0.4\textwidth]{offset_dis_z07.pdf}}&
+\hspace*{-0.4cm} 
+{\includegraphics[height=0.4\textwidth]{offset_dis_z15.pdf}}\\
+\end{tabular}
+\caption{\label{fig:offsets} 
+Histograms of the offset distributions for all simulation samples and observations.
+The mean value and the standard derivation of the histogram are summarized in Table~\ref{tab:sum}.
+The vertical dashed lines show the corresponding mean value for each distribution.
+The mean values for observed sample (i.e., yellow lines) are also show in each simulation plots.
+For the MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$.
+}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[height=0.4\textwidth]{offset_summary_vz.pdf}
+\caption{\label{fig:offsets_vz} 
+The {\it observed} evolution of $\Delta{\rm log}$\mbh\ as a function of redshift using both observation and simulation data.
+The black line shows the evolution by fitting the offset as a function of redshift.
+The predictions from the numerical simulations, given in Table~\ref{tab:sum}, are presented by different colored symbols.
+The grey horizontal band illustrates the level of dispersion for the local sample.
+}
+\end{figure}
+
 \subsection{Global offsets}
-
 We examine the offsets to understand whether the simulations deviate or not from the {\it observed} scaling relation with particular attention to changes with redshift.
@@
 
-\blue{
 \subsection{Trends with stellar mass}
@@
 This trend is not seen in any of the simulations after noise and selection effects have been applied.
-Given the level of uncertainties in the mean offsets of the observed sample, we do not try to interpret this trend any further in this study.}
+Given the level of uncertainties in the mean offsets of the observed sample, we do not try to interpret this trend any further in this study.
 
-\blue{
 Interestingly, we notice that MBII and Illustris have black holes intrinsically under-massive relative to their galaxies at the lower masses that reach the local relation at higher masses.
@@
 In fact, after noise and selection is applied, the simulated sample exhibits very small offsets which agree remarkably well with the observed data.
-{\bf TT edits: This result underscores the importance of taking into account errors and selection --- without accounting for those, one could erroneously interpret an apparent trend as evolution in the opposite sense as the true one.
-The most direct way to circumvent these issues is to probe lower masses (\smass\  $<10^{10}M_{\odot}$) using a more sensitive instrument, such as JWST~\citep{Habouzit2022} across this redshift range \citep[see also][]{2011MNRAS.417.2085V}.}}
-{\bf TT: the following sentences seem out of place} \ding{OK, let's remove the following red sentences can be removed}
-\red{In the local universe, a delayed black hole growth scenario seems to be supported \citep{Reines2015}, %\yo{
-which is understood to be the result of the quenching of BH growth by efficient feedback from SNe in low-mass galaxies~\citep[e.g.][]{dubois_snreg_2015,habouzit_blossom_2017,bower_dark_2017,angles_black_2017}.}
-
-%the intrinsic distribution actually shows an opposite trend in which the host galaxy is more massive at low mass end.
-While the TNG100 and Horizon-AGN also present good comparisons in the {\it observed} plane, they predict the different intrinsic trend unlike Illustris.
-Yet, limited by the stellar mass range of our observed data, our comparison result could not rule out any simulation at this moment.
-To this end, extending the study to lower mass ($<10^{10}M_{\odot}$) using more sensitive instrument, such as JWST, will be the key~\citep{Habouzit2022}.
-
-%For instance, if overlook the observational effect, the HSC observational measurement show that, when host stellar mass is low, the SMBH trend to be more massive taking local scaling relation as reference.
-This could mislead to a wrong conclusion that SMBH grow up first and the host galaxy catch up later to match up with the scaling relation in local universe.
-
-%In fact, taking the Illustris as example who well predicts the {\it observed} scaling relation to the HSC observation,
+This result underscores the importance of taking into account errors and selection --- without accounting for those, one could erroneously interpret an apparent trend as evolution in the opposite sense as the true one.
+The most direct way to circumvent these issues is to probe lower masses (\smass\  $<10^{10}M_{\odot}$) using a more sensitive instrument, such as JWST~\citep{Habouzit2022} across this redshift range \citep[see also][]{2011MNRAS.417.2085V}.
 
@@
 The green color distributions show the intrinsic simulated sample without random noise and selection applied.
-%Since the selection of HST sample has a hard cut on the \mbh\ values, an {\it observed} trend of offset value as a function of stellar mass appears; this trend doesn't appear on the intrinsic ones. 
-%{\bf[MV: If I understand correctly, mean and standard deviation of the offset values are shown only for the simulation once you have included measurement errors and selection effects.
-If this is the case, can you add them also for the intrinsic simulated sample?]}
 }
@@
 
+\begin{deluxetable*}{lccccc}
+\tablecaption{Summary of the central offsets and scatters\label{tab:sum}}
+\tablewidth{0pt}
+\tablehead{
+\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
+\cline{2-4} 
+\colhead{} &  \colhead{$0.2<z<0.4$} & \colhead{$0.4<z<0.6$} & \colhead{$0.6<z<0.8$} & \colhead{$1.2<z<1.7$} & IMF
+}
+\startdata
+Observation & (0.12, 0.51) & (0.20, 0.50)  & (0.21, 0.56)  & (0.43, 0.31) & \\
+SAM & (0.73, 0.49) & (0.65, 0.46)  & (0.51, 0.45)  & (0.51, 0.36) & Salpeter \\
+MBII & (-0.15, 0.48) & \multicolumn{2}{c}{(-0.16, 0.48) [$z=0.6$]}  & (0.14, 0.31) & Salpeter\\
+Illustris & (0.01, 0.52) & (0.08, 0.53)  & (0.06, 0.54)  & (0.07, 0.32) &  Chabrier \\
+TNG100 & (0.27, 0.48) & (0.24, 0.46)  & (0.24, 0.45)  & (0.38, 0.33) & Chabrier \\
+TNG300 & (0.26, 0.48) & (0.20, 0.48)  & (0.17, 0.48)  & (0.41, 0.34) & Chabrier \\
+Horizon-AGN & (0.16, 0.49) & (0.14, 0.47)  & (0.23, 0.47)  & (0.47, 0.35) & Salpeter\\
+\enddata
+\tablecomments{This table collects the comparison results of the \smass-\mbh\ correlations between different simulation at different redshift.
+The value shows the central position offset to the local relation and the scatters measured around the local relation after applying the offset.
+A positive offset means the \mbh\ value predicted by the simulation is higher than the local relationship measurement at fixed \smass\ value.
+The last column shows the corresponding IMF that adopted to the local anchor to make a fair comparison with the observation.
+Note that for the observational data, the relative differences between local and high-$z$ measurements are not affected by the IMF assumptions.
+For the MBII sample, the simulation does not produce the sample at $z=0.5$ or $z=0.7$, but rather at $z=0.6$.
+We use Monte Carlo approach to infer the uncertainties of the values in the table, finding that the uncertainties are within $\pm 0.03$.
+}
+\end{deluxetable*}
+
 \section{Conclusions} \label{sec:con}
-%A brief introduce of the result. Scatter, central, which is best...
 We compared the observed scaling relation \mbh-\smass\ with the predictions from numerical simulations.
@@
 From $z\sim0.7$ to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
-%\ding{In the simulation, is there any observational data that be used to give extra constrain on the recipe/assumption?
-Xuheng and John are surprised to see that all of them have very good scatter matches.
-Maybe we need provide some details on how the scaling relations in the simulations are calibrated.
-For example, why Illustris and TNG sample predict different center for the scaling relation.
-Horizon-AGN could predict well at both low and high z, maybe we can add some discussions.}
-%{\bf[MV: This is very interesting.
-When comparing with BH-galaxy correlations at $z=0$ we noticed in \cite{2016MNRAS.460.2979V} that the simulations showed less scatter wrt the observations, and we thought that this meant that some stochastic processes on small scale were not captured.
-Now I wonder whether instead the lower scatter in the simulated results was because we did not apply any observational measurement error or selection effects to the simulation.
-You note in the Conclusions that this may not be important, but also that, indeed, no strong efforts have been made to include such effects.]}
+
 \end{enumerate}
@@
 
-%So far, a control experiment has not been performed yet in which one numerical model provide the 
-\blue{
-%hydrodynamical} simulation altering the AGN feedback prescription, while fixing all other conditions.
 We can gain more insight into the role of feedback by looking at the SAM model, for which multiple feedback models have been implemented.
@@
 (for given $M_{\rm gas}$) inhibits the BH growth in all the host galaxies that are outliers with respect to the average relation between $M_{\rm gas}$ and $L_{\rm AGN}$. 
-This results into a smaller scatter.}
+This results into a smaller scatter.
 
-\blue{
 In theoretical models, AGN feedback is often assumed to consist of two distinct modes:
-%In theory, it is a common knowledge that two different modes are responsible for AGN feedback: 
 a quasar-heating mode where the SMBH accretion rates are comparable to the Eddington rate and a radio-jet mode occurring at low accretion rates (see e.g.
@@
 After that, the radio-jet mode starts to take control at low redshift by maintaining the tightness of the scaling relation till the level we observe today.
-}
 
@@
 LB acknowledges support from NSF award AST-1909933 and Cottrell Scholar Award \#27553 from the Research Corporation for Science Advancement.
-
 \end{acknowledgments}
 
-\begin{deluxetable*}{lccccc}
-%\tablenum{1}
-\tablecaption{Summary of the central offsets and scatters\label{tab:sum}}
-\tablewidth{0pt}
-\tablehead{
-\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
-\cline{2-4} 
-%  \cline{2-4}  \cline{5} \\
-\colhead{} &  \colhead{$0.2<z<0.4$} & \colhead{$0.4<z<0.6$} & \colhead{$0.6<z<0.8$} & \colhead{$1.2<z<1.7$} & IMF
-}
-\startdata
-Observation & (0.12, 0.51) & (0.20, 0.50)  & (0.21, 0.56)  & (0.43, 0.31) & \\
-SAM & (0.73, 0.49) & (0.65, 0.46)  & (0.51, 0.45)  & (0.51, 0.36) & Salpeter \\
-MBII & (-0.15, 0.48) & \multicolumn{2}{c}{(-0.16, 0.48) [$z=0.6$]}  & (0.14, 0.31) & Salpeter\\
-Illustris & (0.01, 0.52) & (0.08, 0.53)  & (0.06, 0.54)  & (0.07, 0.32) &  Chabrier \\
-TNG100 & (0.27, 0.48) & (0.24, 0.46)  & (0.24, 0.45)  & (0.38, 0.33) & Chabrier \\
-TNG300 & (0.26, 0.48) & (0.20, 0.48)  & (0.17, 0.48)  & (0.41, 0.34) & Chabrier \\
-Horizon-AGN & (0.16, 0.49) & (0.14, 0.47)  & (0.23, 0.47)  & (0.47, 0.35) & Salpeter\\
-\enddata
-\tablecomments{This table collects the comparison results of the \smass-\mbh\ correlations between different simulation at different redshift.
-The value shows the central position offset to the local relation and the scatters measured around the local relation after applying the offset.
-A positive offset means the \mbh\ value predicted by the simulation is higher than the local relationship measurement at fixed \smass\ value.
-The last column shows the corresponding IMF that adopted to the local anchor to make a fair comparison with the observation.
-Note that for the observational data, the relative differences between local and high-$z$ measurements are not affected by the IMF assumptions.
-For the MBII sample, the simulation does not produce the sample at $z=0.5$ or $z=0.7$, but rather at $z=0.6$.
-We use Monte Carlo approach to infer the uncertainties of the values in the table, finding that the uncertainties are within $\pm 0.03$.
-}
-\end{deluxetable*}
-
 \begin{deluxetable*}{lcccc}
-%\tablenum{1}
 \tablecaption{Summary of the central offsets and scatters without noise\label{tab:sum_no_noise}}
@@
 \cline{2-4} 
-%  \cline{2-4}  \cline{5} \\
 \colhead{} &  \colhead{$0.2<z<0.4$} & \colhead{$0.4<z<0.6$} & \colhead{$0.6<z<0.8$} & \colhead{$1.2<z<1.7$}
@@
 Horizon-AGN & (0.19, 0.26) & (0.18, 0.21) & (0.28, 0.20)  & (0.37, 0.13) \\
-%Previous are ones not adding noise but same selection, belows are not add noise and not select
-%SAM & (0.75, 0.26) & (0.74, 0.26) & (0.94, 0.26)  & (0.59, 0.24) \\
-%MBII & (-0.24, 0.22) & \multicolumn{2}{c}{(-0.26, 0.22) [$z=0.6$]}  & (-0.29, 0.22)\\
-%Illustris & (-0.78, 0.40) & (-0.73, 0.40) & (-0.69, 0.40)  & (-0.55, 0.36) \\
-%TNG100 &  (0.33, 0.31) & (0.31, 0.32) & (0.29, 0.33)  & (0.22, 0.37) \\
-%TNG300 & (0.42, 0.58) & (0.40, 0.57) & (0.39, 0.56)  & (0.35, 0.54) \\
-%Horizon & (0.12, 0.30) & (0.13, 0.30) & (0.14, 0.28)  & (-0.00, 0.48) \\
 \enddata
@@
 \begin{deluxetable*}{lcccc}
-%\tablenum{1}
 \tablecaption{Summary of the p-value using KS test \label{tab:pvalue}}
@@
 \cline{2-4} 
-%  \cline{2-4}  \cline{5} \\
 \colhead{} &  \colhead{$z\sim0.3$} & \colhead{$z\sim0.5$} & \colhead{$z\sim0.7$} & \colhead{$z\sim1.5$}
 }
-%\decimalcolnumbers
 \startdata
@@
 
-\vspace{5mm}
-%\facilities{HST, HSC}
-
-%% Similar to \facility{}, there is the optional \software command to allow 
-%% authors a place to specify which programs were used during the creation of 
-%% the manuscript. Authors should list each code and include either a
-%% citation or url to the code inside ()s when available.
-
-%\software{astropy \citep{2013A&A...558A..33A,2018AJ....156..123A},  }
-
-%% Appendix material should be preceded with a single \appendix command.
-%% There should be a \section command for each appendix. Mark appendix
-%% subsections with the same markup you use in the main body of the paper.
-
-%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
-%% The equation counter will reset when it encounters the \appendix
-%% command and will number appendix equations (A1), (A2), etc. The
-%% Figure and Table counter will not reset.
-
-%\appendix
-
-%\section{Comparison of the observed mass function}\label{app:function}
-%Our comparison also provides the opportunity to compare the {\it observed} mass distribution of the BH mass and the stellar mass.
-The histogram distribution of the {\it observed} \mbh\ and \smass\ are shown in Figure~\ref{fig:MB_fun} and Figure~\ref{fig:Mstar_fun}, respectively.
-All the simulations have good agreements to the observed mass function, in terms of the standard derivation.
-However, focus on the central point of the distribution, the TNG100 and TNG300 give the best prediction, indicating that their parent sample are most similar to the HSC sample.
-\todo{Xuheng will talk with Jingjing and add more discussion to this part.}
-
-%\begin{figure*}
-%\centering
-%\begin{tabular}{c c}
-%%\vspace*{-0.2cm} 
-%{\includegraphics[height=0.35\textwidth]{MBH_dis_z03.pdf}}&
-%%\hspace*{-0.4cm} 
-%{\includegraphics[height=0.35\textwidth]{MBH_dis_z05.pdf}}\\
-%%\hspace*{-0.4cm} 
-%{\includegraphics[height=0.35\textwidth]{MBH_dis_z07.pdf}}&
-%%\hspace*{-0.4cm} 
-%{\includegraphics[height=0.35\textwidth]{MBH_dis_z15.pdf}}\\
-%\end{tabular}
-%\caption{\label{fig:MB_fun} 
-%Illustration of the histogram of the observed \mbh\ function.
-For MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$.
-Note that for sample at $z\sim1.5$, the selection cut on \mbh\ is used in the simulation, thus the distribution is almost flat.
-\todo{update hist format as Figure 4}
-%}
-%\end{figure*} 
-%
-%\begin{figure*}
-%\centering
-%\begin{tabular}{c c}
-%%\vspace*{-0.2cm} 
-%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z03.pdf}}&
-%%\hspace*{-0.4cm} 
-%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z05.pdf}}\\
-%%\hspace*{-0.4cm} 
-%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z07.pdf}}&
-%%\hspace*{-0.4cm} 
-%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z15.pdf}}\\
-%\end{tabular}
-%\caption{\label{fig:Mstar_fun} 
-%Illustration of the histogram of the observed MBH function. For MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$.
-%}
-%\end{figure*} 
 \bibliography{reference}{}
@@
 
-%% This command is needed to show the entire author+affiliation list when
-%% the collaboration and author truncation commands are used.  It has to
-%% go at the end of the manuscript.
-%\allauthors
-
-%% Include this line if you are using the \added, \replaced, \deleted
-%% commands to see a summary list of all changes at the end of the article.
-%\listofchanges
-
 \end{document}
-
-% End of file `sample631.tex'.

### 2022-02-06 projects/2020_HSC_to_numerical_simulation/offset_plot.py

@@ -16,7 +16,7 @@ from scipy import stats
 import matplotlib as mat
 mat.rcParams['font.family'] = 'STIXGeneral'
 
-zs = 1.5
+zs = 0.7
 files = glob.glob("offset_result/*{0}.txt".format(zs))
 if zs == 0.5 or zs == 0.7:
     files = files+glob.glob("offset_result/*{0}.txt".format(0.6))
@@ -55,7 +55,7 @@ for i in [3,2,1,4,5,0]:
               linewidth = 14,alpha = 0.8,
                color = colors[ct+1])
     axs[ct+1].set_yticks([])
-    if zs == 0.3:
+    if zs == 0.3 or zs == 0.7:
         axs[ct+1].set_ylabel(label, fontsize = 20)#, rotation=0)
         axs[0].set_ylabel('Obs.', fontsize = 20)
     axs[ct+1].plot([obs_mean,obs_mean], [0, 2], linewidth = 3,color = colors[0])

### 2022-02-22 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
To modify the paper

@@
 %\documentclass[linenumbers]{aastex631}
+%\documentclass[twocolumn, linenumbers]{aastex631}
 \documentclass[twocolumn]{aastex631}
@@
 \newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
+\newcommand{\jshi}[1]{\textcolor{orange}{#1}}
 \newcommand{\blue}[1]{\textcolor{blue}{#1}}
+\newcommand{\yo}[1]{\textcolor{purple}{[{\bf Yohan}: #1]}}
+\newcommand{\red}[1]{\textcolor{purple}{#1}}
 
@@
 
+\newcommand{\aklant}[1]{\textcolor{blue}{#1}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %% this information may be modified by the editorial offices.
-\shorttitle{Simulation comparison}
+\shorttitle{Comparing simulations and observations of black hole - galaxy relations}
 \shortauthors{Ding et al.}
@@
 
-\title{The Black Hole and Galaxy coevolution at $0.2<z<1.7$ using extensive comparisons between observation and simulation}
+\title{Concordance between observations and simulations in the evolution of the mass relation between supermassive black holes and their host galaxies}
 
@@
 \affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
-
-\author[0000-0002-1605-915X]{Junyao Li}
-\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
-\affiliation{CAS Key Laboratory for Research in Galaxies and Cosmology, Department of Astronomy, University of Science and Technology of China, Hefei 230026, China}
-\affiliation{School of Astronomy and Space Science, University of Science and Technology of China, Hefei 230026, China}
 
@@
 
-\author{Friends}
+\author[0000-0002-1605-915X]{Junyao Li}
+\affiliation{CAS Key Laboratory for Research in Galaxies and Cosmology, Department of Astronomy, University of Science and Technology of China, Hefei 230026, China}
+\affiliation{School of Astronomy and Space Science, University of Science and Technology of China, Hefei 230026, China}
 \affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
 
-%% Mark off the abstract in the ``abstract'' environment. 
+\author[0000-0002-7080-2864]{Aklant K. Bhowmick}
+\affiliation{Dept. of Physics, University of Florida, Gainesville, FL 32611, USA}
+
+\author[0000-0002-4096-2680]{Nicola Menci}
+\affiliation{INAF Osservatorio Astronomico di Roma, via Frascati 33, I-00078 Monteporzio, Italy}
+
+\author[0000-0002-3216-1322]{Marta Volonteri}
+\affiliation{Institut d'Astrophysique de Paris, Sorbonne Universit\'e, CNRS, UMR 7095, 98 bis bd Arago, 75014 Paris, France}
+
+\author[0000-0002-2183-1087]{Laura Blecha}
+\affiliation{Dept. of Physics, University of Florida, Gainesville, FL 32611, USA}
+
+\author[0000-0002-6462-5734]{Tiziana Di Matteo}
+\affiliation{McWilliams Center for Cosmology, Dept. of Physics, Carnegie Mellon University, Pittsburgh, PA 15213, USA}
+
+\author[0000-0003-0225-6387]{Yohan Dubois}
+\affiliation{Institut d'Astrophysique de Paris, Sorbonne Universit\'e, CNRS, UMR 7095, 98 bis bd Arago, 75014 Paris, France}
+
 \begin{abstract}
-We carry out a direct comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies (\mbh -- \smass) at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN,  TNG and semianalytic model).
-The observational measurements consistent of 612 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter.
-To make the fair comparisons, we first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as that based on observations.
-Our analysis demonstrates that all simulations predict a comparable level of dispersion of the scaling relations up to $z\sim1.7$, even after consideration of observational uncertainties which are non-negligible.
-%We also find that the selection criteria for the $z<1$ do not produce strong effects on the simulated relation
-%Thus, the original relations (i.e., before adding noise) predicted by the simulation are supposed to have consistent intrinsic scatter compared with the observational data. 
-%Considering that the tight relation of the scaling relation is highly rely on the AGN feedback, our results support the hypothesis of the AGN feedback being responsible for a causal link between the BH and its host galaxy, resulting in a tight correlation between their respective masses.
-Hence, our results support the hypothesis that AGN feedback plays a role in a causal link between the BH and its host galaxy, resulting in a non-evolving and tight correlation between their respective masses.
-\todo{Mentioning the central comparison.}
+We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies (\mbh -- \smass) at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model).
+The observed sample consist of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter.
+To make fair comparisons, we first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations.
+Over the full redshift range, our analysis demonstrates that all simulations predict a level of intrinsic scatter of the scaling relations comparable to the observations which appear to agree with the dispersion of the local relation.
+Regarding the mean scaling relation, Horizon-AGN and TNG are in closest agreement with the observational data at both low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties.
+For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and thus closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow.
+The consistency in the dispersion with redshift in our analysis lends support to the importance of both quasar and radio mode feedback prescriptions in the simulations.
+Finally, we investigate evolution as a function of stellar and black hole mass, and argue that the most direct way to probe the co-evolution of galaxies and black holes is to increase the sensitivity, e.g., with JWST, thereby pushing to lower masses and minimizing possible biases arising from selection effects.
 
-%\todo{Add comments on the center positions. KS test. Estimation of the intrinsic scatter.}
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
+
 The close correlations between supermassive black holes and the properties of their host galaxies (e.g., stellar mass) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
-To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determin how and when the correlation emerges and evolves over cosmic time \citep[e.g.,][]{Peng2006a, Tre++07, Woo++08, Jahnke2009, Bennert11, Schramm2013, Park15, Mechtley2016, Ding2020, 2021arXiv210902751L}.
-While, an {\it apparent} evolution has been found in which the growth of BHs predates that of the host, equally as many studies claim a lack of evolution when considering the host total stellar mass.
-However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014}.
+To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over cosmic time \citep[e.g.,][]{Tre++04,Peng2006a, Tre++07, Woo++08, Jahnke2009, Bennert11, Schramm2013, Park15, Mechtley2016, Ding2020, 2021arXiv210902751L}.
+While, an {\it observed} evolution has been found in many studies in which the growth of BHs predates that of the host, other studies predict that BHs grow commensurately with galaxies.
+However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15}.
 
@@
 Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
-However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ as observed today.
+However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ compared to what is observed today.
 
-Numerical simulations provide an opportunity to further understand the origin of the connection between BHs and their host galaxies.
-For example, a comparison of scaling relations has been made between predictions by the state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and observational measurements at  $0.3<z<1$ based on HST imaging \citep[e.g., ][]{DeG++15}, which show a positive evolution (i.e., the mass growth of the BH growth predates that of its host).
-Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution, including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments suite of SPH simulations~\citep{Schaye2015}, Illustris moving-mesh simulation~\citep{Sijacki2015, Vogelsberger2014, Li2019} and the SIMBA simulation~\citep{Thomas2019}.
-In recent work, the BH populations from the six large-scale cosmological simulations have been adopted to compare the \mbh-\smass\ with observation of the local universe~\citep{Habouzit2021}.
-However, these comparison works are limited by the observation data in terms of the sample size ($<$100) and redshift range ($z<1$).
+Numerical simulations provide an opportunity to further understand the connection between BHs and their host galaxies.
+For example, a comparison of scaling relations has been made using state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and observational measurements at  $0.3<z<1$ \citep[e.g., ][]{DeG++15}, which show a positive evolution (i.e., the mass growth of the BH growth predates that of its host).
+Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution,
+including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH simulations~\citep{Schaye2015}, Illustris moving-mesh simulation~\citep{Sijacki2015, 2014MNRAS.444.1518V, Li2019} and the SIMBA simulation~\citep{Thomas2019}.
+In particular, the \mbh-\smass\ relation using BH populations using six large-scale cosmological simulations (i.e, Illustris, TNG100, TNG300, Horizon-AGN, EAGLE, and SIMBA) has been compared with observations in the local universe in a recent study~\citep{Habouzit2021}.
+However, these comparison works are limited by the observation data in terms of the sample size ($<$100) and redshift range (i.e., limited to the local universe).
 
@@
 A direct means to account for these is to apply the same effects and selection to the simulation products and make a forward comparison in the observational plane.
-In~\citet{Ding2020b}, a direct comparison has been performed using 32 X-ray-selected AGN at $1.2<z<1.7$ and a direct comparison with two state-of-the-art simulation efforts, including {\tt MassiveBlackII} (MBII) and a Semianalytic Model (SAM).
-The dispersion in the mass ratio between black hole mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) confirming the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.
+In~\citet{Ding2020b}, a direct comparison has been performed using 32 X-ray-selected AGN at $1.2<z<1.7$ and a direct comparison with two state-of-the-art simulation efforts, including {\tt MassiveBlackII} (MBII) and a Semi-analytic Model \citep[SAM,][]{Menci2014, Menci2016}.
+The dispersion in the mass ratio between black hole mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) favoring the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.
 
-In this study, we extend our previous work, comparing the observational measurements to that from simulations, by adding recent measurements of hundreds of SDSS quasar at $0.2<z<0.8$ based on wide and deep HSC imaging from the Strategic Subaru Program.
+In this study, we extend our previous work by adding recent measurements of hundreds of SDSS quasars at $0.2<z<0.8$ based on wide and deep HSC imaging from the Strategic Subaru Program, and comparing the observational measurements with that from simulations.
 Furthermore, we extend the simulated quasar populations by including MBII, SAM, Illustris, TNG100, TNG300 and Horizon-AGN.
 This paper is structured as follows.
-In Sections~\ref{sec:observations} and~\ref{sec:simulations}, we describe our observation and simulation sample.
-The direct comparison is performed and the result is presented in Section~\ref{sec:result}.
+In Sections~\ref{sec:observations} and~\ref{sec:simulations}, we describe our observed and simulated samples.
+A direct comparison is performed and the result is presented in Section~\ref{sec:result}.
 The concluding remarks are presented in Section~\ref{sec:con}.
-
-%\section{Comparison Sample: Observations and Simulations} \label{sec:sample}
-%The correlations of \mbh-\smass\ between the observed data and the numerical simulations are compared in this work. 
-%We introduce the comparison samples in this section, including the observational data and the numerical simulations.
 
@@
 \label{sec:observations}
-The observed sample consists of 900 uniformly-selected SDSS quasars at $0.2<z<0.8$, imaged by Subaru/HSC \citep{Li2021a}, and 32 quasars at $1.2<z<1.7$ as imaged by~\hst and described in \citep[][hereafter D20]{Ding2020}.
+The observed sample consists of 646 uniformly-selected SDSS quasars at $0.2<z<0.8$, imaged by Subaru/HSC \citep{Li2021a}, and 32 quasars at $1.2<z<1.7$ as imaged by~\hst~\citep[][hereafter D20]{Ding2020}.
 The latter are selected from three deep-survey fields, namely COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008}.
@@
 
-\subsection{HSC}\label{sec:hsc}
+\subsection{SDSS/HSC sample}\label{sec:hsc}
 A sample of $\sim$5000 type-1 SDSS quasars from the DR14 catalog~\citep{Paris2018} at $0.2<z<1$ has been imaged by the high-resolution Subaru Strategic Program (SSP) wide area survey~\citep{Aihara2019} using Hyper Suprime-Cam~\citep{Miyazaki2018}.
@@
 
-To avoid any potential biases related to the selection of the quasars, \citet[][hereafter, L21b]{2021arXiv210902751L} isolated 877 sources which are uniformly selected based on their PSF-magnitudes, color cuts using single-epoch SDSS photometry and the value of the measured \smass.
+To avoid any potential biases related to the selection of the quasars, \citet{2021arXiv210902751L} isolated 877 sources which are uniformly selected based on their PSF-magnitudes, color cuts using single-epoch SDSS photometry and the value of the measured \smass.
 Specifically, we use the {\it ugri} color-selected sample (228 sources) from SDSS I/II~\citep{Richards2002}, and the CORE sample from SDSS BOSS (408 sources) and eBOSS (241 sources) surveys~\citep{Ross2013, Myers2015} (hereafter the uniform sample).
 These samples are initially selected based on PSF-magnitude cuts of $15 < i < 19.1$ (for {\it ugri}), and $i > 17.8$ and $g, r < 22.0$ (for CORE).
-Finally, a limit on \smass\ is set to assure the detection of the host, especially since the rate and accuracy of detection is higher when \smass\ is increasing.
+Furthermore, a limit on \smass\ is set to assure the detection of the host, especially since the rate and accuracy of detection is higher when \smass\ is increasing, resulting in a final sample of 646 quasars.
 These selections will be adopted in an equivalent manner to the simulated samples to mitigate selection effects thus allowing the fair comparison.
 
-\subsection{HST}
+\subsection{HST sample}
 
@@
 These best-fit models are used to estimate the stellar masses of the host galaxies.
-\mbh\ is determined by \citet{Schulze2018} using near-infrared spectroscopic observations of the broad \halpha\ emission line with the recipe provided by~\citep{Vestergaard2006}, in a consistent manner to that adopted for HSC sample.
+\mbh\ is determined by \citet{Schulze2018} using near-infrared spectroscopic observations of the broad \halpha\ emission line with the recipe provided by~\citet{Vestergaard2006}, in a consistent manner to that adopted for HSC sample.
 We refer the reader to D20 for a more detailed description of the analysis.
 
-With a consistent approach, the measurements of the \mbh-\smass\ relations for the HST and HSC samples are obtained.
+The measurements of the \mbh-\smass\ relations for both the HST and HSC samples are obtained with a consistent approach.
 Thus, we expect the measurement errors of these two samples to be at a comparable level (i.e., $\Delta$\mbh$=0.4~$dex, $\Delta$\smass$=0.2~$dex).
-Indeed, the two samples are consistent with a lack of evolution in the mass ratio (see Figure 6 of L20b), even though the sample selection is slightly different.
+Indeed, the two samples are consistent with a lack of evolution in the mass ratio~\citep[see Figure 6 of][]{2021arXiv210902751L}, even though the sample selection is slightly different.
 
-\section{Simulations}
+\begin{deluxetable*}{lccccc}
+\tablecaption{Key characteristics of hydrodynamic simulations used in this study.\label{tab:sim_sum}}
+\tablewidth{0pt}
+\tablehead{
+\colhead{Simulation} & MBII & Illustris &  TNG100 & TNG300 & Horizon-AGN
+}
+\startdata
+box sizes $(\mathrm{cMpc})^3$  & $142.7^3$ & $(106.5)^3$ & $(111)^3$ & $(302)^3$ & $(142)^3$ \\
+particles  & $2\times1792^3$ & $2\times1820^3$ & $2\times1820^3$ & $2\times2500^3$ & $\sim2\times1024^3$ \\
+\cline{1-6}
+{\bf mass resolution} \\
+ dark matter &$1.57\times10^7$ & $6.26\times10^6$ & $7.5\times10^6$ & $5.9\times10^7$ & $8\times10^7$ \\
+ baryonic matter &$3.14\times10^6$ & $1.26\times10^6$ & $1.4\times10^6$ & $1.1\times10^7$ & $2\times10^6$ \\
+\cline{1-6}
+{\bf AGN feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ radiative efficiency)} \\
+High acc. mode & 0.05 $\times$ 0.1 & 0.05 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.15 $\times$ 0.1 \\
+Low acc. mode  & -- & 0.35 $\times$ 0.2 & $\leq0.2 \times$ 0.2 & $\leq0.2 \times$ 0.2 & 1 $\times$ 0.1 \\
+Transitions btw. modes & -- & 0.05 & \multicolumn{2}{c}{min[$2\times10^{-3}(\frac{M_{\rm BH}}{10^8M_{\odot}})^2$, 10\%]} & 0.01 \\
+\cline{1-6}
+AGN fueling mechanism   & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ & $\alpha \dot{M}_{Bondi}$ & $\dot{M}_{Bondi}$&$\dot{M}_{Bondi}$ & $\alpha\dot{M}_{Bondi}$ \\
+maximum accretion rate & 2 $\times$Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate\\
+\enddata
+\tablecomments{In the penultimate row, $\alpha$ is the boost factor.
+For Illustris, $\alpha = 100$; for Horizon-AGN, $\alpha =$ max$[(\rho/\rho_0)^2, 1]$.
+$\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$.
+}
+\end{deluxetable*}
+
+\section{Simulations and comparison strategy}
 \label{sec:simulations}
-We introduce the simulation sample that adopted in this section. All the simulation are based on the larger-scale cosmological simulations, except the Semianalytic Model (SAM) simulation.
-%\todo{Maybe we can also summarize the importance of AGN feedback somewhere here?}
+We introduce the simulation samples that are adopted in this section.
+All the simulation are based on the larger-scale cosmological simulations, except the Semianalytic Model (SAM) simulation (see Section~\ref{subsec:SAM}).
+In Table~\ref{tab:sim_sum}, we summarized the key elements for each hydrodynamic simulation being considered.
 
-\subsection{{\tt MassiveBlackII} (MBII)}
-MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $100~\mathrm{cMpc/h}$ and $2\times1792^3$ particles.
+\subsection{{\tt MassiveBlackII} (MBII)}\label{subsec:MBII}
+MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $(142.7~\mathrm{cMpc})^3$
+and $2\times1792^3$ particles.
 The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}.
-For dark matter and gas, the elements of the masses resolution are $1.1\times 10^7~M_{\odot}/h$ and $2.2\times 10^6~M_{\odot}/h$, respectively.
-The simulation includes a full modeling of gravity plus gas hydrodynamics, with a wide range of subgrid recipes to model the star formation~\citep{2003MNRAS.339..289S}, BH growth, and the feedback process.
+The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}.
+For dark matter and gas, the mass resolutions are $1.57\times 10^7~M_{\odot}$ and $3.14\times 10^6~M_{\odot}$, respectively.
+The simulation includes a full modeling of gravity plus gas hydrodynamics, with a wide range of subgrid recipes to model the star formation~\citep{2003MNRAS.339..289S}, BH growth, and the feedback process~\citep{2005Natur.433..604D}.
 Halos were identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}.
 Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}.
-The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}, i.e., $\Omega_0=0.275$, $\Omega_l=0.725$, $\Omega_b=0.046$, $\sigma_8=0.816$, $h = 0.701$, $n_s=0.968$.
 
-To model the growth of BH, a feedback prescription is adopted as detailed in the literature~\citep{2005Natur.433..604D, 2005MNRAS.361..776S}.
-In particular, the BH seed with mass $5\times 10^{5}~M_{\odot}/h$ are embedded into halos of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$.
+To model supermassive black holes, a BH seed with mass $5\times 10^{5}~M_{\odot}/h$ are inserted into halos of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$.
 Once seeded, BH growth via gas accretion is assigned at a rate of $\dot{M}_{BH}={4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the interstellar medium (ISM) gas at cold phase; $v_{BH}$ is the relative velocity between the BH and its surrounding gas.
+Note that unlike several previous works, the accretion rate in MBII adopt the prescription in~\citet{Pelupessy2007} which does not include any artificial boost factor.
 The accreted gas is released as radiation at a radiative efficiency of 10\%.
-A fraction of 5\% of the radiated energy couples to the surrounding gas as black hole (or AGN) feedback~\citep{2005Natur.433..604D}.
-A mildly super-Eddington (two times Eddington rate) is allowed; however, unlike some previous work, the accretion rate in MBII adopt the prescription in~\citet{Pelupessy2007}, which does not include any artificial boost factor.
-Two BH are considered to be merged when their separation distance is below the simulation spatial resolution (i.e., the SPH smoothing length) and their relative speeds are lower than the local sound speed of the medium.
-
-For the galaxy photometry, the initial SEDs of the BH host galaxies were determined by combining all the contributions from the overall start particles.
-The stellar SEDs were derived using the PEGASE-2~\citep{1999astro.ph.12179F} stellar population synthesis code with a Salpeter IMF.
-Finally, the galaxy SEDs are  cooperated with the desired filter response to obtain the broadband photometry (e.g., SDSS $r$-band magnitude).
+A fraction of 5\% of the radiated energy thermally couples to the surrounding gas as black hole (or AGN) feedback~\citep{2005Natur.433..604D}.
+A mildly super-Eddington (two times Eddington rate) is allowed.
+Due to resolution limitations, BH dynamics cannot be self-consistently modeled in the simulations.
+Two BHs are considered to be merged when their separation distance is below the simulation spatial resolution (i.e., the SPH smoothing length) and their relative speeds are lower than the local sound speed of the medium.
 
 As a common practice, the stellar mass is obtained by using a 3D spherical aperture of 30~kpc to represent the observed stellar mass.
-By this definition, it has been tested that the corresponding stellar mass function is consistent with the observation measurement~\citep[e.g.,][]{Pillepich2018}.
-Even more, the stellar mass using this 3D aperture can achieve good agreement to those measured within Petrosian radii in observational studies~\citep{Schaye2015}.
+We adopt this definition of stellar masses for all simulations described in the following sections.
+Using this definition, \citet{Pillepich2018} has shown that the corresponding stellar mass function is consistent with the observational measure.
+Even more, the stellar mass using this 3D aperture can achieve good agreement to those measured within the Petrosian radii in observational studies~\citep{Schaye2015}.
+For further details of MBII simulation, we refer the reader to~\citet{Khandai2015}.
 
-For further details of MBII simulation, we refer the reader to~\citet{Khandai2015}
+\subsection{Illustris}
+The Illustris Project is another large scale hydrodynamics simulation, introduced in~\citet{2014MNRAS.444.1518V, 2014Natur.509..177V}.
+The simulation consist of a volume of (106.5 cMpc)$^3$~(slightly smaller than MassiveBlack II),
+and was run with the moving Voronoi mesh code {\tt Arepo}~\citep{2010MNRAS.401..791S} with a base cosmology adopted from WMAP9 results~\citep{2013ApJS..208...19H}.
+Besides gravity and gas hydrodynamics, the simulation calculates the astrophysical processes ~\citep{2013MNRAS.436.3031V, 2014MNRAS.438.1985T} that includes gas cooling and star formation~(with a density threshold of 0.13 cm$^{-3}$, \citealt{2003MNRAS.339..289S}), stellar evolution and chemical enrichment, kinetic stellar feedback by SNe activity, BH growth~(accretion and merging), and AGN feedback.
 
-\subsection{Semianalytic Model (SAM)}
-We highlight here the main points of the simulation with respect to our study; for more detail, a full descriptions of the SAM simulation sample can be found in~\citet{Menci2016} which is based on semianalytic model introduced in~\citet{Menci2014}.
-For dark matter halos that merge with a larger halo, the impact of dynamical friction is assessed to define whether the halo will survive as a satellite or sink to the center of the dominant galaxy to increase its mass.
-The binary interactions (fly-by and merging), among satellite subhalos, are  also described by the model.
+BHs are seeded with an initial mass of $1 \times 10^5~M_{\odot}/h$ when a halo exceeds a mass of $5 \times 10^{10}~M_{\odot}/h$.
+BHs then grow via accretion described by the Eddington limited Bondi-Hoyle-Lyttleton formalism ($\alpha4\pi G^2M_{BH}^2 \rho/c_s^3$), as well as mergers with other BHs.
+The boost factor $\alpha=100$ is introduced to account for the unresolved multiphase ISM~\citep{Springel2005, 2009MNRAS.398...53B}, which is otherwise expected to underestimate the density around the BHs.
+Lastly, accreting black holes radiate with a bolometric luminosity given by $\epsilon_r \dot{M}_{BH}c^2$, where $\dot{M}_{BH}$ is the mass accretion rate and $\epsilon_r=0.2$ is the radiative efficiency.
+
+The AGN feedback consists of three components, namely quasar-mode, radio-mode and radiative feedback.
+In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy.
+For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at~(irregular) intervals between which the BH mass grows by a fixed fraction.
+The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{bh} c^2$ where $\delta M_{bh}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency.
+Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN.
+As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy stellar mass, assuming a \cite{2003PASP..115..763C} IMF.
+
+\subsection{IllustrisTNG}
+{\it The Next Generation Illustris Simulations} (IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes.
+It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modeling, and 3) addressing the identified shortcomings of the previous generation simulations.
+
+The TNG100 and TNG300 have a volume of (100~cMpc)$^3$ and (300~cMpc)$^3$, respectively. The adopted cosmological parameters are updates by the Planck result~\citep{2016A&A...594A..13P}.
+The gas cooling and star formation prescriptions are broadly similar to the Illustris model.
+However significant updates have been made to the stellar feedback model~(more details in \citealt{2018MNRAS.473.4077P}).
+BH seeds with initial mass of $8 \times 10^5 M_{\odot}/h$ are placed in Dark matter halos with a mass exceeding $5 \times 10^{10} M_{\odot}/h$.
+Notably, the seed mass is one order of magnitude higher than in the Illustris simulation.
+The BH accretion also follows the Bondi-Hoyle-Lyttleton formalism, but without any boost factor~(unlike Illustris).
+Accreting black holes release energy with a radiative efficiency of 0.2~(same as Illustris).
+The inclusion of the magnetic fields can affect the relationship between the BHs and their host galaxies properties; the \mbh-\smass\ mean relation is higher with magnetic fields~\citep{2018MNRAS.473.4077P}.
+
+The AGN feedback occurs in thermal, radio, and radiative modes.
+For high accretion rates, the feedback implementation is the same as Illustris i.e., thermal energy is injected in the surroundings of the accreting BHs.
+However, at low accretion rates, the feedback implementation is substantially different from Illustris.
+Instead of releasing hot bubbles, this feedback mode in TNG is purely kinetic.
+In particular, there is a directional injection of momentum along a randomly chosen direction~\citep{2017MNRAS.465.3291W, 2018MNRAS.479.4056W} at irregular intervals.
+The transition between the two feedback modes is also different from Illustris, and is set by the minimum value of 0.1 and $2 \times 10 ^{-3} \times (M_{BH} / 10^8~M_{\odot})$.
+Additionally, the radiative feedback implemented in Illustris~(summarized in the previous section) is also present in TNG.
+Lastly, the galaxy stellar mass in Illustris-TNG is obtained in a similar manner to that of Illustris.
+
+\subsection{Horizon-AGN}\label{subsec:Horizon}
+The simulation Horizon-AGN~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D} has a volume of 142 cMpc$^3$ and was generated using the adaptive mesh refinement code {\tt Ramses}~\citep{2002A&A...385..337T} with a $\Lambda$CDM model based on WMAP7~\citep{2011ApJS..192...18K} cosmological results.
+The dark matter particle mass is $8\times 10^7 M_{\odot}$.
+The stellar particle mass is $2\times 10^6 M_{\odot}$ and the MBH seed mass is $10^5 M_{\odot}$.
+Adaptive mesh refinement is permitted down to $\Delta x=1$~kpc, and, if the total mass in a cell becomes greater than 8 times the initial mass resolution, it is performed in a quasi-Lagrangian manner.
+Collisionless particles (dark matter and star particles) are evolved using a particle-mesh solver with a cloud-in-cell interpolation.
+
+The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation with a constant star formation efficiency $\epsilon_*=0.02$, which occurs in regions where the gas number density exceeds the star formation threshold $n_0 = 0.1\,\rm H\, cm^{-3}$.
+A Salpeter IMF is assumed.
+Stellar feedback is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources.
+
+Differing from simulations presented above, Horizon-AGN does not use a fixed threshold in the dark matter halo mass to seed BHs.
+BHs are seeded with a mass of $10^5 M_\odot$ in cells, with gas density above $n_0$ and stellar velocity dispersion larger than $100 \,\rm km\,s^{-1}$.
+An exclusion radius is imposed so that no BH seed is formed at less than 50 ckpc from an existing BH.
+After $z = 1.5$, new BHs are prevented from forming.
+At these subsequent times, all the progenitors of the \smass$>10^{10} M_{\odot}$ galaxies at $z = 0$ should be formed and seeded with BHs~\citep{2016MNRAS.460.2979V}.
+BH accretion is computed using the Bondi-Hoyle-Lyttleton formalism with a boost factor $\alpha = (\rho/\rho_0)^2$ when the density $\rho$ is higher than the resolution-dependent threshold $\rho_0$.
+Otherwise, the boost factor is fixed as unity~\citep{2009MNRAS.398...53B}.
+
+Horizon-AGN includes two modes of AGN feedback.
+In the quasar mode ($f_{\rm Edd}>0.01$), thermal energy is isotropically released within a sphere of radius a few resolution elements.
+The energy deposition rate is $\dot{E}_{\rm AGN} = 0.015 \dot{M}_{\rm BH} c^2$.
+In the radio mode, energy is injected into a bipolar  outflow  with  a  velocity  of  $10^4\,\rm km\,s^{-1}$, to  mimic the  formation  of  a  jet.
+The  energy  rate  in  this  mode is $\dot{E}_{\rm AGN} = 0.1 \dot{M}_{\rm BH} c^2$.
+The  technical  details  of  BH  formation,  growth  and AGN  feedback  modeling  of  Horizon-AGN  can be found in~\citet{2012MNRAS.420.2662D}.
+
+We identify galaxies applying the AdaptaHOP structure finder \citep{Aubert+04,Tweed+09} to the star particle distribution.
+Galaxies are identified using a local threshold of 178 times the average matter density, with the local density of individual particles calculated using the 20 nearest neighbours.
+Only galaxies with more than 50 particles are considered.
+The galaxy mass corresponds to the total stellar mass of a galaxy identified with this approach.
+The stellar mass function is shown in \cite{2017MNRAS.467.4739K} to be in good agreement with observations.
+
+\begin{figure}
+\centering
+\includegraphics[height=0.37\textwidth]{OpeningAngle.pdf}
+\caption{\label{fig:SAM} 
+Total gas content of galaxies as a function of AGN bolometric luminosity and jet opening angle in a new AGN feedback model incorporated into the SAM simulation.
+}
+\end{figure}
+
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+{\includegraphics[trim = 0mm 0mm 65mm 10mm, clip, height=0.4\textwidth]{HSC_selection_MBII.png}}
+{\includegraphics[trim = 0mm 0mm 20mm 10mm, clip,height=0.4\textwidth]{HST_selection_MBII.png}}
+\end{tabular}
+\caption{\label{fig:selection}Demonstration of AGN selection using MBII.
+{\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles).
+A matched HSC sample is shown by the orange data points.
+The light green background cloud shows the {\it intrinsic} simulated number density in this parameter space.
+{\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample.
+For visual comparison between the HSC and HST selection, we show the region of the HST selection window in the left panel as dashed lines.
+}
+\end{figure*}
+
+\subsection{Semi-analytic Model (SAM)}\label{subsec:SAM}
+We highlight the main points of the simulation with respect to our study; for more detail, a full description of the SAM can be found in~\citet{Menci2016} which is based on an earlier semi-analytic model introduced in~\citet{Menci2014}.
+The specific version adopted here differs from the one presented in the above papers since it implements a new, detailed description of AGN feedback, as discussed in detail below.
+
+For dark matter halos that merge with a larger halo, the impact of dynamical friction is assessed to define whether the halo will survive as a satellite or sink to the center of the dominant galaxy which increases its mass.
+The binary interactions (fly-bys and mergers), among satellite sub-halos, are  also described by the model.
 In each halo, we compute the fraction of gas which cools because of the atomic processes and settles into a disk~\citep{Mo1998}.
-The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr, according to BH feeding; (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulating star formation (as well as BH accretion).
+The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr, according to BH feeding; (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion).
 The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation which returns a fraction of the disk gas into a hot phase.
 A Salpeter IMF is adopted in the SAM simulation.
+A $\Lambda$CDM power spectrum of perturbations with a total matter density parameter $\Omega_0=0.3$, a baryon density parameter
+$\Omega_b=0.04$, a dark energy density parameter $\Omega_\Lambda=0.7$, and a Hubble constant $h$=0.7 is adopted.
 
-The BHs primordial seeds are assumed to originate from PopIII stars with a mass $M_{seed}=100\,M_{\odot}$~\citep{Madau2001}, and to be initially present in all galaxy progenitors.
-The BH accretion is based on interactions feeding mode and disk instabilities feeding mode.
-%\newline(1)~{\it triggered by interactions.} The interaction rate $\tau_r^{-1}=n_T\,\Sigma (r_t,v_c,V)\,V_{rel} (V)$ for galaxies with relative velocity $V_{rel}$ and number density $n_T$ in a common DM halo determines the probability for encounters, either fly-by or merging, through the corresponding cross sections $\Sigma$ given in~\citet{Menci2014}.
-The fraction of gas destabilized in each interaction corresponds to the loss $\Delta j$ of orbital angular momentum $j$, and depends on the mass ratio of the merging partners $M'/M$ and on the impact factor $b$.
-%\newline(2)~{\it induced by disc instabilities.} We assume these to arise  in  galaxies with disc mass exceeding~\citep{Efstathiou1982} $M_{crit} =  {v_{max}^2 R_{d}/ G \epsilon}$ with $\epsilon=0.75$, where $v_{max}$ is the maximum circular velocity associated to each halo ~\citep{Mo1998}.
-Such a criterion strongly suppresses the probability for disc instabilities to occur not only in massive, gas-poor galaxies, but also in dwarf galaxies characterized by small values of the gas-to-DM mass ratios.
-The instabilities induce loss of angular momentum resulting into strong inflows that we compute following the description in~\citet{Hopkins2011}, recast and extended as in~\citet{Menci2014}.
-\todo{This part should be updated for the new SAM version?}
-A detailed treatment of AGN feedback is included, which is introduced in~\citet{Menci2008}. The assumption stems from the fast winds with velocity up to 
-$10^{-1}c$ observed in the central regions of AGNs~\citep{Chartas2002, Pounds2003}.
-The supersonic outflows compress the gas into a blast wave terminated by a leading shock front, which moves outward with a lower but still supersonic speed, and sweeps out the surrounding medium.
-The model follows in detail the expansion of the blast wave through the galaxy disk, and computes the fraction of gas expelled from the galaxy.
-~\citep[see, i.e.,][for the details.]{Menci2016}.
+{We assume BH seed $M_{seed}=100\,M_{\odot}$~\citep{Madau2001}  to be initially present in all galaxy progenitors at the initial redshift $z=15$.
+This constitutes an approximate way of rendering the effect of the collapse of PopIII stars.
+However, the detailed value of $M_{seed}$ has a negligible impact on the final BH masses as long as they remain in the range $M_{seed}=50-500\,M_{\odot}$.
+}
 
-\subsection{Illustris}
-The Illustris Project is a serise of larger-scale hydrodynamical simulations of galaxy formation which was introduced in~\citet{2014MNRAS.444.1518V, 2014Natur.509..177V}.
-The simulation consist of a volume of (106.5 cMpc)$^3$, and was run with the moving Voronoi mesh code {\tt Arepo}~\citep{2010MNRAS.401..791S}.
-Besides gravitational force and hydrodynamical fluxes, the simulation calculates the astrophysical process known to be crucial for galaxy formation~\citep{2013MNRAS.436.3031V, 2014MNRAS.438.1985T}, which includes gas cooling, a subresolution ISM model, stochastic SF with a density threshold of 0.13 cm$^{-3}$, stellar evolution, gas recycling, chemical enrichment, kinetic stellar feedback by SNe activity, BH activity (accretion and merging), and AGN feedback.
-A cosmological background consistent with WMAP9~\citep{2013ApJS..208...19H} and a Chabrier IMF is adopted.
+The BH accretion is based on both interaction-driven and disk instability feeding modes.
+The SAM adopted here implements a new and improved  model for the AGN feedback with respect to the previous versions~\citep{Menci2008}.
+In both versions, the basic assumption is that fast winds with velocity up to $10^{-1}c$ observed in the central regions of AGNs~\citep{Chartas2002, Pounds2003}  result in  supersonic outflows that compress the gas into a blast wave terminated by a leading shock front.
+This  moves outward with a lower but still supersonic speed, and sweeps out the surrounding medium.
+However, while in the earlier version of the SAM~\citep{Menci2016} the blast wave is assumed to expand into an isotropically distributed medium, in the new description of AGN feedback~\citep{Menci2019} the full two-dimensional structure of the gas disc and of the expanding blast wave is followed in detail.
+The main physical difference is that in the new model the large density of gas along the plane of the disc causes the blast wave expansion to stall in such a direction, while it expands with large velocities in the vertical direction.
+The resulting strong dependence of the total (integrated over directions) outflow rate on the AGN luminosity $L_{AGN}$ and on the gas content of the galaxy $M_{gas}$ is shown in Figure~\ref{fig:SAM}.
+Such a new AGN feedback model has been tested in detail against a state-of-the-art compilation of observed outflows in 19 galaxies with different measured gas and dynamical masses~\citep{Fiore2017}, allowing for a detailed, one-by-one comparison with the model predictions.
+This well tested AGN feedback model allowed us to derive, for each simulated galaxy in the SAM,  the outflow expansion and the mass outflow rates in different directions with respect to the plane of the disc.
 
-The BH seeding in the simulation is based on DM halo mass -- when a halo reaching a mass of $7.10 \times 10^{10} M_{\odot}$ is inserted with a BH with initial mass of $1.42 \times 10^5 M_{\odot}$.
-Then, the BH accretion follows the Bondi-Hoyle-Lyttleton formalism ($\alpha4\pi G^2M_{BH}^2 \rho/c_s^3$), but capped at the Eddington limit.
-The boost factor $\alpha$ is introduced to compensate that the ISM multiphase structure is unresolved~\citep{Springel2005, 2009MNRAS.398...53B}, since simulation usually underestimate the density around a BH.
-
-The AGN feedback consists of three components: thermal quasar-mode feedback; thermal-mechanical radio-mode feedback; and radiative feedback.
-Through these process, the AGNs are able to deposit thermal energy into their surroundings with a coupling efficiency of 0.05 in for BHs with low Eddington ratio (i.e., $f_{\rm Edd} < 0.05$).
-For BHs with $f_{\rm Edd} > 0.05$, the thermal energy is released in hot bubbles with a radius of $\sim$ 100~kpc and couple to the gas with an efficiency of 0.35.
-It is highlighted in ~\citet{2014MNRAS.444.1518V} that the AGN feedback is the key process in quenching massive galaxy which is crucial to reproduce a tight stellar mass and BH mass relation.
-
-\subsection{IllustrisTNG}
-{\it The Next Generation Illustris Simulations} (IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018} are an ambitious suite of hydrodynamical simulations of galaxy formation in large cosmological volumes.
-It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modelling, and 3) addressing the identified shortcomings of the previous generation simulations.
-
-The TNG100 and TNG300 have a volume of (111~cMpc)$^3$ and (302~cMpc)$^3$, respectively.
-They use the same initial condition with the previous Illustris simulation.
-The adopted cosmological parameters are updates by the Planck result~\citep{2016A&A...594A..13P}.
-Dark matter halos with a mass exceeding $7.38 \times 10^{10} M_{\odot}$ are seeded in their center using BHs with initial mass as $1.18 \times 10^6 M_{\odot}$, one order of magnitude higher than the assumptions in the previous Illustris simulation.
-The BHs accretion also follows the Bondi-Hoyle-Lyttleton formalism, but without any boost factor.
-The assumption of the magnetic fields can affect the relationship between the BHs and their host galaxies properties; the \mbh-\smass\ mean relation is higher with magnetic fields~\citep{2018MNRAS.473.4077P}.
-The TNG simulation also employs a kernel-weighted accretion rate over about 256 neighboring cells.
-Thus, the TNG BH can build up correlation with the gas properties in the galaxy central region.
-
-TNG includes a two-mode AGN feedback: for high accretion rates -- injection of thermal energy in the surroundings of the BHs accreting; for low accretion rates -- directional injection of momentum with random direction~\citep{2017MNRAS.465.3291W, 2018MNRAS.479.4056W}.
-The transition between two modes is set by the minimum value of 0.1 and $2 \times 10 ^{-3} \times (M_{BH} / 10^8/M_{\odot})$.
-
-\subsection{Horizon-AGN}
-The simulation of Horizon-AGN~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D} has a volume of (142 cMpc)$^3$ which was generated based on the adaptive mesh refinement code {\tt Ramses}~\citep{2002A&A...385..337T} with a $\Lambda$CDM model based on WMAP7~\citep{2011ApJS..192...18K} cosmological results.
-The total volume contains $1024^3$ DM particles, corresponding to a DM mass resolution of $8 \times 10^7  M_{\odot}$  and initial gas resolution of  $1\times10^7M_{\odot}$.
-A Salpeter IMF is assumed in Horizon-AGN simulation.
-
-Different from the previous simulations, Horizon-AGN uses a fixed threshold in the dark matter halo mass.
-Star formation occurs in regions with gas number density exceeds the star formation threshold $n_0 = 0.1$.
-The BHs also form in this dense gas cells with stellar velocity dispersion larger than 100 km/s.
-BH seeds are not formed when they are closer than 50 ckpc of an existing BH.
-After $z = 1.5$, BHs are prevented from forming.
-At that time, all the progenitors of the \smass$>10^{10} M_{\odot}$ galaxies at $z = 0$ should be formed and seeded with BHs~\citep{2016MNRAS.460.2979V}.
-Horizon-AGN simulation also include the feedback from stellar winds, SNe Type Ia and Type II with mass, energy and metal release.
-
-The BH accretion is computed using the Bondi-Hoyle-Lyttleton formalism with a boost factor $\alpha = (\rho/\rho_0)^2$ when the density $\rho$ is higher than the resolution-dependent threshold $\rho_0$.
-Otherwise, the boost factor is fixed as unity~\citep{2009MNRAS.398...53B}.
-
-Horizon-AGN includes a two mode AGN feedback.
-In the high state mode ($f_{\rm Edd}<0.01$), thermal energy is isotropically released within a sphere of radius a few resolution elements.
-The energy deposition rate is $\dot{E}_{\rm AGN} = 0.015 \dot{M}_{\rm BH} c^2$.
-In the low state mode, energy is injected into a bipolar  outflow  with  a  velocity  of  10$^4$ km/s,  to  mimic the  formation  of  a  jet.
-The  energy  rate  in  this  mode is $\dot{E}_{\rm AGN} = 0.1 \dot{M}_{\rm BH} c^2$.
-The  technical  details  of  BH  formation,  growth  and  feedback  modeling  of  Horizon-AGN  can be found in~\citet{2012MNRAS.420.2662D}
-
-%Horizon-AGN  employs  a  kinetic  SN  feedback,  including momentum, mechanical energy and metals from type~II, Type  Ia  SNe,  and  stellar  winds  (details  in  Kaviraj  et  al.2017).
-The  feedback  is  modelled  as  kinetic  release  of  energy on timescale below 50 Myr, and a thermal energy after 50 Myr.
-The feedback is also pulsed, meaning that energy is accumulated until sufficient to propagate the blast wave to  at  least  two  cells.
-The  energy  released  depends  on  theSSP modeled assumed and the metallicity of the gas, and is aboute SN $\sim10^{49}$ erg/$M_{\odot}$.
-
-We summarized some key elements in the simulation in Table~\ref{tab:sim_sum}.
-
-\begin{deluxetable*}{lcccccc}
-%\tablenum{1}
-\tablecaption{Summary of some key assumptions for the hydrodynamic simulations analyzed by this work.\label{tab:sim_sum}}
-\tablewidth{0pt}
-\tablehead{
-%\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
-%  \cline{2-4}  \cline{5} \\
-\colhead{Simulation} & \colhead{box sizes} & particles &  \colhead{resolution} & \colhead{feedback prescription} & \colhead{AGN fueling mechanism}  & what else?
-}
-\startdata
-%SAM & \\
-MBII & $100~\mathrm{cMpc/h}$ & $2\times1792^3$ &&& \\
-Illustris &&&&& \\
-TNG100 &&&&& \\
-TNG300 &&&&& \\
-Horizon-AGN &&&&& \\
-\enddata
-%\tablecomments{This table }
-\end{deluxetable*}
-
-\subsection{Application of observational selection effects}
+\subsection{Application of observational measurement error and selection effects}
 To make direct comparisons with observations, we add measurement errors and apply the equivalent selection to the simulated samples.
-We first inject random noise to the simulated catalog to mimic the scatter caused by the measurement error.
-As mentioned above, \smass\ and \mbh\ for HSC and HST samples are measured with a similar approach thus their uncertainty levels are expected to be equivalent.
+We first inject random noise to the simulated catalog to mimic the scatter caused by measurement error.
+As mentioned above, \smass\ and \mbh\ for HSC and HST samples are measured with a similar approach; thus their uncertainty levels are expected to be equivalent.
 We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = 0.17~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.
@@
 We then apply restrictions on the noise-injected simulation to mimic selection effects as present in the observational data.
-Since the HSC and HST samples have their own selection function, we apply different selection criteria to the simulation as follows.
-\begin{itemize}
+Since the HSC and HST samples have their own selection function, we apply different selection criteria to the simulation as follows:
 
- \item{}HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should be consistent with the \mbh-$L_{\rm bol}$ relation of the HSC sample.
+ HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should match the relationship between \mbh-$L_{\rm bol}$ as seen in the HSC sample.
 We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it top}).
 (2) The $i$-band magnitude of the AGN are bright (see Section~\ref{sec:hsc}).
-The specific selection is made as follows: for systems at $z<0.5$ and $z>0.5$, the AGN $i$-band magnitude are required to be brighter than 20.5 mag and 22.0 mag, respectively.
-Since the simulations do not provide the AGN observed magnitude, we adopt the simulated rest-frame magnitude or L$_{\rm 5100}$ and assume the quasar continuum as a single power-law with an index of $\alpha_\nu=-0.44$~\citep{2001AJ....122..549V} to calculate the observed $i$-band magnitude.
+The specific selection is made as follows: for systems at $z<0.5$ and $z>0.5$, the AGN $i$-band magnitude is required to be brighter than 20.5 mag and 22.0 mag, respectively.
+Since the simulations do not provide the observed AGN magnitude, we adopt a simulated rest-frame magnitude or L$_{\rm 5100}$ and assume the quasar continuum as a single power-law with an index of $\alpha_\nu=-0.44$~\citep{2001AJ....122..549V} to calculate the observed $i$-band magnitude.
  3)~Following the HSC selection, we require the \smass\ value to be above a certain level (according to their redshift) to assure an accurate measurement.
-Finally, the HSC sample is split into three redshift bins which are $0.2<z<0.4$, $0.4<z<0.6$, and $0.6<z<0.8$.
+Finally, the HSC sample is split into three redshift bins for making comparison which are $0.2<z<0.4$, $0.4<z<0.6$, and $0.6<z<0.8$.
 
-\item{}HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is same as the observational selection, see Figure~\ref{fig:selection}--{\it left} taken MBII as example.
+HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example).
 Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., between [7.7, 8.6] $M_{\odot}$).
 The HST sample covers the higher redshift range $1.2<z<1.7$, which is considered as a single redshift bin to make the comparison with the simulations at $z=1.5$.
-\end{itemize}
 
 \section{Results} \label{sec:result}
-\begin{figure*}
-\centering
-\begin{tabular}{c c}
-{\includegraphics[width=0.5\textwidth]{HSC_selection_MBII.png}} &
-{\includegraphics[width=0.45\textwidth]{HST_selection_MBII.png}}
-\end{tabular}
-%\caption{\label{fig:selection}Demonstration of the impact of AGN selection using MBII.
-{\it left}: Correlation between \mbh\ and %$L_{\rm bol}$ of the simulated HSC sample is used to set the selection window for the simulated sample.
-This region roughly bracket %the type-1 AGN sample.
-The light green background cloud shows the simulated number density distribution in this parameter space %which includes a random level of uncertainty to mimic observational measurement errors.
-{\it right}: Similar to the top plane -- %equivalent selection window adopted for the HST-observed and MBII simulated samples.
-%}
-\caption{\label{fig:selection}Demonstration of the impact of AGN selection using MBII.
-{\it left}: Distribution of \mbh\ and $L_{\rm bol}$ for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles).
-A matched HSC sample is shown by the orange data points.
-The light green background cloud shows the simulated number density distribution in this parameter space which includes a random level of uncertainty to mimic observational measurement errors.
-{\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample.
-The y-axis is now given as the Eddington ratio.}
-
-\end{figure*}
-
-In Figure~\ref{fig:comparsion}, we present the comparison of the scaling relation \mbh--\smass\ between the observations and the simulations.
-We use the local relation \mbh$=0.98$\smass$-2.56$ adopted by D20 (Chabrier based\footnote{Since different simulations adopt either the Chabrier or the Salpeter IMF, we will adopt the local relation and the \smass\ of the observation data based on the same IMF to ensure that the comparison with the observation data are self-consistent.}) as the fiducial to estimate relative offsets and dispersions.
-Different simulations are presented in each row and redshift intervals increase from left to right.
-For both the observational and simulated samples, the central offset and scatter of the scaling relation are estimated by the mean and the standard deviation of the \mbh\ residuals for each system\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the value remains the same.} (i.e., the offset to the local relation along the y-axis in Figure~\ref{fig:comparsion}).
-We summarize of these offset distributions based on each redshift bins, as shown in Figure~\ref{fig:offsets}.
-To visually inspect the comparison results, we show the offsets to the local relation (in terms of the $\Delta{\rm log}$\mbh) as a function of redshift (see Figure~\ref{fig:offsets_vz}, left). 
-The values for the central offset and scatter in each case are given in Table~\ref{tab:sum}.
+In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
+The local scaling relation adopted by D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is used as the fiducial relation to assess relative offsets and differences in dispersion.
+A different simulation is presented in each row and the redshift intervals increase from left to right.
+We note that TNG100 and TNG300 yield very similar comparison results, thus only TNG100 is presented in Figure~\ref{fig:comparsion}.
 
@@
 \centering
-\begin{tabular}{c c c c}
-\vspace*{-0.1cm} 
-{\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_SAM_zs_03.png}}&
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_SAM_zs_05.png}}&
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_SAM_zs_07.png}}&
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_SAM_zs_15.png}}\\
-\vspace*{-0.1cm} 
-{\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_MBII_zs_03.png}}&
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_MBII_zs_06.png}}&
-\hspace*{-0.5cm} &
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 30mm 29mm 80mm 25mm, clip, height=0.25\textwidth]{MM_MBII_zs_15.png}}\\
-\vspace*{-0.1cm} 
-{\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Illustris_zs_03.png}}&
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Illustris_zs_05.png}}&
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Illustris_zs_07.png}}&
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_Illustris_zs_15.png}}\\
-\vspace*{-0.1cm} 
-{\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_03.png}}&
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_05.png}}&
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_07.png}}&
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_15.png}}\\
-\vspace*{-0.1cm} 
-{\includegraphics[trim = 0mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_03.png}}&
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 44mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_05.png}}&
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 44mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_07.png}}&
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 30mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_15.png}}\\
-\end{tabular}
+\includegraphics[trim = 50mm 70mm 40mm 90mm, clip,height=1.1\textwidth]{MM_sum.png}
 \caption{\label{fig:comparsion} 
-The comparison of observed black hole mass vs.
-stellar mass relation from observation data and simulation products (by each row).
-The panels from left to right are based on different redshift bin.
-The black line in the panel indicates the local relation adopted by~\citet{Ding2020}.
-The background cloud shows the intrinsic simulation number density before injecting random noise that selection effect.
-\todo{Xuheng will zoom in the figures and enlarger the text to show the them more clear.}
+Black hole mass versus stellar mass for both the observational (small orange circles) and simulated (small colored circles) samples.
+Each row pertains to a particular simulation as labelled.
+The panels, from left to right, show different redshift bins.
+The black line in each panel indicates the local relation adopted by~\citet{Ding2020}.
+The background cloud (in green and yellow) shows the intrinsic simulation number density before injecting random noise and applying selection effects.
+Only TNG100 is presented here since TNG300 presents very similar results.
 }
@@
 
-The absolute value of stellar masses in both observation and theory have significant uncertainty (up to factor of two), which depends on the assumption of initial mass function, and possibly on the implementation of star formation in the models.
-In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematics.
-Thus, in this work, we first consider the scatter as a diagnostic criteria to see whether some simulations match the data better than others.
-Interestingly, the results show that, almost all the simulations \blue{can produce the scatter values consistent with the observations across all the redshift range} --- for simulation sample at $z<1$, this scatter level is $\sim0.5$~dex, while for $z>1$, this scatter level is $\sim0.3$~dex.
-Note that the HST sample $z>1$ has narrow selection window based on the \mbh\ (see Figure~\ref{fig:selection}~bottom), leading to the result that the observed scatter is smaller than HSC sample at $z<1$.
-\ding{In the simulation, is there any observational data that be used to give extra constrain on the recipe/assumption?
-Xuheng and John are surprised to see that all of them have very good scatter matches!}
+For each sample, the central offset and scatter of the scaling relation are estimated by calculating the mean and the standard deviation of the \mbh\ residuals for each system\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the y-axis in Figure~\ref{fig:comparsion}).
+To aid in visualization of the differences among the various simulations compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}.
+Each panel presents a different redshift range.
+In addition, the values for the central offset and scatter in each case are given in Table~\ref{tab:sum} and shown as a function of redshift in Figure~\ref{fig:offsets_vz}.
 
-We recognize that the observed scatter is dominated by the measurement uncertainties in the data.
-An understanding how much of the scatter derives from random noise can help us to determine the intrinsic scatter in the scaling relation.
-To this end, we measure the scatter of the simulation sample without injecting the random noise but adopting the same selecting window for both $z<1$ and $z>1$ sample to infer the central offset and scatter.
+\subsection{Dispersion}
+
+Our results show that almost all simulations can produce scatter which is consistent with the observations across all redshifts examined (Figures~\ref{fig:comparsion}~and~\ref{fig:offsets}) --- for the simulated samples at $z<1$, this level of scatter is $\sim0.5$~dex, while at $z>1$, it is $\sim0.3$~dex.
+Note that the HST sample $z>1$ has a narrow selection window based on \mbh\ (see Figure~\ref{fig:selection}~bottom), causing the observed scatter to be smaller than that of the HSC sample at $z<1$.
+At all redshifts, we recognize that the observed scatter is dominated by measurement uncertainties in the data.
+
+An understanding of how much of the scatter derives from random noise can help us to determine the {\it intrinsic} scatter in the scaling relation.
+To this end, we measure the scatter of the simulation sample without injecting random noise but adopting the same selection window for both $z<1$ and $z>1$ samples to infer the central offset and scatter.
 We find that the intrinsic scatter is at a level of $\sim0.15-0.2$ dex for both $z<1$ and $z>1$ (see Table~\ref{tab:sum_no_noise}).
-These levels are consistent with the {\it intrinsic} scatter as estimated using observation data by~\citet{Ding2020, 2021arXiv210902751L}.
-More important, these values of the scatter are redshift-independent, suggesting that the tight scaling relation could not be explained by a pure stochastic process, i.e., random mergers.
-Still, the scatter is affected by sample selection, and thus these levels can only be taken as an approximation of the intrinsic scatter.
-We demonstrate these offset that without injecting noise as function of redshift in Figure~\ref{fig:offsets_vz}, right.
-%their physical meaning should not be considered as the intrinsic scatter of the overall sample.
+These levels are consistent with the {\it intrinsic} scatter as estimated using observation data alone~\citep{Ding2020, 2021arXiv210902751L}.
+Furthermore, the intrinsic scatter appears to be independent of redshift since the observations and simulations all follow the observed trend with redshift expected to be due to selection effects (Figure~\ref{fig:offsets_vz}).
+This suggests that the tight scaling relation may not be the result of a pure stochastic process, i.e., random mergers.
+However, the scatter is affected by sample selection, and thus these levels can only be taken as an approximation of the true intrinsic scatter.
 
-To further investigate how the offset values are correlated with stellar mass, we take the MBII sample as example and demonstrate them in Figure~\ref{fig:deltaMM}.
-We also use intrinsic simulation value and plot to address how random noise and selection effect changes the correlation.
-The same Figure based on the other simulations are presented in the Appendix.
-\todo{show the other simulation's result.}
-%Taking \mbh\ and \smass\ as independent measurements, we also summarize their distributions and make comparison between the observation and simulation in the Appendix~\ref{app:function}.
-
-We also investigate the central offset to understand whether the simulations deviate or not from the {\it observed} evolution of the scaling relation.
-According to the results in Table~\ref{tab:sum} and Figure~\ref{fig:offsets_vz}, at low redshift range $z<0.6$, Illustris and Horizon-AGN can predict consistent {\it apparent} \mbh\ offset to the observation data (at a level of $\lesssim0.1$ dex) over all redshifts considered.
-At higher redshift $0.6<z<1.5$, the simulations SAM, TNG100, TNG300 and Horizon-AGN follow the {\it observed} evolution.
-These results are consistent with the Kolmogorov-Smirnov (KS) test performed using the offset distributions between the simulation and the observation.
-The inference of the p-values are collected in Table~\ref{tab:pvalue}, showing that only the Illustris presents good match of the scaling relation at $z<0.6$ (i.e., p-value $> 0.1$), while the TNG100, TNG300 and Horizon simulation predict well at $z>0.6$.
-
-%\renewcommand\thefigure{\arabic{figure}}
-%\setcounter{figure}{1}  
-%{\includegraphics[trim = 0mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_03.png}}&
-%\hspace*{-0.5cm} 
-%{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_05.png}}&
-%\hspace*{-0.5cm} 
-%{\includegraphics[trim = 44mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_07.png}}&
-%\hspace*{-0.5cm} 
-%{\includegraphics[trim = 30mm 30mm 80mm 25mm, clip, height=0.25\textwidth]{MM_TNG_zs_15.png}}\\
-%{\includegraphics[trim = 0mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_03.png}}&
-%\hspace*{-0.5cm} 
-%{\includegraphics[trim = 44mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_05.png}}&
-%\hspace*{-0.5cm} 
-%{\includegraphics[trim = 44mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_07.png}}&
-%\hspace*{-0.5cm} 
-%{\includegraphics[trim = 30mm 0mm 80mm 25mm, clip, height=0.28\textwidth]{MM_Horizon_zs_15.png}}\\
-
-\begin{figure*}
+\begin{figure}
 \centering
@@
 \hspace*{-0.4cm} 
-{\includegraphics[height=0.4\textwidth]{offset_dis_z05.pdf}}&
+{\includegraphics[height=0.4\textwidth]{offset_dis_z05.pdf}}\\
 \hspace*{-0.4cm} 
@@
 The mean value and the standard derivation of the histogram are summarized in Table~\ref{tab:sum}.
-The vertical lines show the corresponding mean value for each distribution.
-The mean values for observed sample (i.e., blue lines) are also show in each simulation plots.
+The vertical dashed lines show the corresponding mean value for each distribution.
+The mean values for observed sample (i.e., yellow lines) are also show in each simulation plots.
 For the MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$.
+}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[height=0.4\textwidth]{offset_summary_vz.pdf}
+\caption{\label{fig:offsets_vz} 
+The {\it observed} evolution of $\Delta{\rm log}$\mbh\ as a function of redshift using both observation and simulation data.
+The black line shows the evolution by fitting the offset as a function of redshift.
+The predictions from the numerical simulations, given in Table~\ref{tab:sum}, are presented by different colored symbols.
+The grey horizontal band illustrates the level of dispersion for the local sample.
+}
+\end{figure}
+
+\subsection{Global offsets}
+We examine the offsets to understand whether the simulations deviate or not from the {\it observed} scaling relation with particular attention to changes with redshift.
+Considering the values given in Table~\ref{tab:sum} and shown in Figure~\ref{fig:offsets_vz}, over the lower redshift range $z<0.6$, Illustris and Horizon-AGN predict {\it observed} \mbh\ offsets consistent with the observation data (at a level of $\lesssim0.1$~dex).
+At higher redshift $0.6<z<1.5$, the simulations SAM, TNG100, TNG300 and Horizon-AGN follow the {\it observed} evolution.
+These results are consistent with the Kolmogorov-Smirnov (KS) test performed using the offset distributions between each simulated sample and the observed sample --- the p-values are given in Table~\ref{tab:pvalue} showing that Horizon-AGN and Illustris have a good statistical match to the scaling relation at $z<0.6$ (i.e., p-value $> 0.1$), while the TNG100, TNG300 and Horizon-AGN simulation do well at $z>0.6$.
+Overall, we find that the mass ratios between SMBHs and their host galaxies are generally consistent between observations and simulations with some subtle differences which are not at the level of concern for this present study.
+
+\subsection{Trends with stellar mass}
+In Figure~\ref{fig:deltaMM}, we investigate how the offset values are correlated with stellar mass.
+Here, we focus on the sample at $z\sim0.7$.
+The other redshift bins at $z<1$, where there is a large observation sample from HSC, show similar trends.
+We include the intrinsic values from the simulations in the figures to address how the observational effects (i.e., random noise and selection) change the observed scaling relations and offsets.
+First, considering the observed quasar sample (same in each panel), there is a trend for which black holes have masses further offset from their stellar mass with decreasing stellar mass.
+This trend is not seen in any of the simulations after noise and selection effects have been applied.
+Given the level of uncertainties in the mean offsets of the observed sample, we do not try to interpret this trend any further in this study.
+
+Interestingly, we notice that MBII and Illustris have black holes intrinsically under-massive relative to their galaxies at the lower masses that reach the local relation at higher masses.
+In contrast, TNG and Horizon-AGN have black holes slightly elevated from the local relation at most masses.
+These differences between simulations present two different scenarios, either one where the black holes come later or co-evolution with the two growing in tandem.
+Considering the former scenario, Illustris show the strongest trend with stellar mass.
+In fact, after noise and selection is applied, the simulated sample exhibits very small offsets which agree remarkably well with the observed data.
+This result underscores the importance of taking into account errors and selection --- without accounting for those, one could erroneously interpret an apparent trend as evolution in the opposite sense as the true one.
+The most direct way to circumvent these issues is to probe lower masses (\smass\  $<10^{10}M_{\odot}$) using a more sensitive instrument, such as JWST~\citep{Habouzit2022} across this redshift range \citep[see also][]{2011MNRAS.417.2085V}.
+
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+\hspace*{-0.5cm} 
+{\includegraphics[trim = 0mm 0mm 0mm 0mm, clip,
+height=0.4\textwidth]{DeltaMM_MBII_zs_06.png}}&
+\hspace*{-0.3cm} 
+{\includegraphics[trim = 36mm 0mm 0mm 0mm, clip,
+height=0.4\textwidth]{DeltaMM_Illustris_zs_07.png}}\\
+\hspace*{-0.5cm} 
+{\includegraphics[trim = 0mm 0mm 0mm 0mm, clip,
+height=0.4\textwidth]{DeltaMM_TNG100_zs_07.png}}&
+\hspace*{-0.3cm} 
+{\includegraphics[trim = 36mm 0mm 0mm 0mm, clip,
+height=0.4\textwidth]{DeltaMM_Horizon_zs_07.png}}\\
+\end{tabular}
+\caption{\label{fig:deltaMM} Comparison of the offset of the \mbh\ (to the local relation) as a function of stellar mass from observation data and the simulations at $z\sim0.7$.
+In each stellar mass bin, we give the mean and standard derivation of the offset values.
+The histograms on the right indicate the offset distribution with lines marking the mean offsets for observation and simulation.
+The green color distributions show the intrinsic simulated sample without random noise and selection applied.
 }
@@
 \begin{deluxetable*}{lccccc}
-%\tablenum{1}
 \tablecaption{Summary of the central offsets and scatters\label{tab:sum}}
@@
 \cline{2-4} 
-%  \cline{2-4}  \cline{5} \\
 \colhead{} &  \colhead{$0.2<z<0.4$} & \colhead{$0.4<z<0.6$} & \colhead{$0.6<z<0.8$} & \colhead{$1.2<z<1.7$} & IMF
@@
 \startdata
-Observation & (0.07, 0.58) & (0.17, 0.52)  & (0.18, 0.54)  & (0.43, 0.31) \\
+Observation & (0.12, 0.51) & (0.20, 0.50)  & (0.21, 0.56)  & (0.43, 0.31) & \\
 SAM & (0.73, 0.49) & (0.65, 0.46)  & (0.51, 0.45)  & (0.51, 0.36) & Salpeter \\
@@
 TNG300 & (0.26, 0.48) & (0.20, 0.48)  & (0.17, 0.48)  & (0.41, 0.34) & Chabrier \\
-Horizon-AGN & (0.20, 0.47) & (0.21, 0.48)  & (0.28, 0.47)  & (0.47, 0.35) & Salpeter\\
+Horizon-AGN & (0.16, 0.49) & (0.14, 0.47)  & (0.23, 0.47)  & (0.47, 0.35) & Salpeter\\
 \enddata
-\tablecomments{This table collects the  comparison results between different simulation at different redshift.
-The value shows the central position offset to the local relation and the scatters of the sample of the \smass-\mbh\ correlations.
-A positive offset means the \mbh\ value predicted by the simulation is higher than the compared measurement at fixed \smass\ value.
+\tablecomments{This table collects the comparison results of the \smass-\mbh\ correlations between different simulation at different redshift.
+The value shows the central position offset to the local relation and the scatters measured around the local relation after applying the offset.
+A positive offset means the \mbh\ value predicted by the simulation is higher than the local relationship measurement at fixed \smass\ value.
 The last column shows the corresponding IMF that adopted to the local anchor to make a fair comparison with the observation.
+Note that for the observational data, the relative differences between local and high-$z$ measurements are not affected by the IMF assumptions.
 For the MBII sample, the simulation does not produce the sample at $z=0.5$ or $z=0.7$, but rather at $z=0.6$.
-\blue{We use Monte Carlo approach to infer the uncertainties of the central offset and scatter for each simulation sample, finding that the uncertainties are within $\pm 0.03$.}
-%This comparison includes the injection of noise and sample selection. and 
-%The estimation of offsets are repeated up to 1000 times until the result is stable. 
+We use Monte Carlo approach to infer the uncertainties of the values in the table, finding that the uncertainties are within $\pm 0.03$.
 }
@@
 
-\begin{figure*}
-\centering
-\begin{tabular}{c c}
-{\includegraphics[height=0.4\textwidth]{offset_summary_vz.pdf}}&
-{\includegraphics[height=0.4\textwidth]{offset_int_summary_vz.pdf}}\\
-\end{tabular}
-\caption{\label{fig:offsets_vz} 
-{\it left}: The apparent evolution of $\Delta{\rm log}$\mbh\ as a function of redshift using both observation and simulation data.
-The black line shows the evolution by fitting the offset as a function of redshift.
-The predictions from the numerical simulations are presented by different color regions, using the values in Table~\ref{tab:sum}.}
-\end{figure*}
+\section{Conclusions} \label{sec:con}
+We compared the observed scaling relation \mbh-\smass\ with the predictions from numerical simulations.
+The observation data are composed of 626 quasars at $0.2 < z < 0.8$ imaged by HSC and 32 X-ray-selected quasars at $1.2 < z < 1.7$ imaged by HST.
+The simulations include a semi-analytic model (SAM) and five hydrodynamic simulations, i.e., MBII, Illustris, TNG100, TNG300 and Horizon-AGN.
+We carried out the comparisons in the observed pararameter space to account for uncertainties and selection effects.
+To achieve this, we first injected random errors with the same observational uncertainty to the simulation, and then adopted the same selection condition to the simulation data (see Figure~\ref{fig:selection}).
+Finally, we adopted the scaling relation from the local universe as our reference and performed comparisons using the scatter of the measurements and their central offset to the local relation.
+Our main results are summarized as follows:
 
-\begin{figure*}
-\centering
-\begin{tabular}{c c c}
-\hspace*{-0.5cm} 
-{\includegraphics[trim = 0mm 0mm 0mm 0mm, clip,
-height=0.3\textwidth]{DeltaMM_MBII_zs_03.png}}&
-\hspace*{-0.3cm} 
-{\includegraphics[trim = 25mm 0mm 0mm 0mm, clip,
-height=0.3\textwidth]{DeltaMM_MBII_zs_06.png}}&
-\hspace*{-0.3cm} 
-{\includegraphics[trim = 25mm 0mm 0mm 0mm, clip,
-height=0.3\textwidth]{DeltaMM_MBII_zs_15.png}}\\
-\end{tabular}
-\caption{\label{fig:deltaMM} 
-The comparison of the offset of the \mbh\ (to the local relation) as a function of stellar mass from observation data and the MBII simulation at three different redshift bins, with same format as Figure~\ref{fig:comparsion}.
-The histogram on the right indicates the offset distribution with lines indicates the mean value of the offset for observation and simulation.
-The green color distributions indicate the intrinsic simulation values that without random noise and selection effect.
-}
-\end{figure*}
+\begin{enumerate}
+
+\item{}The {\it observed} scatter predicted by the simulations is consistent with the observational measurements, i.e., $\sim0.5$~dex at $z<1$ and $\sim0.3$~dex at $z>1$ (see Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}).
+This result indicates that the simulated and observed samples have consistent {\it intrinsic} scatter.
+
+\item{}To understand how much the {\it observed} scatter is dominated by random observational error,
+we re-run the estimation without injecting noise to the simulations.
+The obtained scatter for both $z<1$ and $z>1$ are at a similar level (i.e.,  $\sim$0.15$-$0.2 dex, see Table~\ref{tab:sum_no_noise}), indicating that observational errors dominate the scatter.
+
+\item{} Regarding the mass ratios and offsets from the local relation ($\Delta$\mbh\ at a given \smass\ ), all simulations generally match the observations with some subtle, yet notable, differences.
+While Illustris and Horizon-AGN show good correspondence with observations at $z<0.6$, the comparisons at $z>0.6$ are better for SAM, TNG100, TNG300 and Horizon-AGN.
+From $z\sim0.7$ to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
+
+\end{enumerate}
+
+The absolute value of stellar masses in both observation and theory have significant uncertainty (up to factor of two), which depends on the assumption of initial mass function, and possibly on the implementation of star formation in the models.
+In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematic effect.
+Thus, in this work, we first consider the scatter as a diagnostic criteria to see whether some simulations match the data better than others.
+Taking (1) and (2), our results suggest that the tightness of the scaling relations have been formed since redshift 1.7, which is in contrast with the scenario of the central limit theorem~\citep{Peng2007, Jahnke2011, Hirschmann2010} that the scaling relation is a consequence of a stochastic cloud in the early universe with subsequent random mergers thereafter.
+In this stochastic scenario we expect the scatter of the scaling relations to increase towards higher redshift.
+In fact, the scatter level in the simulation without adding random noise is consistent with the {\it intrinsic} scatter estimations reported in~\citet{Ding2020, 2021arXiv210902751L} (i.e., $\lesssim0.35$~dex).
+This level is also not larger than the typical scatter of the local relations reported in the literature~\citep{Kormendy13, Gul++09, Reines2015}.
+
+The simulations studied in this work have adopted completely different numerical techniques.
+However, all of them can provide good agreement with the observed dispersion in the scaling relation.
+In fact, the tightness of the scaling relation is stem from the same physics assumed in these simulations (i.e., AGN feedback).
+Thus, the consistency of the scatter between simulation and observations is consistent with the hypothesis that the AGN feedback as a causal link between SMBHs and their hosts plays a key role in establishing the scaling relation.
+
+We can gain more insight into the role of feedback by looking at the SAM model, for which multiple feedback models have been implemented.
+\citet{Ding2020b} compared the scaling relations obtained with the same HST sample and the SAM simulation but with a different, isotropic, AGN feedback model, and found a larger scatter ($\sim0.7$~dex) with respect to the present SAM version ($\sim0.36$~dex).
+We ascribed the change to the following reasons: in the new 2D model for feedback, the wave expansions stalls along the direction of the disc, and the radius where the expansion stops depends strongly on both the gas density of the disk and the AGN luminosity.
+This means that the opening angle (and hence the fraction of expelled gas) is larger when the gas density is small (because of the lower energy that has to be spent to push the gas outwards) and when the AGN luminosity is large (because of the larger energy available to push the blast wave outwards).
+These dependencies are summarized in Figure~\ref{fig:SAM}.
+Both quantities depend on the merging histories and are  related, since the AGN luminosity $L_{\rm AGN}$ depends on the available cold gas reservoir $M_{\rm gas}$.
+The large efficiency of feedback in galaxies with particularly small $M_{\rm gas}$ (for given $L_{\rm AGN}$) or in those with particularly large $L_{\rm AGN}$
+(for given $M_{\rm gas}$) inhibits the BH growth in all the host galaxies that are outliers with respect to the average relation between $M_{\rm gas}$ and $L_{\rm AGN}$. 
+This results into a smaller scatter.
+
+In theoretical models, AGN feedback is often assumed to consist of two distinct modes:
+a quasar-heating mode where the SMBH accretion rates are comparable to the Eddington rate and a radio-jet mode occurring at low accretion rates (see e.g.
+Section~\ref{subsec:Horizon}).
+In high redshift universe, the cold material in early universe leads to the vigorous accretion to the SMBH which drives the high accretion rates, and thus the quasar mode dominates the feedback.
+At low redshift, the star formation and feedback ejection reduce the cold material leading to a lower accretion rate and a radio-mode-dominating feedback~\citep[e.g.][]{2012MNRAS.420.2662D,2016MNRAS.460.2979V,2018MNRAS.479.4056W}.
+Our comparison result shows that the level of intrinsic scatter in the scaling relation at redshifts up to 1.7 is consistent with the low redshift one (see Table~\ref{tab:sum_no_noise}), which reveals the fact that at high redshift the AGN feedback described by the quasar mode has already regulated the tight correlation between SMBH and its host galaxy.
+After that, the radio-jet mode starts to take control at low redshift by maintaining the tightness of the scaling relation till the level we observe today.
+
+Our work highlights the importance of applying measurement uncertainty and the effect of selection to the simulated data in order to make direct comparisons with observations.
+Such comparisons have been made in the local universe~\citep[e.g.,][]{Habouzit2021} where the measurements are relatively robust and the selection function is broad thus it is less crucial to ensure consistency between observations and simulations.
+However, beyond $z>0.2$, the scatter and the central distribution of the scaling relations are dominated by measurement uncertainty and selection effects (see Figures~\ref{fig:comparsion} and~\ref{fig:deltaMM}) and a forward modeling in the observational plane becomes essential.
+For example, from trends seen with stellar mass in Illustris and MBII (Figure~\ref{fig:deltaMM}), selection effects may hamper our understanding of whether BHs and their hosts co-evolve or not.
+
+Extending this study to even higher redshift (and lower mass galaxies, \smass\ $<10^{10}M_{\odot}$) will be very beneficial, probing closer to the epoch of formation of massive galaxies and SMBHs.
+The understanding of how and when the tight scaling relation emerged are crucial to test theoretical models \citep{Volonteri2021}.
+On the observational side, the James Webb Space Telescope will provide high-quality imaging data of AGNs at redshift up to $z\sim7$ (i.e., JWST cycle 1 program GO-1967 and GO-1727).
+These upcoming measurements will represent stringent tests on the proposed physical mechanisms for the initial formation of supermassive black holes and of their subsequent evolution with galaxies.
+
+\begin{acknowledgments}
+This work was supported by World Premier International Research Center Initiative (WPI), MEXT, Japan. 
+The authors fully appreciate input from Jingjing Shi.
+
+Based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
+These observations are associated with programs \#15115.
+Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555.
+JS is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
+TT acknowledges support by the Packard Foundation through a Packard Research fellowship to TT.
+LB acknowledges support from NSF award AST-1909933 and Cottrell Scholar Award \#27553 from the Research Corporation for Science Advancement.
+\end{acknowledgments}
 
 \begin{deluxetable*}{lcccc}
-%\tablenum{1}
-\tablecaption{Summary of the {\it intrinsic} central offsets and scatters\label{tab:sum_no_noise}}
+\tablecaption{Summary of the central offsets and scatters without noise\label{tab:sum_no_noise}}
 \tablewidth{0pt}
@@
 TNG300 & (0.25, 0.21) & (0.19, 0.23) & (0.20, 0.22)  & (0.32, 0.16) \\
-Horizon-AGN & (0.24, 0.21) & (0.23, 0.22) & (0.29, 0.19)  & (0.37, 0.13) \\
-%Previous are ones not adding noise but same selection, belows are not add noise and not select
-%SAM & (0.75, 0.26) & (0.74, 0.26) & (0.94, 0.26)  & (0.59, 0.24) \\
-%MBII & (-0.24, 0.22) & \multicolumn{2}{c}{(-0.26, 0.22) [$z=0.6$]}  & (-0.29, 0.22)\\
-%Illustris & (-0.78, 0.40) & (-0.73, 0.40) & (-0.69, 0.40)  & (-0.55, 0.36) \\
-%TNG100 &  (0.33, 0.31) & (0.31, 0.32) & (0.29, 0.33)  & (0.22, 0.37) \\
-%TNG300 & (0.42, 0.58) & (0.40, 0.57) & (0.39, 0.56)  & (0.35, 0.54) \\
-%Horizon & (0.12, 0.30) & (0.13, 0.30) & (0.14, 0.28)  & (-0.00, 0.48) \\
+Horizon-AGN & (0.19, 0.26) & (0.18, 0.21) & (0.28, 0.20)  & (0.37, 0.13) \\
 \enddata
@@
 \cline{2-4} 
-%  \cline{2-4}  \cline{5} \\
 \colhead{} &  \colhead{$z\sim0.3$} & \colhead{$z\sim0.5$} & \colhead{$z\sim0.7$} & \colhead{$z\sim1.5$}
 }
-%\decimalcolnumbers
 \startdata
-SAM &  $<$1e-10 & $<$1e-10  & $<$1e-10  & 7.456907e-03  \\
-MBII & 2.663415e-06 & \multicolumn{2}{c}{$<$1e-10 [$z=0.6$]}  & 2.218653e-06  \\
-Illustris & 4.061962e-02 & 1.029493e-01  & 5.525678e-03  & 2.330195e-07  \\
-TNG100 & 6.677469e-06 & 7.304761e-03  & 1.331638e-01  & 4.708287e-01  \\
-TNG300 & 1.100287e-07 & 5.446812e-01  & 2.942672e-02  & 2.118038e-01  \\
-Horizon & 1.306432e-01 & 3.175037e-01  & 5.094878e-02  & 1.953735e-01  \\
+SAM &  3.119926e-09 & $<$1e-10  & $<$1e-10  & 7.456907e-03  \\
+MBII & 4.228845e-02 & \multicolumn{2}{c}{$<$1e-10 [$z=0.6$]}  & 2.218653e-06  \\
+Illustris & 2.306434e-01 & 6.144066e-02  & 9.963678e-03  & 2.330195e-07  \\
+TNG100 & 1.207389e-02 & 2.530020e-01  & 3.756821e-01  & 4.708287e-01  \\
+TNG300 & 1.817531e-02 & 9.192506e-01  & 1.208812e-01  & 2.118038e-01  \\
+Horizon-AGN & 2.699897e-01 & 2.865927e-01  & 6.129553e-01  & 1.953735e-01  \\
 \enddata
-\tablecomments{The p-value of the KS test between the simulation and the observation.}
+\tablecomments{These p-values are obtained by the KS test between the simulation and the observation.}
 \end{deluxetable*}
 
-\section{Conclusion} \label{sec:con}
-%A brief introduce of the result. Scatter, central, which is best...
-We compare the scaling relation of \mbh-\smass\ using both the observation data and the predictions from numerical simulations.
-The observation data are composed of 612 quasars at $0.2 < z < 0.8$ imaged by HSC and 32 X-ray-selected quasars at $1.2 < z < 1.7$ imaged by HST.
-These observational measurements are compared with simulations including a semi-analytic model (SAM) and five hydrodynamic simulation, i.e., MBII, Illustris, TNG100, TNG300 and Horizon-AGN.
-We designed the direct comparisons that were made in the observational plane.
-To this end, we first injected random errors with the same observational uncertainty to the simulation, and then adopt the same selection condition to the simulation data.
-Finally, we adopted the scaling relation from the local universe and performed the comparisons using the scatter of the measurements and their central offset to the local relation.
-
-%We also estimate the scatter of the sample without inject the noise.
-Our main results are presented in Figure~\ref{fig:offsets_vz} and the Table~\ref{tab:sum} which summarize the scatter and the offset for each sample.
-These results show that the scatter predicted by the simulations are all consistent to the observational measurements, i.e., $\sim0.5$~dex at $z<1$ and $\sim0.3$~dex at $z>1$.
-We note that the scatter are {\it apparent} rather than {\it intrinsic}, which are affected by the observational error and the selection effects.
-To understand how much the random observational error dominates the scatter, we re-run the estimation without injecting noise to the simulations.
-The obtained scatter for both $z<1$ and $z>1$ are at a comparable level of $\sim$0.15$-$0.2 dex.
-This result suggests that the tightness of the scaling relations have been formed up to redshift 1.7, which is against the scenario of the central limit theorem~\citep{Peng2007, Jahnke2011, Hirschmann2010} in which the scaling relation is a consequence of a stochastic cloud in the early universe with subsequent random mergers thereafter.
-Otherwise, the scatter of the scaling relations should increase towards higher redshift.
-In fact, the scatter level in the simulation without adding random noise are consistent with the {\it intrinsic} scatter estimations reported in~\citet{Ding2020, 2021arXiv210902751L}, which is also not larger than the typical scatter of the local relations reported in the literature~\citep[][i.e., $\gtrsim0.35$~dex]{Kormendy13, Gul++09, Reines2015}.
-
-The results also show that Illustris and Horizon-AGN simulation could predict well the scaling relation central offset (related to the local) at $z<0.6$, while SAM, TNG100, TNG300 and Horizon-AGN predict the {\it observed} evolution at $z>0.6$.
-\todo{As mentioned in the result section, we need provide some details on how the scaling relations in the simulations are calibrated.
-For example, why Illustris and TNG sample predict different center for the scaling relation.
-Horizon-AGN could predict well at both low and high z, maybe we can add some discussions.}
-From $z\sim0.7$ to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations could well predict the evolution trend of the scaling relation --- the  {\it observed} offset of the $\Delta$\mbh\ (to the local relation at a given \smass) is larger at higher redshift, which are clearly shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
-
-The simulations studied in this work have adopted completely different numerical techniques.
-However, all of them can provide good agreement with the observed dispersion in the scaling relation.
-In fact, the tightness of the scaling relation is the result of the AGN feedback adopted in the recipe.
-Thus, the consistency of the scatter level between simulation and observations support the hypothesis that the causal link (i.e., AGN feedback) between BH and their hosts plays a dominate role in the scaling relation.
-\ding{The fact that in previous SAM version with a different AGN feedback recipe, the apparent scatter in the simulation is much larger up to 0.7 dex.
-Hi Nicola, could you add more details here and example the different of AGN feedback in SAM compared to previous version?}
-So far, a control experiment is still not performed yet in which one numerical model provide the simulation and altering the AGN feedback prescription, while fixing all other conditions.
-%\todo{We need a paragraph or section to highlight that SAM simulation has been updated. The comparison of the HST in old version shows that the scatter can be up to 0.7 dex.}
-
-\todo{Some discussion of the comparison with Habouzit et al to be added. Also, do we want to take ENGLE simulaiton?}
-
-Extending this study to even higher redshift would be very beneficial, probing closer to the epoch of formation of massive galaxies and SMBHs.
-The understanding of how and when the tight scaling relation emerged are crucial to test the theory.
-On the observational side, the James Webb Space Telescope will provide high-quality imaging data of AGNs at redshift up to $z\sim7$ (i.e., JWST cycle 1 program GO-1967 and GO-1727).
-These upcoming measurements will provide severe constraints to the theories such as the initial conditions in the simulations.
-
-%Look at the further.
-
-\begin{acknowledgments}
-We thank all the people that give us comments and useful suggestions. \todo{More to be added.}
-
-\end{acknowledgments}
-
-\vspace{5mm}
-\facilities{HST, HSC}
-
-%% Similar to \facility{}, there is the optional \software command to allow 
-%% authors a place to specify which programs were used during the creation of 
-%% the manuscript. Authors should list each code and include either a
-%% citation or url to the code inside ()s when available.
-
-%\software{astropy \citep{2013A&A...558A..33A,2018AJ....156..123A},  }
-
-%% Appendix material should be preceded with a single \appendix command.
-%% There should be a \section command for each appendix. Mark appendix
-%% subsections with the same markup you use in the main body of the paper.
-
-%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
-%% The equation counter will reset when it encounters the \appendix
-%% command and will number appendix equations (A1), (A2), etc. The
-%% Figure and Table counter will not reset.
-
-%\appendix
-%\section{Comparison of the observed mass function}\label{app:function}
-%Our comparison also provides the opportunity to compare the {\it apparent} mass distribution of the BH mass and the stellar mass.
-The histogram distribution of the {\it observed} \mbh\ and \smass\ are shown in Figure~\ref{fig:MB_fun} and Figure~\ref{fig:Mstar_fun}, respectively.
-All the simulations have good agreements to the observed mass function, in terms of the standard derivation.
-However, focus on the central point of the distribution, the TNG100 and TNG300 give the best prediction, indicating that their parent sample are most similar to the HSC sample.
-\todo{Xuheng will talk with Jingjing and add more discussion to this part.}
-
-%\begin{figure*}
-%\centering
-%\begin{tabular}{c c}
-%%\vspace*{-0.2cm} 
-%{\includegraphics[height=0.35\textwidth]{MBH_dis_z03.pdf}}&
-%%\hspace*{-0.4cm} 
-%{\includegraphics[height=0.35\textwidth]{MBH_dis_z05.pdf}}\\
-%%\hspace*{-0.4cm} 
-%{\includegraphics[height=0.35\textwidth]{MBH_dis_z07.pdf}}&
-%%\hspace*{-0.4cm} 
-%{\includegraphics[height=0.35\textwidth]{MBH_dis_z15.pdf}}\\
-%\end{tabular}
-%\caption{\label{fig:MB_fun} 
-%Illustration of the histogram of the observed \mbh\ function.
-For MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$.
-Note that for sample at $z\sim1.5$, the selection cut on \mbh\ is used in the simulation, thus the distribution is almost flat.
-\todo{update hist format as Figure 4}
-%}
-%\end{figure*} 
-%
-%\begin{figure*}
-%\centering
-%\begin{tabular}{c c}
-%%\vspace*{-0.2cm} 
-%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z03.pdf}}&
-%%\hspace*{-0.4cm} 
-%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z05.pdf}}\\
-%%\hspace*{-0.4cm} 
-%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z07.pdf}}&
-%%\hspace*{-0.4cm} 
-%{\includegraphics[height=0.35\textwidth]{Mstar_dis_z15.pdf}}\\
-%\end{tabular}
-%\caption{\label{fig:Mstar_fun} 
-%Illustration of the histogram of the observed MBH function. For MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$.
-%}
-%\end{figure*}
-
-\bibliography{reference}{}
+%\bibliography{reference}{}
+\input{manuscript.bbl}
 \bibliographystyle{aasjournal}
 
-%% This command is needed to show the entire author+affiliation list when
-%% the collaboration and author truncation commands are used.  It has to
-%% go at the end of the manuscript.
-%\allauthors
-
-%% Include this line if you are using the \added, \replaced, \deleted
-%% commands to see a summary list of all changes at the end of the article.
-%\listofchanges
-
 \end{document}
-
-% End of file `sample631.tex'.

### 2022-03-28 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
Some updates before change selection

@@
 %% using aastex version 6.3
-%\documentclass[linenumbers]{aastex631}
 %\documentclass[twocolumn, linenumbers]{aastex631}
@@
 \def\hbeta{${\rm H}\beta$}
-\def\mbh{$\mathcal M_{\rm BH}$}
+\def\mbh{$M_{\rm BH}$}
 \def\lcdm{$\Lambda$CDM}	
@@
 \begin{abstract}
-We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies (\mbh -- \smass) at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model).
+We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies (\mbh --\smass) at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model).
 The observed sample consist of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter.
@@
 The consistency in the dispersion with redshift in our analysis lends support to the importance of both quasar and radio mode feedback prescriptions in the simulations.
-Finally, we investigate evolution as a function of stellar and black hole mass, and argue that the most direct way to probe the co-evolution of galaxies and black holes is to increase the sensitivity, e.g., with JWST, thereby pushing to lower masses and minimizing possible biases arising from selection effects.
+Finally, we investigate evolution as a function of stellar and \red{BH} mass, and argue that the most direct way to probe the co-evolution of galaxies and \red{BH}s is to increase the sensitivity, e.g., with JWST, thereby pushing to lower masses and minimizing possible biases arising from selection effects.
 
@@
 \section{Introduction} \label{sec:intro}
-
-The close correlations between supermassive black holes and the properties of their host galaxies (e.g., stellar mass) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
+\todo{Re-read to avoid residual P1.}
+The close correlations between \red{the mass of} supermassive black holes (\red{\mbh}) and the properties of their host galaxies (e.g., stellar mass\red{, \smass}) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
 To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over cosmic time \citep[e.g.,][]{Tre++04,Peng2006a, Tre++07, Woo++08, Jahnke2009, Bennert11, Schramm2013, Park15, Mechtley2016, Ding2020, 2021arXiv210902751L}.
-While, an {\it observed} evolution has been found in many studies in which the growth of BHs predates that of the host, other studies predict that BHs grow commensurately with galaxies.
+While, an {\it observed} evolution has been found \red{at redshift range xxx} in many studies \todo{move ref} in which the growth of BHs predates that of the host, other studies predict \todo{move ref} that BHs grow commensurately with galaxies.
 However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15}.
@@
 Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution,
-including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH simulations~\citep{Schaye2015}, Illustris moving-mesh simulation~\citep{Sijacki2015, 2014MNRAS.444.1518V, Li2019} and the SIMBA simulation~\citep{Thomas2019}.
+including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH \red{simulations~\citep{Schaye2015, Crain2015, McAlpine2016},} Illustris moving-mesh \red{simulation~\citep{Genel2014, 2014MNRAS.444.1518V, Sijacki2015, Nelson2015, Li2019}} and the SIMBA \red{simulation~\citep{Thomas2019, Dave2019}.
+}
 In particular, the \mbh-\smass\ relation using BH populations using six large-scale cosmological simulations (i.e, Illustris, TNG100, TNG300, Horizon-AGN, EAGLE, and SIMBA) has been compared with observations in the local universe in a recent study~\citep{Habouzit2021}.
@@
 In~\citet{Ding2020b}, a direct comparison has been performed using 32 X-ray-selected AGN at $1.2<z<1.7$ and a direct comparison with two state-of-the-art simulation efforts, including {\tt MassiveBlackII} (MBII) and a Semi-analytic Model \citep[SAM,][]{Menci2014, Menci2016}.
-The dispersion in the mass ratio between black hole mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) favoring the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.
+The dispersion in the mass ratio between \red{BH} mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) favoring the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.
 
@@
 A sample of $\sim$5000 type-1 SDSS quasars from the DR14 catalog~\citep{Paris2018} at $0.2<z<1$ has been imaged by the high-resolution Subaru Strategic Program (SSP) wide area survey~\citep{Aihara2019} using Hyper Suprime-Cam~\citep{Miyazaki2018}.
-With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been performed \citep[][hereafter L21a]{Li2021a} to obtain the flux and color of each quasar's host galaxy.
+With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been \red{performed \citep[][]{Li2021a}} to obtain the flux and color of each quasar's host galaxy.
 The stare-of-the-art image modeling software {\tt lenstronomy} \citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task.
@@
 $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$.
+\todo{The $\leq$ sign in the low accretion feedback mode of TNG is also not clear.
+Is it a fixed value or a distribution?} \todo{Please mention whether the same radiative efficiency is used to compute AGN luminosity in all the simulations.}
 }
@@
 \section{Simulations and comparison strategy}
+\todo{Uniform the descriptions of the simulations to lack homogeneity. (Illustris has star formation threshold). Re-write the section and provide the same information}
 \label{sec:simulations}
@@
 and $2\times1792^3$ particles.
-The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}.
+\todo{answer what is the factor 2 here.
+A twin box with 1793$^3$ each?} The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}.
 The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}.
@@
 
-To model supermassive black holes, a BH seed with mass $5\times 10^{5}~M_{\odot}/h$ are inserted into halos of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$.
+To model supermassive \red{BH, the initial} seed with mass $5\times 10^{5}~M_{\odot}/h$ are inserted into halos of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$.
 Once seeded, BH growth via gas accretion is assigned at a rate of $\dot{M}_{BH}={4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the interstellar medium (ISM) gas at cold phase; $v_{BH}$ is the relative velocity between the BH and its surrounding gas.
@@
 The accreted gas is released as radiation at a radiative efficiency of 10\%.
-A fraction of 5\% of the radiated energy thermally couples to the surrounding gas as black hole (or AGN) feedback~\citep{2005Natur.433..604D}.
+A fraction of 5\% of the radiated energy thermally couples to the surrounding gas as \red{BH} (or AGN) feedback~\citep{2005Natur.433..604D}.
 A mildly super-Eddington (two times Eddington rate) is allowed.
@@
 \subsection{Illustris}
-The Illustris Project is another large scale hydrodynamics simulation, introduced in~\citet{2014MNRAS.444.1518V, 2014Natur.509..177V}.
-The simulation consist of a volume of (106.5 cMpc)$^3$~(slightly smaller than MassiveBlack II),
+The Illustris Project is another large scale hydrodynamics simulation, introduced \red{in~\citet{Genel2014, 2014MNRAS.444.1518V, 2014Natur.509..177V, Sijacki2015, Nelson2015}.} The simulation consist of a volume of (106.5 cMpc)$^3$~(slightly smaller than MassiveBlack II),
 and was run with the moving Voronoi mesh code {\tt Arepo}~\citep{2010MNRAS.401..791S} with a base cosmology adopted from WMAP9 results~\citep{2013ApJS..208...19H}.
@@
 The boost factor $\alpha=100$ is introduced to account for the unresolved multiphase ISM~\citep{Springel2005, 2009MNRAS.398...53B}, which is otherwise expected to underestimate the density around the BHs.
-Lastly, accreting black holes radiate with a bolometric luminosity given by $\epsilon_r \dot{M}_{BH}c^2$, where $\dot{M}_{BH}$ is the mass accretion rate and $\epsilon_r=0.2$ is the radiative efficiency.
+Lastly, accreting \red{BH}s radiate with a bolometric luminosity given by $\epsilon_r \dot{M}_{BH}c^2$, where $\dot{M}_{BH}$ is the mass accretion rate and $\epsilon_r=0.2$ is the radiative efficiency.
 
@@
 For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at~(irregular) intervals between which the BH mass grows by a fixed fraction.
-The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{bh} c^2$ where $\delta M_{bh}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency.
+The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency.
 Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN.
@@
 \subsection{IllustrisTNG}
-{\it The Next Generation Illustris Simulations} (IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes.
+{\it The Next Generation Illustris Simulations} \red{(IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018, Naiman2018, Marinacci2018, Nelson2018}} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes.
 It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modeling, and 3) addressing the identified shortcomings of the previous generation simulations.
@@
 The BH accretion also follows the Bondi-Hoyle-Lyttleton formalism, but without any boost factor~(unlike Illustris).
-Accreting black holes release energy with a radiative efficiency of 0.2~(same as Illustris).
+Accreting \red{BH}s release energy with a radiative efficiency of 0.2~(same as Illustris).
 The inclusion of the magnetic fields can affect the relationship between the BHs and their host galaxies properties; the \mbh-\smass\ mean relation is higher with magnetic fields~\citep{2018MNRAS.473.4077P}.
@@
 For visual comparison between the HSC and HST selection, we show the region of the HST selection window in the left panel as dashed lines.
+\todo{No mention of the redshift in Fig.2}
 }
@@
 In each halo, we compute the fraction of gas which cools because of the atomic processes and settles into a disk~\citep{Mo1998}.
-The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr, according to BH feeding; (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion).
+The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr, according to BH feeding; \todo{the link between BH feeding and star formation channels in this sentence is not clear.} (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion).
 The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation which returns a fraction of the disk gas into a hot phase.
@@
 As mentioned above, \smass\ and \mbh\ for HSC and HST samples are measured with a similar approach; thus their uncertainty levels are expected to be equivalent.
-We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = 0.17~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.
+We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = \red{0.2}~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.
 
@@
 
+\todo{A little discussion on the \smass\ P16. And address the properties what does it mean by intrinsic. P9+P12}
+
 \section{Results} \label{sec:result}
+%\todo{Explain the offset depends.}
+\red{For comparison purpose, the local scaling relation introduced by D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion.
+\todo{Explain how D20's local is obtained and why it is IMF related.
+P10}}
+
+\red{For each sample, we focus on the \mbh\ residuals\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the y-axis) and calculating their mean and the standard deviation to make comparisons with the observation.}
+
+\red{As introduced in previous section, to make direct comparison, the simulation sample is processed in two steps: inject observational noise injection, and apply equivalent selection.
 In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
+For the simulation data, both the initial sample and the ones after selection and with noise corrections are show in the figure.
+There are three types of offset value that are considered from simulation: the initial offset, the offset with selection effect, and the offset with noise and selection effect.
+For the initial one, it has been known~\citep[e.g.,][Figure 2]{Habouzit2021} and can be seen in Figure~\ref{fig:comparsion} that the initial offset values vary at different stellar mass range, and thus the mean and standard derivation could not represent the entire distribution.
+The discussion of this initial offset is also beyond the scope of this work.
+We focus on the other two offset value distributions in this work.
+To aid in visualization of the differences among the various simulations compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}.
+Each panel presents a different redshift range.
+In addition, the values of the central offset and scatter for before and after considering the noise are presented in Table~\ref{tab:sum} (after noise).
+The interpolations and the comparison with the observations are presented in the rest of this section.
+}
+\todo{Read to avoid description (intrinsic and then noise).}
+%For the initial level, it has been known that the offset depended by range of the stellar mass and thus it is less meaningful to make comparison in this work.
+
+%In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
 The local scaling relation adopted by D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is used as the fiducial relation to assess relative offsets and differences in dispersion.
 A different simulation is presented in each row and the redshift intervals increase from left to right.
-We note that TNG100 and TNG300 yield very similar comparison results, thus only TNG100 is presented in Figure~\ref{fig:comparsion}.
+
+%For each sample, the central offset and scatter of the scaling relation are estimated by calculating the mean and the standard deviation of the \mbh\ residuals for each system\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the y-axis in Figure~\ref{fig:comparsion}).
+To aid in visualization of the differences among the various simulations compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}.
+Each panel presents a different redshift range.
+In addition, the values for the central offset and scatter in each case are given in Table~\ref{tab:sum} and shown as a function of redshift in Figure~\ref{fig:offsets_vz}.
 
@@
 The background cloud (in green and yellow) shows the intrinsic simulation number density before injecting random noise and applying selection effects.
-Only TNG100 is presented here since TNG300 presents very similar results.
+Only TNG100 is presented here since TNG300 presents very similar results \red{(see discussion section)}.
 }
 \end{figure*}
-
-For each sample, the central offset and scatter of the scaling relation are estimated by calculating the mean and the standard deviation of the \mbh\ residuals for each system\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the y-axis in Figure~\ref{fig:comparsion}).
-To aid in visualization of the differences among the various simulations compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}.
-Each panel presents a different redshift range.
-In addition, the values for the central offset and scatter in each case are given in Table~\ref{tab:sum} and shown as a function of redshift in Figure~\ref{fig:offsets_vz}.
 
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
@@
 \hspace*{-0.4cm} 
-{\includegraphics[height=0.4\textwidth]{offset_dis_z05.pdf}}\\
+{\includegraphics[height=0.4\textwidth]{offset_dis_z05.pdf}}&
 \hspace*{-0.4cm} 
@@
 \caption{\label{fig:offsets} 
-Histograms of the offset distributions for all simulation samples and observations.
+\red{Color filled histograms show the offset distributions} for all simulation samples and observations.
 The mean value and the standard derivation of the histogram are summarized in Table~\ref{tab:sum}.
@@
 The mean values for observed sample (i.e., yellow lines) are also show in each simulation plots.
+\red{For the simulation samples, their offset distribution without adding noise is shown using black line.}
 For the MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$. 
 }
-\end{figure}
+\end{figure*}
 
@@
 The predictions from the numerical simulations, given in Table~\ref{tab:sum}, are presented by different colored symbols.
-The grey horizontal band illustrates the level of dispersion for the local sample.
+The grey horizontal band illustrates the level of dispersion for the local sample \red{from D20}.
 }
@@
 These results are consistent with the Kolmogorov-Smirnov (KS) test performed using the offset distributions between each simulated sample and the observed sample --- the p-values are given in Table~\ref{tab:pvalue} showing that Horizon-AGN and Illustris have a good statistical match to the scaling relation at $z<0.6$ (i.e., p-value $> 0.1$), while the TNG100, TNG300 and Horizon-AGN simulation do well at $z>0.6$.
-Overall, we find that the mass ratios between SMBHs and their host galaxies are generally consistent between observations and simulations with some subtle differences which are not at the level of concern for this present study.
+Overall, we find that the mass ratios between \red{supermassive BH}s and their host galaxies are generally consistent between observations and simulations with some subtle differences which are not at the level of concern for this present study.
+\todo{To add that 4/6 of the simulations have decreasing mass offsets from z=0.2 and 0.6 while the offsets from the observations increase with redshift all the way (Fig. 5). P15}
+%\todo{shift offset at 0.3 and discussion the difference. P11}
 
@@
 We include the intrinsic values from the simulations in the figures to address how the observational effects (i.e., random noise and selection) change the observed scaling relations and offsets.
-First, considering the observed quasar sample (same in each panel), there is a trend for which black holes have masses further offset from their stellar mass with decreasing stellar mass.
+First, considering the observed quasar sample (same in each panel), there is a trend for which \red{BH}s have masses further offset from their stellar mass with decreasing stellar mass.
 This trend is not seen in any of the simulations after noise and selection effects have been applied.
@@
 
-Interestingly, we notice that MBII and Illustris have black holes intrinsically under-massive relative to their galaxies at the lower masses that reach the local relation at higher masses.
-In contrast, TNG and Horizon-AGN have black holes slightly elevated from the local relation at most masses.
-These differences between simulations present two different scenarios, either one where the black holes come later or co-evolution with the two growing in tandem.
+Interestingly, we notice that MBII and Illustris have \red{BH}s intrinsically under-massive relative to their galaxies at the lower masses that reach the local relation at higher masses.
+In contrast, TNG and Horizon-AGN have \red{BH}s slightly elevated from the local relation at most masses.
+These differences between simulations present two different scenarios, either one where the \red{BH}s come later or co-evolution with the two growing in tandem.
 Considering the former scenario, Illustris show the strongest trend with stellar mass.
@@
 The most direct way to circumvent these issues is to probe lower masses (\smass\  $<10^{10}M_{\odot}$) using a more sensitive instrument, such as JWST~\citep{Habouzit2022} across this redshift range \citep[see also][]{2011MNRAS.417.2085V}.
+\todo{highlight the selection effect that the offset doesn't reflect the truth. P20}
 
@@
 
+%\begin{deluxetable*}{lcccc}
+%\tablecaption{Summary of the central offsets and scatters without noise\label{tab:sum_no_noise}}
+%\tablewidth{0pt}
+%\tablehead{
+%\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
+%\cline{2-4} 
+%\colhead{} &  \colhead{$0.2<z<0.4$} & \colhead{$0.4<z<0.6$} & \colhead{$0.6<z<0.8$} & \colhead{$1.2<z<1.7$}
+%}
+%\startdata
+%SAM & (0.72, 0.20) & (0.64, 0.18) & (0.56, 0.16)  & (0.08, 0.18) \\
+%MBII & (-0.15, 0.21) & \multicolumn{2}{c}{(-0.15, 0.22) [$z=0.6$]}  & (0.08, 0.19)\\
+%Illustris & (0.03, 0.32) & (0.10, 0.36) & (0.08, 0.36)  & (0.04, 0.19) \\
+%TNG100 &  (0.27, 0.20) & (0.27, 0.15) & (0.26, 0.16)  & (0.36, 0.15) \\
+%TNG300 & (0.25, 0.21) & (0.19, 0.23) & (0.20, 0.22)  & (0.32, 0.16) \\
+%Horizon-AGN & (0.19, 0.26) & (0.18, 0.21) & (0.28, 0.20)  & (0.37, 0.13) \\
+%\enddata
+%\tablecomments{Same as Table~\ref{tab:sum} but without inject noise to the simulation data. Note that same selection window is still adopted to infer the values. \todo{Merger Table 2 and 3}}
+%\end{deluxetable*}
+
 \begin{deluxetable*}{lccccc}
 \tablecaption{Summary of the central offsets and scatters\label{tab:sum}}
-\tablewidth{0pt}
+%\tablewidth{0pt}
+\tabletypesize{\footnotesize}
 \tablehead{
-\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
+\colhead{Sample} &  \multicolumn{3}{c}{HSC comparison} & \colhead{HST comparison} \\
 \cline{2-4} 
@@
 \startdata
-Observation & (0.12, 0.51) & (0.20, 0.50)  & (0.21, 0.56)  & (0.43, 0.31) & \\
-SAM & (0.73, 0.49) & (0.65, 0.46)  & (0.51, 0.45)  & (0.51, 0.36) & Salpeter \\
-MBII & (-0.15, 0.48) & \multicolumn{2}{c}{(-0.16, 0.48) [$z=0.6$]}  & (0.14, 0.31) & Salpeter\\
-Illustris & (0.01, 0.52) & (0.08, 0.53)  & (0.06, 0.54)  & (0.07, 0.32) &  Chabrier \\
-TNG100 & (0.27, 0.48) & (0.24, 0.46)  & (0.24, 0.45)  & (0.38, 0.33) & Chabrier \\
-TNG300 & (0.26, 0.48) & (0.20, 0.48)  & (0.17, 0.48)  & (0.41, 0.34) & Chabrier \\
-Horizon-AGN & (0.16, 0.49) & (0.14, 0.47)  & (0.23, 0.47)  & (0.47, 0.35) & Salpeter\\
+Observation & (0.12$\pm$0.51) & (0.20$\pm$0.50)  & (0.21$\pm$0.56)  & (0.43$\pm$0.31) & \\
+SAM & (0.72$\pm$0.20)$\rightarrow$(0.73$\pm$0.49) & (0.64$\pm$0.18)$\rightarrow$(0.65$\pm$0.46)  &(0.56$\pm$0.16)$\rightarrow$(0.51$\pm$0.45)  &  (0.08$\pm$0.18)$\rightarrow$(0.51$\pm$0.36) & Salpeter \\
+MBII & (-0.15$\pm$0.21)$\rightarrow$(-0.15$\pm$0.48) & \multicolumn{2}{c}{[$z=0.6$] (-0.15$\pm$0.22)$\rightarrow$(-0.16$\pm$0.48)}  & (0.08$\pm$0.19)$\rightarrow$(0.14$\pm$0.31) & Salpeter\\
+Illustris & (0.03$\pm$0.32)$\rightarrow$(0.01$\pm$0.52) & (0.10$\pm$0.36)$\rightarrow$(0.08$\pm$0.53)  &(0.08$\pm$0.36)$\rightarrow$(0.06$\pm$0.54)  &  (0.04$\pm$0.19)$\rightarrow$(0.07$\pm$0.32) &  Chabrier \\
+TNG100 & (0.27$\pm$0.20)$\rightarrow$(0.27$\pm$0.48) & (0.27$\pm$0.15)$\rightarrow$(0.24$\pm$0.46)  &(0.26$\pm$0.16)$\rightarrow$(0.24$\pm$0.45)  &  (0.36$\pm$0.15)$\rightarrow$(0.38$\pm$0.33) & Chabrier \\
+TNG300 & (0.25$\pm$0.21)$\rightarrow$(0.26$\pm$0.48) & (0.19$\pm$0.23)$\rightarrow$(0.20$\pm$0.48)  &(0.20$\pm$0.22)$\rightarrow$(0.17$\pm$0.48)  &  (0.32$\pm$0.16)$\rightarrow$(0.41$\pm$0.34) & Chabrier \\
+Horizon & (0.19$\pm$0.26)$\rightarrow$(0.16$\pm$0.49) & (0.18$\pm$0.21)$\rightarrow$(0.14$\pm$0.47)  &(0.28$\pm$0.20)$\rightarrow$(0.23$\pm$0.47)  &  (0.37$\pm$0.13)$\rightarrow$(0.47$\pm$0.35) & Salpeter\\
+%SAM & (0.72, 0.20) $\rightarrow$ (0.73, 0.49) & (0.65, 0.46)  & (0.51, 0.45)  & (0.51, 0.36) & Salpeter \\
+%Illustris & (0.03, 0.32) $\rightarrow$ (0.01, 0.52) & (0.08, 0.53)  & (0.06, 0.54)  & (0.07, 0.32) &  Chabrier \\
+%TNG100 & (0.27, 0.20) $\rightarrow$ (0.27, 0.48) & (0.24, 0.46)  & (0.24, 0.45)  & (0.38, 0.33) & Chabrier \\
+%TNG300 & (0.25, 0.21) $\rightarrow$ (0.26, 0.48) & (0.20, 0.48)  & (0.17, 0.48)  & (0.41, 0.34) & Chabrier \\
+%Horizon & (0.19, 0.26) $\rightarrow$ (0.16, 0.49) & (0.14, 0.47)  & (0.23, 0.47)  & (0.47, 0.35) & Salpeter\\
 \enddata
+\tabletypesize{\normalsize}
 \tablecomments{This table collects the comparison results of the \smass-\mbh\ correlations between different simulation at different redshift.
@@
 \end{deluxetable*}
+
+\section{Discussion} \label{sec:dis}
+\todo{TNG100 and TNG300 -- explain the why no difference between TNGs.
+P8}~\red{We note that TNG100 and TNG300 yield very similar comparison results, thus only TNG100 is presented in~Figure~\ref{fig:comparsion}}.
+
+\todo{QSO selection. Lbol vary and QSO II type. P7}
+
+\todo{Discussion when shift offset as z=0.3. P11}
+
+\todo{Discussion how random make difference on the scatter. P13}
+
+\todo{Discussion on the \smass of the simulation and why IMF is part of the picture. P16}
 
@@
 
-\item{} Regarding the mass ratios and offsets from the local relation ($\Delta$\mbh\ at a given \smass\ ), all simulations generally match the observations with some subtle, yet notable, differences.
+\item{} Regarding the \red{offsets of the scaling relation from the local} ($\Delta$\mbh\ at a given \smass), all simulations generally match the observations with some subtle, yet notable, differences.
 While Illustris and Horizon-AGN show good correspondence with observations at $z<0.6$, the comparisons at $z>0.6$ are better for SAM, TNG100, TNG300 and Horizon-AGN.
@@
 
+\todo{To add that 4/6 of the simulations have decreasing mass offsets from z=0.2 and 0.6 while the offsets from the observations increase with redshift all the way (Fig. 5). P15}
+
 \end{enumerate}
-
+\todo{For clarity the first paragraph after 3) should specify the stellar mass range considered when discussing the scatter of the local relation etc.}
 The absolute value of stellar masses in both observation and theory have significant uncertainty (up to factor of two), which depends on the assumption of initial mass function, and possibly on the implementation of star formation in the models.
-In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematic effect.
+\todo{If this sentence includes the simulations, then the stellar mass of the galaxies also depends on other subgrid models such as supernova feedback, AGN feedback.} In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematic effect.
 Thus, in this work, we first consider the scatter as a diagnostic criteria to see whether some simulations match the data better than others.
@@
 In fact, the tightness of the scaling relation is stem from the same physics assumed in these simulations (i.e., AGN feedback).
-Thus, the consistency of the scatter between simulation and observations is consistent with the hypothesis that the AGN feedback as a causal link between SMBHs and their hosts plays a key role in establishing the scaling relation.
+Thus, the consistency of the scatter between simulation and observations is consistent with the hypothesis that the AGN feedback as a causal link between \red{supermassive BH}s and their hosts plays a key role in establishing the scaling relation.
+\todo{AGN feedback, causal link? P18}
 
@@
 In theoretical models, AGN feedback is often assumed to consist of two distinct modes:
-a quasar-heating mode where the SMBH accretion rates are comparable to the Eddington rate and a radio-jet mode occurring at low accretion rates (see e.g.
+a quasar-heating mode where the \red{BH} accretion rates are comparable to the Eddington rate and a radio-jet mode occurring at low accretion rates (see e.g.
 Section~\ref{subsec:Horizon}).
-In high redshift universe, the cold material in early universe leads to the vigorous accretion to the SMBH which drives the high accretion rates, and thus the quasar mode dominates the feedback.
+In high redshift universe, the cold material in early universe leads to the vigorous accretion to the \red{supermassive BH} which drives the high accretion rates, and thus the quasar mode dominates the feedback.
 At low redshift, the star formation and feedback ejection reduce the cold material leading to a lower accretion rate and a radio-mode-dominating feedback~\citep[e.g.][]{2012MNRAS.420.2662D,2016MNRAS.460.2979V,2018MNRAS.479.4056W}.
-Our comparison result shows that the level of intrinsic scatter in the scaling relation at redshifts up to 1.7 is consistent with the low redshift one (see Table~\ref{tab:sum_no_noise}), which reveals the fact that at high redshift the AGN feedback described by the quasar mode has already regulated the tight correlation between SMBH and its host galaxy.
+Our comparison result shows that the level of intrinsic scatter in the scaling relation at redshifts up to 1.7 is consistent with the low redshift one (see Table~\ref{tab:sum_no_noise}), which reveals the fact that at high redshift the AGN feedback described by the quasar mode has already regulated the tight correlation between \red{supermassive BH} and its host galaxy.
 After that, the radio-jet mode starts to take control at low redshift by maintaining the tightness of the scaling relation till the level we observe today.
+\todo{P19.}
 
@@
 
-Extending this study to even higher redshift (and lower mass galaxies, \smass\ $<10^{10}M_{\odot}$) will be very beneficial, probing closer to the epoch of formation of massive galaxies and SMBHs.
+Extending this study to even higher redshift (and lower mass galaxies, \smass\ $<10^{10}M_{\odot}$) will be very beneficial, probing closer to the epoch of formation of massive galaxies and \red{supermassive BH}s.
 The understanding of how and when the tight scaling relation emerged are crucial to test theoretical models \citep{Volonteri2021}.
 On the observational side, the James Webb Space Telescope will provide high-quality imaging data of AGNs at redshift up to $z\sim7$ (i.e., JWST cycle 1 program GO-1967 and GO-1727).
-These upcoming measurements will represent stringent tests on the proposed physical mechanisms for the initial formation of supermassive black holes and of their subsequent evolution with galaxies.
+These upcoming measurements will represent stringent tests on the proposed physical mechanisms for the initial formation of supermassive \red{BH}s and of their subsequent evolution with galaxies.
 
@@
 \begin{deluxetable*}{lcccc}
-\tablecaption{Summary of the central offsets and scatters without noise\label{tab:sum_no_noise}}
-\tablewidth{0pt}
-\tablehead{
-\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
-\cline{2-4} 
-\colhead{} &  \colhead{$0.2<z<0.4$} & \colhead{$0.4<z<0.6$} & \colhead{$0.6<z<0.8$} & \colhead{$1.2<z<1.7$}
-}
-\startdata
-SAM & (0.72, 0.20) & (0.64, 0.18) & (0.56, 0.16)  & (0.08, 0.18) \\
-MBII & (-0.15, 0.21) & \multicolumn{2}{c}{(-0.15, 0.22) [$z=0.6$]}  & (0.08, 0.19)\\
-Illustris & (0.03, 0.32) & (0.10, 0.36) & (0.08, 0.36)  & (0.04, 0.19) \\
-TNG100 &  (0.27, 0.20) & (0.27, 0.15) & (0.26, 0.16)  & (0.36, 0.15) \\
-TNG300 & (0.25, 0.21) & (0.19, 0.23) & (0.20, 0.22)  & (0.32, 0.16) \\
-Horizon-AGN & (0.19, 0.26) & (0.18, 0.21) & (0.28, 0.20)  & (0.37, 0.13) \\
-\enddata
-\tablecomments{Same as Table~\ref{tab:sum} but without inject noise to the simulation data. Note that same selection window is still adopted to infer the values.}
-\end{deluxetable*}
-
-\begin{deluxetable*}{lcccc}
-\tablecaption{Summary of the p-value using KS test \label{tab:pvalue}}
+\tablecaption{\red{Summary of the p-value using KS test \label{tab:pvalue}}}
 \tablewidth{0pt}
@@
 \startdata
-SAM &  3.119926e-09 & $<$1e-10  & $<$1e-10  & 7.456907e-03  \\
-MBII & 4.228845e-02 & \multicolumn{2}{c}{$<$1e-10 [$z=0.6$]}  & 2.218653e-06  \\
-Illustris & 2.306434e-01 & 6.144066e-02  & 9.963678e-03  & 2.330195e-07  \\
-TNG100 & 1.207389e-02 & 2.530020e-01  & 3.756821e-01  & 4.708287e-01  \\
-TNG300 & 1.817531e-02 & 9.192506e-01  & 1.208812e-01  & 2.118038e-01  \\
-Horizon-AGN & 2.699897e-01 & 2.865927e-01  & 6.129553e-01  & 1.953735e-01  \\
+SAM &  3.12e-09 & $<$1e-10  & $<$1e-10  & 7.46e-03  \\
+MBII & 4.23e-02 & \multicolumn{2}{c}{$<$1e-10 [$z=0.6$]}  & 2.22e-06  \\
+Illustris & 2.31e-01 & 6.14e-02  & 9.96e-03  & 2.33e-07  \\
+TNG100 & 1.21e-02 & 2.53e-01  & 3.76e-01  & 4.71e-01  \\
+TNG300 & 1.82e-02 & 9.19e-01  & 1.21e-01  & 2.12e-01  \\
+Horizon-AGN & 2.70e-01 & 2.87e-01  & 6.13e-01  & 1.95e-01  \\
 \enddata
@@
 
-%\bibliography{reference}{}
-\input{manuscript.bbl}
+\bibliography{reference}{}
+%\input{manuscript.bbl}
 \bibliographystyle{aasjournal}

### 2022-03-29 projects/2020_HSC_to_numerical_simulation/HSCvsTNG300.py
Update for referee report's cal

@@ -25,14 +25,15 @@ filename = filenames[idx]
 zs = float(filename.split("_z")[1][:4])
 
 HSC = HSC_set(zs, core = True)
-if zs <= 0.5:
-    # HSC_Mstar = HSC_Mstar_overall[HSC_z<0.5]
-    # HSC_MBHs = HSC_MBHs_overall[HSC_z<0.5]
-    I_mag_break = 20.5  #z~0.3
-if zs > 0.5:    
-    # HSC_Mstar = HSC_Mstar_overall[HSC_z>0.5]
-    # HSC_MBHs = HSC_MBHs_overall[HSC_z>0.5]
-    I_mag_break = 22.0    #z~0.7
+# if zs <= 0.5:
+#     # HSC_Mstar = HSC_Mstar_overall[HSC_z<0.5]
+#     # HSC_MBHs = HSC_MBHs_overall[HSC_z<0.5]
+#     I_mag_break = 20.5  #z~0.3
+# if zs > 0.5:    
+#     # HSC_Mstar = HSC_Mstar_overall[HSC_z>0.5]
+#     # HSC_MBHs = HSC_MBHs_overall[HSC_z>0.5]
+#     I_mag_break = 22.0    #z~0.7
+I_mag_break = 19.5
 
 for i in range(1):
     TNG300 = TNG300_set(filename, HSC_Lbol_overall=HSC['HSC_Lbol_overall'], HSC_MBHs_overall=HSC['HSC_MBHs_overall'],

### 2022-03-29 projects/2020_HSC_to_numerical_simulation/check_distribuion_step1.py

@@ -1,0 +1,136 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Mar  7 18:16:30 2022
+
+@author: Dartoon
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+from sum_prep import load_HSC_comp, load_HST_comp, imf_dict
+import matplotlib as mat
+mat.rcParams['font.family'] = 'STIXGeneral'
+
+import glob
+import pickle
+from matplotlib.ticker import AutoMinorLocator
+import seaborn as sns
+
+m_ml, b_ml = (0.981139684856507, -2.545890295477823)
+#%%
+eps = 1.5
+I_mag_break=21.5
+fig = plt.figure(figsize=(16*eps, 20*eps))
+gs = fig.add_gridspec(5, 4, hspace=0, wspace=0)
+axs = gs.subplots()
+i, j = 0, 0
+obsname = ['HSC', 'HST']
+colors_sim = ['deepskyblue', 'steelblue', 'c', 'deeppink', 'm']
+for zs in [0.3, 0.5, 0.7, 1.5]:
+    if zs == 0.3:
+        I_mag_break = 19.5
+    if zs == 0.5 :
+        I_mag_break = 20.5
+    if zs == 0.7 :
+        I_mag_break = 21.5
+    if glob.glob('comb_zs{0}_Imag_{1}.pkl'.format(zs, I_mag_break)) != []:
+        obs_dict, sim_dict = pickle.load(open(glob.glob('comb_zs{0}_Imag_{1}.pkl'.format(zs,I_mag_break))[0],'rb'))
+    # else:
+    #     if zs<1:
+    #         obs_dict, sim_dict = load_HSC_comp(zs =zs, I_mag_break=I_mag_break)
+    #     elif zs>1: 
+    #         obs_dict, sim_dict = load_HST_comp()
+    # pickle.dump([obs_dict, sim_dict], open('comb_zs{0}_Imag_{1}.pkl'.format(zs,I_mag_break), 'wb'))    
+        
+    for sname in ['SAM', 'MBII', 'Illustris', 'TNG100', 'Horizon']:
+        sim = sim_dict[sname]
+        imf = imf_dict[sname]
+        obs = obs_dict[imf]
+        
+        if sname == 'MBII':
+            if zs==0.5: 
+                obs = obs_dict['zs06']   
[…]

### 2022-03-29 projects/2020_HSC_to_numerical_simulation/check_distribuion_step2.py

@@ -1,0 +1,91 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Mar  3 10:18:00 2022
+
+@author: Dartoon
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import glob, pickle
+from sum_prep import imf_dict
+
+zs = 0.3
+consider_noise = False
+# Imag = [19.5, 20.0, 20.5, 21.0, 21.5, 22.0][2]
+
+# zs 0.3 Imag 19.5; zs 0.5 Imag 20.5; zs 0.7 Imag 21.5
+Imag_list = {0.3: 19.5, 0.5: 20.5, 0.7: 21.5}
+Imag= Imag_list[zs]
+
+files = glob.glob("offset_result/*{0}.txt".format(zs))
+if zs == 0.5 or zs == 0.7:
+    files = files+glob.glob("offset_result/*{0}.txt".format(0.6))
+files.sort()
+m_ml, b_ml = (0.981139684856507, -2.545890295477823)
+
+print(zs, Imag)
+n_flag = ''
+if consider_noise == False:
+    n_flag = '_nonoise'
+dis = {'MBII': 142.7, 'Illustris': 106.5, 'TNG100': 111, 'TNG300': 302, 'Horizon':142, 'SAM':100}
+hists = []
+labels = []
+for i in [3,2,1,4,5,0]:
+    label = files[i].split("/")[1].split('_')[0] 
+    
+    imf = imf_dict[label]
+    detlaM  = 0
+    if imf == 'Sal': 
+        detlaM = 0.23
+        
+    # if Imag == 22.0:
+    #     obs_dict, sim_dict = pickle.load(open(glob.glob('pickles/comb_zs{0}{1}.pkl'.format(zs,n_flag))[0],'rb'))
+    # else:
+    obs_dict, sim_dict = pickle.load(open(glob.glob('pickles/comb_zs{0}_Imag_{2}{1}.pkl'.format(zs,n_flag,Imag))[0],'rb'))
+        
+    if zs == 0.5 and Imag!=22.0:
+        _, sim_dict_ = pickle.load(open(glob.glob('pickles/comb_zs{0}_Imag_{2}{1}.pkl'.format(zs,n_flag,21.0))[0],'rb'))
+        sim_dict['MBII'] = sim_dict_['MBII']
+    
[…]

### 2022-03-29 projects/2020_HSC_to_numerical_simulation/offset_plot.py

@@ -12,72 +12,142 @@ import matplotlib.pyplot as plt
 import glob
 from matplotlib.ticker import AutoMinorLocator
 from scipy import stats
-
+import pickle
 import matplotlib as mat
 mat.rcParams['font.family'] = 'STIXGeneral'
 
-zs = 0.7
+zs = 1.5
+print_p = True
+print_dis = False
+
+
+consider_noise = True
+n_flag = ''
+if consider_noise == False:
+    n_flag = '_nonoise'
+
+Imag_list = {0.3: 19.5, 0.5: 20.5, 0.7: 21.5}
+
 files = glob.glob("offset_result/*{0}.txt".format(zs))
 if zs == 0.5 or zs == 0.7:
     files = files+glob.glob("offset_result/*{0}.txt".format(0.6))
 files.sort()
+
 ct = 0
+m_ml, b_ml = (0.981139684856507, -2.545890295477823)
 # fig, ax = plt.subplots(figsize=(8,7))
 # colors = ['green','steelblue','c','deeppink','plum','m']
 # colors = ['#1f77b4', '#ff7f0e', '#2ca02c', '#d62728', '#9467bd', '#8c564b', '#e377c2', '#7f7f7f', '#bcbd22', '#17becf']
 colors = ['orange','deepskyblue', 'steelblue', 'c', 'deeppink', 'deeppink', 'm']
 fig, axs = plt.subplots(len(files)+1, figsize=(5,8), sharex = True)
+
+from sum_prep import imf_dict
 for i in [3,2,1,4,5,0]:
-    data = np.loadtxt(files[i]) #nosl, sl, obs, sl_M*, sl_BH, obs_M*, obs_BH
-    if zs == 1.5:
-        data[:,2] = -data[:,2]
-        data[:,1] = -data[:,1]
+    label = files[i].split("/")[1].split('_')[0] 
+    imf = imf_dict[label]
+    detlaM  = 0
+    if imf == 'Sal': 
+        detlaM = 0.23
+    # data = np.loadtxt(files[i]) #nosl, sl, obs, sl_M*, sl_BH, obs_M*, obs_BH
+    # if zs == 1.5:
+    #     data[:,2] = -data[:,2]
+    #     data[:,1] = -data[:,1]
+    
+    # if Imag == 22.0:
+    #     obs_dict, sim_dict = pickle.load(open(glob.glob('pickles/comb_zs{0}{1}.pkl'.format(zs,n_flag))[0],'rb'))
+    # else:
+    if zs<1:
[…]

### 2022-03-29 projects/2020_HSC_to_numerical_simulation/prep_comparison.py

@@ -99,7 +99,7 @@ def EE(z):
 vec_EE=np.vectorize(EE)               #Perform the function EE in array style
 
 
-def Horizon_set(filename, HSC_Lbol_overall, HSC_MBHs_overall, zs, I_mag_break = 20.5, consider_type1= True, imf ='Sal'):
+def Horizon_set(filename, HSC_Lbol_overall, HSC_MBHs_overall, zs, I_mag_break = 20.5, consider_type1= True, imf ='Sal', no_noise = False):
     Horizon = {}
     # Stellar_Mass, BH_Mass, sdss_i_galaxy, sdss_g_galaxy, sdss_r_galaxy, sdss_i_pointsource, sdss_g_pointsource, Eddington_ratio = np.load(filename)
     texts = np.loadtxt(filename)
@@ -140,7 +140,11 @@ def Horizon_set(filename, HSC_Lbol_overall, HSC_MBHs_overall, zs, I_mag_break = 
         sdss_mag = g_pointsource #-2.5*np.log10(10**(-0.4*sdss_g_galaxy) + 10**(-0.4*sdss_g_pointsource))
     elif zs<0.5:
         sdss_mag= r_pointsource #-2.5*np.log10(10**(-0.4*sdss_r_galaxy) + 10**(-0.4*abs_sdss_r_pointsource))
-    dMBH, dmag, dMstar, dLbol= 0.4, 0.3, 0.2, 0.1  #dmag is for host magnitude. 
+    if  no_noise == False:
+        dMBH, dmag, dMstar, dLbol= 0.4, 0.3, 0.2, 0.1  #dmag is for host magnitude. 
+    elif no_noise == True:
+        dMBH, dmag, dMstar, dLbol= 0.001, 0.001, 0.001, 0.001  #dmag is for host magnitude. 
+    # dMBH, dmag, dMstar, dLbol= 0.4, 0.3, 0.2, 0.1  #dmag is for host magnitude. 
     # dMBH, dmag, dMstar, dLbol= 0.001, 0.001, 0.001, 0.001  #dmag is for host magnitude. 
     
     z_range = np.arange(0.2, 1.0, 0.05)
@@ -247,7 +251,7 @@ def EAGLE_set(filename, HSC_Lbol_overall, HSC_MBHs_overall, zs, I_mag_break = 20
     EAGLE['select_bool'] = select_bool
     return EAGLE
 
[…]

### 2022-03-29 projects/2020_HSC_to_numerical_simulation/sum_prep.py

@@ -15,14 +15,17 @@ import pickle
 # import matplotlib as mat
 # mat.rcParams['font.family'] = 'STIXGeneral'
 
+def lfit(x,m = 1/0.9811,c = 2.545/0.9811):
+    return m*x+c
+
 import copy
 ifplot = False
 # zs = 0.3
-imf_dict = {'MBII': 'Sal', 'SAM': 'Sal', 'TNG100': 'Cha', 'Illustris': 'Cha', 'Horizon': 'Sal'}
+imf_dict = {'MBII': 'Sal', 'SAM': 'Sal', 'TNG100': 'Cha', 'TNG300': 'Cha', 'Illustris': 'Cha', 'Horizon': 'Sal'}
 #%% Prep HSC data with dict as Sal and Cha
 from prep_comparison import HSC_set
 from prep_comparison import TNG_set, SAM_set, Horizon_set   #MBII and Illustris are loaded using TNG_set function
-def load_HSC_comp(zs):
+def load_HSC_comp(zs, I_mag_break=None, no_noise = False):
     HSC_dict = {}
     HSC_dict['Sal'] = HSC_set(zs, core = True, imf = 'Sal')
     HSC_dict['Cha'] = HSC_set(zs, core = True, imf = 'Cha')
@@ -30,10 +33,14 @@ def load_HSC_comp(zs):
     HSC_dict['Sal']['MBHs'] = HSC_dict['Sal']['HSC_MBHs']
     HSC_dict['Cha']['Mstar'] = HSC_dict['Cha']['HSC_Mstar']
     HSC_dict['Cha']['MBHs'] = HSC_dict['Cha']['HSC_MBHs']
-    if zs < 0.5:
-        I_mag_break = 20.5  #z~0.3
-    if zs >= 0.5:    
-        I_mag_break = 22.0    #z~0.7
+    I_mag_break_SAM = [20.5,22.0]
+    if I_mag_break is None:
+        if zs < 0.5:
+            I_mag_break = 20.5  #z~0.3
+        if zs >= 0.5:    
+            I_mag_break = 22.0    #z~0.7
+    else:
+        I_mag_break_SAM = [I_mag_break, I_mag_break]
     filename_dict = {}
     zs_MBII = 0.3
     if zs!= 0.3:
@@ -46,6 +53,7 @@ def load_HSC_comp(zs):
     if zs == 0.7:
         filename_dict['SAM'] = 'SAM/catalogue2.dat'
[…]

### 2022-04-08 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
draft updated

@@
 Finally, we investigate evolution as a function of stellar and \red{BH} mass, and argue that the most direct way to probe the co-evolution of galaxies and \red{BH}s is to increase the sensitivity, e.g., with JWST, thereby pushing to lower masses and minimizing possible biases arising from selection effects.
+\todo{Check if updated needed.}
 
@@
 The close correlations between \red{the mass of} supermassive black holes (\red{\mbh}) and the properties of their host galaxies (e.g., stellar mass\red{, \smass}) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
-To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over cosmic time \citep[e.g.,][]{Tre++04,Peng2006a, Tre++07, Woo++08, Jahnke2009, Bennert11, Schramm2013, Park15, Mechtley2016, Ding2020, 2021arXiv210902751L}.
-While, an {\it observed} evolution has been found \red{at redshift range xxx} in many studies \todo{move ref} in which the growth of BHs predates that of the host, other studies predict \todo{move ref} that BHs grow commensurately with galaxies.
-However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15}.
+To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over \red{cosmic time}.
+While, an {\it observed} evolution has been found \red{since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15, Ding2020, 2021arXiv210902751L} in} which the growth of BHs predates that of the host, other studies \red{predict \citep[e.g.,][]{Schramm2013, Sun2015} that} BHs grow commensurately with galaxies.
+However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15,Jahnke2009}.
 
@@
 In this scenario, star formation is inhibited by the heating and unbinding of a significant amount of gas.
-Alternatively, the mass relations can be explained through an indirect connection in which AGN accretion and star formation are fed through a common gas supply~\citep{Cen2015, Menci2016}.
-Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
+Alternatively, the mass relations can be explained through an indirect connection in which AGN accretion and star formation are fed through a common \red{gas supply~\citep{Cen2015, Menci2016, angles_black_2017}.
+}Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
 However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ compared to what is observed today.
@@
 Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution,
-including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH \red{simulations~\citep{Schaye2015, Crain2015, McAlpine2016},} Illustris moving-mesh \red{simulation~\citep{Genel2014, 2014MNRAS.444.1518V, Sijacki2015, Nelson2015, Li2019}} and the SIMBA \red{simulation~\citep{Thomas2019, Dave2019}.
+including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH \red{simulations~\citep{Schaye2015, Crain2015, McAlpine2016},} Illustris moving-mesh \red{simulation~\citep{Genel2014, 2014MNRAS.444.1518V, Sijacki2015, Nelson2015, Li2019}, the Horizon-AGN simulation~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D, 2016MNRAS.460.2979V}, and the SIMBA simulation~\citep{Thomas2019, Dave2019}.
 }
@@
 The typical error of \mbh\ are estimated to be 0.4 dex.
+\red{The mass ranges for the entire sample are log(\smass) $\in$ [9.0, 11.5] $M_{\odot}$, and log(\mbh) $\in$  [6.5, 10.0] $M_{\odot}$)}.
  We refer the reader to~\citet{Li2021a} in the Section~4.2 for more details.
@@
 \mbh\ is determined by \citet{Schulze2018} using near-infrared spectroscopic observations of the broad \halpha\ emission line with the recipe provided by~\citet{Vestergaard2006}, in a consistent manner to that adopted for HSC sample.
+\red{The mass ranges for the HST sample are log(\smass) $\in$ [9.5, 11.0] $M_{\odot}$, and log(\mbh) $\in$  [7.5, 9.0] $M_{\odot}$)}.
  We refer the reader to D20 for a more detailed description of the analysis.
@@
 \cline{1-6}
-{\bf AGN feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ radiative efficiency)} \\
+{\bf AGN feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ \red{radiative efficiency})} \\
 High acc. mode & 0.05 $\times$ 0.1 & 0.05 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.15 $\times$ 0.1 \\
@@
 $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$.
-\todo{The $\leq$ sign in the low accretion feedback mode of TNG is also not clear.
-Is it a fixed value or a distribution?} \todo{Please mention whether the same radiative efficiency is used to compute AGN luminosity in all the simulations.}
+\todo{Aklant: The $\leq$ sign in the low accretion feedback mode of TNG is also not clear.
+Is it a fixed value or a distribution?} \todo{Aklant: Referee asks us whether the same radiative efficiency is used to compute AGN luminosity in all the simulations.
+But we already show these values in Table 1, which are different, don't we?}
 }
@@
 
+\red{Note that each simulation adopt either a  \cite{2003PASP..115..763C} or a \cite{1955ApJ...121..161S} IMF.
+To make a self-consistent comparison, we ensure that the adopted IMF for the simulation and the observation are the consistent and to be the same.
+For numerical simulation, the mass is the base materials which are IMF independent.
+Actually, this assumption is still needed so that one can convert the observed luminosity to stellar mass to perform the comparison.}
+
 \subsection{{\tt MassiveBlackII} (MBII)}\label{subsec:MBII}
@@
 and $2\times1792^3$ particles.
-\todo{answer what is the factor 2 here.
+\todo{Aklant: answer what is the factor 2 here.
 A twin box with 1793$^3$ each?} The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}.
@@
 As a common practice, the stellar mass is obtained by using a 3D spherical aperture of 30~kpc to represent the observed stellar mass.
-We adopt this definition of stellar masses for all simulations described in the following sections.
-Using this definition, \citet{Pillepich2018} has shown that the corresponding stellar mass function is consistent with the observational measure.
+We adopt this definition of stellar masses for all \red{larger-scale cosmological} simulations described in the following sections, \red{except for Horizon-AGN which use total mass (see Section~\ref{subsec:Horizon}) for details.}  Using this definition, \citet{Pillepich2018} has shown that the corresponding stellar mass function is consistent with the observational measure.
 Even more, the stellar mass using this 3D aperture can achieve good agreement to those measured within the Petrosian radii in observational studies~\citep{Schaye2015}.
@@
 In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy.
-For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at~(irregular) intervals between which the BH mass grows by a fixed fraction.
-The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency.
+For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at irregular intervals between which the BH mass grows by a fixed fraction.
+\todo{Aklant: Referee asks are these irregular intervals included in the feedback modeling, or simply due to the time-varying accretion onto BHs?
+does it mean that the BH accretion is not modeled by the Bondi accretion between AGN feedback events?} The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency.
 Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN.
-As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy stellar mass, assuming a \cite{2003PASP..115..763C} IMF.
+As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy \red{stellar mass}.
+%, assuming a \cite{2003PASP..115..763C} IMF.
 
 \subsection{IllustrisTNG}
-{\it The Next Generation Illustris Simulations} \red{(IllustrisTNG)~\citep{2018MNRAS.475..676S, Pillepich2018, Naiman2018, Marinacci2018, Nelson2018}} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes.
+{\it The Next Generation Illustris Simulations} \red{(IllustrisTNG, hereafter, TNG)~\citep{2018MNRAS.475..676S, Pillepich2018, Naiman2018, Marinacci2018, Nelson2018}} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes.
 It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modeling, and 3) addressing the identified shortcomings of the previous generation simulations.
+\red{Note that TNG simulations employ a modified version of the Bondi formalism, with $c_s$ explicitly including a B term for these magneto-hydro simulations.}
 
@@
 The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation with a constant star formation efficiency $\epsilon_*=0.02$, which occurs in regions where the gas number density exceeds the star formation threshold $n_0 = 0.1\,\rm H\, cm^{-3}$.
-A Salpeter IMF is assumed.
-Stellar feedback is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources.
+%A Salpeter IMF is assumed.
+\red{Stellar feedback} is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources.
 
@@
 Only galaxies with more than 50 particles are considered.
-The galaxy mass corresponds to the total stellar mass of a galaxy identified with this approach.
-The stellar mass function is shown in \cite{2017MNRAS.467.4739K} to be in good agreement with observations.
+\red{Identified with this approach, for Horizon-AGN, the adopted galaxy mass corresponds to the total stellar mass of a galaxy, which is different than the other hydrodynamic simulations (i.e., within a 3D 30~kpc spherical aperture.
+The Horizon-AGN's stellar mass by this definition is commonly used, whose stellar mass function is known} in \citet{2017MNRAS.467.4739K} to be in good agreement with observations.
+%\todo{Mention that the \smass.}
 
@@
 \caption{\label{fig:selection}Demonstration of AGN selection using MBII.
-{\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles).
+{\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles) \red{for sample at redshift $z=0.6$}.
 A matched HSC sample is shown by the orange data points.
 The light green background cloud shows the {\it intrinsic} simulated number density in this parameter space.
+\red{Note that this is the first  step of the sample selection.
+We future use AGN magnitude cut to assure that the simulation sample present similar $L_{\rm bol}$ distribution (e.g., see Figure~\ref{fig:offsets_nochange}-left) and \mbh\ distribution with the observation.
+We then use the same \smass\ cut to collect the final sample.}
 {\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample.
-For visual comparison between the HSC and HST selection, we show the region of the HST selection window in the left panel as dashed lines.
-\todo{No mention of the redshift in Fig.2}
+% For visual comparison between the HSC and HST selection, we show the region of the HST selection window in the left panel as dashed lines. % \todo{No mention of the redshift in Fig.2}
 }
@@
 In each halo, we compute the fraction of gas which cools because of the atomic processes and settles into a disk~\citep{Mo1998}.
-The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr, according to BH feeding; \todo{the link between BH feeding and star formation channels in this sentence is not clear.} (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion).
+The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr, according to BH feeding; \todo{Nicola: the link between BH feeding and star formation channels in this sentence is not clear.} (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion).
 The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation which returns a fraction of the disk gas into a hot phase.
-A Salpeter IMF is adopted in the SAM simulation.
-A $\Lambda$CDM power spectrum of perturbations with a total matter density parameter $\Omega_0=0.3$, a baryon density parameter
+%A Salpeter IMF is adopted in the SAM simulation.
+\red{A $\Lambda$CDM power} spectrum of perturbations with a total matter density parameter $\Omega_0=0.3$, a baryon density parameter 
 $\Omega_b=0.04$, a dark energy density parameter $\Omega_\Lambda=0.7$, and a Hubble constant $h$=0.7 is adopted.
@@
 We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = \red{0.2}~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.
+\red{Since the selection based on $L_{\rm bol}$ has limited effects in this study (see Section~\ref{sec:dis} and Figure~\ref{fig:offsets_nochange} for details), the AGN variability correction is not considered.}
 
@@
 
-HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should match the relationship between \mbh-$L_{\rm bol}$ as seen in the HSC sample.
-We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it top}).
+\red{Comparing with} HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should match the relationship between \mbh-$L_{\rm bol}$ as seen in the HSC sample.
+We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it \red{left}}).
 (2) The $i$-band magnitude of the AGN are bright (see Section~\ref{sec:hsc}).
-The specific selection is made as follows: for systems at $z<0.5$ and $z>0.5$, the AGN $i$-band magnitude is required to be brighter than 20.5 mag and 22.0 mag, respectively.
+%The specific selection is made as follows: for systems at $z<0.5$ and $z>0.5$, the AGN $i$-band magnitude is required to be brighter than 20.5 mag and 22.0 mag, respectively.
+\red{The specific selection is made as follows: a value of AGN $i$-band magnitude is selected to make the sample selection so that the $L_{\rm bol}$ distribution is similar to the observation (see Section~\ref{sec:dis} for details).
+}
 Since the simulations do not provide the observed AGN magnitude, we adopt a simulated rest-frame magnitude or L$_{\rm 5100}$ and assume the quasar continuum as a single power-law with an index of $\alpha_\nu=-0.44$~\citep{2001AJ....122..549V} to calculate the observed $i$-band magnitude.
@@
 
-HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example).
-Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., between [7.7, 8.6] $M_{\odot}$).
+\red{Comparing with} HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example).
+Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., \red{log(\mbh)} between [7.7, 8.6] $M_{\odot}$).
 The HST sample covers the higher redshift range $1.2<z<1.7$, which is considered as a single redshift bin to make the comparison with the simulations at $z=1.5$.
 
-\todo{A little discussion on the \smass\ P16. And address the properties what does it mean by intrinsic. P9+P12}
+%\todo{Address the properties what does it mean by intrinsic. P9+P12}
 
@@
 %\todo{Explain the offset depends.}
-\red{For comparison purpose, the local scaling relation introduced by D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion.
-\todo{Explain how D20's local is obtained and why it is IMF related.
-P10}}
-
+\red{For comparison purpose, the local scaling relation introduced by D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF based\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion.
+This local relation is derived by fitting the \mbh-\smass\ relations using 55 local galaxies by~\citet{Bennert++2011} and \citet{H+R04}, in which \smass\ measurements are Chabrier IMF based.}
 \red{For each sample, we focus on the \mbh\ residuals\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the y-axis) and calculating their mean and the standard deviation to make comparisons with the observation.}
 
-\red{As introduced in previous section, to make direct comparison, the simulation sample is processed in two steps: inject observational noise injection, and apply equivalent selection.
+\red{To make direct comparison, the simulation sample is processed in two steps: inject observational noise injection, and apply equivalent selection.
 In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
@@
 For the initial one, it has been known~\citep[e.g.,][Figure 2]{Habouzit2021} and can be seen in Figure~\ref{fig:comparsion} that the initial offset values vary at different stellar mass range, and thus the mean and standard derivation could not represent the entire distribution.
-The discussion of this initial offset is also beyond the scope of this work.
-We focus on the other two offset value distributions in this work.
+The discussion of this initial offset is also beyond the scope of this work.}
+
+\red{We focus on the other two offset value distributions in this work.
 To aid in visualization of the differences among the various simulations compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}.
 Each panel presents a different redshift range.
-In addition, the values of the central offset and scatter for before and after considering the noise are presented in Table~\ref{tab:sum} (after noise).
-The interpolations and the comparison with the observations are presented in the rest of this section.
-}
-\todo{Read to avoid description (intrinsic and then noise).}
+In addition, the values of the central offset and scatter for before and after considering the noise are presented in Table~\ref{tab:sum}.
+The interpolations and the comparison with the observations are presented in the rest of this section.}
+\todo{s: Read again to avoid description conflict (intrinsic and then noise).}
 %For the initial level, it has been known that the offset depended by range of the stellar mass and thus it is less meaningful to make comparison in this work.
+
+%\todo{Discussion how random make difference on the scatter. P13}
+%\red{We performed the 1000 times realizations for the comparison of each sample to estimate the uncertainties of the values in Table~\ref{tab:sum} arises by the random scatter.
+We find that the uncertainty level of the }
 
@@
 \centering
-\includegraphics[trim = 50mm 70mm 40mm 90mm, clip,height=1.1\textwidth]{MM_sum.png}
+\includegraphics[trim = 40mm 70mm 30mm 90mm, clip,height=1.1\textwidth]{MM_sum.png}
 \caption{\label{fig:comparsion} 
@@
 The black line in each panel indicates the local relation adopted by~\citet{Ding2020}.
-The background cloud (in green and yellow) shows the intrinsic simulation number density before injecting random noise and applying selection effects.
+The background cloud (in green and yellow \red{with contours}) shows the intrinsic simulation number density before injecting random noise and applying selection effects.
 Only TNG100 is presented here since TNG300 presents very similar results \red{(see discussion section)}.
@@
 To this end, we measure the scatter of the simulation sample without injecting random noise but adopting the same selection window for both $z<1$ and $z>1$ samples to infer the central offset and scatter.
-We find that the intrinsic scatter is at a level of $\sim0.15-0.2$ dex for both $z<1$ and $z>1$ (see Table~\ref{tab:sum_no_noise}).
+We find that the intrinsic scatter is at a level of $\sim0.15-0.2$ dex for both $z<1$ and $z>1$ (see Table~\ref{tab:sum}).
 These levels are consistent with the {\it intrinsic} scatter as estimated using observation data alone~\citep{Ding2020, 2021arXiv210902751L}.
@@
 The mean values for observed sample (i.e., yellow lines) are also show in each simulation plots.
-\red{For the simulation samples, their offset distribution without adding noise is shown using black line.}
+\red{To address the noise effect, the offset distributions of the simulation without adding noise are also shown using black line.}
 For the MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$. 
@@
 The black line shows the evolution by fitting the offset as a function of redshift.
-The predictions from the numerical simulations, given in Table~\ref{tab:sum}, are presented by different colored symbols.
-The grey horizontal band illustrates the level of dispersion for the local sample \red{from D20}.
+\red{The black dots (error bars) are the mean (standard deviation) value of the observations at the four redshift bins.
+The \smass\ and \mbh\ ranges are different at each redshift bins, which are indicated in Figure~\ref{fig:comparsion}.} The predictions from the numerical simulations, given in Table~\ref{tab:sum}, are presented by different colored symbols.
+The grey horizontal band illustrates the level of dispersion for \red{D20's} local sample.
 }
@@
 
-\subsection{Global offsets}
+\subsection{Global offsets}\label{subsec:offset}
 We examine the offsets to understand whether the simulations deviate or not from the {\it observed} scaling relation with particular attention to changes with redshift.
@@
 These results are consistent with the Kolmogorov-Smirnov (KS) test performed using the offset distributions between each simulated sample and the observed sample --- the p-values are given in Table~\ref{tab:pvalue} showing that Horizon-AGN and Illustris have a good statistical match to the scaling relation at $z<0.6$ (i.e., p-value $> 0.1$), while the TNG100, TNG300 and Horizon-AGN simulation do well at $z>0.6$.
-Overall, we find that the mass ratios between \red{supermassive BH}s and their host galaxies are generally consistent between observations and simulations with some subtle differences which are not at the level of concern for this present study.
-\todo{To add that 4/6 of the simulations have decreasing mass offsets from z=0.2 and 0.6 while the offsets from the observations increase with redshift all the way (Fig. 5). P15}
+\red{We also see that, except MBII and Horizon-AGN, all the other simulations have the mass offset that are decreasing from $z=0.2$ to $z=0.6$, while the observations have offset value increase with redshift all the way up to $z\sim1.5$.
+However, this inconsistency is well below a $1-\sigma$ scatter level.}
+Overall, we find that the mass \red{correlation} between \red{supermassive BH}s and their host galaxies are generally consistent between observations and simulations with some subtle differences which are not at the level of concern for this present study.
+%\todo{To add that 4/6 of the simulations have decreasing mass offsets from z=0.2 and 0.6 while the offsets from the observations increase with redshift all the way (Fig. 5). P15}
+%\todo{Update with MBII's new result. }
 %\todo{shift offset at 0.3 and discussion the difference. P11}
@@
 
-Interestingly, we notice that MBII and Illustris have \red{BH}s intrinsically under-massive relative to their galaxies at the lower masses that reach the local relation at higher masses.
-In contrast, TNG and Horizon-AGN have \red{BH}s slightly elevated from the local relation at most masses.
+Interestingly, we notice that MBII and Illustris have \red{BH}s intrinsically under-massive relative to their galaxies at the lower masses that reach the \red{D20 local scaling} relation at higher masses.
+In contrast, TNG and Horizon-AGN have \red{BH}s slightly elevated from \red{D20} local relation at most masses.
 These differences between simulations present two different scenarios, either one where the \red{BH}s come later or co-evolution with the two growing in tandem.
@@
 In fact, after noise and selection is applied, the simulated sample exhibits very small offsets which agree remarkably well with the observed data.
-This result underscores the importance of taking into account errors and selection --- without accounting for those, one could erroneously interpret an apparent trend as evolution in the opposite sense as the true one.
+\red{Upon this, one interpretation is that depending on the BH population in the Universe, the observations of AGN such as our HSC sample, do not inform us of the true \mbh\ offsets as a function of \smass.}  This result underscores the importance of taking into account errors and selection --- without accounting for those, one could erroneously interpret an apparent trend as evolution in the opposite sense as the true one.
 The most direct way to circumvent these issues is to probe lower masses (\smass\  $<10^{10}M_{\odot}$) using a more sensitive instrument, such as JWST~\citep{Habouzit2022} across this redshift range \citep[see also][]{2011MNRAS.417.2085V}.
-\todo{highlight the selection effect that the offset doesn't reflect the truth. P20}
+%\todo{highlight the selection effect that the offset doesn't reflect the truth. P20}
 
@@
 \end{tabular}
-\caption{\label{fig:deltaMM} Comparison of the offset of the \mbh\ (to the local relation) as a function of stellar mass from observation data and the simulations at $z\sim0.7$.
-In each stellar mass bin, we give the mean and standard derivation of the offset values.
-The histograms on the right indicate the offset distribution with lines marking the mean offsets for observation and simulation.
-The green color distributions show the intrinsic simulated sample without random noise and selection applied.
+\caption{\label{fig:deltaMM} Comparison of the offset of the \mbh\ (to the \red{D20 local scaling} relation) as a function of stellar mass from observation data and the simulations at $z\sim0.7$.
+In each stellar mass bin \red{(minimum number of objects are larger than 6)}, we give the mean and standard derivation of the offset values.
+\red{To consider the random noise, we use ten times realizations's average to calculate the mean and standard derivation in each bin.} The histograms on the right indicate the offset distribution with lines marking the mean offsets for observation and simulation \red{using all the galaxy sample}.
+The green color distributions \red{with contours show the intrinsic simulated sample distribution} without random noise and selection applied.
 }
@@
 \begin{deluxetable*}{lccccc}
-\tablecaption{Summary of the central offsets and scatters\label{tab:sum}}
+\tablecaption{\red{Summary of the central offsets and scatters\label{tab:sum}}}
 %\tablewidth{0pt}
@@
 Observation & (0.12$\pm$0.51) & (0.20$\pm$0.50)  & (0.21$\pm$0.56)  & (0.43$\pm$0.31) & \\
-SAM & (0.72$\pm$0.20)$\rightarrow$(0.73$\pm$0.49) & (0.64$\pm$0.18)$\rightarrow$(0.65$\pm$0.46)  &(0.56$\pm$0.16)$\rightarrow$(0.51$\pm$0.45)  &  (0.08$\pm$0.18)$\rightarrow$(0.51$\pm$0.36) & Salpeter \\
-MBII & (-0.15$\pm$0.21)$\rightarrow$(-0.15$\pm$0.48) & \multicolumn{2}{c}{[$z=0.6$] (-0.15$\pm$0.22)$\rightarrow$(-0.16$\pm$0.48)}  & (0.08$\pm$0.19)$\rightarrow$(0.14$\pm$0.31) & Salpeter\\
-Illustris & (0.03$\pm$0.32)$\rightarrow$(0.01$\pm$0.52) & (0.10$\pm$0.36)$\rightarrow$(0.08$\pm$0.53)  &(0.08$\pm$0.36)$\rightarrow$(0.06$\pm$0.54)  &  (0.04$\pm$0.19)$\rightarrow$(0.07$\pm$0.32) &  Chabrier \\
-TNG100 & (0.27$\pm$0.20)$\rightarrow$(0.27$\pm$0.48) & (0.27$\pm$0.15)$\rightarrow$(0.24$\pm$0.46)  &(0.26$\pm$0.16)$\rightarrow$(0.24$\pm$0.45)  &  (0.36$\pm$0.15)$\rightarrow$(0.38$\pm$0.33) & Chabrier \\
-TNG300 & (0.25$\pm$0.21)$\rightarrow$(0.26$\pm$0.48) & (0.19$\pm$0.23)$\rightarrow$(0.20$\pm$0.48)  &(0.20$\pm$0.22)$\rightarrow$(0.17$\pm$0.48)  &  (0.32$\pm$0.16)$\rightarrow$(0.41$\pm$0.34) & Chabrier \\
-Horizon & (0.19$\pm$0.26)$\rightarrow$(0.16$\pm$0.49) & (0.18$\pm$0.21)$\rightarrow$(0.14$\pm$0.47)  &(0.28$\pm$0.20)$\rightarrow$(0.23$\pm$0.47)  &  (0.37$\pm$0.13)$\rightarrow$(0.47$\pm$0.35) & Salpeter\\
-%SAM & (0.72, 0.20) $\rightarrow$ (0.73, 0.49) & (0.65, 0.46)  & (0.51, 0.45)  & (0.51, 0.36) & Salpeter \\
-%Illustris & (0.03, 0.32) $\rightarrow$ (0.01, 0.52) & (0.08, 0.53)  & (0.06, 0.54)  & (0.07, 0.32) &  Chabrier \\
-%TNG100 & (0.27, 0.20) $\rightarrow$ (0.27, 0.48) & (0.24, 0.46)  & (0.24, 0.45)  & (0.38, 0.33) & Chabrier \\
-%TNG300 & (0.25, 0.21) $\rightarrow$ (0.26, 0.48) & (0.20, 0.48)  & (0.17, 0.48)  & (0.41, 0.34) & Chabrier \\
-%Horizon & (0.19, 0.26) $\rightarrow$ (0.16, 0.49) & (0.14, 0.47)  & (0.23, 0.47)  & (0.47, 0.35) & Salpeter\\
+SAM & (0.75$\pm$0.22)$\rightarrow$(0.72$\pm$0.48) & (0.64$\pm$0.17)$\rightarrow$(0.63$\pm$0.49)  &(0.55$\pm$0.16)$\rightarrow$(0.55$\pm$0.44)  &  (0.52$\pm$0.18)$\rightarrow$(0.50$\pm$0.34) & Salpeter \\
+MBII & (0.13$\pm$0.25)$\rightarrow$(0.13$\pm$0.48) & \multicolumn{2}{c}{[$z=0.6$] (0.22$\pm$0.23)$\rightarrow$(0.18$\pm$0.48)}  & (0.08$\pm$0.19)$\rightarrow$(0.14$\pm$0.31) & Salpeter\\
+Illustris & (0.17$\pm$0.31)$\rightarrow$(0.21$\pm$0.49) & (0.17$\pm$0.38)$\rightarrow$(0.20$\pm$0.49)  &(0.32$\pm$0.36)$\rightarrow$(0.17$\pm$0.54)  &  (0.04$\pm$0.19)$\rightarrow$(0.07$\pm$0.32) &  Chabrier \\
+TNG100 & (0.26$\pm$0.24)$\rightarrow$(0.28$\pm$0.49) & (0.27$\pm$0.15)$\rightarrow$(0.24$\pm$0.44)  &(0.25$\pm$0.17)$\rightarrow$(0.21$\pm$0.52)  &  (0.36$\pm$0.15)$\rightarrow$(0.38$\pm$0.33) & Chabrier \\
+TNG300 & (0.25$\pm$0.22)$\rightarrow$(0.25$\pm$0.49) & (0.21$\pm$0.23)$\rightarrow$(0.22$\pm$0.47)  &(0.22$\pm$0.22)$\rightarrow$(0.19$\pm$0.47)  &  (0.32$\pm$0.16)$\rightarrow$(0.41$\pm$0.34) & Chabrier \\
+Horizon-AGN & (0.21$\pm$0.22)$\rightarrow$(0.21$\pm$0.47) & (0.21$\pm$0.21)$\rightarrow$(0.23$\pm$0.49)  &(0.29$\pm$0.19)$\rightarrow$(0.24$\pm$0.46)  &  (0.37$\pm$0.13)$\rightarrow$(0.47$\pm$0.35) & Salpeter\\
 \enddata
@@
 \tablecomments{This table collects the comparison results of the \smass-\mbh\ correlations between different simulation at different redshift.
-The value shows the central position offset to the local relation and the scatters measured around the local relation after applying the offset.
+The value shows the central position offset to the \red{D20 local scaling} relation and the scatters measured around the local relation after applying the offset.
 A positive offset means the \mbh\ value predicted by the simulation is higher than the local relationship measurement at fixed \smass\ value.
@@
 For the MBII sample, the simulation does not produce the sample at $z=0.5$ or $z=0.7$, but rather at $z=0.6$.
-We use Monte Carlo approach to infer the uncertainties of the values in the table, finding that the uncertainties are within $\pm 0.03$.
+We use Monte Carlo approach \red{with 500 realizations} to infer the uncertainties of the values in the table, finding that the uncertainties are within $\pm 0.03$.
 }
@@
 \section{Discussion} \label{sec:dis}
-\todo{TNG100 and TNG300 -- explain the why no difference between TNGs.
+%\todo{Discussion when shift offset as z=0.3. P11}
+\red{In our comparison work, the mass offsets are compared to the relation derived in the local Universe.
+In fact, the different simulations could have different mean relations at $z=0$~\citep[e.g.,][]{Habouzit2021}.
+The interpretation of how BH mass offset of the simulation increasing with redshift with respect to the D20 local scaling relation can be different than using the simulations' own local relation.
+Moreover, even though the effect is very limited, the galaxy mass of the Horizon-AGN sample is the total stellar mass; while all the other hydrodynamic simulations' are determined within the 3D 30 kpc spherical aperture.
+Thus, to compare the evolution even more fair, we manually shift all the simulation's relation to the same position as the observation one at $z=0.3$ in Figure~\ref{fig:offsets_vz_shiftz03} where the offset evolution trend can be seen more clear.
+In general, the new result show that the evolution for the simulations are consistent with our interpretations in Section~\ref{subsec:offset}.
+This result can be expected since most of the simulation have demonstrated good offset match to the observation at redshift $z=0.3$.
+} %Furthermore, the MBII simulation result becomes very close with observation from across all redshift range, indicating that its prediction of \mbh\ mass offset evolution actually are very consistent with the observation.}
+
+%\todo{TNG100 and TNG300 -- explain the why no difference between TNGs.
 P8}~\red{We note that TNG100 and TNG300 yield very similar comparison results, thus only TNG100 is presented in~Figure~\ref{fig:comparsion}}.
+\red{In the literature~\citep{Weinberger2018, Habouzit2021}, it have been noted that the correlation predicted by TNG300 and TNG100 are not identical.
+For example, with larger volume, TNG300 process larger scatter of \mbh\ at fixed \smass\ than TNG100 (at \smass  $>10^{10}M_{\odot}$).
+Also, since in TNG100 the BH growth is more efficient, the BH mass function in TNG100 is found to be at higher normalization at low BH mass end.
+In our result, the difference between TNG100 and TNG300 also exist.
+However, since the compared samples have been processed with selection effect and/or random noise injection, such a difference became very slight.}
+\todo{The referee says TNG300 has larger scatter, but in Habouzit2021 section 4.2.2, it actually says scatter in TNG300 is smaller. Any one know if the referee is wrong?}
 
-\todo{QSO selection. Lbol vary and QSO II type. P7}
+\red{We collected all the available simulation sample to perform the comparison, and thus the number of points that used from the simulation are not designed by us.
+Despite that the observational samples are volume-unlimited and the simulated sample are thus not volume-matched, fortunately, the volume of all the simulation appears to be sufficient $-$ all of them can present similar (or more) amount of data points to compare with the observation (see Figure~\ref{fig:comparsion}).
+Also, the similar results are inferred using smaller and larger volume simulation, i.e., TNG100 and TNG300, which reflect the fact that the simulation's volume has reached to a sufficient level to be compared with observation.}
 
-\todo{Discussion when shift offset as z=0.3. P11}
+\red{To make a fair comparison, we performed the same sample selection so that the $L_{\rm bol}$ and \mbh\ distribution are also similar.
+Furthermore, we also assured that the \smass\ are compared at the similar range.
+In fact, we find that our comparison result are very robust; we tested to change our selection that generate a very different $L_{\rm bol}$ distribution, the offset distribution of all the simulations are almost identical (see demonstrations in Figure~\ref{fig:offsets_nochange}).
+This test implies that even consider the situation of AGN variability ($10-20\%$ level flux variation) and obscuration (i.e., removing a certain fraction of the sample) at extreme level, our result are still valid .
+}
 
-\todo{Discussion how random make difference on the scatter. P13}
+\begin{figure*}
+\centering
+\begin{tabular}{c c c}
+\hspace*{-0.4cm} 
+{\includegraphics[trim = 25mm -10mm 20mm 15mm, clip, height=0.3\textwidth]{Lbol_dis_zs05_Imag205.pdf}}&
+\hspace*{-0.4cm} 
+{\includegraphics[trim = 25mm -10mm 20mm 15mm, clip, height=0.3\textwidth]{Lbol_dis_zs05_Imag215.pdf}}&
+\hspace*{-0.4cm} 
+{\includegraphics[height=0.4\textwidth]{offset_dis_z05_different_selectImag.pdf}}\\
+\end{tabular}
+\caption{\label{fig:offsets_nochange} 
+\red{Different bolometric luminosity selection of the comparison sample and the changes of the comparison result.
+{\it left:}~The $L_{\rm bol}$ distribution of samples at redshift $z=0.5$ that according to the selection choose made in this work.
+The simulation sample presents good match with the observation.
+{\it middle:} Using different magnitude threshold to select the sample.
+As result, the distribution of the simulation are much different with the observation.
+{\it right:} The difference of the offset by these two selection (dashed line is the new selection result).
+As shown, the changes by different selection based on $L_{\rm bol}$ values have very limited effects on our result.}
+}
+\end{figure*}
 
-\todo{Discussion on the \smass of the simulation and why IMF is part of the picture. P16}
+\begin{figure}
+\centering
+\includegraphics[height=0.4\textwidth]{offset_summary_vz_shiftz03.pdf}
+\caption{\label{fig:offsets_vz_shiftz03} 
+\red{Same as Figure~\ref{fig:offsets_vz} but shift all the simulation's result to the observation at $z=0.3$.
+After this recalibrating, the MBII's result appears to match very well with the observation.}
+}
+\end{figure}
+
+%\todo{Some discussion on BH spin. What does consistent means? P9, P12 and P18.}
+\red{We considered all the known observational effects, including the sample selection and random noise injection, and applied to the first-hand products of the simulation in order to directly compare with observations.
+Our result shows that the scatter between observation and simulation are very similar.
+Considering that the observation and simulation sample has went through the same observational process, this result is {\it consistent} with the fact that the intrinsic of the simulation (i.e., the first-hand product) and the observation are similar.
+Of course, there are limitations in our comparisons and this {\it consistency} doesn't necessarily mean their intrinsic must be the same.
+On the one hand, there is always unknown-unknown in the observational effects that haven't applied to the simulation yet.
+On the other hand, even the state-of-the-art simulations could not capture all the physical aspects that impact the scatter.
+For example, the spin of BHs is not modeled in the simulation the which could change the scatter since the spin affects to both the accretion the energy that can be released by AGN feedback \citep{Dubois2014, 2019MNRAS.490.4133B, Habouzit2021} at some level.
+Even though the spin effect is still not well known and the study of the spin effect in detail is beyond the scope of this paper, the comparison work are needed be done once these simulations considered spin in the future.
+ \todo{Xuheng checked the cited reference but could not find quantitively how much this spin will change the simulation scatter.}
+}
 
@@
 The simulations include a semi-analytic model (SAM) and five hydrodynamic simulations, i.e., MBII, Illustris, TNG100, TNG300 and Horizon-AGN.
-We carried out the comparisons in the observed pararameter space to account for uncertainties and selection effects.
+We carried out the comparisons in the observed parameter space to account for uncertainties and selection effects.
 To achieve this, we first injected random errors with the same observational uncertainty to the simulation, and then adopted the same selection condition to the simulation data (see Figure~\ref{fig:selection}).
-Finally, we adopted the scaling relation from the local universe as our reference and performed comparisons using the scatter of the measurements and their central offset to the local relation.
+Finally, we adopted the scaling relation from the local universe as our reference and performed comparisons using the scatter of the measurements and their central offset to the \red{D20 local scaling} relation.
 Our main results are summarized as follows:
@@
 we re-run the estimation without injecting noise to the simulations.
-The obtained scatter for both $z<1$ and $z>1$ are at a similar level (i.e.,  $\sim$0.15$-$0.2 dex, see Table~\ref{tab:sum_no_noise}), indicating that observational errors dominate the scatter.
+The obtained scatter for both $z<1$ and $z>1$ are at a similar level (i.e.,  $\sim$0.15$-$0.2 dex, see Table~\ref{tab:sum}), indicating that observational errors dominate the scatter.
 
-\item{} Regarding the \red{offsets of the scaling relation from the local} ($\Delta$\mbh\ at a given \smass), all simulations generally match the observations with some subtle, yet notable, differences.
-While Illustris and Horizon-AGN show good correspondence with observations at $z<0.6$, the comparisons at $z>0.6$ are better for SAM, TNG100, TNG300 and Horizon-AGN.
+\item{} Regarding the \red{offsets of the scaling relation from the D20 local} ($\Delta$\mbh\ at a given \smass), all simulations generally match the observations with some subtle, yet notable, differences.
+While Illustris\red{, MBII,} and Horizon-AGN show good correspondence with observations at $z<0.6$, the comparisons at $z>0.6$ are better for SAM, \red{MBII,} TNG100, TNG300 and Horizon-AGN.
 From $z\sim0.7$ to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
+\red{Despite that the offset difference between $z=0.2$ and $z=0.6$ is well below the observed scatter, 4/6 of the simulations have decreasing mass offset from $z=0.2$ and $z=0.6$ while the observation mass offset are increasing with redshift all the way.}
+%\todo{To add that 4/6 of the simulations have decreasing mass offsets from z=0.2 and 0.6 while the offsets from the observations increase with redshift all the way (Fig. 5). P15}
+\end{enumerate}
 
-\todo{To add that 4/6 of the simulations have decreasing mass offsets from z=0.2 and 0.6 while the offsets from the observations increase with redshift all the way (Fig. 5). P15}
-
-\end{enumerate}
-\todo{For clarity the first paragraph after 3) should specify the stellar mass range considered when discussing the scatter of the local relation etc.}
-The absolute value of stellar masses in both observation and theory have significant uncertainty (up to factor of two), which depends on the assumption of initial mass function, and possibly on the implementation of star formation in the models.
-\todo{If this sentence includes the simulations, then the stellar mass of the galaxies also depends on other subgrid models such as supernova feedback, AGN feedback.} In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematic effect.
+%\todo{For clarity the first paragraph after 3) should specify the stellar mass range considered when discussing the scatter of the local relation etc.}
+\red{These results are inferred by studying the sample with stellar mass mainly with the range [9.5, 11.5] $M_{\odot}$. Note that
+the} absolute value of stellar masses in both observation and theory have significant uncertainty (up to factor of two)\red{.
+For example, for the observation, the \smass\ of the galaxies depends on the assumption of initial mass function, possibly on the implementation of star formation in the models; for the simulation, the \smass\ depends on their definition (i.e., total mass or within 30~kpc aperture), and other subgrid models such as supernova feedback, AGN feedback.} In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematic effect.
 Thus, in this work, we first consider the scatter as a diagnostic criteria to see whether some simulations match the data better than others.
@@
 The simulations studied in this work have adopted completely different numerical techniques.
-However, all of them can provide good agreement with the observed dispersion in the scaling relation.
+However, all of them \red{have similar tightness intrinsic scaling relation and thus provide good agreement with the observation in terms of the sample dispersion}.
 In fact, the tightness of the scaling relation is stem from the same physics assumed in these simulations (i.e., AGN feedback).
-Thus, the consistency of the scatter between simulation and observations is consistent with the hypothesis that the AGN feedback as a causal link between \red{supermassive BH}s and their hosts plays a key role in establishing the scaling relation.
-\todo{AGN feedback, causal link? P18}
+Thus, \red{our result} is {\it consistent} with the hypothesis\footnote{\red{As discussed in the Section~\ref{sec:dis}, by saying `consistent', we do not mean this hypothesis is the unique interpretation  which rule out the other possible models.}} that the AGN feedback as a causal link between \red{supermassive BH}s and their hosts plays a key role in establishing the scaling relation.
+%\todo{P18: AGN feedback, causal link?}
 
@@
 In theoretical models, AGN feedback is often assumed to consist of two distinct modes:
-a quasar-heating mode where the \red{BH} accretion rates are comparable to the Eddington rate and a radio-jet mode occurring at low accretion rates (see e.g.
-Section~\ref{subsec:Horizon}).
+a quasar-heating mode where the \red{BH} accretion rates are comparable to the Eddington rate and a radio-jet mode occurring at low accretion rates (see, e.g., Section~\ref{subsec:Horizon}).
 In high redshift universe, the cold material in early universe leads to the vigorous accretion to the \red{supermassive BH} which drives the high accretion rates, and thus the quasar mode dominates the feedback.
 At low redshift, the star formation and feedback ejection reduce the cold material leading to a lower accretion rate and a radio-mode-dominating feedback~\citep[e.g.][]{2012MNRAS.420.2662D,2016MNRAS.460.2979V,2018MNRAS.479.4056W}.
-Our comparison result shows that the level of intrinsic scatter in the scaling relation at redshifts up to 1.7 is consistent with the low redshift one (see Table~\ref{tab:sum_no_noise}), which reveals the fact that at high redshift the AGN feedback described by the quasar mode has already regulated the tight correlation between \red{supermassive BH} and its host galaxy.
+Our comparison result shows that the level of intrinsic scatter in the scaling relation at redshifts up to 1.7 is consistent with the low redshift one (see \red{Table~\ref{tab:sum})}, which reveals the fact that at high redshift the AGN feedback described by the quasar mode has already regulated the tight correlation between \red{supermassive BH} and its host galaxy.
 After that, the radio-jet mode starts to take control at low redshift by maintaining the tightness of the scaling relation till the level we observe today.
-\todo{P19.}
+\todo{Address referee's P19 (to talk with John).
+Some discussions on the two modes.
+I plot a figure 9 for to understand it (see Figure~\ref{fig:fedd}).}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.4\textwidth]{Horizon_fedd_dis.pdf}
+\caption{\label{fig:fedd} 
+\red{Distribution of the Eddington ratio and \mbh\ for Horizon sample at high and low redshift range.
+Most of the sample at $z=1.5$ are adopted at quasar mode (i.e., $f_{\rm Edd}>0.01$).
+The distribution are in the radio-jet mode ($f_{\rm Edd}<0.01$) at $z=0.3$.}
+}
+\end{figure}
 
@@
 However, beyond $z>0.2$, the scatter and the central distribution of the scaling relations are dominated by measurement uncertainty and selection effects (see Figures~\ref{fig:comparsion} and~\ref{fig:deltaMM}) and a forward modeling in the observational plane becomes essential.
-For example, from trends seen with stellar mass in Illustris and MBII (Figure~\ref{fig:deltaMM}), selection effects may hamper our understanding of whether BHs and their hosts co-evolve or not.
+\red{Indeed, those effects would hamper our understanding of whether BHs and their hosts co-evolve or not.
+For example, from trends seen with stellar mass in Illustris and MBII (Figure~\ref{fig:deltaMM}), we found that the observations of the \mbh\ offsets as a function of \smass\  show a very different trend to the intrinsic one.}
 
-Extending this study to even higher redshift (and lower mass galaxies, \smass\ $<10^{10}M_{\odot}$) will be very beneficial, probing closer to the epoch of formation of massive galaxies and \red{supermassive BH}s.
+Extending this study to even higher redshift \red{and lower mass galaxies (}\smass\ $<10^{10}M_{\odot}$) will be very beneficial, probing closer to the epoch of formation of massive galaxies and \red{supermassive BH}s.
 The understanding of how and when the tight scaling relation emerged are crucial to test theoretical models \citep{Volonteri2021}.
@@
 \startdata
-SAM &  3.12e-09 & $<$1e-10  & $<$1e-10  & 7.46e-03  \\
-MBII & 4.23e-02 & \multicolumn{2}{c}{$<$1e-10 [$z=0.6$]}  & 2.22e-06  \\
-Illustris & 2.31e-01 & 6.14e-02  & 9.96e-03  & 2.33e-07  \\
-TNG100 & 1.21e-02 & 2.53e-01  & 3.76e-01  & 4.71e-01  \\
-TNG300 & 1.82e-02 & 9.19e-01  & 1.21e-01  & 2.12e-01  \\
-Horizon-AGN & 2.70e-01 & 2.87e-01  & 6.13e-01  & 1.95e-01  \\
+SAM &  1.99e-09 & $<$1e-10  & $<$1e-10  & 7.46e-03  \\
+MBII & 7.51e-01 & \multicolumn{2}{c}{$<$3.93e-01  [$z=0.6$]}  & 2.22e-05  \\
+Illustris & 5.01e-01 & 8.38e-01  & 5.98e-01  & 3.90e-05  \\
+TNG100 & 1.15e-02 & 4.06e-01  & 4.84e-01  & 4.71e-01  \\
+TNG300 & 2.36e-02 & 5.46e-01  & 3.10e-01  & 2.12e-01  \\
+Horizon-AGN & 2.01e-01 & 4.83e-01  & 1.40e-01  & 1.95e-01  \\
 \enddata
-\tablecomments{These p-values are obtained by the KS test between the simulation and the observation.}
+\tablecomments{These p-values are obtained by the KS test between the simulation and the observation \red{based on one realization}.}
 \end{deluxetable*}

### 2022-04-13 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
Pass the ball to John and Aklant

@@
 Finally, we investigate evolution as a function of stellar and \red{BH} mass, and argue that the most direct way to probe the co-evolution of galaxies and \red{BH}s is to increase the sensitivity, e.g., with JWST, thereby pushing to lower masses and minimizing possible biases arising from selection effects.
-\todo{Check if updated needed.}
 
@@
 \section{Introduction} \label{sec:intro}
-\todo{Re-read to avoid residual P1.}
 The close correlations between \red{the mass of} supermassive black holes (\red{\mbh}) and the properties of their host galaxies (e.g., stellar mass\red{, \smass}) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
 To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over \red{cosmic time}.
-While, an {\it observed} evolution has been found \red{since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15, Ding2020, 2021arXiv210902751L} in} which the growth of BHs predates that of the host, other studies \red{predict \citep[e.g.,][]{Schramm2013, Sun2015} that} BHs grow commensurately with galaxies.
+While, an {\it observed} evolution has been found \red{since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15, Ding2020, 2021arXiv210902751L} in} which the growth of BHs predates that of the host, other studies \red{\citep[e.g.,][]{Schramm2013, Sun2015} predict that} BHs grow commensurately with galaxies.
 However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15,Jahnke2009}.
@@
 Is it a fixed value or a distribution?} \todo{Aklant: Referee asks us whether the same radiative efficiency is used to compute AGN luminosity in all the simulations.
-But we already show these values in Table 1, which are different, don't we?}
+But we already show these values in Table 1, which are different, don't we?} \aklant{\bf{Yes the radiative efficiencies are different in the different simulations, and we use these different values for the computing the luminosities in each case.
+This is true at least for the simulations that I provided to you.}}
 }
@@
 \red{Note that each simulation adopt either a  \cite{2003PASP..115..763C} or a \cite{1955ApJ...121..161S} IMF.
-To make a self-consistent comparison, we ensure that the adopted IMF for the simulation and the observation are the consistent and to be the same.
-For numerical simulation, the mass is the base materials which are IMF independent.
-Actually, this assumption is still needed so that one can convert the observed luminosity to stellar mass to perform the comparison.}
+To make a self-consistent comparison, we ensure that the adopted IMF for both the simulation and the observation are the same.
+The assumed IMF is needed to obtain the mass-to-light ratio and convert the observed luminosity to stellar mass to perform the comparison.
+For numerical simulation, the mass is the base material which is IMF independent.}
 
@@
 and $2\times1792^3$ particles.
-\todo{Aklant: answer what is the factor 2 here.
+\todo{Aklant: Please answer what is the factor 2 here.
 A twin box with 1793$^3$ each?} The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}.
@@
 In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy.
-For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at irregular intervals between which the BH mass grows by a fixed fraction.
-\todo{Aklant: Referee asks are these irregular intervals included in the feedback modeling, or simply due to the time-varying accretion onto BHs?
-does it mean that the BH accretion is not modeled by the Bondi accretion between AGN feedback events?} The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency.
+For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at intervals between which the BH mass grows by a fixed fraction.
+\todo{Aklant: Referee asks: are these irregular intervals included in the feedback modeling, or simply due to the time-varying accretion onto BHs?
+does it mean that the BH accretion is not modeled by the Bondi accretion between AGN feedback events?} \aklant{\bf{They are irregular simply because the BH mass growth is non- uniform.
+So it takes different amounts of time for the BH to grow by a fixed fraction.
+Bondi accretion is happening at all times.
+I have now removed the word `irregular' from this statement.}} The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency.
 Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN.
@@
 Only galaxies with more than 50 particles are considered.
-\red{Identified with this approach, for Horizon-AGN, the adopted galaxy mass corresponds to the total stellar mass of a galaxy, which is different than the other hydrodynamic simulations (i.e., within a 3D 30~kpc spherical aperture.
-The Horizon-AGN's stellar mass by this definition is commonly used, whose stellar mass function is known} in \citet{2017MNRAS.467.4739K} to be in good agreement with observations.
+\red{Identified with this approach, for Horizon-AGN, the adopted galaxy mass corresponds to the total stellar mass of a galaxy, which is different than the other hydrodynamic simulations (i.e., within a 3D 30~kpc spherical aperture).
+This definition of stellar mass is commonly used in Horizon-AGN, whose stellar mass function is known~\citep{2017MNRAS.467.4739K}} to be in good agreement with observations.
 %\todo{Mention that the \smass.}
@@
 
-\subsection{Application of observational measurement error and selection effects}
+\subsection{Application of observational measurement error and selection effects}\label{subsec:add_obs_eff}
 To make direct comparisons with observations, we add measurement errors and apply the equivalent selection to the simulated samples.
@@
 We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = \red{0.2}~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.
-\red{Since the selection based on $L_{\rm bol}$ has limited effects in this study (see Section~\ref{sec:dis} and Figure~\ref{fig:offsets_nochange} for details), the AGN variability correction is not considered.}
+\red{Since the selection of the simulation sample based on $L_{\rm bol}$ has limited effects in this study (see the discussion in Section~\ref{sec:dis} and Figure~\ref{fig:offsets_nochange} for details), the AGN variability correction is not considered.}
 
@@
 This local relation is derived by fitting the \mbh-\smass\ relations using 55 local galaxies by~\citet{Bennert++2011} and \citet{H+R04}, in which \smass\ measurements are Chabrier IMF based.}
-\red{For each sample, we focus on the \mbh\ residuals\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the y-axis) and calculating their mean and the standard deviation to make comparisons with the observation.}
+\red{For each sample, we focus on the \mbh\ residuals\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the $y$-axis) and calculating their mean and the standard deviation to make comparisons with the observation.}
 
-\red{To make direct comparison, the simulation sample is processed in two steps: inject observational noise injection, and apply equivalent selection.
-In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
-For the simulation data, both the initial sample and the ones after selection and with noise corrections are show in the figure.
-There are three types of offset value that are considered from simulation: the initial offset, the offset with selection effect, and the offset with noise and selection effect.
-For the initial one, it has been known~\citep[e.g.,][Figure 2]{Habouzit2021} and can be seen in Figure~\ref{fig:comparsion} that the initial offset values vary at different stellar mass range, and thus the mean and standard derivation could not represent the entire distribution.
-The discussion of this initial offset is also beyond the scope of this work.}
-
-\red{We focus on the other two offset value distributions in this work.
+\red{In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
+For the simulation data, both the initial sample and the ones after observational effect (i.e., inject observational noise correction, and apply equivalent selection) are show in the figure.
+Note that there are three types of offset value that can be collected for the simulation sample: the initial offset, the offset with selection effect, and the offset with noise injection and selection effect.
+For the initial offset, it has been known~\citep[e.g.,][Figure 2]{Habouzit2021} and can be seen in Figure~\ref{fig:comparsion} that the initial offset values vary at different stellar mass range, and thus the mean and standard derivation could not represent the entire distribution.}
+\red{In this work, we focus on the other two offset value distributions, i.e., considering selection effect but with/without noise correction.
 To aid in visualization of the differences among the various simulations compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}.
@@
 The interpolations and the comparison with the observations are presented in the rest of this section.}
-\todo{s: Read again to avoid description conflict (intrinsic and then noise).}
-%For the initial level, it has been known that the offset depended by range of the stellar mass and thus it is less meaningful to make comparison in this work.
-
-%\todo{Discussion how random make difference on the scatter. P13}
-%\red{We performed the 1000 times realizations for the comparison of each sample to estimate the uncertainties of the values in Table~\ref{tab:sum} arises by the random scatter.
-We find that the uncertainty level of the }
-
-%In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
-The local scaling relation adopted by D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is used as the fiducial relation to assess relative offsets and differences in dispersion.
-A different simulation is presented in each row and the redshift intervals increase from left to right.
-
-%For each sample, the central offset and scatter of the scaling relation are estimated by calculating the mean and the standard deviation of the \mbh\ residuals for each system\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the y-axis in Figure~\ref{fig:comparsion}).
-To aid in visualization of the differences among the various simulations compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}.
-Each panel presents a different redshift range.
-In addition, the values for the central offset and scatter in each case are given in Table~\ref{tab:sum} and shown as a function of redshift in Figure~\ref{fig:offsets_vz}.
 
@@
 The background cloud (in green and yellow \red{with contours}) shows the intrinsic simulation number density before injecting random noise and applying selection effects.
-Only TNG100 is presented here since TNG300 presents very similar results \red{(see discussion section)}.
+\red{The TNG100 and TNG300 appear to present similar results (see discussion section)}.
 }
@@
 \red{We also see that, except MBII and Horizon-AGN, all the other simulations have the mass offset that are decreasing from $z=0.2$ to $z=0.6$, while the observations have offset value increase with redshift all the way up to $z\sim1.5$.
-However, this inconsistency is well below a $1-\sigma$ scatter level.}
+However, this inconsistency is well below the $1-\sigma$ scatter level.}
 Overall, we find that the mass \red{correlation} between \red{supermassive BH}s and their host galaxies are generally consistent between observations and simulations with some subtle differences which are not at the level of concern for this present study.
@@
 \caption{\label{fig:deltaMM} Comparison of the offset of the \mbh\ (to the \red{D20 local scaling} relation) as a function of stellar mass from observation data and the simulations at $z\sim0.7$.
-In each stellar mass bin \red{(minimum number of objects are larger than 6)}, we give the mean and standard derivation of the offset values.
-\red{To consider the random noise, we use ten times realizations's average to calculate the mean and standard derivation in each bin.} The histograms on the right indicate the offset distribution with lines marking the mean offsets for observation and simulation \red{using all the galaxy sample}.
-The green color distributions \red{with contours show the intrinsic simulated sample distribution} without random noise and selection applied.
+In each stellar mass bin \red{(minimum number of objects is larger than 6)}, we give the mean and standard derivation of the offset values.
+\red{To consider the random noise, we use the average of ten times realizations to calculate the mean and standard derivation in each bin.} The histograms on the right indicate the offset distribution with lines marking the mean offsets for observation and simulation \red{using all the galaxy sample}.
+The green color distributions \red{with contours show the intrinsic simulated sample distribution without random noise and selection effect.}
 }
@@
 The interpretation of how BH mass offset of the simulation increasing with redshift with respect to the D20 local scaling relation can be different than using the simulations' own local relation.
-Moreover, even though the effect is very limited, the galaxy mass of the Horizon-AGN sample is the total stellar mass; while all the other hydrodynamic simulations' are determined within the 3D 30 kpc spherical aperture.
-Thus, to compare the evolution even more fair, we manually shift all the simulation's relation to the same position as the observation one at $z=0.3$ in Figure~\ref{fig:offsets_vz_shiftz03} where the offset evolution trend can be seen more clear.
+Moreover, the stellar mass of the Horizon-AGN sample is the total mass; while all the other hydrodynamic simulations' stellar mass values are determined within the 3D 30 kpc spherical aperture.
+Thus, in Figure~\ref{fig:offsets_vz_shiftz03} we manually shift all the simulation's relation to as the same to the observation at $z=0.3$, where the offset evolution trend of each sample can be seen more clear.
 In general, the new result show that the evolution for the simulations are consistent with our interpretations in Section~\ref{subsec:offset}.
-This result can be expected since most of the simulation have demonstrated good offset match to the observation at redshift $z=0.3$.
-} %Furthermore, the MBII simulation result becomes very close with observation from across all redshift range, indicating that its prediction of \mbh\ mass offset evolution actually are very consistent with the observation.}
+This result can be expected since most of the simulation have demonstrated good offset match to the observation at redshift $z=0.3$.}
 
-%\todo{TNG100 and TNG300 -- explain the why no difference between TNGs.
-P8}~\red{We note that TNG100 and TNG300 yield very similar comparison results, thus only TNG100 is presented in~Figure~\ref{fig:comparsion}}.
-\red{In the literature~\citep{Weinberger2018, Habouzit2021}, it have been noted that the correlation predicted by TNG300 and TNG100 are not identical.
-For example, with larger volume, TNG300 process larger scatter of \mbh\ at fixed \smass\ than TNG100 (at \smass  $>10^{10}M_{\odot}$).
-Also, since in TNG100 the BH growth is more efficient, the BH mass function in TNG100 is found to be at higher normalization at low BH mass end.
-In our result, the difference between TNG100 and TNG300 also exist.
-However, since the compared samples have been processed with selection effect and/or random noise injection, such a difference became very slight.}
-\todo{The referee says TNG300 has larger scatter, but in Habouzit2021 section 4.2.2, it actually says scatter in TNG300 is smaller. Any one know if the referee is wrong?}
+\red{We collected all the available sample in the simulation to perform the comparison, and final number of points that used to compare with observation are not by our design.
+Despite that the observational samples are volume-unlimited and the simulated sample are thus not volume-matched, fortunately, the volume of all the simulation appears to be sufficient $-$ all of the simulation can produce similar amount (or more) data points to compare with the observation (see Figure~\ref{fig:comparsion}).
+Also, the similar results are inferred using smaller and larger volume simulation, i.e., TNG100 and TNG300, which reflect the fact that the simulation's volume has reached to a sufficient level to be for this comparison work.}
 
-\red{We collected all the available simulation sample to perform the comparison, and thus the number of points that used from the simulation are not designed by us.
-Despite that the observational samples are volume-unlimited and the simulated sample are thus not volume-matched, fortunately, the volume of all the simulation appears to be sufficient $-$ all of them can present similar (or more) amount of data points to compare with the observation (see Figure~\ref{fig:comparsion}).
-Also, the similar results are inferred using smaller and larger volume simulation, i.e., TNG100 and TNG300, which reflect the fact that the simulation's volume has reached to a sufficient level to be compared with observation.}
-
-\red{To make a fair comparison, we performed the same sample selection so that the $L_{\rm bol}$ and \mbh\ distribution are also similar.
-Furthermore, we also assured that the \smass\ are compared at the similar range.
-In fact, we find that our comparison result are very robust; we tested to change our selection that generate a very different $L_{\rm bol}$ distribution, the offset distribution of all the simulations are almost identical (see demonstrations in Figure~\ref{fig:offsets_nochange}).
-This test implies that even consider the situation of AGN variability ($10-20\%$ level flux variation) and obscuration (i.e., removing a certain fraction of the sample) at extreme level, our result are still valid .
+\red{To avoid any possible bias raised by sample mismatch, we designed our selection in Section~\ref{subsec:add_obs_eff} so that the distribution of $L_{\rm bol}$ and \mbh\ are similar.
+We also assured that the \smass\ is compared at a similar range.
+Furthermore, we tested to change our selection so that a different $L_{\rm bol}$ distribution is finally adopted in the simulation.
+The result shows that the offset distribution of all the simulations are almost identical (see demonstrations in Figure~\ref{fig:offsets_nochange}).
+This test implies that our comparison results are very robust; even considering the situation of AGN variability ($10-20\%$ level flux variation) and obscuration (i.e., removing a certain fraction of the sample), our result should keep the same.
 }
@@
 \caption{\label{fig:offsets_nochange} 
-\red{Different bolometric luminosity selection of the comparison sample and the changes of the comparison result.
-{\it left:}~The $L_{\rm bol}$ distribution of samples at redshift $z=0.5$ that according to the selection choose made in this work.
-The simulation sample presents good match with the observation.
-{\it middle:} Using different magnitude threshold to select the sample.
-As result, the distribution of the simulation are much different with the observation.
-{\it right:} The difference of the offset by these two selection (dashed line is the new selection result).
-As shown, the changes by different selection based on $L_{\rm bol}$ values have very limited effects on our result.}
+\red{Adopting different bolometric luminosity selection for the simulation sample and the changes in the comparison result.
+{\it left:}~The $L_{\rm bol}$ distribution of samples at redshift $z=0.5$ in this work.
+The simulation sample presents a good match with the observation.
+{\it middle:} Using a different magnitude thresholds to select the simulation sample to force the distribution of the simulation to be different from the observation.
+{\it right:} The offset distribution by these two selections (dashed line is the result by mismatched selection).
+As shown, the different selections have very small effects to change of the offset distribution.}
 }
@@
 \caption{\label{fig:offsets_vz_shiftz03} 
-\red{Same as Figure~\ref{fig:offsets_vz} but shift all the simulation's result to the observation at $z=0.3$.
-After this recalibrating, the MBII's result appears to match very well with the observation.}
+\red{Same as Figure~\ref{fig:offsets_vz} but shift all the simulation's result to the observation at $z=0.3$.}
 }
 \end{figure}
+
+%\todo{TNG100 and TNG300 -- explain the why no difference between TNGs.
+P8}~\red{We note that TNG100 and TNG300 yield very similar comparison results, thus only TNG100 is presented in~Figure~\ref{fig:comparsion}}.
+\red{In the literature~\citep{Weinberger2018, Habouzit2021}, it have been noted that the correlation predicted by TNG300 and TNG100 are not identical.
+For example, with larger volume, TNG300 process larger scatter of \mbh\ at fixed \smass\ than TNG100 (at \smass  $>10^{10}M_{\odot}$).
+Also, since in TNG100 the BH growth is more efficient, the BH mass function in TNG100 is found to be at higher normalization at low BH mass end.
+In our result, the difference between TNG100 and TNG300 also exist.
+However, since the compared samples have been processed with selection effect and/or random noise injection, such a difference became very slight.}
+\todo{The referee says TNG300 has larger scatter, but in Habouzit2021 section 4.2.2, it actually says scatter in TNG300 is smaller. Any one know if the referee is wrong?}
 
@@
 Considering that the observation and simulation sample has went through the same observational process, this result is {\it consistent} with the fact that the intrinsic of the simulation (i.e., the first-hand product) and the observation are similar.
-Of course, there are limitations in our comparisons and this {\it consistency} doesn't necessarily mean their intrinsic must be the same.
+Of course, there are limitations in our comparisons and this {\it consistency} doesn't necessarily mean their intrinsic must only be the same.
 On the one hand, there is always unknown-unknown in the observational effects that haven't applied to the simulation yet.
 On the other hand, even the state-of-the-art simulations could not capture all the physical aspects that impact the scatter.
-For example, the spin of BHs is not modeled in the simulation the which could change the scatter since the spin affects to both the accretion the energy that can be released by AGN feedback \citep{Dubois2014, 2019MNRAS.490.4133B, Habouzit2021} at some level.
-Even though the spin effect is still not well known and the study of the spin effect in detail is beyond the scope of this paper, the comparison work are needed be done once these simulations considered spin in the future.
- \todo{Xuheng checked the cited reference but could not find quantitively how much this spin will change the simulation scatter.}
+For example, the spin of BHs is not modeled in the simulation which could change the scatter since the spin affects to both the accretion the energy that can be released by AGN feedback \citep{Dubois2014, 2019MNRAS.490.4133B, Habouzit2021} at some level.
+Even though the spin effect is still not well known and the study of the spin effect is beyond the scope of this paper, the comparison work is worth to be done in the future once the simulations consider spin.
+ \todo{Xuheng checked the cited reference but could not find quantitatively how much this spin will change the simulation scatter.}
 }
@@
 From $z\sim0.7$ to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
-\red{Despite that the offset difference between $z=0.2$ and $z=0.6$ is well below the observed scatter, 4/6 of the simulations have decreasing mass offset from $z=0.2$ and $z=0.6$ while the observation mass offset are increasing with redshift all the way.}
+\red{4/6 of the simulations have decreasing mass offset from $z=0.2$ and $z=0.6$ while the observation mass offset increases with redshift all the way, despite that the offset difference between $z=0.2$ and $z=0.6$ is well below the observed scatter.}
 %\todo{To add that 4/6 of the simulations have decreasing mass offsets from z=0.2 and 0.6 while the offsets from the observations increase with redshift all the way (Fig. 5). P15}

### 2022-04-25 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
Merger with Aklant and John's edit

@@
 To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over \red{cosmic time}.
-While, an {\it observed} evolution has been found \red{since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15, Ding2020, 2021arXiv210902751L} in} which the growth of BHs predates that of the host, other studies \red{\citep[e.g.,][]{Schramm2013, Sun2015} predict that} BHs grow commensurately with galaxies.
-However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15,Jahnke2009}.
+While, an {\it observed} evolution has been found \red{since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15} in} which the growth of BHs predates that of the host, other studies \red{\citep[e.g.,][]{Schramm2013, Sun2015} predict that} BHs grow commensurately with galaxies.
+However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15,Jahnke2009,  Ding2020,Li2021b}.
 
@@
 
-To avoid any potential biases related to the selection of the quasars, \citet{2021arXiv210902751L} isolated 877 sources which are uniformly selected based on their PSF-magnitudes, color cuts using single-epoch SDSS photometry and the value of the measured \smass.
+To avoid any potential biases related to the selection of the quasars, \citet{Li2021b} isolated 877 sources which are uniformly selected based on their PSF-magnitudes, color cuts using single-epoch SDSS photometry and the value of the measured \smass.
 Specifically, we use the {\it ugri} color-selected sample (228 sources) from SDSS I/II~\citep{Richards2002}, and the CORE sample from SDSS BOSS (408 sources) and eBOSS (241 sources) surveys~\citep{Ross2013, Myers2015} (hereafter the uniform sample).
@@
 Thus, we expect the measurement errors of these two samples to be at a comparable level (i.e., $\Delta$\mbh$=0.4~$dex, $\Delta$\smass$=0.2~$dex).
-Indeed, the two samples are consistent with a lack of evolution in the mass ratio~\citep[see Figure 6 of][]{2021arXiv210902751L}, even though the sample selection is slightly different.
+Indeed, the two samples are consistent with a lack of evolution in the mass ratio~\citep[see Figure 6 of][]{Li2021b}, even though the sample selection is slightly different.
 
@@
 $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$.
-\todo{Aklant: The $\leq$ sign in the low accretion feedback mode of TNG is also not clear.
-Is it a fixed value or a distribution?} \todo{Aklant: Referee asks us whether the same radiative efficiency is used to compute AGN luminosity in all the simulations.
+\red{The `$\leq$' sign in the low accretion feedback mode of TNG means that the feedback efficiency follows a distribution with a maximum value of 0.2.
+Note that the radiative efficiencies are different in various simulations.
+Thus, different values are used for calculating the luminosity.}
+%\todo{Aklant: The $\leq$ sign in the low accretion feedback mode of TNG is also not clear.
+Is it a fixed value or a distribution?}\aklant{[\bf{It just means that the efficiency is actually function (not a constant) but the maximum value is 0.2}]}
+%\todo{Aklant: Referee asks us whether the same radiative efficiency is used to compute AGN luminosity in all the simulations.
 But we already show these values in Table 1, which are different, don't we?} \aklant{\bf{Yes the radiative efficiencies are different in the different simulations, and we use these different values for the computing the luminosities in each case.
@@
 \section{Simulations and comparison strategy}
-\todo{Uniform the descriptions of the simulations to lack homogeneity. (Illustris has star formation threshold). Re-write the section and provide the same information}
+%\todo{Uniform the descriptions of the simulations to lack homogeneity. (Illustris has star formation threshold). Re-write the section and provide the same information}
 \label{sec:simulations}
-We introduce the simulation samples that are adopted in this section.
-All the simulation are based on the larger-scale cosmological simulations, except the Semianalytic Model (SAM) simulation (see Section~\ref{subsec:SAM}).
+We introduce the simulation samples that are adopted in this study.
+All are based on larger-scale cosmological simulations, except the Semianalytic Model (SAM; see Section~\ref{subsec:SAM}).
 In Table~\ref{tab:sim_sum}, we summarized the key elements for each hydrodynamic simulation being considered.
-
-\red{Note that each simulation adopt either a  \cite{2003PASP..115..763C} or a \cite{1955ApJ...121..161S} IMF.
-To make a self-consistent comparison, we ensure that the adopted IMF for both the simulation and the observation are the same.
-The assumed IMF is needed to obtain the mass-to-light ratio and convert the observed luminosity to stellar mass to perform the comparison.
+\red{We note that each simulation adopts either a  \cite{2003PASP..115..763C} or a \cite{1955ApJ...121..161S} IMF.
+To make self-consistent comparisons, we ensure that the adopted IMF for both the simulations and the observations are consistent.
+The assumed IMF is needed to obtain the mass-to-light ratio and convert the observed luminosity to stellar mass to perform the comparisons.
 For numerical simulation, the mass is the base material which is IMF independent.}
@@
 MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $(142.7~\mathrm{cMpc})^3$
-and $2\times1792^3$ particles.
-\todo{Aklant: Please answer what is the factor 2 here.
-A twin box with 1793$^3$ each?} The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}.
+and $2\times1792^3$~\red{(i.e., dark matter + gas)} particles. 
+%\todo{Aklant: Please answer what is the factor 2 here. A twin box with 1793$^3$ each?\aklant{\bf{The 2 represents that there are $1792^3$ DM particles and $1792^3$ gas particles}}} 
+The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}.
 The base cosmology parameters are based on the WMAP7 results~\citep{2011ApJS..192...18K}.
@@
 The simulation includes a full modeling of gravity plus gas hydrodynamics, with a wide range of subgrid recipes to model the star formation~\citep{2003MNRAS.339..289S}, BH growth, and the feedback process~\citep{2005Natur.433..604D}.
-Halos were identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}.
-Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}.
 
@@
 
+Halos were identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}.
+Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}.
 As a common practice, the stellar mass is obtained by using a 3D spherical aperture of 30~kpc to represent the observed stellar mass.
@@
 In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy.
-For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at intervals between which the BH mass grows by a fixed fraction.
-\todo{Aklant: Referee asks: are these irregular intervals included in the feedback modeling, or simply due to the time-varying accretion onto BHs?
+For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at \red{the} intervals between which the BH mass grows by a fixed fraction.
+(%\todo{Aklant: Referee asks: are these irregular intervals included in the feedback modeling, or simply due to the time-varying accretion onto BHs?
 does it mean that the BH accretion is not modeled by the Bondi accretion between AGN feedback events?} \aklant{\bf{They are irregular simply because the BH mass growth is non- uniform.
@@
 Bondi accretion is happening at all times.
-I have now removed the word `irregular' from this statement.}} The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency.
+I have now removed the word `irregular' from this statement.}}
+The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency.
 Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN.
+\aklant{Halos and galaxies are identified similar to that of MBII}.
 As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy \red{stellar mass}.
@@
 Instead of releasing hot bubbles, this feedback mode in TNG is purely kinetic.
-In particular, there is a directional injection of momentum along a randomly chosen direction~\citep{2017MNRAS.465.3291W, 2018MNRAS.479.4056W} at irregular intervals.
+In particular, there is a directional injection of momentum along a randomly \red{chosen direction~\citep{2017MNRAS.465.3291W, 2018MNRAS.479.4056W}}.
+% at irregular intervals.
 The transition between the two feedback modes is also different from Illustris, and is set by the minimum value of 0.1 and $2 \times 10 ^{-3} \times (M_{BH} / 10^8~M_{\odot})$.
 Additionally, the radiative feedback implemented in Illustris~(summarized in the previous section) is also present in TNG.
-Lastly, the galaxy stellar mass in Illustris-TNG is obtained in a similar manner to that of Illustris.
+Lastly, \aklant{halo and galaxy identification, as well as calculation of galaxy stellar mass, is done in a similar manner to that of Illustris and MBII}.
 
@@
 
-The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation with a constant star formation efficiency $\epsilon_*=0.02$, which occurs in regions where the gas number density exceeds the star formation threshold $n_0 = 0.1\,\rm H\, cm^{-3}$.
+%The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation with a constant star formation efficiency $\epsilon_*=0.02$, which occurs in regions where the gas number density exceeds the star formation threshold $n_0 = 0.1\,\rm H\, cm^{-3}$.
 %A Salpeter IMF is assumed.
-\red{Stellar feedback} is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources.
+%\red{Stellar feedback} is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources.
 
@@
 Only galaxies with more than 50 particles are considered.
-\red{Identified with this approach, for Horizon-AGN, the adopted galaxy mass corresponds to the total stellar mass of a galaxy, which is different than the other hydrodynamic simulations (i.e., within a 3D 30~kpc spherical aperture).
+\red{With this approach for Horizon-AGN, the adopted galaxy mass corresponds to the total stellar mass of a galaxy, which is different than the other hydrodynamic simulations (i.e., within a 3D 30~kpc spherical aperture).
 This definition of stellar mass is commonly used in Horizon-AGN, whose stellar mass function is known~\citep{2017MNRAS.467.4739K}} to be in good agreement with observations.
@@
 \caption{\label{fig:selection}Demonstration of AGN selection using MBII.
-{\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles) \red{for sample at redshift $z=0.6$}.
+{\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles) \red{for those at redshift $z=0.6$}.
 A matched HSC sample is shown by the orange data points.
 The light green background cloud shows the {\it intrinsic} simulated number density in this parameter space.
-\red{Note that this is the first  step of the sample selection.
-We future use AGN magnitude cut to assure that the simulation sample present similar $L_{\rm bol}$ distribution (e.g., see Figure~\ref{fig:offsets_nochange}-left) and \mbh\ distribution with the observation.
-We then use the same \smass\ cut to collect the final sample.}
+\red{Note that this is the first step of sample selection.
+We further use an AGN magnitude cut to assure that the simulation sample has a similar $L_{\rm bol}$ distribution (e.g., see Figure~\ref{fig:offsets_nochange}-left) and \mbh\ distribution with the observations.
+We then use the same \smass\ cut to construct the final sample.}
 {\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample.
@@
 
-\red{Comparing with} HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should match the relationship between \mbh-$L_{\rm bol}$ as seen in the HSC sample.
+\red{Comparing with} the HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should match the relationship between \mbh-$L_{\rm bol}$ as seen in the HSC sample.
 We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it \red{left}}).
@@
 %The specific selection is made as follows: for systems at $z<0.5$ and $z>0.5$, the AGN $i$-band magnitude is required to be brighter than 20.5 mag and 22.0 mag, respectively.
-\red{The specific selection is made as follows: a value of AGN $i$-band magnitude is selected to make the sample selection so that the $L_{\rm bol}$ distribution is similar to the observation (see Section~\ref{sec:dis} for details).
+\red{The specific selection is carried out as follows: a value of AGN $i$-band magnitude is chosen to make the sample selection such that the $L_{\rm bol}$ distribution is similar to the observations (see Section~\ref{sec:dis} for details).
 }
@@
 
-\red{Comparing with} HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example).
+\red{Comparing with} the HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example).
 Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., \red{log(\mbh)} between [7.7, 8.6] $M_{\odot}$).
@@
 %\todo{Explain the offset depends.}
-\red{For comparison purpose, the local scaling relation introduced by D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF based\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion.
-This local relation is derived by fitting the \mbh-\smass\ relations using 55 local galaxies by~\citet{Bennert++2011} and \citet{H+R04}, in which \smass\ measurements are Chabrier IMF based.}
-\red{For each sample, we focus on the \mbh\ residuals\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the $y$-axis) and calculating their mean and the standard deviation to make comparisons with the observation.}
+\red{For comparison, the local scaling relation provided by  D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion \blue{with redshift}.
+This local relation \blue{(\mbh-\smass\))} is derived by \blue{fitting measurements for} 55 local galaxies as given in~\citet{Bennert++2011} and \citet{H+R04}.
+%, in which \smass\ measurements are Chabrier IMF based.
+}
+\red{For each sample, we focus on the \mbh\ residuals\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the $y$-axis) and calculate their mean and standard deviation to make comparisons with observations.}
 
 \red{In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
-For the simulation data, both the initial sample and the ones after observational effect (i.e., inject observational noise correction, and apply equivalent selection) are show in the figure.
-Note that there are three types of offset value that can be collected for the simulation sample: the initial offset, the offset with selection effect, and the offset with noise injection and selection effect.
-For the initial offset, it has been known~\citep[e.g.,][Figure 2]{Habouzit2021} and can be seen in Figure~\ref{fig:comparsion} that the initial offset values vary at different stellar mass range, and thus the mean and standard derivation could not represent the entire distribution.}
-\red{In this work, we focus on the other two offset value distributions, i.e., considering selection effect but with/without noise correction.
-To aid in visualization of the differences among the various simulations compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}.
+For the simulated data, both the initial sample and that with observational effects applied (i.e., noise correction, and selection) are shown.
+Note that \blue{offsets can occur for the simulated sample in three cases}: an \blue{inherent} offset, an offset due to selection, and offsets from added noise and selection.
+For the first, it has been recognized~\citep[e.g.,][Figure 2]{Habouzit2021}, and seen in Figure~\ref{fig:comparsion}, that the  offset values \blue{vary over a range of} stellar mass, and thus the mean and standard derivation do not represent the entire mass distribution.}
+\red{In this work, we focus on the latter two offset distributions, i.e., considering selection effects with and without noise correction.
+To aid in visualization of the differences among the various simulations, compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}.
 Each panel presents a different redshift range.
-In addition, the values of the central offset and scatter for before and after considering the noise are presented in Table~\ref{tab:sum}.
-The interpolations and the comparison with the observations are presented in the rest of this section.}
+In addition, the values of the central offset and scatter are presented
+in Table~\ref{tab:sum}, both before and after consideration of the noise. \blue{Comparisons with the} observations are presented in the remainder of this section.}
 
@@
 \centering
-\includegraphics[trim = 40mm 70mm 30mm 90mm, clip,height=1.1\textwidth]{MM_sum.png}
+\includegraphics[trim = 40mm 60mm 30mm 90mm, clip,height=1.1\textwidth]{MM_sum.png}
 \caption{\label{fig:comparsion} 
@@
 We find that the intrinsic scatter is at a level of $\sim0.15-0.2$ dex for both $z<1$ and $z>1$ (see Table~\ref{tab:sum}).
-These levels are consistent with the {\it intrinsic} scatter as estimated using observation data alone~\citep{Ding2020, 2021arXiv210902751L}.
+These levels are consistent with the {\it intrinsic} scatter as estimated using observation data alone~\citep{Ding2020, Li2021b}.
 Furthermore, the intrinsic scatter appears to be independent of redshift since the observations and simulations all follow the observed trend with redshift expected to be due to selection effects (Figure~\ref{fig:offsets_vz}).
@@
 \caption{\label{fig:offsets} 
-\red{Color filled histograms show the offset distributions} for all simulation samples and observations.
-The mean value and the standard derivation of the histogram are summarized in Table~\ref{tab:sum}.
-The vertical dashed lines show the corresponding mean value for each distribution.
-The mean values for observed sample (i.e., yellow lines) are also show in each simulation plots.
-\red{To address the noise effect, the offset distributions of the simulation without adding noise are also shown using black line.}
+\red{Colored histograms show the offset distributions} for all simulated samples.
+The mean value and standard deviation of each are summarized in Table~\ref{tab:sum}.
+The vertical dashed lines indicate the corresponding mean value for each distribution.
+The mean values for the observed sample (i.e., yellow lines) are also given in each panel.
+\red{To address the effect of noise, the offset distributions of the simulation without adding noise are also shown by the open black histograms.}
 For the MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$. 
@@
 \caption{\label{fig:offsets_vz} 
-The {\it observed} evolution of $\Delta{\rm log}$\mbh\ as a function of redshift using both observation and simulation data.
+The {\it observed} evolution of $\Delta{\rm log}$\mbh\ as a function of redshift using both observational and simulated data.
 The black line shows the evolution by fitting the offset as a function of redshift.
-\red{The black dots (error bars) are the mean (standard deviation) value of the observations at the four redshift bins.
-The \smass\ and \mbh\ ranges are different at each redshift bins, which are indicated in Figure~\ref{fig:comparsion}.} The predictions from the numerical simulations, given in Table~\ref{tab:sum}, are presented by different colored symbols.
-The grey horizontal band illustrates the level of dispersion for \red{D20's} local sample.
+\red{The black dots (with error bars) represent the mean (and standard deviation) values for the observations in four redshift bins.
+The \smass\ and \mbh\ ranges are different for each redshift bin, which are indicated in Figure~\ref{fig:comparsion}.} The predictions from the numerical simulations, given in Table~\ref{tab:sum}, are presented by different colored symbols.
+The grey horizontal band illustrates the level of dispersion for the local sample (\red{D20}).
 }
@@
 These results are consistent with the Kolmogorov-Smirnov (KS) test performed using the offset distributions between each simulated sample and the observed sample --- the p-values are given in Table~\ref{tab:pvalue} showing that Horizon-AGN and Illustris have a good statistical match to the scaling relation at $z<0.6$ (i.e., p-value $> 0.1$), while the TNG100, TNG300 and Horizon-AGN simulation do well at $z>0.6$.
-\red{We also see that, except MBII and Horizon-AGN, all the other simulations have the mass offset that are decreasing from $z=0.2$ to $z=0.6$, while the observations have offset value increase with redshift all the way up to $z\sim1.5$.
-However, this inconsistency is well below the $1-\sigma$ scatter level.}
+\red{Except for MBII and Horizon-AGN, we also see that the other simulations have mass offsets that are decreasing from $z=0.2$ to $z=0.6$, while the observations offsets increasing with redshift up to $z\sim1.5$.
+However, this inconsistency is well below the $1\sigma$ scatter level.}
 Overall, we find that the mass \red{correlation} between \red{supermassive BH}s and their host galaxies are generally consistent between observations and simulations with some subtle differences which are not at the level of concern for this present study.
@@
 These differences between simulations present two different scenarios, either one where the \red{BH}s come later or co-evolution with the two growing in tandem.
-Considering the former scenario, Illustris show the strongest trend with stellar mass.
+Considering the former scenario, Illustris shows the strongest trend with stellar mass.
 In fact, after noise and selection is applied, the simulated sample exhibits very small offsets which agree remarkably well with the observed data.
-\red{Upon this, one interpretation is that depending on the BH population in the Universe, the observations of AGN such as our HSC sample, do not inform us of the true \mbh\ offsets as a function of \smass.}  This result underscores the importance of taking into account errors and selection --- without accounting for those, one could erroneously interpret an apparent trend as evolution in the opposite sense as the true one.
+\blue{If the BHs are accurately characterized in the simulation, one interpretation is that the observations, including our HSC AGN sample, do not inform us of the true \mbh\ offsets as a function of \smass.}  This result underscores the importance of taking into account errors and selection --- without accounting for those, one could erroneously interpret an apparent trend as evolution in the opposite sense as the true one.
 The most direct way to circumvent these issues is to probe lower masses (\smass\  $<10^{10}M_{\odot}$) using a more sensitive instrument, such as JWST~\citep{Habouzit2022} across this redshift range \citep[see also][]{2011MNRAS.417.2085V}.
@@
 \end{tabular}
-\caption{\label{fig:deltaMM} Comparison of the offset of the \mbh\ (to the \red{D20 local scaling} relation) as a function of stellar mass from observation data and the simulations at $z\sim0.7$.
-In each stellar mass bin \red{(minimum number of objects is larger than 6)}, we give the mean and standard derivation of the offset values.
-\red{To consider the random noise, we use the average of ten times realizations to calculate the mean and standard derivation in each bin.} The histograms on the right indicate the offset distribution with lines marking the mean offsets for observation and simulation \red{using all the galaxy sample}.
+\caption{\label{fig:deltaMM} Comparisons of the offset of \mbh\ (to the \red{D20 local scaling} relation) as a function of stellar mass from observational data and the simulations at $z\sim0.7$.
+In each stellar mass bin \red{(minimum number of objects is larger than 6)}, we give the mean and standard deviation of the offset values.
+\red{To consider random noise, we use the average of ten realizations to calculate the mean and standard deviation in each bin.} The histograms on the right show the offset distribution with lines marking the mean offsets for the observations and simulations \red{using the full galaxy sample}.
 The green color distributions \red{with contours show the intrinsic simulated sample distribution without random noise and selection effect.}
@@
 %\todo{Discussion when shift offset as z=0.3. P11}
-\red{In our comparison work, the mass offsets are compared to the relation derived in the local Universe.
+\red{In this study, there are a few issues that may bias the results thus need to be considered.
+First, the mass offsets are compared to the observe relation derived in the local Universe (D20).
 In fact, the different simulations could have different mean relations at $z=0$~\citep[e.g.,][]{Habouzit2021}.
-The interpretation of how BH mass offset of the simulation increasing with redshift with respect to the D20 local scaling relation can be different than using the simulations' own local relation.
-Moreover, the stellar mass of the Horizon-AGN sample is the total mass; while all the other hydrodynamic simulations' stellar mass values are determined within the 3D 30 kpc spherical aperture.
-Thus, in Figure~\ref{fig:offsets_vz_shiftz03} we manually shift all the simulation's relation to as the same to the observation at $z=0.3$, where the offset evolution trend of each sample can be seen more clear.
-In general, the new result show that the evolution for the simulations are consistent with our interpretations in Section~\ref{subsec:offset}.
-This result can be expected since most of the simulation have demonstrated good offset match to the observation at redshift $z=0.3$.}
+As a result, the interpretation of the BH mass offsets of the simulations with redshift, anchored to the D20 local scaling relation, can be different if using the local relation of each individual simulation.
+In addition, the stellar mass of the Horizon-AGN sample is the total mass while that for the other hydrodynamic simulations are determined within a 3D 30 kpc spherical aperture.
+Therefore, in Figure~\ref{fig:offsets_vz_shiftz03}, we manually shift all simulations to match the observations at $z=0.3$.
+This enables the evolutionary trend in the offsets of each sample to be clearer.
+In general, the updated results show that the evolution of the simulations are consistent with our interpretations in Section~\ref{subsec:offset}.
+This result can be expected since most of the simulations have demonstrated a good match to the observations at redshift $z=0.3$.}
 
-\red{We collected all the available sample in the simulation to perform the comparison, and final number of points that used to compare with observation are not by our design.
-Despite that the observational samples are volume-unlimited and the simulated sample are thus not volume-matched, fortunately, the volume of all the simulation appears to be sufficient $-$ all of the simulation can produce similar amount (or more) data points to compare with the observation (see Figure~\ref{fig:comparsion}).
-Also, the similar results are inferred using smaller and larger volume simulation, i.e., TNG100 and TNG300, which reflect the fact that the simulation's volume has reached to a sufficient level to be for this comparison work.}
+\blue{Regarding the survey volumes, we collected all available samples in the simulations to perform these comparisons.
+The final sample sizes, used to compare with observation, are not set by design.
+Despite that the observed samples are not volume-limited and the simulated samples are not volume-matched, fortunately, the volume of all the simulations appear to be sufficient, i.e., all simulations have a similar amount (or more) of data points to compare with the observations (see Figure~\ref{fig:comparsion}).
+Also, similar results are found with the smaller and larger volumes simulations, e.g., TNG100 and TNG300, which reflect the fact that the simulation volume reaches a sufficient size to be effective for these comparisons.}
 
-\red{To avoid any possible bias raised by sample mismatch, we designed our selection in Section~\ref{subsec:add_obs_eff} so that the distribution of $L_{\rm bol}$ and \mbh\ are similar.
-We also assured that the \smass\ is compared at a similar range.
-Furthermore, we tested to change our selection so that a different $L_{\rm bol}$ distribution is finally adopted in the simulation.
-The result shows that the offset distribution of all the simulations are almost identical (see demonstrations in Figure~\ref{fig:offsets_nochange}).
-This test implies that our comparison results are very robust; even considering the situation of AGN variability ($10-20\%$ level flux variation) and obscuration (i.e., removing a certain fraction of the sample), our result should keep the same.
+\red{To avoid any possible bias raised by sample mismatch, we designed our selection (Section~\ref{subsec:add_obs_eff}) so that the distribution of $L_{\rm bol}$ and \mbh\ are similar.
+We also assure that the \smass\ \blue{spans similar ranges}.
+As a test, we loosened the selection by not requiring equivalent $L_{\rm bol}$ distributions.
+The result shows that the offset distributions for all simulations are similar (see demonstrations in Figure~\ref{fig:offsets_nochange}) to those requiring matched $L_{\rm bol}$ distributions.
+This test implies that our comparison results \blue{are stable}, even considering the possibility for AGN variability ($10-20\%$ level flux variation) and the lack of the obscured population being represented in our observed samples.
 }
@@
 \caption{\label{fig:offsets_nochange} 
-\red{Adopting different bolometric luminosity selection for the simulation sample and the changes in the comparison result.
-{\it left:}~The $L_{\rm bol}$ distribution of samples at redshift $z=0.5$ in this work.
-The simulation sample presents a good match with the observation.
-{\it middle:} Using a different magnitude thresholds to select the simulation sample to force the distribution of the simulation to be different from the observation.
-{\it right:} The offset distribution by these two selections (dashed line is the result by mismatched selection).
-As shown, the different selections have very small effects to change of the offset distribution.}
+\red{Mass comparisons using different bolometric luminosity selection.
+{\it left:}~$L_{\rm bol}$ distribution of our simulated samples at $z=0.5$ tailored to match with the observations.
+{\it middle:} Using a different magnitude thresholds to select the simulated samples to force the distribution of the simulation to be different from the observation.
+{\it right:} Offset distributions using these two selections with the dashed line being the result for a mismatched luminosity distribution).
+As shown, the different selections have minimal effect on the offset distributions.}
 }
@@
 \caption{\label{fig:offsets_vz_shiftz03} 
-\red{Same as Figure~\ref{fig:offsets_vz} but shift all the simulation's result to the observation at $z=0.3$.}
+\red{Same as Figure~\ref{fig:offsets_vz} but now including a shift of all simulations to match the observations at $z=0.3$.}
 }
@@
 P8}~\red{We note that TNG100 and TNG300 yield very similar comparison results, thus only TNG100 is presented in~Figure~\ref{fig:comparsion}}.
-\red{In the literature~\citep{Weinberger2018, Habouzit2021}, it have been noted that the correlation predicted by TNG300 and TNG100 are not identical.
-For example, with larger volume, TNG300 process larger scatter of \mbh\ at fixed \smass\ than TNG100 (at \smass  $>10^{10}M_{\odot}$).
-Also, since in TNG100 the BH growth is more efficient, the BH mass function in TNG100 is found to be at higher normalization at low BH mass end.
-In our result, the difference between TNG100 and TNG300 also exist.
-However, since the compared samples have been processed with selection effect and/or random noise injection, such a difference became very slight.}
-\todo{The referee says TNG300 has larger scatter, but in Habouzit2021 section 4.2.2, it actually says scatter in TNG300 is smaller. Any one know if the referee is wrong?}
+\red{In the literature~\citep{Weinberger2018, Habouzit2021}, it has been noted that the mass correlations predicted by TNG300 and TNG100 are not identical.
+For example, TNG300 has larger scatter in \mbh\ at fixed \smass\ than TNG100 at \smass $>10^{10}M_{\odot}$.
+Also, BH growth is more efficient in TNG100 thus causing the BH mass function to have higher normalization at the low mass end.
+In our work, the differences between TNG100 and TNG300 also exist.
+However, the difference are milder after selection effects and random noise injection have been applied to the samples.} \todo{The referee says TNG300 has larger scatter, but in Habouzit2021 section 4.2.2, it actually says scatter in TNG300 is smaller.
+Any one know if the referee is wrong?}
 
 %\todo{Some discussion on BH spin. What does consistent means? P9, P12 and P18.}
-\red{We considered all the known observational effects, including the sample selection and random noise injection, and applied to the first-hand products of the simulation in order to directly compare with observations.
-Our result shows that the scatter between observation and simulation are very similar.
-Considering that the observation and simulation sample has went through the same observational process, this result is {\it consistent} with the fact that the intrinsic of the simulation (i.e., the first-hand product) and the observation are similar.
-Of course, there are limitations in our comparisons and this {\it consistency} doesn't necessarily mean their intrinsic must only be the same.
-On the one hand, there is always unknown-unknown in the observational effects that haven't applied to the simulation yet.
-On the other hand, even the state-of-the-art simulations could not capture all the physical aspects that impact the scatter.
-For example, the spin of BHs is not modeled in the simulation which could change the scatter since the spin affects to both the accretion the energy that can be released by AGN feedback \citep{Dubois2014, 2019MNRAS.490.4133B, Habouzit2021} at some level.
-Even though the spin effect is still not well known and the study of the spin effect is beyond the scope of this paper, the comparison work is worth to be done in the future once the simulations consider spin.
+\red{We considered all known observational effects, including sample selection and random noise injection, and applied these to the data products from the simulations in order to directly compare with observations.
+Our result shows that the scatter between the observations and simulations are very similar.
+Considering that the observational and simulated samples are matched to the best of our ability, their intrinsic properties are also similar.
+However, there may be limitations in our comparisons that may impact the results.
+For instance, there may be unknown observational effects that haven't been properly applied to the simulations.
+Even so, state-of-the-art simulations likely do not capture all the physical aspects that impact the scatter.
+For example, the spin of BHs is not modeled in the simulation which could change the scatter since the spin affects both the accretion rate and the energy that can be released through AGN feedback \citep{Dubois2014, 2019MNRAS.490.4133B, Habouzit2021} at some level.
+Even though the spin effect is still not well known and such a study is beyond the scope of this paper, a future effort may be warranted when the simulations incorporate spin.
  \todo{Xuheng checked the cited reference but could not find quantitatively how much this spin will change the simulation scatter.}
@@
 We compared the observed scaling relation \mbh-\smass\ with the predictions from numerical simulations.
-The observation data are composed of 626 quasars at $0.2 < z < 0.8$ imaged by HSC and 32 X-ray-selected quasars at $1.2 < z < 1.7$ imaged by HST.
+The observational data are composed of 626 quasars at $0.2 < z < 0.8$ imaged by HSC and 32 X-ray-selected quasars at $1.2 < z < 1.7$ imaged by HST.
 The simulations include a semi-analytic model (SAM) and five hydrodynamic simulations, i.e., MBII, Illustris, TNG100, TNG300 and Horizon-AGN.
 We carried out the comparisons in the observed parameter space to account for uncertainties and selection effects.
-To achieve this, we first injected random errors with the same observational uncertainty to the simulation, and then adopted the same selection condition to the simulation data (see Figure~\ref{fig:selection}).
+To achieve this, we first injected random errors with the same observational uncertainty to the simulation, and then adopted the same selection condition to the simulated data (see Figure~\ref{fig:selection}).
 Finally, we adopted the scaling relation from the local universe as our reference and performed comparisons using the scatter of the measurements and their central offset to the \red{D20 local scaling} relation.
@@
 
-\item{} Regarding the \red{offsets of the scaling relation from the D20 local} ($\Delta$\mbh\ at a given \smass), all simulations generally match the observations with some subtle, yet notable, differences.
+\item{} Regarding the \red{offsets of the scaling relation from the local one} ($\Delta$\mbh\ at a given \smass; D20), {\it all simulations generally match the observations} with some subtle, yet notable, differences.
 While Illustris\red{, MBII,} and Horizon-AGN show good correspondence with observations at $z<0.6$, the comparisons at $z>0.6$ are better for SAM, \red{MBII,} TNG100, TNG300 and Horizon-AGN.
-From $z\sim0.7$ to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
-\red{4/6 of the simulations have decreasing mass offset from $z=0.2$ and $z=0.6$ while the observation mass offset increases with redshift all the way, despite that the offset difference between $z=0.2$ and $z=0.6$ is well below the observed scatter.}
+Bridging the gap from \hbox{$z\sim0.7$} to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
+\blue{Four out of six of the simulations have a decreasing mass offset from $z=0.2$ to $z=0.6$ while the observational mass offset increases with redshift; however, this is well below the observed scatter.}
 %\todo{To add that 4/6 of the simulations have decreasing mass offsets from z=0.2 and 0.6 while the offsets from the observations increase with redshift all the way (Fig. 5). P15}
@@
 %\todo{For clarity the first paragraph after 3) should specify the stellar mass range considered when discussing the scatter of the local relation etc.}
-\red{These results are inferred by studying the sample with stellar mass mainly with the range [9.5, 11.5] $M_{\odot}$. Note that
-the} absolute value of stellar masses in both observation and theory have significant uncertainty (up to factor of two)\red{.
-For example, for the observation, the \smass\ of the galaxies depends on the assumption of initial mass function, possibly on the implementation of star formation in the models; for the simulation, the \smass\ depends on their definition (i.e., total mass or within 30~kpc aperture), and other subgrid models such as supernova feedback, AGN feedback.} In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematic effect.
+\red{These results are based on samples with stellar masses mainly with the range [9.5, 11.5] $M_{\odot}$. Note that
+the} value of stellar masses in both the observations and simulations have significant uncertainty (up to factor of two)\red{.
+For example, the observed \smass\ depends on the assumption of initial mass function and star formation history while the value of \smass\ in the simulation depends on how it's defined (i.e., total mass or within 30~kpc aperture), and other subgrid models such as supernova feedback, AGN feedback.} In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematic effect.
 Thus, in this work, we first consider the scatter as a diagnostic criteria to see whether some simulations match the data better than others.
@@
 In this stochastic scenario we expect the scatter of the scaling relations to increase towards higher redshift.
-In fact, the scatter level in the simulation without adding random noise is consistent with the {\it intrinsic} scatter estimations reported in~\citet{Ding2020, 2021arXiv210902751L} (i.e., $\lesssim0.35$~dex).
+In fact, the scatter level in the simulation without adding random noise is consistent with the {\it intrinsic} scatter estimations reported in~\citet{Ding2020,Li2021b} (i.e., $\lesssim0.35$~dex).
 This level is also not larger than the typical scatter of the local relations reported in the literature~\citep{Kormendy13, Gul++09, Reines2015}.
@@
 The simulations studied in this work have adopted completely different numerical techniques.
-However, all of them \red{have similar tightness intrinsic scaling relation and thus provide good agreement with the observation in terms of the sample dispersion}.
-In fact, the tightness of the scaling relation is stem from the same physics assumed in these simulations (i.e., AGN feedback).
-Thus, \red{our result} is {\it consistent} with the hypothesis\footnote{\red{As discussed in the Section~\ref{sec:dis}, by saying `consistent', we do not mean this hypothesis is the unique interpretation  which rule out the other possible models.}} that the AGN feedback as a causal link between \red{supermassive BH}s and their hosts plays a key role in establishing the scaling relation.
+Suprisingly, all of them \red{have similar tightness of the intrinsic scaling relation and thus provide good agreement with the observations in terms of the sample dispersion}.
+In fact, the tightness of the scaling relation \blue{likely stems} from the same physics assumed in these simulations (i.e., AGN feedback).
+Thus, \red{our result} is {\it consistent} with the hypothesis\footnote{\blue{By stating that our comparisons are `consistent' (Section~\ref{sec:dis}), we do not mean that our hypothesis is the only plausible interpretation; there may be others.}} that AGN feedback, as a causal link between \red{supermassive BH}s and their hosts, plays a key role in establishing the scaling relation.
 %\todo{P18: AGN feedback, causal link?}
@@
 At low redshift, the star formation and feedback ejection reduce the cold material leading to a lower accretion rate and a radio-mode-dominating feedback~\citep[e.g.][]{2012MNRAS.420.2662D,2016MNRAS.460.2979V,2018MNRAS.479.4056W}.
-Our comparison result shows that the level of intrinsic scatter in the scaling relation at redshifts up to 1.7 is consistent with the low redshift one (see \red{Table~\ref{tab:sum})}, which reveals the fact that at high redshift the AGN feedback described by the quasar mode has already regulated the tight correlation between \red{supermassive BH} and its host galaxy.
-After that, the radio-jet mode starts to take control at low redshift by maintaining the tightness of the scaling relation till the level we observe today.
-\todo{Address referee's P19 (to talk with John).
-Some discussions on the two modes.
-I plot a figure 9 for to understand it (see Figure~\ref{fig:fedd}).}
+Our comparison result shows that the level of intrinsic scatter in the scaling relation at redshifts up to 1.7 is consistent with low redshift (see \red{Table~\ref{tab:sum})}, \red{which reveals the fact that at high redshift the AGN feedback described by the quasar mode may be responsible at some level for the tight correlation between \red{supermassive BH} and its host galaxy.
+In Figure~\ref{fig:fedd}, we demonstrate that essentially all of the quasars in Horizon-AGN that match the observed samples are at high Eddington rates.} After that, the radio-jet mode starts to take control at low redshift by maintaining the tightness of the scaling relation till the level we observe today.
+
+%Most of the sample at $z=1.5$ are adopted at quasar mode (i.e., $f_{\rm Edd}>0.01$). The distribution are in the radio-jet mode ($f_{\rm Edd}<0.01$) at $z=0.3$.
 
 \begin{figure}
+%\begin{tabular}{c c}
 \centering
-\includegraphics[width=0.4\textwidth]{Horizon_fedd_dis.pdf}
+\includegraphics[trim = 0mm 0mm 0mm 30mm, clip, width=0.4\textwidth]{Horizon_fedd_dis.pdf}&
+%\includegraphics[trim = 0mm 0mm 0mm 30mm, clip, %width=0.4\textwidth]{TNG100_fedd_dis.pdf}\\
+%\end{tabular}
 \caption{\label{fig:fedd} 
-\red{Distribution of the Eddington ratio and \mbh\ for Horizon sample at high and low redshift range.
-Most of the sample at $z=1.5$ are adopted at quasar mode (i.e., $f_{\rm Edd}>0.01$).
-The distribution are in the radio-jet mode ($f_{\rm Edd}<0.01$) at $z=0.3$.}
-}
+\red{Distribution of Eddington ratio and \mbh\ for the Horizon-AGN sample at redshifts $z=0.3$ and $z=1.5$.
+The data points indicate the distribution of the selected sample.
+The black line denotes the criterion in the simulation for which a SMBH is in a quasar (above) or radio (below) mode.}}
 \end{figure}
@@
 The understanding of how and when the tight scaling relation emerged are crucial to test theoretical models \citep{Volonteri2021}.
-On the observational side, the James Webb Space Telescope will provide high-quality imaging data of AGNs at redshift up to $z\sim7$ (i.e., JWST cycle 1 program GO-1967 and GO-1727).
-These upcoming measurements will represent stringent tests on the proposed physical mechanisms for the initial formation of supermassive \red{BH}s and of their subsequent evolution with galaxies.
+On the observational side, the James Webb Space Telescope will provide high-quality imaging data of AGNs at redshift up to $z\sim7$ and beyond.
+The upcoming measurements will represent stringent tests on the proposed physical mechanisms for the initial formation of supermassive \red{BH}s and of their subsequent evolution with galaxies.
 

### 2022-04-25 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
Make notes and pass to TT

@@
 Thus, different values are used for calculating the luminosity.}
-%\todo{Aklant: The $\leq$ sign in the low accretion feedback mode of TNG is also not clear.
-Is it a fixed value or a distribution?}\aklant{[\bf{It just means that the efficiency is actually function (not a constant) but the maximum value is 0.2}]}
-%\todo{Aklant: Referee asks us whether the same radiative efficiency is used to compute AGN luminosity in all the simulations.
-But we already show these values in Table 1, which are different, don't we?} \aklant{\bf{Yes the radiative efficiencies are different in the different simulations, and we use these different values for the computing the luminosities in each case.
-This is true at least for the simulations that I provided to you.}}
 }
@@
 \section{Simulations and comparison strategy}
-%\todo{Uniform the descriptions of the simulations to lack homogeneity. (Illustris has star formation threshold). Re-write the section and provide the same information}
 \label{sec:simulations}
@@
 
-Halos were identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}.
+\red{Halos are identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}.
 Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}.
-As a common practice, the stellar mass is obtained by using a 3D spherical aperture of 30~kpc to represent the observed stellar mass.
+As a common practice, the stellar mass is obtained by using a 3D spherical aperture of 30~kpc to represent the observed stellar mass.}
 We adopt this definition of stellar masses for all \red{larger-scale cosmological} simulations described in the following sections, \red{except for Horizon-AGN which use total mass (see Section~\ref{subsec:Horizon}) for details.}  Using this definition, \citet{Pillepich2018} has shown that the corresponding stellar mass function is consistent with the observational measure.
@@
 Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN.
-\aklant{Halos and galaxies are identified similar to that of MBII}.
+\red{Halos and galaxies are identified similar to that of MBII}.
 As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy \red{stellar mass}.
@@
 Additionally, the radiative feedback implemented in Illustris~(summarized in the previous section) is also present in TNG.
-Lastly, \aklant{halo and galaxy identification, as well as calculation of galaxy stellar mass, is done in a similar manner to that of Illustris and MBII}.
+Lastly, \red{halo and galaxy identification, as well as calculation of galaxy stellar mass, is done in a similar manner to that of Illustris and MBII}.
 
@@
 
-Differing from simulations presented above, Horizon-AGN does not use a fixed threshold in the dark matter halo mass to seed BHs.
+\red{Differing from} simulations presented above, Horizon-AGN does not use a fixed threshold in the dark matter halo mass to seed BHs.
 BHs are seeded with a mass of $10^5 M_\odot$ in cells, with gas density above $n_0$ and stellar velocity dispersion larger than $100 \,\rm km\,s^{-1}$.
@@
 %\todo{Explain the offset depends.}
-\red{For comparison, the local scaling relation provided by  D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion \blue{with redshift}.
-This local relation \blue{(\mbh-\smass\))} is derived by \blue{fitting measurements for} 55 local galaxies as given in~\citet{Bennert++2011} and \citet{H+R04}.
-%, in which \smass\ measurements are Chabrier IMF based.
-}
+\red{For comparison, the local scaling relation provided by  D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion with redshift.
+This local (\mbh-\smass) relation is derived by fitting measurements for 55 local galaxies as given in~\citet{Bennert++2011} and \citet{H+R04}.}
 \red{For each sample, we focus on the \mbh\ residuals\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the $y$-axis) and calculate their mean and standard deviation to make comparisons with observations.}
@@
 For the simulated data, both the initial sample and that with observational effects applied (i.e., noise correction, and selection) are shown.
-Note that \blue{offsets can occur for the simulated sample in three cases}: an \blue{inherent} offset, an offset due to selection, and offsets from added noise and selection.
-For the first, it has been recognized~\citep[e.g.,][Figure 2]{Habouzit2021}, and seen in Figure~\ref{fig:comparsion}, that the  offset values \blue{vary over a range of} stellar mass, and thus the mean and standard derivation do not represent the entire mass distribution.}
+Note that offsets can occur for the simulated sample in three cases: an inherent offset, an offset due to selection, and offsets from added noise and selection.
+For the first, it has been recognized~\citep[e.g.,][Figure 2]{Habouzit2021}, and seen in our Figure~\ref{fig:comparsion}, that the  offset values vary over a range of stellar mass, and thus the mean and standard derivation do not represent the entire mass distribution.}
 \red{In this work, we focus on the latter two offset distributions, i.e., considering selection effects with and without noise correction.
@@
 In addition, the values of the central offset and scatter are presented
-in Table~\ref{tab:sum}, both before and after consideration of the noise. \blue{Comparisons with the} observations are presented in the remainder of this section.}
+in Table~\ref{tab:sum}, both before and after consideration of the noise. Comparisons with the observations are presented in the remainder of this section.}
 
@@
 In fact, after noise and selection is applied, the simulated sample exhibits very small offsets which agree remarkably well with the observed data.
-\blue{If the BHs are accurately characterized in the simulation, one interpretation is that the observations, including our HSC AGN sample, do not inform us of the true \mbh\ offsets as a function of \smass.}  This result underscores the importance of taking into account errors and selection --- without accounting for those, one could erroneously interpret an apparent trend as evolution in the opposite sense as the true one.
+\red{If the BHs are accurately characterized in the simulation, one interpretation is that the observations, including our HSC AGN sample, do not inform us of the true \mbh\ offsets as a function of \smass.}  This result underscores the importance of taking into account errors and selection --- without accounting for those, one could erroneously interpret an apparent trend as evolution in the opposite sense as the true one.
 The most direct way to circumvent these issues is to probe lower masses (\smass\  $<10^{10}M_{\odot}$) using a more sensitive instrument, such as JWST~\citep{Habouzit2022} across this redshift range \citep[see also][]{2011MNRAS.417.2085V}.
@@
 
-\blue{Regarding the survey volumes, we collected all available samples in the simulations to perform these comparisons.
+\red{Regarding the survey volumes, we collected all available samples in the simulations to perform these comparisons.
 The final sample sizes, used to compare with observation, are not set by design.
@@
 \red{To avoid any possible bias raised by sample mismatch, we designed our selection (Section~\ref{subsec:add_obs_eff}) so that the distribution of $L_{\rm bol}$ and \mbh\ are similar.
-We also assure that the \smass\ \blue{spans similar ranges}.
+We also assure that the \smass\ spans similar ranges.
 As a test, we loosened the selection by not requiring equivalent $L_{\rm bol}$ distributions.
 The result shows that the offset distributions for all simulations are similar (see demonstrations in Figure~\ref{fig:offsets_nochange}) to those requiring matched $L_{\rm bol}$ distributions.
-This test implies that our comparison results \blue{are stable}, even considering the possibility for AGN variability ($10-20\%$ level flux variation) and the lack of the obscured population being represented in our observed samples.
+This test implies that our comparison results are stable, even considering the possibility for AGN variability ($10-20\%$ level flux variation) and the lack of the obscured population being represented in our observed samples.
 }
@@
 \red{In the literature~\citep{Weinberger2018, Habouzit2021}, it has been noted that the mass correlations predicted by TNG300 and TNG100 are not identical.
-For example, TNG300 has larger scatter in \mbh\ at fixed \smass\ than TNG100 at \smass $>10^{10}M_{\odot}$.
+For example, TNG300 appares to have different scatter in \mbh\ at fixed \smass\ to TNG100 at \smass $>10^{10}M_{\odot}$.
 Also, BH growth is more efficient in TNG100 thus causing the BH mass function to have higher normalization at the low mass end.
@@
 For example, the spin of BHs is not modeled in the simulation which could change the scatter since the spin affects both the accretion rate and the energy that can be released through AGN feedback \citep{Dubois2014, 2019MNRAS.490.4133B, Habouzit2021} at some level.
-Even though the spin effect is still not well known and such a study is beyond the scope of this paper, a future effort may be warranted when the simulations incorporate spin.
- \todo{Xuheng checked the cited reference but could not find quantitatively how much this spin will change the simulation scatter.}
-}
+Even though the spin effect is still not well known and such a study is beyond the scope of this paper, a future effort may be warranted when the simulations incorporate spin.}
 
@@
 Bridging the gap from \hbox{$z\sim0.7$} to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
-\blue{Four out of six of the simulations have a decreasing mass offset from $z=0.2$ to $z=0.6$ while the observational mass offset increases with redshift; however, this is well below the observed scatter.}
-%\todo{To add that 4/6 of the simulations have decreasing mass offsets from z=0.2 and 0.6 while the offsets from the observations increase with redshift all the way (Fig. 5). P15}
+Four out of six of the simulations have a decreasing mass offset from $z=0.2$ to $z=0.6$ while the observational mass offset increases with redshift; however, this is well below the observed scatter.
 \end{enumerate}
 
-%\todo{For clarity the first paragraph after 3) should specify the stellar mass range considered when discussing the scatter of the local relation etc.}
 \red{These results are based on samples with stellar masses mainly with the range [9.5, 11.5] $M_{\odot}$. Note that
@@
 The simulations studied in this work have adopted completely different numerical techniques.
-Suprisingly, all of them \red{have similar tightness of the intrinsic scaling relation and thus provide good agreement with the observations in terms of the sample dispersion}.
-In fact, the tightness of the scaling relation \blue{likely stems} from the same physics assumed in these simulations (i.e., AGN feedback).
-Thus, \red{our result} is {\it consistent} with the hypothesis\footnote{\blue{By stating that our comparisons are `consistent' (Section~\ref{sec:dis}), we do not mean that our hypothesis is the only plausible interpretation; there may be others.}} that AGN feedback, as a causal link between \red{supermassive BH}s and their hosts, plays a key role in establishing the scaling relation.
+\red{Surprisingly, all of them have similar tightness of the intrinsic scaling relation and thus provide good agreement with the observations in terms of the sample dispersion}.
+In fact, the tightness of the scaling relation \red{likely stems} from the same physics assumed in these simulations (i.e., AGN feedback).
+Thus, \red{our result} is {\it consistent} with the hypothesis\footnote{\red{By stating that our comparisons are `consistent' (Section~\ref{sec:dis}), we do not mean that our hypothesis is the only plausible interpretation; there may be others.}} that AGN feedback, as a causal link between \red{supermassive BH}s and their hosts, plays a key role in establishing the scaling relation.
 %\todo{P18: AGN feedback, causal link?}
@@
 At low redshift, the star formation and feedback ejection reduce the cold material leading to a lower accretion rate and a radio-mode-dominating feedback~\citep[e.g.][]{2012MNRAS.420.2662D,2016MNRAS.460.2979V,2018MNRAS.479.4056W}.
-Our comparison result shows that the level of intrinsic scatter in the scaling relation at redshifts up to 1.7 is consistent with low redshift (see \red{Table~\ref{tab:sum})}, \red{which reveals the fact that at high redshift the AGN feedback described by the quasar mode may be responsible at some level for the tight correlation between \red{supermassive BH} and its host galaxy.
-In Figure~\ref{fig:fedd}, we demonstrate that essentially all of the quasars in Horizon-AGN that match the observed samples are at high Eddington rates.} After that, the radio-jet mode starts to take control at low redshift by maintaining the tightness of the scaling relation till the level we observe today.
+Our comparison result shows that the level of intrinsic scatter in the scaling relation at redshifts up to 1.7 is consistent with \red{low redshift (see Table~\ref{tab:sum}), which reveals the fact that at high redshift the AGN feedback described by the quasar mode may be responsible at some level for the tight correlation between supermassive BH and its host galaxy.
+In Figure~\ref{fig:fedd}, we demonstrate that essentially all of the quasars in Horizon-AGN that match the observed samples are at high Eddington rates.
+After that, the radio-jet mode starts to take control at low redshift by maintaining the tightness of the scaling relation till the level we observe today.
+}
 
@@
 \centering
-\includegraphics[trim = 0mm 0mm 0mm 30mm, clip, width=0.4\textwidth]{Horizon_fedd_dis.pdf}&
+\includegraphics[trim = 0mm 0mm 0mm 30mm, clip, width=0.4\textwidth]{Horizon_fedd_dis.pdf}\\
 %\includegraphics[trim = 0mm 0mm 0mm 30mm, clip, %width=0.4\textwidth]{TNG100_fedd_dis.pdf}\\
@@
 The understanding of how and when the tight scaling relation emerged are crucial to test theoretical models \citep{Volonteri2021}.
-On the observational side, the James Webb Space Telescope will provide high-quality imaging data of AGNs at redshift up to $z\sim7$ and beyond.
+On the observational side, the James Webb Space Telescope will provide high-quality imaging data of AGNs at redshift up to $z\sim7$ \red{and beyond}.
 The upcoming measurements will represent stringent tests on the proposed physical mechanisms for the initial formation of supermassive \red{BH}s and of their subsequent evolution with galaxies.
@@
 \begin{acknowledgments}
+\red{The authors thank the anonymous referee for helpful suggestions and comments that improved this paper. We fully appreciate input from Jingjing Shi.}
+
 This work was supported by World Premier International Research Center Initiative (WPI), MEXT, Japan.
-The authors fully appreciate input from Jingjing Shi.
-
 Based in part on observations made with the NASA/ESA Hubble Space Telescope, obtained at the Space Telescope Science Institute, which is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS 5-26555.
@@
 Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555.
+\red{This work was supported by JSPS KAKENHI Grant Number JP22K14071.} 
 JS is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.

### 2022-04-28 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
Short the abs

@@
 \begin{abstract}
-We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies (\mbh --\smass) at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model).
+We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host \red{galaxies} at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model).
 The observed sample consist of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter.
-To make fair comparisons, we first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations.
+\red{We} first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations.
 Over the full redshift range, our analysis demonstrates that all simulations predict a level of intrinsic scatter of the scaling relations comparable to the observations which appear to agree with the dispersion of the local relation.
-Regarding the mean scaling relation, Horizon-AGN and TNG are in closest agreement with the observational data at both low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties.
-For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and thus closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow.
-The consistency in the dispersion with redshift in our analysis lends support to the importance of both quasar and radio mode feedback prescriptions in the simulations.
-Finally, we investigate evolution as a function of stellar and \red{BH} mass, and argue that the most direct way to probe the co-evolution of galaxies and \red{BH}s is to increase the sensitivity, e.g., with JWST, thereby pushing to lower masses and minimizing possible biases arising from selection effects.
-
+Regarding the mean relation, Horizon-AGN and TNG are in closest agreement with the \red{observations} at low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties.
+For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow.
+The consistency in the dispersion with redshift in our analysis \red{supports} the importance of both quasar and radio mode feedback prescriptions in the simulations.
+Finally, we \red{highlight the importance of increasing} the sensitivity, e.g., JWST, thereby pushing to lower masses and minimizing biases \red{due to} selection effects.
 \end{abstract}
@@
 Collisionless particles (dark matter and star particles) are evolved using a particle-mesh solver with a cloud-in-cell interpolation.
-
+\red{The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation.
+Stellar feedback is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources.}
 %The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation with a constant star formation efficiency $\epsilon_*=0.02$, which occurs in regions where the gas number density exceeds the star formation threshold $n_0 = 0.1\,\rm H\, cm^{-3}$.
@@
 In each halo, we compute the fraction of gas which cools because of the atomic processes and settles into a disk~\citep{Mo1998}.
-The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr, according to BH feeding; \todo{Nicola: the link between BH feeding and star formation channels in this sentence is not clear.} (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion).
+The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr;  (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion).
 The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation which returns a fraction of the disk gas into a hot phase.
@@
 
-The BH accretion is based on both interaction-driven and disk instability feeding modes.
+\red{The BH accretion is assumed to follow from the gas instabilities resulting from either galaxy interactions and disk instabilities, and is thus related to star formations channels 2-3: a fraction of the cold gas destabilized during galaxy encounters and through disc instabilities is in fact accreted onto the central BHs (with the remaining fraction fueling star formation through channels 2-3 described above).
+Such fractions and the corresponding timescales for accretion are computed as described in~\citet[][in Section 3]{Menci2014}.}
+
 The SAM adopted here implements a new and improved  model for the AGN feedback with respect to the previous versions~\citep{Menci2008}.

### 2022-04-28 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
resubmit for ApJ

@@
 %% using aastex version 6.3
-%\documentclass[twocolumn, linenumbers]{aastex631}
-\documentclass[twocolumn]{aastex631}
+\documentclass[twocolumn, linenumbers]{aastex631}
+%\documentclass[twocolumn]{aastex631}
 
@@
 \newcommand{\todo}[1]{\textcolor{red}{[{\bf TODO}: #1]}}
-\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
 \newcommand{\jshi}[1]{\textcolor{orange}{#1}}
 \newcommand{\blue}[1]{\textcolor{blue}{#1}}
-\newcommand{\yo}[1]{\textcolor{purple}{[{\bf Yohan}: #1]}}
-\newcommand{\red}[1]{\textcolor{purple}{#1}}
+%\newcommand{\red}[1]{\textcolor{purple}{#1}}
+\newcommand{\red}[1]{{\bf #1}}
 
@@
 
-\author[0000-0002-0000-6977]{John D.Silverman}
+\author[0000-0002-0000-6977]{John D. Silverman}
 \affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
@@
 We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host \red{galaxies} at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model).
-The observed sample consist of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter.
+The observed sample consist\red{s} of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter.
 \red{We} first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations.
@@
 For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at \red{the} intervals between which the BH mass grows by a fixed fraction.
-(%\todo{Aklant: Referee asks: are these irregular intervals included in the feedback modeling, or simply due to the time-varying accretion onto BHs?
+%\todo{Aklant: Referee asks: are these irregular intervals included in the feedback modeling, or simply due to the time-varying accretion onto BHs?
 does it mean that the BH accretion is not modeled by the Bondi accretion between AGN feedback events?} \aklant{\bf{They are irregular simply because the BH mass growth is non- uniform.
@@
 In our work, the differences between TNG100 and TNG300 also exist.
-However, the difference are milder after selection effects and random noise injection have been applied to the samples.} \todo{The referee says TNG300 has larger scatter, but in Habouzit2021 section 4.2.2, it actually says scatter in TNG300 is smaller.
-Any one know if the referee is wrong?}
+However, the difference are milder after selection effects and random noise injection have been applied to the samples.}
+%\todo{The referee says TNG300 has larger scatter, but in Habouzit2021 section 4.2.2, it actually says scatter in TNG300 is smaller. Any one know if the referee is wrong?}
 
@@
 Bridging the gap from \hbox{$z\sim0.7$} to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
-Four out of six of the simulations have a decreasing mass offset from $z=0.2$ to $z=0.6$ while the observational mass offset increases with redshift; however, this is well below the observed scatter.
+\red{Four out of six of the simulations have a decreasing mass offset from $z=0.2$ to $z=0.6$ while the observational mass offset increases with redshift; however, this is well below the observed scatter.}
 \end{enumerate}
@@
 
-\bibliography{reference}{}
-%\input{manuscript.bbl}
+%\bibliography{reference}{}
+\input{manuscript.bbl}
 \bibliographystyle{aasjournal}

### 2022-05-07 projects/2020_HSC_to_numerical_simulation/manuscript/arxiv_sub/manuscript.tex
Create manuscript.tex

--- 2022-04-28 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
@@
 %% using aastex version 6.3
-\documentclass[twocolumn, linenumbers]{aastex631}
-%\documentclass[twocolumn]{aastex631}
+%\documentclass[twocolumn, linenumbers]{aastex631}
+\documentclass[twocolumn]{aastex631}
 
@@
 \newcommand\latex{La\TeX}
-\newcommand{\todo}[1]{\textcolor{red}{[{\bf TODO}: #1]}}
-\newcommand{\jshi}[1]{\textcolor{orange}{#1}}
-\newcommand{\blue}[1]{\textcolor{blue}{#1}}
-%\newcommand{\red}[1]{\textcolor{purple}{#1}}
-\newcommand{\red}[1]{{\bf #1}}
+%\newcommand{\red}[1]{{#1}}
+\newcommand{\red}[1]{\textcolor{red}{#1}}
 
@@
 
-\newcommand{\aklant}[1]{\textcolor{blue}{#1}}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \begin{abstract}
-We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host \red{galaxies} at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model).
-The observed sample consist\red{s} of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter.
-\red{We} first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations.
+We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model).
+The observed sample consists of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter.
+We first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations.
 Over the full redshift range, our analysis demonstrates that all simulations predict a level of intrinsic scatter of the scaling relations comparable to the observations which appear to agree with the dispersion of the local relation.
-Regarding the mean relation, Horizon-AGN and TNG are in closest agreement with the \red{observations} at low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties.
+Regarding the mean relation, Horizon-AGN and TNG are in closest agreement with the observations at low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties.
 For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow.
-The consistency in the dispersion with redshift in our analysis \red{supports} the importance of both quasar and radio mode feedback prescriptions in the simulations.
-Finally, we \red{highlight the importance of increasing} the sensitivity, e.g., JWST, thereby pushing to lower masses and minimizing biases \red{due to} selection effects.
+The consistency in the dispersion with redshift in our analysis supports the importance of both quasar and radio mode feedback prescriptions in the simulations.
+Finally, we highlight the importance of increasing the sensitivity, e.g., JWST, thereby pushing to lower masses and minimizing biases due to selection effects.
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
-The close correlations between \red{the mass of} supermassive black holes (\red{\mbh}) and the properties of their host galaxies (e.g., stellar mass\red{, \smass}) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
-To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over \red{cosmic time}.
-While, an {\it observed} evolution has been found \red{since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15} in} which the growth of BHs predates that of the host, other studies \red{\citep[e.g.,][]{Schramm2013, Sun2015} predict that} BHs grow commensurately with galaxies.
+The close correlations between the mass of supermassive black holes (\mbh) and the properties of their host galaxies (e.g., stellar mass, \smass) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
+To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over cosmic time.
+While, an {\it observed} evolution has been found since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15} in which the growth of BHs predates that of the host, other studies \citep[e.g.,][]{Schramm2013, Sun2015} predict that BHs grow commensurately with galaxies.
 However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15,Jahnke2009,  Ding2020,Li2021b}.
@@
 In this scenario, star formation is inhibited by the heating and unbinding of a significant amount of gas.
-Alternatively, the mass relations can be explained through an indirect connection in which AGN accretion and star formation are fed through a common \red{gas supply~\citep{Cen2015, Menci2016, angles_black_2017}.
-}Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
+Alternatively, the mass relations can be explained through an indirect connection in which AGN accretion and star formation are fed through a common gas supply~\citep{Cen2015, Menci2016, angles_black_2017}.
+Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
 However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ compared to what is observed today.
@@
 Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution,
-including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH \red{simulations~\citep{Schaye2015, Crain2015, McAlpine2016},} Illustris moving-mesh \red{simulation~\citep{Genel2014, 2014MNRAS.444.1518V, Sijacki2015, Nelson2015, Li2019}, the Horizon-AGN simulation~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D, 2016MNRAS.460.2979V}, and the SIMBA simulation~\citep{Thomas2019, Dave2019}.
-}
+including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH simulations~\citep{Schaye2015, Crain2015, McAlpine2016}, Illustris moving-mesh simulation~\citep{Genel2014, 2014MNRAS.444.1518V, Sijacki2015, Nelson2015, Li2019}, the Horizon-AGN simulation~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D, 2016MNRAS.460.2979V}, and the SIMBA simulation~\citep{Thomas2019, Dave2019}.
 In particular, the \mbh-\smass\ relation using BH populations using six large-scale cosmological simulations (i.e, Illustris, TNG100, TNG300, Horizon-AGN, EAGLE, and SIMBA) has been compared with observations in the local universe in a recent study~\citep{Habouzit2021}.
@@
 In~\citet{Ding2020b}, a direct comparison has been performed using 32 X-ray-selected AGN at $1.2<z<1.7$ and a direct comparison with two state-of-the-art simulation efforts, including {\tt MassiveBlackII} (MBII) and a Semi-analytic Model \citep[SAM,][]{Menci2014, Menci2016}.
-The dispersion in the mass ratio between \red{BH} mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) favoring the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.
+The dispersion in the mass ratio between BH mass and stellar mass is significantly more consistent with the MBII prediction ($\sim0.3$~dex) favoring the hypothesis of AGN feedback being responsible for a causal link between the BH and its host galaxy.
 
@@
 A sample of $\sim$5000 type-1 SDSS quasars from the DR14 catalog~\citep{Paris2018} at $0.2<z<1$ has been imaged by the high-resolution Subaru Strategic Program (SSP) wide area survey~\citep{Aihara2019} using Hyper Suprime-Cam~\citep{Miyazaki2018}.
-With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been \red{performed \citep[][]{Li2021a}} to obtain the flux and color of each quasar's host galaxy.
+With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been performed \citep[][]{Li2021a} to obtain the flux and color of each quasar's host galaxy.
 The stare-of-the-art image modeling software {\tt lenstronomy} \citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task.
@@
 The typical error of \mbh\ are estimated to be 0.4 dex.
-\red{The mass ranges for the entire sample are log(\smass) $\in$ [9.0, 11.5] $M_{\odot}$, and log(\mbh) $\in$  [6.5, 10.0] $M_{\odot}$)}.
+The mass ranges for the entire sample are log(\smass) $\in$ [9.0, 11.5] $M_{\odot}$, and log(\mbh) $\in$  [6.5, 10.0] $M_{\odot}$).
  We refer the reader to~\citet{Li2021a} in the Section~4.2 for more details.
@@
 \mbh\ is determined by \citet{Schulze2018} using near-infrared spectroscopic observations of the broad \halpha\ emission line with the recipe provided by~\citet{Vestergaard2006}, in a consistent manner to that adopted for HSC sample.
-\red{The mass ranges for the HST sample are log(\smass) $\in$ [9.5, 11.0] $M_{\odot}$, and log(\mbh) $\in$  [7.5, 9.0] $M_{\odot}$)}.
+The mass ranges for the HST sample are log(\smass) $\in$ [9.5, 11.0] $M_{\odot}$, and log(\mbh) $\in$  [7.5, 9.0] $M_{\odot}$).
  We refer the reader to D20 for a more detailed description of the analysis.
@@
 \cline{1-6}
-{\bf AGN feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ \red{radiative efficiency})} \\
+{\bf AGN feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ radiative efficiency)} \\
 High acc. mode & 0.05 $\times$ 0.1 & 0.05 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.15 $\times$ 0.1 \\
@@
 $\dot{M}_{Bondi}= 4\pi G^2M_{BH}^2 \rho/c_s^3$.
-\red{The `$\leq$' sign in the low accretion feedback mode of TNG means that the feedback efficiency follows a distribution with a maximum value of 0.2.
+The `$\leq$' sign in the low accretion feedback mode of TNG means that the feedback efficiency follows a distribution with a maximum value of 0.2.
 Note that the radiative efficiencies are different in various simulations.
-Thus, different values are used for calculating the luminosity.}
+Thus, different values are used for calculating the luminosity.
 }
@@
 In Table~\ref{tab:sim_sum}, we summarized the key elements for each hydrodynamic simulation being considered.
-\red{We note that each simulation adopts either a  \cite{2003PASP..115..763C} or a \cite{1955ApJ...121..161S} IMF.
+We note that each simulation adopts either a  \cite{2003PASP..115..763C} or a \cite{1955ApJ...121..161S} IMF.
 To make self-consistent comparisons, we ensure that the adopted IMF for both the simulations and the observations are consistent.
 The assumed IMF is needed to obtain the mass-to-light ratio and convert the observed luminosity to stellar mass to perform the comparisons.
-For numerical simulation, the mass is the base material which is IMF independent.}
+For numerical simulation, the mass is the base material which is IMF independent.
 
@@
 MBII is a high-resolution cosmological hydrodynamic simulation that has a box size of $(142.7~\mathrm{cMpc})^3$
-and $2\times1792^3$~\red{(i.e., dark matter + gas)} particles. 
-%\todo{Aklant: Please answer what is the factor 2 here. A twin box with 1793$^3$ each?\aklant{\bf{The 2 represents that there are $1792^3$ DM particles and $1792^3$ gas particles}}} 
+and $2\times1792^3$~(i.e., dark matter + gas) particles. 
 The simulation is based on smooth particle hydrodynamic (SPH) code \texttt{P-GADGET}, a hybrid version of the parallel code {\tt GADGET}~\citep{2005MNRAS.364.1105S}.
@@
 
-To model supermassive \red{BH, the initial} seed with mass $5\times 10^{5}~M_{\odot}/h$ are inserted into halos of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$.
+To model supermassive BH, the initial seed with mass $5\times 10^{5}~M_{\odot}/h$ are inserted into halos of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$.
 Once seeded, BH growth via gas accretion is assigned at a rate of $\dot{M}_{BH}={4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the interstellar medium (ISM) gas at cold phase; $v_{BH}$ is the relative velocity between the BH and its surrounding gas.
@@
 The accreted gas is released as radiation at a radiative efficiency of 10\%.
-A fraction of 5\% of the radiated energy thermally couples to the surrounding gas as \red{BH} (or AGN) feedback~\citep{2005Natur.433..604D}.
+A fraction of 5\% of the radiated energy thermally couples to the surrounding gas as BH (or AGN) feedback~\citep{2005Natur.433..604D}.
 A mildly super-Eddington (two times Eddington rate) is allowed.
@@
 
-\red{Halos are identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}.
+Halos are identified using a friends-of-friends (FOF) group finder~\citep{1985ApJ...292..371D}.
 Galaxies are identified with the stellar matter components of subhalos; these subhalos are identified using {\tt SUBFIND} within the halos~\citep{2005MNRAS.364.1105S}.
-As a common practice, the stellar mass is obtained by using a 3D spherical aperture of 30~kpc to represent the observed stellar mass.}
-We adopt this definition of stellar masses for all \red{larger-scale cosmological} simulations described in the following sections, \red{except for Horizon-AGN which use total mass (see Section~\ref{subsec:Horizon}) for details.}  Using this definition, \citet{Pillepich2018} has shown that the corresponding stellar mass function is consistent with the observational measure.
+As a common practice, the stellar mass is obtained by using a 3D spherical aperture of 30~kpc to represent the observed stellar mass.
+We adopt this definition of stellar masses for all larger-scale cosmological simulations described in the following sections, except for Horizon-AGN which use total mass (see Section~\ref{subsec:Horizon}) for details.
+Using this definition, \citet{Pillepich2018} has shown that the corresponding stellar mass function is consistent with the observational measure.
 Even more, the stellar mass using this 3D aperture can achieve good agreement to those measured within the Petrosian radii in observational studies~\citep{Schaye2015}.
@@
 \subsection{Illustris}
-The Illustris Project is another large scale hydrodynamics simulation, introduced \red{in~\citet{Genel2014, 2014MNRAS.444.1518V, 2014Natur.509..177V, Sijacki2015, Nelson2015}.} The simulation consist of a volume of (106.5 cMpc)$^3$~(slightly smaller than MassiveBlack II),
+The Illustris Project is another large scale hydrodynamics simulation, introduced in~\citet{Genel2014, 2014MNRAS.444.1518V, 2014Natur.509..177V, Sijacki2015, Nelson2015}.
+The simulation consist of a volume of (106.5 cMpc)$^3$~(slightly smaller than MassiveBlack II),
 and was run with the moving Voronoi mesh code {\tt Arepo}~\citep{2010MNRAS.401..791S} with a base cosmology adopted from WMAP9 results~\citep{2013ApJS..208...19H}.
@@
 The boost factor $\alpha=100$ is introduced to account for the unresolved multiphase ISM~\citep{Springel2005, 2009MNRAS.398...53B}, which is otherwise expected to underestimate the density around the BHs.
-Lastly, accreting \red{BH}s radiate with a bolometric luminosity given by $\epsilon_r \dot{M}_{BH}c^2$, where $\dot{M}_{BH}$ is the mass accretion rate and $\epsilon_r=0.2$ is the radiative efficiency.
+Lastly, accreting BHs radiate with a bolometric luminosity given by $\epsilon_r \dot{M}_{BH}c^2$, where $\dot{M}_{BH}$ is the mass accretion rate and $\epsilon_r=0.2$ is the radiative efficiency.
 
@@
 In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy.
-For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at \red{the} intervals between which the BH mass grows by a fixed fraction.
-%\todo{Aklant: Referee asks: are these irregular intervals included in the feedback modeling, or simply due to the time-varying accretion onto BHs?
-does it mean that the BH accretion is not modeled by the Bondi accretion between AGN feedback events?} \aklant{\bf{They are irregular simply because the BH mass growth is non- uniform.
-So it takes different amounts of time for the BH to grow by a fixed fraction.
-Bondi accretion is happening at all times.
-I have now removed the word `irregular' from this statement.}}
+For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at the intervals between which the BH mass grows by a fixed fraction.
 The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency.
 Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN.
-\red{Halos and galaxies are identified similar to that of MBII}.
-As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy \red{stellar mass}.
+Halos and galaxies are identified similar to that of MBII.
+As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy stellar mass.
 %, assuming a \cite{2003PASP..115..763C} IMF.
@@
 \subsection{IllustrisTNG}
-{\it The Next Generation Illustris Simulations} \red{(IllustrisTNG, hereafter, TNG)~\citep{2018MNRAS.475..676S, Pillepich2018, Naiman2018, Marinacci2018, Nelson2018}} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes.
+{\it The Next Generation Illustris Simulations} (IllustrisTNG, hereafter, TNG)~\citep{2018MNRAS.475..676S, Pillepich2018, Naiman2018, Marinacci2018, Nelson2018} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes.
 It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modeling, and 3) addressing the identified shortcomings of the previous generation simulations.
-\red{Note that TNG simulations employ a modified version of the Bondi formalism, with $c_s$ explicitly including a B term for these magneto-hydro simulations.}
+Note that TNG simulations employ a modified version of the Bondi formalism, with $c_s$ explicitly including a B term for these magneto-hydro simulations.
 
@@
 The BH accretion also follows the Bondi-Hoyle-Lyttleton formalism, but without any boost factor~(unlike Illustris).
-Accreting \red{BH}s release energy with a radiative efficiency of 0.2~(same as Illustris).
+Accreting BHs release energy with a radiative efficiency of 0.2~(same as Illustris).
 The inclusion of the magnetic fields can affect the relationship between the BHs and their host galaxies properties; the \mbh-\smass\ mean relation is higher with magnetic fields~\citep{2018MNRAS.473.4077P}.
@@
 Instead of releasing hot bubbles, this feedback mode in TNG is purely kinetic.
-In particular, there is a directional injection of momentum along a randomly \red{chosen direction~\citep{2017MNRAS.465.3291W, 2018MNRAS.479.4056W}}.
+In particular, there is a directional injection of momentum along a randomly chosen direction~\citep{2017MNRAS.465.3291W, 2018MNRAS.479.4056W}.
 % at irregular intervals.
@@
 Additionally, the radiative feedback implemented in Illustris~(summarized in the previous section) is also present in TNG.
-Lastly, \red{halo and galaxy identification, as well as calculation of galaxy stellar mass, is done in a similar manner to that of Illustris and MBII}.
+Lastly, halo and galaxy identification, as well as calculation of galaxy stellar mass, is done in a similar manner to that of Illustris and MBII.
 
@@
 Collisionless particles (dark matter and star particles) are evolved using a particle-mesh solver with a cloud-in-cell interpolation.
-\red{The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation.
-Stellar feedback is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources.}
-%The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation with a constant star formation efficiency $\epsilon_*=0.02$, which occurs in regions where the gas number density exceeds the star formation threshold $n_0 = 0.1\,\rm H\, cm^{-3}$.
-%A Salpeter IMF is assumed.
-%\red{Stellar feedback} is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources.
+The simulation includes gas cooling down to $10^4\, \rm K$ \citep{sutherland&dopita93}, and stochastic star formation.
+Stellar feedback is modeled as mechanical energy injection from Type Ia SNe, Type II SNe and stellar winds, with the metal enrichment from these sources.
 
-\red{Differing from} simulations presented above, Horizon-AGN does not use a fixed threshold in the dark matter halo mass to seed BHs.
+Differing from simulations presented above, Horizon-AGN does not use a fixed threshold in the dark matter halo mass to seed BHs.
 BHs are seeded with a mass of $10^5 M_\odot$ in cells, with gas density above $n_0$ and stellar velocity dispersion larger than $100 \,\rm km\,s^{-1}$.
@@
 Only galaxies with more than 50 particles are considered.
-\red{With this approach for Horizon-AGN, the adopted galaxy mass corresponds to the total stellar mass of a galaxy, which is different than the other hydrodynamic simulations (i.e., within a 3D 30~kpc spherical aperture).
-This definition of stellar mass is commonly used in Horizon-AGN, whose stellar mass function is known~\citep{2017MNRAS.467.4739K}} to be in good agreement with observations.
-%\todo{Mention that the \smass.}
+With this approach for Horizon-AGN, the adopted galaxy mass corresponds to the total stellar mass of a galaxy, which is different than the other hydrodynamic simulations (i.e., within a 3D 30~kpc spherical aperture).
+This definition of stellar mass is commonly used in Horizon-AGN, whose stellar mass function is known~\citep{2017MNRAS.467.4739K} to be in good agreement with observations.
 
@@
 \caption{\label{fig:selection}Demonstration of AGN selection using MBII.
-{\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles) \red{for those at redshift $z=0.6$}.
+{\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles) for those at redshift $z=0.6$.
 A matched HSC sample is shown by the orange data points.
 The light green background cloud shows the {\it intrinsic} simulated number density in this parameter space.
-\red{Note that this is the first step of sample selection.
+Note that this is the first step of sample selection.
 We further use an AGN magnitude cut to assure that the simulation sample has a similar $L_{\rm bol}$ distribution (e.g., see Figure~\ref{fig:offsets_nochange}-left) and \mbh\ distribution with the observations.
-We then use the same \smass\ cut to construct the final sample.}
+We then use the same \smass\ cut to construct the final sample.
 {\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample.
-% For visual comparison between the HSC and HST selection, we show the region of the HST selection window in the left panel as dashed lines. % \todo{No mention of the redshift in Fig.2}
 }
@@
 The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation which returns a fraction of the disk gas into a hot phase.
-%A Salpeter IMF is adopted in the SAM simulation.
-\red{A $\Lambda$CDM power} spectrum of perturbations with a total matter density parameter $\Omega_0=0.3$, a baryon density parameter 
+A $\Lambda$CDM power spectrum of perturbations with a total matter density parameter $\Omega_0=0.3$, a baryon density parameter 
 $\Omega_b=0.04$, a dark energy density parameter $\Omega_\Lambda=0.7$, and a Hubble constant $h$=0.7 is adopted.
@@
 
-\red{The BH accretion is assumed to follow from the gas instabilities resulting from either galaxy interactions and disk instabilities, and is thus related to star formations channels 2-3: a fraction of the cold gas destabilized during galaxy encounters and through disc instabilities is in fact accreted onto the central BHs (with the remaining fraction fueling star formation through channels 2-3 described above).
-Such fractions and the corresponding timescales for accretion are computed as described in~\citet[][in Section 3]{Menci2014}.}
+The BH accretion is assumed to follow from the gas instabilities resulting from either galaxy interactions and disk instabilities, and is thus related to star formations channels 2-3: a fraction of the cold gas destabilized during galaxy encounters and through disc instabilities is in fact accreted onto the central BHs (with the remaining fraction fueling star formation through channels 2-3 described above).
+Such fractions and the corresponding timescales for accretion are computed as described in~\citet[][in Section 3]{Menci2014}.
 
@@
 As mentioned above, \smass\ and \mbh\ for HSC and HST samples are measured with a similar approach; thus their uncertainty levels are expected to be equivalent.
-We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = \red{0.2}~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.
-\red{Since the selection of the simulation sample based on $L_{\rm bol}$ has limited effects in this study (see the discussion in Section~\ref{sec:dis} and Figure~\ref{fig:offsets_nochange} for details), the AGN variability correction is not considered.}
+We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = 0.2~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.
+Since the selection of the simulation sample based on $L_{\rm bol}$ has limited effects in this study (see the discussion in Section~\ref{sec:dis} and Figure~\ref{fig:offsets_nochange} for details), the AGN variability correction is not considered.
 
@@
 
-\red{Comparing with} the HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should match the relationship between \mbh-$L_{\rm bol}$ as seen in the HSC sample.
-We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it \red{left}}).
+Comparing with the HSC sample: (1) The observed sample consists of type-1 AGN, and thus the simulated sample should match the relationship between \mbh-$L_{\rm bol}$ as seen in the HSC sample.
+We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it left}).
 (2) The $i$-band magnitude of the AGN are bright (see Section~\ref{sec:hsc}).
-%The specific selection is made as follows: for systems at $z<0.5$ and $z>0.5$, the AGN $i$-band magnitude is required to be brighter than 20.5 mag and 22.0 mag, respectively.
-\red{The specific selection is carried out as follows: a value of AGN $i$-band magnitude is chosen to make the sample selection such that the $L_{\rm bol}$ distribution is similar to the observations (see Section~\ref{sec:dis} for details).
-}
+The specific selection is carried out as follows: a value of AGN $i$-band magnitude is chosen to make the sample selection such that the $L_{\rm bol}$ distribution is similar to the observations (see Section~\ref{sec:dis} for details).
 Since the simulations do not provide the observed AGN magnitude, we adopt a simulated rest-frame magnitude or L$_{\rm 5100}$ and assume the quasar continuum as a single power-law with an index of $\alpha_\nu=-0.44$~\citep{2001AJ....122..549V} to calculate the observed $i$-band magnitude.
@@
 
-\red{Comparing with} the HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example).
-Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., \red{log(\mbh)} between [7.7, 8.6] $M_{\odot}$).
+Comparing with the HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example).
+Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., log(\mbh) between [7.7, 8.6] $M_{\odot}$).
 The HST sample covers the higher redshift range $1.2<z<1.7$, which is considered as a single redshift bin to make the comparison with the simulations at $z=1.5$.
 
-%\todo{Address the properties what does it mean by intrinsic. P9+P12}
+\section{Results} \label{sec:result}
+For comparison, the local scaling relation provided by  D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion with redshift.
+This local (\mbh-\smass) relation is derived by fitting measurements for 55 local galaxies as given in~\citet{Bennert++2011} and \citet{H+R04}.
+For each sample, we focus on the \mbh\ residuals\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the $y$-axis) and calculate their mean and standard deviation to make comparisons with observations.
 
-\section{Results} \label{sec:result}
-%\todo{Explain the offset depends.}
-\red{For comparison, the local scaling relation provided by  D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion with redshift.
-This local (\mbh-\smass) relation is derived by fitting measurements for 55 local galaxies as given in~\citet{Bennert++2011} and \citet{H+R04}.}
-\red{For each sample, we focus on the \mbh\ residuals\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the $y$-axis) and calculate their mean and standard deviation to make comparisons with observations.}
-
-\red{In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
+In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
 For the simulated data, both the initial sample and that with observational effects applied (i.e., noise correction, and selection) are shown.
 Note that offsets can occur for the simulated sample in three cases: an inherent offset, an offset due to selection, and offsets from added noise and selection.
-For the first, it has been recognized~\citep[e.g.,][Figure 2]{Habouzit2021}, and seen in our Figure~\ref{fig:comparsion}, that the  offset values vary over a range of stellar mass, and thus the mean and standard derivation do not represent the entire mass distribution.}
-\red{In this work, we focus on the latter two offset distributions, i.e., considering selection effects with and without noise correction.
+For the first, it has been recognized~\citep[e.g.,][Figure 2]{Habouzit2021}, and seen in our Figure~\ref{fig:comparsion}, that the  offset values vary over a range of stellar mass, and thus the mean and standard derivation do not represent the entire mass distribution.
+In this work, we focus on the latter two offset distributions, i.e., considering selection effects with and without noise correction.
 To aid in visualization of the differences among the various simulations, compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}.
@@
 In addition, the values of the central offset and scatter are presented
-in Table~\ref{tab:sum}, both before and after consideration of the noise. Comparisons with the observations are presented in the remainder of this section.}
+in Table~\ref{tab:sum}, both before and after consideration of the noise. Comparisons with the observations are presented in the remainder of this section.
 
@@
 The black line in each panel indicates the local relation adopted by~\citet{Ding2020}.
-The background cloud (in green and yellow \red{with contours}) shows the intrinsic simulation number density before injecting random noise and applying selection effects.
-\red{The TNG100 and TNG300 appear to present similar results (see discussion section)}.
+The background cloud (in green and yellow with contours) shows the intrinsic simulation number density before injecting random noise and applying selection effects.
+The TNG100 and TNG300 appear to present similar results (see discussion section).
 }
@@
 \caption{\label{fig:offsets} 
-\red{Colored histograms show the offset distributions} for all simulated samples.
+Colored histograms show the offset distributions for all simulated samples.
 The mean value and standard deviation of each are summarized in Table~\ref{tab:sum}.
@@
 The mean values for the observed sample (i.e., yellow lines) are also given in each panel.
-\red{To address the effect of noise, the offset distributions of the simulation without adding noise are also shown by the open black histograms.}
+To address the effect of noise, the offset distributions of the simulation without adding noise are also shown by the open black histograms.
 For the MBII simulation, the sample at redshift 0.6 is used to compare with other samples at $z=0.5$ and $z=0.7$. 
@@
 The black line shows the evolution by fitting the offset as a function of redshift.
-\red{The black dots (with error bars) represent the mean (and standard deviation) values for the observations in four redshift bins.
-The \smass\ and \mbh\ ranges are different for each redshift bin, which are indicated in Figure~\ref{fig:comparsion}.} The predictions from the numerical simulations, given in Table~\ref{tab:sum}, are presented by different colored symbols.
-The grey horizontal band illustrates the level of dispersion for the local sample (\red{D20}).
+The black dots (with error bars) represent the mean (and standard deviation) values for the observations in four redshift bins.
+The \smass\ and \mbh\ ranges are different for each redshift bin, which are indicated in Figure~\ref{fig:comparsion}.
+The predictions from the numerical simulations, given in Table~\ref{tab:sum}, are presented by different colored symbols.
+The grey horizontal band illustrates the level of dispersion for the local sample (D20).
 }
@@
 These results are consistent with the Kolmogorov-Smirnov (KS) test performed using the offset distributions between each simulated sample and the observed sample --- the p-values are given in Table~\ref{tab:pvalue} showing that Horizon-AGN and Illustris have a good statistical match to the scaling relation at $z<0.6$ (i.e., p-value $> 0.1$), while the TNG100, TNG300 and Horizon-AGN simulation do well at $z>0.6$.
-\red{Except for MBII and Horizon-AGN, we also see that the other simulations have mass offsets that are decreasing from $z=0.2$ to $z=0.6$, while the observations offsets increasing with redshift up to $z\sim1.5$.
-However, this inconsistency is well below the $1\sigma$ scatter level.}
-Overall, we find that the mass \red{correlation} between \red{supermassive BH}s and their host galaxies are generally consistent between observations and simulations with some subtle differences which are not at the level of concern for this present study.
-%\todo{To add that 4/6 of the simulations have decreasing mass offsets from z=0.2 and 0.6 while the offsets from the observations increase with redshift all the way (Fig. 5). P15}
-%\todo{Update with MBII's new result. }
-%\todo{shift offset at 0.3 and discussion the difference. P11}
+Except for MBII and Horizon-AGN, we also see that the other simulations have mass offsets that are decreasing from $z=0.2$ to $z=0.6$, while the observations offsets increasing with redshift up to $z\sim1.5$.
+However, this inconsistency is well below the $1\sigma$ scatter level.
+Overall, we find that the mass correlation between supermassive BHs and their host galaxies are generally consistent between observations and simulations with some subtle differences which are not at the level of concern for this present study.
 
@@
 We include the intrinsic values from the simulations in the figures to address how the observational effects (i.e., random noise and selection) change the observed scaling relations and offsets.
-First, considering the observed quasar sample (same in each panel), there is a trend for which \red{BH}s have masses further offset from their stellar mass with decreasing stellar mass.
+First, considering the observed quasar sample (same in each panel), there is a trend for which BHs have masses further offset from their stellar mass with decreasing stellar mass.
 This trend is not seen in any of the simulations after noise and selection effects have been applied.
@@
 
-Interestingly, we notice that MBII and Illustris have \red{BH}s intrinsically under-massive relative to their galaxies at the lower masses that reach the \red{D20 local scaling} relation at higher masses.
-In contrast, TNG and Horizon-AGN have \red{BH}s slightly elevated from \red{D20} local relation at most masses.
-These differences between simulations present two different scenarios, either one where the \red{BH}s come later or co-evolution with the two growing in tandem.
+Interestingly, we notice that MBII and Illustris have BHs intrinsically under-massive relative to their galaxies at the lower masses that reach the D20 local scaling relation at higher masses.
+In contrast, TNG and Horizon-AGN have BHs slightly elevated from D20 local relation at most masses.
+These differences between simulations present two different scenarios, either one where the BHs come later or co-evolution with the two growing in tandem.
 Considering the former scenario, Illustris shows the strongest trend with stellar mass.
 In fact, after noise and selection is applied, the simulated sample exhibits very small offsets which agree remarkably well with the observed data.
-\red{If the BHs are accurately characterized in the simulation, one interpretation is that the observations, including our HSC AGN sample, do not inform us of the true \mbh\ offsets as a function of \smass.}  This result underscores the importance of taking into account errors and selection --- without accounting for those, one could erroneously interpret an apparent trend as evolution in the opposite sense as the true one.
+If the BHs are accurately characterized in the simulation, one interpretation is that the observations, including our HSC AGN sample, do not inform us of the true \mbh\ offsets as a function of \smass.
+This result underscores the importance of taking into account errors and selection --- without accounting for those, one could erroneously interpret an apparent trend as evolution in the opposite sense as the true one.
 The most direct way to circumvent these issues is to probe lower masses (\smass\  $<10^{10}M_{\odot}$) using a more sensitive instrument, such as JWST~\citep{Habouzit2022} across this redshift range \citep[see also][]{2011MNRAS.417.2085V}.
-%\todo{highlight the selection effect that the offset doesn't reflect the truth. P20}
 
@@
 \end{tabular}
-\caption{\label{fig:deltaMM} Comparisons of the offset of \mbh\ (to the \red{D20 local scaling} relation) as a function of stellar mass from observational data and the simulations at $z\sim0.7$.
-In each stellar mass bin \red{(minimum number of objects is larger than 6)}, we give the mean and standard deviation of the offset values.
-\red{To consider random noise, we use the average of ten realizations to calculate the mean and standard deviation in each bin.} The histograms on the right show the offset distribution with lines marking the mean offsets for the observations and simulations \red{using the full galaxy sample}.
-The green color distributions \red{with contours show the intrinsic simulated sample distribution without random noise and selection effect.}
+\caption{\label{fig:deltaMM} Comparisons of the offset of \mbh\ (to the D20 local scaling relation) as a function of stellar mass from observational data and the simulations at $z\sim0.7$.
+In each stellar mass bin (minimum number of objects is larger than 6), we give the mean and standard deviation of the offset values.
+To consider random noise, we use the average of ten realizations to calculate the mean and standard deviation in each bin.
+The histograms on the right show the offset distribution with lines marking the mean offsets for the observations and simulations using the full galaxy sample.
+The green color distributions with contours show the intrinsic simulated sample distribution without random noise and selection effect.
 }
@@
 
-%\begin{deluxetable*}{lcccc}
-%\tablecaption{Summary of the central offsets and scatters without noise\label{tab:sum_no_noise}}
-%\tablewidth{0pt}
-%\tablehead{
-%\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison (offset, scatter)} & \colhead{HST comparison (offset, scatter)} \\
-%\cline{2-4} 
-%\colhead{} &  \colhead{$0.2<z<0.4$} & \colhead{$0.4<z<0.6$} & \colhead{$0.6<z<0.8$} & \colhead{$1.2<z<1.7$}
-%}
-%\startdata
-%SAM & (0.72, 0.20) & (0.64, 0.18) & (0.56, 0.16)  & (0.08, 0.18) \\
-%MBII & (-0.15, 0.21) & \multicolumn{2}{c}{(-0.15, 0.22) [$z=0.6$]}  & (0.08, 0.19)\\
-%Illustris & (0.03, 0.32) & (0.10, 0.36) & (0.08, 0.36)  & (0.04, 0.19) \\
-%TNG100 &  (0.27, 0.20) & (0.27, 0.15) & (0.26, 0.16)  & (0.36, 0.15) \\
-%TNG300 & (0.25, 0.21) & (0.19, 0.23) & (0.20, 0.22)  & (0.32, 0.16) \\
-%Horizon-AGN & (0.19, 0.26) & (0.18, 0.21) & (0.28, 0.20)  & (0.37, 0.13) \\
-%\enddata
-%\tablecomments{Same as Table~\ref{tab:sum} but without inject noise to the simulation data. Note that same selection window is still adopted to infer the values. \todo{Merger Table 2 and 3}}
-%\end{deluxetable*}
-
 \begin{deluxetable*}{lccccc}
-\tablecaption{\red{Summary of the central offsets and scatters\label{tab:sum}}}
-%\tablewidth{0pt}
+\tablecaption{Summary of the central offsets and scatters\label{tab:sum}}
 \tabletypesize{\footnotesize}
@@
 \tablecomments{This table collects the comparison results of the \smass-\mbh\ correlations between different simulation at different redshift.
-The value shows the central position offset to the \red{D20 local scaling} relation and the scatters measured around the local relation after applying the offset.
+The value shows the central position offset to the D20 local scaling relation and the scatters measured around the local relation after applying the offset.
 A positive offset means the \mbh\ value predicted by the simulation is higher than the local relationship measurement at fixed \smass\ value.
@@
 For the MBII sample, the simulation does not produce the sample at $z=0.5$ or $z=0.7$, but rather at $z=0.6$.
-We use Monte Carlo approach \red{with 500 realizations} to infer the uncertainties of the values in the table, finding that the uncertainties are within $\pm 0.03$.
+We use Monte Carlo approach with 500 realizations to infer the uncertainties of the values in the table, finding that the uncertainties are within $\pm 0.03$.
 }
@@
 \section{Discussion} \label{sec:dis}
-%\todo{Discussion when shift offset as z=0.3. P11}
-\red{In this study, there are a few issues that may bias the results thus need to be considered.
+In this study, there are a few issues that may bias the results thus need to be considered.
 First, the mass offsets are compared to the observe relation derived in the local Universe (D20).
@@
 In general, the updated results show that the evolution of the simulations are consistent with our interpretations in Section~\ref{subsec:offset}.
-This result can be expected since most of the simulations have demonstrated a good match to the observations at redshift $z=0.3$.}
+This result can be expected since most of the simulations have demonstrated a good match to the observations at redshift $z=0.3$.
 
-\red{Regarding the survey volumes, we collected all available samples in the simulations to perform these comparisons.
+Regarding the survey volumes, we collected all available samples in the simulations to perform these comparisons.
 The final sample sizes, used to compare with observation, are not set by design.
 Despite that the observed samples are not volume-limited and the simulated samples are not volume-matched, fortunately, the volume of all the simulations appear to be sufficient, i.e., all simulations have a similar amount (or more) of data points to compare with the observations (see Figure~\ref{fig:comparsion}).
-Also, similar results are found with the smaller and larger volumes simulations, e.g., TNG100 and TNG300, which reflect the fact that the simulation volume reaches a sufficient size to be effective for these comparisons.}
+Also, similar results are found with the smaller and larger volumes simulations, e.g., TNG100 and TNG300, which reflect the fact that the simulation volume reaches a sufficient size to be effective for these comparisons.
 
-\red{To avoid any possible bias raised by sample mismatch, we designed our selection (Section~\ref{subsec:add_obs_eff}) so that the distribution of $L_{\rm bol}$ and \mbh\ are similar.
+To avoid any possible bias raised by sample mismatch, we designed our selection (Section~\ref{subsec:add_obs_eff}) so that the distribution of $L_{\rm bol}$ and \mbh\ are similar.
 We also assure that the \smass\ spans similar ranges.
@@
 This test implies that our comparison results are stable, even considering the possibility for AGN variability ($10-20\%$ level flux variation) and the lack of the obscured population being represented in our observed samples.
-}
 
@@
 \caption{\label{fig:offsets_nochange} 
-\red{Mass comparisons using different bolometric luminosity selection.
+Mass comparisons using different bolometric luminosity selection.
 {\it left:}~$L_{\rm bol}$ distribution of our simulated samples at $z=0.5$ tailored to match with the observations.
@@
 {\it right:} Offset distributions using these two selections with the dashed line being the result for a mismatched luminosity distribution).
-As shown, the different selections have minimal effect on the offset distributions.}
+As shown, the different selections have minimal effect on the offset distributions.
 }
@@
 \caption{\label{fig:offsets_vz_shiftz03} 
-\red{Same as Figure~\ref{fig:offsets_vz} but now including a shift of all simulations to match the observations at $z=0.3$.}
+Same as Figure~\ref{fig:offsets_vz} but now including a shift of all simulations to match the observations at $z=0.3$.
 }
@@
 
-%\todo{TNG100 and TNG300 -- explain the why no difference between TNGs.
-P8}~\red{We note that TNG100 and TNG300 yield very similar comparison results, thus only TNG100 is presented in~Figure~\ref{fig:comparsion}}.
-\red{In the literature~\citep{Weinberger2018, Habouzit2021}, it has been noted that the mass correlations predicted by TNG300 and TNG100 are not identical.
+In the literature~\citep{Weinberger2018, Habouzit2021}, it has been noted that the mass correlations predicted by TNG300 and TNG100 are not identical.
 For example, TNG300 appares to have different scatter in \mbh\ at fixed \smass\ to TNG100 at \smass $>10^{10}M_{\odot}$.
@@
 In our work, the differences between TNG100 and TNG300 also exist.
-However, the difference are milder after selection effects and random noise injection have been applied to the samples.}
-%\todo{The referee says TNG300 has larger scatter, but in Habouzit2021 section 4.2.2, it actually says scatter in TNG300 is smaller. Any one know if the referee is wrong?}
+However, the difference are milder after selection effects and random noise injection have been applied to the samples.
 
-%\todo{Some discussion on BH spin. What does consistent means? P9, P12 and P18.}
-\red{We considered all known observational effects, including sample selection and random noise injection, and applied these to the data products from the simulations in order to directly compare with observations.
+We considered all known observational effects, including sample selection and random noise injection, and applied these to the data products from the simulations in order to directly compare with observations.
 Our result shows that the scatter between the observations and simulations are very similar.
@@
 For example, the spin of BHs is not modeled in the simulation which could change the scatter since the spin affects both the accretion rate and the energy that can be released through AGN feedback \citep{Dubois2014, 2019MNRAS.490.4133B, Habouzit2021} at some level.
-Even though the spin effect is still not well known and such a study is beyond the scope of this paper, a future effort may be warranted when the simulations incorporate spin.}
+Even though the spin effect is still not well known and such a study is beyond the scope of this paper, a future effort may be warranted when the simulations incorporate spin.
 
@@
 To achieve this, we first injected random errors with the same observational uncertainty to the simulation, and then adopted the same selection condition to the simulated data (see Figure~\ref{fig:selection}).
-Finally, we adopted the scaling relation from the local universe as our reference and performed comparisons using the scatter of the measurements and their central offset to the \red{D20 local scaling} relation.
+Finally, we adopted the scaling relation from the local universe as our reference and performed comparisons using the scatter of the measurements and their central offset to the D20 local scaling relation.
 Our main results are summarized as follows:
@@
 
-\item{} Regarding the \red{offsets of the scaling relation from the local one} ($\Delta$\mbh\ at a given \smass; D20), {\it all simulations generally match the observations} with some subtle, yet notable, differences.
-While Illustris\red{, MBII,} and Horizon-AGN show good correspondence with observations at $z<0.6$, the comparisons at $z>0.6$ are better for SAM, \red{MBII,} TNG100, TNG300 and Horizon-AGN.
+\item{} Regarding the offsets of the scaling relation from the local one ($\Delta$\mbh\ at a given \smass; D20), {\it all simulations generally match the observations} with some subtle, yet notable, differences.
+While Illustris, MBII, and Horizon-AGN show good correspondence with observations at $z<0.6$, the comparisons at $z>0.6$ are better for SAM, MBII, TNG100, TNG300 and Horizon-AGN.
 Bridging the gap from \hbox{$z\sim0.7$} to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
-\red{Four out of six of the simulations have a decreasing mass offset from $z=0.2$ to $z=0.6$ while the observational mass offset increases with redshift; however, this is well below the observed scatter.}
+Four out of six of the simulations have a decreasing mass offset from $z=0.2$ to $z=0.6$ while the observational mass offset increases with redshift; however, this is well below the observed scatter.
 \end{enumerate}
 
-\red{These results are based on samples with stellar masses mainly with the range [9.5, 11.5] $M_{\odot}$. Note that
-the} value of stellar masses in both the observations and simulations have significant uncertainty (up to factor of two)\red{.
-For example, the observed \smass\ depends on the assumption of initial mass function and star formation history while the value of \smass\ in the simulation depends on how it's defined (i.e., total mass or within 30~kpc aperture), and other subgrid models such as supernova feedback, AGN feedback.} In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematic effect.
+These results are based on samples with stellar masses mainly with the range [9.5, 11.5] $M_{\odot}$.
+Note that the value of stellar masses in both the observations and simulations have significant uncertainty (up to factor of two).
+For example, the observed \smass\ depends on the assumption of initial mass function and star formation history while the value of \smass\ in the simulation depends on how it's defined (i.e., total mass or within 30~kpc aperture), and other subgrid models such as supernova feedback, AGN feedback.
+In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematic effect.
 Thus, in this work, we first consider the scatter as a diagnostic criteria to see whether some simulations match the data better than others.
@@
 The simulations studied in this work have adopted completely different numerical techniques.
-\red{Surprisingly, all of them have similar tightness of the intrinsic scaling relation and thus provide good agreement with the observations in terms of the sample dispersion}.
-In fact, the tightness of the scaling relation \red{likely stems} from the same physics assumed in these simulations (i.e., AGN feedback).
-Thus, \red{our result} is {\it consistent} with the hypothesis\footnote{\red{By stating that our comparisons are `consistent' (Section~\ref{sec:dis}), we do not mean that our hypothesis is the only plausible interpretation; there may be others.}} that AGN feedback, as a causal link between \red{supermassive BH}s and their hosts, plays a key role in establishing the scaling relation.
-%\todo{P18: AGN feedback, causal link?}
+Surprisingly, all of them have similar tightness of the intrinsic scaling relation and thus provide good agreement with the observations in terms of the sample dispersion.
+In fact, the tightness of the scaling relation likely stems from the same physics assumed in these simulations (i.e., AGN feedback).
+Thus, our result is {\it consistent} with the hypothesis\footnote{By stating that our comparisons are `consistent' (Section~\ref{sec:dis}), we do not mean that our hypothesis is the only plausible interpretation; there may be others.} that AGN feedback, as a causal link between supermassive BHs and their hosts, plays a key role in establishing the scaling relation.
 
@@
 In theoretical models, AGN feedback is often assumed to consist of two distinct modes:
-a quasar-heating mode where the \red{BH} accretion rates are comparable to the Eddington rate and a radio-jet mode occurring at low accretion rates (see, e.g., Section~\ref{subsec:Horizon}).
-In high redshift universe, the cold material in early universe leads to the vigorous accretion to the \red{supermassive BH} which drives the high accretion rates, and thus the quasar mode dominates the feedback.
+a quasar-heating mode where the BH accretion rates are comparable to the Eddington rate and a radio-jet mode occurring at low accretion rates (see, e.g., Section~\ref{subsec:Horizon}).
+In high redshift universe, the cold material in early universe leads to the vigorous accretion to the supermassive BH which drives the high accretion rates, and thus the quasar mode dominates the feedback.
 At low redshift, the star formation and feedback ejection reduce the cold material leading to a lower accretion rate and a radio-mode-dominating feedback~\citep[e.g.][]{2012MNRAS.420.2662D,2016MNRAS.460.2979V,2018MNRAS.479.4056W}.
-Our comparison result shows that the level of intrinsic scatter in the scaling relation at redshifts up to 1.7 is consistent with \red{low redshift (see Table~\ref{tab:sum}), which reveals the fact that at high redshift the AGN feedback described by the quasar mode may be responsible at some level for the tight correlation between supermassive BH and its host galaxy.
+Our comparison result shows that the level of intrinsic scatter in the scaling relation at redshifts up to 1.7 is consistent with low redshift (see Table~\ref{tab:sum}), which reveals the fact that at high redshift the AGN feedback described by the quasar mode may be responsible at some level for the tight correlation between supermassive BH and its host galaxy.
 In Figure~\ref{fig:fedd}, we demonstrate that essentially all of the quasars in Horizon-AGN that match the observed samples are at high Eddington rates.
 After that, the radio-jet mode starts to take control at low redshift by maintaining the tightness of the scaling relation till the level we observe today.
-}
-
-%Most of the sample at $z=1.5$ are adopted at quasar mode (i.e., $f_{\rm Edd}>0.01$). The distribution are in the radio-jet mode ($f_{\rm Edd}<0.01$) at $z=0.3$.
 
 \begin{figure}
-%\begin{tabular}{c c}
 \centering
 \includegraphics[trim = 0mm 0mm 0mm 30mm, clip, width=0.4\textwidth]{Horizon_fedd_dis.pdf}\\
-%\includegraphics[trim = 0mm 0mm 0mm 30mm, clip, %width=0.4\textwidth]{TNG100_fedd_dis.pdf}\\
-%\end{tabular}
 \caption{\label{fig:fedd} 
-\red{Distribution of Eddington ratio and \mbh\ for the Horizon-AGN sample at redshifts $z=0.3$ and $z=1.5$.
+Distribution of Eddington ratio and \mbh\ for the Horizon-AGN sample at redshifts $z=0.3$ and $z=1.5$.
 The data points indicate the distribution of the selected sample.
-The black line denotes the criterion in the simulation for which a SMBH is in a quasar (above) or radio (below) mode.}}
+The black line denotes the criterion in the simulation for which a SMBH is in a quasar (above) or radio (below) mode.}
 \end{figure}
@@
 However, beyond $z>0.2$, the scatter and the central distribution of the scaling relations are dominated by measurement uncertainty and selection effects (see Figures~\ref{fig:comparsion} and~\ref{fig:deltaMM}) and a forward modeling in the observational plane becomes essential.
-\red{Indeed, those effects would hamper our understanding of whether BHs and their hosts co-evolve or not.
-For example, from trends seen with stellar mass in Illustris and MBII (Figure~\ref{fig:deltaMM}), we found that the observations of the \mbh\ offsets as a function of \smass\  show a very different trend to the intrinsic one.}
+Indeed, those effects would hamper our understanding of whether BHs and their hosts co-evolve or not.
+For example, from trends seen with stellar mass in Illustris and MBII (Figure~\ref{fig:deltaMM}), we found that the observations of the \mbh\ offsets as a function of \smass\  show a very different trend to the intrinsic one.
 
-Extending this study to even higher redshift \red{and lower mass galaxies (}\smass\ $<10^{10}M_{\odot}$) will be very beneficial, probing closer to the epoch of formation of massive galaxies and \red{supermassive BH}s.
+Extending this study to even higher redshift and lower mass galaxies (\smass\ $<10^{10}M_{\odot}$) will be very beneficial, probing closer to the epoch of formation of massive galaxies and supermassive BHs.
 The understanding of how and when the tight scaling relation emerged are crucial to test theoretical models \citep{Volonteri2021}.
-On the observational side, the James Webb Space Telescope will provide high-quality imaging data of AGNs at redshift up to $z\sim7$ \red{and beyond}.
-The upcoming measurements will represent stringent tests on the proposed physical mechanisms for the initial formation of supermassive \red{BH}s and of their subsequent evolution with galaxies.
+On the observational side, the James Webb Space Telescope will provide high-quality imaging data of AGNs at redshift up to $z\sim7$ and beyond.
+The upcoming measurements will represent stringent tests on the proposed physical mechanisms for the initial formation of supermassive BHs and of their subsequent evolution with galaxies.
 
 \begin{acknowledgments}
-\red{The authors thank the anonymous referee for helpful suggestions and comments that improved this paper. We fully appreciate input from Jingjing Shi.}
+The authors thank the anonymous referee for helpful suggestions and comments that improved this paper. We fully appreciate input from Jingjing Shi.
 
@@
 Support for this work was provided by NASA through grant number HST-GO-15115 from the Space Telescope Science Institute, which is operated by AURA, Inc., under NASA contract NAS 5-26555.
-\red{This work was supported by JSPS KAKENHI Grant Number JP22K14071.} 
+This work was supported by JSPS KAKENHI Grant Number JP22K14071.
 JS is supported by JSPS KAKENHI Grant Number JP18H01251 and the World Premier International Research Center Initiative (WPI), MEXT, Japan.
@@
 \begin{deluxetable*}{lcccc}
-\tablecaption{\red{Summary of the p-value using KS test \label{tab:pvalue}}}
+\tablecaption{Summary of the p-value using KS test \label{tab:pvalue}}
 \tablewidth{0pt}
@@
 \enddata
-\tablecomments{These p-values are obtained by the KS test between the simulation and the observation \red{based on one realization}.}
+\tablecomments{These p-values are obtained by the KS test between the simulation and the observation based on one realization.}
 \end{deluxetable*}

### 2022-05-13 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
Finish revision

--- 2022-04-28 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
@@
 \newcommand\latex{La\TeX}
-\newcommand{\todo}[1]{\textcolor{red}{[{\bf TODO}: #1]}}
-\newcommand{\ding}[1]{\textcolor{red}{[{\bf Xuheng}: #1]}}
-\newcommand{\jshi}[1]{\textcolor{orange}{#1}}
-\newcommand{\blue}[1]{\textcolor{blue}{#1}}
-\newcommand{\yo}[1]{\textcolor{purple}{[{\bf Yohan}: #1]}}
-\newcommand{\red}[1]{\textcolor{purple}{#1}}
+%\newcommand{\red}[1]{{#1}}
+\newcommand{\red}[1]{\textcolor{red}{#1}}
+\newcommand{\blue}[1]{\textcolor{blue}{\bf #1}}
 
@@
 \begin{abstract}
-We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host \red{galaxies} at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model).
-The observed sample consist of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter.
-\red{We} first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations.
+We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model).
+The observed sample consists of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter.
+We first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations.
 Over the full redshift range, our analysis demonstrates that all simulations predict a level of intrinsic scatter of the scaling relations comparable to the observations which appear to agree with the dispersion of the local relation.
-Regarding the mean relation, Horizon-AGN and TNG are in closest agreement with the \red{observations} at low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties.
+Regarding the mean relation, Horizon-AGN and TNG are in closest agreement with the observations at low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties.
 For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow.
-The consistency in the dispersion with redshift in our analysis \red{supports} the importance of both quasar and radio mode feedback prescriptions in the simulations.
-Finally, we \red{highlight the importance of increasing} the sensitivity, e.g., JWST, thereby pushing to lower masses and minimizing biases \red{due to} selection effects.
+The consistency in the dispersion with redshift in our analysis supports the importance of both quasar and radio mode feedback prescriptions in the simulations.
+Finally, we highlight the importance of increasing the sensitivity, e.g., JWST, thereby pushing to lower masses and minimizing biases due to selection effects.
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
-The close correlations between \red{the mass of} supermassive black holes (\red{\mbh}) and the properties of their host galaxies (e.g., stellar mass\red{, \smass}) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
-To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over \red{cosmic time}.
-While, an {\it observed} evolution has been found \red{since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15} in} which the growth of BHs predates that of the host, other studies \red{\citep[e.g.,][]{Schramm2013, Sun2015} predict that} BHs grow commensurately with galaxies.
+The close correlations between the mass of supermassive black holes (\mbh) and the properties of their host galaxies (e.g., stellar mass, \smass) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
+To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over cosmic time.
+While, an {\it observed} evolution has been found since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15} in which the growth of BHs predates that of the host, other studies\blue{~\citep[e.g.,][]{Schramm2013, Sun2015, 2021ApJ...906..103L}} predict that BHs grow commensurately with galaxies.
 However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15,Jahnke2009,  Ding2020,Li2021b}.
@@
 In this scenario, star formation is inhibited by the heating and unbinding of a significant amount of gas.
-Alternatively, the mass relations can be explained through an indirect connection in which AGN accretion and star formation are fed through a common \red{gas supply~\citep{Cen2015, Menci2016, angles_black_2017}.
-}Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
-However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ compared to what is observed today.
+Alternatively, the mass relations can be explained through an indirect connection in which AGN accretion and star formation are fed through a common gas supply~\citep{Cen2015, Menci2016, angles_black_2017}.
+Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
+However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ compared to what is observed today~\blue{\citep[e.g.,][]{Ginat2016, 2020MNRAS.498.5652K}}.
 
 Numerical simulations provide an opportunity to further understand the connection between BHs and their host galaxies.
-For example, a comparison of scaling relations has been made using state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and observational measurements at  $0.3<z<1$ \citep[e.g., ][]{DeG++15}, which show a positive evolution (i.e., the mass growth of the BH growth predates that of its host).
+For example, a comparison of scaling relations has been made using state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and observational measurements at  $0.3<z<1$ \citep[e.g., ][]{DeG++15}, which show a positive evolution (i.e., the \blue{mass growth of the BH predates} that of its host).
 Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution,
-including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH \red{simulations~\citep{Schaye2015, Crain2015, McAlpine2016},} Illustris moving-mesh \red{simulation~\citep{Genel2014, 2014MNRAS.444.1518V, Sijacki2015, Nelson2015, Li2019}, the Horizon-AGN simulation~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D, 2016MNRAS.460.2979V}, and the SIMBA simulation~\citep{Thomas2019, Dave2019}.
-}
+including the Magneticum Pathfinder smooth-particle hydrodynamics (SPH) Simulations~\citep{Steinborn2015}, the Evolution and Assembly of Galaxies and their Environments~(EAGLE) suite of SPH simulations~\citep{Schaye2015, Crain2015, McAlpine2016}, Illustris moving-mesh simulation~\citep{Genel2014, 2014MNRAS.444.1518V, Sijacki2015, Nelson2015, Li2019}, the Horizon-AGN simulation~\citep{2014MNRAS.444.1453D, 2016MNRAS.463.3948D, 2016MNRAS.460.2979V}, and the SIMBA simulation~\citep{Thomas2019, Dave2019}.
 In particular, the \mbh-\smass\ relation using BH populations using six large-scale cosmological simulations (i.e, Illustris, TNG100, TNG300, Horizon-AGN, EAGLE, and SIMBA) has been compared with observations in the local universe in a recent study~\citep{Habouzit2021}.
@@
 A sample of $\sim$5000 type-1 SDSS quasars from the DR14 catalog~\citep{Paris2018} at $0.2<z<1$ has been imaged by the high-resolution Subaru Strategic Program (SSP) wide area survey~\citep{Aihara2019} using Hyper Suprime-Cam~\citep{Miyazaki2018}.
-With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been \red{performed \citep[][]{Li2021a}} to obtain the flux and color of each quasar's host galaxy.
-The stare-of-the-art image modeling software {\tt lenstronomy} \citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task.
+With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been performed \citep[][]{Li2021a} to obtain the flux and color of each quasar's host galaxy.
+The \blue{state-of-the-art} image modeling software {\tt lenstronomy} \citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task.
 This approach is first developed by~\citet{Ding2020} and used to decompose the near-infrared emission of the HST sample (see next section).
@@
 
-To model supermassive \red{BH, the initial} seed with mass $5\times 10^{5}~M_{\odot}/h$ are inserted into halos of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$.
+To model supermassive BH, the initial seed with mass $5\times 10^{5}~M_{\odot}/h$ \blue{is} inserted into halos of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$.
 Once seeded, BH growth via gas accretion is assigned at a rate of $\dot{M}_{BH}={4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the interstellar medium (ISM) gas at cold phase; $v_{BH}$ is the relative velocity between the BH and its surrounding gas.
@@
 In the quasar-mode which holds for BHs with Eddington ratio $>0.01$, the AGNs deposit $5\%$~(quasar-mode feedback efficiency) of their released energy into the surrounding gas as thermal energy.
-For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at \red{the} intervals between which the BH mass grows by a fixed fraction.
-(%\todo{Aklant: Referee asks: are these irregular intervals included in the feedback modeling, or simply due to the time-varying accretion onto BHs?
-does it mean that the BH accretion is not modeled by the Bondi accretion between AGN feedback events?} \aklant{\bf{They are irregular simply because the BH mass growth is non- uniform.
-So it takes different amounts of time for the BH to grow by a fixed fraction.
-Bondi accretion is happening at all times.
-I have now removed the word `irregular' from this statement.}}
+For Eddington ratios $<0.01$, the AGN feedback is in radio-mode where the thermal energy is released as hot bubbles with a radius of $\sim$ 100~kpc at the intervals between which the BH mass grows by a fixed fraction.
 The energy of the bubbles is given by $\epsilon_m \epsilon_r \delta M_{BH} c^2$ where $\delta M_{BH}$ is the change in BH mass within the last time interval, and $\epsilon_m=0.35$ is the radio-mode feedback efficiency.
 Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN.
-\red{Halos and galaxies are identified similar to that of MBII}.
-As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy \red{stellar mass}.
+Halos and galaxies are identified similar to that of MBII.
+As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy stellar mass.
 %, assuming a \cite{2003PASP..115..763C} IMF.
@@
 
-\red{Comparing with} the HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example).
-Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., \red{log(\mbh)} between [7.7, 8.6] $M_{\odot}$).
+Comparing with the HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example).
+Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., log(\mbh) between [7.7, 8.6] $M_{\odot}$).
 The HST sample covers the higher redshift range $1.2<z<1.7$, which is considered as a single redshift bin to make the comparison with the simulations at $z=1.5$.
 
-%\todo{Address the properties what does it mean by intrinsic. P9+P12}
+\section{Results} \label{sec:result}
+For comparison, the local scaling relation provided by  D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion with redshift.
+This local (\mbh-\smass) relation is derived by fitting measurements for 55 local galaxies as given in~\citet{Bennert++2011} and \citet{H+R04}.
+For each sample, we focus on the \mbh\ residuals\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the $y$-axis) and calculate their mean and standard deviation to make comparisons with observations.
 
-\section{Results} \label{sec:result}
-%\todo{Explain the offset depends.}
-\red{For comparison, the local scaling relation provided by  D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion with redshift.
-This local (\mbh-\smass) relation is derived by fitting measurements for 55 local galaxies as given in~\citet{Bennert++2011} and \citet{H+R04}.}
-\red{For each sample, we focus on the \mbh\ residuals\footnote{The value of the slope for the local sample is close to 1, and thus if taking the \smass\ to calculate the residual for each system, the offset value remains the same.} (i.e., the offset to the local relation along the $y$-axis) and calculate their mean and standard deviation to make comparisons with observations.}
-
-\red{In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
+In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
 For the simulated data, both the initial sample and that with observational effects applied (i.e., noise correction, and selection) are shown.
-Note that offsets can occur for the simulated sample in three cases: an inherent offset, an offset due to selection, and offsets from added noise and selection.
-For the first, it has been recognized~\citep[e.g.,][Figure 2]{Habouzit2021}, and seen in our Figure~\ref{fig:comparsion}, that the  offset values vary over a range of stellar mass, and thus the mean and standard derivation do not represent the entire mass distribution.}
-\red{In this work, we focus on the latter two offset distributions, i.e., considering selection effects with and without noise correction.
+Note that offsets can occur for the simulated \blue{samples} in three cases: an inherent offset, an offset due to selection, and offsets from added noise and selection.
+For the first, it has been recognized~\citep[e.g.,][Figure 2]{Habouzit2021}, and seen in our Figure~\ref{fig:comparsion}, that the  offset values vary over a range of stellar mass, and thus the mean and standard derivation do not represent the entire mass distribution.
+In this work, we focus on the latter two offset distributions, i.e., considering selection effects with and without noise correction.
 To aid in visualization of the differences among the various simulations, compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}.
@@
 The black line in each panel indicates the local relation adopted by~\citet{Ding2020}.
-The background cloud (in green and yellow \red{with contours}) shows the intrinsic simulation number density before injecting random noise and applying selection effects.
-\red{The TNG100 and TNG300 appear to present similar results (see discussion section)}.
+The background cloud (in green and yellow with contours) shows the intrinsic simulation number density before injecting random noise and applying selection effects.
+The TNG100 and TNG300 appear to present similar results (see discussion section).
+\blue{Note that different sample adopt either a Chabrier or a Salpeter IMF for calculating the stellar mass, thus the \smass\ value for the observation and the local relation can be slightly different in each vertical plane.}
 }
@@
 \section{Discussion} \label{sec:dis}
-%\todo{Discussion when shift offset as z=0.3. P11}
-\red{In this study, there are a few issues that may bias the results thus need to be considered.
-First, the mass offsets are compared to the observe relation derived in the local Universe (D20).
+In this study, there are a few issues that may bias the results thus need to be considered.
+First, the mass offsets are compared to the \blue{observed} relation derived in the local Universe (D20).
 In fact, the different simulations could have different mean relations at $z=0$~\citep[e.g.,][]{Habouzit2021}.
 As a result, the interpretation of the BH mass offsets of the simulations with redshift, anchored to the D20 local scaling relation, can be different if using the local relation of each individual simulation.
-In addition, the stellar mass of the Horizon-AGN sample is the total mass while that for the other hydrodynamic simulations are determined within a 3D 30 kpc spherical aperture.
-Therefore, in Figure~\ref{fig:offsets_vz_shiftz03}, we manually shift all simulations to match the observations at $z=0.3$.
+In addition, the stellar mass of the Horizon-AGN sample is the total mass while that for the other hydrodynamic simulations are determined within a 3D 30 kpc spherical aperture\footnote{\blue{In fact, we also checked to use total stellar mass for Illustris, TNG100, and TNG300 for the comparison, the results appear to be consistent with the ones when using the 30 kpc stellar mass.}}.
+Therefore, in Figure~\ref{fig:offsets_vz_shiftz03}, we manually \blue{recalibrate the offset of all simulations so that their mean offset value  at $z=0.3$ are at the same level with the observations}.
 This enables the evolutionary trend in the offsets of each sample to be clearer.
 In general, the updated results show that the evolution of the simulations are consistent with our interpretations in Section~\ref{subsec:offset}.
-This result can be expected since most of the simulations have demonstrated a good match to the observations at redshift $z=0.3$.}
+This result can be expected since most of the simulations have demonstrated a good match to the observations at redshift $z=0.3$.
 
-\red{Regarding the survey volumes, we collected all available samples in the simulations to perform these comparisons.
+Regarding the survey volumes, we collected all available samples in the simulations to perform these comparisons.
 The final sample sizes, used to compare with observation, are not set by design.
 Despite that the observed samples are not volume-limited and the simulated samples are not volume-matched, fortunately, the volume of all the simulations appear to be sufficient, i.e., all simulations have a similar amount (or more) of data points to compare with the observations (see Figure~\ref{fig:comparsion}).
-Also, similar results are found with the smaller and larger volumes simulations, e.g., TNG100 and TNG300, which reflect the fact that the simulation volume reaches a sufficient size to be effective for these comparisons.}
+Also, similar results are found with the smaller and larger volumes simulations, e.g., TNG100 and TNG300, which reflect the fact that the simulation volume reaches a sufficient size to be effective for \blue{the comparisons in the observational plane.
+Even though, the intrinsic scatters of TNG100 and TNG300 (before the noise/selection) can be still different.}\footnote{\blue{In particular, our study is made at \smass$>10~M_{\odot}$, while intrinsically, the subgrid models of the TNG simulation can change a lot at low redshift, especially for \smass$<10.5~M_{\odot}$ (see green controus in Figure 3 for $z<0.7$ sample).
+}}
 
-\red{To avoid any possible bias raised by sample mismatch, we designed our selection (Section~\ref{subsec:add_obs_eff}) so that the distribution of $L_{\rm bol}$ and \mbh\ are similar.
+To avoid any possible bias raised by sample mismatch, we designed our selection (Section~\ref{subsec:add_obs_eff}) so that the distribution of $L_{\rm bol}$ and \mbh\ are similar.
 We also assure that the \smass\ spans similar ranges.
@@
 In our work, the differences between TNG100 and TNG300 also exist.
-However, the difference are milder after selection effects and random noise injection have been applied to the samples.} \todo{The referee says TNG300 has larger scatter, but in Habouzit2021 section 4.2.2, it actually says scatter in TNG300 is smaller.
-Any one know if the referee is wrong?}
+However, the difference are milder after selection effects and random noise injection have been applied to the samples.
 
-%\todo{Some discussion on BH spin. What does consistent means? P9, P12 and P18.}
-\red{We considered all known observational effects, including sample selection and random noise injection, and applied these to the data products from the simulations in order to directly compare with observations.
+We considered all known observational effects, including sample selection and random noise injection, and applied these to the data products from the simulations in order to directly compare with observations.
 Our result shows that the scatter between the observations and simulations are very similar.
@@
 
-\item{} Regarding the \red{offsets of the scaling relation from the local one} ($\Delta$\mbh\ at a given \smass; D20), {\it all simulations generally match the observations} with some subtle, yet notable, differences.
-While Illustris\red{, MBII,} and Horizon-AGN show good correspondence with observations at $z<0.6$, the comparisons at $z>0.6$ are better for SAM, \red{MBII,} TNG100, TNG300 and Horizon-AGN.
+\item{} Regarding the offsets of the scaling relation from the local one ($\Delta$\mbh\ at a given \smass; D20), {\it all simulations generally match the observations} with some subtle, yet notable, differences.
+While Illustris, MBII, and Horizon-AGN show good correspondence with observations at $z<0.6$, the comparisons at $z>0.6$ are better for SAM, MBII, TNG100, TNG300 and Horizon-AGN.
 Bridging the gap from \hbox{$z\sim0.7$} to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
@@
 
-\red{These results are based on samples with stellar masses mainly with the range [9.5, 11.5] $M_{\odot}$. Note that
-the} value of stellar masses in both the observations and simulations have significant uncertainty (up to factor of two)\red{.
-For example, the observed \smass\ depends on the assumption of initial mass function and star formation history while the value of \smass\ in the simulation depends on how it's defined (i.e., total mass or within 30~kpc aperture), and other subgrid models such as supernova feedback, AGN feedback.} In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematic effect.
+These results are based on samples with stellar masses mainly with the range [9.5, 11.5] $M_{\odot}$.
+Note that the value of stellar masses in both the observations and simulations have significant uncertainty (up to factor of two).
+For example, the observed \smass\ depends on the assumption of initial mass function and star formation history while the value of \smass\ in the simulation depends on how it's defined (i.e., total mass or within 30~kpc aperture), and other subgrid models such as supernova feedback, AGN feedback.
+In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematic effect.
 Thus, in this work, we first consider the scatter as a diagnostic criteria to see whether some simulations match the data better than others.

### 2022-05-24 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
For uploading final materials

@@
 %\newcommand{\red}[1]{{#1}}
-\newcommand{\red}[1]{\textcolor{red}{#1}}
-\newcommand{\blue}[1]{\textcolor{blue}{\bf #1}}
+%\newcommand{\red}[1]{\textcolor{red}{#1}}
+%\newcommand{\blue}[1]{\textcolor{black}{\bf #1}}
 
@@
 To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over cosmic time.
-While, an {\it observed} evolution has been found since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15} in which the growth of BHs predates that of the host, other studies\blue{~\citep[e.g.,][]{Schramm2013, Sun2015, 2021ApJ...906..103L}} predict that BHs grow commensurately with galaxies.
+While, an {\it observed} evolution has been found since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15} in which the growth of BHs predates that of the host, other studies~\citep[e.g.,][]{Schramm2013, Sun2015, 2021ApJ...906..103L} predict that BHs grow commensurately with galaxies.
 However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15,Jahnke2009,  Ding2020,Li2021b}.
@@
 Actually, even without any physical mechanisms, statistical convergence from galaxy assembly alone (i.e., dry mergers) could instill the observed correlations~\citep{Peng2007, Jahnke2011, Hirschmann2010}.
-However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ compared to what is observed today~\blue{\citep[e.g.,][]{Ginat2016, 2020MNRAS.498.5652K}}.
+However, as expected from the central limit theorem, a higher dispersion would appear in the scaling relations at high-$z$ compared to what is observed today~\citep[e.g.,][]{Ginat2016, 2020MNRAS.498.5652K}.
 
 Numerical simulations provide an opportunity to further understand the connection between BHs and their host galaxies.
-For example, a comparison of scaling relations has been made using state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and observational measurements at  $0.3<z<1$ \citep[e.g., ][]{DeG++15}, which show a positive evolution (i.e., the \blue{mass growth of the BH predates} that of its host).
+For example, a comparison of scaling relations has been made using state-of-the-art cosmological hydrodynamical simulation of structure formation ({\tt MassiveBlackII}) and observational measurements at  $0.3<z<1$ \citep[e.g., ][]{DeG++15}, which show a positive evolution (i.e., the mass growth of the BH predates that of its host).
 Further efforts are using large-volume simulations to investigate the scaling relations and find good agreement with the local relation with redshift evolution,
@@
 With accurate PSF models in five optical bands {\it grizy}, two-dimensional quasar-host decompositions have been performed \citep[][]{Li2021a} to obtain the flux and color of each quasar's host galaxy.
-The \blue{state-of-the-art} image modeling software {\tt lenstronomy} \citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task.
+The state-of-the-art image modeling software {\tt lenstronomy} \citep{Birrer2015, Birrer2018, Birrer2021} is adopted to perform the modeling task.
 This approach is first developed by~\citet{Ding2020} and used to decompose the near-infrared emission of the HST sample (see next section).
@@
 
-To model supermassive BH, the initial seed with mass $5\times 10^{5}~M_{\odot}/h$ \blue{is} inserted into halos of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$.
+To model supermassive BH, the initial seed with mass $5\times 10^{5}~M_{\odot}/h$ is inserted into halos of mass $\gtrsim 5\times 10^{10}~M_{\odot}/h$.
 Once seeded, BH growth via gas accretion is assigned at a rate of $\dot{M}_{BH}={4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ where $\rho$ and $c_s$ are the density and sound speed of the interstellar medium (ISM) gas at cold phase; $v_{BH}$ is the relative velocity between the BH and its surrounding gas.
@@
 For the simulated data, both the initial sample and that with observational effects applied (i.e., noise correction, and selection) are shown.
-Note that offsets can occur for the simulated \blue{samples} in three cases: an inherent offset, an offset due to selection, and offsets from added noise and selection.
+Note that offsets can occur for the simulated samples in three cases: an inherent offset, an offset due to selection, and offsets from added noise and selection.
 For the first, it has been recognized~\citep[e.g.,][Figure 2]{Habouzit2021}, and seen in our Figure~\ref{fig:comparsion}, that the  offset values vary over a range of stellar mass, and thus the mean and standard derivation do not represent the entire mass distribution.
@@
 The TNG100 and TNG300 appear to present similar results (see discussion section).
-\blue{Note that different sample adopt either a Chabrier or a Salpeter IMF for calculating the stellar mass, thus the \smass\ value for the observation and the local relation can be slightly different in each vertical plane.}
+We note that different samples adopt either a Chabrier or a Salpeter IMF for calculating the stellar mass thus the \smass\ values for the observations and the local relation are shifted appropriately.
 }
@@
 In this study, there are a few issues that may bias the results thus need to be considered.
-First, the mass offsets are compared to the \blue{observed} relation derived in the local Universe (D20).
+First, the mass offsets are compared to the observed relation derived in the local Universe (D20).
 In fact, the different simulations could have different mean relations at $z=0$~\citep[e.g.,][]{Habouzit2021}.
 As a result, the interpretation of the BH mass offsets of the simulations with redshift, anchored to the D20 local scaling relation, can be different if using the local relation of each individual simulation.
-In addition, the stellar mass of the Horizon-AGN sample is the total mass while that for the other hydrodynamic simulations are determined within a 3D 30 kpc spherical aperture\footnote{\blue{In fact, we also checked to use total stellar mass for Illustris, TNG100, and TNG300 for the comparison, the results appear to be consistent with the ones when using the 30 kpc stellar mass.}}.
-Therefore, in Figure~\ref{fig:offsets_vz_shiftz03}, we manually \blue{recalibrate the offset of all simulations so that their mean offset value  at $z=0.3$ are at the same level with the observations}.
+In addition, the stellar mass of the Horizon-AGN sample is the total mass while that for the other hydrodynamic simulations are determined within a 3D 30 kpc spherical aperture\footnote{We checked the use of total stellar mass for Illustris, TNG100, and TNG300 in these comparisons; the results are consistent with those based on a 30 kpc region.}.
+Therefore, in Figure~\ref{fig:offsets_vz_shiftz03}, we manually recalibrate the offsets of all simulations so that their mean value at $z=0.3$ is fixed to match that of the observations.
 This enables the evolutionary trend in the offsets of each sample to be clearer.
@@
 Despite that the observed samples are not volume-limited and the simulated samples are not volume-matched, fortunately, the volume of all the simulations appear to be sufficient, i.e., all simulations have a similar amount (or more) of data points to compare with the observations (see Figure~\ref{fig:comparsion}).
-Also, similar results are found with the smaller and larger volumes simulations, e.g., TNG100 and TNG300, which reflect the fact that the simulation volume reaches a sufficient size to be effective for \blue{the comparisons in the observational plane.
-Even though, the intrinsic scatters of TNG100 and TNG300 (before the noise/selection) can be still different.}\footnote{\blue{In particular, our study is made at \smass$>10~M_{\odot}$, while intrinsically, the subgrid models of the TNG simulation can change a lot at low redshift, especially for \smass$<10.5~M_{\odot}$ (see green controus in Figure 3 for $z<0.7$ sample).
-}}
+Also, similar results are found with the smaller and larger volumes simulations, e.g., TNG100 and TNG300, which reflect the fact that the simulation volume reaches a sufficient size to be effective for the comparisons in the observational plane.
+Even though, the intrinsic scatter of TNG100 and TNG300 (before the noise/selection) can differ.\footnote{We note that
+%Our study is primarily at \smass$>10~M_{\odot}$, while 
+the subgrid models of the TNG simulation can change the intrinsic distributions at low redshift, especially for log~\smass$<10.5~M_{\odot}$ (see green contours in Figure 3 for $z<0.7$ sample). }
 
@@
 SAM &  1.99e-09 & $<$1e-10  & $<$1e-10  & 7.46e-03  \\
-MBII & 7.51e-01 & \multicolumn{2}{c}{$<$3.93e-01  [$z=0.6$]}  & 2.22e-05  \\
+MBII & 7.51e-01 & \multicolumn{2}{c}{3.93e-01  [$z=0.6$]}  & 2.22e-05  \\
 Illustris & 5.01e-01 & 8.38e-01  & 5.98e-01  & 3.90e-05  \\

### 2022-07-25 projects/2020_HSC_to_numerical_simulation/manuscript/manuscript.tex
final edit for post arxiv based on proof

@@
 We carry out a comparative analysis of the relation between the mass of supermassive black holes (BHs) and the stellar mass of their host galaxies at $0.2<z<1.7$ using well-matched observations and multiple state-of-the-art simulations (e.g., Massive Black II, Horizon-AGN, Illustris, TNG and a semi-analytic model).
-The observed sample consists of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line AGNs ($1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter.
+The observed sample consists of 646 uniformly-selected SDSS quasars ($0.2 < z < 0.8$) and 32 broad-line active galactic nuclei (AGNs; $1.2<z<1.7$) with imaging from Hyper Suprime-Cam (HSC) for the former and Hubble Space Telescope (HST) for the latter.
 We first add realistic observational uncertainties to the simulation data and then construct a simulated sample in the same manner as the observations.
@@
 Regarding the mean relation, Horizon-AGN and TNG are in closest agreement with the observations at low and high redshift ($z\sim$ 0.2 and 1.5, respectively) while the other simulations show subtle differences within the uncertainties.
-For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and closer to the observations after adopting a new feedback model which considers the geometry of the AGN outflow.
-The consistency in the dispersion with redshift in our analysis supports the importance of both quasar and radio mode feedback prescriptions in the simulations.
-Finally, we highlight the importance of increasing the sensitivity, e.g., JWST, thereby pushing to lower masses and minimizing biases due to selection effects.
+For insight into the physics involved, the scatter of the scaling relation, seen in the SAM, is reduced by a factor of two and closer to the observations after adopting a new feedback model that considers the geometry of the AGN outflow.
+The consistency in the dispersion with redshift in our analysis supports the importance of both quasar- and radio-mode feedback prescriptions in the simulations.
+Finally, we highlight the importance of increasing the sensitivity (e.g., using the James Webb Space Telescope), thereby pushing to lower masses and minimizing biases due to selection effects.
 \end{abstract}
@@
 \section{Introduction} \label{sec:intro}
-The close correlations between the mass of supermassive black holes (\mbh) and the properties of their host galaxies (e.g., stellar mass, \smass) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
-To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGN) over a range of redshifts with the intention to determine how and when the correlation emerges and evolves over cosmic time.
-While, an {\it observed} evolution has been found since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15} in which the growth of BHs predates that of the host, other studies~\citep[e.g.,][]{Schramm2013, Sun2015, 2021ApJ...906..103L} predict that BHs grow commensurately with galaxies.
+The close correlations between the mass of supermassive black holes (BHs), \mbh, and the properties of their host galaxies (e.g., stellar mass, \smass) indicate a physical coupling during their joint evolution~\citep{Mag++98, F+M00, M+H03, H+R04, Gul++09}.
+To understand the nature of this connection, considerable efforts have been focused on measuring such correlations using broad-line active galactic nucleus (AGNs) over a range of redshifts, with the intention to determine how and when the correlation emerges and evolves over cosmic time.
+While an {\it observed} evolution has been found since redshift $z\sim2$ in galaxies with stellar mass \smass\ $\gtrsim 10^{10}M_{\odot}$ \citep[e.g.,][]{Tre++04, Peng2006a,Tre++07,Woo++08,Bennert11,Park15} in which the growth of BHs predates that of the host, other studies~\citep[e.g.,][]{Schramm2013, Sun2015, 2021ApJ...906..103L} predict that BHs grow commensurately with galaxies.
 However, to understand the significance {\it intrinsic} evolution, it is necessary to take into account systematic uncertainties and the selection effects~\citep{Tre++07, Lauer2007, Schulze2014, Park15,Jahnke2009,  Ding2020,Li2021b}.
@@
 
-In this study, we extend our previous work by adding recent measurements of hundreds of SDSS quasars at $0.2<z<0.8$ based on wide and deep HSC imaging from the Strategic Subaru Program, and comparing the observational measurements with that from simulations.
-Furthermore, we extend the simulated quasar populations by including MBII, SAM, Illustris, TNG100, TNG300 and Horizon-AGN.
+In this study, we extend our previous work by adding recent measurements of hundreds of Sloan Digital Sky Survey (SDSS) quasars at $0.2<z<0.8$ based on wide and deep Hyper Suprime-Cam (HSC) imaging from the Strategic Subaru Program, and comparing the observational measurements with that from simulations.
+Furthermore, we extend the simulated quasar populations by including MBII, SAM, Illustris, TNG100, TNG300, and Horizon-AGN.
 This paper is structured as follows.
@@
 A sample of 32 HST-observed AGN systems across the redshift range $1.2<z<1.7$ are selected from three deep-survey fields (COSMOS, (E)-CDFS-S, and SXDS).
-HSC/WFC3 IR camera is used to obtain the high-resolution imaging data (HST program GO-15115, PI: John Silverman) with six position dither pattern and a total exposure time $\sim$2348~s.
+The HST/WFC3 IR camera is used to obtain the high-resolution imaging data (HST program GO-15115, PI: John Silverman) with six position dither pattern and a total exposure time $\sim$2348~s.
 The filters F125W ($1.2<z<1.44$) and F140W ($1.44<z<1.7$) were employed, according to the redshift of each target to bracket the 4000~\AA~break.
@@
 \startdata
-box sizes $(\mathrm{cMpc})^3$  & $142.7^3$ & $(106.5)^3$ & $(111)^3$ & $(302)^3$ & $(142)^3$ \\
-particles  & $2\times1792^3$ & $2\times1820^3$ & $2\times1820^3$ & $2\times2500^3$ & $\sim2\times1024^3$ \\
+Box sizes $(\mathrm{cMpc})^3$  & $142.7^3$ & $(106.5)^3$ & $(111)^3$ & $(302)^3$ & $(142)^3$ \\
+Particles  & $2\times1792^3$ & $2\times1820^3$ & $2\times1820^3$ & $2\times2500^3$ & $\sim2\times1024^3$ \\
 \cline{1-6}
-{\bf mass resolution} \\
- dark matter &$1.57\times10^7$ & $6.26\times10^6$ & $7.5\times10^6$ & $5.9\times10^7$ & $8\times10^7$ \\
- baryonic matter &$3.14\times10^6$ & $1.26\times10^6$ & $1.4\times10^6$ & $1.1\times10^7$ & $2\times10^6$ \\
+{\bf Mass Resolution} \\
+ Dark matter &$1.57\times10^7$ & $6.26\times10^6$ & $7.5\times10^6$ & $5.9\times10^7$ & $8\times10^7$ \\
+ Baryonic matter &$3.14\times10^6$ & $1.26\times10^6$ & $1.4\times10^6$ & $1.1\times10^7$ & $2\times10^6$ \\
 \cline{1-6}
-{\bf AGN feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ radiative efficiency)} \\
+{\bf AGN Feedback} & \multicolumn{2}{c}{(feedback efficiency $\times$ radiative efficiency)} \\
 High acc. mode & 0.05 $\times$ 0.1 & 0.05 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.1 $\times$ 0.2 & 0.15 $\times$ 0.1 \\
@@
 AGN fueling mechanism   & ${4\pi G^2 M_{BH}^2 \rho}/{(c_s^2+v_{BH}^2)^{3/2}}$ & $\alpha \dot{M}_{Bondi}$ & $\dot{M}_{Bondi}$&$\dot{M}_{Bondi}$ & $\alpha\dot{M}_{Bondi}$ \\
-maximum accretion rate & 2 $\times$Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate\\
+Maximum accretion rate & 2 $\times$Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate & Edd. acc. rate\\
 \enddata
@@
 In Table~\ref{tab:sim_sum}, we summarized the key elements for each hydrodynamic simulation being considered.
-We note that each simulation adopts either a  \cite{2003PASP..115..763C} or a \cite{1955ApJ...121..161S} IMF.
-To make self-consistent comparisons, we ensure that the adopted IMF for both the simulations and the observations are consistent.
+We note that each simulation adopts either a  \cite{2003PASP..115..763C} or a \cite{1955ApJ...121..161S} initial mass function (IMF).
+To make self-consistent comparisons, we ensure that the adopted IMFs for both the simulations and the observations are consistent.
 The assumed IMF is needed to obtain the mass-to-light ratio and convert the observed luminosity to stellar mass to perform the comparisons.
-For numerical simulation, the mass is the base material which is IMF independent.
+For numerical simulation, the mass is the base material, which is IMF independent.
 
@@
 Lastly, the radiative feedback mode is implemented by modifying the heating and cooling rates of the gas in the presence of radiation from all surrounding AGN.
-Halos and galaxies are identified similar to that of MBII.
+Halos and galaxies are identified similar to those of MBII.
 As in MBII, a 3D 30~kpc spherical aperture is used to obtained the galaxy stellar mass.
@@
 {\it The Next Generation Illustris Simulations} (IllustrisTNG, hereafter, TNG)~\citep{2018MNRAS.475..676S, Pillepich2018, Naiman2018, Marinacci2018, Nelson2018} are a suite of magnetohydrodynamical simulations of galaxy formation in large cosmological volumes.
-It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modeling, and 3) addressing the identified shortcomings of the previous generation simulations.
+It builds upon the scientific achievements of the Illustris simulation with improvements upon Illustris by 1) extending the mass range of the simulated galaxies and haloes, 2) adopting an improved numerical and astrophysical modeling, and 3) addressing the identified shortcomings of the previous-generation simulations.
 Note that TNG simulations employ a modified version of the Bondi formalism, with $c_s$ explicitly including a B term for these magneto-hydro simulations.
@@
 The AGN feedback occurs in thermal, radio, and radiative modes.
-For high accretion rates, the feedback implementation is the same as Illustris i.e., thermal energy is injected in the surroundings of the accreting BHs.
+For high accretion rates, the feedback implementation is the same as in Illustris i.e., thermal energy is injected in the surroundings of the accreting BHs.
 However, at low accretion rates, the feedback implementation is substantially different from Illustris.
@@
 We identify galaxies applying the AdaptaHOP structure finder \citep{Aubert+04,Tweed+09} to the star particle distribution.
-Galaxies are identified using a local threshold of 178 times the average matter density, with the local density of individual particles calculated using the 20 nearest neighbours.
+Galaxies are identified using a local threshold of 178 times the average matter density, with the local density of individual particles calculated using the 20 nearest neighbors.
 Only galaxies with more than 50 particles are considered.
@@
 \caption{\label{fig:selection}Demonstration of AGN selection using MBII.
-{\it left}: Distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles) for those at redshift $z=0.6$.
+{\it left}: distribution of \mbh\ and Eddington ratio for the full (colored squares) MBII sample and individual objects meeting the observed selection criteria (blue circles) for those at redshift $z=0.6$.
 A matched HSC sample is shown by the orange data points.
-The light green background cloud shows the {\it intrinsic} simulated number density in this parameter space.
+The light-green background cloud shows the {\it intrinsic} simulated number density in this parameter space.
 Note that this is the first step of sample selection.
@@
 We then use the same \smass\ cut to construct the final sample.
-{\it right}: Similar to the panel on the left, this figure presents the impact of selection on the HST sample.
+{\it right}: similar to the left panel, but presenting the impact of selection on the HST sample.
 }
@@
 In each halo, we compute the fraction of gas which cools because of the atomic processes and settles into a disk~\citep{Mo1998}.
-The stars are converted from the gas through three channels: (1) quiescent star formation with long time scales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr;  (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion).
-The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation which returns a fraction of the disk gas into a hot phase.
+The stars are converted from the gas through three channels: (1) quiescent star formation with long timescales: $\sim1$~Gyr; (2) starbursts following galaxy interactions with timescales $\lesssim 100$~Myr;  (3) the loss of angular momentum triggered by the internal disk instabilities causing the gas inflows to the center, resulting in stimulated star formation (as well as BH accretion).
+The stellar feedback is also considered by calculating the energy released by the supernovae associated with the total star formation, which returns a fraction of the disk gas into a hot phase.
 A $\Lambda$CDM power spectrum of perturbations with a total matter density parameter $\Omega_0=0.3$, a baryon density parameter 
@@
 {We assume BH seed $M_{seed}=100\,M_{\odot}$~\citep{Madau2001}  to be initially present in all galaxy progenitors at the initial redshift $z=15$.
-This constitutes an approximate way of rendering the effect of the collapse of PopIII stars.
+This constitutes an approximate way of rendering the effect of the collapse of Population III stars.
 However, the detailed value of $M_{seed}$ has a negligible impact on the final BH masses as long as they remain in the range $M_{seed}=50-500\,M_{\odot}$.
@@
 
-The BH accretion is assumed to follow from the gas instabilities resulting from either galaxy interactions and disk instabilities, and is thus related to star formations channels 2-3: a fraction of the cold gas destabilized during galaxy encounters and through disc instabilities is in fact accreted onto the central BHs (with the remaining fraction fueling star formation through channels 2-3 described above).
-Such fractions and the corresponding timescales for accretion are computed as described in~\citet[][in Section 3]{Menci2014}.
+The BH accretion is assumed to follow from the gas instabilities resulting from either galaxy interactions or disk instabilities, and is thus related to star formation channels 2-3: a fraction of the cold gas destabilized during galaxy encounters and through disk instabilities is in fact accreted onto the central BHs (with the remaining fraction fueling star formation channels 2-3 described above).
+Such fractions and the corresponding timescales for accretion are computed as described in~\citet[][their Section 3]{Menci2014}.
 
@@
 This  moves outward with a lower but still supersonic speed, and sweeps out the surrounding medium.
-However, while in the earlier version of the SAM~\citep{Menci2016} the blast wave is assumed to expand into an isotropically distributed medium, in the new description of AGN feedback~\citep{Menci2019} the full two-dimensional structure of the gas disc and of the expanding blast wave is followed in detail.
-The main physical difference is that in the new model the large density of gas along the plane of the disc causes the blast wave expansion to stall in such a direction, while it expands with large velocities in the vertical direction.
+However, while in the earlier version of the SAM~\citep{Menci2016} the blast wave is assumed to expand into an isotropically distributed medium, in the new description of AGN feedback~\citep{Menci2019} the full two-dimensional structure of the gas disk and of the expanding blast wave is followed in detail.
+The main physical difference is that in the new model the large density of gas along the plane of the disk causes the blast wave expansion to stall in such a direction, while it expands with large velocities in the vertical direction.
 The resulting strong dependence of the total (integrated over directions) outflow rate on the AGN luminosity $L_{AGN}$ and on the gas content of the galaxy $M_{gas}$ is shown in Figure~\ref{fig:SAM}.
@@
 We first inject random noise to the simulated catalog to mimic the scatter caused by measurement error.
-As mentioned above, \smass\ and \mbh\ for HSC and HST samples are measured with a similar approach; thus their uncertainty levels are expected to be equivalent.
+As mentioned above, \smass\ and \mbh\ for HSC and HST samples are measured with a similar approach; thus, their uncertainty levels are expected to be equivalent.
 We assume the following measurement uncertainties that are added as random noise: $\Delta$\mbh$ = 0.4~$dex, $\Delta$\smass$ = 0.2~$dex, and $\Delta L_{\rm bol} = 0.03~$dex.
@@
 We then apply restrictions on the noise-injected simulation to mimic selection effects as present in the observational data.
-Since the HSC and HST samples have their own selection function, we apply different selection criteria to the simulation as follows:
+Since the HSC and HST samples have their own selection function, we apply different selection criteria to the simulation as follows.
 
@@
 We use MBII to demonstrate the importance of matching the sample selection (Figure~\ref{fig:selection}--{\it left}).
-(2) The $i$-band magnitude of the AGN are bright (see Section~\ref{sec:hsc}).
+(2) The $i$-band magnitudes of the AGN are bright (see Section~\ref{sec:hsc}).
 The specific selection is carried out as follows: a value of AGN $i$-band magnitude is chosen to make the sample selection such that the $L_{\rm bol}$ distribution is similar to the observations (see Section~\ref{sec:dis} for details).
 Since the simulations do not provide the observed AGN magnitude, we adopt a simulated rest-frame magnitude or L$_{\rm 5100}$ and assume the quasar continuum as a single power-law with an index of $\alpha_\nu=-0.44$~\citep{2001AJ....122..549V} to calculate the observed $i$-band magnitude.
- 3)~Following the HSC selection, we require the \smass\ value to be above a certain level (according to their redshift) to assure an accurate measurement.
-Finally, the HSC sample is split into three redshift bins for making comparison which are $0.2<z<0.4$, $0.4<z<0.6$, and $0.6<z<0.8$.
+ (3)~Following the HSC selection, we require the \smass\ value to be above a certain level (according to their redshift) to assure an accurate measurement.
+Finally, the HSC sample is split into three redshift bins for making comparisons, which are $0.2<z<0.4$, $0.4<z<0.6$, and $0.6<z<0.8$.
 
-Comparing with the HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example).
+Comparing with the HST sample: Simulated AGN systems are selected only when they match the  \mbh-$L_{\rm bol}$ targeting window, which is the same as the observational selection (see Figure~\ref{fig:selection}--{\it right} using MBII as an example).
 Note that the selection of the HST sample has a hard cut on the \mbh\ values (i.e., log(\mbh) between [7.7, 8.6] $M_{\odot}$).
@@
 \section{Results} \label{sec:result}
-For comparison, the local scaling relation provided by  D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF thus a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion with redshift.
+For comparison, the local scaling relation provided by  D20 (e.g., \mbh$=0.98$\smass$-2.56$, Chabrier IMF\footnote{Since different simulations adopt either a Chabrier or a Salpeter IMF, we use the local relation and \smass\ of the observational data that are based on the same IMF; thus, a comparison between the observations and simulations are self-consistent.}) is adopted as the fiducial relation to assess relative offsets and differences in dispersion with redshift.
 This local (\mbh-\smass) relation is derived by fitting measurements for 55 local galaxies as given in~\citet{Bennert++2011} and \citet{H+R04}.
@@
 In Figure~\ref{fig:comparsion}, we present the mass scaling relation \mbh--\smass\ for both the observations and simulations for direct comparison.
-For the simulated data, both the initial sample and that with observational effects applied (i.e., noise correction, and selection) are shown.
+For the simulated data, both the initial sample and that with observational effects applied (i.e., noise correction and selection) are shown.
 Note that offsets can occur for the simulated samples in three cases: an inherent offset, an offset due to selection, and offsets from added noise and selection.
 For the first, it has been recognized~\citep[e.g.,][Figure 2]{Habouzit2021}, and seen in our Figure~\ref{fig:comparsion}, that the  offset values vary over a range of stellar mass, and thus the mean and standard derivation do not represent the entire mass distribution.
-In this work, we focus on the latter two offset distributions, i.e., considering selection effects with and without noise correction.
+In this work, we focus on the last two offset distributions, i.e., considering selection effects with and without noise correction.
 To aid in visualization of the differences among the various simulations, compared to the observed sample, we show the distribution of offsets (in terms of the $\Delta{\rm log}$\mbh) as histograms in Figure~\ref{fig:offsets}.
@@
 \caption{\label{fig:comparsion} 
-Black hole mass versus stellar mass for both the observational (small orange circles) and simulated (small colored circles) samples.
-Each row pertains to a particular simulation as labelled.
+BH mass vs.
+stellar mass for both the observational (small orange circles) and simulated (small colored circles) samples.
+Each row pertains to a particular simulation as labeled.
 The panels, from left to right, show different redshift bins.
@@
 The TNG100 and TNG300 appear to present similar results (see discussion section).
-We note that different samples adopt either a Chabrier or a Salpeter IMF for calculating the stellar mass thus the \smass\ values for the observations and the local relation are shifted appropriately.
+We note that different samples adopt either a Chabrier or a Salpeter IMF for calculating the stellar mass; thus, the \smass\ values for the observations and the local relation are shifted appropriately.
 }
@@
 \subsection{Global offsets}\label{subsec:offset}
-We examine the offsets to understand whether the simulations deviate or not from the {\it observed} scaling relation with particular attention to changes with redshift.
+We examine the offsets to understand whether the simulations deviate or not from the {\it observed} scaling relation, with particular attention to changes with redshift.
 Considering the values given in Table~\ref{tab:sum} and shown in Figure~\ref{fig:offsets_vz}, over the lower redshift range $z<0.6$, Illustris and Horizon-AGN predict {\it observed} \mbh\ offsets consistent with the observation data (at a level of $\lesssim0.1$~dex).
 At higher redshift $0.6<z<1.5$, the simulations SAM, TNG100, TNG300 and Horizon-AGN follow the {\it observed} evolution.
-These results are consistent with the Kolmogorov-Smirnov (KS) test performed using the offset distributions between each simulated sample and the observed sample --- the p-values are given in Table~\ref{tab:pvalue} showing that Horizon-AGN and Illustris have a good statistical match to the scaling relation at $z<0.6$ (i.e., p-value $> 0.1$), while the TNG100, TNG300 and Horizon-AGN simulation do well at $z>0.6$.
-Except for MBII and Horizon-AGN, we also see that the other simulations have mass offsets that are decreasing from $z=0.2$ to $z=0.6$, while the observations offsets increasing with redshift up to $z\sim1.5$.
+These results are consistent with the Kolmogorov-Smirnov (KS) test performed using the offset distributions between each simulated sample and the observed sample --- the $p$-values are given in Table~\ref{tab:pvalue} showing that Horizon-AGN and Illustris have a good statistical match to the scaling relation at $z<0.6$ (i.e., $p$-value $> 0.1$), while the TNG100, TNG300 and Horizon-AGN simulation do well at $z>0.6$.
+Except for MBII and Horizon-AGN, we also see that the other simulations have mass offsets that are decreasing from $z=0.2$ to $z=0.6$, while the observation offsets increase with redshift up to $z\sim1.5$.
 However, this inconsistency is well below the $1\sigma$ scatter level.
-Overall, we find that the mass correlation between supermassive BHs and their host galaxies are generally consistent between observations and simulations with some subtle differences which are not at the level of concern for this present study.
+Overall, we find that the mass correlation between supermassive BHs and their host galaxies is generally consistent between observations and simulations, with some subtle differences that are not at the level of concern for this present study.
 
@@
 In Figure~\ref{fig:deltaMM}, we investigate how the offset values are correlated with stellar mass.
-Here, we focus on the sample at $z\sim0.7$.
+Here we focus on the sample at $z\sim0.7$.
 The other redshift bins at $z<1$, where there is a large observation sample from HSC, show similar trends.
@@
 First, considering the observed quasar sample (same in each panel), there is a trend for which BHs have masses further offset from their stellar mass with decreasing stellar mass.
-This trend is not seen in any of the simulations after noise and selection effects have been applied.
+This trend is not seen in any of the simulations after noise, and selection effects have been applied.
 Given the level of uncertainties in the mean offsets of the observed sample, we do not try to interpret this trend any further in this study.
 
-Interestingly, we notice that MBII and Illustris have BHs intrinsically under-massive relative to their galaxies at the lower masses that reach the D20 local scaling relation at higher masses.
+Interestingly, we notice that MBII and Illustris have BHs intrinsically undermassive relative to their galaxies at the lower masses that reach the D20 local scaling relation at higher masses.
 In contrast, TNG and Horizon-AGN have BHs slightly elevated from D20 local relation at most masses.
-These differences between simulations present two different scenarios, either one where the BHs come later or co-evolution with the two growing in tandem.
+These differences between simulations present two different scenarios, either one where the BHs come later, or coevolution with the two growing in tandem.
 Considering the former scenario, Illustris shows the strongest trend with stellar mass.
-In fact, after noise and selection is applied, the simulated sample exhibits very small offsets which agree remarkably well with the observed data.
+In fact, after noise and selection are applied, the simulated sample exhibits very small offsets that agree remarkably well with the observed data.
 If the BHs are accurately characterized in the simulation, one interpretation is that the observations, including our HSC AGN sample, do not inform us of the true \mbh\ offsets as a function of \smass.
 This result underscores the importance of taking into account errors and selection --- without accounting for those, one could erroneously interpret an apparent trend as evolution in the opposite sense as the true one.
-The most direct way to circumvent these issues is to probe lower masses (\smass\  $<10^{10}M_{\odot}$) using a more sensitive instrument, such as JWST~\citep{Habouzit2022} across this redshift range \citep[see also][]{2011MNRAS.417.2085V}.
+The most direct way to circumvent these issues is to probe lower masses (\smass\  $<10^{10}M_{\odot}$) using a more sensitive instrument, such as the James Webb Space Telescope~\citep{Habouzit2022}, across this redshift range \citep[see also][]{2011MNRAS.417.2085V}.
 
@@
 \tablehead{
-\colhead{Sample} &  \multicolumn{3}{c}{HSC comparison} & \colhead{HST comparison} \\
+\colhead{Sample} &  \multicolumn{3}{c}{HSC Comparison} & \colhead{HST Comparison} \\
 \cline{2-4} 
@@
 A positive offset means the \mbh\ value predicted by the simulation is higher than the local relationship measurement at fixed \smass\ value.
-The last column shows the corresponding IMF that adopted to the local anchor to make a fair comparison with the observation.
+The last column shows the corresponding IMF that was adopted to the local anchor to make a fair comparison with the observation.
 Note that for the observational data, the relative differences between local and high-$z$ measurements are not affected by the IMF assumptions.
 For the MBII sample, the simulation does not produce the sample at $z=0.5$ or $z=0.7$, but rather at $z=0.6$.
-We use Monte Carlo approach with 500 realizations to infer the uncertainties of the values in the table, finding that the uncertainties are within $\pm 0.03$.
+We use a Monte Carlo approach with 500 realizations to infer the uncertainties of the values in the table, finding that the uncertainties are within $\pm 0.03$.
 }
@@
 \section{Discussion} \label{sec:dis}
-In this study, there are a few issues that may bias the results thus need to be considered.
-First, the mass offsets are compared to the observed relation derived in the local Universe (D20).
+In this study, there are a few issues that may bias the results and thus need to be considered.
+First, the mass offsets are compared to the observed relation derived in the local universe (D20).
 In fact, the different simulations could have different mean relations at $z=0$~\citep[e.g.,][]{Habouzit2021}.
 As a result, the interpretation of the BH mass offsets of the simulations with redshift, anchored to the D20 local scaling relation, can be different if using the local relation of each individual simulation.
-In addition, the stellar mass of the Horizon-AGN sample is the total mass while that for the other hydrodynamic simulations are determined within a 3D 30 kpc spherical aperture\footnote{We checked the use of total stellar mass for Illustris, TNG100, and TNG300 in these comparisons; the results are consistent with those based on a 30 kpc region.}.
+In addition, the stellar mass of the Horizon-AGN sample is the total mass, while that for the other hydrodynamic simulations is determined within a 3D 30 kpc spherical aperture\footnote{We checked the use of total stellar mass for Illustris, TNG100, and TNG300 in these comparisons; the results are consistent with those based on a 30 kpc region.}.
 Therefore, in Figure~\ref{fig:offsets_vz_shiftz03}, we manually recalibrate the offsets of all simulations so that their mean value at $z=0.3$ is fixed to match that of the observations.
 This enables the evolutionary trend in the offsets of each sample to be clearer.
-In general, the updated results show that the evolution of the simulations are consistent with our interpretations in Section~\ref{subsec:offset}.
+In general, the updated results show that the evolution of the simulations is consistent with our interpretations in Section~\ref{subsec:offset}.
 This result can be expected since most of the simulations have demonstrated a good match to the observations at redshift $z=0.3$.
@@
 The final sample sizes, used to compare with observation, are not set by design.
-Despite that the observed samples are not volume-limited and the simulated samples are not volume-matched, fortunately, the volume of all the simulations appear to be sufficient, i.e., all simulations have a similar amount (or more) of data points to compare with the observations (see Figure~\ref{fig:comparsion}).
-Also, similar results are found with the smaller and larger volumes simulations, e.g., TNG100 and TNG300, which reflect the fact that the simulation volume reaches a sufficient size to be effective for the comparisons in the observational plane.
+Despite that the observed samples are not volume limited and the simulated samples are not volume matched, fortunately, the volumes of all the simulations appear to be sufficient, i.e., all simulations have a similar number (or more) of data points to compare with the observations (see Figure~\ref{fig:comparsion}).
+In addition, similar results are found with the smaller- and larger-volumes simulations, e.g., TNG100 and TNG300, which reflect the fact that the simulation volume reaches a sufficient size to be effective for the comparisons in the observational plane.
 Even though, the intrinsic scatter of TNG100 and TNG300 (before the noise/selection) can differ.\footnote{We note that
 %Our study is primarily at \smass$>10~M_{\odot}$, while 
-the subgrid models of the TNG simulation can change the intrinsic distributions at low redshift, especially for log~\smass$<10.5~M_{\odot}$ (see green contours in Figure 3 for $z<0.7$ sample). }
+the subgrid models of the TNG simulation can change the intrinsic distributions at low redshift, especially for log~\smass$<10.5~M_{\odot}$ (see green contours in Figure 3 for the $z<0.7$ sample). }
 
-To avoid any possible bias raised by sample mismatch, we designed our selection (Section~\ref{subsec:add_obs_eff}) so that the distribution of $L_{\rm bol}$ and \mbh\ are similar.
+To avoid any possible bias raised by sample mismatch, we designed our selection (Section~\ref{subsec:add_obs_eff}) so that the distributions of $L_{\rm bol}$ and \mbh\ are similar.
 We also assure that the \smass\ spans similar ranges.
@@
 Mass comparisons using different bolometric luminosity selection.
-{\it left:}~$L_{\rm bol}$ distribution of our simulated samples at $z=0.5$ tailored to match with the observations.
-{\it middle:} Using a different magnitude thresholds to select the simulated samples to force the distribution of the simulation to be different from the observation.
-{\it right:} Offset distributions using these two selections with the dashed line being the result for a mismatched luminosity distribution).
+{\it Left:}~$L_{\rm bol}$ distribution of our simulated samples at $z=0.5$ tailored to match with the observations.
+{\it Middle:} using a different magnitude thresholds to select the simulated samples to force the distribution of the simulation to be different from the observation.
+{\it Right:} offset distributions using these two selections with the dashed line being the result for a mismatched luminosity distribution.
 As shown, the different selections have minimal effect on the offset distributions.
@@
 In the literature~\citep{Weinberger2018, Habouzit2021}, it has been noted that the mass correlations predicted by TNG300 and TNG100 are not identical.
-For example, TNG300 appares to have different scatter in \mbh\ at fixed \smass\ to TNG100 at \smass $>10^{10}M_{\odot}$.
-Also, BH growth is more efficient in TNG100 thus causing the BH mass function to have higher normalization at the low mass end.
+For example, TNG300 appears to have different scatter in \mbh\ at fixed \smass\ from TNG100 at \smass $>10^{10}M_{\odot}$.
+In addition, BH growth is more efficient in TNG100, thus causing the BH mass function to have higher normalization at the low-mass end.
 In our work, the differences between TNG100 and TNG300 also exist.
-However, the difference are milder after selection effects and random noise injection have been applied to the samples.
+However, the differences are milder after selection effects and random noise injection have been applied to the samples.
 
 We considered all known observational effects, including sample selection and random noise injection, and applied these to the data products from the simulations in order to directly compare with observations.
-Our result shows that the scatter between the observations and simulations are very similar.
+Our result shows that the scatters between the observations and simulations are very similar.
 Considering that the observational and simulated samples are matched to the best of our ability, their intrinsic properties are also similar.
 However, there may be limitations in our comparisons that may impact the results.
-For instance, there may be unknown observational effects that haven't been properly applied to the simulations.
+For instance, there may be unknown observational effects that have not been properly applied to the simulations.
 Even so, state-of-the-art simulations likely do not capture all the physical aspects that impact the scatter.
-For example, the spin of BHs is not modeled in the simulation which could change the scatter since the spin affects both the accretion rate and the energy that can be released through AGN feedback \citep{Dubois2014, 2019MNRAS.490.4133B, Habouzit2021} at some level.
+For example, the spin of BHs is not modeled in the simulation, which could change the scatter since the spin affects both the accretion rate and the energy that can be released through AGN feedback \citep{Dubois2014, 2019MNRAS.490.4133B, Habouzit2021} at some level.
 Even though the spin effect is still not well known and such a study is beyond the scope of this paper, a future effort may be warranted when the simulations incorporate spin.
@@
 The observational data are composed of 626 quasars at $0.2 < z < 0.8$ imaged by HSC and 32 X-ray-selected quasars at $1.2 < z < 1.7$ imaged by HST.
-The simulations include a semi-analytic model (SAM) and five hydrodynamic simulations, i.e., MBII, Illustris, TNG100, TNG300 and Horizon-AGN.
+The simulations include an SAM and five hydrodynamic simulations, i.e., MBII, Illustris, TNG100, TNG300, and Horizon-AGN.
 We carried out the comparisons in the observed parameter space to account for uncertainties and selection effects.
-To achieve this, we first injected random errors with the same observational uncertainty to the simulation, and then adopted the same selection condition to the simulated data (see Figure~\ref{fig:selection}).
+To achieve this, we first injected random errors with the same observational uncertainty into the simulation and then adopted the same selection condition for the simulated data (see Figure~\ref{fig:selection}).
 Finally, we adopted the scaling relation from the local universe as our reference and performed comparisons using the scatter of the measurements and their central offset to the D20 local scaling relation.
@@
 \item{}To understand how much the {\it observed} scatter is dominated by random observational error,
-we re-run the estimation without injecting noise to the simulations.
-The obtained scatter for both $z<1$ and $z>1$ are at a similar level (i.e.,  $\sim$0.15$-$0.2 dex, see Table~\ref{tab:sum}), indicating that observational errors dominate the scatter.
+we rerun the estimation without injecting noise into the simulations.
+The obtained scatters for both $z<1$ and $z>1$ are at a similar level (i.e.,  $\sim$0.15$-$0.2 dex, see Table~\ref{tab:sum}), indicating that observational errors dominate the scatter.
 
 \item{} Regarding the offsets of the scaling relation from the local one ($\Delta$\mbh\ at a given \smass; D20), {\it all simulations generally match the observations} with some subtle, yet notable, differences.
-While Illustris, MBII, and Horizon-AGN show good correspondence with observations at $z<0.6$, the comparisons at $z>0.6$ are better for SAM, MBII, TNG100, TNG300 and Horizon-AGN.
-Bridging the gap from \hbox{$z\sim0.7$} to $z\sim1.5$, TNG100, TNG300 and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
+While Illustris, MBII, and Horizon-AGN show good correspondence with observations at $z<0.6$, the comparisons at $z>0.6$ are better for SAM, MBII, TNG100, TNG300, and Horizon-AGN.
+Bridging the gap from \hbox{$z\sim0.7$} to $z\sim1.5$, TNG100, TNG300, and Horizon-AGN simulations match well the observed evolution of the scaling relation, i.e., the offsets are larger at higher redshift as shown in Figure~\ref{fig:offsets_vz} and Table~\ref{tab:sum}.
 Four out of six of the simulations have a decreasing mass offset from $z=0.2$ to $z=0.6$ while the observational mass offset increases with redshift; however, this is well below the observed scatter.
@@
 These results are based on samples with stellar masses mainly with the range [9.5, 11.5] $M_{\odot}$.
-Note that the value of stellar masses in both the observations and simulations have significant uncertainty (up to factor of two).
-For example, the observed \smass\ depends on the assumption of initial mass function and star formation history while the value of \smass\ in the simulation depends on how it's defined (i.e., total mass or within 30~kpc aperture), and other subgrid models such as supernova feedback, AGN feedback.
+Note that the values of stellar masses in both the observations and simulations have significant uncertainty (up to a factor of two).
+For example, the observed \smass\ depends on the assumption of initial mass function and star formation history, while the value of \smass\ in the simulation depends on how it is defined (i.e., total mass or within 30~kpc aperture), and other subgrid models such as SN feedback and AGN feedback.
 In contrast, the scatter around the mean correlation is a relative quantity, which is less affected by such systematic effect.
-Thus, in this work, we first consider the scatter as a diagnostic criteria to see whether some simulations match the data better than others.
-Taking (1) and (2), our results suggest that the tightness of the scaling relations have been formed since redshift 1.7, which is in contrast with the scenario of the central limit theorem~\citep{Peng2007, Jahnke2011, Hirschmann2010} that the scaling relation is a consequence of a stochastic cloud in the early universe with subsequent random mergers thereafter.
-In this stochastic scenario we expect the scatter of the scaling relations to increase towards higher redshift.
-In fact, the scatter level in the simulation without adding random noise is consistent with the {\it intrinsic} scatter estimations reported in~\citet{Ding2020,Li2021b} (i.e., $\lesssim0.35$~dex).
+Thus, in this work we first consider the scatter as a diagnostic criterion to see whether some simulations match the data better than others.
+Taking (1) and (2), our results suggest that the tightness of the scaling relations has been formed since redshift 1.7, which is in contrast with the scenario of the central limit theorem~\citep{Peng2007, Jahnke2011, Hirschmann2010} that the scaling relation is a consequence of a stochastic cloud in the early universe with subsequent random mergers thereafter.
+In this stochastic scenario we expect the scatter of the scaling relations to increase toward higher redshift.
+In fact, the scatter level in the simulation without adding random noise is consistent with the {\it intrinsic} scatter estimations reported in~\citet{Ding2020, Li2021b} (i.e., $\lesssim0.35$~dex).
 This level is also not larger than the typical scatter of the local relations reported in the literature~\citep{Kormendy13, Gul++09, Reines2015}.
@@
 \citet{Ding2020b} compared the scaling relations obtained with the same HST sample and the SAM simulation but with a different, isotropic, AGN feedback model, and found a larger scatter ($\sim0.7$~dex) with respect to the present SAM version ($\sim0.36$~dex).
-We ascribed the change to the following reasons: in the new 2D model for feedback, the wave expansions stalls along the direction of the disc, and the radius where the expansion stops depends strongly on both the gas density of the disk and the AGN luminosity.
-This means that the opening angle (and hence the fraction of expelled gas) is larger when the gas density is small (because of the lower energy that has to be spent to push the gas outwards) and when the AGN luminosity is large (because of the larger energy available to push the blast wave outwards).
+We ascribed the change to the following reasons: in the new 2D model for feedback, the wave expansions stalls along the direction of the disk, and the radius where the expansion stops depends strongly on both the gas density of the disk and the AGN luminosity.
+This means that the opening angle (and hence the fraction of expelled gas) is larger when the gas density is small (because of the lower energy that has to be spent to push the gas outward) and when the AGN luminosity is large (because of the larger energy available to push the blast wave outward).
 These dependencies are summarized in Figure~\ref{fig:SAM}.
@@
 (for given $M_{\rm gas}$) inhibits the BH growth in all the host galaxies that are outliers with respect to the average relation between $M_{\rm gas}$ and $L_{\rm AGN}$. 
-This results into a smaller scatter.
+This results in a smaller scatter.
 
 In theoretical models, AGN feedback is often assumed to consist of two distinct modes:
-a quasar-heating mode where the BH accretion rates are comparable to the Eddington rate and a radio-jet mode occurring at low accretion rates (see, e.g., Section~\ref{subsec:Horizon}).
-In high redshift universe, the cold material in early universe leads to the vigorous accretion to the supermassive BH which drives the high accretion rates, and thus the quasar mode dominates the feedback.
-At low redshift, the star formation and feedback ejection reduce the cold material leading to a lower accretion rate and a radio-mode-dominating feedback~\citep[e.g.][]{2012MNRAS.420.2662D,2016MNRAS.460.2979V,2018MNRAS.479.4056W}.
+a quasar-heating mode where the BH accretion rates are comparable to the Eddington rate, and a radio-jet mode occurring at low accretion rates (see, e.g., Section~\ref{subsec:Horizon}).
+In high-redshift universe, the cold material in the early universe leads to the vigorous accretion to the supermassive BH, which drives the high accretion rates, and thus the quasar mode dominates the feedback.
+At low redshift, the star formation and feedback ejection reduce the cold material, leading to a lower accretion rate and a radio-mode-dominating feedback~\citep[e.g.][]{2012MNRAS.420.2662D,2016MNRAS.460.2979V,2018MNRAS.479.4056W}.
 Our comparison result shows that the level of intrinsic scatter in the scaling relation at redshifts up to 1.7 is consistent with low redshift (see Table~\ref{tab:sum}), which reveals the fact that at high redshift the AGN feedback described by the quasar mode may be responsible at some level for the tight correlation between supermassive BH and its host galaxy.
 In Figure~\ref{fig:fedd}, we demonstrate that essentially all of the quasars in Horizon-AGN that match the observed samples are at high Eddington rates.
-After that, the radio-jet mode starts to take control at low redshift by maintaining the tightness of the scaling relation till the level we observe today.
+After that, the radio-jet mode starts to take control at low redshift by maintaining the tightness of the scaling relation untill the level we observe today.
 
@@
 The data points indicate the distribution of the selected sample.
-The black line denotes the criterion in the simulation for which a SMBH is in a quasar (above) or radio (below) mode.}
+The black line denotes the criterion in the simulation for which a supermassive BH is in a quasar (above) or radio (below) mode.}
 \end{figure}
@@
 Our work highlights the importance of applying measurement uncertainty and the effect of selection to the simulated data in order to make direct comparisons with observations.
-Such comparisons have been made in the local universe~\citep[e.g.,][]{Habouzit2021} where the measurements are relatively robust and the selection function is broad thus it is less crucial to ensure consistency between observations and simulations.
+Such comparisons have been made in the local universe~\citep[e.g.,][]{Habouzit2021} where the measurements are relatively robust and the selection function is broad; thus, it is less crucial to ensure consistency between observations and simulations.
 However, beyond $z>0.2$, the scatter and the central distribution of the scaling relations are dominated by measurement uncertainty and selection effects (see Figures~\ref{fig:comparsion} and~\ref{fig:deltaMM}) and a forward modeling in the observational plane becomes essential.
-Indeed, those effects would hamper our understanding of whether BHs and their hosts co-evolve or not.
-For example, from trends seen with stellar mass in Illustris and MBII (Figure~\ref{fig:deltaMM}), we found that the observations of the \mbh\ offsets as a function of \smass\  show a very different trend to the intrinsic one.
+Indeed, those effects would hamper our understanding of whether BHs and their hosts coevolve or not.
+For example, from trends seen with stellar mass in Illustris and MBII (Figure~\ref{fig:deltaMM}), we found that the observations of the \mbh\ offsets as a function of \smass\  show a very different trend from the intrinsic one.
 
-Extending this study to even higher redshift and lower mass galaxies (\smass\ $<10^{10}M_{\odot}$) will be very beneficial, probing closer to the epoch of formation of massive galaxies and supermassive BHs.
-The understanding of how and when the tight scaling relation emerged are crucial to test theoretical models \citep{Volonteri2021}.
-On the observational side, the James Webb Space Telescope will provide high-quality imaging data of AGNs at redshift up to $z\sim7$ and beyond.
+Extending this study to even higher-redshift and lower-mass galaxies (\smass\ $<10^{10}M_{\odot}$) will be very beneficial, probing closer to the epoch of formation of massive galaxies and supermassive BHs.
+The understanding of how and when the tight scaling relation emerged is crucial for testing theoretical models \citep{Volonteri2021}.
+On the observational side, the James Webb Space Telescope will provide high-quality imaging data of AGNs at redshifts up to $z\sim7$ and beyond.
 The upcoming measurements will represent stringent tests on the proposed physical mechanisms for the initial formation of supermassive BHs and of their subsequent evolution with galaxies.
@@
 
-\begin{deluxetable*}{lcccc}
-\tablecaption{Summary of the p-value using KS test \label{tab:pvalue}}
+\begin{deluxetable}{lcccc}
+\tablecaption{Summary of the $p$-value using KS test \label{tab:pvalue}}
 \tablewidth{0pt}
 \tablehead{
-\colhead{Simulation} &  \multicolumn{3}{c}{HSC comparison} & \colhead{HST comparison} \\
+\colhead{Simulation} &  \multicolumn{3}{c}{HSC Comparison} & \colhead{HST Comparison} \\
 \cline{2-4} 
@@
 \enddata
-\tablecomments{These p-values are obtained by the KS test between the simulation and the observation based on one realization.}
-\end{deluxetable*}
+\tablecomments{These $p$-values are obtained by the KS test between the simulation and the observation based on one realization.}
+\end{deluxetable}
 

### 2022-10-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/paper submit/first submit/ding_jwst_v1.tex
Update when address referee report

\documentclass[twocolumn]{aastex631}
\usepackage{amsmath}
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

\makeatletter
\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}  %For share same footnote
\makeatother

\newcommand{\sersic}{S\'ersic}
\newcommand{\lenstronomy}{\texttt{lenstronomy}}
\newcommand{\galight}{\texttt{galight}}
\newcommand{\reff}{{$R_{\mathrm{eff}}$}}
\newcommand{\smass}{{$M_*$}}
\newcommand{\hst}{{\it HST}}
\newcommand{\jwst}{{\it JWST}}
\newcommand{\angstrom}{\text{\normalfont\AA}}

\newcommand{\org}[1]{\textcolor{orange}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\todo}[1]{\textcolor{red}{[{\bf TODO}: #1]}}
\newcommand{\tbd}[1]{\textcolor{red}{[{\bf TBD}: #1]}}

\begin{document}
\title{Opening the era of quasar host studies at high redshift with JWST}

\author[0000-0002-0786-7307]{Xuheng Ding}
\email{xuheng.ding@ipmu.jp}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}

\author[0000-0002-0000-6977]{John D. Silverman}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
\affiliation{Department of Astronomy, School of Science, The University of Tokyo, 7-3-1 Hongo, Bunkyo, Tokyo 113-0033, Japan}

\author[0000-0003-2984-6803]{Masafusa Onoue}
\affiliation{Kavli Institute for Astronomy and Astrophysics, Peking University, Beijing 100871, China}
\affiliation{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}

\begin{abstract}
We measure the host galaxy properties of five quasars with $z\sim 1.6 - 3.5$ selected from SDSS and AEGIS, which fall within the \jwst/\hst\ CEERS survey area. A PSF library is constructed based on stars in the full field-of-view of the data and used with a 2-dimensional image modeling tool \galight\ to decompose the quasar and its host with multi-band filters available for \hst\ ACS+WFC3 and \jwst\ NIRCAM (12 filters covering \hst\ F606W to \jwst\ F444W). As demonstrated, \jwst\ provides the first capability to detect quasar hosts at $z>3$ and enables spatially-resolved studies of the underlying stellar populations at $z\sim2$ within morphological structures (spiral arms, bar) not possible with \hst. Overall, we find quasar hosts to be disk-like, lack merger signatures, and have sizes generally more compact than typical star-forming galaxies at their respective stellar, thus in agreement with results at lower redshifts. The fortuitous face-on orientation of SDSSJ1420+5300A at $z = 1.646$ enables us to find higher star formation and younger ages in the central $2-4$ kpc region relative to the outskirts, which may help explain the relatively compact nature of quasar hosts and pose a challenge to AGN feedback models.

\end{abstract}
\keywords{Galaxy evolution(594) --- AGN host galaxies(2017) --- Quasars (1319) --- Active galaxies(17)}

\section{Introduction} \label{sec:intro}

A key open question in astrophysics is how the tight correlations between the mass of supermassive black holes (SMBH) and their host galaxy properties (e.g.,~velocity dispersion, bulge stellar mass) emerge~\citep[e.g.,~][]{Mag++98, F+M00, M+H03, H+R04, Gul++09, Geb++01b, Gra++2011,Beifi2012}. Galaxy mergers are too rare, and most quasar hosts do not show signs of interactions or disturbances to be a primary driver \citep[e.g.,][]{Cisternas2011,Kocevski2012,Mechtley2016}. Thus, secular (i.e., internal) processes are the only other conceivable options that can concurrently feed the black hole and build the central stellar mass concentration. Likely relevant, quasars hosts have been recently shown to have sizes (effective radius) more compact than the star-forming population but not yet as small as the quiescent population \citep{Silverman2019,Li2021}. We do not yet know whether those central stars are formed in situ or brought in from further out, possibly due to minor mergers.

To make further progress, a decomposition of the host galaxy from its central quasar is required to measure the host properties at earlier cosmic times ($z\gtrsim2$) when the central regions of galaxies are forming stars and particularly those that can be spatially resolved. At a cosmological distance, galaxies have smaller apparent sizes and become fainter due to cosmological surface dimming. The unresolved quasars as bright point sources can outshine the host galaxy, which makes the decomposition of the host challenging, even with {\it Hubble Space Telescope} (\hst) WFC3-IR, which has excelled at $z < 2$. Owing to this reason, most of the studies in the literature so far have been focused on the moderate-luminosity AGNs whose brightness is comparable to their host ~\citep{Park15, Tre++07, Bennert11, Woo++08, Jah++09, SS13, Mechtley2016,Ding2020, Ding2021, 2021ApJ...906..103L}. Hence, the stellar content of the luminous AGN hosts at $z>2$, which harbors the most massive SMBHs, has not yet been studied.

The {\it James Webb Space Telescope} (\jwst) opens up a new opportunity to extend the study of quasar hosts at high-$z$. The infrared coverage at $\lambda > 2 \mu$m provides the ability to probe the galaxy 4000~\angstrom\ break beyond $z\sim 3.5$.  The unprecedented sensitivity and resolution by \jwst\ will be a key to separating the unresolved quasar component from the extended emission of its host galaxy, particularly due to the larger aperture compared to \hst\ and the stability of the telescope, which effectively improves the characterization of the PSF.

In this paper, we use deep \textit{Near Infrared Camera} \citep[NIRCam,][]{Rieke05} imaging data from the \jwst\ Cosmic Evolution Early Release Science\footnote{\url{https://ceers.github.io}}~\citep[CEERS,][]{CEERS} program to decompose the optical and infrared emission from five quasars with redshift between 1.6 and 3.5. We limit the AGN sample to those with spectroscopic redshifts to provide accurate stellar masses and sizes of their host galaxies. We will carry out an AGN decomposition to reveal the host galaxy and then perform the spectral energy distribution (SED) fitting to infer the stellar mass, star formation rate (SFR), and stellar age. These results will aid in our ability to establish relations between AGN and host galaxy formation with \jwst\ \citep{Kocevski2022}.

The paper is organized as follows. In Section~\ref{sec:design}, we describe the \jwst/\hst\ data and our sample selection. We introduce our decomposition method in Section~\ref{sec:decomp}, including our PSF library construction, decomposition tool, and SED fitting. In Section~\ref{sec:result}, we present our measurement result and compare the inferred size mass relations with the ones from the literature. The concluding remarks are presented in Section~\ref{sec:conclusion}. Magnitudes are given in AB System. A Chabrier initial mass function is employed to measure the galaxy's stellar mass for consistency. We use a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.

\section{Experimental design} \label{sec:design}

\subsection{CEERS survey imaging and data reduction}
The CEERS \jwst\ early release science program (ERS Program \#1345) is designed to cover 100 arcmin$^2$ of the AEGIS fields with imaging and spectroscopic data~\citep{CEERS}. This program will observe ten pointings with \jwst/NIRCam as parallel with primary fields to be taken with NIRSpec and MIRI. In late June 2022, four pointings  (CEERS1, CEERS2, CEERS3, and CEERS6) were completed using 7 NIRCam filters: F115W, F150W, F200W, F277W, F356W, F410M, and F444W. The integration times are 2,635 seconds for each filter, with the exception of F115W, which was taken with an exposure time twice as long. For the CEERS2 pointing, one additional visit is performed with a slightly different PA and positional offset using filters F200W and F444W. We refer the reader to~\citet{Finkelstein2022} for more details on the \jwst\ observations and survey design.

\begin{figure*}
\centering
\includegraphics[trim={3cm 0cm 3cm 0cm},clip,width=1.8\columnwidth]{figures/psfs_profile.pdf}
\caption{Selected nine PSF surface brightness (SB) profiles (annuli) as a function of radius (based on stars detected by \jwst) per filter are shown selected from our PSF library compared with the simulated PSF model by \texttt{webbpsf}. The vertical lines indicate the FWHM values of the PSF-stars (averaged) and PSF model by \texttt{webbpsf}. We only show the profile's very inner region ($<7$ pixels), which is the key to the AGN subtraction. The PSFs in our library demonstrate a very stable performance, while the simulated PSF models by \jwst\ are too narrow (i.e., peaking at the center) for all the filters.
\label{fig:PSFprofile}}
\end{figure*}

 We performed our own data reduction to achieve science-quality images. The archived data products (stage 2) were acquired from the STScI MAST Portal\footnote{\url{https://archive.stsci.edu/}}. The stage 2 data were processed by the \jwst\ pipeline version 1.5.3 with the mapping file \textsf{jwst\_0942.pmap} except for F410M and F444W. Depending on the fields, we use \textsf{jwst\_0877.pmap} and \textsf{jwst\_0878.pmap} for F410M. For F444W, we use \textsf{jwst\_0877.pmap}, \textsf{jwst\_0878.pmap} and \textsf{jwst\_0881.pmap}. Due to the known issue for the background subtraction with the v.1.5.3 pipeline, we further post-process the stage 2 images as follows. We first subtracted the background light using \texttt{photutils} based on \textsf{Background2D} function. 
 The so-called $1/f$ noise pattern due to detector read noise was removed with the code provided by the CEERS team\footnote{\url{https://ceers.github.io/releases.html\#sdr1}}.

We then use the \jwst\ stage 3 pipeline to produce the individual images. In the  \textsf{Resample} step, we increase the pixel resolution by a factor of two with the drizzle algorithm. The pixel scale for the long-wavelength (LW) filters is $\sim$ 0\farcs{}0315 and short-wavelength (SW) filters $\sim$ 0\farcs{}0156. Saturated pixels are labeled as empty in this process. For the purposes of building a PSF library (see Section~\ref{sec:psfLibrary}), we require all four CEERS fields to have the same rotation angle. Thus, we do not apply any rotations when drizzling the images. For WCS calibration, we use the GAIA DR3 source catalog\footnote{\url{https://gea.esac.esa.int/archive/}}~\citep{GAIA16} to align our image.

The conversion factor from the instrumental signal to physical units Mega-Janskys per steradian is based on the calibration files \textsf{jwst\_nircam\_photom\_0101.fits} for module A, and \textsf{jwst\_nircam\_photom\_0104.fits} for module B. This step requires a re-calibration to correct the original flux based on pre-flight measurements. A significant difference ($10\%-20\%$ flux level) between the pre-flight and post-flight photometric reference files is noted and mentioned in~\citet{Adams22}. We have updated our calibration for the F410M and F444W flux densities based on this information. Until today, the calibration file of \jwst\ still requires updating, and there is still up
%to 0.3 mag 
to 20\% uncertainty to conversion between the ADU and flux in filters.

For the \hst\ imaging, we adopt the datasets provided by CEERS collaboration\footnote{\url{https://ceers.github.io/hdr1.html\#hst-egs}}. These \hst\ images are observed from eight different \hst\ programs (10134, 12063, 12099, 12167, 12177, 12547, 13063 and 13792), with a total of 1,767 exposures. The data reduction follows the procedures described in~\citet{Koekemoer2011}. We adopt the filters including ACS/WFC F606W and F814W, and WFC3/IR F125W, F140W, and F160W. The final pixel scale has been drizzled to a 0\farcs{}03 for all bands.

\subsection{Sample Selection}
We searched for quasars in the SDSS DR16 quasar catalog~\citep{2020ApJS..250....8L} and the AEGIS-X AGN catalog~\citep{2009ApJS..180..102L, Nandra2015} that fall within the CEERS field. We also limited our targets to those with spectroscopic redshifts greater than 1.6 to focus on high redshift quasars, which have been challenging for \hst\ to detect their host. Three SDSS quasars were identified with redshifts at 1.646, 2.588, and 3.442, respectively. SDSS1419+5254 ($z=3.442$) falls in CEERS2 and thus has only two \jwst\ filters (i.e., F200W and F444W) available at this moment. From AEGIS-X, we also find four quasars with spectroscopic redshifts above $z>1.6$. After manually checking, we find that two of them are matched to SDSS quasars\footnote{After the manual confirmation, we find SDSS1419+5254 and AEGIS 585 are the same system;  SDSS1420+5300A and AEGIS 742 are the same system.}. As a result, two additional targets are selected with redshift at 2.317 and 3.465, respectively. While MIRI images were taken in parallel, no additional quasars were found. We note that only one quasar (AEGIS 482) is in common with a recent \jwst\ study of X-ray-selected AGN in CEERS \citep{Kocevski2022}. The properties of our five quasars are given in Table~\ref{table:sample}.

\section{Quasar-host image decomposition} \label{sec:decomp}
We use our previous 2D image modeling strategy, as fully presented in~\citet{Ding2020}, to perform the AGN decomposition. We first build a PSF library by searching for all point sources (i.e., stars) in the \jwst\ field of views (FOVs). We then perform the fitting of the main quasar target by using the 2D image modeling tool \galight~\citep{Ding2020, Ding2021a} and consider each PSF-star in the library. The final PSF will be chosen from the top-ranked fits as described below.

\subsection{PSF Library}\label{sec:psfLibrary}
The key to AGN-host decomposition is the quality of the PSF, especially when revealing the host galaxy for luminous quasars whose central point source usually dominates the emission. The PSF shape varies with color, brightness, position across the detector, and over time due to aberration and telescope breathing.

In this paper, we use the previous strategy of~\citet{Ding2022} and collect all isolated, unsaturated PSF stars with sufficient signal-to-noise levels to build our PSF library. We use the PSF-pickers (the \texttt{find$\_$PSF()} function) provided by \galight\ (see next section~\ref{subsec:decomp} for details) to help us collect these objects having a point-like feature as our initial PSF candidates through all the \jwst/\hst\ filters in four CEERS visits. By sorting the FWHM values from low to high and manually viewing the local image stamps of each PSF candidate, we select the PSF candidates that are isolated and sharp. To build the library, we select at least 12 PSF stars for each filter.

It is also known that simulated PSF for \hst\ based on \texttt{TinyTim}~\citep{2011SPIE.8127E..0JK} is usually inaccurate (narrow) and not ideal for our goal of AGN decomposition~\citep[e.g.,][]{Mechtley2012}. In this work, we also test the effectiveness of \texttt{webbpsf}~\citep{2014SPIE.9143E..3XP} to generate the PSF model for \jwst\ but find that the simulated PSF is also too narrow compared with the PSF in the library \citep[see][for similar conclusions]{Ono2022}. We show the surface brightness profiles of PSF stars and the PSF by \texttt{webbpsf} as a function of the radius (in pixel unit) in Figure~\ref{fig:PSFprofile}.

\begin{figure*}
\centering
\includegraphics[trim={7cm 1.5cm 7cm 0.5cm},clip,width=1.7\columnwidth]{figures/datahost_35.pdf}
\includegraphics[trim={7cm 1.5cm 7cm 0.5cm},clip,width=1.7\columnwidth]{figures/datahost_0.pdf}
\includegraphics[trim={7cm 1.5cm 7cm 0.5cm},clip,width=1.7\columnwidth]{figures/datahost_2.pdf}
\includegraphics[trim={7cm 1.5cm 7cm 0.5cm},clip,width=1.7\columnwidth]{figures/datahost_51.pdf}
\caption{Science-grade images (1st and 3rd columns) and the host galaxy images (2nd and 4th columns) for the four quasar targets at $z>2$ with F200W and F444W filters are presented. In each case, the host galaxy image (i.e., data minus quasar) is produced by subtracting the best-fit PSF. The redshift of each quasar is indicated in each panel. The pixel units are in Mega-Janskys per steradian (MJy/sr).
For the LW (e.g., F444W) filter, AEGIS 477 happens to be located at the edge of FOV in module B; only the right-side part of the quasar is observed.}
\label{fig:datahost}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim={9cm 1cm 3cm 0cm},clip,width=2\columnwidth]{figures/ID1_F814W_qso_final_plot.pdf}  \\
\vspace*{-0.2cm} 
\includegraphics[trim={9cm 1cm 3cm 0.5cm},clip,width=2\columnwidth]{figures/ID1_F160W_qso_final_plot.pdf}  \\
\vspace*{0.6cm} 
\includegraphics[trim={9cm 1cm 3cm 0cm},clip,width=2\columnwidth]{figures/ID1_F150W_qso_final_plot.pdf}  \\  
\vspace*{-0.2cm} 
\includegraphics[trim={9cm 1cm 3cm 0.5cm},clip,width=2\columnwidth]{figures/ID1_F444W_qso_final_plot.pdf}  \\
\caption{2D decomposition of SDSS1420A based on imaging data from \hst\ in panel~(a) and \jwst\ in panel~(b); two filters are selected for each telescope. The panels are as follows from left to right: original data, model (quasar + galaxies) convolved with the PSF, data $-$ quasar (host galaxy only), normalized residual image, and 1D surface brightness profile (top), and the corresponding residual (bottom).
\label{fig:fitting}}
\end{figure*}

\subsection{Image Decomposition}\label{subsec:decomp}

Two-dimensional modeling of images is performed based on our self-developed software \galight, which is a \texttt{python}-based open-source package that provides various astronomical data processing tools and performs 2D profile fitting. It utilizes the image modeling capabilities of \lenstronomy~\citep{2018PDU....22..189B, 2021JOSS....6.3283B} while redesigning the user interface to allow for an automated fitting ability. \galight\ uses the Particle Swarm Optimization~\citep{Kennedy1995} technique embedded in \lenstronomy\ to perform for $\chi ^2$ minimization.

We use \galight\ to prepare our modeling ingredients, which include the following: 1) the image cutouts that cover sufficient light emission from the quasar, 2) the noise level map that describes the uncertainty of each pixel, 3) a PSF that is taken from our PSF library. In general, the noise level includes both Poisson and random background noise. Poisson noise is estimated by calculating the effective exposure time based on the \texttt{WHT} array maps and taking into account the gain values. The background RMS noise level is measured using pixels from a blank region close to the target.

Having prepared the inputs to \galight, we perform the quasar-host decomposition. We assume the central quasar is described as a scaled PSF at an arbitrary position. We use a 2D \sersic\ profile~\citep{sersic} to model the host galaxy. If any object happens to be close to our target, we use another \sersic\ profile to model their light and remove any potential contamination from their extended profile. To avoid any unphysical results, we limit the \sersic\ parameters as follows: effective radius \reff~$\in[0\farcs{}06,2\farcs{0}]$, \sersic\ $n\in[0.3,9]$.

We recognize that the morphology of the quasar host is more complicated than a single \sersic\ profile. Nevertheless, the extended profile by a single \sersic\ model provides a good first-order approximation of the surface brightness distribution, which is sufficient to describe the host and separate it from the central quasar. The routine also produces a `data minus quasar' image, i.e., a host galaxy image, which can be used to perform a more sophisticated study of the host photometry and morphology for different scientific purposes. We apply the same \sersic\ model settings for \hst\ data and \jwst\ LW data. During the fitting, the central quasar and all galaxies within the FOV of the cutout image are modeled simultaneously since object profiles can overlap with each other.

The performance of each PSF in the library usually behaves differently for each target. Thus, we evaluate the performance of each PSF based on the final model reduced $\chi^2$ values and rank the PSFs. For \jwst, we are able to use the top 3, 5, and 8 PSFs with good performance and stack them to get a combined averaged PSF using \texttt{psfr}\footnote{\url{https://github.com/sibirrer/psfr}\label{note1}} (Birrer et al. in prep) and re-run the fitting. In the final step, we visually check the fit results for all PSFs and remove those with strong PSF mismatch residuals that could affect the result.

Our reported measurements are based on either the top-ranked individual PSFs or the combined PSFs. We then assess measurement uncertainties by calculating the dispersion from the top-5 high-ranked PSFs. After a visual check, we find that only one PSF from the library in the F444W band can produce the clean quasar subtraction for AEGIS~482 and SDSS1419+5254; thus, the uncertainty for these two targets with this filter is not estimated. As shown later, we use 0.4 mag for the error budget for the SED fitting in the F444W bands of these two systems.

\begin{figure*}
\centering
\begin{tabular}{c c}
\hspace*{-1cm}  
{\includegraphics[trim={0cm 0cm 2.4cm 0cm},clip,height=0.65\columnwidth]{figures/idx1_sed.pdf}}&
{\includegraphics[trim={2.4cm 0cm 2.4cm 0cm},clip,height=0.65\columnwidth]{figures/idx51_sed.pdf}}\\
\hspace*{-1cm}  
{\includegraphics[trim={0cm 0cm 2.4cm 0cm},clip,height=0.65\columnwidth]{figures/idx2_sed.pdf}}&
{\includegraphics[trim={2.0cm 0cm 2.4cm 0cm},clip,height=0.65\columnwidth]{figures/idx35_sed.pdf}}\\
\end{tabular}
\caption{SED fitting of the host galaxy photometry based on \texttt{gsf}~\citep{Morishita2019} software. The red data points with errors indicate the host flux only, i.e., the quasar emission has been removed. The red arrow represents an upper limit. The blue diamonds show the predictions using the best-fit model. The inferred \smass\ is also shown in the figure with 16\%, 50\%, and 84\% confidence levels, along with the age and SFRs, both with lower and upper limits.
\label{fig:sed_spec}}
\end{figure*}

\section{Results} \label{sec:result}
%The decomposition of the result. 
We detect the host galaxies for all five quasars in most of the \jwst\ filters based on the 2D model fitting as described in Section~\ref{subsec:decomp}. Considering all targets and filters, the host-to-total flux ratio (total = host + quasar) spans from 5\% to 60\%. For the two quasars at $z>3$, the host ratio is lower than 10\%, which is very challenging to achieve with \hst\ and impossible at $z>3$. The stability of the \jwst\ PSFs allows a significant host detection down to these low flux ratios after the removal of the quasar component. We find that the measurements of the host properties are generally consistent across the different filters, which strengthens the fidelity of our results. We list our host measurements in Table~\ref{table:sample}.

For quasars at $z>2$, we show the images resulting from the decomposition in Figure~\ref{fig:datahost} for the F200W and F444W filters. The other filters have comparable results and are not shown due to space limitations. First, it is clearly demonstrated that any information on the host properties can only be determined after the accurate removal of the unresolved quasar component (2nd and 4th columns: host only = data $-$ quasar model component). The host galaxies of these quasars are generally isolated and do not show significant signs of undergoing a merger which is consistent with the previous studies~\citep[e.g.,][]{Cisternas2011,Kocevski2012,Ding2020} including recently reported results from CEERS on X-ray selected AGN \citep{Kocevski2022}.  We note that the fits to the \hst\ images (not shown), for this sample at $z>2$, present a larger PSF mismatch in the center that contributes significantly to the unreliability of the detection of the host.

For SDSS1420A ($z=1.646$), the 2D fitting results are presented in Figure~\ref{fig:fitting} to highlight the performance of \jwst\ (F150W, F444W) compared to \hst\ (F814W and F160W). With the 4000~\angstrom\ break ($\sim 10,000$~\angstrom\ at $z\sim1.6$) being redshifted out of the F814W filter, a very marginal detection of the host is obtained with \hst/F814W. At longer wavelengths, a highly significant detection of the host galaxy with \hst/F160W leads to very consistent fitting results with that from \jwst/F150W (see Table~\ref{table:sample}). Now, with the high-resolution power of \jwst, we can now clearly see that the quasar host is residing in a spiral galaxy with a prominent bar. Thus, the galaxy can be classified as an SBa or SBb in the Hubble classification scheme.

Overall, the majority (4/5) of quasars hosts have a low \sersic\ index ($n<2$), implying a significant disk-like component in the host galaxy. This is consistent with similar studies at lower redshift~\citep[e.g.,][]{Schawinski2012,Ding2020,Li2021,Zhuang2022}.

\subsection{SED fitting and stellar population}

We use the \texttt{gsf} package~\citep{Morishita2019} to fit the broad-band spectral energy distributions (SEDs) to infer the host stellar mass and further properties of the stellar population (i.e., stellar age and SFR). 
Stellar templates of different ages are combined to generate galaxy SED templates. In this process, weights are assigned to each stellar template and fit as free parameters to produce the final galaxy templates.
The stellar metallicity is fixed and set to the solar value. Despite the well-known degeneracy between age and metallicity, there is little effect on the determination of the \smass. The star formation rate and age will then be obtained from the final best-fit template. Dust attenuation and stellar emission lines are also considered in our SED fitting model.

We only use the host magnitudes obtained by \jwst\ filters to perform our SED fitting since the reliability of host magnitudes from \hst\ is highly uncertain. 
The SED fitting also requires errors on the magnitudes, which are estimated using the scatter of the magnitude inference from the top-5 ranked PSFs fits. If the scatter is below 0.15 mag, we fix the uncertainty at this value to account for a reported systematic error. For AEGIS 482 and SDSS1419+5254, we adopt 0.4 mag for the error since their results are provided by a single PSF.
For our sample at $z>2$, seven \jwst\ filters cover above and below the 4000~\angstrom\ break; thus, the SED fitting should provide a reliable best-fit galaxy template. Unfortunately, SDSS1419 currently only has observations with F200W and F444W, both above the 4000~\angstrom\ break. The SED fits are presented in Figure~\ref{fig:sed_spec} with the exception of SDSS1419. We note that SDSS1420A at $z=1.646$ has a marginal detection with ACS/F814W. As a constraint, we use five times the inferred flux from the F814W filter to set up an upper limit on the SED fit to constrain the strength of the 4000~\angstrom\ break. The host stellar inference, including \smass, SFR, and age, is given at the end of Table~\ref{table:sample}.

We classify the quasar hosts into star-forming and quiescent galaxies using the rest-frame U-V and V-J colors inferred by our model SED fits as done in \citet{vdW+2014}. For reference, we plot galaxy samples from CANDELS~\citep{vdW+2012, vdW+2014} at the equivalent redshifts to our sample (i.e., $1.6<z<3.5$), see Figure~\ref{fig:sizemass} - left. The distribution shows that the quasar hosts are mainly located in a star-forming region. One quasar host is at the boundary, possibly indicating that the host galaxy is close to transitioning to a more quiescent state. Broadly, these results are consistent with numerous studies that demonstrate an association between AGN/quasar activity and ongoing star formation over a wide range of cosmic time.

\subsection{Galaxy size - stellar mass relation}

As recently reported, the stellar sizes (i.e., half-light radii) of quasars hosts span a broad distribution, with the average being intermediate between that of typical star-forming and quiescent galaxy populations. These results have been demonstrated at lower redshifts with \hst~\citep[$z\sim1.5$,][]{Silverman2019} and Subaru's Hyper Suprime-Cam Strategic Survey Program~\citep[$z < 1$,][]{Li2021}. The intermediate sizes of quasar hosts may indicate that rapidly accreting SMBHs are currently in the process of forming their central mass concentrations (i.e., bulges) in order to align with the local black hole-host mass relation. In fact, a high AGN fraction is seen in compact star-forming galaxies at $z\sim2$ \citep{Kocevski2017}.

Here, we investigate the location of our five high-$z$ quasar hosts relative to the size -- \smass\ relation for inactive galaxies at their respective redshift and stellar mass. The size is the median value of those measured in each filter which removes the possibility that errant fits in a single filter affect the final size measurement. As seen in Table~\ref{table:sample}, the fit using \jwst/F150W for AEGIS-482 has a size that is very small and inconsistent with the other bands. For sizes, i.e., \reff, we use recipes in~\citet{vdW+2014} to the adjust the median \reff\ to the rest-frame 5000~\angstrom. For the control sample, we use the size measurements of individual galaxies at equivalent redshifts (i.e., $1.6<z<3.5$) and the best-fit relation at $z\sim2.2$ in~\citet{vdW+2014} for star-forming and quiescent galaxies, which are classified using UVJ photometry.

In Figure~\ref{fig:sizemass}, we show that most (4/5) quasar hosts are compact with sizes \reff$\lesssim$1~kpc. SDSS1420A is larger due to its high stellar mass. Two quasars (AEGIS~482, SDSS1420A) are in agreement with the average star-forming galaxy at their respective stellar mass, as indicated by the solid blue line. The remaining three are smaller than typical star-forming galaxies. SDSS1420B is very compact based on our upper limit resulting from a fit that hits the boundary of our allowed range in size; even so, the size constraint is consistent with quiescent galaxies. Both AEGIS~477 and SDSS1419 have host sizes ($\sim$1 kpc) right at the boundary between the two galaxy populations. Considering the quasars with \jwst\ measurements and published results using \hst/WFC3 at $1.6<z<1.7$~\citep{Ding2020}, we conclude that many of the quasar hosts are likely undergoing structural changes. The quasars with size measurements from \jwst\ are consistent with the aforementioned studies. However, a larger sample is required to make definitive claims at $z>2$ and over a broad range in stellar mass. As evident, the \jwst\ hosts start to fill in the lower mass regime ($\log~M_*<10.5$), even down to \smass$\sim9~\log$ M$_{\odot}$.

%that may be simultaneously associated with changes in star formation activity ().

\begin{figure*}
\centering
\begin{tabular}{c c}
\hspace*{-1cm}  
{\includegraphics[trim={0.6cm 1.1cm 2cm 2.5cm},clip, height=0.4\textwidth]{figures/UVJ.png}}&
{\includegraphics[trim={1cm 1.1cm 2cm 2.5cm},clip, height=0.4\textwidth]{figures/Mstar-Reff.png}}\\
\end{tabular}
\caption{$Left:$ UVJ diagram for the five quasar systems, together with the sample from CANDELS at $1.6<z<3.5$. Two systems whose 4000~\angstrom\ break is not constrained by \jwst\ are filled in white.
$Right:$ Galaxy size-\smass\ distribution and relations. The \sersic\ index values are presented by the symbol color. For SDSS1420B, \reff\ is labeled using an arrow to indicate an upper limit. We also show the best-fit relation reported in~\citet{vdW+2014} for the star-forming (blue line) and quiescent (red line) at $z\sim2.2$. We also include six broad-line AGNs at $1.6<z<1.7$ from~\citep{Ding2020} based on \hst/WFC3 imaging. 
\label{fig:sizemass}}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[trim={4cm 0cm 3cm 0cm},clip,width=2.0\columnwidth]{figures/SED_map.pdf}
\caption{Spatially-resolved host properties of SDSS1420A. The panels from left to right are as follows: (1) the original quasar color image from combining three \jwst\ filters as indicated, (2) the color image of the host galaxy after the central quasar is subtracted in each filter, (3) the stellar mass map. (4) SFR map, and (5) age map. In various panels, three regions are indicated with a radius of 2~kpc, 4~kpc, and 8~kpc. The 2~kpc region is applied as a mask in (3)-(5) panels.}
\label{fig:sedmap}
\end{figure*}

\subsection{SDSS1420A: spatially-resolved host properties}

SDSS1420A is an ideal laboratory to further study high-$z$ quasar hosts since spatially-resolved properties of the stellar population are feasible due to the angular extent of the host, being face-on, and the spatial resolution of multi-band \jwst\ observations. SDSS1420A is a very massive disk galaxy (\smass$\sim11.5~\log$ M$_{\odot}$), thus likely to be fully quenched on a short timescale and transition to a bulge-dominated galaxy. Here, our aim is to demonstrate new science capabilities enabled by \jwst. While larger samples will be required to make substantive claims, the CEERS observations of a small quasar sample can already provide further insight into the resolved properties of quasar hosts that have yet to be explored at this resolution.

As mentioned above, the decomposition of SDSS1420A reveals a clear spiral galaxy for which 2D SED fitting is feasible. We use the host-only image in seven \jwst\ filters and run the SED fitting on a pixel-by-pixel basis to generate spatially-resolved maps. Since the \hst\ F814W filter cannot resolve the host, we do not include this filter in the 2D SED fitting. To enhance the signal-to-noise and generate a map at the resolution of the PSF, we re-bin the pixels to 2$\times$2 for LW filter image and 4$\times$4 for SW filter image. Finally, the 2D SED fitting is performed at a pixel scale of $\sim0\farcs{}06$.

%Result and inspiration
The final 2D SED fitting result is shown in Figure~\ref{fig:sedmap} which includes the maps of stellar mass, SFR, and galaxy age. Since residual PSF features caused by the mismatch are strong in the center pixels, we only consider the region beyond $0\farcs{}24$ ($\sim$2~kpc), which are left unmasked in the images. The 2D SED fitting result shows that the inner region seems to have higher SFR and younger age. 
Within an inner annulus (2.0$<$ radius $<$ 4.0 kpc), we measure an average SFR density of 0.54~M$_{\odot}$/yr/kpc$^2$ and age of 1.26 Gyr. This SFR density is close to that of normal star-forming disk galaxies (i.e., sBzK) at $z\sim1.5$ \citep{Daddi2010}. In a larger annulus (4.0$<$ radius $<$ 8.0 kpc), the SFR density drops to 0.095~M$_{\odot}$/yr/kpc$^2$ while the age rises to 1.64 Gyr. The relative SFR density decreases by a factor of $\sim$six. 
Based on our 2D SED fit results, stars are growing in the center region, possibly contributing to the build-up of the bulge component. This may argue against simple AGN quenching since one would expect less star formation in the central regions as compared to the outskirts. 
\newpage

\section{Concluding Remarks}\label{sec:conclusion}

We presented two-dimensional image decomposition in the optical and infrared of five luminous quasars from SDSS and AEGIS with $1.6<z<3.5$ based on \jwst+\hst\ imaging (12 filters in total from \hst/ACS/F606W to \jwst/NIRCam/F444W) provided by the CEERS collaboration. Our purpose is to detect their host galaxies and measure their properties (i.e., size, \sersic\ index, magnitude, color) for the first time beyond $z>3$. For this, we constructed a PSF library from stars within each field-of-view for every filter (see Section~\ref{subsec:decomp}). Two-dimensional modeling is then carried out using the tool \galight. A single top-ranked PSF, assessed by the goodness-of-fit, is used for host-quasar decomposition, while additional fits using other high-ranked PSFs provide an assessment of the uncertainty in the host magnitudes. With multi-band photometry of the host, we performed SED fitting to infer the properties of the stellar population, including stellar mass, age, and star formation rate.

We detect the host galaxy and model the emission for all five quasars as shown in Figure~\ref{fig:datahost} and~\ref{fig:fitting}. The host-to-total flux ratios vary greatly from 5\% to 60\% with the lower ratios only possible with the remarkable stability of the \jwst\ PSF. Our main science results are summarized as follows:

\begin{enumerate}

\item Overall, the inferred \sersic\ indices are low, with 4/5 of them having $n<2$ that agrees with past studies which demonstrate the presence of a significant stellar disk \citep[e.g.,][]{Li2021, Zhuang2022}.

\item Based on SED fitting, the \smass\ distribution ranges from 9.2 to 11.5 in units of $\log~$M$_{\odot}$. According to the UVJ classification (Figure~\ref{fig:sizemass}, left panel), the quasar hosts lie in the star-forming region. One is close to the boundary with quiescent galaxies, possibly indicating a transitioning stage.

\item The stellar sizes cover a broad range with 2/5 consistent with the size--mass relation of star-forming galaxies, while the other three have compact sizes in agreement with quiescent galaxies or transitioning to that state.

\item Based on a spatially-resolved investigation, SDSS1420+5300A ($z=1.646$) is a face-on galaxy with an extended profile exhibiting spiral arms and a bar. We are able to perform a 2D SED fitting using the host image with seven \jwst\ filters (Figure~\ref{fig:sedmap}). The SED map shows that the averaged SFR density in the inner annulus (2.0$<$ radius $<$ 4.0 kpc) is higher than that in an outer annulus (4.0$<$ radius $<$ 8.0 kpc) by a factor of six. The ongoing star formation and newly-formed stars in the central region are likely signs of a bulge in formation without direct evidence for quasar-mode feedback. 
\end{enumerate}

Our work demonstrates the unprecedented ability of \jwst\ to reveal the host of luminous quasars, especially at $z>3$. As demonstrated, accurate characterization of the PSF is crucial using stars within the \jwst\ FOV. The PSF shape also varies at each AGN's location; using just one empirical PSF may not always provide a decent model. Finally, the model PSF by \texttt{webbpsf} is always too peaked in the center for quasar subtraction as shown in Figure~\ref{fig:PSFprofile}.

\jwst\ has ushered in a new era for which we are now able to study quasar hosts to even higher redshift ($z\sim6$ and beyond) and lower mass. This is crucial to probe epochs closer to the formation of massive galaxies and their supermassive BHs, thus better constraining theoretical models of their connection \citep{Volonteri2021, Ding2022}.

\begin{table*}
% \centering
\caption{Quasar information and inferred host properties}\label{table:sample}
\resizebox{17cm}{!}{
\begin{tabular}{llllll}
\hline
Inference & SDSS1420+5300A & AEGIS 477 & SDSS1420+5300B & SDSS1419+5254 & AEGIS 482 \\
\hline\hline
                %idx1       & idx51        & idx2         & idx0       & idx35
% \multicolumn{5}{c}{} \\
RA & 215.0233 & 214.8707 & 215.0359 & 214.9316 & 214.7552 \\
Dec & 53.0102 & 52.8331 & 53.0011 &  52.9087 & 52.8368  \\
Redshift &  1.646 & 2.317 & 2.588 & 3.442 & 3.465 \\\cline{2-6}

& \multicolumn{5}{c}{\hst\ WFC3 F160W (18 PSFs in library)} \\ \cline{2-6}
host-total flux ratio & 31.7\%$\pm$1.3\% & 20.3\%$\pm$6.4\% & 21.8\%$\pm$2.3\% & 10.7\%$\pm$1.1\% & 5.5\%$\pm$2.5\%\\
Reff ($\arcsec$) & 0.532$\pm$0.035 & 0.177$\pm$0.021 & 0.139$\pm$0.013 & 0.185$\pm$0.009 & 0.142$\pm$0.030\\
Reff (kpc) & 4.50$\pm$0.30 & 1.45$\pm$0.17 & 1.11$\pm$0.11 & 1.36$\pm$0.07 & 1.04$\pm$0.22\\
\sersic\ $n$ & 2.2$\pm$0.7 & 0.4$\pm$0.1 & 0.3$\downarrow$ & 0.3$\downarrow$ & 0.3$\downarrow$\\
host mag & 20.96$\pm$0.15 & 23.49$\pm$0.26 & 22.87$\pm$0.15 & 23.42$\pm$0.15 & 25.11$\pm$0.34\\
$\chi ^2$ (Reduced) & 15.04 & 2.41 & 4.39 & 5.59 & 2.68\\
\cline{2-6}

& \multicolumn{5}{c}{\jwst\ NIRCam F150W (26 PSFs in library)} \\ \cline{2-6}
host-total flux ratio & 32.1\%$\pm$8.8\% & 39.8\%$\pm$6.1\% & 14.1\%$\pm$3.9\% & \nodata & 5.8\%$\pm$2.2\%\\
Reff ($\arcsec$) & 0.478$\pm$0.07 & 0.101$\pm$0.016 & 0.06$\downarrow$ & \nodata & 0.091$\pm$0.031\\
Reff (kpc) & 4.05$\pm$0.59 & 0.83$\pm$0.13 & 0.48$\downarrow$ & \nodata & 0.67$\pm$0.23\\
\sersic\ $n$ & 2.0$\pm$0.8 & 1.7$\pm$1.2 & 9.0$\uparrow$ & \nodata & 7.1$\pm$1.9\\
host mag & 21.17$\pm$0.58 & 22.81$\pm$0.15 & 23.17$\pm$0.41 & \nodata & 25.16$\pm$0.78\\
$\chi ^2$ (Reduced) & 3.24 & 3.34 & 2.22 & \nodata & 1.29\\
\cline{2-6}
& \multicolumn{5}{c}{\jwst\ NIRCam F200W (23 PSFs in library)} \\ \cline{2-6}
host-total flux ratio & 41.4\%$\pm$0.3\% & 36.5\%$\pm$1.1\% & 15.0\%$\pm$3.7\% & 16.3\%$\pm$5.5\% & 8.3\%$\pm$4.7\%\\
Reff ($\arcsec$) & 0.436$\pm$0.004 & 0.122$\pm$0.003 & 0.089$\pm$0.029 & 0.161$\pm$0.03 & 0.159$\pm$0.045\\
Reff (kpc) & 3.69$\pm$0.04 & 1.00$\pm$0.03 & 0.71$\pm$0.23 & 1.18$\pm$0.22 & 1.17$\pm$0.33\\
\sersic\ $n$ & 2.3$\pm$0.1 & 1.2$\pm$0.1 & 7.7$\pm$1.3 & 1.2$\pm$1.9 & 1.4$\pm$3.6\\
host mag & 20.45$\pm$0.15 & 22.49$\pm$0.15 & 23.0$\pm$0.38 & 23.01$\pm$0.26 & 24.69$\pm$0.41\\
$\chi ^2$ (Reduced) & 2.74 & 2.69 & 2.17 & 5.42 & 1.58\\
\cline{2-6}

& \multicolumn{5}{c}{\jwst\ NIRCam F356W (12 PSFs in library)} \\ \cline{2-6}
host-total flux ratio & 40.0\%$\pm$0.2\% & 44.4\%$\pm$2.2\% & 29.3\%$\pm$6.8\% & \nodata & 10.9\%$\pm$0.6\%\\
Reff ($\arcsec$) & 0.4000$\pm$0.004 & 0.129$\pm$0.008 & 0.095$\pm$0.035 & \nodata & 0.221$\pm$0.007\\
Reff (kpc) & 3.39$\pm$0.04 & 1.06$\pm$0.06 & 0.76$\pm$0.28 & \nodata & 1.63$\pm$0.05\\
\sersic\ $n$ & 2.1$\pm$0.1 & 1.2$\pm$0.1 & 5.6$\pm$2.3 & \nodata & 1.3$\pm$0.2\\
host mag & 19.96$\pm$0.15 & 22.27$\pm$0.15 & 22.29$\pm$0.40 & \nodata & 24.6$\pm$0.15\\
$\chi ^2$ (Reduced) & 17.36 & 1.11 & 3.56 & \nodata & 3.53\\
\cline{2-6}

& \multicolumn{5}{c}{\jwst\ NIRCam F444W (18 PSFs in library)} \\ \cline{2-6}
host-total flux ratio & 32.8\%$\pm$1.1\% & 48.1\%$\pm$4.9\% & 22.6\%$\pm$2.4\% & 12.1\%& 6.2\%\\
Reff ($\arcsec$) & 0.386$\pm$0.008 & 0.102$\pm$0.011 & 0.067$\pm$0.013 & 0.312 & 0.295\\
Reff (kpc) & 3.27$\pm$0.07 & 0.84$\pm$0.09 & 0.54$\pm$0.10 & 2.30 & 2.17\\
\sersic\ $n$ & 1.9$\pm$0.1 & 1.6$\pm$0.2 & 4.9$\pm$0.6 & 0.7 & 0.4\\
host mag & 19.87$\pm$0.15 & 22.13$\pm$0.17 & 22.58$\pm$0.15 & 23.44 & 24.93\\
$\chi ^2$ (Reduced) & 10.45 & 3.27 & 2.03 & 12.13 & 4.21\\
\cline{2-6}

& \multicolumn{5}{c}{SED inference} \\ \cline{2-6}
$M_*$ ($\log$ M$_{\odot}$) & [11.30, 11.35 ,11.39] & [10.21, 10.36 ,10.45] & [10.14, 10.19 ,10.25] & [9.02, 10.16 ,10.41] & [9.17, 9.34 ,9.55] \\
age (Gyr)  &                  [0.6$-$1.5]  & [0.3$-$0.9] & [0.1$-$0.4] & [0.1$-$0.5] & [$\leftarrow$0.3] \\
SFR (M$_{\odot}$/yr) &       [$\leftarrow$14.5] & [9.2$-$51.4]  & [$\leftarrow$2.1] & [$\leftarrow$6.4] & [7.6$-$15.0] \\
\cline{2-6} \\
\hline
\hline
\end{tabular}}
\tablecomments{The information of each target is listed by column. For page limitation, we only present one band from \hst\ and four bands from \jwst. The total number of selected PSF from the entire FOV for each filter is also shown in the table. The \reff\ is referred to as the semi-major-axis half-light radius. We present the inferred values for the SED fitting inference at 16\%, 50\% (if present), and 84\% confidence. For AEGIS~482 and SDSS1419+5254, only one PSF in the library can produce a decent fit in the F444W filter (see Figure~\ref{fig:datahost}); we thus only show the result using that PSF. The up/down arrows are used to indicate the \sersic\ fitting hit the parameter boundary. Note that, for $z>2$ sample, the host measurements provided by \hst\ should be considered highly uncertain.
}
\end{table*}

\section*{Acknowledgments}
\begin{acknowledgments}
We thank the CEERS collaboration that achieves the \jwst\ observation for the data. We thank Takahiro Morishita for the help with using the \texttt{gsf} package. We thank Simon Birrer for providing the \texttt{psfr} package that has been used for the PSF stacking. We thank Knud Jahnke, Takuma Izumi, Yoshiki Matsuoka, Lilan Yang, and Hassen Yesuf for the useful discussion.

This work was supported by World Premier International Research Center Initiative (WPI), MEXT, Japan. X.D. is supported by JSPS KAKENHI Grant Number JP22K14071. J.S. is supported by JSPS KAKENHI (grant Nos. JP18H01251 and JP22H01262) and the World Premier International Research Center Initiative (WPI), MEXT, Japan. 
M.O. is supported by the National Natural Science Foundation of China (12150410307).
\\
\end{acknowledgments}

\facilities{\hst, \jwst}

\software{\galight\citep{Ding2020,Ding2021a}, \lenstronomy~\citep{2018PDU....22..189B, 2021JOSS....6.3283B}, \texttt{gsf}~\citep{Morishita2019}, \texttt{psfr}\footnoteref{note1} (Birrer et al. in prep), \texttt{astropy}~\citep{2013A&A...558A..33A,2018AJ....156..123A}, \texttt{photutils}~\citep{larry_bradley_2020_4044744}}.

\bibliography{jwst_hosts}{}
\bibliographystyle{aasjournal}

\end{document}

### 2022-10-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/1_read_PSF_pos.py

@@ -1,0 +1,29 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Oct  3 21:12:35 2022
+
+@author: Dartoon
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+
+import glob, pickle
+
+filters =  ['F115','F150','F200','F277','F356', 'F410','F444']
+
+for filt in filters:
+    PSF_lib_files = glob.glob('material/*'+filt[:-1]+'*_PSF_Library.pkl')[0]
+    PSF_list, PSF_list_clean, PSF_RA_DEC_list, PSF_from_file_list = pickle.load(open(PSF_lib_files,'rb'))
+    if filt != 'F410':
+        s = 'W'
+    else:
+        s = 'M'
+        
+    filt = filt+s
+    
+    print(filt, 'WCS Positions RA, Dec')
+    for item in PSF_RA_DEC_list:
+        print("{0:.4f} {1:.4f}".format(item[0], item[1]))

### 2022-10-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/4_check_fitrun_allbands_JWST+HST.py

@@ -35,9 +35,9 @@ remove_id = [24, 55]
 # for idx in [31, 32, 56]:   #JWST PS position corrected
 # for idx in [0, 2, 8, 28, 35, 51]:  #z_spec > 2
 # for idx in [29, 53]:  #z_spec > 2
-
+from functions_for_result import name_list
 result = []
-for idx in [1]:  #CEERS
+for idx in [0]:  #CEERS
     if idx in remove_id:
         continue
     else:
@@ -106,12 +106,13 @@ for idx in [1]:  #CEERS
             fit_run.plot_final_qso_fit(target_ID = target_id+'$-$'+filt)
             
             # name_list = {1:'SDSS1420+5300A', 2: 'SDSS1420+5300B', 0: 'SDSS1419+5254', 
-            #              51: 'aegis_477', 35: 'aegis_482'}
+            #               51: 'aegis_477', 35: 'aegis_482'}
+
             # target_id = name_list[int(idx)]
             # fit_run.savename = 'outcomes/'+'ID' + idx + '_' + filt
             # fit_run.plot_final_qso_fit(target_ID = target_id+'  '+filt, save_plot= True)
             
-            prop_name = 'R_sersic'
+            prop_name = 'magnitude'
             # all_values = [fit_run_list[i].final_result_ps[0][prop_name] for i in range(len(fit_run_list))]
             all_values = [fit_run_list[i].final_result_galaxy[0][prop_name] for i in range(len(fit_run_list))]
             weighted_value = np.sum(np.array(all_values)*weight) / np.sum(weight)

### 2022-10-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/4_plot_PSF_profiles.py

@@ -93,18 +93,22 @@ for i_filt, filt in enumerate(filt_list):
     axs[_i][_j].tick_params(which='both', width=2, direction='in')
     axs[_i][_j].tick_params(which='major', length=7, direction='in')
     axs[_i][_j].tick_params(which='minor', length=4, color='r', direction='in')
-    axs[_i][_j].text(2, 1.6,filt, fontsize=25)
+    axs[_i][_j].text(4.9, 2.0,filt, fontsize=25)
     if _i == 0:
-        axs[_i][_j].set_xlim([1.7, 6])
-        axs[_i][_j].set_ylim([0.1, 1.8])
+        axs[_i][_j].set_xlim([1.4, 6.9])
+        axs[_i][_j].set_ylim([0.04, 2.5])
     if _i == 1:
-        axs[_i][_j].set_xlim([1.7, 5.9])
-        axs[_i][_j].set_ylim([0.1, 1.8])
+        axs[_i][_j].set_xlim([1.4, 6.9])
+        axs[_i][_j].set_ylim([0.04, 2.5])
     
     if _i == 1:
         axs[_i][_j].set_xlabel("Pixels", fontsize=20)
     if _j == 0:
-        axs[_i][_j].set_ylabel("Scaled Surface Brightness", fontsize=17)
+        axs[_i][_j].set_ylabel("Scaled SB (annuli)", fontsize=17)
+    if _j > 0:
+        # axs[_i][_j].axes.yaxis.set_visible(False)
+        # plt.grid(which="minor")
+        axs[_i][_j].set_yticklabels([])
     if x_gridspace == 'log':
         axs[_i][_j].set_xscale('log')
         # plt.xlim(1.3, ) 
@@ -112,12 +116,13 @@ for i_filt, filt in enumerate(filt_list):
     # plt.grid(which="minor")
     # plt.legend(prop={'size':15},ncol=2)
     plt.tick_params(labelsize=20)
-    axs[_i][_j].tick_params(labelsize=20)        
-    if hide_axes == True:
-        axs[_i][_j].axes.xaxis.set_visible(False)
-        axs[_i][_j].axes.yaxis.set_visible(False)
+    axs[_i][_j].tick_params(labelsize=20)      
+    
+    # if hide_axes == True:
+    #     axs[_i][_j].axes.xaxis.set_visible(False)
+    #     axs[_i][_j].axes.yaxis.set_visible(False)
         
[…]

### 2022-10-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/4_plot_UVJ.py

@@ -22,7 +22,8 @@ matt.rcParams['font.family'] = 'STIXGeneral'
 
 # #0.4 mag error
 # folder = '20220901_' #Not HST
-folder = '20220901' #HST upper limit
+# folder = '20220901' #HST upper limit
+folder = '20220906' #mag error based on PSF lib
 
 from functions_for_result import esti_smass, load_prop, load_info, name_list
 
@@ -44,18 +45,19 @@ plt.figure(figsize=(11,11))
 
 empty = np.array([True, False, True, False, False])
 confrim = empty==False
-plt.scatter(color[:,0][empty], color[:,1][empty],s=280,marker="H",
+# empty = np.array([True, False, False, False, False])
+plt.scatter(color[:,0][empty], color[:,1][empty],s=880,marker="H",
             # c='darkred',s=280,marker="o",zorder=1, vmin=0.5, vmax=5, edgecolors='white')
-             facecolors='none', edgecolors='darkred', linewidths=2)
-plt.scatter(color[:,0][confrim], color[:,1][confrim],
-            c='darkred',s=280,marker="H",zorder=1, vmin=0.5, vmax=5, edgecolors='black')
+             facecolors='white', edgecolors='black', linewidths=2, zorder=4, alpha =0.8)
+jwst_p = plt.scatter(color[:,0][confrim], color[:,1][confrim],
+            c='lightskyblue',s=880,marker="H",zorder=2, vmin=0.5, vmax=5, edgecolors='black')
 
 for i in range(len(target_id_list)):
-    if target_id_list[i] == 'AEGIS 477':
-        plt.text(color[i,0]+0.1, color[i,1]-0.1,target_id_list[i],  fontsize = 21, zorder =2,
-                 bbox={'facecolor': 'white', 'alpha': 0.5, 'pad': 3})   
-    else:
-        plt.text(color[i,0]+0.1, color[i,1],target_id_list[i],  fontsize = 21, zorder =2,
+    if target_id_list[i] == 'SDSS1419':
+        plt.text(color[i,0]-0.6, color[i,1]+0.1,target_id_list[i],  fontsize = 21, zorder =2,
+                  bbox={'facecolor': 'white', 'alpha': 0.5, 'pad': 3})   
+    if target_id_list[i] != 'SDSS1419':
[…]

### 2022-10-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/4_plot_each_host.py

@@ -16,7 +16,7 @@ from matplotlib.colors import LogNorm
 
 # ID, mags, z = 'idx0', 
 # 1,2,0,51,35
-idx = 35
+idx = 51
 # root_folder = '../*/*'  #Include HST
 root_folder = './*'  #Not include HST
 fit_run_dict = load_prop(idx, root_folder = root_folder, prop_name='fit_run')
@@ -31,7 +31,7 @@ for filt in use_filt:
     image_list.append(data)
     image_list.append(host)
     label.append(filt+'\ndata')
-    label.append(filt+'\nhost (data-AGN)')
+    label.append(filt+'\nhost (data-quasar)')
     deltaPix_list.append(fit_run.fitting_specify_class.deltaPix)
     deltaPix_list.append(fit_run.fitting_specify_class.deltaPix)
 
@@ -83,6 +83,11 @@ def total_compare(flux_list_2d, label_list_2d,
     """
     # norm = LogNorm() #ImageNormalize(stretch=SqrtStretch())
     cl_num = len(flux_list_2d)
+    left, width = .25, .5
+    bottom, height = .25, .5
+    right = left + width
+    top = bottom + height
+    
     f = plt.figure(0, figsize=(6.5+ (cl_num-1)*3.5,4))    
     ax_l = [plt.subplot2grid((6,cl_num), (0,i), rowspan=6) for i in range(len(flux_list_2d))] #The image plot
     if cmap == None:
@@ -109,12 +114,15 @@ def total_compare(flux_list_2d, label_list_2d,
                      weight='bold', color='white')
         
         if z != None:
-            ax_l[i].text(frame_size*0.65, frame_size*0.05, 'z={0}'.format(z),fontsize=fontsize, 
+            ax_l[i].text(frame_size*0.95, frame_size*0.05, 'z={0}'.format(z),fontsize=fontsize, 
+                         ha='right', va='bottom',
                          weight='bold', color='white', bbox={'facecolor': 'gold', 'alpha': 0.6, 'pad': 3})
         
         if i == 0:
-            ax_l[i].text(frame_size*0.5, frame_size*0.9, target_ID,fontsize=fontsize, 
+            ax_l[i].text(frame_size*0.95, frame_size*0.95, target_ID,fontsize=fontsize, 
+                         ha='right', va='top',
                          weight='bold', color='white',  bbox={'facecolor': 'gold', 'alpha': 0.6, 'pad': 3})
+
[…]

### 2022-10-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/4_refit_residual_central_mask.py

@@ -55,14 +55,14 @@ if refit == True:
 
 
 #%%
-# for idx in [0]:
-for idx in [0, 1, 2, 35, 51]:
+for idx in [2]:
+# for idx in [0, 1, 2, 35, 51]:
     target_id, z = load_info(idx)
     fit_run_dict = load_prop(idx, root_folder = './*', prop_name='fit_run')
     dirct_Reff = []
     refit_Reff = []
-    prop = 'R_sersic'
-    # prop = 'n_sersic'
+    # prop = 'R_sersic'
+    prop = 'n_sersic'
     # prop = 'magnitude'
     # prop = 'flux_within_frame'
     plt.figure(figsize=(6,6))

### 2022-10-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/fit_one_target/4_plot_SED_fitting.py

@@ -18,17 +18,18 @@ mat.rcParams['font.family'] = 'STIXGeneral'
 # folder = '202209' #0.2 mag no HST.
 # folder = '20220901_' #Not HST
 # folder = '20220901' #HST upper limit
+# idx = 51
 
-folder = '20220906' #mag error bar from top 5 PSF
-
-# for idx in [1,51,2,0,35]:  #z from low to high
-idx = 51
-
-target_id = name_list[idx]
-folder = 'esti_smass/'+folder+str(idx)
+# folder = '20220904' 
+# target_id = name_list[idx]
+# folder = 'esti_smass/'+folder+str(idx)
 
 
-print(idx)
+folder = 'fit_one_target/F140M_20220904101/' #
+# folder = 'fit_one_target/F140Mupper_20220904101/' #
+# folder = 'esti_smass/20220904101/' #
+idx = 101
+
 steller_file = glob.glob(folder+'/SFH_*.fits')[0]
 hdul = pyfits.open(steller_file)
 info = hdul[0].header 
@@ -53,6 +54,7 @@ print('sfr_h', sfr_h)
 print('age', age)
 print('age_l', age_l)
 print('age_h', age_h)
+
 print('AV', float(info['AV_50']) )
 print('SSFR', round(float(info['SFR_50']) - float(info['Mstel_50']) ,3) )
 # print("open",'esti_smass/'+folder+str(idx), '/' )
@@ -128,7 +130,7 @@ for i, fid in enumerate(filt_id[::-1]):
         lam = lam/10000.
         yerr_l = fnu_err/fnu
         plt.scatter(lam, flambda, c='r', zorder=100,  s=180)
-        plt.errorbar(lam, flambda, yerr=yerr_l*flambda,fmt='.',color='red',markersize=1, zorder =100, linewidth=2)
+        plt.errorbar(lam, flambda, yerr=yerr_l*flambda,fmt='.',color='gray',markersize=1, zorder =90, linewidth=2)
     if fnu == 0:
         mag = -2.5*np.log10(fnu_err) + 25
[…]

### 2022-11-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/paper submit/submit/apjl_source_file/ding_jwst_v1.tex
For ceers and upcoming data

--- 2022-10-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/paper submit/first submit/ding_jwst_v1.tex
@@
-\documentclass[twocolumn]{aastex631}
+\documentclass[twocolumn,]{aastex631}
 \usepackage{amsmath}
@@
 \newcommand{\org}[1]{\textcolor{orange}{#1}}
-\newcommand{\blue}[1]{\textcolor{blue}{#1}}
+\newcommand{\blue}[1]{\textcolor{blue}{\bf #1}}
 \newcommand{\todo}[1]{\textcolor{red}{[{\bf TODO}: #1]}}
@@
 We measure the host galaxy properties of five quasars with $z\sim 1.6 - 3.5$ selected from SDSS and AEGIS, which fall within the \jwst/\hst\ CEERS survey area.
-A PSF library is constructed based on stars in the full field-of-view of the data and used with a 2-dimensional image modeling tool \galight\ to decompose the quasar and its host with multi-band filters available for \hst\ ACS+WFC3 and \jwst\ NIRCAM (12 filters covering \hst\ F606W to \jwst\ F444W).
+A PSF library is constructed based on stars in the full field-of-view of the data and used with the 2-dimensional image modeling tool \galight\ to decompose the quasar and its host with multi-band filters available for \hst\ ACS+WFC3 and \jwst\ NIRCAM (12 filters covering \hst\ F606W to \jwst\ F444W).
 As demonstrated, \jwst\ provides the first capability to detect quasar hosts at $z>3$ and enables spatially-resolved studies of the underlying stellar populations at $z\sim2$ within morphological structures (spiral arms, bar) not possible with \hst.
-Overall, we find quasar hosts to be disk-like, lack merger signatures, and have sizes generally more compact than typical star-forming galaxies at their respective stellar, thus in agreement with results at lower redshifts.
+Overall, we find quasar hosts to be disk-like, lack merger signatures, and have sizes generally more compact than typical star-forming galaxies at their respective stellar mass, thus in agreement with results at lower redshifts.
 The fortuitous face-on orientation of SDSSJ1420+5300A at $z = 1.646$ enables us to find higher star formation and younger ages in the central $2-4$ kpc region relative to the outskirts, which may help explain the relatively compact nature of quasar hosts and pose a challenge to AGN feedback models.
@@
 To make further progress, a decomposition of the host galaxy from its central quasar is required to measure the host properties at earlier cosmic times ($z\gtrsim2$) when the central regions of galaxies are forming stars and particularly those that can be spatially resolved.
-At a cosmological distance, galaxies have smaller apparent sizes and become fainter due to cosmological surface dimming.
-The unresolved quasars as bright point sources can outshine the host galaxy, which makes the decomposition of the host challenging, even with {\it Hubble Space Telescope} (\hst) WFC3-IR, which has excelled at $z < 2$.
+At cosmological distances, galaxies have smaller apparent sizes and become fainter due to surface brightness dimming.
+The unresolved quasars, seen as bright point sources, can outshine the host galaxy, which makes the decomposition of the host challenging, even with {\it Hubble Space Telescope} (\hst) WFC3-IR, which has excelled at $z < 2$.
 Owing to this reason, most of the studies in the literature so far have been focused on the moderate-luminosity AGNs whose brightness is comparable to their host ~\citep{Park15, Tre++07, Bennert11, Woo++08, Jah++09, SS13, Mechtley2016,Ding2020, Ding2021, 2021ApJ...906..103L}.
@@
 The infrared coverage at $\lambda > 2 \mu$m provides the ability to probe the galaxy 4000~\angstrom\ break beyond $z\sim 3.5$.
-The unprecedented sensitivity and resolution by \jwst\ will be a key to separating the unresolved quasar component from the extended emission of its host galaxy, particularly due to the larger aperture compared to \hst\ and the stability of the telescope, which effectively improves the characterization of the PSF.
+The unprecedented sensitivity and resolution by \jwst\ is key to separating the unresolved quasar component from the extended emission of its host galaxy, particularly due to the larger aperture compared to \hst\ and the stability of the telescope, which effectively improves the characterization of the PSF.
 
@@
 We limit the AGN sample to those with spectroscopic redshifts to provide accurate stellar masses and sizes of their host galaxies.
-We will carry out an AGN decomposition to reveal the host galaxy and then perform the spectral energy distribution (SED) fitting to infer the stellar mass, star formation rate (SFR), and stellar age.
+We carry out a quasar decomposition to reveal the host galaxy and then perform the spectral energy distribution (SED) fitting to infer the stellar mass, star formation rate (SFR), and stellar age.
 These results will aid in our ability to establish relations between AGN and host galaxy formation with \jwst\ \citep{Kocevski2022}.
@@
 We introduce our decomposition method in Section~\ref{sec:decomp}, including our PSF library construction, decomposition tool, and SED fitting.
-In Section~\ref{sec:result}, we present our measurement result and compare the inferred size mass relations with the ones from the literature.
+In Section~\ref{sec:result}, we present our measurements and compare to the size - mass relations of non-active galaxies from the literature.
 The concluding remarks are presented in Section~\ref{sec:conclusion}.
 Magnitudes are given in AB System.
-A Chabrier initial mass function is employed to measure the galaxy's stellar mass for consistency.
+A Chabrier initial mass function is employed to measure the stellar mass of the host galaxies.
 We use a standard concordance cosmology with $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$.
@@
 The CEERS \jwst\ early release science program (ERS Program \#1345) is designed to cover 100 arcmin$^2$ of the AEGIS fields with imaging and spectroscopic data~\citep{CEERS}.
-This program will observe ten pointings with \jwst/NIRCam as parallel with primary fields to be taken with NIRSpec and MIRI.
+This program will observe ten pointings with \jwst/NIRCam, six with NIRSpec in parallel, and four with MIRI in parallel.
 In late June 2022, four pointings  (CEERS1, CEERS2, CEERS3, and CEERS6) were completed using 7 NIRCam filters: F115W, F150W, F200W, F277W, F356W, F410M, and F444W.
 The integration times are 2,635 seconds for each filter, with the exception of F115W, which was taken with an exposure time twice as long.
-For the CEERS2 pointing, one additional visit is performed with a slightly different PA and positional offset using filters F200W and F444W.
-We refer the reader to~\citet{Finkelstein2022} for more details on the \jwst\ observations and survey design.
+For the CEERS2 pointing, one additional visit was performed with a slightly different PA and positional offset using filters F200W and F444W.
+We refer the reader to~\citet{Finkelstein2022} and the CEERS overview paper (Finkelstein et al.
+in prep) for more details on the \jwst\ observations and survey design including the positions of the three dither pattern.
+This information can also be found via the\dataset[DOI]{https://doi.org/10.17909/3pf0-8b20} information.
 
@@
 \includegraphics[trim={3cm 0cm 3cm 0cm},clip,width=1.8\columnwidth]{figures/psfs_profile.pdf}
-\caption{Selected nine PSF surface brightness (SB) profiles (annuli) as a function of radius (based on stars detected by \jwst) per filter are shown selected from our PSF library compared with the simulated PSF model by \texttt{webbpsf}.
+\caption{Surface brightness (SB) profiles (annuli) of nine select PSFs are shown as a function of radius (based on stars detected by \jwst) per filter and compared with the simulated PSF model from \texttt{webbpsf}.
 The vertical lines indicate the FWHM values of the PSF-stars (averaged) and PSF model by \texttt{webbpsf}.
-We only show the profile's very inner region ($<7$ pixels), which is the key to the AGN subtraction.
-The PSFs in our library demonstrate a very stable performance, while the simulated PSF models by \jwst\ are too narrow (i.e., peaking at the center) for all the filters.
+We only show the inner regions ($<7$ pixels) of these profiles which are key for quasar subtraction.
+The PSFs in our library demonstrate very stable performance, while the simulated PSF models by \jwst\ are too narrow (i.e., peaking at the center) for all the filters.
 \label{fig:PSFprofile}}
@@
 For F444W, we use \textsf{jwst\_0877.pmap}, \textsf{jwst\_0878.pmap} and \textsf{jwst\_0881.pmap}.
-Due to the known issue for the background subtraction with the v.1.5.3 pipeline, we further post-process the stage 2 images as follows.
+Due to the known issue with the background subtraction for the v.1.5.3 pipeline, we further post-process the stage 2 images as follows.
 We first subtracted the background light using \texttt{photutils} based on \textsf{Background2D} function.
@@
 Thus, we do not apply any rotations when drizzling the images.
-For WCS calibration, we use the GAIA DR3 source catalog\footnote{\url{https://gea.esac.esa.int/archive/}}~\citep{GAIA16} to align our image.
+For WCS calibration, we use the GAIA DR3 source catalog\footnote{\url{https://gea.esac.esa.int/archive/}}~\citep{GAIA16} to align the images.
 
@@
 %to 0.3 mag 
-to 20\% uncertainty to conversion between the ADU and flux in filters.
+to 20\% uncertainty in conversion between the ADU and flux in these filters.
+As a note, this reduced data was also effective in identifying a low-luminosity AGN candidate at $z=5$~\citep{2022arXiv220907325O}.
 
@@
 We adopt the filters including ACS/WFC F606W and F814W, and WFC3/IR F125W, F140W, and F160W.
-The final pixel scale has been drizzled to a 0\farcs{}03 for all bands.
+The final pixel scale has been drizzled to 0\farcs{}03 for all bands.
 
@@
 Three SDSS quasars were identified with redshifts at 1.646, 2.588, and 3.442, respectively.
-SDSS1419+5254 ($z=3.442$) falls in CEERS2 and thus has only two \jwst\ filters (i.e., F200W and F444W) available at this moment.
-From AEGIS-X, we also find four quasars with spectroscopic redshifts above $z>1.6$.
-After manually checking, we find that two of them are matched to SDSS quasars\footnote{After the manual confirmation, we find SDSS1419+5254 and AEGIS 585 are the same system;  SDSS1420+5300A and AEGIS 742 are the same system.}.
+SDSS1419+5254 ($z=3.442$) falls in CEERS2 and thus has only two \jwst\ filters (i.e., F200W and F444W) available at the time.
+From AEGIS-X, we found four quasars with spectroscopic redshifts above $z>1.6$ with two of them matched to SDSS quasars\footnote{We find SDSS1419+5254 and AEGIS 585 are the same system;  SDSS1420+5300A and AEGIS 742 are the same system.}.
 As a result, two additional targets are selected with redshift at 2.317 and 3.465, respectively.
@@
 \section{Quasar-host image decomposition} \label{sec:decomp}
-We use our previous 2D image modeling strategy, as fully presented in~\citet{Ding2020}, to perform the AGN decomposition.
+We use our previous 2D image modeling strategy, as fully presented in~\citet{Ding2020} and originally based on HST/WFC3 imaging of quasars at $z\sim1.5$, to perform the AGN decomposition.
 We first build a PSF library by searching for all point sources (i.e., stars) in the \jwst\ field of views (FOVs).
@@
 
-In this paper, we use the previous strategy of~\citet{Ding2022} and collect all isolated, unsaturated PSF stars with sufficient signal-to-noise levels to build our PSF library.
-We use the PSF-pickers (the \texttt{find$\_$PSF()} function) provided by \galight\ (see next section~\ref{subsec:decomp} for details) to help us collect these objects having a point-like feature as our initial PSF candidates through all the \jwst/\hst\ filters in four CEERS visits.
+We use the previous strategy %of~\citet{Ding2020} 
+and collect all isolated, unsaturated PSF stars with sufficient signal-to-noise levels to build our PSF library.
+We use the PSF-pickers (\texttt{find$\_$PSF()} function) provided by \galight\ (see section~\ref{subsec:decomp} for details) to help us collect these objects having a point-like feature as our initial PSF candidates through all the \jwst/\hst\ filters in four CEERS visits.
 By sorting the FWHM values from low to high and manually viewing the local image stamps of each PSF candidate, we select the PSF candidates that are isolated and sharp.
 To build the library, we select at least 12 PSF stars for each filter.
+Note that these PSFs are normalized to unity by \galight\ before fitting.
+We provide the positions of each object used to construct the PSFs for each filter through an online website\footnote{\url{https://github.com/dartoon/my_code/blob/master/share_data/PSF_library_info.txt}}.
 
 It is also known that simulated PSF for \hst\ based on \texttt{TinyTim}~\citep{2011SPIE.8127E..0JK} is usually inaccurate (narrow) and not ideal for our goal of AGN decomposition~\citep[e.g.,][]{Mechtley2012}.
-In this work, we also test the effectiveness of \texttt{webbpsf}~\citep{2014SPIE.9143E..3XP} to generate the PSF model for \jwst\ but find that the simulated PSF is also too narrow compared with the PSF in the library \citep[see][for similar conclusions]{Ono2022}.
-We show the surface brightness profiles of PSF stars and the PSF by \texttt{webbpsf} as a function of the radius (in pixel unit) in Figure~\ref{fig:PSFprofile}.
+In this work, we also test the effectiveness of \texttt{webbpsf}~\citep{2014SPIE.9143E..3XP} to generate the PSF model for \jwst\ but find that the simulated PSF is also too narrow compared with the empirical PSFs our the library \citep[see][for similar conclusions]{Ono2022}.
+We show the surface brightness profiles of PSF stars and the PSF by \texttt{webbpsf} as a function of radius (in pixel unit) in Figure~\ref{fig:PSFprofile}.
 
@@
 \includegraphics[trim={7cm 1.5cm 7cm 0.5cm},clip,width=1.7\columnwidth]{figures/datahost_51.pdf}
-\caption{Science-grade images (1st and 3rd columns) and the host galaxy images (2nd and 4th columns) for the four quasar targets at $z>2$ with F200W and F444W filters are presented.
+\caption{Science-grade images (1st and 3rd columns) and host galaxy images (2nd and 4th columns) for the four quasars at $z>2$ with F200W and F444W filters.
 In each case, the host galaxy image (i.e., data minus quasar) is produced by subtracting the best-fit PSF.
@@
 Dust attenuation and stellar emission lines are also considered in our SED fitting model.
+Note that the seven JWST filters together provide continuous wavelength coverage (see the filters' response in Figure~\ref{fig:sed_spec}) and most of the well-known rest-frame optical emission lines fall within these filters.
+Nevertheless, most of the filters are wide; thus, these emission lines have limited effect on our SED fitting.
+Indeed, we checked this by ignoring the emission lines and re-running the SED fitting which resulted in almost identical stellar properties.
 
@@
 If the scatter is below 0.15 mag, we fix the uncertainty at this value to account for a reported systematic error.
-For AEGIS 482 and SDSS1419+5254, we adopt 0.4 mag for the error since their results are provided by a single PSF.
-For our sample at $z>2$, seven \jwst\ filters cover above and below the 4000~\angstrom\ break; thus, the SED fitting should provide a reliable best-fit galaxy template.
+For AEGIS 482 and SDSS1419+5254, we adopt 0.4 mag for the error for F444W filter, since these results are provided by a single PSF.
+During the SED fitting process, these errors will be used to assess the posterior probability distribution for SED parameters such as ages, stellar mass, and dust attenuation, and to perform a Markov Chain Monte Carlo routine to constrain the likelihood of these parameters.
+For our sample at $z>2$, the seven \jwst\ filters span wavelengths above and below the 4000~\angstrom\ break; thus, the SED fitting should provide a reliable best-fit galaxy template.
 Unfortunately, SDSS1419 currently only has observations with F200W and F444W, both above the 4000~\angstrom\ break.
@@
 The distribution shows that the quasar hosts are mainly located in a star-forming region.
-One quasar host is at the boundary, possibly indicating that the host galaxy is close to transitioning to a more quiescent state.
+One quasar host is at the boundary, possibly indicating that the host galaxy is close to transitioning to a more quiescent state, likely given its high stellar mass ($\sim2\times10^{11}$ M$_{\odot}$).
 Broadly, these results are consistent with numerous studies that demonstrate an association between AGN/quasar activity and ongoing star formation over a wide range of cosmic time.
@@
 In fact, a high AGN fraction is seen in compact star-forming galaxies at $z\sim2$ \citep{Kocevski2017}.
+
+\begin{figure*}
+\centering
+\begin{tabular}{c c}
+\hspace*{-1cm}  
+{\includegraphics[trim={0.6cm 1.1cm 2cm 2.5cm},clip, height=0.4\textwidth]{figures/UVJ.png}}&
+{\includegraphics[trim={1cm 1.1cm 2cm 2.5cm},clip, height=0.4\textwidth]{figures/Mstar-Reff.png}}\\
+\end{tabular}
+\caption{$Left:$ UVJ diagram for the five quasar systems, together with the sample from CANDELS at $1.6<z<3.5$.
+Two systems whose 4000~\angstrom\ break is not constrained by \jwst\ are filled in white.
+$Right:$ Galaxy size--\smass\ distribution and relations.
+The \sersic\ index values are presented by the symbol color.
+For SDSS1420B, \reff\ is labeled using an arrow to indicate an upper limit.
+We also show the best-fit relation reported in~\citet{vdW+2014} for the star-forming (blue line) and quiescent (red line) at $z\sim2.2$.
+We also include six broad-line AGNs at $1.6<z<1.7$ from~\citet{Ding2020} based on \hst/WFC3 imaging.
+\label{fig:sizemass}}
+\end{figure*}
 
@@
 The quasars with size measurements from \jwst\ are consistent with the aforementioned studies.
+Our result is consistent with the recent study using a sample lensed quasars using ALMA at $1.5<z<2.8$ observation~\citep{Stacey2021}, in which the quasar hosts are found to be more compact than normal dusty star-forming galaxies.
 However, a larger sample is required to make definitive claims at $z>2$ and over a broad range in stellar mass.
-As evident, the \jwst\ hosts start to fill in the lower mass regime ($\log~M_*<10.5$), even down to \smass$\sim9~\log$ M$_{\odot}$.
-
+As evident, the \jwst\ hosts start to fill in the lower mass regime ($\log~M_*<10.5$), even down to \smass$\sim10^9$ M$_{\odot}$.
+It is worth noting that the recent work by~\citet{Miller2022} also used CEERS JWST data and identified a population of star-forming galaxies that have an SFR gradient implying centrally concentrated star-formation.
 %that may be simultaneously associated with changes in star formation activity ().
@@
 \centering
-\begin{tabular}{c c}
-\hspace*{-1cm}  
-{\includegraphics[trim={0.6cm 1.1cm 2cm 2.5cm},clip, height=0.4\textwidth]{figures/UVJ.png}}&
-{\includegraphics[trim={1cm 1.1cm 2cm 2.5cm},clip, height=0.4\textwidth]{figures/Mstar-Reff.png}}\\
-\end{tabular}
-\caption{$Left:$ UVJ diagram for the five quasar systems, together with the sample from CANDELS at $1.6<z<3.5$.
-Two systems whose 4000~\angstrom\ break is not constrained by \jwst\ are filled in white.
-$Right:$ Galaxy size-\smass\ distribution and relations.
-The \sersic\ index values are presented by the symbol color.
-For SDSS1420B, \reff\ is labeled using an arrow to indicate an upper limit.
-We also show the best-fit relation reported in~\citet{vdW+2014} for the star-forming (blue line) and quiescent (red line) at $z\sim2.2$.
-We also include six broad-line AGNs at $1.6<z<1.7$ from~\citep{Ding2020} based on \hst/WFC3 imaging.
-\label{fig:sizemass}}
-\end{figure*}
-
-\begin{figure*}
-\centering
-\includegraphics[trim={4cm 0cm 3cm 0cm},clip,width=2.0\columnwidth]{figures/SED_map.pdf}
+\includegraphics[trim={4.8cm 1.5cm 21.5cm 2cm},clip,height=0.5\columnwidth]{figures/SED_map.pdf}\\
+\includegraphics[trim={16.6cm 0.2cm 4.2cm 1.5cm},clip,height=0.65\columnwidth]{figures/SED_map.pdf}
 \caption{Spatially-resolved host properties of SDSS1420A.
-The panels from left to right are as follows: (1) the original quasar color image from combining three \jwst\ filters as indicated, (2) the color image of the host galaxy after the central quasar is subtracted in each filter, (3) the stellar mass map.
-(4) SFR map, and (5) age map.
+The top panels are ($Left$) the original quasar color image from combining three \jwst\ filters as indicated, ($Right$) the color image of the host galaxy after the central quasar is subtracted in each filter.
+The bottom panels from left to right are (1) the stellar mass map.
+(2) SFR map, and (3) age map.
 In various panels, three regions are indicated with a radius of 2~kpc, 4~kpc, and 8~kpc.
-The 2~kpc region is applied as a mask in (3)-(5) panels.}
+The 2~kpc region is applied as a mask in the bottom panels.}
 \label{fig:sedmap}
@@
 SDSS1420A is an ideal laboratory to further study high-$z$ quasar hosts since spatially-resolved properties of the stellar population are feasible due to the angular extent of the host, being face-on, and the spatial resolution of multi-band \jwst\ observations.
-SDSS1420A is a very massive disk galaxy (\smass$\sim11.5~\log$ M$_{\odot}$), thus likely to be fully quenched on a short timescale and transition to a bulge-dominated galaxy.
+SDSS1420A is a massive disk galaxy ($log$~\smass$\sim11.3$), thus likely to be fully quenched on a short timescale and transition to a bulge-dominated galaxy.
 Here, our aim is to demonstrate new science capabilities enabled by \jwst.
-While larger samples will be required to make substantive claims, the CEERS observations of a small quasar sample can already provide further insight into the resolved properties of quasar hosts that have yet to be explored at this resolution.
+While larger samples will be required to make substantive claims, the CEERS observations of a small quasar sample can already provide further insight into the resolved properties of quasar hosts that have yet to be explored at this redshift and resolution.
 
@@
 Since residual PSF features caused by the mismatch are strong in the center pixels, we only consider the region beyond $0\farcs{}24$ ($\sim$2~kpc), which are left unmasked in the images.
-The 2D SED fitting result shows that the inner region seems to have higher SFR and younger age.
-Within an inner annulus (2.0$<$ radius $<$ 4.0 kpc), we measure an average SFR density of 0.54~M$_{\odot}$/yr/kpc$^2$ and age of 1.26 Gyr.
+The 2D SED fitting result shows that the inner region has higher SFR and a younger age.
+Within an inner annulus (2.0 $<$ radius $<$ 4.0 kpc), we measure an average SFR density of 0.54~M$_{\odot}$/yr/kpc$^2$ and age of 1.26 Gyr.
 This SFR density is close to that of normal star-forming disk galaxies (i.e., sBzK) at $z\sim1.5$ \citep{Daddi2010}.
-In a larger annulus (4.0$<$ radius $<$ 8.0 kpc), the SFR density drops to 0.095~M$_{\odot}$/yr/kpc$^2$ while the age rises to 1.64 Gyr.
-The relative SFR density decreases by a factor of $\sim$six.
+In a larger annulus (4.0 $<$ radius $<$ 8.0 kpc), the SFR density drops to 0.095~M$_{\odot}$/yr/kpc$^2$ while the age rises to 1.64 Gyr.
+The relative SFR density decreases by a factor of six.
+Furthermore, the specific star formation rate (sSFR) is $\log$(sSFR/yr$^{-1})=-9.98$ and  $\log$(sSFR/yr$^{-1})=-10.20$ in the inner and outer annulus, respectively.
 Based on our 2D SED fit results, stars are growing in the center region, possibly contributing to the build-up of the bulge component.
 This may argue against simple AGN quenching since one would expect less star formation in the central regions as compared to the outskirts.
-\newpage
 
@@
 This is crucial to probe epochs closer to the formation of massive galaxies and their supermassive BHs, thus better constraining theoretical models of their connection \citep{Volonteri2021, Ding2022}.
+%Kroupa2020\todo{Hi John, Kroupa emailed me to cite this Kroupa2020 which is a comprehensive theory paper. If you feel uncomfortable, you can remove this reference.}
 
@@
 host mag & 20.96$\pm$0.15 & 23.49$\pm$0.26 & 22.87$\pm$0.15 & 23.42$\pm$0.15 & 25.11$\pm$0.34\\
+total mag & 19.715$\pm$0.001 & 21.758$\pm$0.005 & 21.216$\pm$0.008 & 20.995$\pm$0.007 & 21.958$\pm$0.006\\
 $\chi ^2$ (Reduced) & 15.04 & 2.41 & 4.39 & 5.59 & 2.68\\
@@
 host mag & 21.17$\pm$0.58 & 22.81$\pm$0.15 & 23.17$\pm$0.41 & \nodata & 25.16$\pm$0.78\\
+total mag & 19.935$\pm$0.142 & 21.808$\pm$0.008 & 21.042$\pm$0.003 & \nodata & 22.068$\pm$0.003\\
 $\chi ^2$ (Reduced) & 3.24 & 3.34 & 2.22 & \nodata & 1.29\\
@@
 host mag & 20.45$\pm$0.15 & 22.49$\pm$0.15 & 23.0$\pm$0.38 & 23.01$\pm$0.26 & 24.69$\pm$0.41\\
+total mag & 19.497$\pm$0.002 & 21.401$\pm$0.003 & 20.947$\pm$0.005 & 21.043$\pm$0.002 & 21.995$\pm$0.004\\
 $\chi ^2$ (Reduced) & 2.74 & 2.69 & 2.17 & 5.42 & 1.58\\
@@
 host mag & 19.96$\pm$0.15 & 22.27$\pm$0.15 & 22.29$\pm$0.40 & \nodata & 24.6$\pm$0.15\\
+total mag & 18.969$\pm$0.006 & 21.391$\pm$0.001 & 20.953$\pm$0.004 & \nodata & 22.186$\pm$0.001\\
 $\chi ^2$ (Reduced) & 17.36 & 1.11 & 3.56 & \nodata & 3.53\\
@@
 host mag & 19.87$\pm$0.15 & 22.13$\pm$0.17 & 22.58$\pm$0.15 & 23.44 & 24.93\\
+total mag & 18.548$\pm$0.032 & 21.245$\pm$0.039 & 20.83$\pm$0.016 & 21.005$\pm$0.010 & 21.648$\pm$0.009\\
 $\chi ^2$ (Reduced) & 10.45 & 3.27 & 2.03 & 12.13 & 4.21\\
@@
 Note that, for $z>2$ sample, the host measurements provided by \hst\ should be considered highly uncertain.
+The inference of the total (i.e., host+quasar) magnitudes is also provided. Combining with host magnitude, the quasar properties (e.g., magnitude, luminosity) can be obtained.
 }
@@
 \section*{Acknowledgments}
-\begin{acknowledgments}
-We thank the CEERS collaboration that achieves the \jwst\ observation for the data.
+\newpage 
+% \begin{acknowledgments}
+We thank the CEERS collaboration that achieves the \jwst\ observation for the data and for developing their observing program with a zero-exclusive-access period.
 We thank Takahiro Morishita for the help with using the \texttt{gsf} package.
 We thank Simon Birrer for providing the \texttt{psfr} package that has been used for the PSF stacking.
+We thank Connor Bottrell for providing the algorithm for momentum measurement that improves the \galight\ fitting performance.
 We thank Knud Jahnke, Takuma Izumi, Yoshiki Matsuoka, Lilan Yang, and Hassen Yesuf for the useful discussion.
+
+Quasar decomposition works were performed on the {\it idark} cluster at Kavli IPMU, The University of Tokyo.
+
+All of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST) at the Space Telescope Science Institute.
+The specific observations analyzed can be accessed via \dataset[https://doi.org/10.17909/3pf0-8b20]{https://doi.org/10.17909/3pf0-8b20}.
+STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-03127 and NAS5–26555 for JWST.
+Support to MAST for these data is provided by the NASA Office of Space Science via grant NAG5–7584 and by other grants and contracts.
+These observations are associated with program 1345.
 
@@
 M.O. is supported by the National Natural Science Foundation of China (12150410307).
-\\
-\end{acknowledgments}
+% \end{acknowledgments}
 
@@
 
-\bibliography{jwst_hosts}{}
+%\bibliography{jwst_hosts}{}
 \bibliographystyle{aasjournal}
+\input{ding_jwst_v1.bbl}
 

### 2022-11-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/paper submit/submit/ding_jwst_v1.tex
For ceers and upcoming data

--- 2022-11-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/paper submit/submit/apjl_source_file/ding_jwst_v1.tex
@@
 
-\software{\galight\citep{Ding2020,Ding2021a}, \lenstronomy~\citep{2018PDU....22..189B, 2021JOSS....6.3283B}, \texttt{gsf}~\citep{Morishita2019}, \texttt{psfr}\footnoteref{note1} (Birrer et al.
+\software{\galight~\citep{Ding2020,Ding2021a}, \lenstronomy~\citep{2018PDU....22..189B, 2021JOSS....6.3283B}, \texttt{gsf}~\citep{Morishita2019}, \texttt{psfr}\footnoteref{note1} (Birrer et al.
 in prep), \texttt{astropy}~\citep{2013A&A...558A..33A,2018AJ....156..123A}, \texttt{photutils}~\citep{larry_bradley_2020_4044744}}.

### 2022-11-03 projects/2022_CEERS_checkup/real_analysis/model_HST_material/1_generate_and_run_onetarget_Masafusa_z5.py

@@ -125,6 +125,8 @@ zp_list = {'F606W':26.489, 'F814W':25.937, 'F105W':26.264,
 fit_run_all = []
 aper = com_aper_l[0]
 for i, filt in enumerate(filters):
+    
+    #Take the PSF from the otherband fitting:
     fit_files = glob.glob('fit_material/fit_run_idx48_{0}*.pkl'.format(filt))
     fit_run_list = []
     for k in range(len(fit_files)):
@@ -135,12 +137,14 @@ for i, filt in enumerate(filters):
     _fit_run = fit_run_list[sort_Chisq[0]]
     psf = _fit_run.fitting_specify_class.data_process_class.PSF_list[0]
     
+    #Use PSF to run:
     data_process = data_process_list[i]
     data_process.zp = zp_list[filt]
     aper.positions = np.array([32, 50])
     aper.a, aper.b = 3, 3
     data_process.apertures = []
     data_process.PSF_list = [psf]
+    psf[psf<0] = 0
     fit_sepc = FittingSpecify(data_process)
     target_stamp = data_process.target_stamp
     ps_pos = np.where(target_stamp == np.max(target_stamp))
@@ -158,12 +162,23 @@ for i, filt in enumerate(filters):
     fit_run_all.append(fit_run)
     # filt = data_process.filt
     # pickle.dump(fit_run , open('fit_material/'+'fit_run_idx{2}_{0}_psf{1}.pkl'.format(filt, i, idx), 'wb'))
-# pickle.dump([filters, fit_run_all] , open('run_z5_target.pkl', 'wb'))
+pickle.dump([filters, fit_run_all] , open('run_z5_target.pkl', 'wb'))
+
+#%%
+from galight.tools.measure_tools import esti_bgkstd
+from galight.tools.measure_tools import detect_obj, mask_obj
+run_z5_target = pickle.load(open('run_z5_target.pkl','rb'))
+filters, fit_run_all = run_z5_target
 from galight.tools.measure_tools import measure_FWHM
 for i in range(len(filters)):
+    data_process = fit_run_all[i].fitting_specify_class.data_process_class
+    apertures, segm_deblend, mask_apertures, tbl  = detect_obj(data_process.target_stamp)
+    flux = tbl['kron_flux'][0]
+    print(-2.5*np.log10(flux) + zp_list[filters[i]])
+    # data_process = fit_run_all
[…]

### 2022-11-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/1_load_data_process.py

@@ -19,11 +19,11 @@ lines = string.split('\n')   # Split in to \n
 result_folder = 'fit_result/'
 lines = lines[1:]
 remove_id = [24, 55]
-cid = 0
+cid = 10
 
 # files = glob.glob('material/data_process+apertures_*.pkl')
 # files.sort()
-for idx in range(cid,cid+10):
+for idx in range(cid,cid+1):
     if idx in remove_id:
         continue
     line = lines[idx]

### 2022-11-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/4_check_fitrun_allbands_JWST+HST.py

@@ -37,7 +37,7 @@ remove_id = [24, 55]
 # for idx in [29, 53]:  #z_spec > 2
 from functions_for_result import name_list
 result = []
-for idx in [0]:  #CEERS
+for idx in range(10, 21):  #CEERS
     if idx in remove_id:
         continue
     else:
@@ -69,13 +69,26 @@ for idx in [0]:  #CEERS
         lines = string.split('\n')   # Split in to \n
         target_id = [lines[i].split(' ')[1] for i in range(len(lines)) if lines[i].split(' ')[0] == str(idx)][0]
         
+        f = open("./material/target_info.txt","r")
+        string_1 = f.read()
+        lines_ = string_1.split('\n')   # Split in to \n
+        spec_z = [lines_[i].split(' ')[3] for i in range(len(lines_)) if lines_[i].split(' ')[0] == target_id][0]
+        photo_z = [lines_[i].split(' ')[4] for i in range(len(lines_)) if lines_[i].split(' ')[0] == target_id][0]
+        
+        if float(spec_z) >0:
+            z_str = 'spec_z=' + spec_z
+        else:
+            z_str = 'photo=' + photo_z
+        
+        filters = [filters[0], filters[-1]]
+        
         for count in range(len(filters)):
             fit_run_list = []
             idx = idx_info
             filt = filters[count]
             # idx, filt= item
-            fit_files = glob.glob('./*fit_material/fit_run_idx{0}_{1}_*.pkl'.format(idx, filt))+\
-                        glob.glob('../model_HST_material/fit_material/fit_run_idx{0}_{1}_*.pkl'.format(idx, filt))
+            fit_files = glob.glob('./*fit_material/fit_run_idx{0}_{1}_*.pkl'.format(idx, filt))#+\
+                        # glob.glob('../model_HST_material/fit_material/fit_run_idx{0}_{1}_*.pkl'.format(idx, filt))
             fit_files.sort()
             warn_strs = ['F115W_psf6', 'F150W_psf7', 'F277W_psf2']
             for warn_str in warn_strs:
@@ -103,9 +116,11 @@ for idx in [0]:  #CEERS
                 fit_run = fit_run_list[sort_Chisq[3]]
             if idx == '0' and filt == 'F444W':  #!!!
                 fit_run = fit_run_list[sort_Chisq[1]]
[…]

### 2022-11-03 projects/2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/4_plot_SED_fitting.py

@@ -22,7 +22,7 @@ mat.rcParams['font.family'] = 'STIXGeneral'
 folder = '20220906' #mag error bar from top 5 PSF
 
 # for idx in [1,51,2,0,35]:  #z from low to high
-idx = 51
+idx = 35
 
 target_id = name_list[idx]
 folder = 'esti_smass/'+folder+str(idx)
@@ -166,22 +166,22 @@ for i, fid in enumerate(filt_id[::-1]):
     plt.plot(f_fil[1:,1]/10000., f_fil[1:,2], label='{0}'.format(ivd[fid]))
 
 # plt.text( (xmax-xmin)*0.7, (ymax-ymin)*0.53, 'stellar population with:', fontsize=17)
-plt.text( (xmax-xmin)*0.6, (ymax-ymin)*0.63, 'z: {0}'.format(z), fontsize=17)
+plt.text( (xmax-xmin)*0.57, (ymax-ymin)*0.63, 'z: {0}'.format(z), fontsize=17)
 # plt.text( (xmax-xmin)*0.6, (ymax-ymin)*0.43, 'age:  [{1:.3f}, {0:.3f}, {2:.3f}]  Gyr'.format(age, age_l, age_h), fontsize=17)
 # plt.text( (xmax-xmin)*0.6, (ymax-ymin)*0.33, "SFR:  [{1:.3f} {0:.3f} {2:.3f}]".format(sfr, sfr_l, sfr_h) + r" M$_{\rm \odot}$/yr ", fontsize=17)
-plt.text( (xmax-xmin)*0.6, (ymax-ymin)*0.57, 'M$_*$: [{1:.2f}, {0:.2f}, {2:.2f}] log'.format(smass, smass_l, smass_h)+r"M$_{\rm \odot}$", fontsize=17)
+plt.text( (xmax-xmin)*0.57, (ymax-ymin)*0.57, r"M$_*$: [{1:.2f}$\leftarrow${0:.2f}$\rightarrow${2:.2f}] log".format(smass, smass_l, smass_h)+r"M$_{\rm \odot}$", fontsize=17)
 print('M$_*$:  [{1:.2f}, {0:.2f} ,{2:.2f}]'.format(smass, smass_l, smass_h))
 if '{0:.1f}'.format(age_l) == '0.0':
[…]

### 2022-11-03 projects/2022_JWST_QSOz6/model_z6_data/0_check_PSF.py

@@ -1,0 +1,27 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Oct 28 17:23:49 2022
+
+@author: Dartoon
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+
+
+import glob, pickle
+run_folder = 'stage3_all*/' #!!!
+filt = 'F356W'
+idx = 0
+PSF_lib_files = glob.glob(run_folder+'material/*'+filt[:-1]+'*_PSF_Library_idx{0}.pkl'.format(idx))[0]
+PSF_list, PSF_list_clean, PSF_RA_DEC_list, PSF_from_file_list = pickle.load(open(PSF_lib_files,'rb'))
+from galight.tools.astro_tools import plt_fits
+
+# PSF_lib_files = glob.glob('../../2022_CEERS_checkup/real_analysis/model_JWST_stage3_Masafusa/material/*'+filt[:-1]+'*_PSF_Library.pkl')[0]
+# PSF_list, PSF_list_clean, PSF_RA_DEC_list, PSF_from_file_list = pickle.load(open(PSF_lib_files,'rb'))
+
+
+for i in range(len(PSF_list_clean)):
+    plt_fits(PSF_list_clean[i][40:-40, 40:-40])

### 2022-11-03 projects/2022_JWST_QSOz6/model_z6_data/1_build_PSF_library.py

@@ -1,0 +1,155 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Aug 11 11:36:24 2022
+
+@author: Dartoon
+
+come form 0_remove_JWST_bkg.py
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import glob
+import pickle
+from galight.tools.astro_tools import plt_fits
+from galight.tools.astro_tools import plt_many_fits
+
+filters =  ['F150','F356']
+
+data_type = 'all'
+filt = filters[0] #!!!
+file_NO = 0  #!!!
+
+folder = '/Users/Dartoon/Downloads/z6JWSTNIRcam/NIRCam_J2255_stage3_{0}/bkg_removed'.format(data_type)
+idx = 0
+from target_info import target_info
+info = target_info[str(idx)]
+target_id, RA, Dec, z = info['target_id'], info['RA'], info['Dec'], info['z']
+
+from astropy.coordinates import SkyCoord
+from astropy import units as u
+pos = SkyCoord('{0} {1}'.format(RA, Dec), unit=(u.hourangle, u.deg))
+target_pos = np.array([pos.ra.degree, pos.dec.degree])
+#%%
+filter_files= glob.glob(folder+'/*{0}*.fits'.format(filt))  #For NIRCam
+filter_files.sort()
+
+from galight.tools.cutout_tools import psf_clean
+filter_files = [filter_files[file_NO]]
+if data_type == 'all':
+    run_folder = 'stage3_{0}/'.format(data_type)
+elif data_type == 'half':
+    if file_NO == 0:
+        run_folder = 'stage3_first_half/'
+    if file_NO == 1:
+        run_folder = 'stage3_second_half/'
+
+re_select = True
+clean_up = True
+#%% Select PSF library:
+if re_select == True:
+    for filename in filter_files:
+        print("Select for", filename.split('/')[-1])
+        # Grab the JWST provided ERR map:
+        
+        fitsFile = pyfits.open(filename)
+        fov_image = fitsFile[1].data # check the back grounp
+        header = fitsFile[1].header # if target position is add in WCS, the header should have the wcs information, i.e. header['EXPTIME']
+        from galight.data_process import DataProcess
+        from galight.tools.astro_tools import read_pixel_scale
[…]

### 2022-11-03 projects/2022_JWST_QSOz6/model_z6_data/1_generate_data_process.py

@@ -1,0 +1,103 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Aug 15 16:13:10 2022
+
+@author: Dartoon
+
+After 1_align_jwst_astromerty.py. 
+
+Propose: Generate the data_process for JWST and HST together. Apertures will also be generated. 
+
+Template: 1_test_model_allbands.py 
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import glob
+import sys
+import pickle
+from galight.data_process import DataProcess
+from galight.tools.astro_tools import read_pixel_scale
+from galight.tools.measure_tools import measure_bkg
+from astropy.wcs import WCS
+from galight.tools.cutout_tools import common_data_class_aperture
+from galight.tools.plot_tools import plot_data_apertures_point
+from galight.tools.cutout_tools import cutout
+import warnings
+warnings.filterwarnings("ignore")
+
+
+data_type = 'half' 
+filt = 'F150W'
+file_NO = 1
+
+idx = 0
+folder = '/Users/Dartoon/Downloads/z6JWSTNIRcam/NIRCam_J2255_stage3_{0}/bkg_removed'.format(data_type)
+from target_info import target_info
+info = target_info[str(idx)]
+target_id, RA, Dec, z = info['target_id'], info['RA'], info['Dec'], info['z']
+
+# jwst_all_filenames = glob.glob(folder+'/*{0}*{1}*.fits'.format(target_id[:5], filts[0]))
+jwst_all_filenames = glob.glob(folder+'/*{0}*.fits'.format(filt))
+jwst_all_filenames.sort()
+file = jwst_all_filenames[file_NO]
+if data_type == 'all':
+    run_folder = 'stage3_{0}/'.format(data_type)
+elif data_type == 'half':
+    if file_NO == 0:
+        run_folder = 'stage3_first_half/'
+    if file_NO == 1:
+        run_folder = 'stage3_second_half/'
+
+result_folder = run_folder + 'fit_result/'
+#%%
+cut_kernel = None #After pos correct then, do the nearest_obj_center
+# filts = ['F356W', 'F150W']
+for filt in [filt]:
+    _fitsFile = pyfits.open(file)
+    fov_image = _fitsFile[1].data # check the back grounp
[…]

### 2022-11-03 projects/2022_JWST_QSOz6/model_z6_data/2_run_all_DP_fit.py

@@ -1,0 +1,77 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Oct 27 12:02:58 2022
+
+@author: Dartoon
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+
+import glob
+from galight.fitting_specify import FittingSpecify
+from galight.fitting_process import FittingProcess
+from galight.data_process import DataProcess
+from galight.tools.astro_tools import plt_fits
+from galight.tools.measure_tools import measure_bkg
+import pickle
+
+run_folder = 'stage3_second_half/' #!!!
+filt = 'F150W'
+# dp_files = glob.glob('fit_material_second_smFOV/data_process_idx0_*F150W*.pkl')
+# dp_files = glob.glob('fit_material_second_smFOV/data_process_idx0_F356W_FOVpsf2.pkl')
+dp_files = glob.glob(run_folder+'fit_material/data_process_idx0_{0}_FOVpsf*.pkl'.format(filt))
+dp_files.sort()
+
+idx = 0
+from target_info import target_info
+info = target_info[str(idx)]
+target_id, RA, Dec, z = info['target_id'], info['RA'], info['Dec'], info['z']
+
+#%%
+# for i in [0]:
+for i in range(9):
+# for i in range(8,16):
+# for i in range(16,24):
+# for i in range(24, 30):
+# for i in range(30, len(dp_files)):
+    file = dp_files[i]
+    print(file)
+    filename = dp_files[i].replace('data_process', 'fit_run')[:-4]+'_{0}.pkl'.format(i)
+    idx = file.split('idx')[1].split('_')[0]
+    target_id = target_id
+    _data_process = pickle.load(open(file,'rb'))
+    psf = _data_process.PSF_list[-1]
+    psf[psf<0] = 0.
+    psf = abs(psf)
+    _data_process.PSF_list[-1] = psf
+    _data_process.noise_map = np.nan_to_num(_data_process.noise_map, nan=1000)
+    
+    # if int(idx) in [31, 32, 56]:
+    #     ps_pos = np.where(_data_process.target_stamp == _data_process.target_stamp.max())
+    #     ps_pos = (ps_pos[0][0] - _data_process.radius, ps_pos[1][0] - _data_process.radius)
+    #     ps_pos = [ps_pos[1], ps_pos[0]]
+    # else:
[…]

### 2022-11-03 projects/2022_JWST_QSOz6/model_z6_data/3_comb_Best_PSF.py

@@ -1,0 +1,71 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Fri Oct 28 15:03:04 2022
+
+@author: Dartoon
+"""
+
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import glob
+import pickle
+import copy
+
+
+run_folder = 'stage3_second_half/' #!!!
+filt = 'F150W'
+files = glob.glob(run_folder+'fit_material/data_process_idx0_*{0}*_*FOVpsf*.pkl'.format(filt))
+files.sort()
+collect_info = []
+for i in range(len(files)):
+    _file = files[i]
+    idx_info = _file.split('idx')[1].split('_')[0]
+    filt_info = _file.split('W_')[0].split('_')[-1] + 'W'
+    this_info = [idx_info, filt_info]
+    if this_info not in collect_info:
+        collect_info.append(this_info)
+
+# - [ ] F115W_psf6 is QSO (idx 2). [136, 137, 139]
+# - [ ] F150W_psf7 is QSO (idx 2).
+# - [ ] F277W_psf2 is QSO (idx 2).
+
+#%%
+if_printshow = False
+for count in range(len(collect_info)):
+    item = collect_info[count]
+    fit_run_list = []
+    idx, filt= item
+    fit_files = glob.glob(run_folder+'fit_material/fit_run_idx{0}_{1}_*FOVpsf*.pkl'.format(idx, filt))
+    fit_files.sort()
+    
+    for i in range(len(fit_files)):
+        fit_run_list.append(pickle.load(open(fit_files[i],'rb')))
+    chisqs = np.array([fit_run_list[i].reduced_Chisq for i in range(len(fit_run_list))])
+    idx_counts = chisqs.argsort()  
+    if len(idx_counts)<8:
+        print(idx, filt, len(idx_counts))
+    print("work on", count, 'idx', idx, filt, "Total PSF NO.", len(idx_counts))
+    for ct in [2, 3, 5]:
+        _data_process_list = [fit_run_list[i].fitting_specify_class.data_process_class for i in idx_counts[:ct]] 
+        PSF_list_for_comb = [_data_process_list[i].PSF_list[0] for i in range(len(_data_process_list))]
+        _data_process = copy.deepcopy(_data_process_list[0])
+        _data_process.PSF_list  = copy.deepcopy(PSF_list_for_comb)
[…]

### 2022-11-03 projects/2022_JWST_QSOz6/model_z6_data/4_check_fit_run.py

@@ -1,0 +1,94 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Oct 27 12:58:31 2022
+
+@author: Dartoon
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import glob, pickle
+
+idx = 0
+from target_info import target_info
+info = target_info[str(idx)]
+target_id, RA, Dec, z = info['target_id'], info['RA'], info['Dec'], info['z']
+
+# files = glob.glob('./*fit_material*sm*/data_process_idx{0}_*_psf*.pkl'.format(idx))
+# files.sort()
+# run_folder = 'stage3_*/' #!!!
+run_folder = 'stage3_second_half/' #!!!
+z_str = str(z)
+
+# filters = ['F150W', 'F356W']
+filters = ['F150W']
+
+for top_psf_id in [0]:
+    for count in range(len(filters)):
+        fit_run_list = []
+        # idx = idx_info
+        filt = filters[count]
+        PSF_lib_files = glob.glob(run_folder+'material/*'+filt[:-1]+'*_PSF_Library_idx{0}.pkl'.format(idx))[0]
+        # idx, filt= item
+        # fit_files = glob.glob(run_folder+'*fit_material*/fit_run_withcentralMask_idx{0}_{1}_FOV*.pkl'.format(idx, filt))#+\
+        fit_files = glob.glob(run_folder+'*fit_material*/fit_run_idx{0}_{1}_FOV*.pkl'.format(idx, filt))#+\
+        fit_files.sort()
+        for i in range(len(fit_files)):
+            fit_run_list.append(pickle.load(open(fit_files[i],'rb')))
+        chisqs = np.array([fit_run_list[i].reduced_Chisq for i in range(len(fit_run_list))])
+        sort_Chisq = chisqs.argsort()  
+        print('idx', idx, filt, "Total PSF NO.", 'chisq',chisqs[sort_Chisq[top_psf_id]], len(sort_Chisq), fit_files[sort_Chisq[top_psf_id]])
+        fit_run = fit_run_list[sort_Chisq[top_psf_id]]
+        fit_run.plot_final_qso_fit(target_ID = target_id+'$-$'+filt + z_str, save_plot = True)
+        count_n = 5
+        Chisq_best = chisqs[sort_Chisq[top_psf_id]]
+        Chisq_last= chisqs[sort_Chisq[count_n-1]]
[…]

### 2022-11-03 projects/2022_JWST_QSOz6/model_z6_data/backup_files/1_generate_data_process_idx0.py

@@ -1,0 +1,90 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Mon Aug 15 16:13:10 2022
+
+@author: Dartoon
+
+After 1_align_jwst_astromerty.py. 
+
+Propose: Generate the data_process for JWST and HST together. Apertures will also be generated. 
+
+Template: 1_test_model_allbands.py 
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import glob
+import sys
+import pickle
+from galight.data_process import DataProcess
+from galight.tools.astro_tools import read_pixel_scale
+from galight.tools.measure_tools import measure_bkg
+from astropy.wcs import WCS
+from galight.tools.cutout_tools import common_data_class_aperture
+from galight.tools.plot_tools import plot_data_apertures_point
+from galight.tools.cutout_tools import cutout
+import warnings
+warnings.filterwarnings("ignore")
+
+folder = '/Users/Dartoon/Downloads/z6JWSTNIRcam/bkg_removed'
+
+idx = 0
+from target_info import target_info
+info = target_info[str(idx)]
+target_id, RA, Dec, z = info['target_id'], info['RA'], info['Dec'], info['z']
+
+filts = ['F150W']
+jwst_all_filenames = glob.glob(folder+'/*{0}*{1}*.fits'.format(target_id[:5], filts[0]))
+file = jwst_all_filenames[0]
+result_folder = 'fit_result/'
+#%%
+cut_kernel = None #After pos correct then, do the nearest_obj_center
+# filts = ['F356W', 'F150W']
+for filt in filts:
+    _fitsFile = pyfits.open(file)
+    fov_image = _fitsFile[1].data # check the back grounp
+    header = _fitsFile[1].header # if target position is add in WCS, the header should have the wcs information, i.e. header['EXPTIME']
+    flux_mjsr = header['PHOTMJSR']
+    pixscale = read_pixel_scale(header)
+    zp = -2.5*np.log10(2.350443 * 10**(-5) *pixscale**2/3631) #- 2.5*np.log10(flux_mjsr)  #zp for flux
+    wht = _fitsFile[4].data # The WHT map
+    exp = _fitsFile[0].header['EFFEXPTM']
+    if _fitsFile[0].header['CHANNEL'] == 'LONG':
+        gain_value = 2
+        expsize = 1
+        exppix = 1
[…]

### 2022-11-03 projects/2022_JWST_QSOz6/model_z6_data/demonstrate_present.py

@@ -1,0 +1,117 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Nov  2 09:06:09 2022
+
+@author: Dartoon
+"""
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import glob
+import sys
+import pickle
+from galight.data_process import DataProcess
+from galight.tools.astro_tools import read_pixel_scale
+from galight.tools.measure_tools import measure_bkg
+from astropy.wcs import WCS
+from galight.tools.cutout_tools import common_data_class_aperture
+from galight.tools.plot_tools import plot_data_apertures_point
+from galight.tools.cutout_tools import cutout
+import warnings
+warnings.filterwarnings("ignore")
+from target_info import target_info
+from galight.tools.astro_tools import plt_fits, plt_many_fits
+#%%
+data_type = 'all' 
+filt = 'F356W'
+file_NO = 0
+
+idx = 0
+folder = '/Users/Dartoon/Downloads/z6JWSTNIRcam/NIRCam_J2255_stage3_{0}/bkg_removed'.format(data_type)
+info = target_info[str(idx)]
+target_id, RA, Dec, z = info['target_id'], info['RA'], info['Dec'], info['z']
+# jwst_all_filenames = glob.glob(folder+'/*{0}*{1}*.fits'.format(target_id[:5], filts[0]))
+jwst_all_filenames = glob.glob(folder+'/*{0}*.fits'.format(filt))
+jwst_all_filenames.sort()
+file = jwst_all_filenames[file_NO]
+if data_type == 'all':
+    run_folder = 'stage3_{0}/'.format(data_type)
+elif data_type == 'half':
+    if file_NO == 0:
+        run_folder = 'stage3_first_half/'
+    if file_NO == 1:
+        run_folder = 'stage3_second_half/'
+result_folder = run_folder + 'fit_result/'
+
+#%%Demonstrate the local envs.
+cut_kernel = None #After pos correct then, do the nearest_obj_center
+# filts = ['F356W', 'F150W']
+for filt in [filt]:
+    _fitsFile = pyfits.open(file)
+    fov_image = _fitsFile[1].data # check the back grounp
[…]

### 2022-11-03 projects/2022_JWST_QSOz6/model_z6_data/figure_0.py

@@ -1,0 +1,186 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Wed Nov  2 23:19:06 2022
+
+@author: Dartoon
+"""
+
+
+import numpy as np
+import astropy.io.fits as pyfits
+import matplotlib.pyplot as plt
+import glob
+import sys
+import pickle
+from galight.data_process import DataProcess
+from galight.tools.astro_tools import read_pixel_scale
+from galight.tools.measure_tools import measure_bkg
+from astropy.wcs import WCS
+from galight.tools.cutout_tools import common_data_class_aperture
+from galight.tools.plot_tools import plot_data_apertures_point
+from galight.tools.cutout_tools import cutout
+import warnings
+warnings.filterwarnings("ignore")
+from target_info import target_info
+from galight.tools.astro_tools import plt_fits, plt_many_fits
+#%%
+data_type = 'all' 
+filt = 'F356W'
+file_NO = 0
+
+idx = 0
+folder = '/Users/Dartoon/Downloads/z6JWSTNIRcam/NIRCam_J2255_stage3_{0}/bkg_removed'.format(data_type)
+info = target_info[str(idx)]
+target_id, RA, Dec, z = info['target_id'], info['RA'], info['Dec'], info['z']
+# jwst_all_filenames = glob.glob(folder+'/*{0}*{1}*.fits'.format(target_id[:5], filts[0]))
+jwst_all_filenames = glob.glob(folder+'/*{0}*.fits'.format(filt))
+jwst_all_filenames.sort()
+file = jwst_all_filenames[file_NO]
+if data_type == 'all':
+    run_folder = 'stage3_{0}/'.format(data_type)
+elif data_type == 'half':
+    if file_NO == 0:
+        run_folder = 'stage3_first_half/'
+    if file_NO == 1:
+        run_folder = 'stage3_second_half/'
+result_folder = run_folder + 'fit_result/'
+
+#%%Demonstrate the local envs.
+import copy, matplotlib
+from matplotlib.colors import LogNorm
+my_cmap = copy.copy(matplotlib.cm.get_cmap('gist_heat')) # copy the default cmap
+my_cmap.set_bad('black')
+
+def coordinate_arrows(ax, d, header, color='white', arrow_size=0.02):
+    wcs = WCS(header)
[…]

### 2022-11-03 projects/2022_JWST_QSOz6/model_z6_data/target_info.py

@@ -1,0 +1,13 @@
+#!/usr/bin/env python3
+# -*- coding: utf-8 -*-
+"""
+Created on Thu Oct 27 11:32:30 2022
+
+@author: Dartoon
+"""
+
+target_info = {'0': {'target_id': 'J2255+0251', 
+                      'RA': '22:55:38.0400',
+                      'Dec': '+02 51 26.60',
+                      'z': 6.34} } 
+
